### 2015-09-15 abstract.tex
Adding files for the original article

%% Abstract
The problem of file synchronization (making two, differently modified
copies of a filesystem the same again without losing information) emerges
in many cases, and is solved in many different ways. Our goal was to
create a \emph{general mathematical model} for file synchronization and
use it as a basis to define the behavior of a synchronizer.

We developed a specific algebraic model on filesystem commands and proved
that it is sound and complete for its intended interpretation on real
systems, that is, if commands are considered to be equivalent according to
the algebra then they are equivalent when applied to a real filesystem and
vice versa.

Then we defined algorithms for synchronization using our algebra and
created an implementation which was tested on various filesystems. This
method turned out to be an effective way to create the specification of a
synchronizer since it simplified both the definition and the
implementation.

The methods used in the proofs for soundness and completeness are likely
be usable on other algebras, too. Thus using algebraic approach could make
it possible to extend the synchronizer to other types of datasystems and
to create a general theory of synchronization in the future.

### 2015-09-15 ack.tex
Adding files for the original article

%% Acknowledgments
\section{Acknowledgements}

%I would like to thank everybody who made it possible for me to write
%this paper. 
I would like to thank my mentor, 
{Norman Ramsey}
%\footnote{Norman Ramsey is a professor at Harvard University (Electrical
%Engineering and Computer Science).}
for offering me such a fascinating project and for giving me a hand when
all the theorems and proofs seemed to be incorrect. I also appreciate the
constructive criticism of my tutor, {Jenny Sendova} 
who was so kind as to read
through the drafts several times and tirelessly untangle my absolutely
confusing complex sentences. I thank {LeeAnn Tzeng} for her remarks
on the paper which helped me a lot to make it more understandable.

Also I would like to thank all sponsors and members of staff of the
{Research Science Institute} for making the research possible.

### 2015-09-15 algorithm.tex
Adding files for the original article

%% Reconcilation algorithm
\section{Algorithm for reconciliation}
\label{sec:alg}

In this section we provide an algorithm for reconciliation. The reconciler
algorithm takes sequences leading from the original filesystem to the
replicas (\(S_1, S_2, \ldots S_n\)) and creates sequences of commands for
each replica \(S_1^*, S_2^*, \ldots S_n^*\) which make the
filesystems as close as possible. 
%%%\(S_i^*\) contains all
%%%non--conflicting commands from \(S_1, S_2, \ldots S_n\) which is not
%%%already applied to \(S_i\). 
%%%\begin{notrsi}
%%%We also would like to be sure that if there
%%%are no conflicting commands, then after synchronization, all replicas
%%%should be the same.
%%%\end{notrsi}

%%%Thus, 
When creating the algorithm, we keep in mind the following:\\
\emph{a command 
\(C\in {S}_1\cup{S}_2\cup\ldots\cup{S}_n\) 
should be propagated to replica \(R_i\) iff:}
\begin{itemize}
\item \(C\) is not already applied to \(R_i\)
\item there are no conflicts on command \(C\)
\item there are no conflicts on any command which must precede \(C\) 
\end{itemize}

\medskip
{\small{
Why do we need the last criterion? Consider the following case: in the
original replica we had \(O(\pi)=\cfile{X}\). 
We modified replica \(A\) with the following
commands: \(edit(\pi,\cdir{Y}); create(\pi\cdot p,\cfile{W})\).
Replica \(B\) was modified by the command \(edit(\pi,\cfile{Z})\).
Now \(edit(\pi,\cdir{Y})\) and \(edit(\pi,\cfile{Z})\) are
conflicting commands, so we cannot apply \(edit(\pi,\cdir{Y})\) to replica
\(B\). But that way, we cannot propagate
\(create(\pi\cdot p,\cfile{W})\) to it either.
\remark{However, if \(O(\pi)\) was a directory, it could be.}
}}\medskip

%We also need to determine which commands must precede another
%one. Clearly
A
command \(C_1\) must precede command \(C_2\) iff 
\(\neg(C_1; C_2\eqifnbr C_2; C_1)\), it originally preceded \(C_2\),
and they appear in the same sequence \(S_i\). 
%Note that we define this property only
%if \(C_1\) and \(C_2\) are from the same sequence since otherwise they
%would be conflicting commands.

Now, in order to preserve the order of commands in sequences 
\(S_1, S_2, \ldots S_n\), we define the algorithm as follows:
\begin{notrsi}
\\
\emph{To determine \(S_i^*\):}
\begin{enumerate}
\item Detect conflicting commands between sequences
\item Detect must--follow conflicting commands
\item Omit these commands from all sequences
\item Omit commands in \(S_i\) from all other sequences
\item Define \(S_i^*\) as 
\(S_1; S_2; \ldots S_{i-1}; S_{i+1}; \ldots S_n\)
\end{enumerate}
Or, more formally:
\end{notrsi}
\begin{alltt}
FOR every sequence \(S\sb{i}\)
  FOR each command \(C\in S\sb{i}\)  
    FOR every sequence \(S\sb{j}\)
      IF \(C\) should be propagated to replica \(R\sb{j}\) THEN
        append \(C\) to \(S\sb{j}\sp{*}\).
\end{alltt}

We can get the sequence of conflicting commands using a similar
algorithm. The reconciler produces two sequences for every replica: the
first one (\(S_i^*\)) can be applied to the replica immediately, while
the second one (conflicting commands, \(S_i^C\)) needs the user's or
other algorithms' help to be resolved.

See Appendix~\ref{app:impl} for test result of the implementation of the
algorithm.

\begin{comment}
\subsection{Move and subtree-detection}

In order that we should apply less commands on the filesystem or the user
would have to deal with smaller amount of conflicting commands we should
try to detect operations on whole subtrees (e.g. removing a directory not
by removing all files under it first, but by using one delete command).

Also, to ease the user that no information will be lost if a file has been
moved we should detect the move operation rather than use delete and
create commands.

Both of these problems can be solved easily.
Subtree--detection by majority voting which means that we should use
an operation on a subtree if the same operation would be applied to the
majority of its descendants.

Move--detection can be done by tracking the contents of files.
We use data--fingerprints, a compressed identification string for each
file to determine whether the contents of a new file 
%which should be created
are the same as that of a file already present in the replica, say 
\(contents_F(\pi)=contents_F(\varphi)\). Suppose that we are about to
create \(F(\pi)\). If (according to the sequence of commands) we should
remove \(F(\varphi)\), we will use \(move(\varphi\to\pi)\). If not, we can
use \(copy\). In both cases, we avoided to transmit a huge amount of data 
between the replicas.
\end{comment}

### 2015-09-15 bp.tex
Adding files for the original article

%% Comparing our definition to B&P
\section{Equivalence of definitions of conflicting updates}
\label{cbp:bp}

In this section we try to find a relation between
a definition for conflicting updates found in \BP~(\cite{BP:whatis}) and
our definition.

\subsection{Detecting conflicts using ``dirtiness''}
\label{subsec:defdirty}

In \BP, we can read about an update--detection method whose result when
applied to filesystems \(O\) and \(A\) is a set
\(dirty_A\) for which the following holds:
\begin{itemize}
\item
\(\pi\not\in dirty_A \implies A(\pi)=O(\pi)\) holds where \(O\) is the
original filesystem (Definition 3.1.1 in \BP).
\item
\(dirty_F\) is up--closed for any filesystem,
that is, if \(\pi\preceq\piesub\) and \(\piesub\in dirty_F\) then \(\pi\in
dirty_F\) (Fact 3.1.3).
\end{itemize}
This set is a \emph{safe estimate} of paths where updates have been
made, that is, it may contain paths where the replica has not
changed.

According to the paper, there's a conflict at path \(\pi\) iff
\(\pi\in dirty_A, dirty_B\) and \(A(\pi)\neq B(\pi)\) and
\((A(\pi)\neq\cdir{X})\vee(B(\pi)\neq\cdir{Y})\).
We write \(conflict(\pi)\) if there are conflicting updates at
path \(\pi\) according to this definition. (Definition 4.1.2)

\subsection{Does a conflict at paths imply that there are
conflicting commands?}
\label{subsec:pathimplcom}

Consider the following case. 
We have the original filesystem:
\[\begin{array}{r@{}l@{}l}
O=\{&root&\mapsto\cdir{X};\\
&root\cdot dir&\mapsto\cdir{Y};\\
&root\cdot dir\cdot file&\mapsto\cfile{Z}\}\end{array}\]
In replica A, we apply the following commands to \(O\): 
\(remove(root\cdot dir\cdot file); remove(root\cdot dir)\).
In replica B, we use
\(remove(root\cdot dir\cdot file)\).
Now, according to the definitions in subsection
\ref{subsec:defdirty}, \(root\cdot dir\cdot file\in dirty_A\) and 
\(root\cdot dir\in dirty_A\). We know that \(root\cdot dir\cdot file\in
dirty_B\) and therefore \(root\cdot dir\in dirty_B\) (\(dirty_B\) is
up--closed). Thus we have a conflicting command at path 
\(root\cdot dir\), because it's dirty in both replicas and 
\(A(root\cdot dir)=\ud\), so one of the filesystem entries at that path is
not a directory.

If we investigate this case using sequences, there's no conflict. Since we
know that 
\(S_A=remove(root\cdot dir\cdot file); remove(root\cdot dir)\) and
\(S_B=remove(root\cdot dir\cdot file)\), we can apply the second
command in \(S_A\) to replica \(B\) because it does not conflict
with any command in \(S_B\). (We think this case is not a conflicting
update, however, some file synchronizers, like \emph{unison}, detect such
an update here.)

Therefore, unfortunately, conflicting paths do not imply 
conflicting commands.

\subsection{A conflict at commands implies a conflict at paths}
\label{subsec:comimplpath}

%Again, consider the following case.
%
%In this example we show problems which emerge when we try to edit
%directories or distinguish between them by their contents (properties).
%Suppose that we have an original filesystem \(O\) with one directory
%\(D\). Then we change the properties of this directory in replica
%\(A\) in
%a different way than in replica \(B\) (for example we modify the
%permissions of it). Clearly path \(D\) is dirty in both
%replicas. But the definition does consider this neither a conflict nor a
%resolvable update according to the specification of the reconciler
%provided in section 4.1.2 in \BP~since both \(A(D)\) and \(B(D)\) are
%directories. In other words, this specification does not refer to such a
%case.
%
%This is why we disallow editing directories or telling them apart 
%by comparing their contents. Therefore we modify or model for the
%proof such that
%\remark{I'm not sure this is enough How to formalize this?}
%the contents of every directories are the same and directories cannot be
%modified, that is, if \(F(\pi)=\cdir{X}\) then 
%\(edit(\pi,\cdir{Y})F=\ud\).

We prove this theorem for two replicas.

We prove that if we have filesystems \(O,A,B\neq\ud\) and we have
the minimal sequences \(S_A\) and \(S_B\) and the dirty--sets
\(dirty_A\) and \(dirty_B\) from the update--detectors then if we have
conflicting commands in the sequences we have dirty--conflicts too.

The fact that we gained the sequences from update--detectors allows us to
assume that there are no superfluous commands in the sequences, e.g. a
command which leaves the filesystem in the same state.

Since we cannot distinguish between directories by their contents in the
model of \BP, we have some preconditions.

Our theorem is true if:
\begin{itemize}
\item commands do not modify directories to directories (that is,
\(O(\pi)=\cdir{X}\implies edit(\pi,\cdir{Y})\not\in\) \(S_A\) or
\(S_B\)) 
\emph{and}
\item all directories have the same contents (that is, for any \(F\) and
\(G\), if
\(F(\pi)\) is a directory and \(G(\gamma)\) is a directory then
\(F(\pi)=G(\gamma)\));
\item and there are no superfluous commands in \(S_A\) and \(S_B\).
\end{itemize}

First of all, notice that \(C_A(\pi)\confl C_B(\gamma)\) can be true only
if \(\pi\preceq\gamma\) or \(\gamma\preceq\pi\). (Otherwise they
would commute.) Without loss of generality suppose the first
one is true. Now we know: \(C_A(\pi)\confl C_B(\piesub)\), where
\(\piesub=\gamma\).

Our theorem is that 
\[\mbox{\bf if~} C_A(\pi)\confl C_B(\piesub) \mbox{~\bf then~}
conflict(\pi),\]
that is, there's a dirty--conflict at path \(\pi\).

\emph{Proof.} We know that \(C_A(\pi)\in S_A\) therefore 
\(O(\pi)\neq S_AO(\pi)\) where \(O\) is the original filesystem (remember
that we don't have superfluous commands). 
Hence \(\pi\in dirty_A\) according to the definition of this set.

The same holds for \(C_B(\piesub)\) therefore \(\piesub\in dirty_B\). This
implies that \(\pi\in dirty_B\) since \(dirty_B\) is up--closed.

Now we need to show that \(A(\pi)\) or \(B(\pi)\) is not a
directory. Suppose that both of them are directories. That is,
\(A(\pi)=S_AO(\pi)=\cdir{X}\). In other words (\(S_A\) is
minimal) \(C_A(\pi)O(\pi)=\cdir{X}\) since there are no other
command on this path. 
Thus \(C_A(\pi)\) is \(create(\pi,\cdir{X})\) 
or \(edit(\pi,\cdir{X})\), but we can be sure that 
\(O(\pi)\neq\cdir{X}\) because otherwise we would edit (modify) a
directory to a directory, and by assumption we cannot do that.

We also know that \(B(\pi)=S_BO(\pi)=\cdir{X}\) since we don't distinguish
between directories. Since we know that \(O(\pi)\neq\cdir{X}\),
we must have a command on \(\pi\) in \(S_B\), namely \(C_B^*(\pi)\). 
This command can be either \(create(\pi,\cdir{X})\) or
\(edit(\pi,\cdir{X})\) but it is equivalent to \(C_A(\pi)\) since
we must use \(create\) in both cases if \(O(\pi)=\ud\) and \(edit\) if
\(O(\pi)=\cfile{X}\). But then \(C_A(\pi)\in S_B\) since
\(C_A(\pi)=C_B^*(\pi)\in S_B\) which
contradicts the definition of conflicting commands.

We also need to show that \(A(\pi)\neq B(\pi)\). If so, similarly
to the above, \(C_A(\pi)=C_B^*(\pi)\) would hold.

Now we know that every condition of a dirty--conflict holds. Our theorem
is proved.

### 2015-09-15 compl.tex
Adding files for the original article

%% Proof for completeness theorem +foreword
%%%\begin{forrsi}
\section{Proof of the completeness theorem}
\label{app:compl}

Let us repeat our theorem and introduce minimal sequences again:
\[\begin{array}{r@{}l}
\forall S,S':&\\
&((\forall G: (SG\ne\ud\wedge S'G\ne\ud)\implies SG=S'G)\\
&\wedge\\
&(\exists F: SF\ne\ud\wedge S'F\ne\ud\wedge SF=S'F)\\
&\implies S \eqifnbr S'),
\end{array}\]
where \(G\) and \(F\) refer to filesystems.
%%%\end{forrsi}
%%%%%%%%%%%%%%%%%
%%%\begin{notrsi*}
%%%\newcommand{\varsection}[1]{\subsubsection{#1}}%
%%%\end{notrsi*}
%%%\begin{forrsi*}
\newcommand{\varsection}[1]{\subsection{#1}}%
%%%\end{forrsi*}

In the proof, by \(F\), we
mean a filesystem which satisfies the second condition. By \(G\), we
refer to any filesystem which satisfies \(SG\ne\ud\wedge S'G\ne\ud\).

Now consider the set of sequences \(\wp_S = \{ S^* | S \eqexp S^*\}\).
Because of our preconditions, the sequence \(break\) is not in
\(\wp_S\) (if it was, that is, \(S\eqexp break\), \(SF=\ud\) would hold
since by definition \(SF=(break)F\) if \(SF\ne\ud\)).

Let \(S_0\) be (one of) the shortest sequence(s) in \(\wp_S\) and
similarly
\(S^\prime_0\) (one of) the shortest sequence(s) in \(\wp_{S^\prime}\). 
%
The following holds for these sequences:
\[(SG\ne\ud\wedge S'G\ne\ud\implies) \quad SG=S'G=S_0G=S'_0G\ne\ud.\]
\begin{notrsi}
\emph{Proof.} Since 
\(SG\ne\ud\wedge S\eqexp S_0\implies SG=S_0G\) and
\(S'G\ne\ud\wedge S'\eqexp S'_0\implies S'G=S'_0G\); and since
\(SG\ne\ud\wedge S'G\ne\ud\) by assumption \(SG=S'G\ne\ud\) holds,
we have \(S_0G=SG=S'G=S'_0G\ne\ud\).

As a special case, we also know that \(SF=S'F=S_0F=S'_0F\ne\ud\).

\medskip
\end{notrsi}
Now let's investigate these ``minimal'' sequences.

\varsection{Investigating the command \emph{edit}}

We know that the command \(edit(\pi,\cdir{X})\) commutes or collapses
(i.e., a commuting or a simplifying law can be applied to it) with
every command on its left side (see Laws \lawi, \lawip, \lawiv,
\lawvp, \lawvip,
\lawiiiap, \lawxiii, \lawxviii, \lawxix, \lawxxiv, \lawxxvi, \lawiib).
%
We also know that \(edit(\pi,\cfile{X})\) does the same on its right side
(see Laws \lawi, \lawip, \lawiv, \lawv, \lawvi, \lawiia, \lawiiib, \lawx,
\lawxi, \lawxii, \lawxxiv, \lawxxv).
%
From Laws \lawi, \lawip~and \lawxxiv~we know that \(edit\)s commute
amongst each other.

Therefore in a minimal sequence all \(edit(\pi,\cdir{X})\) commands can be
moved to the beginning, and all \(edit(\pi,\cfile{X})\) commands to the
end of the sequence. Since they commute amongst themselves, we can order
the two groups alphabetically. Therefore if there were two commands on
the same path, they would be neighbors and would be simplified by the
algebraic laws. 
Therefore we can be sure that there are at most one
\(edit(\pi,\cfile{X})\) or \(edit(\pi,\cdir{X})\) command on each path.

That way we also separated these commands from the other ones.
Now we focus on the remaining part: on the \(create\) and 
\(remove\) commands.

\varsection{Investigating \emph{create} and \emph{remove}}
\label{theorem:crrm}

We will prove some lemmas about minimal sequences.
\begin{description}
%%\begin{notrsi*} 
\item[Lemma 0]
%%\end{notrsi*}
%%\begin{notrsi}
If a sequence is minimal, then it cannot have any pairs that match the
left-hand sides of Laws \lawx--\lawxxxv, \lawiia, \lawiiap, \lawiiib.
Also, if we apply any of the
commutative laws 
(\lawi, \lawip, \lawiib, \lawiiia, \lawiiiap, \lawiv--\lawix),
the resulting sequence is still minimal.

\emph{Proof.}
For the first part, the laws mentioned all give an equivalent shorter
sequence, but by hypothesis, there is no equivalent shorter sequence.
For the second part, the commutative laws don't change the length of a
sequence.
%%\end{notrsi}

\item[Lemma 1] {\bf It is impossible that a command
\(remove(\pi)\) precedes (not necessarily as a neighbor) a command
\(remove(\piesub)\) in a minimal sequence.} 
\begin{notrsi}
(A parent can't be removed before any descendant, or
more precisely, \(\not\exists i,j: i<j \land S[i] = remove(\pi) \land
S[j] = remove(\pi') \land \pi \preceq \pi'\).)
\end{notrsi}
\begin{notrsi}
\begin{center}
\begin{tabular}{c|c|c|c|c|c|c|c|c}
\hline
\(\cdots\) & & \(S[i]: remove(\pi)\) & & & & &
\(S[j]: remove(\piesub)\) & \(\cdots\) \\
\hline
\end{tabular}
\end{center}
\end{notrsi}
\emph{Proof.}
By contradiction; we assume there is such an \(i\) and \(j\), and we show
that implies \(S \eqexp break\).

We show the contradiction by induction on \(j-i\).
The base case is \(j = i+1\).
In this case, by Laws \lawxxii~and~\lawxxiii, 
\(S[i]; S[i+1] \eqexp break\),
and therefore \(S\eqexp break\).

For the induction step, we perform a case analysis on \(S[j-1]\).
\begin{itemize}
\item
If it mentions a path that is disjoint with \(\piesub\),
%or if $\pi \prec \piesub$ and it is $edit(\pi, \cdir X)$,
we can swap it
with \(S[j]\) to get an equivalent sequence, and by the induction   
hypothesis and transitivity of equivalence, \(S\eqexp break\).
%\item
%By Lemma 0 (Laws~3B, 12, and~25), it cannot be any other edit operation.
\item
Also by Lemma 0 (Laws~\lawxvi, \lawxvii, and~\lawxxvii), it cannot be a
non-disjoint create operation. (Note that there are no \(edit\) operations
in this part of the sequence according to our preconditions.)
\item
If $S[j-1] =remove(\hat\pi)$, if $\hat\pi \preceq \piesub$, then by laws
\lawxxii~and~\lawxxiii, $S[j-1]; S[j] \equiv \{break\}$, and therefore 
$S\eqexp\{break\}$.
But if $\piesub \prec \hat\pi$, then by transitivity $\pi \preceq
\hat\pi$, so the induction hypothesis applies, and again 
$S \eqexp break$.
\end{itemize}

\begin{forrsi}
The following lemmas can be proved with a similar method.
%For the sake of brevity, the proofs are omitted.
\end{forrsi}
\item[Lemma 2]
{\bf A command \(create(\pi)\) can not precede a command  
\(remove(\piesub)\).} 
\begin{notrsi}
\emph{Proof.} 
This can be proved the same way, only
the base case differs; now 
\(create(\pi); remove({\piesub})\) equals \(break\) or expands 
to \(skip\) by Law \lawxvi~and \lawxxvii.
The induction step is the same.
\end{notrsi}

\item[Lemma 3]
{\bf A command \(remove(\piesub)\) can not precede a command
\(create(\pi)\).} 
\begin{notrsi}
\emph{Proof.} This can be proved similarly, in this 
case the base step is
\(remove(\piesub); create({\pi})\) equals \(break\) or
expands to \(edit\) (Law \lawxxi~and \lawxxviii);
in the induction step we can prove that if
\(S[j-1]=create(\pisup)\) precedes \(S[j]=create(\pi)\), according to
the induction hypothesis, \(S\eqexp break\) 
(we know that \(\pisup\prec\pi\)). Otherwise the commands
would be able to be simplified (which contradicts the condition being
minimal sequence) or commuted (and therefore the induction hypothesis
still holds). (Laws \lawvii,
\lawviii, \lawxiv, \lawxv, \lawxx, \lawxxi, \lawxxviii.)
\end{notrsi}

\item[Lemma 4]
{\bf A command \(create(\piesub)\) can not precede a command
\(create(\pi)\).} 
\begin{notrsi}
\emph{Proof.} 
We obtain this result from Lemma 3: the base step is 
\(create(\piesub); create({\pi}) \equiv (\eqexp) break\) (Law 15); the
induction step is the same.
\end{notrsi}

\item[Lemma 5]
{\bf A command \(create(\piesub)\) can not precede a command
\(remove(\pi)\).} 
\begin{notrsi}
\emph{Proof.} 
Our base step now is 
\(S[j-1];S[j]=create({\piesub}); remove(\pi)\eqexp skip\) or equals
\(break\) according to Laws \lawxxvii~and \lawxvii.
But in our induction step, we go in the opposite direction and perform
analysis on \(S[i+1]\).
If \(S[i+1]=create({\piesub}_{sub})\) follows \(S[i]=create(\piesub)\),
the induction hypothesis applies, therefore \(S\eqexp break\). Otherwise
the commands could be simplified or commuted (Laws \lawxviii, \lawxiv,
\lawxv, \lawxvi, \lawxvii, \lawxxvii.)
\end{notrsi}

\item[Lemma 6] 
{\bf It is impossible that a command \(remove(\pi)\)
precedes a command \(create(\piesub)\).} 
\begin{notrsi}
\emph{Proof.} 
Now our base step is
\(remove(\pi); create(\piesub)\eqexp edit\) or equals to
\(break\) (Laws \lawxxviii~and \lawxx). In the induction step we
examine command \(S[i+1]\). 
If it's not commutable or simplifyable,
it can be only \(remove(\pisup)\).
In that case the induction hypothesis applies.
\end{notrsi}
\end{description}

\varsection{More lemmas on commands}

Now we go back to \(edit\) commands. We will prove two additional lemmas.
\begin{description}
\item[Lemma E1] {\bf A command \(remove(\pi)\) cannot precede a command
\(edit(\pi,\cfile{X})\).} \emph{Proof.} 
By contradiction; we assume there are such two commands in the sequence,
\(S[i]=remove(\pi)\) and \(S[j]=edit(\pi,\cfile{X})\) where \(i<j\). We
use induction on \(j-i\). The base
step is when \(j-i=1\). Now, according to Law \lawxviii, \(S\equiv
break\) which contradicts our condition on \(S\).
For the induction step, we assume that \(S\eqexp break\) if
\(S[j-1]=edit(\pi,\cfile{X})\). Now we investigate \(S[j-1]\). If it is
not \(remove(\pisub)\), then a commuting (or simplifying) law can be
applied to \(S[j-1];S[j]\). That way
\(S[j-1]\) would be \(edit(\pi,\cfile{X})\), and according to the
induction hypothesis \(S\eqexp break\). If \(S[j-1]\) is
\(remove(\pisub)\), we have the same result by Lemma 1.

\begin{forrsi}
The following lemmas can be proved similarly.
\end{forrsi}
\item[Lemma E2] {\bf A command \(create(\pi)\) cannot precede a command 
\(edit(\pi)\).} 
\begin{notrsi}
\emph{Proof.} The same; last step is made according to
Lemma 2.
\end{notrsi}

\item[Lemma E3] {\bf A command \(remove(\pi)\) cannot follow a
command \(edit(\pi,\cdir{X})\).} 
\begin{notrsi}
\emph{Proof.} 
This proof is also very similar to the aboves. The base step is 
\(edit(\pi,\cdir{X}); remove(\pi)\equiv remove(\pi)\) (Law \lawxxv). In the
induction step we investigate command \(S[i+1]\). If it was not
\(create(\pisub)\), a commuting (or simplifying) law could be applied. If
it is, we have \(S\eqexp break\) according to Lemma 5.
\end{notrsi}

\item[Lemma E4] {\bf A command \(create(\pi)\) cannot follow a
command \(edit(\pi,\cdir{X})\).} 
\begin{notrsi}
\emph{Proof.} The same; last step
according to Lemma 4.
\end{notrsi}
\end{description}

\noindent
Keeping in mind that we have all the \(edit\) commands at the ends of the
sequence, it follows from Lemma E1, E2, E3 and E4 that there cannot be an
\(edit\) and another command on the same path.

\begin{description}
\item[Lemma E5] {\bf A command \(edit(\pi,\cdir{X})\) cannot precede a law
\(edit(\pi,\cfile{X})\).} \emph{Proof.} Now we know that between these
commands there are no commands on path \(\pi\). We also know from Lemmas
1---6 that there is at most one \(remove\) or \(create\) command on each
path. Therefore
there cannot be a \(create(\pisub)\) command since we would have to
remove it before modifying \(\pi\) to a file.
Thus we could have moved \(edit(\pi,\cdir{X})\) to the end of the sequence
and simplify it with \(edit(\pi,\cfile{X})\).
\end{description}

\varsection{Conclusions}
\label{theorem:conc}

As a result of the lemmas we know that
\emph{there is at most one command on each path in a minimal sequence.}

Now we prove that \(C\in S_0\Longleftrightarrow C\in S'_0\) for any
command \(C\). (Without loss of generality, it is enough to prove that 
\(C\in S_0\implies C\in S'_0\).)
\begin{itemize}
\item \(create(\pi,X)\in S_0\implies create(\pi,X)\in S'_0\). 
\emph{Proof.} By contradiction. First of all, we know that
\(F(\pi)=\ud\) otherwise \(S_0\) would break \(F\) and that would
contradict our assumption. Now assume that 
\(create(\pi,X)\not\in S'_0\). 
We have three cases. If there is no command on path \(\pi\) in
\(S'_0\) then \(S'_0F(\pi)=\ud\) and therefore 
\(S_0F(\pi)\ne S'_0F(\pi)\), that is, \(S_0F\ne S'_0F\) which contradicts
our assumption that \(S_0F=S'_0F\). If there was a command \(edit\) or
\(remove\) on path \(\pi\), it would break \(F\) since \(F(\pi)=\ud\) and
that again contradicts the precondition.

\item \(remove(\pi)\in S_0\implies remove(\pi)\in S'_0\).
\emph{Proof.} 
\begin{forrsi}
It can be done similarly to the case of \(create\).
\end{forrsi}
\begin{notrsi}
Now we can be sure that \(F(\pi)\ne\ud\) and
\(S_0F(\pi)=\ud\). If (instead of
\(remove\)) there was no command on \(\pi\) in \(S'_0\) then 
\(S'_0F(\pi)\ne\ud\)  would hold. In case of \(edit\), 
\(S'_0F(\pi)\ne\ud\) would hold (contradicting
\(S_0F(\pi)=\ud\)). \(create\) would break \(F\) since
\(F(\pi)\ne\ud\). Again, we have contradiction in all cases.
\end{notrsi}

\item \(edit(\pi,X)\in S_0\implies edit(\pi,X)\in S'_0\).
\emph{Proof.} Similarly we cannot have \(create\) or \(remove\) on path
\(\pi\) in sequence \(S'_0\) since \(F(\pi)\ne\ud\) and 
\(S'F(\pi)=SF(\pi)\ne\ud\). 
But now we might have no commands on
\(\pi\) in \(S'_0\): that way if \(F(\pi)=X\) then \(S_0F(\pi)=X\) and
\(S'_0F(\pi)=X\), too. 
But clearly \(\neg(S_0\eqifnbr S'_0)\). To prove that this is also
impossible, we need the first condition about all filesystems.

Define
\(H\) as \(F\{\pi\mapsto Y\}\) where \(Y\) has the same type
(file/directory) as \(F(\pi)\). If \(SF\ne\ud\) then \(SH\ne\ud\) since no
command breaks the filesystem because of the contents (not the type) of a
file or directory. Also, \(S'F\ne\ud\implies S'H\ne\ud\). Now, as a
special case of \(S_0G=S'_0G\) (note that 
\(SH\ne\ud\wedge S'H\ne\ud\) holds) we know
that \(S_0H=S'_0H\). But \(S_0H(\pi)=edit(\pi,X)H(\pi)=X\) and
\(S'_0H(\pi)=H(\pi)=Y\). We have a contradiction, therefore the lemma is
proved.
\end{itemize}

This means that
\emph{\(S_0\) and \(S^\prime_0\) contain the same commands;} they can be
different only in the order of the commands.

\medskip
Now we will show that they can be made exactly the same by the
commuting algebraic laws.

We know that \(edit\)s can be moved to the ends of the sequences and
ordered. Let's suppose they are arranged this way.
Since we know that the two sequences contain the same
commands, these parts of the sequences is the same.
Therefore we can omit them in the discussion. Now we focus on
\(create\)s and \(remove\)s as we did above.

%%%\begin{notrsi}
If there are two commands in a minimal sequence
referring to comparable directories, according to the lemmas, they
can only be
%not be
%\begin{itemize}
%\item \(remove(\pi) \ldots remove(\pisub)\)
%\item \(remove(\pi) \ldots create(\pisub)\)
%\item \(create(\pisub) \ldots create(\pi)\)
%\item \(create(\pisub) \ldots remove(\pi)\)
%\item \(create(\pi) \ldots remove(\pisub)\)
%\item \(remove(\pisub) \ldots create(\pi)\).
%\end{itemize}
%The remaining possibilities are:
\begin{itemize}
\item \(create(\pi) \ldots create(\pisub)\)
\item \(remove(\pisub) \ldots remove(\pi)\).
\end{itemize}

Therefore any two \(create\) or \(remove\) commands in a (minimal)
sequence can be freely interchanged if they refer to incomparable
directories, but they have a well--defined order otherwise. (Keep in
mind that we have no \(edit\) commands in this part of the sequences.)
That is, we have a partial order over the set of these commands. Note
that we cannot have cycles in this order (since that way \(\pi\) would 
be equal to one of its descendants). Because of this, there is always
a minimal element, which has no predecessors. Also, this ordering is the
same on both sequences. 
%%%\end{notrsi}

We prove that the commands can be ordered the same way by induction on the
length of the sequences. If it
is \(1\), the problem can be solved easily. If the length of the sequences
are \(i>1\), we can choose a command from \(S_0\) which has no
preceding commands (i.e., a command which must precede it).
It is sure that it has no precedents in \(S'_0\). Now we
can move this command to the front of the sequences. Now the rest of
the sequences have length \(i-1\) therefore we can order them according to
the induction hypothesis.

We obtain \(S_0^*\) by applying this method to \(S_0\) and
\({S^\prime_0}^*\) from \(S^\prime_0\). Since they contain the same
commands, and the resulting order is the same,
\(S_0^*\) and
\({S^\prime_0}^*\) are \emph{exactly the same}. Now we have
\(S\eqexp S_0\eqexp S_0^*\equiv{S^\prime_0}^*\eqshr S^\prime_0\eqshr
S^\prime\), that is, \(S\eqifnbr S^\prime\). Our theorem is proved.
\begin{forrsi}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\end{forrsi}

\begin{CMNT}
It is also can be shown that 
\(S\equiv S'\). \emph{Proof.} We already know
that \(S\eqifnbr S'\). It means that we have a chain of sequences, 
\(S\eqexp S_1\eqexp S_2\ldots S'\) so that we gained each sequence by
applying a law to the preceding one. If \(S\not\equiv S'\), we used
somewhere an `\(E\)'--marked law, namely \(S_i\eqexp S_{i+1}\). It could 
be Law \lawiib, \lawxxiv, \lawxxvii~or \lawxxviii. [??...]
\end{CMNT}

### 2015-09-15 conclusion.tex
Adding files for the original article

%% Conclusion
\section{Conclusion}

We built an algebra of commands on filesystems. Then we proved that the
algebra is sound and complete, that is, commands which are algebraically
equivalent commands are also equivalent on real filesystems, and vice
versa.

We defined conflicts with the help of this algebra, then we defined
algorithms for update--detection and reconciliation. Finally, we
implemented these algorithms and tested it on numerous cases (see
Appendix \ref{app:impl}). The results were always in accordance with what
we expected from the philosophy ``propagate every command possible on
every replica''.  Because of that, using algebraical methods in file
synchronization turned out to be an effective solution.

We also gained some information about the provability of such theorems and
algebras. The methods we used in the proofs are likely be able to be used
in proofs for other algebras as well, so that we would be able to create a
more general theory of synchronization.

### 2015-09-15 confl.tex
Adding files for the original article

%% Definition of conflicts
\section{Definition of conflicting commands}
\label{cbp:defconfl}

We define conflicting updates using minimal sequences made by the
update detector algorithm. Actually, we define conflicting \emph{pairs
of commands} since only two modifications can interfere with each other.
Later we will mark every command as a conflicting command if
it was a member of a conflicting pair.

Consider two commands, \(C_A(\pi)\in S_A\) and \(C_B(\gamma)\in S_B\) 
where \(S_A\) is the minimal sequence which
leads the original filesystem \(O\) to replica \(A\) and similarly,
\(S_B\) leads \(O\) to replica \(B\).

Now \(C_A\) and \(C_B\) are conflicting commands iff
\begin{center}
\((C_B\not\in S_A)\wedge(C_A\not\in S_B)\)\\\medskip
\emph{and} one of the following holds:\\\medskip
\begin{minipage}{12cm}
\begin{itemize}
\item \(\neg(C_A(\pi); C_B(\gamma) \eqifnbr C_B(\gamma); C_A(\pi))\)
 (they do not commute), \emph{or}
\item \(C_A(\pi); C_B(\gamma) \equiv break\), \emph{or}
\(C_B(\gamma); C_A(\pi) \equiv break\)\\(they break every
filesystem).
\end{itemize}\end{minipage}
\end{center}

We write \(C_1\confl C_2\) if \(C_1\) and \(C_2\) are conflicting
commands.
\begin{notrsi}
Clearly this relation is symmetrical i.e.,
\(C_1\confl C_2\implies C_2\confl C_1\).
\end{notrsi}

In appendix \ref{cbp:bp} we try to find a relation between this
definition and another one found in \BP.

### 2015-09-15 definition.tex
Adding files for the original article

%% Definitions: filesystem, path, commands
\section{Definitions}
\label{theorem:def}
\subsection{The filesystem}
We introduce some known notations on filesystems and paths.

A filesystem can be \emph{broken} (\(F=\ud\))
or it can be a function mapping whole paths to their
contents. The filesystem is broken if a command caused an error, for
example deleting a directory with files under it.

A \emph{path} is either empty (/), or a finite sequence of names
separated by \(\cdot\). The concatenation of paths \(\pi\) and
\(\varphi\) can be written as \(\pi\cdot\varphi\).
We write
\(\pi\preceq\gamma\) iff \(\pi\) is a prefix of \(\gamma\), i.e., if
\(\gamma=\pi\cdot\alpha\) for some path \(\alpha\) which might be
empty. We also write
\(\pi\prec\gamma\) if \(\pi\) is a proper prefix of \(\gamma\), that is,
\(\pi\preceq\gamma\) and \(\pi\ne\gamma\). If we refer to the contents of
path \(\pi\) in filesystem \(F\), we write simply \(F(\pi)\).

In the paper, \(\pisub\) always refers to a file or directory under
\(\pi\), that is, \(\pi\prec\pisub\). For \(\piesub\),
\(\pi\preceq\piesub\) holds. The same for the opposite direction:
\(\pisup\prec\pi\) and \(\piesup\preceq\pi\). Paths \(\pi\) and
\(\varphi\) are usually incomparable paths.

In a filesystem, the contents of a path can be broken (\(F(\pi)=\ud\),
if the file or directory does not exist), they can be
a file (\(F(\pi)=\cfile{X}\)) or a directory (\(F(\pi)=\cdir{Y}\)).  
We also write \(X\) or \(Y\) for some unspecified but non-\(\ud\)
contents.
\begin{notrsi} 
Both files and directories can carry additional information
(modtimes, permissions, the bytes in a file, etc.), which we leave
unspecified, simply writing the contents as shown above.
\end{notrsi}

Filesystems are functions and are compared using extensional equality.
Two filesystems \(F_1\) and \(F_2\) are equivalent iff
\((F_1=\ud)\wedge(F_2=\ud)\),
\emph{or} \(\forall\pi: F_1(\pi)=F_2(\pi)\).

We write \(F\{\pi \mapsto X\}\) for the function that is like \(F\),
except it maps \(\pi\) to \(X\).
\begin{notrsi}
So
\[F\{\pi \mapsto X\}(\gamma)=
\begin{cases}
X,&\mbox{if $\pi=\gamma$}\\
F(\gamma), &\mbox{otherwise}
\end{cases}\]
\end{notrsi}

We write \(childless_F(\pi)\) iff \(F(\pi)\) has no descendants,
i.e. \(\forall\gamma: \pi\prec\gamma\implies F(\gamma)=\ud\).

\(parent(\pi)\) denotes the path which immediately precedes \(pi\), that
is, for some name \(\mathbf{p}\), \(parent(\pi)\cdot \mathbf{p}=\pi\).

\(S\) always refers to sequences of commands. \(SF\) is the filesystem
obtained by applying all commands in \(S\) to \(F\). We may also write a
command instead of \(S\). \(S_1;S_2\) refers to the concatenation of
sequences \(S_1\) and \(S_2\).

We have some restrictions on filesystems: all filesystems must satisfy
the \emph{tree property}, that
is, if \(\pi\prec\gamma\) and \(F(\gamma)\neq\ud\) then
\(F(\pi)=\cdir{X}\). It means that every path which has a descendant must
be a directory.

\subsection{Commands}

Now we introduce the basis of our algebra: the commands on filesystems.

At first, we
thought about using four commands: \(create\), \(remove\), \(edit\) and
\(move\), as the most common commands on a filesystem. Later, \(move\)
turned out to be hard to handle in the algebra. We decided to introduce
this command only in the user interface, after running the synchronizer.
We also needed a command to reason about commands that cause errors
(\(break\)). So we took another set of commands; it consists of the
commands \(create\), \(remove\), \(edit\) and \(break\). In appendix
\ref{app:update-move} we provide an argument to justify using a
move--free
algebra.

\begin{notrsi}
All the commands have the following property: if applied to a filesystem,
then it either breaks the system (\(command(\pi,X)F=\ud\)) or 
\(command(\pi,X)F=F\{\pi\mapsto X\}\); that is, if a command does not
break the filesystem, it only affects the filesystem at the path on which
it was applied. 
\end{notrsi}

Now we define the exact behavior of each command.
%We have four commands: \emph{create, edit, remove} and \emph{break.} 
Applied to the broken filesystem, they all have the same effect:  leaving
the filesystem in the broken state. Otherwise, 
the definition of their effect is the following:

\begin{notrsi}
\begin{itemize}
\item
\(create(\pi,X)\) modifies \(F(\pi)\) to \(X\) iff
\(F(\pi)\) is broken and its parent is a directory; i.e.
\[create(\pi,X)F=
\begin{cases}
F\{\pi\mapsto X\}, &\mbox{iff~} F(\pi)=\ud
\wedge F(parent(\pi))=\cdir{Y}\\
\ud, &\mbox{otherwise.}
\end{cases}\]
\item
The command \(edit\) can change the type of a path (file or
directory), according to its second argument.
Since the tree--property must be preserved, the definition is:
\begin{align*}
edit(\pi,\cdir{X})F&=
\begin{cases}
F\{\pi\mapsto \cdir{X}\}, &\mbox{iff~}
F(\pi)\neq\ud\\
\ud &\mbox{otherwise;}
\end{cases}\\
edit(\pi,\cfile{X})F&=
\begin{cases}
F\{\pi\mapsto\cfile{X}\} &\mbox{iff~}
F(\pi)\neq\ud\wedge childless_F(\pi)\\
\ud &\mbox{otherwise.}
\end{cases}
\end{align*}
\item
\(remove(\pi)\) only removes files or directories without files:
\[remove(\pi)F=
\begin{cases}  
F\{\pi\mapsto\ud\} &\mbox{iff~}
F(\pi)\neq\ud \wedge childless_F(\pi)\\
\ud &\mbox{otherwise.}
\end{cases}\]
\item
\(break\) breaks the filesystem:
\[\begin{array}{r@{}ll}
breakF&{}=\ud &\mbox{for every $F$.}\end{array}\]
\end{itemize}
\end{notrsi}
%
\begin{forrsi}
{\small{
%\begin{align}
\begin{gather*}\begin{array}{r@{}ll}
create(\pi,X)F&{}=F\{\pi\mapsto X\}, 
&\mbox{iff~}(F(\pi)=\ud)\wedge(F(parent(\pi))=\cdir{Y})\\
&{}=\ud, &\mbox{otherwise.}\\
edit(\pi,\cdir{X})F&{}=F\{\pi\mapsto \cdir{X}\}, 
&\mbox{iff~}F(\pi)\neq\ud\\
&{}=\ud &\mbox{otherwise;}\\
edit(\pi,\cfile{X})F&{}=F\{\pi\mapsto\cfile{X}\} 
&\mbox{iff~}(F(\pi)\neq\ud)\wedge(childless_F(\pi))\\  
&{}=\ud &\mbox{otherwise.}\\
remove(\pi)F&{}=F\{\pi\mapsto\ud\} 
&\mbox{iff~}(F(\pi)\neq\ud)\wedge(childless_F(\pi))\\
&{}=\ud &\mbox{otherwise.}\\
breakF&{}=\ud &\mbox{for every $F$.}
\end{array}\end{gather*}
%\end{align}
}}
\end{forrsi}
%%%%%%%%%% TAGS!
We write \(\emptyseq\) for the empty sequence of commands.

### 2015-09-15 impl.tex
Adding files for the original article

%% Description of implementation
\section{Implementation}
\label{app:impl}

We created an implementation based on the algorithms described in Section
\ref{sec:alg} and Appendix \ref{app:upd}. Its main purpose was to
verify that the algorithms are implementable and they work as we expect
them. The program is written in Perl and it runs under UNIX
systems. It handles two replicas and does not modify the filesystem; it
only detects updates and conflicts among commands. Then it provides the
sequences of commands which should be applied to the replicas.

It has no archives of the filesystem, therefore we must also provide it
the original version of the filesystems. This is because the
implementation was built to examine the algorithms, not to make a complete
synchronizer. It also does not simplify the outcoming sequences with
\(move\) commands or commands on subtrees.

When referring to the contents of directories, it looks at the writable
flags of a directory. That is, the contents of two directories are
different if one of them is writable for the program and the other one is
not.

The brief description of its method is the following:
\begin{enumerate}
\item Creates flat representations of the original filesystem and the
replicas \(O(), A(), B()\).
\item Update--detection: defines the minimal sequences \(S_A, S_B\) for
which \(S_AO=A\) and
\(S_BO=B\).
\item Orders these sequences using the method discussed in 
section \ref{app:upd}.
\item Reconciling: detects conflicting commands in sequences.
\item Provides sequences \(S_A^*\) and \(S_B^*\) for
reconciliation.
\item Provides a list of paths where conflicts occurred.
\end{enumerate}

\subsection{Equivalence of \emph{edit} and \emph{create} commands}

To be able to determine whether two \(edit\) or \(create\) commands are
equivalent, we introduced a \emph{list of samples} in the program, which
is a list of paths.
When the program detects an \(edit(\pi,X)\) or a
\(create(\pi,X)\) command as an update, it looks for a path \(\gamma\) in
the list for
which \(A(\pi)=A(\gamma)\) (in case it is detecting updates at replica
\(A\)). If it finds such a \(\gamma\), it will attach its number in the
list to the command. If not, it appends \(\pi\) to the list and attaches
the new number.

That way, two \(edit\) or \(create\) commands are equivalent if and only
if they are applied to the same path and they have the same
sample--number.

\subsection{Notation}

The program uses the ordinary \texttt{directory/directory/file} notation
for paths. For commands, it uses:
\begin{center}\begin{tabular}{rcl}
\texttt{EF0/path} &for& \(edit(path,\cfile{X})\) \\
\texttt{ED0/path} &for& \(edit(path,\cdir{X})\) \\
\texttt{CF0/path} &for& \(create(path,\cfile{X})\) \\
\texttt{CD0/path} &for& \(create(path,\cdir{X})\) \\
\texttt{RM/path} &for& \(remove(path)\), 
\end{tabular}\end{center}
where \texttt{0} is the sample--number for which 
\(A(Samplelist(\texttt{0}))=A(\texttt{path})\).

When marking conflicting commands, it uses `\texttt{<->A3}' if the command
conflicts with the 3\({}^{rd}\) command in sequence \(S_A\) and
`\texttt{==>A3}' if the command \(S_A[3]\) must precede the current
command but it already conflicts, so the current command cannot be
applied.

\subsection{Examples}

In this section we provide some examples of how the program runs. In the
first section of the output the program lists the flat representation of
the filesystems (the original and the two replicas). The next section is
the result of the detection of updates and conflicting commands. It lists
the samples and the sequences of commands (\(S_A\) and \(S_B\)). Then
sequences \(S_A^*\) and \(S_B^*\) follow which should be applied to
replicas to propagate non--conflicting commands. In the last section it
lists paths where there were conflicts.

\begin{forrsi*}  
\begin{singlesp}
\end{forrsi*}
%%\begin{multicols}{2}
\subsubsection{Example 1}
This example is the case we discussed in section \ref{subsec:pathimplcom}.
\begin{center}
{\small{
\begin{alltt}\input{exp1}\end{alltt}
}}
\end{center}
As we can see, a situation like this does not cause conflicting updates.
\subsubsection{Example 2}
This example shows a case when we have conflicts because a conflicting
command must precede another. \texttt{/dir/file} was modified in replica
\(A\).
\begin{center}
{\small{
\begin{alltt}\input{exp4}\end{alltt}
}}
\end{center}
Actually, in this case the synchronizer cannot do anything, because all
commands conflicted.
%%\end{multicols}
\begin{forrsi*}
\end{singlesp}
\end{forrsi*}

### 2015-09-15 intro.tex
Adding files for the original article

%% Introduction
\section{Introduction}

If we have multiple copies (called \emph{replicas}) of a filesystem or a
part of a filesystem (for example on a laptop and on a desktop
computer), it is often the case that changes are made to each
replica independently and as a result they do not contain the same
information. In that case, a \emph{file synchronizer} is used to make them
similar (consistent) again, without losing any information.

The goal of a file synchronizer is to \emph{detect conflicting updates}
and \emph{propagate non--conflicting updates on each replica.} Due to the
various cases of file updates and the various behaviors of filesystem
commands it is difficult to give a complete and correct definition of its
behavior.

It can be helpful in solving this problem if we have a
formalized mathematical model for describing file synchronization.

We investigated algebraic models of synchronization in a specific case to
see the properties of such a system and the method of proving theorems in
it which will hopefully aid us to create a general theory of
synchronization based on algebraic structure in the future. This specific
case was the synchronization of filesystems.

In the paper we develop an algebraic representation of filesystem
commands. Then we show that this model is both complete and sound,
and after that we define the expected behavior of a file synchronizer and
create its specification with the help of our algebra.

This method will
hopefully simplify the specification as well as the implementation of the
synchronizer, and it might make it possible to extend the synchronizer to
other types of datasystems, such as mail folders or databases.

\subsection{The main idea of synchronization}

In general, two phases of a synchronizer's task can be separated: the
\emph{update detection}, when the program recognizes where updates have
been made since the last synchronization and \emph{reconciliation}, when
it combines updates to yield a new, synchronized version of each replica.
If there are no conflicting updates, then at the end of the
synchronization the replicas will be the same. Otherwise a synchronizer
may leave them unchanged at paths where conflicts occurred and warn the
user about them.

In this paper,
we focus on the commands that were applied to these replicas while they
were modified independently. The main aim of a synchronizer is to perform
\emph{all} commands on \emph{all} replicas.

%\remark{Explanation why we DO need O?}
Let us introduce some notation. We have the original system, \(O\); 
and the present replicas \(R_1, R_2, \ldots R_n\).
Somehow we know the sequences of commands which were applied to
\(O\) in each replica (for example from the update detector). They are
\(S_1, S_2, \ldots S_n\). The synchronizer algorithm will provide us
commands on each replica (\(S_1^*, S_2^*, \cdots S_n^*\)) which lead each
replica to a common state \(O'\) if possible.
%, that is, 
%\(S_1^*R_1=S_2^*R_2=\cdots=S_n^*R_n=O'\).

In order to determine each sequence \(S_i^*\), we take all commands
applied
to the systems (\(S_1\cup S_2\cup \cdots\cup S_n\)) then omit commands
in \(S_i\) which were already applied to replica \(R_i\).

But that way we only gain a \emph{set} of commands without order. We
must order it somehow to be able to apply the commands to the
system. But it is possible that some orders cause errors in a filesystem
(for example, trying to remove a directory before removing the files in
it). It is also possible that not all error--free orders have the same
effect on the filesystem. For example, modifying the contents of a file to
``xxx'' and modifying them to ``yyy'' are not commutable commands: they
leave the system in different states if applied in different order to it.
In this case the synchronizer cannot synchronize the systems fully, since
``last modifying wins'' is not a good solution in every case.  
Therefore the aim of the synchronizer is to find commands for which 
\emph{all error--free orders have
the same effect} and apply them to the system.

The reason we may have two differently ordered sequences of commands which
do not lead a system to the same state is that we have incommutable pairs
of commands in them. This is because if all pairs of commands
commuted (that is, pair of commands \(C_1; C_2\) had the same effect on
a system as \(C_2; C_1\)) then clearly one of the sequences could be
changed to the other one by commuting commands
without any change in the effect of the sequence on the system.

Because of this, we focused on the commutability of pairs of commands.  
We defined this property with the help of an algebraic 
proof system on commands.% for commutivity. %%%

%\subsection{Synchronizing filesystems}
%This specific case was the synchronization of a filesystem.

### 2015-09-15 sound.tex
Adding files for the original article

%% Proof for the soundness theorem + foreword
%%%\begin{forrsi}
\section{Proof for the soundness theorem}
\label{app:theosound}

Let us repeat our statement:
We prove that for every two sequences of commands 
\begin{gather*}
S\equiv S^* \implies \forall F: SF=S^*F,\\
S\eqexp S^*\wedge SF\ne\ud \implies \forall F: SF=S^*F.%\\
%S\eqifnbr S^*\wedge SF\ne\ud \wedge S^*F\ne\ud 
%\implies \forall F: SF=S^*F.
\end{gather*}
%%%\end{forrsi}

Both statement is true if our axioms and inference rules are sound since
we can only gain equivalent (or extending) sequences from axioms
or by using inference rules.

First, we prove the soundness of our inference rules. The proof for the
first two inference rules are quite similar. For the first one, we know
that the intended interpretation of \(S_1\equiv S_2\) is true and our
statement is that for every \(S,S'\), the interpretation of
\(S;S_1;S'\equiv S;S_2;S'\) holds. 
We know that for every filesystem
\(F\), \((S;S_1;S')F=S'(S_1(SF))\) and similarly
\(((S;S_2;S')F=S'(S_2(SF))\). We know that for every
\(G\), \(S_1G=S_2G\) holds, and therefore
as a special case \(S_1(SF)=S_2(SF)\). Thus
\(\forall F: (S;S_1;S')F=((S;S_2;S')F\). This is the interpretation of our
statement.

For the second law, we now that the interpretation of 
\(S_1\eqexp S_2\) is true and we show that in that
case \(S;S_1;S'\eqexp S;S_2;S'\) also true for filesystems. 
We know that for every \(F\) if \(S_1F\ne\ud\) then \(S_1F=S_2F\). If
\((S;S_1;S')F=\ud\) then the relation is clearly true (since it refers to
only the case if the filesystem is not broken). In the other case, if
\((S;S_1;S')F=S'(S_1(SF))\ne\ud\), we know that \(SF\ne\ud\) since
%%\remark{`defined' is not quite defined}
a filesystem cannot be made non--broken again by applying commands to it.
Now since \(S_1\eqexp S_2\) is true therefore either 
\(S_1(SF)=\ud\) and the relation is true similarly to the case above;
or \(S_1(SF)\ne\ud\) and therefore
\(S_1(SF)=S_2(SF)\ne\ud\) and \(S'(S_1(SF))=S'(S_2(SF))\ne\ud\).

The soundness proof of the third law is quite simple since if two
sequences act the same on \emph{all} filesystems then they act the same on
a subset of the filesystems, too.

It remains to show the soundness of each individual law,
but all the laws were derived from the definitions of the
commands. For precise proofs,
Appendix~\ref{app:soundness} shows an example.

Our theorem is proved.

### 2015-09-15 theorems.tex
Adding files for the original article

%% Algebra, laws, inference rule, description of theorems
\section{Algebra on commands}
\label{theorem:laws}

In order to reason about commands, we define \emph{algebraic laws} on
commands. We use formal logic to build a proof system which is sound and
complete for its intended interpretation.

For sequences \(S_1\) and \(S_2\), we have two kinds of judgements:
\begin{itemize}
\item \(S_1\equiv S_2\), or \emph{\(S_1\) is algebraically equivalent to
\(S_2\)}. Its intended interpretation is that they act the same on all
filesystems, i.e. \(\forall F: S_1F=S_2F\).
\item \(S_1\eqexp S_2\), or \emph{\(S_2\) extends \(S_1\)}; its intended
interpretation is the following: if \(S_1\eqexp S_2\) and 
\(S_1F\ne\ud\) then \(S_1F=S_2F\).
%%%
%%% Transitivity? == => =C ?
%%%
\end{itemize}

%%%% REF!!
The axioms of our proof system are the laws listed in Table 1. We have two
inference rules, one for each judgement.

\subsection{The laws}

We created the laws with the help of pairs of commands.
Lines in the last section are not axioms; they are written
there to list all possible pairs.

\begin{notrsi}
\medskip
{\small{
How many pairs do we have? 
For the first group of laws which contain a pair of commands from
\(edit\), \(create\) and \(remove\), we can choose a pair 9 ways.
We have four types of
path-pairs: \(\pi;\pi\), \(\pisub;\pi\), \(\pi;\pisub\)
and \(\pi;\varphi\). That makes \(4\times9\) cases. With \(break\), we have
\(3\times 2\) cases
with an other non--break command (there are 3 types and they can follow
or precede \(break\)) and one case when we have a pair made of two
\(break\)s. Thus, we have \(4\times 9+3\times2+1=43\) pairs. 
}}
\medskip
\end{notrsi}

We subdivide some laws containing \(edit\) because of \(edit\)'s different
behavior when modifying paths to files or to directories. These laws are
numbered with A or B.
Extension laws (that is, where the relation is \(\eqexp\), not
\(\equiv\)) are marked with \(E\).
%%%
%%% reference
%%%
(See table 1 for the laws.)

\ifnum\Textsize=1%
\def\crlw{\)\\\indent\(}%
\else%
\def\crlw{\relax}%
\fi%
\newcommand{\lawsection}[1]{\par\medskip{\bf{#1}}\medskip\\}%
\def\lawi{1}%
\def\lawip{2}%
\def\lawiib{4A${}_E$}%
\def\lawiibp{3A}% not true semilaw
\def\lawiiia{5A}%
\def\lawiiiap{6A}%
\def\lawiv{7}%
\def\lawv{8}%
\def\lawvi{9}%
\def\lawvp{10}%
\def\lawvii{11}%
\def\lawviii{12}%
\def\lawvip{13}%
\def\lawviiip{14}%
\def\lawix{15}%
\def\lawiia{3B}%
\def\lawiiap{4B}%
\def\lawiiib{5B}%
\def\lawx{16}%
\def\lawxi{17}%
\def\lawxii{18}%
\def\lawxiii{19}%
\def\lawxiv{20}%
\def\lawxv{21}%
\def\lawxvi{22}%
\def\lawxvii{23}%
\def\lawxviii{24}%
\def\lawxix{25}%
\def\lawxx{26}%
\def\lawxxi{27}%
\def\lawxxii{28}%
\def\lawxxiii{29}%
\def\lawxxiv{30${}_E$}%
\def\lawxxv{31}%
\def\lawxxvi{32}%
\def\lawxxvii{33${}_E$}%
\def\lawxxviii{34${}_E$}%
\def\lawxxix{35}%
\def\lawxxx{36}%
\def\lawxxxi{37}%
\def\lawxxxii{38}%
\def\lawxxxiii{39}%
\def\lawxxxiv{40}%
\def\lawxxxv{41}%
\def\lawiiic{6B}%
\def\lawxxxvi{42}%
\def\lawxxxvii{43}%
%%%
\ifnum\Textsize=1
%%\begin{forrsi*}
\afterpage{\clearpage}
\begin{table}[H]
\singlespacing
\else
%%\end{forrsi*}
%%\begin{notrsi*}
\begin{table}[thb]
\fi
%%\end{notrsi*}
\relax
\label{table:laws}
\relax
\framebox{
{\small{
\begin{minipage}{8.3cm}
\setlength{\rightskip}{0cm plus 7cm}
\lawsection{Commuting laws}
\lawi. \(edit(\pi,X); edit(\pisub,Y) \equiv\crlw
edit(\pisub,Y); edit(\pi,X)\)\\
\lawip. \(edit(\pisub,Y); edit(\pi,X) \equiv\crlw
edit(\pi,X); edit(\pisub,Y)\)\\
%2. \(edit(\pi,X); create(\pisub,Y) \equiv
%create(\pisub,Y); edit(\pi,X)\)\\
%%\lawiibp. \(edit(\pi,\cdir{X}); create(\pisub,Y)\eqshr\)\\\indent\(%
%%create(\pisub,Y); edit(\pi,\cdir{X})\)\\
\lawiib. \(create(\pisub,Y); edit(\pi,\cdir{X})\eqexp\)\\\indent\(%
edit(\pi,\cdir{X}); create(\pisub,Y)\)\\
\lawiiia. \(edit(\pi,\cdir{X}); remove(\pisub) \equiv\)\\\indent\(%
remove(\pisub); edit(\pi,\cdir{X})\)\\
\lawiiiap. \(remove(\pisub); edit(\pi,\cdir{X})\equiv\)\\\indent\(%
edit(\pi,\cdir{X}); remove(\pisub)\)\\
\lawiv. \(edit(\pi,X); edit(\varphi,Y) \equiv
edit(\varphi,Y); edit(\pi,X)\)\\
\lawv. \(edit(\pi,X); create(\varphi,Y) \equiv\crlw
create(\varphi,Y); edit(\pi,X)\)\\
\lawvi. \(edit(\pi,X); remove(\varphi) \equiv\crlw
remove(\varphi); edit(\pi,X)\)\\
\lawvp. \(create(\varphi,Y); edit(\pi,X) \equiv\crlw
edit(\pi,X); create(\varphi,Y)\)\\
\lawvii. \(create(\pi,X); create(\varphi,Y) \equiv\)\\\indent\(%
create(\varphi,Y); create(\pi,X)\)\\
\lawviii. \(create(\pi,X); remove(\varphi) \equiv\crlw
remove(\varphi); create(\pi,X)\)\\
\lawvip. \(remove(\varphi); edit(\pi,X) \equiv\crlw
edit(\pi,X); remove(\varphi)\)\\
\lawviiip. \(remove(\varphi); create(\pi,X) \equiv\crlw
create(\pi,X); remove(\varphi)\)\\
\lawix. \(remove(\pi); remove(\varphi) \equiv\crlw
remove(\varphi); remove(\pi)\)
\lawsection{Breaking laws}
%1*. \(edit(\pi,\cfile{X}); edit(\pisub,Y) \equiv 
%edit(\pisub,Y); edit(\pi,\cfile{X}) \equiv break\)\\
\lawiia. \(edit(\pi,\cfile{X}); create(\pisub,Y) \equiv
break\)\\
\lawiiap. \(create(\pisub,Y); edit(\pi,\cfile{X}) \equiv
break\)\\
\lawiiib. \(edit(\pi,\cfile{X}); remove(\pisub) \equiv break\)\\
\lawx. \(edit(\pi,X); create(\pi,Y) \equiv break\)\\
\lawxi. \(edit(\pisub,X); create(\pi,Y) \equiv break\)\\
\lawxii. \(edit(\pisub,X); remove(\pi) \equiv break\)\\
\lawxiii. \(create(\pi,X); edit(\pisub,Y) \equiv break\)\\
\lawxiv. \(create(\pi,X); create(\pi,Y) \equiv break\)\\
\end{minipage}\begin{minipage}{7.2cm}\setlength{\rightskip}{0cm plus 7cm}
\lawxv. \(create(\pisub,X); create(\pi,Y) \equiv break\)\\
\lawxvi. \(create(\pi,X); remove(\pisub) \equiv break\)\\
\lawxvii. \(create(\pisub,X); remove(\pi) \equiv break\)\\
\lawxviii. \(remove(\pi); edit(\pi,X) \equiv break\)\\
\lawxix. \(remove(\pi); edit(\pisub,X) \equiv break\)\\
\lawxx. \(remove(\pi); create(\pisub,X) \equiv break\)\\
\lawxxi. \(remove(\pisub); create(\pi,X) \equiv break\)\\
\lawxxii. \(remove(\pi); remove(\pi) \equiv break\)\\
\lawxxiii. \(remove(\pi); remove(\pisub) \equiv break\)
\lawsection{Simplifying laws}
\lawxxiv. \(edit(\pi,X); edit(\pi,Y) \eqexp edit(\pi,Y)\)\\
\lawxxv. \(edit(\pi,X); remove(\pi) \equiv remove(\pi)\)\\ 
\lawxxvi. \(create(\pi,X); edit(\pi,Y) \equiv create(\pi,Y)\)\\
\lawxxvii. \(create(\pi,X); remove(\pi) \eqexp \emptyseq\)\\
\lawxxviii. \(remove(\pi); create(\pi,X) \eqexp edit(\pi,X)\)
\lawsection{Laws for \(break\)}
\lawxxix. \(break; edit(\pi,X) \equiv break\)\\
\lawxxx. \(break; create(\pi,X) \equiv break\)\\
\lawxxxi. \(break; remove(\pi) \equiv break\)\\
\lawxxxii. \(edit(\pi,X); break \equiv break\)\\
\lawxxxiii. \(create(\pi,X); break \equiv break\)\\
\lawxxxiv. \(remove(\pi); break \equiv break\)\\
\lawxxxv. \(break; break \equiv break\)
\lawsection{Remaining pairs\\(no substitution)}
\lawiibp. \(edit(\pi,\cdir{X}); create(\pisub,Y)\eqshr\)\\\indent\(%
create(\pisub,Y); edit(\pi,\cdir{X})\)\\
\lawiiic. \(remove(\pisub); edit(\pi,\cfile{X})\)\\
\lawxxxvi. \(create(\pi,X); create(\pisub,Y)\)\\
\lawxxxvii. \(remove(\pisub); remove(\pi)\)
\end{minipage}
}}
}
%\begin{forrsi}
%\doublespacing
%\end{forrsi}
\caption{Algebraic laws}
\end{table}
%}

\subsection{Inference rules}

An inference rule makes it possible to derive new statements from 
statements already true or from the axioms. 
Our inference rules are:\\
\emph{For any sequences \(S_1, S_2, S, S'\):}
\begin{itemize}
\item if \(S_1\equiv S_2\) then \(S;S_1;S'\equiv S;S_2;S'\)
\item if \(S_1\eqexp S_2\) then \(S;S_1;S'\eqexp S;S_2;S'\)
\item if \(S_1\equiv S_2\) then \(S_1\eqexp S_2\).
\end{itemize}
As we can see, the first inference rules are mere substitutions of a part
of the sequence to another sequence. 
%%\remark{``...'' is only for app. \ref{app:theosound}}
If ``\(S_1\equiv S_2\)'' or 
``\(S_1\eqexp S_2\)'' is a law itself, we say that we applied that law to
the sequence \(S;S_1;S'\).

\subsection{Soundness theorem}
\label{theorem:soundness}
In order to be able to use our algebra,
we must show that algebraic relation between sequences also means
that the sequences act the same on filesystems.
%
It can be proven that for every two sequences of commands 
\begin{gather*}
S\equiv S^* \implies \forall F: SF=S^*F,\\
(S\eqexp S^*)\wedge(SF\ne\ud)\implies \forall F: SF=S^*F.%\\
%S\eqifnbr S^*\wedge SF\ne\ud \wedge S^*F\ne\ud 
%\implies \forall F: SF=S^*F.
\end{gather*}
%%%\begin{forrsi}
The proof for the two cases are very similar. We use induction on the
number of times the inference rules were applied to the sequences. 
We obtain these results by
showing the soundness of each individual law (which can be done by
investigating numerous cases) and the inference rules.

The detailed proof can be found in Appendix \ref{app:theosound}.
%%%\end{forrsi}
%%%\begin{notrsi}
%%%\input{sound}
%%%\end{notrsi}

\subsection{Theorem of completeness}
\label{theorem:completeness}
In this section, we show that our proof system is complete for its
interpretation. This is also mandatory to be able to use our algebra.

Let us introduce some notation. We write 
\(S_1\eqifnbr S_2\), or \emph{\(S_1\) and \(S_2\) have a common upper 
bound} iff
\(\exists S^*: S_1\eqexp S^* \wedge S_2\eqexp S^*\), that is, iff
both \(S_1\) and \(S_2\) can be extended to the same sequence.
It is a symmetric relation, but not transitive.

\(S_1\equiv S_2\implies S_1\eqexp S_2\implies S_1\eqifnbr S_2\) also
holds.

%To show that we have enough laws to describe the algebra of
%filesystems,
Now we prove that if 
two sequences of commands act the same on any filesystem neither of
them breaks, \emph{and} there is a filesystem neither of them
breaks then they have a common upper bound.
Formally, 
\[\begin{array}{r@{}l}
\forall S,S':&\\ 
&((\forall G: (SG\ne\ud\wedge S'G\ne\ud)\implies SG=S'G)\\
&\wedge\\
&(\exists F: SF\ne\ud\wedge S'F\ne\ud)\\
&\implies S \eqifnbr S'),
\end{array}\]
where \(G\) and \(F\) refer to filesystems.

%%%\begin{notrsi}
%%%\input{compl}
%%%\end{notrsi}
%%%\begin{forrsi}

In the proof we define \emph{minimal sequences} in the following way:
Consider the set of sequences \(\wp_S = \{ S^* | S \eqexp S^*\}\).
Because of our preconditions, the sequence \(break\) is not in
\(\wp_S\) (if it was, that is, \(S\eqexp break\), \(SF=\ud\) would hold
since by definition \(SF=(break)F\) if \(SF\ne\ud\)).

Let \(S_0\) be (one of) the shortest sequence(s) in \(\wp_S\) and
similarly
\(S^\prime_0\) (one of) the shortest sequence(s) in \(\wp_{S^\prime}\). 
These sequences are called minimal sequences. It can be shown that for
every \(G\) which satisfies the condition \(SG\ne\ud\wedge S'G\ne\ud\), 
\(S_0G=S'_0G\ne\ud\) applies.
As a special case, we know that \(S_0F=S'_0F\ne\ud\).

The proof has three main steps.
\begin{itemize}
\item[i.]
We have some constraints on \(S_0\) and \(S'_0\). Since they do not break
every filesystem, no breaking laws can be applied to them. And since
they have minimal length, we cannot apply a simplifying law either. From
these properties we can prove that there is at most one command on each
path in a minimal sequence. (If there were more, such a law would
be appliable.)
\item[ii.]
We know that a command on path \(\pi\) only affects the filesystem at
\(\pi\) if it does not break the filesystem. Therefore \(S_0\) and
\(S'_0\) must contain commands on the same paths since
they do not break \(F\) and \(S_0F=S'_0F\), so they modify \(F\) at 
the same points. 
And we can also prove that the sequences must contain the same
commands on each path from the fact that they act the same on every \(G\).
Therefore they consist of the very same commands.
\item[iii.]
We prove that \(S_0\) and \(S'_0\) can be reordered by commuting
laws so that they would be the same sequences. That is, a sequence
\(S^*\) exists for which \(S_0\eqexp S^*\eqshr S'_0\). It means that
\(S\eqexp S_0\eqexp S^*\eqshr S'_0\eqshr S'\), i.e. \(S\eqifnbr S'\).
\end{itemize}

In appendix \ref{app:compl} we provide the detailed version of the
proof.

\medskip
Now, since we know that our algebra is sound and complete for its
intended interpretation, we can use it to define the specification of the
file synchronizer.
%%%\end{forrsi}

### 2015-09-15 udetect-move.tex
Adding files for the original article

%% Why don't we use move; Update-detector algorithm
\section{A solution for update-detection for a move--free algebra}
\label{app:update-move}

\begin{comment}
\subsection{A simple way}
\remark{Do we need this in the paper?}
A ``simple way'' means that when determining the commands which lead from
the
original to the present state of the filesystems we do not use commands
like moving a whole subtree or removing a subtree. Commands only allowed
at leaves of the tree of the filesystem, e.g. files or directories
containing no files.

Consider the original state, called \(O\) and the present state called
\(A\). In order to be able to determine the \emph{move} operations, we'd
like to compare the containings of two files in the original and in the
present state. It doesn't mean that we have to store the original
filesystem. This can be achieved by a method called
\emph{data--fingerprint} with which we can compare contents of files
without comparing the whole amount of data stored in them.

A function called \(origin(\pi)\) gives
us a path for a file in the filesystem \(O\) which has the same contents 
as the file \(A\cdot\pi\), or empty--file (\(\perp\)) if such a file does
not exist. Note that more files may be found in \(O\) with the same
contents.

Another function, \(\#(\pi)\) gives the number of paths \(\varphi\) for
which \(origin(\varphi)=\pi\) holds.

Then to gain a possible sequence of commands, compare \(O\cdot\pi\) and
\(A\cdot\pi\). (For this purpose, we can use timestamps, inode numbers,
or any other data on files provided by the operation system.) 
If they're the same, we
don't need to do anything. If not, we have three cases. First, if the
file \(A\cdot\pi\) has been deleted, we can delete this file iff
\(\#(\pi)=0\). If the file exists in \(A\) it may have an origin or not.
If it has, and \(\#(\pi)=0\), than we can \emph{move} \(origin(\pi)\) to
\(\pi\) iff \(\#(origin(\pi))=1\), or \emph{copy} it if
\(\#(origin(\pi))>1\). In both cases, we should decrease
\(\#(origin(\pi))\) by one.

If we couldn't do anything because \(\#(\pi)\) was greater than \(0\), we
can do one of the followings: wait till it decreases due to another
commands, or, if there's a \emph{loop} of file displacings (for example
\(origin(a)=b\) and \(origin(b)=a\)) than we should rename the origin of
one of the files in order to be able to continue (solving the
example: \emph{move} \(b\to b^\prime\), \(a\to b\) and \(b^\prime\to
a\)).

That way we gained a possible sequence of commands which if we apply
to 
filesystem \(O\) we'll get filesystem \(A\).
\end{comment}

First, we provide an example which explains why we chose working on
move--free algebra.

\subsection{Moving and removing subtrees}

When trying to determine the minimal sequence of commands which was
applied to the original filesystem \(O\) so that we get its present state
\(A\) we should try to move
or remove subtrees instead of (re)moving all files in it
in order to gain the most simple sequence possible.
We can achieve
this by counting the files under a directory and how many of
them should be (re)moved. If there are many files to be moved, we should
move the subtree first and then the other files back to their place
(majority voting).

\subsection{Problems with move}

But, unfortunately, difficulties emerge when using such commands.

First of all, consider the following situation: we have files \(X\cdot1,
X\cdot2, X\cdot3, X\cdot4, X\cdot5, X\cdot6\) in filesystem \(O\). In
replica A, we have moved \(X\cdot1, \ldots X\cdot4\) to \(Y\cdot1, \ldots
Y\cdot4\). In replica B, we have moved only \(X\cdot1, X\cdot2\) under
the new directory \(Y\).

In replica \(A\), without using commands on subtrees, we'd
have \emph{move} \(X\cdot1\to Y\cdot1, X\cdot2\to Y\cdot2,
X\cdot3\to Y\cdot3, X\cdot4\to Y\cdot4\). But using subtree--moving,
we'll
notice that using \emph{move} \(X\to Y, Y\cdot5\to X\cdot5,
Y\cdot6\to X\cdot6\) would be shorter, so this is our sequence of
commands. In replica \(B\), \emph{move}
\(X\cdot1\to Y\cdot1, X\cdot2\to Y\cdot2\) is the shortest way.

Now we want to choose commands from each sequence so that they would not
cause a conflicting update if propagated on other replicas.
It is easily provable that such subsequences of commands
do not exist. 
\remark{Proof?}
We reached the conclusion that not always the
shortest sequence should be used to generate the interleaving; or, in
other words, we should be able to change the sequences according to the
algebraic laws before choosing. It'd make the problem much more
complicated since we have a lot of possibilities here as well as at
choosing the subsequences.  Using \(move\), we also have a very 
complicated relationship among the commands considering which two can
commute and which two not. (Note that \(move\) is the only function
which modifies \emph{two} paths at the same time.)

%We can solve this problem by \emph{delaying
%the subtree--detection} to the end of the update--detection and
%reconciliation.

Therefore, we decided to focus on a \emph{move--free} algebra and delay
detecting possibilities of simplification (subtree--detection) until
after the update--detection and reconciliation.

\subsection{A simple algorithm for update--detection}
\label{app:upd}

With no \(move\)s and subtree--commands, a simple algorithm can be
used for update--detection. It takes information from the filesystems
and gives a minimal sequence of commands which will make one similar to
the other.

Let \(P_O\) be all the paths in the original
filesystem, \(P_A\) all the paths in the current state of the replica. 
(We assume \(O,A\ne\ud\).)
For
every \(\pi\in P_O\cup P_A\) add the following command to sequence \(S\):
\begin{itemize}
\item \(create(\pi,X)\) iff \(O(\pi)=\ud\) and \(A(\pi)=X\ne\ud\),
\item \(edit(\pi,X)\) iff \(O(\pi)\ne\ud\) and \(A(\pi)=X\ne\ud\) and
\(X\ne O(\pi)\),
\item \(remove(\pi)\) iff \(O(\pi)\ne\ud\) and \(A(\pi)=\ud\).
\end{itemize}
Then arrange the commands so that
\begin{itemize}
\item all \(edit(\pi,\cdir{X})\) commands precede all other commands, 
\item all \(edit(\pi,\cfile{X})\) commands follow all other commands,
\item \(create(\pi,X)\) commands precede \(create(\pisub,Y)\) commands,
\item \(remove(\pisub,X)\) commands precede \(remove(\pi,Y)\) commands.
\end{itemize}
This can be done by the method discussed below.

First, we move all \(edit(\pi,\cdir{X})\) commands to the front and then
all \(edit(\pi,\cfile{X})\) commands to the end of the sequence. Now for
the middle part, we know the following:

Since there is only one command on each path, we have a partial
ordering on the set of the commands (see section
\ref{theorem:conc}) showing us which command must precede another one.
Two commands can be interchanged if they refer to incomparable
paths; otherwise, they are one of the following:
\begin{itemize}
\item \(create(\pi) \ldots create(\pisub)\)
\item \(remove(\pisub) \ldots remove(\pi)\).
\end{itemize}
That is, every \(create\) must precede all other \(create\)s on its
descendants and all \(remove\)s must precede \(remove\)s on its parents.

This ordering can be represented by a graph. This graph is a tree (or
forest). It's worth remarking that every tree of the forest is formed
from the same commands, \(remove\)s or \(create\)s, since two different
types of commands cannot show up at comparable paths.

Starting at the leaves of the trees, we move the leaves as close as
possible to their parent. (They will form a row at the left side of the
branch--command at the \(remove\)--trees and at the other side at
\(create\)--trees.) Then we order them alphabetically and form a
\emph{group--command} from the leaves and the branch. This
group--command
will act like a single command since all of its members commute the
same commands. Then we continue this method until every tree is
grouped into one meta-group--command. We order these groups again.
That way we gain an order of the commands. It's worth remarking that
we gain the same order for the same set of commands every time.

We know that \(SO=A\) since because of the ordering it does not break the
filesystem. Also, \(S\) is a minimal sequence. \emph{Proof.} 
By contradiction.
If \(S'\) is shorter than \(S\), then we have a path \(\varphi\) on which
we have a command in \(S\) but not in \(S'\) since all paths are different
in \(S\). Now we know that \(SF(\varphi)\ne F(\varphi)\) but 
\(S'F(\varphi)=F(\varphi)\). (Note that we have no superfluous commands
in \(S\) since we gained it from the update detector algorithm.)

### 2015-09-15 definition.tex
Improved text

@@
 \subsection{The filesystem}
-We introduce some known notations on filesystems and paths.
+We introduce some notation on filesystems and paths.
 
@@
 or it can be a function mapping whole paths to their
-contents. The filesystem is broken if a command caused an error, for
-example deleting a directory with files under it.
+contents. The filesystem is broken if a command has caused an error, for
+example attempted to delete a directory with files under it.
 
-A \emph{path} is either empty (/), or a finite sequence of names
+A \emph{path} is either empty (/), or is a finite sequence of names
 separated by \(\cdot\). The concatenation of paths \(\pi\) and
@@
 \(\pi\preceq\gamma\) iff \(\pi\) is a prefix of \(\gamma\), i.e., if
-\(\gamma=\pi\cdot\alpha\) for some path \(\alpha\) which might be
+\(\gamma=\pi\cdot\alpha\) for some path \(\alpha\) which may be
 empty. We also write
@@
 \(\pi\preceq\gamma\) and \(\pi\ne\gamma\). If we refer to the contents of
-path \(\pi\) in filesystem \(F\), we write simply \(F(\pi)\).
+path \(\pi\) in filesystem \(F\), we simply write \(F(\pi)\).
 
@@
 \begin{notrsi} 
-Both files and directories can carry additional information
-(modtimes, permissions, the bytes in a file, etc.), which we leave
-unspecified, simply writing the contents as shown above.
+In real-life filesystems, files and directories can carry additional information
+like modification times, permissions, etc.
+Here we consider these included in the contents. 
 \end{notrsi}
@@
 
-We have some restrictions on filesystems: all filesystems must satisfy
+All filesystems must satisfy
 the \emph{tree property}, that
-is, if \(\pi\prec\gamma\) and \(F(\gamma)\neq\ud\) then
-\(F(\pi)=\cdir{X}\). It means that every path which has a descendant must
+is, if \(F(\gamma)\neq\ud\) then for every \(\pi\) either
+\(childless_F(\pi)\) or \(F(\pi)=\cdir{X}\).
+This means that every path which has a descendant must
 be a directory.
@@
 At first, we
-thought about using four commands: \(create\), \(remove\), \(edit\) and
+considered using four commands: \(create\), \(remove\), \(edit\) and
 \(move\), as the most common commands on a filesystem. Later, \(move\)
-turned out to be hard to handle in the algebra. We decided to introduce
+turned out to be too complicated to handle in the algebra. We decided to introduce
 this command only in the user interface, after running the synchronizer.
@@
 \begin{notrsi}
-All the commands have the following property: if applied to a filesystem,
-then it either breaks the system (\(command(\pi,X)F=\ud\)) or 
-\(command(\pi,X)F=F\{\pi\mapsto X\}\); that is, if a command does not
-break the filesystem, it only affects the filesystem at the path on which
-it was applied. 
+All commands have the following property: if applied to a filesystem,
+they either break the system (\(command(\pi,X)F=\ud\)) or 
+\(command(\pi,X)F=F\{\pi\mapsto X\}\); that is, they only affect the filesystem at the path on which
+they were applied. 
 \end{notrsi}
@@
 %We have four commands: \emph{create, edit, remove} and \emph{break.} 
-Applied to the broken filesystem, they all have the same effect:  leaving
+Applied to the broken filesystem, they all leave
 the filesystem in the broken state. Otherwise, 
-the definition of their effect is the following:
+the definition of their effect is as follows:
 
@@
 The command \(edit\) can change the type of a path (file or
-directory), according to its second argument.
-Since the tree--property must be preserved, the definition is:
+directory) according to its second argument.
+Since the tree property must be preserved, the definition is:
 \begin{align*}

### 2015-09-15 theorems.tex
Improved text

@@
 \item \(S_1\eqexp S_2\), or \emph{\(S_2\) extends \(S_1\)}; its intended
-interpretation is the following: if \(S_1\eqexp S_2\) and 
-\(S_1F\ne\ud\) then \(S_1F=S_2F\).
+interpretation is that if \(S_1\) does not break a filesystem, then they act
+the same on it, i.e. \(\forall F: S_1F\ne\ud \implies S_1F=S_2F\).
 %%%
@@
 How many pairs do we have? 
-For the first group of laws which contain a pair of commands from
-\(edit\), \(create\) and \(remove\), we can choose a pair 9 ways.
-We have four types of
-path-pairs: \(\pi;\pi\), \(\pisub;\pi\), \(\pi;\pisub\)
-and \(\pi;\varphi\). That makes \(4\times9\) cases. With \(break\), we have
-\(3\times 2\) cases
-with an other non--break command (there are 3 types and they can follow
-or precede \(break\)) and one case when we have a pair made of two
+From
+\(edit\), \(create\) and \(remove\), we can choose a pair in 9 ways.
+Moreover, there are four types of
+path-pairs: equivalence \(\pi;\pi\), subordination \(\pisub;\pi\),
+superordination \(\pi;\pisub\)
+and incomparable paths \(\pi;\varphi\). These make \(4\times9\) cases. With \(break\), we have
+\(3\times 2\) additional cases
+with another non--break command (there are 3 types and they can follow
+or precede \(break\)), and one case when we have a pair made of two
 \(break\)s. Thus, we have \(4\times 9+3\times2+1=43\) pairs. 
@@
 %%%
-(See table 1 for the laws.)
+% (See table 1 for the laws.)
 
@@
 An inference rule makes it possible to derive new statements from 
-statements already true or from the axioms. 
-Our inference rules are:\\
+the axioms or from statements already known to be true. 
+The inference rules are:\\
 \emph{For any sequences \(S_1, S_2, S, S'\):}
@@
 \end{itemize}
-As we can see, the first inference rules are mere substitutions of a part
-of the sequence to another sequence. 
-%%\remark{``...'' is only for app. \ref{app:theosound}}
+Te first two inference rules merely substitute part of a sequence for
+another sequence.
 If ``\(S_1\equiv S_2\)'' or 
-``\(S_1\eqexp S_2\)'' is a law itself, we say that we applied that law to
+``\(S_1\eqexp S_2\)'' is a law, we say that we applied that law to
 the sequence \(S;S_1;S'\).
@@
 In order to be able to use our algebra,
-we must show that algebraic relation between sequences also means
+we must show that an algebraic relation between sequences also means
 that the sequences act the same on filesystems.
@@
 It can be proven that for every two sequences of commands
+\(S\) and \(S^*\) 
 \begin{gather*}
-S\equiv S^* \implies \forall F: SF=S^*F,\\
-(S\eqexp S^*)\wedge(SF\ne\ud)\implies \forall F: SF=S^*F.%\\
-%S\eqifnbr S^*\wedge SF\ne\ud \wedge S^*F\ne\ud 
-%\implies \forall F: SF=S^*F.
+\forall F: S\equiv S^* \implies SF=S^*F,\\
+\forall F: (S\eqexp S^*)\wedge(SF\ne\ud)\implies SF=S^*F.
 \end{gather*}
-%%%\begin{forrsi}
-The proof for the two cases are very similar. We use induction on the
-number of times the inference rules were applied to the sequences. 
-We obtain these results by
-showing the soundness of each individual law (which can be done by
-investigating numerous cases) and the inference rules.
-
-The detailed proof can be found in Appendix \ref{app:theosound}.
-%%%\end{forrsi}
-%%%\begin{notrsi}
-%%%\input{sound}
-%%%\end{notrsi}
+The proofs for the two cases are very similar. We use induction on the
+number of times the inference rules are applied to the sequences.
+The soundness of each individual law
+(by investigating individual cases)
+and that of the inference rules are shown separately.
+For the detailed proof see Appendix \ref{app:theosound}.
 
@@
 It is a symmetric relation, but not transitive.
-
 \(S_1\equiv S_2\implies S_1\eqexp S_2\implies S_1\eqifnbr S_2\) also
@@
 
-%To show that we have enough laws to describe the algebra of
-%filesystems,
 Now we prove that if 
@@
 them breaks, \emph{and} there is a filesystem neither of them
-breaks then they have a common upper bound.
+breaks, then they are also related algebraically; namely, they have a common upper bound.
 Formally, 
@@
 \forall S,S':&\\ 
-&((\forall G: (SG\ne\ud\wedge S'G\ne\ud)\implies SG=S'G)\\
+&(\forall G: (SG\ne\ud\wedge S'G\ne\ud)\implies SG=S'G)\\
 &\wedge\\
 &(\exists F: SF\ne\ud\wedge S'F\ne\ud)\\
-&\implies S \eqifnbr S'),
+&\implies S \eqifnbr S',
 \end{array}\]
 where \(G\) and \(F\) refer to filesystems.
-
-%%%\begin{notrsi}
-%%%\input{compl}
-%%%\end{notrsi}
-%%%\begin{forrsi}
 
@@
 Because of our preconditions, the sequence \(break\) is not in
-\(\wp_S\) (if it was, that is, \(S\eqexp break\), \(SF=\ud\) would hold
-since by definition \(SF=(break)F\) if \(SF\ne\ud\)).
+\(\wp_S\) (if it was, that is, \(S\eqexp break\), \(\forall F:SF=\ud\) would hold
+by definition).
 
@@
 \(S^\prime_0\) (one of) the shortest sequence(s) in \(\wp_{S^\prime}\). 
-These sequences are called minimal sequences. It can be shown that for
+We will call these minimal sequences. It can be shown that for
 every \(G\) which satisfies the condition \(SG\ne\ud\wedge S'G\ne\ud\), 
 \(S_0G=S'_0G\ne\ud\) applies.
-As a special case, we know that \(S_0F=S'_0F\ne\ud\).
+As a special case, we know that \(S_0F=S'_0F\ne\ud\) where \(F\) is the
+fileystem from the formalization of the theorem above.
 
@@
 these properties we can prove that there is at most one command on each
-path in a minimal sequence. (If there were more, such a law would
-be appliable.)
+path in a minimal sequence. (If there were more, a breaking or simplifying law
+could be applied.)
 \item[ii.]
@@
 \(S'_0\) must contain commands on the same paths since
-they do not break \(F\) and \(S_0F=S'_0F\), so they modify \(F\) at 
+they do not break \(F\) and \(S_0F=S'_0F\), that is, they modify \(F\) at 
 the same points. 
@@
 \item[iii.]
-We prove that \(S_0\) and \(S'_0\) can be reordered by commuting
+We prove that \(S_0\) and \(S'_0\) can be reordered using commuting
 laws so that they would be the same sequences. That is, a sequence
@@
 file synchronizer.
-%%%\end{forrsi}

### 2015-09-15 confl.tex
Text improvements, new example for conflict criterion

@@
 
-We define conflicting updates using minimal sequences made by the
-update detector algorithm. Actually, we define conflicting \emph{pairs
+We define conflicting updates using minimal sequences provided by an
+update detector algorithm. More specifically, we define conflicting \emph{pairs
 of commands} since only two modifications can interfere with each other.
-Later we will mark every command as a conflicting command if
-it was a member of a conflicting pair.
+Later, every command will be marked as conflicting if it is a member of a
+conflicting pair.
 
-Consider two commands, \(C_A(\pi)\in S_A\) and \(C_B(\gamma)\in S_B\) 
+Let us consider two commands, \(C_A(\pi)\in S_A\) and \(C_B(\gamma)\in S_B\) 
 where \(S_A\) is the minimal sequence which
@@
 \begin{itemize}
-\item \(\neg(C_A(\pi); C_B(\gamma) \eqifnbr C_B(\gamma); C_A(\pi))\)
+\item \(C_A(\pi); C_B(\gamma) \neqifnbr C_B(\gamma); C_A(\pi)\)
  (they do not commute), \emph{or}
 \item \(C_A(\pi); C_B(\gamma) \equiv break\), \emph{or}
-\(C_B(\gamma); C_A(\pi) \equiv break\)\\(they break every
-filesystem).
+\(C_B(\gamma); C_A(\pi) \equiv break\)\\(they are equivalent to \(break\);
+from which we know they break every filesystem).
 \end{itemize}\end{minipage}
@@
 \begin{notrsi}
-Clearly this relation is symmetrical i.e.,
+Clearly this relation is symmetrical, i.e.
 \(C_1\confl C_2\implies C_2\confl C_1\).
@@
 
-In appendix \ref{cbp:bp} we try to find a relation between this
+In appendix \ref{cbp:bp} we determine the relation between this
 definition and another one found in \BP.

### 2015-09-15 theorems.tex
Text improvements, new example for conflict criterion

@@
 \begin{gather*}
-\forall F: S\equiv S^* \implies SF=S^*F,\\
-\forall F: (S\eqexp S^*)\wedge(SF\ne\ud)\implies SF=S^*F.
+S\equiv S^* \implies \forall F: SF=S^*F,\\
+S\eqexp S^* \implies \forall F: (SF\ne\ud \implies SF=S^*F).
 \end{gather*}
@@
 For the detailed proof see Appendix \ref{app:theosound}.
+
+\medskip\noindent{\small{As special consequences of the soundness theorem, we know
+that both \(S\equiv break\)
+and \(S\eqexp break\) means that \(S\) breaks all filesystems.
+--- EC, 2015
+}}
 
@@
 Because of our preconditions, the sequence \(break\) is not in
-\(\wp_S\) (if it was, that is, \(S\eqexp break\), \(\forall F:SF=\ud\) would hold
-by definition).
+\(\wp_S\) (if it was, that is, \(S\eqexp break\), \(\forall F:SF=\ud\) would
+hold).
 

### 2015-09-15 compl.tex
Text improvements

@@
 %% Proof for completeness theorem +foreword
-%%%\begin{forrsi}
 \section{Proof of the completeness theorem}
@@
 \forall S,S':&\\
-&((\forall G: (SG\ne\ud\wedge S'G\ne\ud)\implies SG=S'G)\\
+&(\forall G: (SG\ne\ud\wedge S'G\ne\ud)\implies SG=S'G)\\
 &\wedge\\
-&(\exists F: SF\ne\ud\wedge S'F\ne\ud\wedge SF=S'F)\\
-&\implies S \eqifnbr S'),
+&(\exists F: SF\ne\ud\wedge S'F\ne\ud)\\
+&\implies S \eqifnbr S',
 \end{array}\]
 where \(G\) and \(F\) refer to filesystems.
-%%%\end{forrsi}
-%%%%%%%%%%%%%%%%%
-%%%\begin{notrsi*}
-%%%\newcommand{\varsection}[1]{\subsubsection{#1}}%
-%%%\end{notrsi*}
-%%%\begin{forrsi*}
 \newcommand{\varsection}[1]{\subsection{#1}}%
-%%%\end{forrsi*}
 
-In the proof, by \(F\), we
-mean a filesystem which satisfies the second condition. By \(G\), we
+Throughout the proof, 
+% by \(F\), we
+% mean a filesystem which satisfies the second condition. 
+by \(G\), we
 refer to any filesystem which satisfies \(SG\ne\ud\wedge S'G\ne\ud\).
@@
 Because of our preconditions, the sequence \(break\) is not in
-\(\wp_S\) (if it was, that is, \(S\eqexp break\), \(SF=\ud\) would hold
-since by definition \(SF=(break)F\) if \(SF\ne\ud\)).
+\(\wp_S\) (if it was, that is, \(S\eqexp break\), \(SG=\ud\) would hold
+based on the soundness theorem).
 
@@
 %
-The following holds for these sequences:
+The following holds for these minimal sequences:
 \[(SG\ne\ud\wedge S'G\ne\ud\implies) \quad SG=S'G=S_0G=S'_0G\ne\ud.\]
@@
 
-As a special case, we also know that \(SF=S'F=S_0F=S'_0F\ne\ud\).
+% As a special case, we also know that \(SF=S'F=S_0F=S'_0F\ne\ud\).
 
@@
 \end{notrsi}
-Now let's investigate these ``minimal'' sequences.
+Now let us investigate these minimal sequences.
 
@@
 
-That way we also separated these commands from the other ones.
-Now we focus on the remaining part: on the \(create\) and 
+This way we also separated these commands from the rest.
+Now we can focus on the remaining part: on the \(create\) and 
 \(remove\) commands.
@@
 the induction hypothesis, \(S\eqexp break\) 
-(we know that \(\pisup\prec\pi\)). Otherwise the commands
-would be able to be simplified (which contradicts the condition being
-minimal sequence) or commuted (and therefore the induction hypothesis
+(we know that \(\pisup\prec\pi\)). Otherwise it would be possible to
+shorten the sequence (which contradicts our precondition) or commuted (and therefore the induction hypothesis
 still holds). (Laws \lawvii,
@@
 \emph{Proof.} By contradiction. First of all, we know that
-\(F(\pi)=\ud\) otherwise \(S_0\) would break \(F\) and that would
+\(G(\pi)=\ud\) otherwise \(S_0\) would break \(G\) and that would
 contradict our assumption. Now assume that 
@@
 We have three cases. If there is no command on path \(\pi\) in
-\(S'_0\) then \(S'_0F(\pi)=\ud\) and therefore 
-\(S_0F(\pi)\ne S'_0F(\pi)\), that is, \(S_0F\ne S'_0F\) which contradicts
-our assumption that \(S_0F=S'_0F\). If there was a command \(edit\) or
-\(remove\) on path \(\pi\), it would break \(F\) since \(F(\pi)=\ud\) and
+\(S'_0\) then \(S'_0G(\pi)=\ud\) and therefore 
+\(S_0G(\pi)\ne S'_0G(\pi)\), that is, \(S_0G\ne S'_0G\) which contradicts
+our assumption. If there was a command \(edit\) or
+\(remove\) on path \(\pi\), it would break \(G\) since \(G(\pi)=\ud\) and
 that again contradicts the precondition.
@@
 Now we can be sure that \(F(\pi)\ne\ud\) and
-\(S_0F(\pi)=\ud\). If (instead of
+\(S_0G(\pi)=\ud\). If (instead of
 \(remove\)) there was no command on \(\pi\) in \(S'_0\) then 
-\(S'_0F(\pi)\ne\ud\)  would hold. In case of \(edit\), 
-\(S'_0F(\pi)\ne\ud\) would hold (contradicting
-\(S_0F(\pi)=\ud\)). \(create\) would break \(F\) since
-\(F(\pi)\ne\ud\). Again, we have contradiction in all cases.
+\(S'_0G(\pi)\ne\ud\)  would hold. In case of \(edit\), 
+\(S'_0G(\pi)\ne\ud\) would hold (contradicting
+\(S_0G(\pi)=\ud\)). \(create\) would break \(G\) since
+\(G(\pi)\ne\ud\). Again, we have contradiction in all cases.
 \end{notrsi}
@@
 \emph{Proof.} Similarly we cannot have \(create\) or \(remove\) on path
-\(\pi\) in sequence \(S'_0\) since \(F(\pi)\ne\ud\) and 
-\(S'F(\pi)=SF(\pi)\ne\ud\). 
+\(\pi\) in sequence \(S'_0\) since \(G(\pi)\ne\ud\) and 
+\(S'G(\pi)=SG(\pi)\ne\ud\). 
 But now we might have no commands on
-\(\pi\) in \(S'_0\): that way if \(F(\pi)=X\) then \(S_0F(\pi)=X\) and
-\(S'_0F(\pi)=X\), too. 
-But clearly \(\neg(S_0\eqifnbr S'_0)\). To prove that this is also
+\(\pi\) in \(S'_0\): that way if \(G(\pi)=X\) then \(S_0G(\pi)=X\) and
+\(S'_0G(\pi)=X\), too. 
+% But clearly \(\neg(S_0\eqifnbr S'_0)\). 
+To prove that this is also
 impossible, we need the first condition about all filesystems.
@@
 Define
-\(H\) as \(F\{\pi\mapsto Y\}\) where \(Y\) has the same type
-(file/directory) as \(F(\pi)\). If \(SF\ne\ud\) then \(SH\ne\ud\) since no
+\(H\) as \(G\{\pi\mapsto Y\}\) where \(Y\) has the same type
+(file/directory) as \(G(\pi)\). If \(SG\ne\ud\) then \(SH\ne\ud\) since no
 command breaks the filesystem because of the contents (not the type) of a
-file or directory. Also, \(S'F\ne\ud\implies S'H\ne\ud\). Now, as a
-special case of \(S_0G=S'_0G\) (note that 
-\(SH\ne\ud\wedge S'H\ne\ud\) holds) we know
+file or directory. Also, \(S'G\ne\ud\implies S'H\ne\ud\). Now, 
+from the coditions of the theorem
+and \(SH\ne\ud\wedge S'H\ne\ud\) we know
 that \(S_0H=S'_0H\). But \(S_0H(\pi)=edit(\pi,X)H(\pi)=X\) and
@@
 \medskip
-Now we will show that they can be made exactly the same by the
+Now we will show that they can be made exactly the same using the
 commuting algebraic laws.
@@
 We know that \(edit\)s can be moved to the ends of the sequences and
-ordered. Let's suppose they are arranged this way.
+ordered. Let us suppose they are arranged this way.
 Since we know that the two sequences contain the same
@@
 is \(1\), the problem can be solved easily. If the length of the sequences
-are \(i>1\), we can choose a command from \(S_0\) which has no
-preceding commands (i.e., a command which must precede it).
+is \(i>1\), we can choose a command from \(S_0\) which has no
+command that must precede it.
 It is sure that it has no precedents in \(S'_0\). Now we
@@
 
-We obtain \(S_0^*\) by applying this method to \(S_0\) and
-\({S^\prime_0}^*\) from \(S^\prime_0\). Since they contain the same
+We obtain \(S_0^*\) and \(S^\prime_0^*\) by applying this method to \(S_0\) and
+\(S^\prime_0\). Since they contain the same
 commands, and the resulting order is the same,
@@
 S^\prime\), that is, \(S\eqifnbr S^\prime\). Our theorem is proved.
-\begin{forrsi}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\end{forrsi}
-
-\begin{CMNT}
-It is also can be shown that 
-\(S\equiv S'\). \emph{Proof.} We already know
-that \(S\eqifnbr S'\). It means that we have a chain of sequences, 
-\(S\eqexp S_1\eqexp S_2\ldots S'\) so that we gained each sequence by
-applying a law to the preceding one. If \(S\not\equiv S'\), we used
-somewhere an `\(E\)'--marked law, namely \(S_i\eqexp S_{i+1}\). It could 
-be Law \lawiib, \lawxxiv, \lawxxvii~or \lawxxviii. [??...]
-\end{CMNT}

### 2015-09-15 sound.tex
Text improvements

@@
 %% Proof for the soundness theorem + foreword
-%%%\begin{forrsi}
 \section{Proof for the soundness theorem}
@@
 S\equiv S^* \implies \forall F: SF=S^*F,\\
-S\eqexp S^*\wedge SF\ne\ud \implies \forall F: SF=S^*F.%\\
-%S\eqifnbr S^*\wedge SF\ne\ud \wedge S^*F\ne\ud 
-%\implies \forall F: SF=S^*F.
+S\eqexp S^* \implies \forall F:(SF\ne\ud \implies SF=S^*F).
 \end{gather*}
-%%%\end{forrsi}
 
-Both statement is true if our axioms and inference rules are sound since
-we can only gain equivalent (or extending) sequences from axioms
+Both statements are true if our axioms and inference rules are sound,
+beacuse
+we can only generate equivalent (or extending) sequences from axioms
 or by using inference rules.
@@
 as a special case \(S_1(SF)=S_2(SF)\). Thus
-\(\forall F: (S;S_1;S')F=((S;S_2;S')F\). This is the interpretation of our
+\(\forall F: (S;S_1;S')F=(S;S_2;S')F\). This is the interpretation of our
 statement.
@@
 For the second law, we now that the interpretation of 
-\(S_1\eqexp S_2\) is true and we show that in that
-case \(S;S_1;S'\eqexp S;S_2;S'\) also true for filesystems. 
+\(S_1\eqexp S_2\) is true and we show that
+\(S;S_1;S'\eqexp S;S_2;S'\) also true for filesystems. 
 We know that for every \(F\) if \(S_1F\ne\ud\) then \(S_1F=S_2F\). If
 \((S;S_1;S')F=\ud\) then the relation is clearly true (since it refers to
-only the case if the filesystem is not broken). In the other case, if
+only the case if the filesystem is not broken). Otherwise, if
 \((S;S_1;S')F=S'(S_1(SF))\ne\ud\), we know that \(SF\ne\ud\) since
-%%\remark{`defined' is not quite defined}
 a filesystem cannot be made non--broken again by applying commands to it.
@@
 
-The soundness proof of the third law is quite simple since if two
+The soundness proof of the third law is quite simple as if two
 sequences act the same on \emph{all} filesystems then they act the same on
@@
 It remains to show the soundness of each individual law,
-but all the laws were derived from the definitions of the
-commands. For precise proofs,
-Appendix~\ref{app:soundness} shows an example.
+which can be verified based on the definitions of the commands from which
+the laws have been derived.
+Appendix~\ref{app:soundness} shows an example of the precise proofs.
 

### 2015-09-16 udetect-move.tex
Text improvements

@@
 %% Why don't we use move; Update-detector algorithm
-\section{A solution for update-detection for a move--free algebra}
+\section{A solution for update-detection in a move--free algebra}
 \label{app:update-move}
 
+% TODO v
 \begin{comment}
 \subsection{A simple way}
-\remark{Do we need this in the paper?}
 A ``simple way'' means that when determining the commands which lead from
@@
 \end{comment}
+% TODO ^
 
 First, we provide an example which explains why we chose working on
-move--free algebra.
+a move--free algebra.
 
@@
 
-When trying to determine the minimal sequence of commands which was
-applied to the original filesystem \(O\) so that we get its present state
-\(A\) we should try to move
-or remove subtrees instead of (re)moving all files in it
+When trying to determine the minimal sequence of commands which has been
+applied to the original filesystem \(O\) to arrive at its present state
+\(A\), we should try to move
+or remove subtrees instead of (re)moving all files in them
 in order to gain the most simple sequence possible.
@@
 this by counting the files under a directory and how many of
-them should be (re)moved. If there are many files to be moved, we should
-move the subtree first and then the other files back to their place
-(majority voting).
+them need to be (re)moved. Then by majority voting, if there are enough files to be moved, 
+we should move the subtree first and then the remaining files back to their
+places.
 
@@
 
-In replica \(A\), without using commands on subtrees, we'd
+In replica \(A\), without using commands on subtrees, we would
 have \emph{move} \(X\cdot1\to Y\cdot1, X\cdot2\to Y\cdot2,
-X\cdot3\to Y\cdot3, X\cdot4\to Y\cdot4\). But using subtree--moving,
-we'll
-notice that using \emph{move} \(X\to Y, Y\cdot5\to X\cdot5,
-Y\cdot6\to X\cdot6\) would be shorter, so this is our sequence of
-commands. In replica \(B\), \emph{move}
-\(X\cdot1\to Y\cdot1, X\cdot2\to Y\cdot2\) is the shortest way.
+X\cdot3\to Y\cdot3, X\cdot4\to Y\cdot4\). But with subtree--moving,
+we will
+notice that the sequence \emph{move} \(X\to Y, Y\cdot5\to X\cdot5,
+Y\cdot6\to X\cdot6\) is shorter. In replica \(B\), \emph{move}
+\(X\cdot1\to Y\cdot1, X\cdot2\to Y\cdot2\) is the shortest sequence.
 
-Now we want to choose commands from each sequence so that they would not
-cause a conflicting update if propagated on other replicas.
-It is easily provable that such subsequences of commands
+The next step is to choose commands from each sequence so that they would not
+cause conflicting updates when propagated to other replicas.
+It is easily to prove that such subsequences of commands
 do not exist.
-\remark{Proof?}
-We reached the conclusion that not always the
-shortest sequence should be used to generate the interleaving; or, in
-other words, we should be able to change the sequences according to the
-algebraic laws before choosing. It'd make the problem much more
-complicated since we have a lot of possibilities here as well as at
-choosing the subsequences.  Using \(move\), we also have a very 
-complicated relationship among the commands considering which two can
-commute and which two not. (Note that \(move\) is the only function
-which modifies \emph{two} paths at the same time.)
 
-%We can solve this problem by \emph{delaying
-%the subtree--detection} to the end of the update--detection and
-%reconciliation.
+We reached the conclusion that it is not always the
+shortest sequence that should be used to generate the interleaving; or, in
+other words, that we should be able to modify the sequences according to the
+algebraic laws before choosing the one used.
+% It would make the problem much more
+% complicated since we have a lot of possibilities here as well as at
+% choosing the subsequences.  
+Using \(move\), we also have a 
+complicated relationship among the commands when considering which pairs
+commute and which do not as \(move\) is the only command
+that modifies two paths at the same time.
 
 Therefore, we decided to focus on a \emph{move--free} algebra and delay
-detecting possibilities of simplification (subtree--detection) until
+detecting possibilities of simplification (e.g. subtree--detection) until
 after the update--detection and reconciliation.
@@
 used for update--detection. It takes information from the filesystems
-and gives a minimal sequence of commands which will make one similar to
+and gives a minimal sequence of commands which transforms one into
 the other.
@@
 Let \(P_O\) be all the paths in the original
-filesystem, \(P_A\) all the paths in the current state of the replica. 
+filesystem, and \(P_A\) all the paths in the current state of the replica. 
 (We assume \(O,A\ne\ud\).)
@@
 First, we move all \(edit(\pi,\cdir{X})\) commands to the front and then
-all \(edit(\pi,\cfile{X})\) commands to the end of the sequence. Now for
-the middle part, we know the following:
-
-Since there is only one command on each path, we have a partial
+all \(edit(\pi,\cfile{X})\) commands to the end of the sequence. 
+Regarding the middle part, since there is only one command on each path, we have a partial
 ordering on the set of the commands (see section
-\ref{theorem:conc}) showing us which command must precede another one.
-Two commands can be interchanged if they refer to incomparable
-paths; otherwise, they are one of the following:
+\ref{theorem:conc}) determining which command must precede another one.
+Two commands can be interchanged freely if they refer to incomparable
+paths; otherwise, they will be ordered in one of the following ways:
 \begin{itemize}
@@
 This ordering can be represented by a graph. This graph is a tree (or
-forest). It's worth remarking that every tree of the forest is formed
-from the same commands, \(remove\)s or \(create\)s, since two different
-types of commands cannot show up at comparable paths.
+forest). It is worth remarking that every tree of the forest is formed
+from the same commands, \(remove\)s or \(create\)s, since 
+we cannot have two different
+types of commands at comparable paths.
 
-Starting at the leaves of the trees, we move the leaves as close as
-possible to their parent. (They will form a row at the left side of the
-branch--command at the \(remove\)--trees and at the other side at
-\(create\)--trees.) Then we order them alphabetically and form a
-\emph{group--command} from the leaves and the branch. This
+Starting at the leaves of the trees, let us move the leaves as close as
+possible to their parents to form a row on the left side of the
+parent command in \(remove\) trees and on the other side in
+\(create\) trees. Then we order the commands alphabetically and create a
+\emph{group--command} from them and their parent. This
 group--command
-will act like a single command since all of its members commute the
-same commands. Then we continue this method until every tree is
-grouped into one meta-group--command. We order these groups again.
-That way we gain an order of the commands. It's worth remarking that
-we gain the same order for the same set of commands every time.
+will act similarly to a single command as all of its members commute with the
+same commands. We continue this method until every tree is
+grouped into one group--command, and order these groups again.
+This way we gain a complete order of the commands. It is worth noting that
+this is a deterministic ordering.
 
@@
 we have a command in \(S\) but not in \(S'\) since all paths are different
-in \(S\). Now we know that \(SF(\varphi)\ne F(\varphi)\) but 
+in \(S\). We know that \(SF(\varphi)\ne F(\varphi)\) but 
 \(S'F(\varphi)=F(\varphi)\). (Note that we have no superfluous commands
-in \(S\) since we gained it from the update detector algorithm.)
+in \(S\) since we generated it using the update detector algorithm.)

### 2015-10-06 definition.tex
Removing unused content

@@
 contents.
-\begin{notrsi} 
 In real-life filesystems, files and directories can carry additional information
@@
 Here we consider these included in the contents.
-\end{notrsi}
 
@@
 
-\begin{notrsi}
 \begin{itemize}
@@
 \end{itemize}
-\end{notrsi}
-%
-\begin{forrsi}
-{\small{
-%\begin{align}
-\begin{gather*}\begin{array}{r@{}ll}
-create(\pi,X)F&{}=F\{\pi\mapsto X\}, 
-&\mbox{iff~}(F(\pi)=\ud)\wedge(F(parent(\pi))=\cdir{Y})\\
-&{}=\ud, &\mbox{otherwise.}\\
-edit(\pi,\cdir{X})F&{}=F\{\pi\mapsto \cdir{X}\}, 
-&\mbox{iff~}F(\pi)\neq\ud\\
-&{}=\ud &\mbox{otherwise;}\\
-edit(\pi,\cfile{X})F&{}=F\{\pi\mapsto\cfile{X}\} 
-&\mbox{iff~}(F(\pi)\neq\ud)\wedge(childless_F(\pi))\\  
-&{}=\ud &\mbox{otherwise.}\\
-remove(\pi)F&{}=F\{\pi\mapsto\ud\} 
-&\mbox{iff~}(F(\pi)\neq\ud)\wedge(childless_F(\pi))\\
-&{}=\ud &\mbox{otherwise.}\\
-breakF&{}=\ud &\mbox{for every $F$.}
-\end{array}\end{gather*}
-%\end{align}
-}}
-\end{forrsi}
-%%%%%%%%%% TAGS!
+
 We write \(\emptyseq\) for the empty sequence of commands.

### 2015-10-06 compl.tex
Text improvements
Removed unused content

@@
 
-\begin{forrsi}
-The following lemmas can be proved with a similar method.
-%For the sake of brevity, the proofs are omitted.
-\end{forrsi}
 \item[Lemma 2]
@@
 \(remove(\piesub)\).} 
-\begin{notrsi}
 \emph{Proof.} 
@@
 The induction step is the same.
-\end{notrsi}
 
@@
 \(create(\pi)\).} 
-\begin{notrsi}
 \emph{Proof.} This can be proved similarly, in this 
@@
 \lawviii, \lawxiv, \lawxv, \lawxx, \lawxxi, \lawxxviii.)
-\end{notrsi}
 
@@
 \(create(\pi)\).} 
-\begin{notrsi}
 \emph{Proof.} 
@@
 induction step is the same.
-\end{notrsi}
 
@@
 \(remove(\pi)\).} 
-\begin{notrsi}
 \emph{Proof.} 
@@
 \lawxv, \lawxvi, \lawxvii, \lawxxvii.)
-\end{notrsi}
 
@@
 precedes a command \(create(\piesub)\).} 
-\begin{notrsi}
 \emph{Proof.} 
@@
 In that case the induction hypothesis applies.
-\end{notrsi}
 \end{description}
@@
 
-\begin{forrsi}
-The following lemmas can be proved similarly.
-\end{forrsi}
 \item[Lemma E2] {\bf A command \(create(\pi)\) cannot precede a command 
 \(edit(\pi)\).} 
-\begin{notrsi}
 \emph{Proof.} The same; last step is made according to
 Lemma 2.
-\end{notrsi}
 
@@
 command \(edit(\pi,\cdir{X})\).} 
-\begin{notrsi}
 \emph{Proof.} 
@@
 it is, we have \(S\eqexp break\) according to Lemma 5.
-\end{notrsi}
 
@@
 command \(edit(\pi,\cdir{X})\).} 
-\begin{notrsi}
 \emph{Proof.} The same; last step
 according to Lemma 4.
-\end{notrsi}
 \end{description}
@@
 \emph{Proof.} 
-\begin{forrsi}
-It can be done similarly to the case of \(create\).
-\end{forrsi}
-\begin{notrsi}
 Now we can be sure that \(F(\pi)\ne\ud\) and
@@
 \(G(\pi)\ne\ud\). Again, we have contradiction in all cases.
-\end{notrsi}
 
@@
 
-We obtain \(S_0^*\) and \(S^\prime_0^*\) by applying this method to \(S_0\) and
+We obtain \(S_0^*\) and \({S^\prime}_0^*\) by applying this method to \(S_0\) and
 \(S^\prime_0\). Since they contain the same

### 2015-10-07 scripts/prove.py
Evaluation of commuting rules

@@ -370,22 +370,38 @@ def SequenceFactory():
 
 
 for sq in SequenceFactory():
+
+    sq_rev = sq.getReverse()
+    print ""
+    print sq.info()
+    print sq_rev.info() # Reverse sequence
+    
+    extends = False
+    narrows = False
+    differs = False
+
     for fs in FilesystemFactory():
-        print ""
-        print fs.info()
+        # print "   " + fs.info()
         
         # Investigate the original sequence
-        print "    " + sq.info()
         fs_res = fs.clone()
         fs_res.applySequence(sq)
-        print "  " + fs_res.info()
+        # print "  " + fs_res.info()
         
         # Investigate the reverse sequence
-        sq_rev = sq.getReverse()
-        print "    " + sq_rev.info()
         fs_rev_res = fs.clone()
         fs_rev_res.applySequence(sq_rev)
-        print "  " + fs_rev_res.info()
+        # print "  " + fs_rev_res.info()
         
-        print ("SAME" if fs_res.isSame(fs_rev_res) else "DIFFERENT")
+        if not fs_res.isSame(fs_rev_res):
+            if fs_res.isBroken():
+                extends = True
+            elif fs_rev_res.isBroken():
+                narrows = True
+            else:
+                differs = True
+        
+            # print ("SAME" if fs_res.isSame(fs_rev_res) else "DIFFERENT")
+            
+    print "::" + ("EXTENDS " if extends else "") + ("NARROWS " if narrows else "") + ("DIFFERS " if differs else "")
         

### 2015-10-23 scripts/prove.py
Started implementing recording path relationships in command pairs

@@ -166,6 +166,7 @@ DIRECT_CHILD       = 'DirectChild'       # p2 is the child of p2
 DIRECT_CHILD_ONLY  = 'DirectChildOnly'   # p2 is the child of p1 and p2 is the only child
 SEPARATE           = 'Separate'          # all other cases
 
+SAME               = 'Same'              # two paths are the same (used for command pairs)
 
 class Filesystem:
     """Models a filesystem focusing on two paths to emulate the results of commands
@@ -285,6 +286,7 @@ class Filesystem:
         sequence.map(lambda x: self.applyCommand(x))
 
 
+# TODO Specify relationship
 def FilesystemFactory():
     yield Filesystem(Node(broken=True), Node(broken=True), SEPARATE)
     for rel in [SEPARATE, DIRECT_CHILD, DIRECT_CHILD_ONLY, DIRECT_PARENT, DIRECT_PARENT_ONLY]:
@@ -361,12 +363,43 @@ class Sequence:
         return map(func, self.commands)
 
 
-# TODO add commands on same paths? (but will never have them from update detector)
-def SequenceFactory():
-    """Constructs all 2-long sequences"""
+
+class CommandPair(Sequence):
+    """ Represents a pair of commands
+   
+    see parent class
+    rel = DIRECT_PARENT or DIRECT_PARENT_ONLY or DIRECT_CHILD or DIRECT_CHILD_ONLY or SEPARATE or SAME
+    """
+    # There is no need to consider any other relationship, e.g. when one path is a parent,
+    # but not a direct parent of the other one, as unless there is a direct relationship,
+    # the command on one path is not going to change the environment of the other.
+
+    def __init__(self, command1, command2, rel):
+        self.commands = [command1, command2]
+        self.rel = rel
+
+    def getReverse(self):
+        tmp = Sequence.getReverse(self)
+        if self.rel == DIRECT_PARENT:
+            tmp.rel = DIRECT_CHILD
+        elif self.rel == DIRECT_PARENT_ONLY
+            tmp.rel = DIRECT_CHILD_ONLY
+        elif self.rel == DIRECT_CHILD
+            tmp.rel = DIRECT_PARENT
+        elif self.rel == DIRECT_CHILD_ONLY
+            tmp.rel = DIRECT_PARENT_ONLY
+        else
+            tmp.rel = SAME
+
+
+def CommandPairFactory():
[…]

### 2015-10-24 scripts/prove.py
Finished implementing testing command pairs while recording path relationships

@@ -195,7 +195,7 @@ class Filesystem:
         if self.rel == DIRECT_PARENT:
             return self.p2.info(debug) + " ~~~<> " + self.p1.info(debug)
         if self.rel == DIRECT_PARENT_ONLY:
-            return self.p2.info(debug) + " ~~~>> " + self.p1.info(debug)        
+            return self.p2.info(debug) + " ~~~>> " + self.p1.info(debug)
     
     def clone(self):
         return self.__class__(self.p1.clone(), self.p2.clone(), self.rel)
@@ -286,15 +286,13 @@ class Filesystem:
         sequence.map(lambda x: self.applyCommand(x))
 
 
-# TODO Specify relationship
-def FilesystemFactory():
-    yield Filesystem(Node(broken=True), Node(broken=True), SEPARATE)
-    for rel in [SEPARATE, DIRECT_CHILD, DIRECT_CHILD_ONLY, DIRECT_PARENT, DIRECT_PARENT_ONLY]:
-        for p1_source in NodeFactory('Old1'):
-            for p2 in NodeFactory('Old2'):
-                fs = Filesystem(p1_source.clone(), p2, rel)  # the constructor may break the p1 node, so we need to clone
-                if not fs.isBroken():
-                    yield fs
+def FilesystemFactory(rel):
+    yield Filesystem(Node(broken=True), Node(broken=True), rel)
+    for p1_source in NodeFactory('Old1'):
+        for p2 in NodeFactory('Old2'):
+            fs = Filesystem(p1_source.clone(), p2, rel)  # the constructor may break the p1 node, so we need to clone
+            if not fs.isBroken():
+                yield fs
 
 
 # Constants for Command.path:
@@ -354,10 +352,13 @@ class Sequence:
         """Returns human-readable information about the object"""
         return "; ".join(map(lambda x: x.info(debug), self.commands))
         
+    def clone(self):
+        return self.__class__(self.commands[:])
+        
     def getReverse(self):
-        tmp = self.commands[:]
-        tmp.reverse()
-        return self.__class__(tmp)
+        tmp = self.clone()
+        tmp.commands.reverse()
+        return tmp
         
     def map(self, func):
         return map(func, self.commands)
@@ -377,19 +378,39 @@ class CommandPair(Sequence):
     def __init__(self, command1, command2, rel):
         self.commands = [command1, command2]
         self.rel = rel
+        
+    def info(self, debug=False):
[…]

### 2015-10-25 scripts/prove.py
Only print summary and group by relationship

@@ -415,10 +415,11 @@ class CommandPair(Sequence):
 
 def CommandPairFactory():
     """Constructs all 2-long command sequences"""
-    for c1 in CommandFactory(PATH1, 'New1'):
-        for rel in [SEPARATE, DIRECT_CHILD, DIRECT_CHILD_ONLY, DIRECT_PARENT, DIRECT_PARENT_ONLY]:
+    for rel in [SEPARATE, DIRECT_CHILD, DIRECT_CHILD_ONLY, DIRECT_PARENT, DIRECT_PARENT_ONLY]:
+        for c1 in CommandFactory(PATH1, 'New1'):
             for c2 in CommandFactory(PATH2, 'New2'):
                 yield CommandPair(c1, c2, rel)
+    for c1 in CommandFactory(PATH1, 'New1'):
         for c2 in CommandFactory(PATH1, 'New2'):
             yield CommandPair(c1, c2, SAME);
 
@@ -426,9 +427,9 @@ def CommandPairFactory():
 for sq in CommandPairFactory():
 
     sq_rev = sq.getReverse() # Reverse sequence
-    print ""
-    print sq.info()
-    print sq_rev.info()
+    # print ""
+    # print sq.info()
+    # print sq_rev.info()
 
     works = False # Whether there are filesystems which sq doesn't break
     rev_works = False # Whether there are filesystems which sq_rev doesn't break
@@ -474,7 +475,10 @@ for sq in CommandPairFactory():
             # print ("SAME" if fs_res.isSame(fs_rev_res) else "DIFFERENT")
     
     if works:
-        print "::" + ("EXTENDS " if extends else "") + ("NARROWS " if narrows else "") + ("DIFFERS " if differs else "") + ("REV-BREAKS " if not rev_works else "") + ("DISJUNCT " if not both_work else "")
+        if rev_works:
+            print sq.info() + " ::" + ("EXTENDS " if extends else "") + ("NARROWS " if narrows else "") + ("DIFFERS " if differs else "") + ("DISJUNCT " if not both_work else "")
+        else:
+            print sq.info() + " ::REV_BREAKS"
     else:
-        print "::BREAKS"
+        print sq.info() + " ::BREAKS"
         

### 2015-10-25 2015/paper.tex
Started describing a new algebra

\documentclass[12pt]{article}

\usepackage{alltt}
\usepackage{comment}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{boxedminipage}
\usepackage{afterpage}

\newcommand{\setv}{\mathcal{V}}
\newcommand{\setf}{\mathcal{V}_F}
\newcommand{\setd}{\mathcal{V}_D}
\newcommand{\setp}{\mathcal{P}}
\newcommand{\empt}{\bot}
\newcommand{\parent}{\mathtt{parent}}
\newcommand{\FS}{\mathrm{FS}}

\title{Real-Life Algebraic File Synchronization}

\author{Elod Pal Csirmaz}

\begin{document}
\begin{abstract}
Abstract goes here
\end{abstract}

\section{Definition of a Filesystem}

We model a filesystem using a function with a set of paths $\setp$ as its domain,
and a set of possible contents $\setv$ as its codomain:
\[ \FS : \setp \rightarrow \setv \] 
In our model, $\setp$ contains all possible paths, and $\setv$ contains a special
element, $\empt$, which is the value of $FS$ at paths where there are no files
or directories.
We consider the contents of files, as well as any meta-information on files
and directories (e.g. permissions or flags) part of the values in $\setv$.

Every filesystem has a so-called \textbf{tree property}, which means that
if the filesystem is not empty at a path, and it is not a root path,
then it must have a directory at the path's parent.
This requires that a parent--child relationship is defined over $\setp$,
which we model using the function $\parent$, which returns the parent path
or $\empt$ if the path is a root path:
\[ \parent : \setp \rightarrow \setp \cup \{\empt\} \]

Moreover, in $\setv$ we distinguish between files ($\setf$) and directories ($\setd$), that is:
\[ \setv = \{\empt\} \cup \setf \cup \setd \]
The tree propety can then be defined as
\[ \forall \FS : \forall p\in\setp : \FS(p) \neq \empt \wedge \parent(p) \neq \empt \Rightarrow \FS(\parent(p)) \in \setd \]

% diagram

In this paper, we write $F$ for an arbitrary element of $\setf$, and $D$ for an arbitrary element
of $\setd$. $V$ is usually a value from $\setv$ and $p$ is a path in $\setp$.

\section{Commands and Sequences}

Next we need to define instructions or commands on the filesystem about which we will reason
using our algebra.
We will aim to draw conclusions or judgements about commands and sequences of commands
based on the algebra we are aiming to construct.
For example, if we believe that two sequences of commands are equivalent as their effect
is the same, then we aim to be able to derive this from the axioms and inference rules of the
algebra.
As the algebra operates on commands only,
these judgements, by definition, need to hold regardless of the filesystem the commands are applied to.
Accordingly, we expect that the more information one encodes into the commands and the sequences,
the better predicitons we will be able to make using our algebra,
as then the commands and sequences will be more specific, and will select a smaller subset
of potential filesystems on which they can meaningfully operate.

Let us consider what kind of information may be encoded in the commands.
A usual set of commands, based on the most frequent tools implemented by filesystems,
might be $create(p,V)$, $edit(p,V)$ and $remove(p,V)$ where $p\in\setp$ and $V\in\setv$.
Clearly the commands need to contain information about the state they leave the filesystem
in at the path on which they operate, that is, they need to contain the ``end'' value, $V$.
Notice, however, that the commands above also encode some information about the filesystem
{\it before} the command is applied; namely, $create$ requires that there are no files
or directories at $p$, while $edit$ and $remove$ require the opposite.

% No "move"

\end{document}

### 2015-10-25 2015/paper.tex
Continued with the new algebra

@@
 \newcommand{\setd}{\mathcal{V}_D}
+\newcommand{\setb}{\mathcal{V}_\empt}
 \newcommand{\setp}{\mathcal{P}}
@@
 \newcommand{\parent}{\mathtt{parent}}
-\newcommand{\FS}{\mathrm{FS}}
+\newcommand{\FS}{\Phi} % {\mathrm{FS}}
+
+\newcommand{\cbrk}{\mathtt{break}}
+\newcommand{\cbb}{\overrightarrow{\empt\empt}}
+\newcommand{\cbf}{\overrightarrow{\empt{F}}}
+\newcommand{\cbd}{\overrightarrow{\empt{D}}}
+\newcommand{\cfb}{\overrightarrow{F\empt}}
+\newcommand{\cff}{\overrightarrow{FF}}
+\newcommand{\cfd}{\overrightarrow{FD}}
+\newcommand{\cdb}{\overrightarrow{D\empt}}
+\newcommand{\cdf}{\overrightarrow{DF}}
+\newcommand{\cdd}{\overrightarrow{DD}}
+\newcommand{\cxy}{\overrightarrow{XY}}
 
@@
 
-We model a filesystem using a function with a set of paths $\setp$ as its domain,
+We model a filesystem using a function $\FS$ with a set of paths $\setp$ as its domain,
 and a set of possible contents $\setv$ as its codomain:
@@
 
-Moreover, in $\setv$ we distinguish between files ($\setf$) and directories ($\setd$), that is:
-\[ \setv = \{\empt\} \cup \setf \cup \setd \]
+Moreover, in $\setv$ we distinguish between files ($\setf$) and directories ($\setd$), that is,
+if $\setb = \{\empt\}$ then:
+\[ \setv = \setb \cup \setf \cup \setd \]
 The tree propety can then be defined as
@@
 % diagram
+% /> D ---> F ---> BOT <\
+% \--/               \--/
 
@@
 
-\section{Commands and Sequences}
+\section{Commands}
 
@@
 A usual set of commands, based on the most frequent tools implemented by filesystems,
-might be $create(p,V)$, $edit(p,V)$ and $remove(p,V)$ where $p\in\setp$ and $V\in\setv$.
+might be $create(p,V)$, $edit(p,V)$ and $remove(p)$ where $p\in\setp$ and $V\in\setv$.
 Clearly the commands need to contain information about the state they leave the filesystem
@@
 
+We also know that after $create$ or $edit$, $\FS(p)\neq\empt$, whereas after $remove$,
+$\FS(p)$ will be $\empt$. However, from \cite{NREC:alg} we know that a useful set of axioms
+will need to distinguish between edits that result in directories ($edit(p,D)$) and
+ones that result in files ($edit(p,F)$). This creates a seemingly arbitrary asymmetry where
+there is more information encoded into commands about their results than about the
+original state of the filesystem.
+
+In line with the aim to encode in commands as much information as possible,
+and in order to resolve this asymmetry, we propose a set of commands that encode
+the type of the original state of $\FS(p)$ as well.
+(Some real-life filesystem commands like $mkdir$ or $rmdir$ do this already.)
+Please note that there is never any need to encode information about the
+{\it exact} value of path $p$ in a command, merely its type ($D$, $F$ or $\empt$),
+as the success or failure of subsequent commands only depend on the type of the value.
+
+We therefore propose to have a command for each pair of types.
+For want of a better system, we will simply name our commands by concatenating
+two of $D$, $F$ and $\empt$ with an arrow, where the left sign notes the type of value
+in the filesystem before the command is applied, and the right sign notes the type
+afterwards. For example, $mkdir(p,D)$ is $\cbd(p,D)$ and $rmdir(p)$ is $\cdb(p)$.
+
 % No "move"
 
+\section{Applying Commands}
+
+The commands can only succeed if the original value at $p$ has a type that matches
+the type required by a command. If this is not the case, or if the resulting
+filesystem no longer has the tree property, then we say that the command
+\textbf{breaks} the filesystem. Broken filesystems are considered equal
+(but not equal to any working filesystem), and we note them by $\FS=\empt$.
+
+So that we could reason about sequences of commands that break every filesystem
+in the algebra, we introduce the command $\cbrk$ that simply breaks every filesystem.
+We note that a command or a sequence of commands $S$ is applied to a filesystem
+by prefixing the command or sequence to it:
+$S\FS$; or $\cbrk\FS=\empt$; or $\Xi = \cff(p,F)\FS$, for which $\Xi(p)=F$ holds
+and $\Xi(q)=\FS(q)$ for any path $q\neq p$.
+
+\section{Sequences of Commands}
+
+\begin{thebibliography}{99}
+
+\bibitem{NREC:alg} Ramsey, Norman and Elod Csirmaz: {\it An algebraic approach to
+file synchronization...}
+
+\end{thebibliography}
+
 \end{document}

### 2015-10-26 2015/paper.tex
Continued with describing the new algebra

@@
 \newcommand{\setv}{\mathcal{V}}
-\newcommand{\setf}{\mathcal{V}_F}
-\newcommand{\setd}{\mathcal{V}_D}
-\newcommand{\setb}{\mathcal{V}_\empt}
+\newcommand{\setvx}[1]{\mathcal{V}_{#1}}
+\newcommand{\setf}{\setvx{F}}
+\newcommand{\setd}{\setvx{D}}
+\newcommand{\setb}{\setvx{\empt}}
 \newcommand{\setp}{\mathcal{P}}
@@
 \newcommand{\FS}{\Phi} % {\mathrm{FS}}
+\newcommand{\GS}{\Xi} % another filesystem
 
@@
 \newcommand{\cxy}{\overrightarrow{XY}}
+\newcommand{\czw}{\overrightarrow{ZW}}
 
@@
 \begin{document}
+\maketitle
 \begin{abstract}
@@
 \end{abstract}
+
+\section{Introduction}
+
+% Synchronization:
+% Main aim: apply updates (where possible) from other replicas
+% update detection -> conflict detection -> merging updates -> ordering updates -> apply updates from other replicas
+% Problems: conflict detection, ordering
 
@@
 A usual set of commands, based on the most frequent tools implemented by filesystems,
-might be $create(p,V)$, $edit(p,V)$ and $remove(p)$ where $p\in\setp$ and $V\in\setv$.
+might be $create(p,V)$, $edit(p,V)$ and $remove(p)$ where $p\in\setp$ and $V\in\setv$ (but $V\neq\empt$).
 Clearly the commands need to contain information about the state they leave the filesystem
@@
 in the filesystem before the command is applied, and the right sign notes the type
-afterwards. For example, $mkdir(p,D)$ is $\cbd(p,D)$ and $rmdir(p)$ is $\cdb(p)$.
+afterwards. For example $mkdir(p,D)$ is $\cbd(p,D)$ and $rmdir(p)$ is $\cdb(p)$.
 
-% No "move"
+% TODO No "move"
 
@@
 by prefixing the command or sequence to it:
-$S\FS$; or $\cbrk\FS=\empt$; or $\Xi = \cff(p,F)\FS$, for which $\Xi(p)=F$ holds
-and $\Xi(q)=\FS(q)$ for any path $q\neq p$.
+\begin{itemize}
+\item $S\FS$
+\item $\cbrk\FS=\empt$
+\item $\cff(p,F)\FS = \GS$, for which $\GS(p)=F$ holds
+and $\GS(q)=\FS(q)$ for any path $q\neq p$.
+\end{itemize}
 
 \section{Sequences of Commands}
+
+We aim to use our algebra to define and implement algorithms for conflict detection
+and ordering updates (commands) before we can apply them to all replicas.
+Conflicts and ordering all happen between commands, therefore in our algebra
+we will reason about sequences of commands, 
+and do so based on a set of axioms about pairs of neighbouring commands.
+We are interested to see what pairs of commands can be simplified or reversed
+in order to see under what circumstances commands conflict or can be reordered.
+
+Pairs of commands in general will have the form
+\[ \cxy(p,V_Y) \czw(q,V_W) \]
+where $X,Y,Z,W\in\{D,F,\empt\}$, $p,q\in\setp$, and values are of the appropriate type: $V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$
+(although commands where $Y=\empt$ or $W=\empt$ do not require a value).
+
+Similarly to the case of commands, in \cite{NREC:alg} we found that in order to build
+a set of axioms in a sound and complete algebra we at times needed to take into account
+the relationship between the paths of the commands in the pair, $p$ and $q$.
+As the relationship between the paths determine how the commands affect the filesystem
+and its tree property, 
+and again in line with the aim of providing as much information as possible for the algebra,
+we encoded this relationship in the pair of commands. The possible relationships we
+need to take into account are as follows.
+
+\begin{itemize}
+\item $p=q$.
+\item $\parent(p)=q$ and $\parent(q)=p$. We know that 
+\item Only child
+\item separate
+\end{itemize}
 

### 2015-10-28 2015/prove.py
Check for simplification

@@ -31,6 +31,10 @@ class Content:
         
     def getType(self):
         return self.type
+    
+    def getValue(self):
+        if self.isEmpty(): return 'Unknown'
+        return self.value
         
     def isDir(self):
         return (self.type == DIR)
@@ -411,6 +415,9 @@ class CommandPair(Sequence):
         elif self.rel == DIRECT_CHILD_ONLY:
             tmp.rel = DIRECT_PARENT_ONLY
         return tmp
+    
+    def getLast(self):
+        return self.commands[1]
 
 
 def CommandPairFactory():
@@ -423,41 +430,69 @@ def CommandPairFactory():
         for c2 in CommandFactory(PATH1, 'New2'):
             yield CommandPair(c1, c2, SAME);
 
+# We test command pairs and aim to answer the following questions:
+# - Will the pair break all filesystems?
+# - If not, can the pair be substituted by a single command?
+# - If not, can the pair be reversed?
 
 for sq in CommandPairFactory():
 
-    sq_rev = sq.getReverse() # Reverse sequence
-    # print ""
-    # print sq.info()
+    fs_rel = sq.getRelationship()
+    if fs_rel == SAME:
+        fs_rel = SEPARATE
+        
+    # Does it break all filesystems?
+    for fs in FilesystemFactory(fs_rel):
+        fs.applySequence(sq)
+        if not fs.isBroken():
+            break # skips "else" below
+    else:
+        print sq.info() + " == break"
+        continue
+
+    # Try to find a single command with the same effect
+    # We know this is only possible, if the pair does not break all filesystems,
+    # if the two commands affect the same path.
+    if sq.getRelationship() == SAME:
+        for command in CommandFactory(sq.getLast().getPath(), sq.getLast().getEnd().getValue()):
+            for fs in FilesystemFactory(fs_rel):
+                # Apply the original sequence
+                fs_res = fs.clone()
+                fs_res.applySequence(sq)
+                # Apply the single command
+                fs_single = fs.clone()
+                fs_single.applyCommand(command)
+                if not fs_res.isSame(fs_single):
+                    break # skips "else" below
+            else: # found a suitable command
+                print sq.info() + " == " + command.info()
+                break
+        
+
+    # Reverse sequence
+    sq_rev = sq.getReverse()
     # print sq_rev.info()
 
-    works = False # Whether there are filesystems which sq doesn't break
[…]

### 2015-10-28 2015/prove.py
Finalised the comparison logic

@@ -1,7 +1,7 @@
 
 
 # Constants for Content.type:
-DIR   = 'Dir'
+DIR   = ' Dir'
 FILE  = 'File'
 EMPTY = 'Empty'
 
@@ -208,6 +208,12 @@ class Filesystem:
         if self.isBroken() and fs.isBroken(): return True
         if self.isBroken() or fs.isBroken(): return False
         return (self.p1.isSame(fs.p1) and self.p2.isSame(fs.p2) and self.rel == fs.rel)
+        
+    def isExtendedBy(self, fs):
+        """Returns true if self is broken but fs is not, or the are the same"""
+        if self.isBroken(): return True
+        if fs.isBroken(): return False
+        return (self.p1.isSame(fs.p1) and self.p2.isSame(fs.p2) and self.rel == fs.rel)
     
     def isBroken(self):
         return (self.p1.isBroken() or self.p2.isBroken())
@@ -339,8 +345,7 @@ class Command:
 def CommandFactory(path, value):
     for c1 in ContentFactory('N/A'):
         for c2 in ContentFactory(value):
-            if not(c1.isEmpty() and c2.isEmpty()):
-                yield Command(path, c1, c2)
+            yield Command(path, c1, c2)
 
 
 class Sequence:
@@ -386,17 +391,17 @@ class CommandPair(Sequence):
     def info(self, debug=False):
         """Returns human-readable information about the object"""
         if self.rel == SEPARATE:
-            return self.commands[0].info(debug) + " ==x== " + self.commands[1].info(debug)
+            return self.commands[0].info(debug) + " -x- " + self.commands[1].info(debug)
         if self.rel == DIRECT_CHILD:
-            return self.commands[0].info(debug) + " ===<> " + self.commands[1].info(debug)
+            return self.commands[0].info(debug) + " -<> " + self.commands[1].info(debug)
         if self.rel == DIRECT_CHILD_ONLY:
-            return self.commands[0].info(debug) + " ===>> " + self.commands[1].info(debug)
+            return self.commands[0].info(debug) + " ->> " + self.commands[1].info(debug)
         if self.rel == DIRECT_PARENT:
-            return self.commands[0].info(debug) + " <>=== " + self.commands[1].info(debug)
+            return self.commands[0].info(debug) + " <>- " + self.commands[1].info(debug)
         if self.rel == DIRECT_PARENT_ONLY:
[…]

### 2015-10-29 2015/prove.py
Improved documentation

@@ -7,26 +7,45 @@ EMPTY = 'Empty'
 
 
 class Content:
-    """Represents some content (value) at a given node
+    """Represents some content (value) at a given filesystem node
     
-    type = DIR or FILE or EMPTY
-    value = string
+    Private properties:
+        type (enum): DIR or FILE or EMPTY
+        value (str): an arbitrary string representing the contents
+        
     """
 
-    def __init__(self, type=EMPTY, value=0):
+    def __init__(self, type=EMPTY, value='Unknown'):
+        """Constructor
+        
+        Args:
+            type (Optional[enum]): DIR or FILE or EMPTY
+            value (Optional[str]): an arbitrary string representing the contents
+        
+        """
         self.type = type
         self.value = value
         
     def clone(self):
+        """Returns a deep clone of the object."""
         return self.__class__(self.type, self.value)
 
     def info(self, addvalue=True):
-        """Returns human-readable information about the object"""
+        """Returns human-readable information about the object.
+        
+        Args:
+            addvalue (Optional[bool]): whether to add the value to the output
+            
+        Returns:
+            str
+            
+        """
         r = self.type
         if not self.isEmpty() and addvalue: r += "(" + self.value + ")"
         return r
         
     def isSame(self, content):
+        """Returns whether the current object is the same as another instance of Content."""
         return (self.type == content.type and self.value == content.value)
         
     def getType(self):
@@ -37,17 +56,28 @@ class Content:
         return self.value
         
     def isDir(self):
+        """Returns whether the type of the object is 'diretory'."""
         return (self.type == DIR)
 
     def isFile(self):
+        """Returns whether the type of the object is 'file'."""
         return (self.type == FILE)
 
     def isEmpty(self):
+        """Returns whether the type of the object is 'empty'."""
         return (self.type == EMPTY)
 
 
 def ContentFactory(value='Unknown'):
-    """Constructs all possible contents"""
+    """Generates all possible contents.
+    
+    Args:
+        value (Optional[str]): the value of the content objects
+        
+    Yields:
+        All possible content objects
+        
+    """
     yield Content(EMPTY)
     yield Content(FILE, value)
     yield Content(DIR, value)

### 2015-10-30 2015/prove.py
Improved documentation

@@ -1,4 +1,7 @@
 
+# TODO Documentation
+# TODO Check if empty sequence can replace pair
+# TODO Implement 'broken' command
 
 # Constants for Content.type:
 DIR   = ' Dir'
@@ -7,11 +10,11 @@ EMPTY = 'Empty'
 
 
 class Content:
-    """Represents some content (value) at a given filesystem node
+    """Represents some content (element of set V) at a given path in the filesystem
     
     Private properties:
         type (enum): DIR or FILE or EMPTY
-        value (str): an arbitrary string representing the contents
+        value (str): an arbitrary string representing e.g. file contents and metadata
         
     """
 
@@ -19,8 +22,8 @@ class Content:
         """Constructor
         
         Args:
-            type (Optional[enum]): DIR or FILE or EMPTY
-            value (Optional[str]): an arbitrary string representing the contents
+            type (Optional[enum]):
+            value (Optional[str]):
         
         """
         self.type = type
@@ -45,7 +48,7 @@ class Content:
         return r
         
     def isSame(self, content):
-        """Returns whether the current object is the same as another instance of Content."""
+        """Returns whether the object is the same as another content object."""
         return (self.type == content.type and self.value == content.value)
         
     def getType(self):
@@ -84,15 +87,27 @@ def ContentFactory(value='Unknown'):
 
 
 class Node:
-    """Represents a path and its environment relevant for commands
-    
-    has_parent = bool
-    content = Content object
-    has_child = bool
-    broken = None or string if broken (the reason for being broken)
+    """Represents a path in the filesystem and information about its environment
+
+    Private properties:    
+        has_parent (bool): whether the node has a parent (i.e. there is a directory at the parent path)
+        content (Content): a content object
+        has_child (bool): whether the node has a child (i.e. one of the child paths is not empty)
+        broken (None|str): None if the filesystem is not broken at this node;
+            the reason for being broken otherwise
+
     """
 
     def __init__(self, has_parent=False, content=None, has_child=False, broken=False):
+        """Constructor.
+
+        Args:
+            has_parent (Optional[bool]):
+            content (Optional[Content]):
+            has_child (Optional[bool]):
+            broken (Optional[None|str]):
+
+        """
         self.has_parent = has_parent
         self.content = Content() if content is None else content
         self.has_child = has_child
@@ -100,10 +115,19 @@ class Node:
[…]

### 2015-10-30 2015/prove.py
Invesitgate if the pair is equivalent to noop. Improved documentation.

@@ -1,6 +1,6 @@
 
 # TODO Documentation
-# TODO Check if empty sequence can replace pair
+# TODO Implement a version where there is only one directory value
 # TODO Implement 'broken' command
 
 # Constants for Content.type:
@@ -383,8 +383,10 @@ class Filesystem:
         command_path = command.getPath()
         new_content = command.getEnd()
 
-        # If we apply a command to the (direct) child path,
-        # then we may need to update the has_child flag of the parent
+        # We update the environments stored in the other node if needed.
+        # The node objects mark themselves as broken after any change
+        # if that violates the tree property. This is safe, however,
+        # as we apply only a single change to each path.
         if self.rel != SEPARATE:
             if self.rel in [DIRECT_CHILD, DIRECT_CHILD_ONLY]:
                 childpath = PATH2
@@ -533,35 +535,48 @@ class Sequence:
         return "; ".join(map(lambda x: x.info(debug), self.commands))
         
     def clone(self):
-        """Returns a shallow clone of the sequence. The commands are not mutable."""
+        """Returns a shallow clone of the sequence. Commands are not mutable."""
         return self.__class__(self.commands[:])
         
     def getReverse(self):
+        """Returns a new object with the sequence reversed."""
         tmp = self.clone()
         tmp.commands.reverse()
         return tmp
         
     def map(self, func):
+        """Applies func to all commands in the sequence."""
         return map(func, self.commands)
 
 
 
 class CommandPair(Sequence):
-    """ Represents a pair of commands
-   
-    see parent class
-    rel = DIRECT_PARENT or DIRECT_PARENT_ONLY or DIRECT_CHILD or DIRECT_CHILD_ONLY or SEPARATE or SAME
+    """Represents a pair of commands, including the relationship between their paths.
+    
+    Private properties:
+        commands (list): see parent class
+        rel (enum): the relationship between the paths of the two commands.
+            DIRECT_PARENT or DIRECT_PARENT_ONLY or DIRECT_CHILD or DIRECT_CHILD_ONLY or SEPARATE or SAME
+
     """
     # There is no need to consider any other relationship, e.g. when one path is a parent,
     # but not a direct parent of the other one, as unless there is a direct relationship,
     # the command on one path is not going to change the environment of the other.
 
     def __init__(self, command1, command2, rel):
+        """Constructor.
+        
+        Args:
[…]

### 2015-10-31 2015/paper.tex
Reduced the types of relationships in pairs of commands

@@
 \newcommand{\GS}{\Xi} % another filesystem
+\newcommand{\pp}{\hat{p}} % parent path
+\newcommand{\np}{\mathrel{\ooalign{$p$\cr\hidewidth\hbox{$-$}\cr}}} % path not related to p
 
 \newcommand{\cbrk}{\mathtt{break}}
-\newcommand{\cbb}{\overrightarrow{\empt\empt}}
-\newcommand{\cbf}{\overrightarrow{\empt{F}}}
-\newcommand{\cbd}{\overrightarrow{\empt{D}}}
-\newcommand{\cfb}{\overrightarrow{F\empt}}
-\newcommand{\cff}{\overrightarrow{FF}}
-\newcommand{\cfd}{\overrightarrow{FD}}
-\newcommand{\cdb}{\overrightarrow{D\empt}}
-\newcommand{\cdf}{\overrightarrow{DF}}
-\newcommand{\cdd}{\overrightarrow{DD}}
-\newcommand{\cxy}{\overrightarrow{XY}}
-\newcommand{\czw}{\overrightarrow{ZW}}
+\newcommand{\fscommand}[2]{{#1#2}}
+\newcommand{\cbb}{\fscommand{\empt\empt}}
+\newcommand{\cbf}{\fscommand{\empt{F}}}
+\newcommand{\cbd}{\fscommand{\empt{D}}}
+\newcommand{\cfb}{\fscommand{F\empt}}
+\newcommand{\cff}{\fscommand{FF}}
+\newcommand{\cfd}{\fscommand{FD}}
+\newcommand{\cdb}{\fscommand{D\empt}}
+\newcommand{\cdf}{\fscommand{DF}}
+\newcommand{\cdd}{\fscommand{DD}}
+\newcommand{\cxy}{\fscommand{XY}}
+\newcommand{\czw}{\fscommand{ZW}}
 
@@
 In our model, $\setp$ contains all possible paths, and $\setv$ contains a special
-element, $\empt$, which is the value of $FS$ at paths where there are no files
+element, $\empt$, which is the value of $\FS$ at paths where there are no files
 or directories.
-We consider the contents of files, as well as any meta-information on files
+We consider the contents of files, as well as any meta-information of files
 and directories (e.g. permissions or flags) part of the values in $\setv$.
@@
 In this paper, we write $F$ for an arbitrary element of $\setf$, and $D$ for an arbitrary element
-of $\setd$. $V$ is usually a value from $\setv$ and $p$ is a path in $\setp$.
+of $\setd$. $V$ is usually a value from $\setv$ and $p$ and $q$ are paths in $\setp$.
 
@@
 For want of a better system, we will simply name our commands by concatenating
-two of $D$, $F$ and $\empt$ with an arrow, where the left sign notes the type of value
+two of $\fscommand{D}{}$, $\fscommand{F}{}$ and $\fscommand{\empt}{}$, 
+where the left sign notes the type of value
 in the filesystem before the command is applied, and the right sign notes the type
@@
 Pairs of commands in general will have the form
-\[ \cxy(p,V_Y) \czw(q,V_W) \]
-where $X,Y,Z,W\in\{D,F,\empt\}$, $p,q\in\setp$, and values are of the appropriate type: $V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$
+\[ \cxy(p,V_Y); \czw(q,V_W) \]
+where $X,Y,Z,W\in\{D,F,\empt\}$, $p,q\in\setp$, and values are of the appropriate type: 
+$V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$
 (although commands where $Y=\empt$ or $W=\empt$ do not require a value).
@@
 and again in line with the aim of providing as much information as possible for the algebra,
-we encoded this relationship in the pair of commands. The possible relationships we
-need to take into account are as follows.
+we encode this relationship in the pair of commands. The possible relationships we
+consider are as follows.
 
 \begin{itemize}
-\item $p=q$.
-\item $\parent(p)=q$ and $\parent(q)=p$. We know that 
-\item Only child
-\item separate
+\item $p=q$. If the two commands affect the same path, the pair of commands
+will clearly behave differently than if the paths are different.
+\item Separate paths, that is, $\parent(p)\neq q$ and $\parent(q)\neq p$. If the paths
+are not directly related, then modifying the filesystem at one path is not going
+to affect the outcome of the command on the other path.
+The two commands will therefore commute and the pair will be reversible.
+\item Directly related paths, that is, $\parent(p)=q$ or $\parent(q)=p$.
+Some of these command pairs will not be reversible.
+For example, $\cbd(\parent(p),D);\cbf(p,F)$ will work on some filesystems,
+while $\cbf(p,F);\cbd(\parent(p),D)$ will break all filesystems.
 \end{itemize}
+
+One may think that we may be able to specify more about the reversibility
+or possible simplification of a pair of commands in the last group if we also
+knew whether the child path $p$ was the only (non-empty) child of its parent.
+However, it is easy to see that encoding this information in a pair
+is not going to enrich our algebra as, for example,
+the behaviour of a hypothetical $\cfb(p_{\mathrm{only\ child}}); \cdb(\parent(p))$
+is exactly the same as that of the more generic
+$\cfb(p); \cdb(\parent(p))$. The former will break any filesystem in which
+$p$ is not the only child as it violates its preconditions, but so will
+the generic pair.
+
+In summary, if we adopt the notation $\pp := \parent(p)$ and use $\np$ for a path not directly related to $p$,
+then we have pairs of commands
+of the following forms:
+\begin{align*}
+\cxy(p,V_Y)&; \czw(p,V_W) \\
+\cxy(p,V_Y)&; \czw(\np,V_W) \\
+\cxy(p,V_Y)&; \czw(\pp,V_W) \\
+\cxy(\pp,V_Y)&; \czw(p,V_W)
+\end{align*}
 

### 2015-10-31 2015/prove.py

@@ -556,7 +556,7 @@ class CommandPair(Sequence):
     Private properties:
         commands (list): see parent class
         rel (enum): the relationship between the paths of the two commands.
-            DIRECT_PARENT or DIRECT_PARENT_ONLY or DIRECT_CHILD or DIRECT_CHILD_ONLY or SEPARATE or SAME
+            DIRECT_PARENT or DIRECT_CHILD or SEPARATE or SAME
 
     """
     # There is no need to consider any other relationship, e.g. when one path is a parent,
@@ -617,7 +617,7 @@ class CommandPair(Sequence):
 
 def CommandPairFactory():
     """Generates all possible command pairs. The file content values used will always be different."""
-    for rel in [SEPARATE, DIRECT_CHILD, DIRECT_CHILD_ONLY, DIRECT_PARENT, DIRECT_PARENT_ONLY]:
+    for rel in [SEPARATE, DIRECT_CHILD, DIRECT_PARENT]:
         for c1 in CommandFactory(PATH1, 'New1'):
             for c2 in CommandFactory(PATH2, 'New2'):
                 yield CommandPair(c1, c2, rel)
@@ -669,28 +669,25 @@ for sq in CommandPairFactory():
     
 
     # Try to find a single command with the same effect
-    # We know this is only possible, if the pair does not break all filesystems,
-    # if the two commands affect the same path.
     canSimplify = False
-    if sq.getRelationship() == SAME:
-        for command in CommandFactory(sq.getLast().getPath(), sq.getLast().getEnd().getValue()):
-            simplifiesEq = True  # Whether command is equivalent to sq on all filesystems
-            simplifiesExt = True # Whether command extends sq
-            for fs in FilesystemFactory(fs_rel):
-                # Apply the original sequence
-                fs_res = fs.clone()
-                fs_res.applySequence(sq)
-                # Apply the single command
-                fs_single = fs.clone()
-                fs_single.applyCommand(command)
-                if not fs_res.isSame(fs_single): simplifiesEq = False
-                if not fs_res.isExtendedBy(fs_single): simplifiesExt = False
-            if simplifiesEq:
-                canSimplify = True
-                print sq.info() + " \t== " + command.info()
-            elif simplifiesExt:
-                canSimplify = True
-                print sq.info() + " \t=[ " + command.info()
+    for command in CommandFactory(sq.getLast().getPath(), sq.getLast().getEnd().getValue()):
[…]

### 2015-10-31 2015/prove.py
Inspect filesystems with all suitable relationships. Try the first command when simplifying.

@@ -1,7 +1,7 @@
+from itertools import chain
 
-# TODO Documentation
 # TODO Implement a version where there is only one directory value
-# TODO Implement 'broken' command
+# TODO Implement 'break' command
 
 # Constants for Content.type:
 DIR   = ' Dir'
@@ -49,7 +49,10 @@ class Content:
         
     def isSame(self, content):
         """Returns whether the object is the same as another content object."""
-        return (self.type == content.type and self.value == content.value)
+        if self.type != content.type: return False
+        if self.type == EMPTY: return True
+        # if self.type == DIR: return True
+        return (self.value == content.value)
         
     def getType(self):
         return self.type
@@ -430,22 +433,23 @@ class Filesystem:
         return self
 
 
-def FilesystemFactory(rel):
+def FilesystemFactory(rel_list):
     """Generates all possible filesystems with the given relationship between p1 and p2.
 
     Args:
-        rel (enum): DIRECT_PARENT or DIRECT_PARENT_ONLY or DIRECT_CHILD or DIRECT_CHILD_ONLY or SEPARATE
+        rel_list (list): List of DIRECT_PARENT or DIRECT_PARENT_ONLY or DIRECT_CHILD or DIRECT_CHILD_ONLY or SEPARATE
 
     Yields:
         possible filesystem objects
 
     """
-    yield Filesystem(Node(broken=True), Node(broken=True), rel)
-    for p1_source in NodeFactory('Old1'):
-        for p2 in NodeFactory('Old2'):
-            fs = Filesystem(p1_source.clone(), p2, rel)  # the constructor may break the p1 node, so we need to clone
-            if not fs.isBroken():
-                yield fs
+    for rel in rel_list:
+        yield Filesystem(Node(broken=True), Node(broken=True), rel)
+        for p1_source in NodeFactory('Old1'):
+            for p2 in NodeFactory('Old2'):
+                fs = Filesystem(p1_source.clone(), p2, rel)  # the constructor may break the p1 node, so we need to clone
+                if not fs.isBroken():
+                    yield fs
 
 
 # Constants for Command.path:
@@ -505,9 +509,10 @@ class Command:
 
 
 def CommandFactory(path, value):
-    """Generates all possible commands that uses the given value in its end-content (if applicable).
+    """Generates all possible commands that uses the given path and value in its end-content (if applicable).
 
     Args:
+        path (enum): the path
[…]

### 2015-11-02 2015/prove.py
Implemented defaults, one-directory option and deduplication

@@ -1,7 +1,10 @@
 from itertools import chain
 
-# TODO Implement a version where there is only one directory value
-# TODO Implement 'break' command
+# Whether directories have equal contents, i.e. there is only a single
+# directory-type value in the filesystem.
+ONE_DIRECTORY_VALUE = False
+
+DEBUG = False
 
 # Constants for Content.type:
 DIR   = ' Dir'
@@ -33,25 +36,18 @@ class Content:
         """Returns a deep clone of the object."""
         return self.__class__(self.type, self.value)
 
-    def info(self, addvalue=True):
-        """Returns human-readable information about the object.
-        
-        Args:
-            addvalue (Optional[bool]): whether to add the value to the output
-            
-        Returns:
-            str
-            
-        """
+    def info(self, addvalue=True, debug=False):
+        """Returns human-readable information about the object."""
         r = self.type
-        if not self.isEmpty() and addvalue: r += "(" + self.value + ")"
+        if debug or (addvalue and not self.isEmpty() and not(ONE_DIRECTORY_VALUE and self.isDir())):
+            r += "(" + self.value + ")"
         return r
         
     def isSame(self, content):
         """Returns whether the object is the same as another content object."""
         if self.type != content.type: return False
-        if self.type == EMPTY: return True
-        # if self.type == DIR: return True
+        if self.isEmpty(): return True
+        if ONE_DIRECTORY_VALUE and self.isDir(): return True
         return (self.value == content.value)
         
     def getType(self):
@@ -138,7 +134,7 @@ class Node:
             else:
                 return "(Broken)"
         if self.has_parent: r.append("o--")
-        r.append(self.content.info())
+        r.append(self.content.info(debug))
         if self.has_child: r.append("--o")
         return "(" + "".join(r) + ")"
         
@@ -483,8 +479,15 @@ class Command:
         
     def info(self, debug=False):
         """Returns a human-readable string describing the object."""
-        return "{" + self.path + ":" + self.start.info(False) + ">" + self.end.info() + "}"
+        return "{" + self.path + ":" + self.start.info(False, debug) + ">" + self.end.info(True, debug) + "}"
 
+    def isSame(self, command):
+        """Returns whether self is the same as another command object."""
+        if self.path != command.path: return False
[…]

### 2015-11-03 2015/prove.py
Added TeX output

@@ -4,6 +4,8 @@ from itertools import chain
 # directory-type value in the filesystem.
 ONE_DIRECTORY_VALUE = False
 
+STYLE = 'normal' # 'normal or 'debug' or 'tex'
+
 DEBUG = False
 
 # Constants for Content.type:
@@ -36,11 +38,28 @@ class Content:
         """Returns a deep clone of the object."""
         return self.__class__(self.type, self.value)
 
-    def info(self, addvalue=True, debug=False):
-        """Returns human-readable information about the object."""
-        r = self.type
-        if debug or (addvalue and not self.isEmpty() and not(ONE_DIRECTORY_VALUE and self.isDir())):
-            r += "(" + self.value + ")"
+    def info(self, addvalue=True, path=None):
+        """Returns human-readable information about the object.
+        
+        Args:
+            addvalue (bool): whether to add a description of the value
+            path (None or string): used with TeX output; added if addvalue to become the first argument of a command
+        
+        """
+        if STYLE == 'tex':
+            if self.isEmpty(): rc = 'b'
+            elif self.isDir(): rc = 'd'
+            elif self.isFile(): rc = 'f'
+            r = rc
+            if addvalue: r += '(' + path
+        else:
+            r = self.type
+        if STYLE == 'debug' or (addvalue and not self.isEmpty() and not(ONE_DIRECTORY_VALUE and self.isDir())):
+            if STYLE == 'tex':
+                r += ', ' + rc.upper() + '_' + self.value[-1:]
+            else:
+                r += '(' + self.value + ')'
+        if STYLE == 'tex' and addvalue: r += ')'
         return r
         
     def isSame(self, content):
@@ -117,16 +136,8 @@ class Node:
         """Returns a deep clone of the object."""
         return self.__class__(self.has_parent, self.content.clone(), self.has_child, self.broken)
         
-    def info(self, debug=False):
-        """Returns a human-readable string describing the object.
-
-        Args:
-            debug (Optional[bool]): include extra information if True
-
-        Returns:
-            str
-
-        """
+    def info(self):
+        """Returns a human-readable string describing the object."""
         r = []
         if self.isBroken():
             if debug:
@@ -134,7 +145,7 @@ class Node:
             else:
                 return "(Broken)"
[…]

### 2015-11-04 2015/prove.py
Grouped rules; added labels and predictions

@@ -4,9 +4,7 @@ from itertools import chain
 # directory-type value in the filesystem.
 ONE_DIRECTORY_VALUE = False
 
-STYLE = 'normal' # 'normal or 'debug' or 'tex'
-
-DEBUG = False
+STYLE = 'tex' # 'normal or 'debug' or 'tex'
 
 # Constants for Content.type:
 DIR   = ' Dir'
@@ -61,6 +59,10 @@ class Content:
                 r += '(' + self.value + ')'
         if STYLE == 'tex' and addvalue: r += ')'
         return r
+    
+    def label(self):
+        """Returns a short string describing some parts of the object."""
+        return self.info(False)
         
     def isSame(self, content):
         """Returns whether the object is the same as another content object."""
@@ -498,6 +500,10 @@ class Command:
             return r
         else:
             return "{" + self.path + ":" + self.start.info(False) + ">" + self.end.info(True) + "}"
+        
+    def label(self):
+        """Returns a short string describing some parts of the object."""
+        return self.start.label() + self.end.label()
 
     def isSame(self, command):
         """Returns whether self is the same as another command object."""
@@ -506,8 +512,15 @@ class Command:
         if not self.end.isSame(command.end): return False
         return True
     
+    def isDirToDir(self):
+        """Returns if the command is a Dir->Dir."""
+        return self.getStart().isDir() and self.getEnd().isDir()
+    
     def getPath(self):        
         return self.path
+    
+    def getStart(self):
+        return self.start
         
     def getEnd(self):
         return self.end
@@ -576,6 +589,13 @@ class Sequence:
         return map(func, self.commands)
 
 
+# Cosntants for axiom groups
+A_BREAKING = 'Br'
+A_SIMPLIFY = 'Sp'
+A_COMMUTE = 'Cm'
+A_NORULE = 'No'
+A_UNKNOWN = '??'
+
 
 class CommandPair(Sequence):
     """Represents a pair of commands, including the relationship between their paths.
@@ -610,6 +630,15 @@ class CommandPair(Sequence):
             Dsep = {SEPARATE: 'xx', DIRECT_CHILD: '->', DIRECT_PARENT: '<-', SAME: '--'}
             return self.commands[0].info() + ' ' + Dsep[self.rel] + ' ' + self.commands[1].info()
         
+    def label(self):
+        """Returns a short string describing some of the object"""
[…]

### 2015-11-07 2015/paper.tex
Detailed two sets of axioms. Style improvements.

@@
 \usepackage{comment}
-\usepackage{multicol}
 \usepackage{amsmath}
@@
 \usepackage{graphicx}
-\usepackage{boxedminipage}
 \usepackage{afterpage}
+\usepackage{centernot}
+
+\usepackage{tikz}
 
@@
 \newcommand{\GS}{\Xi} % another filesystem
-\newcommand{\pp}{\hat{p}} % parent path
-\newcommand{\np}{\mathrel{\ooalign{$p$\cr\hidewidth\hbox{$-$}\cr}}} % path not related to p
+\newcommand{\pp}{p^\uparrow} % parent path
+\newcommand{\np}{p_{\centernot\leftrightarrow}} % path not related to p
 
@@
 \newcommand{\fscommand}[2]{{#1#2}}
-\newcommand{\cbb}{\fscommand{\empt\empt}}
-\newcommand{\cbf}{\fscommand{\empt{F}}}
-\newcommand{\cbd}{\fscommand{\empt{D}}}
-\newcommand{\cfb}{\fscommand{F\empt}}
-\newcommand{\cff}{\fscommand{FF}}
-\newcommand{\cfd}{\fscommand{FD}}
-\newcommand{\cdb}{\fscommand{D\empt}}
-\newcommand{\cdf}{\fscommand{DF}}
-\newcommand{\cdd}{\fscommand{DD}}
-\newcommand{\cxy}{\fscommand{XY}}
-\newcommand{\czw}{\fscommand{ZW}}
+\newcommand{\fsregcommandchar}[1]{\mathtt{#1}}
+\newcommand{\fsregcommand}[2]{\fscommand{\fsregcommandchar{#1}}{\fsregcommandchar{#2}}}
+\newcommand{\cbb}{\fsregcommand{\empt}{\empt}}
+\newcommand{\cbf}{\fsregcommand{\empt}{F}}
+\newcommand{\cbd}{\fsregcommand{\empt}{D}}
+\newcommand{\cfb}{\fsregcommand{F}{\empt}}
+\newcommand{\cff}{\fsregcommand{F}{F}}
+\newcommand{\cfd}{\fsregcommand{F}{D}}
+\newcommand{\cdb}{\fsregcommand{D}{\empt}}
+\newcommand{\cdf}{\fsregcommand{D}{F}}
+\newcommand{\cdd}{\fsregcommand{D}{D}}
+\newcommand{\cxy}{\fscommand{X}{Y}}
+\newcommand{\cyz}{\fscommand{Y}{Z}}
+\newcommand{\cxz}{\fscommand{X}{Z}}
+\newcommand{\czw}{\fscommand{Z}{W}}
 
-\title{Real-Life Algebraic File Synchronization}
+\newcommand{\eqext}{\sqsubseteq}
+\newcommand{\eqnrw}{\sqsupseteq}
+
+\newcommand{\emptyseq}{[\,]}
+
+\title{A Complete Algebra for File Synchronization}
 
@@
 The tree propety can then be defined as
-\[ \forall \FS : \forall p\in\setp : \FS(p) \neq \empt \wedge \parent(p) \neq \empt \Rightarrow \FS(\parent(p)) \in \setd \]
+\[ \forall \FS, p\in\setp : \FS(p) \neq \empt \wedge \parent(p) \neq \empt \Rightarrow \FS(\parent(p)) \in \setd \]
+
+This means that as we move from a path to its child, its grandchild, and so on,
+the types of values we encounter in the filesystem can only change according to the following
+transition diagram:
 
@@
 % \--/               \--/
+\input{type-transition}
+
+In other words, the types will form a sequence like $D,D,\cdots,D,F,\empt,\empt,\cdots$.
 
@@
 For want of a better system, we will simply name our commands by concatenating
-two of $\fscommand{D}{}$, $\fscommand{F}{}$ and $\fscommand{\empt}{}$, 
+two of $\fsregcommandchar{D}$, $\fsregcommandchar{F}$ and $\fsregcommandchar{\empt}$, 
 where the left sign notes the type of value
@@
 in the algebra, we introduce the command $\cbrk$ that simply breaks every filesystem.
-We note that a command or a sequence of commands $S$ is applied to a filesystem
-by prefixing the command or sequence to it:
+We note that a sequence of commands $S$ is applied to a filesystem
+by prefixing the sequence to it:
 \begin{itemize}
 \item $S\FS$
-\item $\cbrk\FS=\empt$
-\item $\cff(p,F)\FS = \GS$, for which $\GS(p)=F$ holds
+\item $[\cbrk]\FS=\empt$
+\item $[\cff(p,F)]\FS = \GS$, for which $\GS(p)=F$ holds
 and $\GS(q)=\FS(q)$ for any path $q\neq p$.
@@
 Pairs of commands in general will have the form
-\[ \cxy(p,V_Y); \czw(q,V_W) \]
-where $X,Y,Z,W\in\{D,F,\empt\}$, $p,q\in\setp$, and values are of the appropriate type: 
+\[ [\cxy(p,V_Y); \czw(q,V_W)] \]
+where $X,Y,Z,W\in\{\fsregcommandchar{D},\fsregcommandchar{F},\empt\}$, $p,q\in\setp$, and values are of the appropriate type: 
 $V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$
@@
 will clearly behave differently than if the paths are different.
+%
 \item Separate paths, that is, $\parent(p)\neq q$ and $\parent(q)\neq p$. If the paths
@@
 The two commands will therefore commute and the pair will be reversible.
+We will denote a path separate from $p$ with $\np$.
+%
 \item Directly related paths, that is, $\parent(p)=q$ or $\parent(q)=p$.
+For simplicity, we will write $\pp$ for $\parent(p)$.
 Some of these command pairs will not be reversible.
-For example, $\cbd(\parent(p),D);\cbf(p,F)$ will work on some filesystems,
-while $\cbf(p,F);\cbd(\parent(p),D)$ will break all filesystems.
+For example, $[\cbd(\pp,D);\cbf(p,F)]$ will work on some filesystems,
+while $[\cbf(p,F);\cbd(\pp,D)]$ will break all filesystems.
 \end{itemize}
@@
 is not going to enrich our algebra as, for example,
-the behaviour of a hypothetical $\cfb(p_{\mathrm{only\ child}}); \cdb(\parent(p))$
+the behaviour of a hypothetical $[\cfb(p_{\mathrm{only\ child}}); \cdb(\pp)]$
 is exactly the same as that of the more generic
-$\cfb(p); \cdb(\parent(p))$. The former will break any filesystem in which
+$[\cfb(p); \cdb(\pp)]$. The former will break any filesystem in which
 $p$ is not the only child as it violates its preconditions, but so will
@@
 
-In summary, if we adopt the notation $\pp := \parent(p)$ and use $\np$ for a path not directly related to $p$,
-then we have pairs of commands
+In summary, we have pairs of commands
 of the following forms:
-\begin{align*}
-\cxy(p,V_Y)&; \czw(p,V_W) \\
-\cxy(p,V_Y)&; \czw(\np,V_W) \\
-\cxy(p,V_Y)&; \czw(\pp,V_W) \\
-\cxy(\pp,V_Y)&; \czw(p,V_W)
-\end{align*}
+\begin{itemize}
+\item[i.] \( [\cxy(p,V_Y); \czw(\np,V_W)] \)
+\item[ii.] \( [\cxy(p,V_Y); \czw(p,V_W)] \)
+\item[iii.] \( [\cxy(\pp,V_Y); \czw(p,V_W)] \)
+\item[iv.] \( [\cxy(p,V_Y); \czw(\pp,V_W)] \)
+\end{itemize}
+
+%% What does it mean to restrict the inspected filesystems to a given relationship?
+
+\section{Defining the Algebra}
+
+In order to reason about sequences of commands, we define \emph{algebraic laws} on
+commands. We use formal logic to build a proof system which is sound and
+complete for its intended interpretation.
+
+Similarly to \cite{NREC:alg}, we have two kinds of judgements
+for sequences \(S_1\) and \(S_2\):
+\begin{itemize}
+\item \(S_1\equiv S_2\), or \emph{\(S_1\) is algebraically equivalent to
+\(S_2\)}. Its intended interpretation is that they act in the same way on all
+filesystems.
+\item \(S_1\eqext S_2\), or \emph{\(S_2\) extends \(S_1\)}; its intended
+interpretation is that they act in the same way on all
+filesystems that \(S_1\) does not break.
+\end{itemize}
+
+We have two inference rules for the two judgements,
+which make it possible to derive new statements from the axioms or other statements.
+These are:
+
+\emph{For any sequences \(S_1, S_2, S, S'\):}
+\begin{itemize}
+\item if \(S_1\equiv S_2\) then \(S;S_1;S'\equiv S;S_2;S'\)
+\item if \(S_1\eqext S_2\) then \(S;S_1;S'\eqext S;S_2;S'\)
+\item if \(S_1\equiv S_2\) then \(S_1\eqext S_2\).
+\end{itemize}
+
+Finally, we have a set of axioms or laws that describe the behaviour
+of each command pair. We exclude commands that either break the
+filesystem or leave it in the same state ($\cbb$) and for
+simplicity's sake we merged axioms where the outcome is predictable
+from the relationship between the paths in the commands.
+
+\begin{itemize}
+\item[i.] If the two paths in the pair are separate (not directly related), then
+the commands commute with an equivalence:
+\[ [\cxy(p,V_Y); \czw(\np,V_W)] \equiv [\czw(\np,V_W); \cxy(p,V_Y)] \]
+%
+\item[ii.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), then
+the pair will break every filesystem if $Z\ne Y$, that is, if the second
+command expects a type of value different from the one left by the first command.
+Otherwise, the pair will simplify to a single or no commands
+if both $X$ and $W$ are $\fsregcommandchar{\empt}$ or $\fsregcommandchar{D}$:
+\begin{gather*}
+% bf=fb Sp
+           [\cbf(p, F); \cfb(p)] \eqext \emptyseq \\
+% bd=db Sp
+           [\cbd(p, D); \cdb(p)] \eqext \emptyseq \\
+% db=bd Sp
+           [\cdb(p); \cbd(p, D)] \eqext [\cdd(p, D)] \\
+% df=fd Sp
+           [\cdf(p, F); \cfd(p, D)] \eqext [\cdd(p, D)]
+\end{gather*}
+In all other cases the commands are equivalent to a single command
+replacing the input of the first command with the output of the second:
+\[ [\cxy(p, V_Y); \cyz(p, V_Z)] \equiv [\cxz(p, V_Z)] \]
+%
+\item[iii.]
+Of the pairs in which the first command is applied to the parent of the path
+of the second command there are pairs to which no law applies.
+We call these ``construction'' pairs:
+\begin{gather*}
+% bd>bf
+           [\cbd(\pp, D); \cbf(p, F)] \\
+% bd>bd
+           [\cbd(\pp, D_1); \cbd(p, D_2)] \\
+% fd>bf
+           [\cfd(\pp, D); \cbf(p, F)] \\
+% fd>bd
+           [\cfd(\pp, D_1); \cbd(p, D_2)]
+\end{gather*}
+Otherwise commands in these pairs commute iff the first command is $\cdd$;
+all other pairs break every filesystem. For example:
+\begin{gather*}
+[\cdd(\pp, D); \cbf(p, F)] \equiv [\cbf(p, F); \cdd(\pp, D)] \\
+[\cdf(\pp, F); \cbd(p, D)] \equiv \cbrk
+\end{gather*}
+%
+\item[iv.]
+The final group of pairs are the ones in which the path in the second
+command is the parent of the one in the first.
+These behave similarly to the previous group. There are
+so-called ``destruction'' pairs to which no law applies:
+\begin{gather*}
+% fb<db ??
+           [\cfb(p); \cdb(\pp)] \\
+% fb<df ??
+           [\cfb(p); \cdf(\pp, F)] \\
+% db<db ??
+           [\cdb(p); \cdb(\pp)] \\
+% db<df ??
+           [\cdb(p); \cdf(\pp, F)]
+\end{gather*}
+Otherwise the commands commute iff the \emph{second} command is $\cdd$.
+All other pairs break every filesystem.
+\end{itemize}
+
+\section{Real-Life Variant}
+
+In real-life applications, we often do not want to consider metadata stored in
+directories (\cite{BZ}). In other words, the contents of directories are all equal,
+which can be modelled by assuming that $|\setd|=1$.
+Note that this creates a convenient symmetry where there are only a single value
+for each type, $D$ and $\empt$, that can be repeated as we move from a path to its child.
+
+This also means that $\cdd$, like $\cbb$, becomes a command that either breaks a filesystem
+or leaves it in the same state, and we will disregard it in our algebra.
+The axioms will simplify as follows:
+
+\begin{itemize}
+\item[i.] Pairs with separate paths are still reversible,
+but \emph{these are the only pairs that are so}.
+%
+\item[ii.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), then, as above,
+the pair will break every filesystem if $Z\ne Y$.
+Otherwise, the pair is extended by an empty sequence
+if both $X$ and $W$ are $\fsregcommandchar{\empt}$ or $\fsregcommandchar{D}$:
+\begin{gather*}
+% bf=fb Sp
+           [\cbf(p, F); \cfb(p)] \eqext \emptyseq \\
+% bd=db Sp
+           [\cbd(p, D); \cdb(p)] \eqext \emptyseq \\
+% db=bd Sp
+           [\cdb(p); \cbd(p, D)] \eqext \emptyseq \\
+% df=fd Sp
+           [\cdf(p, F); \cfd(p, D)] \eqext \emptyseq
+\end{gather*}
+And in all other cases, as above, the commands are equivalent to a single command
+replacing the input of the first command with the output of the second:
+\[ [\cxy(p, V_Y); \cyz(p, V_Z)] \equiv [\cxz(p, V_Z)] \]
+%
+\item[iii.]
+Of the pairs in which the first command is applied to the parent path,
+the same ``construction'' pairs still have no laws, but all other pairs
+break all filesystems.
+%
+\item[iv.]
+And we still have the ``destruction'' pairs among the pairs where the second command
+is applied to the parent path, and all other pairs break all filesystems.
+\end{itemize}
 
@@
 
+\bibitem{BZ} Bill Zissimopoulos, ...
+
 \end{thebibliography}

### 2015-11-07 2015/prove.py
TeX output updates

@@ -637,6 +637,8 @@ class CommandPair(Sequence):
     
     def info_label(self):
         """Returns the label and info."""
+        if STYLE == 'tex':
+            return "% " + self.label() + " " + self.predictAxiomGroup() + "\n           " + self.info()
         return self.label() + " " + self.predictAxiomGroup() + "  " + self.info()
         
     def clone(self):
@@ -706,16 +708,18 @@ RulesNoRule = []
 if STYLE == 'tex':
     Pequ = ' \\equiv '
     Pext = ' \\eqext '
-    Pbreak = '\\break'
+    Pbreak = '\\cbrk'
     Pnocomm = '[]'
     Pnorule = ''
+    Pjoin = ' \\\\\n';
 else:
     Pequ = ' == '
     Pext = ' =[ '
     Pbreak = 'break'
     Pnocomm = '(no commands)'
     Pnorule = ' (no rule)'
-    
+    Pjoin = '\n';
+
 
 # print "Default: XY xx ZW == ZW xx XY"
 # print "Default otherwise: XY ?? ZW == break"
@@ -822,11 +826,11 @@ for sq in CommandPairFactory():
     RulesNoRule.append(sq.info_label() + Pnorule)
 
 print "\nBreaking rules"
-print "\n".join(RulesBreaking)
+print Pjoin.join(RulesBreaking)
 print "\nSimplification rules"
-print "\n".join(RulesSimplified)
+print Pjoin.join(RulesSimplified)
 print "\nCommuting rules"
-print "\n".join(RulesCommute)
+print Pjoin.join(RulesCommute)
 print "\nNo rules"
-print "\n".join(RulesNoRule)
+print Pjoin.join(RulesNoRule)
 

### 2015-11-08 2015/paper.tex
Separated subgroups of axioms

@@
 \newcommand{\eqnrw}{\sqsupseteq}
+\newcommand{\nequiv}{\not\equiv}
 
@@
 
-\title{A Complete Algebra for File Synchronization}
+\title{A More Complete Algebra for File Synchronization}
 
@@
 
-% diagram
-% /> D ---> F ---> BOT <\
-% \--/               \--/
 \input{type-transition}
@@
 $\FS(p)$ will be $\empt$. However, from \cite{NREC:alg} we know that a useful set of axioms
-will need to distinguish between edits that result in directories ($edit(p,D)$) and
-ones that result in files ($edit(p,F)$). This creates a seemingly arbitrary asymmetry where
+will in some cases need to distinguish between edits that result in directories ($edit(p,D)$) and
+ones that result in files ($edit(p,F)$);
+and Bill Zissimopoulos suggested in \cite{BZ} that extending this distinction simplifies
+definitions based on our algebra, as it is then able to predict the behaviour of commands
+more precisely. 
+In other words, encoding this information in the commands is definitely useful,
+but it creates a seemingly arbitrary asymmetry where
 there is more information encoded into commands about their results than about the
@@
 and do so based on a set of axioms about pairs of neighbouring commands.
-We are interested to see what pairs of commands can be simplified or reversed
+We are interested to see which pairs of commands cause errors all the time,
+and which can be simplified or reversed
 in order to see under what circumstances commands conflict or can be reordered.
@@
 where $X,Y,Z,W\in\{\fsregcommandchar{D},\fsregcommandchar{F},\empt\}$, $p,q\in\setp$, and values are of the appropriate type: 
-$V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$
-(although commands where $Y=\empt$ or $W=\empt$ do not require a value).
+$V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$.
+(Strictly speaking, commands where $Y=\empt$ or $W=\empt$ do not require a value,
+but they can also be written in a $\fscommand{X}{\empt}(p, \empt)$ form.)
 
 Similarly to the case of commands, in \cite{NREC:alg} we found that in order to build
-a set of axioms in a sound and complete algebra we at times needed to take into account
+a set of axioms in a sound and complete algebra and use the algebra effectively we at times needed to take into account
 the relationship between the paths of the commands in the pair, $p$ and $q$.
@@
 
-\begin{itemize}
-\item $p=q$. If the two commands affect the same path, the pair of commands
+\begin{description}
+\item[Same.] Paths that are the same ($p=q$). If the two commands affect the same path, the pair of commands
 will clearly behave differently than if the paths are different.
 %
-\item Separate paths, that is, $\parent(p)\neq q$ and $\parent(q)\neq p$. If the paths
-are not directly related, then modifying the filesystem at one path is not going
+\item[Unrelated.] Paths that are not \emph{directly} related,
+that is, where $\parent(p)\neq q$ and $\parent(q)\neq p$. 
+In this case modifying the filesystem at one path is not going
 to affect the outcome of the command on the other path.
@@
 %
-\item Directly related paths, that is, $\parent(p)=q$ or $\parent(q)=p$.
+\item[Directly related.] Directly related paths, that is, $\parent(p)=q$ or $\parent(q)=p$.
 For simplicity, we will write $\pp$ for $\parent(p)$.
@@
 while $[\cbf(p,F);\cbd(\pp,D)]$ will break all filesystems.
-\end{itemize}
+\end{description}
 
@@
 
+% TODO Would it be worth encoding non-direct parent/child relationships?
+
 In summary, we have pairs of commands
 of the following forms:
-\begin{itemize}
-\item[i.] \( [\cxy(p,V_Y); \czw(\np,V_W)] \)
-\item[ii.] \( [\cxy(p,V_Y); \czw(p,V_W)] \)
-\item[iii.] \( [\cxy(\pp,V_Y); \czw(p,V_W)] \)
-\item[iv.] \( [\cxy(p,V_Y); \czw(\pp,V_W)] \)
-\end{itemize}
+\begin{description}
+\item[Unrelated.] \( [\cxy(p,V_Y); \czw(\np,V_W)] \)
+\item[Same.] \( [\cxy(p,V_Y); \czw(p,V_W)] \)
+\item[Down.] \( [\cxy(\pp,V_Y); \czw(p,V_W)] \)
+\item[Up.] \( [\cxy(p,V_Y); \czw(\pp,V_W)] \)
+\end{description}
 
@@
 
-\begin{itemize}
-\item[i.] If the two paths in the pair are separate (not directly related), then
-the commands commute with an equivalence:
-\[ [\cxy(p,V_Y); \czw(\np,V_W)] \equiv [\czw(\np,V_W); \cxy(p,V_Y)] \]
+\begin{description}
+\item[Unrelated.] If the two paths in the pair are not directly related, then
+the commands commute with an equivalence and they will not break every filesystem:
+\begin{align*}
+[\cxy(p,V_Y); \czw(\np,V_W)] &\equiv [\czw(\np,V_W); \cxy(p,V_Y)] \\
+&\nequiv \cbrk
+\end{align*}
 %
-\item[ii.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), then
-the pair will break every filesystem if $Z\ne Y$, that is, if the second
+\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), then:
+\begin{description}
+\item[Break.]
+The pair will break every filesystem if $Z\ne Y$, that is, if the second
 command expects a type of value different from the one left by the first command.
+\item[Simplified by extension.]
 Otherwise, the pair will simplify to a single or no commands
@@
 \end{gather*}
-In all other cases the commands are equivalent to a single command
+\item[Simplified by equivalence.]
+In all other cases, the commands are equivalent to a single command
 replacing the input of the first command with the output of the second:
 \[ [\cxy(p, V_Y); \cyz(p, V_Z)] \equiv [\cxz(p, V_Z)] \]
+\end{description}
 %
-\item[iii.]
-Of the pairs in which the first command is applied to the parent of the path
-of the second command there are pairs to which no law applies.
+\item[Down.]
+These are the pairs in which the first command is applied to the parent of the path
+of the second command.
+\begin{description}
+\item[Construction.] There are pairs in this group to which no law applies.
 We call these ``construction'' pairs:
@@
 \end{gather*}
-Otherwise commands in these pairs commute iff the first command is $\cdd$;
-all other pairs break every filesystem. For example:
+\item[Commute.] Otherwise, the commands in these pairs commute iff the first command is $\cdd$. For example:
 \begin{gather*}
-[\cdd(\pp, D); \cbf(p, F)] \equiv [\cbf(p, F); \cdd(\pp, D)] \\
+[\cdd(\pp, D); \cbf(p, F)] \equiv [\cbf(p, F); \cdd(\pp, D)]
+\end{gather*}
+\item[Break.] All other pairs break every filesystem, e.g.:
+\begin{gather*}
 [\cdf(\pp, F); \cbd(p, D)] \equiv \cbrk
 \end{gather*}
+\end{description}
 %
-\item[iv.]
+\item[Up.]
 The final group of pairs are the ones in which the path in the second
 command is the parent of the one in the first.
-These behave similarly to the previous group. There are
+These behave similarly to the previous group. 
+\begin{description}
+\item[Desctruction.] There are
 so-called ``destruction'' pairs to which no law applies:
@@
 \end{gather*}
-Otherwise the commands commute iff the \emph{second} command is $\cdd$.
-All other pairs break every filesystem.
-\end{itemize}
+\item[Commute.] Otherwise the commands commute iff the \emph{second} command is $\cdd$.
+\item[Break.] All other pairs break every filesystem.
+\end{description}
+\end{description}
 
@@
 
-\begin{itemize}
-\item[i.] Pairs with separate paths are still reversible,
-but \emph{these are the only pairs that are so}.
+\begin{description}
+\item[Unrelated.] Pairs with unrelated paths are still reversible and not equivalent to
+$\cbrk$, but these are the only pairs that are reversible.
 %
-\item[ii.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), then, as above,
-the pair will break every filesystem if $Z\ne Y$.
-Otherwise, the pair is extended by an empty sequence
+\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), then:
+\begin{description}
+\item[Break.] As above, the pair will break every filesystem if $Z\ne Y$.
+\item[Simplified by extension.] Otherwise, the pair is extended by an empty sequence
 if both $X$ and $W$ are $\fsregcommandchar{\empt}$ or $\fsregcommandchar{D}$:
@@
 \end{gather*}
+\item[Simplified by equivalence.]
 And in all other cases, as above, the commands are equivalent to a single command
@@
 \[ [\cxy(p, V_Y); \cyz(p, V_Z)] \equiv [\cxz(p, V_Z)] \]
+\end{description}
 %
-\item[iii.]
-Of the pairs in which the first command is applied to the parent path,
-the same ``construction'' pairs still have no laws, but all other pairs
-break all filesystems.
+\item[Down.]
+Of the pairs in which the first command is applied to the parent path:
+\begin{description}
+\item[Construction.] the same ``construction'' pairs still have no laws, 
+\item[Break.] but all other pairs break all filesystems.
+\end{description}
 %
 \item[iv.]
-And we still have the ``destruction'' pairs among the pairs where the second command
-is applied to the parent path, and all other pairs break all filesystems.
-\end{itemize}
+And of the pairs where the second command
+is applied to the parent path,
+\begin{description}
+\item[Destruction.] we still have the ``destruction'' pairs,
+\item[Break.] and all other pairs break all filesystems.
+\end{description}
+\end{description}
 
@@
 
-\bibitem{BZ} Bill Zissimopoulos, ...
+\bibitem{BZ} Bill Zissimopoulos, personal communication, ...
 

### 2015-11-08 2015/paper.tex
Same-pairs do not commute

@@
 %
-\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), then:
+\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), the
+the commands cannot be reversed. Instead:
    \begin{description}
@@
 Note that this creates a convenient symmetry where there are only a single value
-for each type, $D$ and $\empt$, that can be repeated as we move from a path to its child.
+for each type that can be repeated as we move from a path to its child ($D$ and $\empt$).
 
@@
 %
-\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), then:
+\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), then,
+as above, the commands do not commute.
    \begin{description}
-\item[Break.] As above, the pair will break every filesystem if $Z\ne Y$.
+   \item[Break.] Also, as above, the pair will break every filesystem if $Z\ne Y$.
    \item[Simplified by extension.] Otherwise, the pair is extended by an empty sequence
@@
 %
-\item[iv.]
+\item[Up.]
 And of the pairs where the second command

### 2015-11-09 2015/paper.tex
Described order sets; first part of proof for intersection of sequences

@@
 \newcommand{\czw}{\fscommand{Z}{W}}
+\newcommand{\cqr}{\fscommand{Q}{R}}
 
@@
 \newcommand{\emptyseq}{[\,]}
+
+\newcommand{\extset}[1]{\wp{#1}}
+\newcommand{\orderset}[1]{\vec{\wp}{#1}}
 
@@
 
+{\bf Going forward we use the algebra derived from the $|\setd|=1$ case.}
+
+\section{Ordering commands}
+
+We often encounter the case where we only have a set of commands without a sepcified order.
+Indeed, it is actually the task of the reconciler to determine whether there is an order
+in which updates from multiple replicas can all be applied to a filesystem.
+
+By a {\bf minimal sequence or set} of commands we mean a sequence / set in which
+there is at most one command on each path.
+
+If $U$ is a minimal set of commands
+that we know can be applied to at least one filesystem in some order without breaking it,
+then we can split $U$ into a maximum number of disjunct subsets
+(components) so that the paths of two commands from different subsets would never be directly related.
+If we aim to order the commands in $U$, then we can focus on order the commands
+inside the components, as all permutations of the components are allowed:
+the commands in them will commute.
+
+Components containing a single command do not pose a problem when determining
+possible orders.
+(Note that $\cff$ can only appear in a component of one.)
+
+In each component that is larger than one, the patch are directly related
+and the commands form construction or destruction chains.
+To order the commands,
+select the command with the topmost path, so that there would be no command
+on its parent path. If the command removes content at this path, the command
+needs to follow all other commands in the component, and
+the component is a destruction component.
+Otherwise the command with the topmost component needs to precede other commands
+in the component, and it is a construction component.
+Repeat the above process of splitting commands into subsets on the remaining commands
+in the component. Recursively, this way we can determine all allowed orders of the commands.
+
+We use $\orderset{U}$ to denote the set of sequences that contain all commands in $U$
+and represent all allowed orders. As a specific case, we can regard a sequence of commands $S$
+as a set and determine its $\orderset{S}$.
+At times by $\orderset{U}$ we mean an arbitrary sequence in the set.
+
+% (O-D)
+{\bf Lemma.} If $U$ contains commands on both $p$ and $\pp$, then
+there is a $U^*\in\orderset{U}$ where they are next to each other.
+
+{\bf Lemma.} For any minimal sequence $S$ not equivalent to $\cbrk$,
+$\orderset{S} = \extset{S}$.
+
+\section{Soundness}
+
+\section{Completeness}
+
+{\bf Lemma.} \((\forall\FS: S\FS = \empt) \Rightarrow S \equiv \cbrk\)
+
+\section{Update detection}
+
+\section{Reconciliation}
+
+If $A$ and $B$ are minimal sequences and there is at least one filesystem neither of them breaks,
+we write $A\circ B$. In this case based on the soundness of the algebra
+we also know that $A\nequiv\cbrk$ and $B\nequiv\cbrk$.
+Also, if there are commands on path $p$ in both $A$ ($\cxy(p, V_Y)$) and $B$ ($\czw(p, V_W)$)
+then their input types must match ($X=Z$).
+
+{\bf Lemma.} Let $A$ and $B$ be two minimal sequences so that $A\circ B$.
+Then their intersection can also be applied to any filesystem
+either can be applied to without breaking it.
+
+Proof.
+First we prove the following.
+Mark all commands in $A$ that also appear in $B$.
+Then $\exists A^* \in \orderset{A}$ in which the marked commands are at the beginning.
+
+We show $A$ can be transformed via equivalences so that this would be true
+by induction on the number of non-marked commands preceding the last marked command.
+If it is 0, no transformation is needed.
+For the induction step, select the last marked command preceded by a non-marked command.
+If the two commute, reverse them, thereby reducing the number on relevant non-marked commands.
+If they do not commute, they must be a construction or destruction pair as we know
+that $A$ is minimal and $A\nequiv\cbrk$.
+
+Let the marked command be $\cxy(p, V_Y)$ and the preceding unmarked command in $A$ be $\czw(q, V_W)$.
+We have two cases and we will proceed by indirection.
+
+If $B$ has a command on $q$, let it be $\cqr(q, V_R)$. As $A\circ B$, we know
+that $Q=Z$. From 
+O-D (TODO ref)
+we also know that there is a $B^*\equiv B$ where $\cxy$ and $\cqr$ are next to each other,
+and from the construction and destruction laws we know that $\cxy$ determines that like
+$\czw(q, V_W)$ in $A$, any command on $q$ must precede it in $B$. As $B$ is minimal, $B^*$
+contains the same commands, and so it is the $\cqr$ command that precedes $\cxy$ in $B^*$.
+Going back to the construction and destruction laws we see that the output type of the first command
+is always the same, and it is either $D$ or $\empt$. Therefore $R=W$ and $\cqr(q, V_R)=\czw(q, V_W)$
+as $|\setd|=|\setb|=1$. This is a contradiction as $\czw$ was not marked, but we see it must also be in $B$.
+
+If $B$ has no command on $q$,
+
 \begin{thebibliography}{99}

### 2015-11-09 2015/paper.tex
Fixed typos

@@
 
-We often encounter the case where we only have a set of commands without a sepcified order.
+We often encounter the case where we only have a set of commands without a specified order.
 Indeed, it is actually the task of the reconciler to determine whether there is an order
-in which updates from multiple replicas can all be applied to a filesystem.
+in which updates from multiple replicas can be applied to a filesystem.
 
@@
 (components) so that the paths of two commands from different subsets would never be directly related.
-If we aim to order the commands in $U$, then we can focus on order the commands
+If we aim to order the commands in $U$, then we can focus on ordering the commands
 inside the components, as all permutations of the components are allowed:
@@
 
-In each component that is larger than one, the patch are directly related
+In each component that is larger than one, the paths are directly related
 and the commands form construction or destruction chains.

### 2015-11-10 2015/paper.tex
Introduced existential extensions to the algebra; finished proof

@@
 \usepackage{amssymb}
+\usepackage{amsthm}
 \usepackage{setspace}
@@
 \newcommand{\cqr}{\fscommand{Q}{R}}
+\newcommand{\cqq}{\fscommand{Q}{Q}}
 
@@
 \newcommand{\nequiv}{\not\equiv}
+\newcommand{\wrext}{\stackrel{\mathtt{br}}{\sqsubseteq}}
+\newcommand{\wrnrw}{\stackrel{\mathtt{br}}{\sqsupseteq}}
+\newcommand{\coworks}{\circ}
+\newcommand{\ncoworks}{\centernot\circ}
 
@@
 \newcommand{\orderset}[1]{\vec{\wp}{#1}}
+
+\theoremstyle{definition}
+\newtheorem{mydef}{Definition}
+
+\newtheorem{mylem}{Lemma}
 
@@
 for sequences \(S_1\) and \(S_2\):
-\begin{itemize}
-\item \(S_1\equiv S_2\), or \emph{\(S_1\) is algebraically equivalent to
+\begin{mydef}
+\(S_1\equiv S_2\), or \emph{\(S_1\) is algebraically equivalent to
 \(S_2\)}. Its intended interpretation is that they act in the same way on all
-filesystems.
-\item \(S_1\eqext S_2\), or \emph{\(S_2\) extends \(S_1\)}; its intended
+filesystems. It is a commutative and transitive relation.
+\end{mydef}
+\begin{mydef}
+\(S_1\eqext S_2\), or \emph{\(S_2\) extends \(S_1\)}; its intended
 interpretation is that they act in the same way on all
-filesystems that \(S_1\) does not break.
-\end{itemize}
+filesystems that \(S_1\) does not break. It is a transitive relation.
+\end{mydef}
 
@@
 
-By a {\bf minimal sequence or set} of commands we mean a sequence / set in which
+\begin{mydef}{Minimal set / sequence}
+By a minimal sequence or set of commands we mean a sequence / set in which
 there is at most one command on each path.
+\end{mydef}
 
@@
 select the command with the topmost path, so that there would be no command
-on its parent path. If the command removes content at this path, the command
+on its parent path. If the command removes content at this path, then it
 needs to follow all other commands in the component, and
@@
 in the component, and it is a construction component.
-Repeat the above process of splitting commands into subsets on the remaining commands
+Repeat the process of splitting commands into subsets on the remaining commands
 in the component. Recursively, this way we can determine all allowed orders of the commands.
 
+\begin{mydef}{$\orderset{U}$}
 We use $\orderset{U}$ to denote the set of sequences that contain all commands in $U$
-and represent all allowed orders. As a specific case, we can regard a sequence of commands $S$
+and represent all allowed orders.
+\end{mydef}
+
+As a specific case, we can regard a sequence of commands $S$
 as a set and determine its $\orderset{S}$.
@@
 
-% (O-D)
-{\bf Lemma.} If $U$ contains commands on both $p$ and $\pp$, then
+\begin{mylem}\label{lemma:neighbour}
+If $U$ contains commands on both $p$ and $\pp$, then
 there is a $U^*\in\orderset{U}$ where they are next to each other.
+\end{mylem}
 
-{\bf Lemma.} For any minimal sequence $S$ not equivalent to $\cbrk$,
+\begin{mydef}
+$\extset{S} := \{S^*|S\eqext S^*\}$
+\end{mydef}
+
+\begin{mylem}\label{lemma:minextset}
+For any minimal sequence $S$ not equivalent to $\cbrk$, $\extset{S} = \{S^*|S\equiv S^*\}$.
+\end{mylem}
+\begin{proof}
+This is because as $S$ has at most one command on each path, only equivalence axioms
+can be applied to it.
+\end{proof}
+
+\begin{mylem}\label{lemma:minextorder}
+For any minimal sequence $S$ not equivalent to $\cbrk$,
 $\orderset{S} = \extset{S}$.
+\end{mylem}
 
@@
 
-{\bf Lemma.} \((\forall\FS: S\FS = \empt) \Rightarrow S \equiv \cbrk\)
+\begin{mylem}
+\((\forall\FS: S\FS = \empt) \Rightarrow S \equiv \cbrk\)
+\end{mylem}
 
@@
 
+\section{Extending the algebra}
+
+We have seen that commands can break a filesystem
+either because their input type does not match the filesystem at the given path,
+or because the filesystem loses its tree property.
+
+\begin{mydef}{Fully typed sequences}
+We call a sequence of commands fully typed if whenever it breaks a filesystem
+it is explained by a mismatch on the input types of the commands it contains.
+TODO: define fully typed sequences in terms of the algebra?
+\end{mydef}
+
+To aid the construction of fully typed sequences, we reintroduce
+two assertion commands that either break the filesystem
+or leave it unchanged: $\cbb(p)$ and $\cdd(p)$.
+As $|\setb|=|\setd|=1$, we do not note the exact output value.
+These can be used to test whether $\FS(p)=\empt$ or $\FS(p)=D$.
+
+Furthermore, we note the following axioms:
+
+\begin{itemize}
+\item Laws for construction typing:
+   \begin{gather*}
+            [\cbf(p, F)] \equiv [\cdd(\pp); \cbf(p, F)]\\
+            [\cbd(p, D)] \equiv [\cdd(\pp); \cbd(p, D)]
+   \end{gather*}
+\item Laws for destruction typing:
+   \begin{gather*}
+            [\cdb(\pp)] \equiv [\cbb(p); \cdb(\pp)]\\
+            [\cdf(\pp, F)] \equiv [\cbb(p); \cdf(\pp, F)]
+   \end{gather*}
+\end{itemize}
+
+Separately, we extend the algebra with the following judgements and axioms:
+
+\begin{mydef}{$A\coworks B$}
+or the domains of $A$ and $B$ overlap.
+Its intended interpretation is that
+there is at least one filesystem neither $A$ nor $B$ breaks.
+It is a commutative (but not transitive) relation.
+For $A\ncoworks B$ we say that $A$ and $B$ are disjoint.
+\end{mydef}
+
+\begin{mydef}{$A\wrext B$}
+or the domain of $B$ extends that of $A$.
+Its intended interpretation is that
+$B$ does not break any filesystem $A$ does not break.
+It is a transitive relation.
+\end{mydef}
+
+\begin{itemize}
+\item $A\coworks B \Rightarrow A\nequiv\cbrk$
+\item $A\eqext B \Rightarrow A\wrext B$
+\item $A\coworks B\wrext C \Rightarrow A\coworks C$
+\item $A\ncoworks B\wrnrw C \Rightarrow A\ncoworks C$
+\item $A\ncoworks B \Rightarrow A;S\ncoworks B$
+\end{itemize}
+
+Axioms:
+
+\begin{itemize}
+\item $\cxy(p,V_Y)\ncoworks \czw(p,V_W)$ where $X\neq Z$
+% \item Disjoint laws for construction:
+%    \begin{gather*}
+%    % bd>bf
+%             [\cbd(\pp, D); \cbf(p, F)] \ncoworks [\cbf(p, F)]\\
+%    % bd>bd
+%             [\cbd(\pp, D_1); \cbd(p, D_2)] \ncoworks [\cbd(p, D_2)]\\
+%    % fd>bf
+%             [\cfd(\pp, D); \cbf(p, F)] \ncoworks [\cbf(p, F)]\\
+%    % fd>bd
+%             [\cfd(\pp, D_1); \cbd(p, D_2)] \ncoworks [\cbd(p, D_2)]
+%    \end{gather*}
+% \item Disjoint laws for destruction:
+%    \begin{gather*}
+%    % fb<db ??
+%             [\cfb(p); \cdb(\pp)] \ncoworks [\cdb(\pp)]\\
+%    % fb<df ??
+%             [\cfb(p); \cdf(\pp, F)] \ncoworks [\cdf(\pp, F)]\\
+%    % db<db ??
+%             [\cdb(p); \cdb(\pp)] \ncoworks [\cdb(\pp)]\\
+%    % db<df ??
+%             [\cdb(p); \cdf(\pp, F)] \ncoworks [\cdf(\pp, F)]
+%    \end{gather*}
+\end{itemize}
+
+\begin{mylem}
+If $A$ and $B$ are minimal sequences, $A\coworks B$,
+and there are commands on path $p$ in both $A$ ($\cxy(p, V_Y)$) and $B$ ($\czw(p, V_W)$)
+then their input types must match ($X=Z$).
+TODO: Can this be derived from the algebra?
+\end{mylem}
+
+\begin{mylem}
+If $A$ is fully typed and $S;A$ is minimal, then $S;A\wrext A$
+TODO: Is this an axiom?
+\end{mylem}
+
+\begin{mylem}\label{lemma:ncowprefix}
+$A\ncoworks B \Rightarrow S;A\ncoworks B$ if $A$ is fully typed and $S;A$ is minimal.
+\end{mylem}
+\begin{proof}
+This follows from above.
+\end{proof}
+
 \section{Reconciliation}
 
-If $A$ and $B$ are minimal sequences and there is at least one filesystem neither of them breaks,
-we write $A\circ B$. In this case based on the soundness of the algebra
-we also know that $A\nequiv\cbrk$ and $B\nequiv\cbrk$.
-Also, if there are commands on path $p$ in both $A$ ($\cxy(p, V_Y)$) and $B$ ($\czw(p, V_W)$)
-then their input types must match ($X=Z$).
-
-{\bf Lemma.} Let $A$ and $B$ be two minimal sequences so that $A\circ B$.
+\begin{mylem}
+Let $A$ and $B$ be two minimal sequences so that $A\coworks B$.
 Then their intersection can also be applied to any filesystem
 either can be applied to without breaking it.
+\end{mylem}
 
-Proof.
+\begin{proof}
 First we prove the following.
@@
 Then $\exists A^* \in \orderset{A}$ in which the marked commands are at the beginning.
+
+\medskip
 
@@
 
-If $B$ has a command on $q$, let it be $\cqr(q, V_R)$. As $A\circ B$, we know
-that $Q=Z$. From 
-O-D (TODO ref)
+If $B$ has a command on $q$, let it be $\cqr(q, V_R)$. As $A\coworks B$, we know
+that $Q=Z$. From lemmas \ref{lemma:neighbour}, \ref{lemma:minextset} and \ref{lemma:minextorder}
 we also know that there is a $B^*\equiv B$ where $\cxy$ and $\cqr$ are next to each other,
@@
 
-If $B$ has no command on $q$,
+If $B$ has no command on $q$, $A$ and $B$ cannot work on the same filesystem,
+as the second commands in all construction and destruction laws require a different type of input
+as the first commands. This is a contradiction as we supposed $A\coworks B$.
+
+In terms of the algebra, this latter argument could be rephrased as follows.
+Split $A$ into $[A_0;\czw(q, V_W);\cxy(p, V_Y);A_1]$.
+Add command $\cqq(q)$ before $\cxy(p, V_Y)$ to $B$ according to the construction or destruction typing laws.
+This yields $B^*\equiv B$, which we split into $[B_0;\cqq(q);\cxy(p, V_Y);B_1]$.
+We know $[\czw(q, V_W);\cxy(p, V_Y)]$ is fully typed (TODO: why?)
+and $A$ is minimal, so $[A_0;\czw(q, V_W);\cxy(p, V_Y)]$ is minimal.
+We also know $[\cqq(q);\cxy(p, V_Y)]$ is fully typed and $B^*$ is minimal, so $[B_0;\cqq(q);\cxy(p, V_Y)]$ is minimal.
+But we know $[\czw(q, V_W);\cxy(p, V_Y)]\ncoworks [\cqq(q);\cxy(p, V_Y)]$
+as comparing the construction and destruction laws to their typing counterparts we know that $Z\neq Q$,
+and so from lemma \ref{lemma:ncowprefix} and $A\ncoworks B \Rightarrow A;S\ncoworks B$
+we know that $A\ncoworks B^*\equiv B$ and so $A\ncoworks B$ which is a contradiction.
+(TODO: Is there a point in proving this this way?)
+
+\medskip
+
+\end{proof}
 

### 2015-11-11 2015/paper.tex
Finished proof; added definitions for commands and documented derivations

@@
 \usepackage{setspace}
-\usepackage{fullpage}
+% \usepackage{fullpage}
 \usepackage{graphicx}
-\usepackage{afterpage}
+% \usepackage{afterpage}
+
 \usepackage{centernot}
-
 \usepackage{tikz}
@@
 \newcommand{\parent}{\mathtt{parent}}
+\newcommand{\toppath}{\mathtt{None}}
+\newcommand{\fsbroken}{\mathtt{Broken}}
 \newcommand{\FS}{\Phi} % {\mathrm{FS}}
@@
 \newtheorem{mydef}{Definition}
-
+\newtheorem{myax}{Axiom}
 \newtheorem{mylem}{Lemma}
@@
 
+The paths of a filesystem form a disjoint union of rooted directed trees.
+\begin{mydef}
+The function $\parent(p)$ returns the parent path of $p$, or
+returns $\toppath$ if $p$ is the root of a tree.
+We also write $\pp$ for $\parent(p)$.
+\end{mydef}
+
 Every filesystem has a so-called \textbf{tree property}, which means that
-if the filesystem is not empty at a path, and it is not a root path,
-then it must have a directory at the path's parent.
-This requires that a parent--child relationship is defined over $\setp$,
-which we model using the function $\parent$, which returns the parent path
-or $\empt$ if the path is a root path:
-\[ \parent : \setp \rightarrow \setp \cup \{\empt\} \]
+if the filesystem is not empty at a path, and the path has a parent,
+then there must be a directory at the parent path.
 
-Moreover, in $\setv$ we distinguish between files ($\setf$) and directories ($\setd$), that is,
+To model this, in $\setv$ we distinguish between files ($\setf$) and directories ($\setd$), that is,
 if $\setb = \{\empt\}$ then:
@@
 The tree propety can then be defined as
-\[ \forall \FS, p\in\setp : \FS(p) \neq \empt \wedge \parent(p) \neq \empt \Rightarrow \FS(\parent(p)) \in \setd \]
+\[ \forall \FS, p\in\setp : \FS(p) \neq \empt \wedge \parent(p) \neq \toppath \Rightarrow \FS(\parent(p)) \in \setd \]
 
@@
 
-In other words, the types will form a sequence like $D,D,\cdots,D,F,\empt,\empt,\cdots$.
-
 In this paper, we write $F$ for an arbitrary element of $\setf$, and $D$ for an arbitrary element
@@
 
-\section{Commands}
+\section{Introducing commands}
 
@@
 Clearly the commands need to contain information about the state they leave the filesystem
-in at the path on which they operate, that is, they need to contain the ``end'' value, $V$.
+in at the path on which they operate, that is, they need to contain their output value, $V$.
 Notice, however, that the commands above also encode some information about the filesystem
-{\it before} the command is applied; namely, $create$ requires that there are no files
+\emph{before} the command is applied; namely, $create$ requires that there are no files
 or directories at $p$, while $edit$ and $remove$ require the opposite.
@@
 
-In line with the aim to encode in commands as much information as possible,
+In line with the aim to encode as much information as possible in the commands,
 and in order to resolve this asymmetry, we propose a set of commands that encode
 the type of the original state of $\FS(p)$ as well.
-(Some real-life filesystem commands like $mkdir$ or $rmdir$ do this already.)
+(Some real-life filesystem commands like $rmdir$ do this already.)
 Please note that there is never any need to encode information about the
-{\it exact} value of path $p$ in a command, merely its type ($D$, $F$ or $\empt$),
-as the success or failure of subsequent commands only depend on the type of the value.
+\emph{exact} value of path $p$ in a command, merely its type ($D$, $F$ or $\empt$),
+as the success or failure of filesystem commands only depend on the type of the value.
 
 We therefore propose to have a command for each pair of types.
-For want of a better system, we will simply name our commands by concatenating
+For want of a better system, we will name our commands by concatenating
 two of $\fsregcommandchar{D}$, $\fsregcommandchar{F}$ and $\fsregcommandchar{\empt}$, 
@@
 afterwards. For example $mkdir(p,D)$ is $\cbd(p,D)$ and $rmdir(p)$ is $\cdb(p)$.
+Please find their exact definitions below.
 
@@
 \textbf{breaks} the filesystem. Broken filesystems are considered equal
-(but not equal to any working filesystem), and we note them by $\FS=\empt$.
+(but not equal to any working filesystem), and we note them by $\FS=\fsbroken$.
 
@@
 in the algebra, we introduce the command $\cbrk$ that simply breaks every filesystem.
-We note that a sequence of commands $S$ is applied to a filesystem
-by prefixing the sequence to it:
+
+We note that a command or a sequence of commands is applied to a filsystem
+by prefixing the command or sequence to it, for example: $\cbrk\FS$, $\cbd(p,D)\FS$, 
+or $S\FS$ if $S$ is a sequence of commands.
+
+The exact behaviour of our commands is as follows:
 \begin{itemize}
-\item $S\FS$
-\item $[\cbrk]\FS=\empt$
-\item $[\cff(p,F)]\FS = \GS$, for which $\GS(p)=F$ holds
-and $\GS(q)=\FS(q)$ for any path $q\neq p$.
+\item $\cbrk\FS = \fsbroken$
+\item
+All commands have the generic form $\cxy(p,V_Y)$ where
+$X$ and $Y$ are types ($\fsregcommandchar{D}$, $\fsregcommandchar{F}$ or $\fsregcommandchar{\empt}$),
+$p\in\setp$ and $V_Y$ is a value of the appropriate type from $\setvx{Y}$.
+At times we omit $V_Y$ if there is only one suitable value.
+
+Let us introduce the following notation for a filesystem derived from $\FS$:
+\[ \FS\{p\mapsto V\}(q) :=
+   \begin{cases}
+   V &\mbox{if~} q=p\\
+   \FS(q) &\mbox{otherwise.}
+   \end{cases}
+\]
+
+Then
+\[ \cxy(p,V_Y)\FS = 
+   \begin{cases}
+   \fsbroken &\mbox{if~} \FS=\fsbroken\\
+   \fsbroken &\mbox{if~} \FS(p)\not\in\setvx{X}\\
+   \fsbroken &\mbox{if~} \FS\{p\mapsto V_Y\} \mbox{~violates the tree property}\\
+   \FS\{p\mapsto V_Y\} &\mbox{otherwise.}
+   \end{cases}
+\]
 \end{itemize}
@@
 \[ [\cxy(p,V_Y); \czw(q,V_W)] \]
-where $X,Y,Z,W\in\{\fsregcommandchar{D},\fsregcommandchar{F},\empt\}$, $p,q\in\setp$, and values are of the appropriate type: 
+where $X,Y,Z,W\in\{\fsregcommandchar{D},\fsregcommandchar{F},\empt\}$, $p,q\in\setp$, 
+and values are of the appropriate type: 
 $V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$.
-(Strictly speaking, commands where $Y=\empt$ or $W=\empt$ do not require a value,
-but they can also be written in a $\fscommand{X}{\empt}(p, \empt)$ form.)
 
@@
 
-We have two inference rules for the two judgements,
+We have inference rules for the two judgements,
 which make it possible to derive new statements from the axioms or other statements.
@@
 \begin{itemize}
-\item if \(S_1\equiv S_2\) then \(S;S_1;S'\equiv S;S_2;S'\)
-\item if \(S_1\eqext S_2\) then \(S;S_1;S'\eqext S;S_2;S'\)
-\item if \(S_1\equiv S_2\) then \(S_1\eqext S_2\).
+\item \(S_1\equiv S_2 \Rightarrow S;S_1;S'\equiv S;S_2;S'\)
+\item \(S_1\eqext S_2 \Rightarrow S;S_1;S'\eqext S;S_2;S'\)
+\item \(S_1\equiv S_2 \Rightarrow S_1\eqext S_2\).
 \end{itemize}
@@
 filesystem or leave it in the same state ($\cbb$) and for
-simplicity's sake we merged axioms where the outcome is predictable
-from the relationship between the paths in the commands.
+simplicity's sake instead of listing axioms for all pairs of commands
+we describe the behaviour of groups of pairs
+based on the relationship between the paths in the commands.
 
@@
    \begin{description}
-   \item[Construction.] There are pairs in this group to which no law applies.
+   \item[Construction.] There are pairs in this group to which no law applies:
+   the commands do not commute or break every filesystem, and cannot be simplified.
    We call these ``construction'' pairs:
@@
 which can be modelled by assuming that $|\setd|=1$.
-Note that this creates a convenient symmetry where there are only a single value
+Note that this creates a convenient symmetry where there is only a single value
 for each type that can be repeated as we move from a path to its child ($D$ and $\empt$).
@@
 
+% TODO
 {\bf Going forward we use the algebra derived from the $|\setd|=1$ case.}
@@
 \begin{mydef}{Minimal set / sequence}
-By a minimal sequence or set of commands we mean a sequence / set in which
-there is at most one command on each path.
+By a minimal set or sequence of commands we mean a set / sequence in which
+there is at most one command on every path.
 \end{mydef}
@@
 then we can split $U$ into a maximum number of disjunct subsets
-(components) so that the paths of two commands from different subsets would never be directly related.
-If we aim to order the commands in $U$, then we can focus on ordering the commands
-inside the components, as all permutations of the components are allowed:
-the commands in them will commute.
+(components) so that the paths of two commands from two different subsets are never directly related.
+If we aim to order the commands in $U$, then we can allow any permutation of 
+the components as the commands in them will commute freely.
 
@@
 
-In each component that is larger than one, the paths are directly related
-and the commands form construction or destruction chains.
-To order the commands,
+In each component that is larger than one, the paths 
+form a rooted ordered tree via the parent--child relationships,
+and the pairs connected by edges will be like pairs in the
+construction or destruction laws.
+To order the commands in a component,
 select the command with the topmost path, so that there would be no command
-on its parent path. If the command removes content at this path, then it
+on its parent path (if there is one). 
+If the command removes content at this path (it is of the form $\fsregcommand{X}{\empt}$), then it
 needs to follow all other commands in the component, and
-the component is a destruction component.
+the component is made of destruction pairs.
 Otherwise the command with the topmost component needs to precede other commands
-in the component, and it is a construction component.
-Repeat the process of splitting commands into subsets on the remaining commands
+in the component, and it is made of construction pairs.
+Move the command with the topmost path in place, and
+repeat the process of splitting commands into subsets on the remaining commands
 in the component. Recursively, this way we can determine all allowed orders of the commands.
@@
 We use $\orderset{U}$ to denote the set of sequences that contain all commands in $U$
-and represent all allowed orders.
+and represent all orders generated by this algorithm.
+At times by $\orderset{U}$ we mean an arbitrary sequence in the set.
 \end{mydef}
@@
 as a set and determine its $\orderset{S}$.
-At times by $\orderset{U}$ we mean an arbitrary sequence in the set.
 
@@
 If $U$ contains commands on both $p$ and $\pp$, then
-there is a $U^*\in\orderset{U}$ where they are next to each other.
+there is a $U'\in\orderset{U}$ where they are next to each other.
 \end{mylem}
@@
 \begin{mydef}
-$\extset{S} := \{S^*|S\eqext S^*\}$
+$\extset{S} := \{S'|S\eqext S'\}$
 \end{mydef}
@@
 \begin{mylem}\label{lemma:minextset}
-For any minimal sequence $S$ not equivalent to $\cbrk$, $\extset{S} = \{S^*|S\equiv S^*\}$.
+For any minimal sequence $S$ not equivalent to $\cbrk$, $\extset{S} = \{S'|S\equiv S'\}$.
 \end{mylem}
@@
 \end{mylem}
+
+% TODO Can these be derived from the algebra?
 
@@
 it is explained by a mismatch on the input types of the commands it contains.
+% TODO
 TODO: define fully typed sequences in terms of the algebra?
@@
 or leave it unchanged: $\cbb(p)$ and $\cdd(p)$.
-As $|\setb|=|\setd|=1$, we do not note the exact output value.
-These can be used to test whether $\FS(p)=\empt$ or $\FS(p)=D$.
+(As $|\setb|=|\setd|=1$, we do not note their exact output value.)
+They can be used to test whether $\FS(p)=\empt$ or $\FS(p)=D$.
 
@@
 
-\begin{itemize}
-\item $A\coworks B \Rightarrow A\nequiv\cbrk$
-\item $A\eqext B \Rightarrow A\wrext B$
-\item $A\coworks B\wrext C \Rightarrow A\coworks C$
-\item $A\ncoworks B\wrnrw C \Rightarrow A\ncoworks C$
-\item $A\ncoworks B \Rightarrow A;S\ncoworks B$
-\end{itemize}
+\begin{myax}$A\coworks B \Rightarrow A\nequiv\cbrk$\end{myax}
+\begin{myax}$A\eqext B \Rightarrow A\wrext B$\end{myax}
+\begin{myax}\label{axiom:wrextpostfix}$[A;S] \wrext A$\end{myax}
+\begin{myax}$A\coworks B\wrext C \Rightarrow A\coworks C$\end{myax}
+\begin{myax}\label{axiom:ncowwrnrw}$A\ncoworks B\wrnrw C \Rightarrow A\ncoworks C$\end{myax}
 
-Axioms:
+\begin{mylem}\label{lemma:ncowpostfix}$A\ncoworks B \Rightarrow [A;S]\ncoworks B$\end{mylem}
+\begin{proof}From axioms \ref{axiom:wrextpostfix} and \ref{axiom:ncowwrnrw}\end{proof}
 
-\begin{itemize}
-\item $\cxy(p,V_Y)\ncoworks \czw(p,V_W)$ where $X\neq Z$
+\begin{myax}$\cxy(p,V_Y)\ncoworks \czw(p,V_W)$ if $X\neq Z$\end{myax}
 % \item Disjoint laws for construction:
@@
 %    \end{gather*}
-\end{itemize}
 
@@
 
-\begin{mylem}
-If $A$ is fully typed and $S;A$ is minimal, then $S;A\wrext A$
+\begin{mylem}\label{lemma:wrextprefix}
+$[S;A]\wrext A$
+if $A$ is fully typed and $[S;A]$ is minimal.
 TODO: Is this an axiom?
@@
 \begin{mylem}\label{lemma:ncowprefix}
-$A\ncoworks B \Rightarrow S;A\ncoworks B$ if $A$ is fully typed and $S;A$ is minimal.
+$A\ncoworks B \Rightarrow [S;A]\ncoworks B$ 
+if $A$ is fully typed and $[S;A]$ is minimal.
 \end{mylem}
 \begin{proof}
-This follows from above.
+This follows from lemma \ref{lemma:wrextprefix} and axiom \ref{axiom:ncowwrnrw}.
 \end{proof}
@@
 Let $A$ and $B$ be two minimal sequences so that $A\coworks B$.
-Then their intersection can also be applied to any filesystem
+Then their intersection ($\orderset(A\cap B)$) can also be applied to any filesystem
 either can be applied to without breaking it.
@@
 as comparing the construction and destruction laws to their typing counterparts we know that $Z\neq Q$,
-and so from lemma \ref{lemma:ncowprefix} and $A\ncoworks B \Rightarrow A;S\ncoworks B$
+and so from lemma \ref{lemma:ncowprefix} and lemma \ref{lemma:ncowpostfix}
 we know that $A\ncoworks B^*\equiv B$ and so $A\ncoworks B$ which is a contradiction.
@@
 
+We now know that $A$ can be rearranged in a way that commands in $A\cap B$
+are at the beginning, and therefore $A\wrext \orderset(A\cap B)$ and by symmetry $B\wrext \orderset(A\cap B)$.
 \end{proof}

### 2015-11-12 2015/paper.tex
Description of reconciliation; proof without "fully typed" sequences

@@
 
+% TODO Use cleveref to add prefix to references
+
 \newcommand{\setv}{\mathcal{V}}
@@
 \newcommand{\parent}{\mathtt{parent}}
-\newcommand{\toppath}{\mathtt{None}}
-\newcommand{\fsbroken}{\mathtt{Broken}}
-\newcommand{\FS}{\Phi} % {\mathrm{FS}}
+\newcommand{\toppath}{\mathtt{None}} % return value of parent()
+\newcommand{\fsbroken}{\mathtt{Broken}} % broken FS value
+\newcommand{\FS}{\Phi} % a filesystem
 \newcommand{\GS}{\Xi} % another filesystem
@@
 
-\newcommand{\extset}[1]{\wp{#1}}
-\newcommand{\orderset}[1]{\vec{\wp}{#1}}
+\newcommand{\extset}[1]{\wp({#1})}
+\newcommand{\orderset}[1]{\vec{\wp}({#1})}
+\newcommand{\ordered}[1]{\vec{\mathbf{o}}({#1})}
 
@@
 and represent all orders generated by this algorithm.
-At times by $\orderset{U}$ we mean an arbitrary sequence in the set.
+By $\ordered{U}$ we mean an arbitrary sequence in the set.
 \end{mydef}
@@
 
-We have seen that commands can break a filesystem
-either because their input type does not match the filesystem at the given path,
-or because the filesystem loses its tree property.
-
-\begin{mydef}{Fully typed sequences}
-We call a sequence of commands fully typed if whenever it breaks a filesystem
-it is explained by a mismatch on the input types of the commands it contains.
-% TODO
-TODO: define fully typed sequences in terms of the algebra?
-\end{mydef}
-
-To aid the construction of fully typed sequences, we reintroduce
-two assertion commands that either break the filesystem
+We reintroduce two assertion commands that either break the filesystem
 or leave it unchanged: $\cbb(p)$ and $\cdd(p)$.
@@
 \begin{itemize}
-\item Laws for construction typing:
+\item Laws for construction assertion:
    \begin{gather*}
@@
    \end{gather*}
-\item Laws for destruction typing:
+\item Laws for destruction assertion:
    \begin{gather*}
@@
 
-\begin{myax}$\cxy(p,V_Y)\ncoworks \czw(p,V_W)$ if $X\neq Z$\end{myax}
-% \item Disjoint laws for construction:
-%    \begin{gather*}
-%    % bd>bf
-%             [\cbd(\pp, D); \cbf(p, F)] \ncoworks [\cbf(p, F)]\\
-%    % bd>bd
-%             [\cbd(\pp, D_1); \cbd(p, D_2)] \ncoworks [\cbd(p, D_2)]\\
-%    % fd>bf
-%             [\cfd(\pp, D); \cbf(p, F)] \ncoworks [\cbf(p, F)]\\
-%    % fd>bd
-%             [\cfd(\pp, D_1); \cbd(p, D_2)] \ncoworks [\cbd(p, D_2)]
-%    \end{gather*}
-% \item Disjoint laws for destruction:
-%    \begin{gather*}
-%    % fb<db ??
-%             [\cfb(p); \cdb(\pp)] \ncoworks [\cdb(\pp)]\\
-%    % fb<df ??
-%             [\cfb(p); \cdf(\pp, F)] \ncoworks [\cdf(\pp, F)]\\
-%    % db<db ??
-%             [\cdb(p); \cdb(\pp)] \ncoworks [\cdb(\pp)]\\
-%    % db<df ??
-%             [\cdb(p); \cdf(\pp, F)] \ncoworks [\cdf(\pp, F)]
-%    \end{gather*}
+% \begin{myax}$\cxy(p,V_Y)\ncoworks \czw(p,V_W)$ if $X\neq Z$\end{myax}
 
-\begin{mylem}
+\begin{mylem}\label{lemma:cowinputmatch}
 If $A$ and $B$ are minimal sequences, $A\coworks B$,
-and there are commands on path $p$ in both $A$ ($\cxy(p, V_Y)$) and $B$ ($\czw(p, V_W)$)
+and there are commands on path $p$ in both $A$ ($\cxy(p, V_Y)\in A$) and $B$ ($\czw(p, V_W)\in B$)
 then their input types must match ($X=Z$).
 TODO: Can this be derived from the algebra?
+TODO: maybe this is the only thing needed
 \end{mylem}
-
-\begin{mylem}\label{lemma:wrextprefix}
-$[S;A]\wrext A$
-if $A$ is fully typed and $[S;A]$ is minimal.
-TODO: Is this an axiom?
-\end{mylem}
-
-\begin{mylem}\label{lemma:ncowprefix}
-$A\ncoworks B \Rightarrow [S;A]\ncoworks B$ 
-if $A$ is fully typed and $[S;A]$ is minimal.
-\end{mylem}
-\begin{proof}
-This follows from lemma \ref{lemma:wrextprefix} and axiom \ref{axiom:ncowwrnrw}.
-\end{proof}
 
@@
 
+If we start with two copies of the filesystem $\FS$,
+and two different sequences are applied to the copies to yield $\FS_A:=A\FS$
+and $\FS_B:=B\FS$, then our aim is to define sequences of commands $A^R$ and $B^R$
+so that $B^R\FS_A$ and $A^R\FS_B$ would be as close to each other as possible.
+
+We work based on the assumption that to achieve this, we need
+to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
+As some commands may have been applied to both filesystems, our first approximation
+is $A^R = \ordered{A\setminus B}$ and $B^R = \ordered{B\setminus A}$.
+This, however, will break both filesystems if there have been incompatible updates
+in $A$ and $B$. 
+Our aim is therefore to provide an algorithm that selects the commands 
+$A^R = \ordered{A^{R*}}$  where $A^{R*} \subset A\setminus B$
+and $B^R = \ordered{B^{R*}}$ where $B^{R*} \subset B\setminus A$ 
+so that $A^R\FS_B\neq\fsbroken$ and $B^R\FS_A\neq\fsbroken$,
+and show that these are the longest sequences with this property, that is,
+adding any command left out from $A^R$ or $B^R$ will break the filesystems.
+
+We assume that $A$ and $B$ are returned by an update detector,
+and so they are minimal and do not contain assertion commands.
+We also assume that $\FS_A$ and $\FS_B$ are not broken and therefore $A\coworks B$.
+
+Our reconciliation algorithm is as follows.
+
+\begin{mydef}{Reconciliation}\label{def:reconciliation}
+\[ A^R = \ordered{\{c| c\in A\setminus B \wedge \forall c'\in B\setminus A: [c;c']\equiv[c';c]\}} \]
+
+In other words, the sequence $A^R$ we apply to $\FS_B$ are all commands from $A\setminus B$
+that commute with every command in $B\setminus A$.
+This is equivalent to saying that those commands are selected from $A\setminus B$
+whose paths are unrelated to the paths of the commands in $B\setminus A$.
+\end{mydef}
+
+Now we prove that $A^R\FS_B\neq\fsbroken$.
+
 \begin{mylem}
-Let $A$ and $B$ be two minimal sequences so that $A\coworks B$.
-Then their intersection ($\orderset(A\cap B)$) can also be applied to any filesystem
+Let $A$ and $B$ be two minimal sequences without assertion commands so that $A\coworks B$.
+Then their intersection ($\ordered{A\cap B}$) can also be applied to any filesystem
 either can be applied to without breaking it.
@@
 that $A$ is minimal and $A\nequiv\cbrk$.
+Therefore either $q=\parent(p)$ or $p=\parent(q)$.
 
 Let the marked command be $\cxy(p, V_Y)$ and the preceding unmarked command in $A$ be $\czw(q, V_W)$.
-We have two cases and we will proceed by indirection.
 
-If $B$ has a command on $q$, let it be $\cqr(q, V_R)$. As $A\coworks B$, we know
-that $Q=Z$. From lemmas \ref{lemma:neighbour}, \ref{lemma:minextset} and \ref{lemma:minextorder}
-we also know that there is a $B^*\equiv B$ where $\cxy$ and $\cqr$ are next to each other,
-and from the construction and destruction laws we know that $\cxy$ determines that like
-$\czw(q, V_W)$ in $A$, any command on $q$ must precede it in $B$. As $B$ is minimal, $B^*$
-contains the same commands, and so it is the $\cqr$ command that precedes $\cxy$ in $B^*$.
+If $B$ has a command on $q$, then
+from lemma \ref{lemma:neighbour}
+we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxy$,
+and from lemmas \ref{lemma:minextset} and \ref{lemma:minextorder} we know that $B'\equiv B$.
+From the construction and destruction laws we also know that a command on $q$
+must precede $\cxy(p, V_Y)$ just as it does so in $A$.
+
+If $B$ has no command on $q$, then let $B'$ be $B$, but with an extra command added to it just before $\cxy$
+according to the construction or destruction assertion laws, from which we know
+that $B'\equiv B$.
+We also know that $B'$ is still minimal.
+
+We therefore have a minimal $B'$ which has a command on $q$ just before $\cxy(p, V_Y)$ and $B'\equiv B$.
+Let this command on $q$ be $\cqr(q, V_R)$.
+\begin{gather*}
+A = [\cdots; \czw(q, V_W); \cxy(p, V_Y); \cdots] \\
+B' = [\cdots; \cqr(q, V_R); \cxy(p, V_Y); \cdots]
+\end{gather*}
+
+As $A\coworks B$, 
+from lemma \ref{lemma:cowinputmatch}
+we know that $Q=Z$.
+
 Going back to the construction and destruction laws we see that the output type of the first command
 is always the same, and it is either $D$ or $\empt$. Therefore $R=W$ and $\cqr(q, V_R)=\czw(q, V_W)$
-as $|\setd|=|\setb|=1$. This is a contradiction as $\czw$ was not marked, but we see it must also be in $B$.
-
-If $B$ has no command on $q$, $A$ and $B$ cannot work on the same filesystem,
-as the second commands in all construction and destruction laws require a different type of input
-as the first commands. This is a contradiction as we supposed $A\coworks B$.
-
-In terms of the algebra, this latter argument could be rephrased as follows.
-Split $A$ into $[A_0;\czw(q, V_W);\cxy(p, V_Y);A_1]$.
-Add command $\cqq(q)$ before $\cxy(p, V_Y)$ to $B$ according to the construction or destruction typing laws.
-This yields $B^*\equiv B$, which we split into $[B_0;\cqq(q);\cxy(p, V_Y);B_1]$.
-We know $[\czw(q, V_W);\cxy(p, V_Y)]$ is fully typed (TODO: why?)
-and $A$ is minimal, so $[A_0;\czw(q, V_W);\cxy(p, V_Y)]$ is minimal.
-We also know $[\cqq(q);\cxy(p, V_Y)]$ is fully typed and $B^*$ is minimal, so $[B_0;\cqq(q);\cxy(p, V_Y)]$ is minimal.
-But we know $[\czw(q, V_W);\cxy(p, V_Y)]\ncoworks [\cqq(q);\cxy(p, V_Y)]$
-as comparing the construction and destruction laws to their typing counterparts we know that $Z\neq Q$,
-and so from lemma \ref{lemma:ncowprefix} and lemma \ref{lemma:ncowpostfix}
-we know that $A\ncoworks B^*\equiv B$ and so $A\ncoworks B$ which is a contradiction.
-(TODO: Is there a point in proving this this way?)
+as $|\setd|=|\setb|=1$. 
+If $B$ originally had a command on $q$,
+this is a contradiction as $\czw$ was not marked, but we see it must also be in $B'$ and therefore in $B$.
+If $B$ had no command on $q$,
+this is a contradiction because the command added to $B$ is an assertion command, so $Z=Q=R=W$, 
+but $A$ contained no assertion commands.
 
@@
 
-We now know that $A$ can be rearranged in a way that commands in $A\cap B$
-are at the beginning, and therefore $A\wrext \orderset(A\cap B)$ and by symmetry $B\wrext \orderset(A\cap B)$.
+We now know that there is an $A'\equiv A$ in which commands in $A\cap B$
+are at the beginning, and therefore 
+from axiom \ref{axiom:wrextpostfix}
+$A\wrext \ordered{A\cap B}$ and by symmetry $B\wrext \ordered{A\cap B}$.
 \end{proof}
+
+\medskip
 

### 2015-11-14 2015/paper.tex
Fresh start: new definitions for the algebra

@@
 
-\usepackage{alltt}
-\usepackage{comment}
+% \usepackage{alltt}
+% \usepackage{comment}
 \usepackage{amsmath}
@@
 \usepackage{amsthm}
-\usepackage{setspace}
-% \usepackage{fullpage}
-\usepackage{graphicx}
-% \usepackage{afterpage}
-
+% \usepackage{graphicx}
 \usepackage{centernot}
 \usepackage{tikz}
-
-% TODO Use cleveref to add prefix to references
+\usepackage{cleveref}
 
@@
 \newcommand{\GS}{\Xi} % another filesystem
-\newcommand{\pp}{p^\uparrow} % parent path
-\newcommand{\np}{p_{\centernot\leftrightarrow}} % path not related to p
+\newcommand{\pp}{p\!\!\uparrow} % parent path
 
@@
 \newcommand{\nequiv}{\not\equiv}
+
+\newcommand{\works}{\dot{\mathbf{w}}}
+
+% TODO: delete:
+\newcommand{\np}{p_{\centernot\leftrightarrow}} % path not related to p TODO change this
 \newcommand{\wrext}{\stackrel{\mathtt{br}}{\sqsubseteq}}
@@
 
+\newcommand{\recchar}[3]{{#1}^{#3}_{\mathcal{R}|{#2}}}
+\newcommand{\reca}{\recchar{A}{B}{}} % Reconciliation
+\newcommand{\recb}{\recchar{B}{A}{}}
+\newcommand{\recaset}{\recchar{A}{B}{*}}
+\newcommand{\recbset}{\recchar{B}{A}{*}}
+
 \theoremstyle{definition}
@@
 \newtheorem{mylem}{Lemma}
+
+\crefname{mydef}{definition}{definitions}
+\crefname{myax}{axiom}{axioms}
+\crefname{mylem}{lemma}{lemmas}
 
@@
 The tree propety can then be defined as
-\[ \forall \FS, p\in\setp : \FS(p) \neq \empt \wedge \parent(p) \neq \toppath \Rightarrow \FS(\parent(p)) \in \setd \]
+\[ \forall p\in\setp : \FS(p) \neq \empt \wedge \parent(p) \neq \toppath \Rightarrow \FS(\parent(p)) \in \setd \]
 
@@
 
-The exact behaviour of our commands is as follows:
-\begin{itemize}
-\item $\cbrk\FS = \fsbroken$
-\item
-All commands have the generic form $\cxy(p,V_Y)$ where
-$X$ and $Y$ are types ($\fsregcommandchar{D}$, $\fsregcommandchar{F}$ or $\fsregcommandchar{\empt}$),
-$p\in\setp$ and $V_Y$ is a value of the appropriate type from $\setvx{Y}$.
-At times we omit $V_Y$ if there is only one suitable value.
-
-Let us introduce the following notation for a filesystem derived from $\FS$:
+\begin{mydef}
+Using $\FS\{p\mapsto V\}$ we denote a filesystem derived from $\FS$:
 \[ \FS\{p\mapsto V\}(q) :=
@@
 \]
+\end{mydef}
 
-Then
+The exact behaviour of our commands is as follows:
+\begin{itemize}
+\item $\cbrk\FS = \fsbroken$
+\item
+All other commands have the generic form $\cxy(p,V_Y)$ where
+$X$ and $Y$ are types ($\fsregcommandchar{D}$, $\fsregcommandchar{F}$ or $\fsregcommandchar{\empt}$),
+$p\in\setp$ and $V_Y$ is a value of the appropriate type from $\setvx{Y}$.
+At times we omit $V_Y$ if there is only one suitable value.
 \[ \cxy(p,V_Y)\FS = 
@@
 and again in line with the aim of providing as much information as possible for the algebra,
-we encode this relationship in the pair of commands. The possible relationships we
+we encode this relationship in the pair of commands.
+
+The possible relationships we
 consider are as follows.
 
-\begin{description}
-\item[Same.] Paths that are the same ($p=q$). If the two commands affect the same path, the pair of commands
-will clearly behave differently than if the paths are different.
-%
-\item[Unrelated.] Paths that are not \emph{directly} related,
-that is, where $\parent(p)\neq q$ and $\parent(q)\neq p$. 
-In this case modifying the filesystem at one path is not going
-to affect the outcome of the command on the other path.
-The two commands will therefore commute and the pair will be reversible.
-We will denote a path separate from $p$ with $\np$.
-%
-\item[Directly related.] Directly related paths, that is, $\parent(p)=q$ or $\parent(q)=p$.
-For simplicity, we will write $\pp$ for $\parent(p)$.
-Some of these command pairs will not be reversible.
-For example, $[\cbd(\pp,D);\cbf(p,F)]$ will work on some filesystems,
-while $[\cbf(p,F);\cbd(\pp,D)]$ will break all filesystems.
-\end{description}
-
-One may think that we may be able to specify more about the reversibility
-or possible simplification of a pair of commands in the last group if we also
-knew whether the child path $p$ was the only (non-empty) child of its parent.
-However, it is easy to see that encoding this information in a pair
-is not going to enrich our algebra as, for example,
-the behaviour of a hypothetical $[\cfb(p_{\mathrm{only\ child}}); \cdb(\pp)]$
-is exactly the same as that of the more generic
-$[\cfb(p); \cdb(\pp)]$. The former will break any filesystem in which
-$p$ is not the only child as it violates its preconditions, but so will
-the generic pair.
+% One may think that we may be able to specify more about the reversibility
+% or possible simplification of a pair of commands in the last group if we also
+% knew whether the child path $p$ was the only (non-empty) child of its parent.
+% However, it is easy to see that encoding this information in a pair
+% is not going to enrich our algebra as, for example,
+% the behaviour of a hypothetical $[\cfb(p_{\mathrm{only\ child}}); \cdb(\pp)]$
+% is exactly the same as that of the more generic
+% $[\cfb(p); \cdb(\pp)]$. The former will break any filesystem in which
+% $p$ is not the only child as it violates its preconditions, but so will
+% the generic pair.
 
 % TODO Would it be worth encoding non-direct parent/child relationships?
-
-In summary, we have pairs of commands
-of the following forms:
-\begin{description}
-\item[Unrelated.] \( [\cxy(p,V_Y); \czw(\np,V_W)] \)
-\item[Same.] \( [\cxy(p,V_Y); \czw(p,V_W)] \)
-\item[Down.] \( [\cxy(\pp,V_Y); \czw(p,V_W)] \)
-\item[Up.] \( [\cxy(p,V_Y); \czw(\pp,V_W)] \)
-\end{description}
 
@@
 
-In order to reason about sequences of commands, we define \emph{algebraic laws} on
-commands. We use formal logic to build a proof system which is sound and
-complete for its intended interpretation.
+In the following sections $A,B,S$ and $T$ denote sequences of commands.
+The first two relations echo the ones defined in \cite{NREC:alg}.
 
-Similarly to \cite{NREC:alg}, we have two kinds of judgements
-for sequences \(S_1\) and \(S_2\):
 \begin{mydef}
-\(S_1\equiv S_2\), or \emph{\(S_1\) is algebraically equivalent to
-\(S_2\)}. Its intended interpretation is that they act in the same way on all
-filesystems. It is a commutative and transitive relation.
-\end{mydef}
-\begin{mydef}
-\(S_1\eqext S_2\), or \emph{\(S_2\) extends \(S_1\)}; its intended
-interpretation is that they act in the same way on all
-filesystems that \(S_1\) does not break. It is a transitive relation.
+$A\equiv B$ means that $A$ and $B$ are equivalent.
+Its intended interpretation is that they behave in the same way on
+all filesystems: $\forall \FS: A\FS=B\FS$.
+It is a commutative and transitive relation.
 \end{mydef}
 
-We have inference rules for the two judgements,
-which make it possible to derive new statements from the axioms or other statements.
-These are:
+\begin{mydef}
+$A\eqext B$ means that $B$ extends $A$.
+Its intended interpretation is that they behave in the same way
+on any filesystem $A$ does not break:
+$\forall \FS: A\FS\neq\fsbroken\Rightarrow A\FS=B\FS$
+It is a transitive relation.
+\end{mydef}
 
-\emph{For any sequences \(S_1, S_2, S, S'\):}
-\begin{itemize}
-\item \(S_1\equiv S_2 \Rightarrow S;S_1;S'\equiv S;S_2;S'\)
-\item \(S_1\eqext S_2 \Rightarrow S;S_1;S'\eqext S;S_2;S'\)
-\item \(S_1\equiv S_2 \Rightarrow S_1\eqext S_2\).
-\end{itemize}
+\begin{mydef}
+$\works A$ means that $A$ does not break a filesystem.
+Unlike the operators (TODO:?) defined above,
+$\works$ ties to the same variable in the whole expression.
+For example, the intended interpretation of
+$\works A$ is $\exists \FS: A\FS\neq\fsbroken$,
+and the intended interpretation of
+$\works A\wedge\works B$ is $\exists \FS: A\FS\neq\fsbroken \wedge B\FS\neq\fsbroken$.
+
+Clearly $\works A\Leftrightarrow A\nequiv\cbrk$.
+
+TODO: This is temporary. Check in what expression $\works$ appears
+to see if it can be simplified.
+\end{mydef}
+
+\begin{mydef}{Assertion command.}
+A command is an assertion command if
+for every filesystem it either breaks it or leaves it in the same state.
+In our current algebra $\cbb$ and $\cdd$ are the only two assertion commands.
+\end{mydef}
+
+\begin{mydef}{Minimal set / sequence.}
+A sequence or set of commands is minimal if it contains at most one command on every path.
+\end{mydef}
+
+\begin{mydef}{Simple set / sequence.}
+A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
+\end{mydef}
+
+\begin{myax}
+$A\equiv B \Rightarrow A\eqext B$
+\end{myax}
+
+\begin{myax}
+$A\equiv B \Rightarrow S;A;T\equiv S;B;T$
+\end{myax}
+
+\begin{myax}
+$A\eqext B \Rightarrow S;A;T\eqext S;B;T$
+\end{myax}
+
+\begin{myax}
+$A\eqext B \Rightarrow (\works A \Rightarrow \works B)$
+\end{myax}
+
+\begin{myax}\label{worksextpostfix}
+$\works[A;S] \Rightarrow \works A$
+\end{myax}
+
+\begin{mylem}\label{worksinputmatch}
+If $A$ and $B$ are minimal sequences, $(\works A\wedge \works B)$,
+and there are commands on path $p$ in both $A$ ($\cxy(p, V_Y)\in A$) and $B$ ($\czw(p, V_W)\in B$)
+then their input types must match ($X=Z$).
+TODO: Is this an axiom?
+\end{mylem}
+
+% ---------------------------------------------------------------
 
@@
 \begin{align*}
-[\cxy(p,V_Y); \czw(\np,V_W)] &\equiv [\czw(\np,V_W); \cxy(p,V_Y)] \\
-&\nequiv \cbrk
+[\cxy(p,V_Y); \czw(\np,V_W)] &\equiv [\czw(\np,V_W); \cxy(p,V_Y)]
 \end{align*}
@@
 
-\begin{mydef}{Minimal set / sequence}
-By a minimal set or sequence of commands we mean a set / sequence in which
-there is at most one command on every path.
-\end{mydef}
-
 If $U$ is a minimal set of commands
@@
 
+% TODO See above
 \begin{myax}$A\coworks B \Rightarrow A\nequiv\cbrk$\end{myax}
@@
 
+\begin{mylem}\label{lemma:cowdelfix}$[A;S]\coworks B \Rightarrow A\coworks B$\end{mylem}
 \begin{mylem}\label{lemma:ncowpostfix}$A\ncoworks B \Rightarrow [A;S]\ncoworks B$\end{mylem}
-\begin{proof}From axioms \ref{axiom:wrextpostfix} and \ref{axiom:ncowwrnrw}\end{proof}
-
-% \begin{myax}$\cxy(p,V_Y)\ncoworks \czw(p,V_W)$ if $X\neq Z$\end{myax}
+\begin{proof}From \cref{axiom:wrextpostfix,axiom:ncowwrnrw}\end{proof}
 
@@
 and two different sequences are applied to the copies to yield $\FS_A:=A\FS$
-and $\FS_B:=B\FS$, then our aim is to define sequences of commands $A^R$ and $B^R$
-so that $B^R\FS_A$ and $A^R\FS_B$ would be as close to each other as possible.
+and $\FS_B:=B\FS$, then our aim is to define sequences of commands $\reca$ and $\recb$
+so that $\recb\FS_A$ and $\reca\FS_B$ would be as close to each other as possible.
 
@@
 As some commands may have been applied to both filesystems, our first approximation
-is $A^R = \ordered{A\setminus B}$ and $B^R = \ordered{B\setminus A}$.
+is $\reca = \ordered{A\setminus B}$ and $\recb = \ordered{B\setminus A}$.
 This, however, will break both filesystems if there have been incompatible updates
@@
 Our aim is therefore to provide an algorithm that selects the commands 
-$A^R = \ordered{A^{R*}}$  where $A^{R*} \subset A\setminus B$
-and $B^R = \ordered{B^{R*}}$ where $B^{R*} \subset B\setminus A$ 
-so that $A^R\FS_B\neq\fsbroken$ and $B^R\FS_A\neq\fsbroken$,
+$\reca = \ordered{\recaset}$  where $\recaset \subset A\setminus B$
+and $\recb = \ordered{\recbset}$ where $\recbset \subset B\setminus A$ 
+so that $\reca\FS_B\neq\fsbroken$ and $\recb\FS_A\neq\fsbroken$,
 and show that these are the longest sequences with this property, that is,
-adding any command left out from $A^R$ or $B^R$ will break the filesystems.
+adding any command left out from $\reca$ or $\recb$ will break the filesystems.
 
@@
 \begin{mydef}{Reconciliation}\label{def:reconciliation}
-\[ A^R = \ordered{\{c| c\in A\setminus B \wedge \forall c'\in B\setminus A: [c;c']\equiv[c';c]\}} \]
+\begin{align*}
+\recaset = \{c| & \\
+& c\in A\setminus B \\
+& \wedge \\
+& \forall c'\in B\setminus A: [c;c']\equiv[c';c]\\
+\} & \\
+\reca = \ordered{\recaset}&
+\end{align*}
 
-In other words, the sequence $A^R$ we apply to $\FS_B$ are all commands from $A\setminus B$
+In other words, the sequence $\reca$ we apply to $\FS_B$ consists of all commands from $A\setminus B$
 that commute with every command in $B\setminus A$.
@@
 
-Now we prove that $A^R\FS_B\neq\fsbroken$.
+Now we prove that $\reca\FS_B\neq\fsbroken$.
 
@@
 If $B$ has a command on $q$, then
-from lemma \ref{lemma:neighbour}
+from \cref{lemma:neighbour}
 we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxy$,
-and from lemmas \ref{lemma:minextset} and \ref{lemma:minextorder} we know that $B'\equiv B$.
+and from \cref{lemma:minextset,lemma:minextorder} we know that $B'\equiv B$.
 From the construction and destruction laws we also know that a command on $q$
@@
 
-As $A\coworks B$, 
-from lemma \ref{lemma:cowinputmatch}
+As $A\coworks B\equiv B'$, 
+from \cref{lemma:cowinputmatch}
 we know that $Q=Z$.
@@
 are at the beginning, and therefore 
-from axiom \ref{axiom:wrextpostfix}
+from \cref{axiom:wrextpostfix}
 $A\wrext \ordered{A\cap B}$ and by symmetry $B\wrext \ordered{A\cap B}$.
@@
 \medskip
+
+\begin{mylem}
+If $S\coworks T$ and $\forall s\in S, t\in T: [s;t]\equiv[t;s]$
+then $[S;T]\coworks S$.
+In this case we also know
+$\forall \FS: S\FS\neq\fsbroken \wedge T\FS\neq\fsbroken \Rightarrow [S;T]\FS\neq\fsbroken$
+(but we can't yet express this in the algebra).
+\end{mylem}
+
+\begin{mylem}
+$[S;T]\coworks[S;U]\Rightarrow T\coworks U$.
+TODO Is this an axiom?
+\end{mylem}
+
+Turning back to reconciliation we know
+$A\equiv[\ordered{A\cap B};A_0]$
+where $A_0=\ordered{A\setminus B}$.
+We define $B_0$ similarly.
+As $A\coworks B$ we know $A_0\coworks B_0$.
+
+We also know commands in $A_0$ and $\recb$ commute, that is,
+$\forall a\in A_0, b\in\recb: [a;b]\equiv[b;a]$.
 

### 2015-11-14 2015/prove.py
Removed TeX output

@@ -4,7 +4,7 @@ from itertools import chain
 # directory-type value in the filesystem.
 ONE_DIRECTORY_VALUE = False
 
-STYLE = 'tex' # 'normal or 'debug' or 'tex'
+STYLE = 'debug' # 'normal or 'debug'
 
 # Constants for Content.type:
 DIR   = ' Dir'
@@ -36,28 +36,16 @@ class Content:
         """Returns a deep clone of the object."""
         return self.__class__(self.type, self.value)
 
-    def info(self, addvalue=True, path=None):
+    def info(self, addvalue=True):
         """Returns human-readable information about the object.
         
         Args:
             addvalue (bool): whether to add a description of the value
-            path (None or string): used with TeX output; added if addvalue to become the first argument of a command
         
         """
-        if STYLE == 'tex':
-            if self.isEmpty(): rc = 'b'
-            elif self.isDir(): rc = 'd'
-            elif self.isFile(): rc = 'f'
-            r = rc
-            if addvalue: r += '(' + path
-        else:
-            r = self.type
+        r = self.type
         if STYLE == 'debug' or (addvalue and not self.isEmpty() and not(ONE_DIRECTORY_VALUE and self.isDir())):
-            if STYLE == 'tex':
-                r += ', ' + rc.upper() + '_' + self.value[-1:]
-            else:
-                r += '(' + self.value + ')'
-        if STYLE == 'tex' and addvalue: r += ')'
+            r += '(' + self.value + ')'
         return r
     
     def label(self):
@@ -492,14 +480,7 @@ class Command:
         
     def info(self, isParent=False, asSequence=False):
         """Returns a human-readable string describing the object."""
-        if STYLE == 'tex':
-            path = '\\pp' if isParent else 'p'
-            path += '_1' if self.path == PATH1 else '_2'
-            r = '\\c' + self.start.info(False) + self.end.info(True, path)
-            if asSequence: return '[' + r + ']'
-            return r
-        else:
-            return "{" + self.path + ":" + self.start.info(False) + ">" + self.end.info(True) + "}"
+        return "{" + self.path + ":" + self.start.info(False) + ">" + self.end.info(True) + "}"
         
     def label(self):
[…]

### 2015-11-14 2015/paper.tex
Introducing new 'works' relation; separating axioms from inference rules

@@
 
-\newcommand{\works}{\dot{\mathbf{w}}}
+\newcommand{\works}[1]{\dot{\mathbf{w}}({#1})}
+\newcommand{\worksc}[2]{\dot{\mathbf{w}}({#1}|{#2})}
 
@@
 
+\newcommand{\infer}[2]{\begin{array}{c}{#1}\\\hline{#2}\end{array}}
+\newcommand{\inferr}[3]{\begin{array}{c}{#1}\\{#2}\\\hline{#3}\end{array}}
+
 \theoremstyle{definition}
+
 \newtheorem{mydef}{Definition}
+\crefname{mydef}{definition}{definitions}
+
 \newtheorem{myax}{Axiom}
+\crefname{myax}{axiom}{axioms}
+
 \newtheorem{mylem}{Lemma}
+\crefname{mylem}{lemma}{lemmas}
 
-\crefname{mydef}{definition}{definitions}
-\crefname{myax}{axiom}{axioms}
-\crefname{mylem}{lemma}{lemmas}
+\newtheorem{myth}{Theorem}
+\crefname{myth}{theorem}{theorems}
+
+\newtheorem{myrul}{Rule}
+\crefname{myrul}{rule}{rules}
 
@@
 
+% -----------------------------
+
 We aim to use our algebra to define and implement algorithms for conflict detection
@@
 
-In the following sections $A,B,S$ and $T$ denote sequences of commands.
+In the following sections $A$ and $B$ stand for arbitrary sequences of commands.
 The first two relations echo the ones defined in \cite{NREC:alg}.
@@
 \begin{mydef}
-$\works A$ means that $A$ does not break a filesystem.
-Unlike the operators (TODO:?) defined above,
-$\works$ ties to the same variable in the whole expression.
-For example, the intended interpretation of
-$\works A$ is $\exists \FS: A\FS\neq\fsbroken$,
-and the intended interpretation of
-$\works A\wedge\works B$ is $\exists \FS: A\FS\neq\fsbroken \wedge B\FS\neq\fsbroken$.
+$\works{A_1,A_2,\ldots,A_n}$ means that 
+$A_1,A_2,\ldots,A_n$ work at the same time.
+Its intended interpretation is
+\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_n\FS\neq\fsbroken\]
+\end{mydef}
 
-Clearly $\works A\Leftrightarrow A\nequiv\cbrk$.
-
-TODO: This is temporary. Check in what expression $\works$ appears
-to see if it can be simplified.
+\begin{mydef}
+$\worksc{A_1,A_2,\ldots,A_n}{B_1,B_2,\ldots,B_n}$ means that 
+$A_1,A_2,\ldots,A_n$ work where $B_1,B_2,\ldots,B_n$ work.
+Its intended interpretation is
+\begin{align*}
+\forall \FS:&\\ 
+&B_1\FS\neq\fsbroken \wedge \cdots \wedge B_n\FS\neq\fsbroken\\
+&\Rightarrow\\
+&A_1\FS\neq\fsbroken \wedge \cdots \wedge A_n\FS\neq\fsbroken
+\end{align*}
 \end{mydef}
@@
 
-\begin{myax}
-$A\equiv B \Rightarrow A\eqext B$
-\end{myax}
+We have the following inference rules, in which $A,B,A_i,B_i,S$ and $T$ stand for all possible sequences of commands:
 
-\begin{myax}
-$A\equiv B \Rightarrow S;A;T\equiv S;B;T$
-\end{myax}
+\begin{myrul}
+\[\infer{A\equiv B}{A\eqext B}\]
+\end{myrul}
 
-\begin{myax}
-$A\eqext B \Rightarrow S;A;T\eqext S;B;T$
-\end{myax}
+\begin{myrul}
+\[\infer{A\equiv B}{S;A;T\equiv S;B;T}\]
+\end{myrul}
 
-\begin{myax}
-$A\eqext B \Rightarrow (\works A \Rightarrow \works B)$
-\end{myax}
+\begin{myrul}
+\[\infer{A\eqext B}{S;A;T\eqext S;B;T}\]
+\end{myrul}
+
+\begin{myrul}
+\[\infer{A\eqnrw B}{\worksc{A}{B}}\]
+\end{myrul}
+
+\begin{myrul}
+\[\infer{\works{A_1,\ldots,A_{n-1},A_n}}{\works{A_1,\ldots,A_{n-1}}}\]
+\end{myrul}
+
+\begin{myrul}
+\[\infer{\worksc{A_1,\ldots,A_{n-1},A_n}{B_1,\ldots,B_n}}{\worksc{A_1,\ldots,A_{n-1}}{B_1,\ldots,B_n}}\]
+\end{myrul}
+
+\begin{myrul}{??? - and vice versa}
+\[\infer{\works{A}}{A\nequiv\cbrk}\]
+\end{myrul}
 
 \begin{myax}\label{worksextpostfix}
-$\works[A;S] \Rightarrow \works A$
+$\worksc{A}{A;S}$ where $A$ and $S$ are arbitrary sequences
 \end{myax}
@@
 \begin{mylem}\label{worksinputmatch}
-If $A$ and $B$ are minimal sequences, $(\works A\wedge \works B)$,
+If $A$ and $B$ are minimal sequences, $\works{A,B}$,
 and there are commands on path $p$ in both $A$ ($\cxy(p, V_Y)\in A$) and $B$ ($\czw(p, V_W)\in B$)
@@
 We assume that $A$ and $B$ are returned by an update detector,
-and so they are minimal and do not contain assertion commands.
-We also assume that $\FS_A$ and $\FS_B$ are not broken and therefore $A\coworks B$.
+and so they are simple sequences.
+We also assume that $\FS_A$ and $\FS_B$ are not broken and therefore $\works{A,B}$.
 
@@
 that commute with every command in $B\setminus A$.
-This is equivalent to saying that those commands are selected from $A\setminus B$
-whose paths are unrelated to the paths of the commands in $B\setminus A$.
 \end{mydef}
 
-Now we prove that $\reca\FS_B\neq\fsbroken$.
+Now we prove that $\reca\FS_B\neq\fsbroken$, and, in general:
+
+\begin{myth}
+If $A, B$ are simple, then $\worksc{[B;\reca]}{A,B}$
+\end{myth}
+
+This is trivial unless $\works{A,B}$.
 
 \begin{mylem}
-Let $A$ and $B$ be two minimal sequences without assertion commands so that $A\coworks B$.
-Then their intersection ($\ordered{A\cap B}$) can also be applied to any filesystem
-either can be applied to without breaking it.
+Let $A$ and $B$ be two simple sequences so that $\works{A, B}$.
+Then their intersection works on any filesystem
+either of them works on:
+$\worksc{\ordered{A\cap B}}{A}$, and, by symmetry, for $B$.
 \end{mylem}

### 2015-11-16 2015/prove.py
New relationship; matrix output

@@ -1,10 +1,16 @@
 from itertools import chain
+import sys
 
 # Whether directories have equal contents, i.e. there is only a single
 # directory-type value in the filesystem.
-ONE_DIRECTORY_VALUE = False
+ONE_DIRECTORY_VALUE = True
 
-STYLE = 'debug' # 'normal or 'debug'
+# Whether a rule using a DISTANT relationship should be tested on DIRECT and DIRECT_ONLY,
+# and a rule using a DIRECT relationship should be tested on DIRECT_ONLY.
+RULE_RELATIONSHIPS_INCLUSIVE = False
+
+DEBUG = 0
+STYLE = 'normal' # Style of info() methods: 'normal or 'debug'
 
 # Constants for Content.type:
 DIR   = ' Dir'
@@ -50,7 +56,8 @@ class Content:
     
     def label(self):
         """Returns a short string describing some parts of the object."""
-        return self.info(False)
+        disp = { EMPTY:'b', FILE:'f', DIR:'d' }
+        return disp[self.type]
         
     def isSame(self, content):
         """Returns whether the object is the same as another content object."""
@@ -130,7 +137,7 @@ class Node:
         """Returns a human-readable string describing the object."""
         r = []
         if self.isBroken():
-            if debug:
+            if STYLE == 'debug':
                 r.append("Broken(" + self.broken + ") ")
             else:
                 return "(Broken)"
@@ -262,12 +269,41 @@ def NodeFactory(contents='Unknown'):
 
 
 # Constants for Filesystem.rel and CommandPair.rel:
-DIRECT_PARENT      = 'DirectParent'      # p2 is the parent of p1
+DISTANT_PARENT     = 'DistantParent'     # p2 is an ancestor of p1 but not its parent
+DIRECT_PARENT      = 'DirectParent'      # p2 is the parent of p1 and p1 is not the only child
 DIRECT_PARENT_ONLY = 'DirectParentOnly'  # p2 is the parent of p1 and p1 is the only child
-DIRECT_CHILD       = 'DirectChild'       # p2 is the child of p2
+DISTANT_CHILD      = 'DistantChild'      # p2 is the descendant of p1 but not its child
+DIRECT_CHILD       = 'DirectChild'       # p2 is the child of p2 and p2 is not the only child
 DIRECT_CHILD_ONLY  = 'DirectChildOnly'   # p2 is the child of p1 and p2 is the only child
-SEPARATE           = 'Separate'          # all other cases
[…]

### 2015-11-17 2015/prove.py
Fixes to the filesystem logic

@@ -248,6 +248,17 @@ class Node:
             self.broken = 'assert-no-parent'
         return self
 
+    def assertDir(self):
+        """ Mark the node as broken if it is not a directory.
+
+        Returns:
+            self
+
+        """
+        if not self.content.isDir():
+            self.broken = 'assert-dir'
+        return self
+
 
 def NodeFactory(contents='Unknown'):
     """Generates all possible nodes.
@@ -386,13 +397,13 @@ class Filesystem:
 
         if not child.getContent().isEmpty():
             # print "child not empty"
-            parent.assertDescendant()
+            parent.assertDir().assertDescendant()
 
-        if isDirectRel(self.rel) and not parent.getContent().isEmpty():
+        if isDirectRel(self.rel) and parent.getContent().isDir():
             # print "parent not empty"
             child.assertParent()
             
-        if parent.getContent().isEmpty():
+        if not parent.getContent().isDir():
             # print "parent empty"
             child.assertNoParent()
 
@@ -448,16 +459,14 @@ class Filesystem:
                     parent.setHasChild(False)
                     
             if command_path == parentpath:
-            
-                if isDirectRel(self.rel):
+                                
+                # If the parent becomes a file or empty, the child loses parent
+                if not new_content.isDir():
+                    child.setHasParent(False)
                     
-                    # If the parent gets deleted, the child loses parent
-                    if new_content.isEmpty():
-                        child.setHasParent(False)
-                    
-                    # If the parent gets created, the child gets a parent
-                    else:
-                        child.setHasParent(True)
+                # If the parent becomes a directory, the child gets a parent
+                if isDirectRel(self.rel) and new_content.isDir():
+                    child.setHasParent(True)
   
         # Here the command is always applied to a different path than the one we changed above
         command.applyToNode(self.p1 if command_path == PATH1 else self.p2)

### 2015-11-17 2015/prove.py
Grouped output by relationship between paths; cleaner output

@@ -315,6 +315,23 @@ def getReverseRel(rel):
     }
     return rev[rel]
 
+def getFilesystemRelationship(rel):
+    fs_rel = [SEPARATE if rel == SAME else rel]
+    
+    if RULE_RELATIONSHIPS_INCLUSIVE:
+        if rel == DISTANT_CHILD:
+            fs_rel.append(DIRECT_CHILD)
+            fs_rel.append(DIRECT_CHILD_ONLY)
+        if rel == DIRECT_CHILD:
+            fs_rel.append(DIRECT_CHILD_ONLY)
+        if rel == DISTANT_PARENT:
+            fs_rel.append(DIRECT_PARENT)
+            fs_rel.append(DIRECT_PARENT_ONLY)
+        if rel == DIRECT_PARENT:
+            fs_rel.append(DIRECT_PARENT_ONLY)
+    if DEBUG > 1: print "FSRel : " + ",".join(fs_rel)
+    return fs_rel
+
 
 class Filesystem:
     """Models two paths in a filesystem to simulate the effects of a pair of commands.
@@ -679,23 +696,6 @@ class CommandPair(Sequence):
     def getRelationship(self):
         return self.rel
     
-    def getFilesystemRelationship(self):
-        fs_rel = [SEPARATE if self.rel == SAME else self.rel]
-        
-        if RULE_RELATIONSHIPS_INCLUSIVE:
-            if self.rel == DISTANT_CHILD:
-                fs_rel.append(DIRECT_CHILD)
-                fs_rel.append(DIRECT_CHILD_ONLY)
-            if self.rel == DIRECT_CHILD:
-                fs_rel.append(DIRECT_CHILD_ONLY)
-            if self.rel == DISTANT_PARENT:
-                fs_rel.append(DIRECT_PARENT)
-                fs_rel.append(DIRECT_PARENT_ONLY)
-            if self.rel == DIRECT_PARENT:
-                fs_rel.append(DIRECT_PARENT_ONLY)
-        if DEBUG > 1: print "FSRel : " + ",".join(fs_rel)
-        return fs_rel
-
     def getReverse(self):
         """Returns a new object with the pair reversed."""
         tmp = Sequence.getReverse(self)
@@ -711,22 +711,20 @@ class CommandPair(Sequence):
         return self.commands[1]
     
 
-def CommandPairFactory():
+def CommandPairFactory(rel):
[…]

### 2015-11-17 2015/paper.tex
New axioms and definitions

@@
 \newcommand{\cqq}{\fscommand{Q}{Q}}
+
+\newcommand{\typeset}{\{\fsregcommandchar{D},\fsregcommandchar{F},\empt\}}
+
+\newcommand{\descendant}{\prec}
+\newcommand{\ancestor}{\succ}
 
@@
 returns $\toppath$ if $p$ is the root of a tree.
-We also write $\pp$ for $\parent(p)$.
 \end{mydef}
@@
 afterwards. For example $mkdir(p,D)$ is $\cbd(p,D)$ and $rmdir(p)$ is $\cdb(p)$.
-Please find their exact definitions below.
+
+When we describe multiple or unknown commands, we may substitute one or both
+types with a variable, e.g. $\cxy(p,V)$. In this context,
+if we write that $\cxy=\czw$, we mean that their input and output types
+are the same ($X=Z$ and $Y=W$).
 
 % TODO No "move"
+
+% TODO Only one directory value
+In real-life applications, we often do not want to consider metadata stored in
+directories (\cite{BZ}). In other words, the contents of directories are all equal,
+which can be modelled by assuming that $|\setd|=1$.
+Note that this creates a convenient symmetry where there is only a single value
+for each type that can be repeated as we move from a path to its child ($D$ and $\empt$).
 
@@
 
-\section{Sequences of Commands}
+\section{Notation and definitions}
 
-% -----------------------------
+\begin{mydef}{$p\descendant q$.}
+$p\descendant q$ if $p$ is the ancestor of $q$ ($p=\parent^n(q)$).
+\end{mydef}
 
-We aim to use our algebra to define and implement algorithms for conflict detection
-and ordering updates (commands) before we can apply them to all replicas.
-Conflicts and ordering all happen between commands, therefore in our algebra
-we will reason about sequences of commands, 
-and do so based on a set of axioms about pairs of neighbouring commands.
-We are interested to see which pairs of commands cause errors all the time,
-and which can be simplified or reversed
-in order to see under what circumstances commands conflict or can be reordered.
+\begin{mydef}{Assertion command.}
+A command is an assertion command if
+for every filesystem it either breaks it or leaves it in the same state.
+In other words, assertion commands have the same input and output type,
+and there must also be only one possible value for their output.
+Accordingly in our current algebra $\cbb$ and $\cdd$ are the only two assertion commands.
+As $|\setb|=|\setd|=1$, we do not note their exact output value.
+\end{mydef}
 
-Pairs of commands in general will have the form
-\[ [\cxy(p,V_Y); \czw(q,V_W)] \]
-where $X,Y,Z,W\in\{\fsregcommandchar{D},\fsregcommandchar{F},\empt\}$, $p,q\in\setp$, 
-and values are of the appropriate type: 
-$V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$.
+\begin{mydef}{Minimal set / sequence.}
+A sequence or set of commands is minimal if it contains at most one command on every path.
+\end{mydef}
 
-Similarly to the case of commands, in \cite{NREC:alg} we found that in order to build
-a set of axioms in a sound and complete algebra and use the algebra effectively we at times needed to take into account
-the relationship between the paths of the commands in the pair, $p$ and $q$.
-As the relationship between the paths determine how the commands affect the filesystem
-and its tree property, 
-and again in line with the aim of providing as much information as possible for the algebra,
-we encode this relationship in the pair of commands.
-
-The possible relationships we
-consider are as follows.
-
-% One may think that we may be able to specify more about the reversibility
-% or possible simplification of a pair of commands in the last group if we also
-% knew whether the child path $p$ was the only (non-empty) child of its parent.
-% However, it is easy to see that encoding this information in a pair
-% is not going to enrich our algebra as, for example,
-% the behaviour of a hypothetical $[\cfb(p_{\mathrm{only\ child}}); \cdb(\pp)]$
-% is exactly the same as that of the more generic
-% $[\cfb(p); \cdb(\pp)]$. The former will break any filesystem in which
-% $p$ is not the only child as it violates its preconditions, but so will
-% the generic pair.
-
-% TODO Would it be worth encoding non-direct parent/child relationships?
-
-%% What does it mean to restrict the inspected filesystems to a given relationship?
+\begin{mydef}{Simple set / sequence.}
+A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
+\end{mydef}
 
@@
 
-\begin{mydef}{Assertion command.}
-A command is an assertion command if
-for every filesystem it either breaks it or leaves it in the same state.
-In our current algebra $\cbb$ and $\cdd$ are the only two assertion commands.
-\end{mydef}
+We have the following inference rules, in which $A,B,A_i,B_i,S$ and $T$ stand for all possible sequences of commands:
 
-\begin{mydef}{Minimal set / sequence.}
-A sequence or set of commands is minimal if it contains at most one command on every path.
-\end{mydef}
-
-\begin{mydef}{Simple set / sequence.}
-A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
-\end{mydef}
-
-We have the following inference rules, in which $A,B,A_i,B_i,S$ and $T$ stand for all possible sequences of commands:
+% TODO A=B -> B=A; A=B B=C -> A=C; etc.
 
@@
 
-\begin{myax}\label{worksextpostfix}
-$\worksc{A}{A;S}$ where $A$ and $S$ are arbitrary sequences
-\end{myax}
-
 \begin{mylem}\label{worksinputmatch}
@@
 
-% ---------------------------------------------------------------
+We aim to use our algebra to define and implement algorithms for conflict detection
+and ordering commands before we can apply them to all replicas.
+Conflicts and ordering all happen between commands, therefore in our algebra
+we will reason about sequences of commands, 
+and do so based on a set of axioms about pairs of neighbouring commands.
+We are interested to see which pairs of commands cause errors all the time,
+and which can be simplified or reversed
+in order to see under what circumstances commands conflict or can be reordered.
 
-Finally, we have a set of axioms or laws that describe the behaviour
-of each command pair. We exclude commands that either break the
-filesystem or leave it in the same state ($\cbb$) and for
-simplicity's sake instead of listing axioms for all pairs of commands
-we describe the behaviour of groups of pairs
-based on the relationship between the paths in the commands.
+Pairs of commands in general will have the form
+\[ [\cxy(p,V_Y); \czw(q,V_W)] \]
+where $X,Y,Z,W\in\typeset$, $p,q\in\setp$, 
+and values are of the appropriate type: 
+$V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$.
 
-\begin{description}
-\item[Unrelated.] If the two paths in the pair are not directly related, then
-the commands commute with an equivalence and they will not break every filesystem:
-\begin{align*}
-[\cxy(p,V_Y); \czw(\np,V_W)] &\equiv [\czw(\np,V_W); \cxy(p,V_Y)]
-\end{align*}
-%
-\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), the
-the commands cannot be reversed. Instead:
-   \begin{description}
-   \item[Break.]
-   The pair will break every filesystem if $Z\ne Y$, that is, if the second
-   command expects a type of value different from the one left by the first command.
-   \item[Simplified by extension.]
-   Otherwise, the pair will simplify to a single or no commands
-   if both $X$ and $W$ are $\fsregcommandchar{\empt}$ or $\fsregcommandchar{D}$:
-   \begin{gather*}
-   % bf=fb Sp
-            [\cbf(p, F); \cfb(p)] \eqext \emptyseq \\
-   % bd=db Sp
-            [\cbd(p, D); \cdb(p)] \eqext \emptyseq \\
-   % db=bd Sp
-            [\cdb(p); \cbd(p, D)] \eqext [\cdd(p, D)] \\
-   % df=fd Sp
-            [\cdf(p, F); \cfd(p, D)] \eqext [\cdd(p, D)]
-   \end{gather*}
-   \item[Simplified by equivalence.]
-   In all other cases, the commands are equivalent to a single command
-   replacing the input of the first command with the output of the second:
-   \[ [\cxy(p, V_Y); \cyz(p, V_Z)] \equiv [\cxz(p, V_Z)] \]
-   \end{description}
-%
-\item[Down.]
-These are the pairs in which the first command is applied to the parent of the path
-of the second command.
-   \begin{description}
-   \item[Construction.] There are pairs in this group to which no law applies:
-   the commands do not commute or break every filesystem, and cannot be simplified.
-   We call these ``construction'' pairs:
+The following axioms describe multiple statements
+that we accept as true in the algebra.
+These statements are generated by substituting 
+all possible values for
+$X,Y,Z,W\in\typeset$; $p,q\in\setp$; $V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$
+under the conditions noted in the axiom.
+
+\begin{myax}\label{ax_separate_commute}
+$\cxy(p,V_Y); \czw(q,V_W) \equiv \czw(q,V_W); \cxy(p,V_Y)$ where $p\not\descendant q$ and $q\not\descendant p$.
+\end{myax}
+
+\begin{myax}\label{ax_separate_nobreaks}
+$\cxy(p,V_Y); \czw(q,V_W) \nequiv \cbrk$ where $p\not\descendant q$ and $q\not\descendant p$.
+\end{myax}
+
+\begin{myax}\label{ax_same_breaks}
+$\cxy(p,V_Y); \czw(p,V_W) \equiv \cbrk$ if $Y\ne Z$.
+\end{myax}
+
+\begin{myax}\label{ax_distantchild_breaks}
+$\cxy(p,V_Y); \czw(q,V_W) \equiv \cbrk$ if $p\descendant q$ and $p\neq\parent(q)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
+\end{myax}
+
+\begin{myax}\label{ax_distantparent_breaks}
+$\cxy(p,V_Y); \czw(q,V_W) \equiv \cbrk$ if $p\ancestor q$ and $\parent(p)\neq q$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$.
+\end{myax}
+
+\begin{mydef}{Construction pair.}
+A pair of commands on paths $p$ and $q$ is a construction pair if $p=\parent(q)$ and the commands are one
+of the following:
    \begin{gather*}
    % bd>bf
-            [\cbd(\pp, D); \cbf(p, F)] \\
+            [\cbd(p, D); \cbf(q, F)] \\
    % bd>bd
-            [\cbd(\pp, D_1); \cbd(p, D_2)] \\
+            [\cbd(p, D_1); \cbd(q, D_2)] \\
    % fd>bf
-            [\cfd(\pp, D); \cbf(p, F)] \\
+            [\cfd(p, D); \cbf(q, F)] \\
    % fd>bd
-            [\cfd(\pp, D_1); \cbd(p, D_2)]
+            [\cfd(p, D_1); \cbd(q, D_2)]
    \end{gather*}
-   \item[Commute.] Otherwise, the commands in these pairs commute iff the first command is $\cdd$. For example:
-   \begin{gather*}
-   [\cdd(\pp, D); \cbf(p, F)] \equiv [\cbf(p, F); \cdd(\pp, D)]
-   \end{gather*}
-   \item[Break.] All other pairs break every filesystem, e.g.:
-   \begin{gather*}
-   [\cdf(\pp, F); \cbd(p, D)] \equiv \cbrk
-   \end{gather*}
-   \end{description}
-%
-\item[Up.]
-The final group of pairs are the ones in which the path in the second
-command is the parent of the one in the first.
-These behave similarly to the previous group. 
-   \begin{description}
-   \item[Desctruction.] There are
-   so-called ``destruction'' pairs to which no law applies:
+\end{mydef}
+
+\begin{mydef}{Destruction pair.}
+A pair of commands on paths $p$ and $q$ is a destruction pair if $\parent(p)=q$ and the commands are one
+of the following:
    \begin{gather*}
@@
    \end{gather*}
-   \item[Commute.] Otherwise the commands commute iff the \emph{second} command is $\cdd$.
-   \item[Break.] All other pairs break every filesystem.
-   \end{description}
-\end{description}
+\end{mydef}
 
-\section{Real-Life Variant}
+\begin{myax}\label{ax_directchild_breaks}
+$\cxy(p,V_Y); \czw(q,V_W) \equiv \cbrk$ if $p=\parent(q)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
+and the pair is not a construction pair.
+\end{myax}
 
-In real-life applications, we often do not want to consider metadata stored in
-directories (\cite{BZ}). In other words, the contents of directories are all equal,
-which can be modelled by assuming that $|\setd|=1$.
-Note that this creates a convenient symmetry where there is only a single value
-for each type that can be repeated as we move from a path to its child ($D$ and $\empt$).
+\begin{myax}\label{ax_directparent_breaks}
+$\cxy(p,V_Y); \czw(q,V_W) \equiv \cbrk$ if $\parent(p)=q$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
+and the pair is not a destruction pair.
+\end{myax}
 
-This also means that $\cdd$, like $\cbb$, becomes a command that either breaks a filesystem
-or leaves it in the same state, and we will disregard it in our algebra.
-The axioms will simplify as follows:
+\begin{myax}\label{worksextpostfix}
+$\worksc{A}{A;S}$ where $A$ and $S$ are arbitrary sequences of commands
+\end{myax}
 
-\begin{description}
-\item[Unrelated.] Pairs with unrelated paths are still reversible and not equivalent to
-$\cbrk$, but these are the only pairs that are reversible.
-%
-\item[Same.] If the two paths are the same ($[\cxy(p,V_Y); \czw(p,V_W)]$), then,
-as above, the commands do not commute.
-   \begin{description}
-   \item[Break.] Also, as above, the pair will break every filesystem if $Z\ne Y$.
-   \item[Simplified by extension.] Otherwise, the pair is extended by an empty sequence
-   if both $X$ and $W$ are $\fsregcommandchar{\empt}$ or $\fsregcommandchar{D}$:
-   \begin{gather*}
-   % bf=fb Sp
-            [\cbf(p, F); \cfb(p)] \eqext \emptyseq \\
-   % bd=db Sp
-            [\cbd(p, D); \cdb(p)] \eqext \emptyseq \\
-   % db=bd Sp
-            [\cdb(p); \cbd(p, D)] \eqext \emptyseq \\
-   % df=fd Sp
-            [\cdf(p, F); \cfd(p, D)] \eqext \emptyseq
-   \end{gather*}
-   \item[Simplified by equivalence.]
-   And in all other cases, as above, the commands are equivalent to a single command
-   replacing the input of the first command with the output of the second:
-   \[ [\cxy(p, V_Y); \cyz(p, V_Z)] \equiv [\cxz(p, V_Z)] \]
-   \end{description}
-%
-\item[Down.]
-Of the pairs in which the first command is applied to the parent path:
-   \begin{description}
-   \item[Construction.] the same ``construction'' pairs still have no laws, 
-   \item[Break.] but all other pairs break all filesystems.
-   \end{description}
-%
-\item[Up.]
-And of the pairs where the second command
-is applied to the parent path,
-   \begin{description}
-   \item[Destruction.] we still have the ``destruction'' pairs,
-   \item[Break.] and all other pairs break all filesystems.
-   \end{description}
-\end{description}
-
-% TODO
-{\bf Going forward we use the algebra derived from the $|\setd|=1$ case.}
+% Separate:
+% * commute
+% - if both are BB or DD, extended by empty seq
+% - if either is BB or DD, extended by the other command
+% - not equiv to break
+% Same:
+% * equiv break unless 1-out == 2-in
+% - extended by empty seq if 1-out==2-in & 1-in==2-out==B,D
+% - extended by single command (if 1-out==2-in) (otherwise breaks so true)
 
@@
 
-We reintroduce two assertion commands that either break the filesystem
-or leave it unchanged: $\cbb(p)$ and $\cdd(p)$.
-(As $|\setb|=|\setd|=1$, we do not note their exact output value.)
-They can be used to test whether $\FS(p)=\empt$ or $\FS(p)=D$.
-
-Furthermore, we note the following axioms:
+We note the following axioms:
 

### 2015-11-18 2015/paper.tex
Updated proof to new notation

@@
 \newcommand{\GS}{\Xi} % another filesystem
-\newcommand{\pp}{p\!\!\uparrow} % parent path
+\newcommand{\pp}{p^*} % parent path
 
@@
 \newcommand{\cxz}{\fscommand{X}{Z}}
+\newcommand{\cxw}{\fscommand{X}{W}}
 \newcommand{\czw}{\fscommand{Z}{W}}
@@
 
+\begin{mydef}{Unrelated paths.}
+Paths $p$ and $q$ are unrelated if $p\not\descendant q$ and $p\not\ancestor q$.
+\end{mydef}
+
 \begin{mydef}{Assertion command.}
@@
 
-\begin{myrul}
+\begin{myrul}\label{r_eq_ex}
 \[\infer{A\equiv B}{A\eqext B}\]
@@
 
-\begin{myrul}
+\begin{myrul}\label{r_ex_w}
 \[\infer{A\eqnrw B}{\worksc{A}{B}}\]
@@
 
+These rules also apply if the second, conditional part of $\worksc{\ldots}{B_1,\ldots,B_n}$ is empty:
+
 \begin{myrul}
-\[\infer{\works{A_1,\ldots,A_{n-1},A_n}}{\works{A_1,\ldots,A_{n-1}}}\]
+\[\infer{\worksc{A_1,\ldots,A_{n-1},A_n}{B_1,\ldots,B_n}}{\worksc{A_1,\ldots,A_{n-1}}{B_1,\ldots,B_n}}\]
 \end{myrul}
@@
 \begin{myrul}
-\[\infer{\worksc{A_1,\ldots,A_{n-1},A_n}{B_1,\ldots,B_n}}{\worksc{A_1,\ldots,A_{n-1}}{B_1,\ldots,B_n}}\]
+\[\infer{\worksc{A_1,\ldots,A_i,\ldots,A_n}{B_1,\ldots,B_n}}{\worksc{A_i,A_1,\ldots,A_{i-1},A_{i+1},\ldots,A_n}{B_1,\ldots,B_n}}\]
+\end{myrul}
+
+\begin{myrul}\label{r_w_w}
+\[\inferr{\worksc{A_1,\ldots,A_n}{B_1,\ldots,B_n}}{\worksc{C}{A_n}}{\worksc{A_1,\ldots,A_n,C}{B_1,\ldots,B_n}}\]
 \end{myrul}
@@
 Pairs of commands in general will have the form
-\[ [\cxy(p,V_Y); \czw(q,V_W)] \]
+\[ \cxy(p,V_Y); \czw(q,V_W) \]
 where $X,Y,Z,W\in\typeset$, $p,q\in\setp$, 
@@
 all possible values for
-$X,Y,Z,W\in\typeset$; $p,q\in\setp$; $V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$
+$X,Y,Z,W\in\typeset$; $p,q,\pp\in\setp$; $V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$
 under the conditions noted in the axiom.
@@
 \begin{myax}\label{ax_separate_commute}
+Commands on unrelated paths commute:
 $\cxy(p,V_Y); \czw(q,V_W) \equiv \czw(q,V_W); \cxy(p,V_Y)$ where $p\not\descendant q$ and $q\not\descendant p$.
@@
 \begin{myax}\label{ax_separate_nobreaks}
+Commands on unrelated paths do not break every filesystem:
 $\cxy(p,V_Y); \czw(q,V_W) \nequiv \cbrk$ where $p\not\descendant q$ and $q\not\descendant p$.
@@
 \begin{myax}\label{ax_same_breaks}
-$\cxy(p,V_Y); \czw(p,V_W) \equiv \cbrk$ if $Y\ne Z$.
+Commands on the same path break every filesystem if incompatible:
+$\cxy(p,V_Y); \czw(p,V_W) \equiv \cbrk$ where $Y\ne Z$.
+\end{myax}
+
+\begin{myax}\label{ax_same_emptyseq}
+Commands on the same path simplify:
+$\cxy(p,V_Y); \czw(p,V_W) \eqext \emptyseq$ where $Y=Z$ and $X=W=\fsregcommandchar{\empt}$ or $X=W=\fsregcommandchar{D}$.
+\end{myax}
+
+\begin{myax}\label{ax_same_singlec}
+Commands on the same path simplify:
+$\cxy(p,V_Y); \czw(p,V_W) \equiv \cxw(p,V_W)$ where $Y=Z$ and $XW\neq\cbb$ and $XW\neq\cdd$.
 \end{myax}
@@
 \begin{myax}\label{ax_distantchild_breaks}
-$\cxy(p,V_Y); \czw(q,V_W) \equiv \cbrk$ if $p\descendant q$ and $p\neq\parent(q)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
+$\cxy(\pp,V_Y); \czw(p,V_W) \equiv \cbrk$ where $\pp\descendant p$ and $\pp\neq\parent(p)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
 \end{myax}
@@
 \begin{myax}\label{ax_distantparent_breaks}
-$\cxy(p,V_Y); \czw(q,V_W) \equiv \cbrk$ if $p\ancestor q$ and $\parent(p)\neq q$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$.
+$\cxy(p,V_Y); \czw(\pp,V_W) \equiv \cbrk$ where $p\ancestor \pp$ and $\parent(p)\neq \pp$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$.
 \end{myax}
@@
 \begin{mydef}{Construction pair.}
-A pair of commands on paths $p$ and $q$ is a construction pair if $p=\parent(q)$ and the commands are one
+A pair of commands on paths $\pp$ and $p$ is a construction pair if $\pp=\parent(p)$ and the commands are one
 of the following:
@@
    % bd>bf
-            [\cbd(p, D); \cbf(q, F)] \\
+            [\cbd(\pp, D); \cbf(p, F)] \\
    % bd>bd
-            [\cbd(p, D_1); \cbd(q, D_2)] \\
+            [\cbd(\pp, D_1); \cbd(p, D_2)] \\
    % fd>bf
-            [\cfd(p, D); \cbf(q, F)] \\
+            [\cfd(\pp, D); \cbf(p, F)] \\
    % fd>bd
-            [\cfd(p, D_1); \cbd(q, D_2)]
+            [\cfd(\pp, D_1); \cbd(p, D_2)]
    \end{gather*}
@@
 \begin{mydef}{Destruction pair.}
-A pair of commands on paths $p$ and $q$ is a destruction pair if $\parent(p)=q$ and the commands are one
+A pair of commands on paths $p$ and $\pp$ is a destruction pair if $\parent(p)=\pp$ and the commands are one
 of the following:
@@
 \begin{myax}\label{ax_directchild_breaks}
-$\cxy(p,V_Y); \czw(q,V_W) \equiv \cbrk$ if $p=\parent(q)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
+$\cxy(\pp,V_Y); \czw(p,V_W) \equiv \cbrk$ where $\pp=\parent(p)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
 and the pair is not a construction pair.
@@
 \begin{myax}\label{ax_directparent_breaks}
-$\cxy(p,V_Y); \czw(q,V_W) \equiv \cbrk$ if $\parent(p)=q$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
+$\cxy(p,V_Y); \czw(\pp,V_W) \equiv \cbrk$ where $\parent(p)=\pp$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
 and the pair is not a destruction pair.
+\end{myax}
+
+\begin{myax}\label{ax_child_assert}
+An assertion command can be added on a child path:
+$\cbb(p);\cxy(\pp,V_Y) \equiv \cxy(\pp,V_Y) \equiv \cxy(\pp,V_Y);\cbb(p)$ where $\pp\descendant p$ and $\cxy\neq\cdd$.
+\end{myax}
+
+\begin{myax}\label{ax_parent_assert}
+An assertion command can be added on the parent path:
+$\cdd(\pp);\cxy(p,V_Y) \equiv \cxy(p,V_Y) \equiv \cxy(p,V_Y);\cdd(\pp)$ where $\pp\descendant p$ and $\cxy\neq\cbb$.
+\end{myax}
+
+\begin{myax}\label{ax_assert}
+$\cxy(p,V_Y) \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
 \end{myax}
@@
 \end{myax}
-
-% Separate:
-% * commute
-% - if both are BB or DD, extended by empty seq
-% - if either is BB or DD, extended by the other command
-% - not equiv to break
-% Same:
-% * equiv break unless 1-out == 2-in
-% - extended by empty seq if 1-out==2-in & 1-in==2-out==B,D
-% - extended by single command (if 1-out==2-in) (otherwise breaks so true)
 
@@
 
-\section{Extending the algebra}
-
-We note the following axioms:
-
-\begin{itemize}
-\item Laws for construction assertion:
-   \begin{gather*}
-            [\cbf(p, F)] \equiv [\cdd(\pp); \cbf(p, F)]\\
-            [\cbd(p, D)] \equiv [\cdd(\pp); \cbd(p, D)]
-   \end{gather*}
-\item Laws for destruction assertion:
-   \begin{gather*}
-            [\cdb(\pp)] \equiv [\cbb(p); \cdb(\pp)]\\
-            [\cdf(\pp, F)] \equiv [\cbb(p); \cdf(\pp, F)]
-   \end{gather*}
-\end{itemize}
-
-Separately, we extend the algebra with the following judgements and axioms:
-
-\begin{mydef}{$A\coworks B$}
-or the domains of $A$ and $B$ overlap.
-Its intended interpretation is that
-there is at least one filesystem neither $A$ nor $B$ breaks.
-It is a commutative (but not transitive) relation.
-For $A\ncoworks B$ we say that $A$ and $B$ are disjoint.
-\end{mydef}
-
-\begin{mydef}{$A\wrext B$}
-or the domain of $B$ extends that of $A$.
-Its intended interpretation is that
-$B$ does not break any filesystem $A$ does not break.
-It is a transitive relation.
-\end{mydef}
-
-% TODO See above
-\begin{myax}$A\coworks B \Rightarrow A\nequiv\cbrk$\end{myax}
-\begin{myax}$A\eqext B \Rightarrow A\wrext B$\end{myax}
-\begin{myax}\label{axiom:wrextpostfix}$[A;S] \wrext A$\end{myax}
-\begin{myax}$A\coworks B\wrext C \Rightarrow A\coworks C$\end{myax}
-\begin{myax}\label{axiom:ncowwrnrw}$A\ncoworks B\wrnrw C \Rightarrow A\ncoworks C$\end{myax}
-
-\begin{mylem}\label{lemma:cowdelfix}$[A;S]\coworks B \Rightarrow A\coworks B$\end{mylem}
-\begin{mylem}\label{lemma:ncowpostfix}$A\ncoworks B \Rightarrow [A;S]\ncoworks B$\end{mylem}
-\begin{proof}From \cref{axiom:wrextpostfix,axiom:ncowwrnrw}\end{proof}
-
-\begin{mylem}\label{lemma:cowinputmatch}
-If $A$ and $B$ are minimal sequences, $A\coworks B$,
-and there are commands on path $p$ in both $A$ ($\cxy(p, V_Y)\in A$) and $B$ ($\czw(p, V_W)\in B$)
-then their input types must match ($X=Z$).
-TODO: Can this be derived from the algebra?
-TODO: maybe this is the only thing needed
-\end{mylem}
-
 \section{Reconciliation}
@@
 Mark all commands in $A$ that also appear in $B$.
-Then $\exists A^* \in \orderset{A}$ in which the marked commands are at the beginning.
+Then there is an $A'$ in $\orderset{A}$ in which the marked commands are at the beginning.
 
@@
 
-We show $A$ can be transformed via equivalences so that this would be true
+We show $A$ can be transformed via equivalences so that this would be true,
 by induction on the number of non-marked commands preceding the last marked command.
 If it is 0, no transformation is needed.
-For the induction step, select the last marked command preceded by a non-marked command.
-If the two commute, reverse them, thereby reducing the number on relevant non-marked commands.
-If they do not commute, they must be a construction or destruction pair as we know
-that $A$ is minimal and $A\nequiv\cbrk$.
-Therefore either $q=\parent(p)$ or $p=\parent(q)$.
+For the induction step, consider the last marked command preceded by a non-marked command,
+and the non-marked command itself.
+As $A$ is a simple command and $\works{A}$, from 
+\cref{ax_distantchild_breaks,ax_distantparent_breaks,ax_directchild_breaks,ax_directparent_breaks}
+we know that these commands can only be on unrelated paths or form a construction or destruction pair.
+In the first case, swapping the commands results in a sequence equivalent to $A$,
+with the number on relevant non-marked commands reduced by one.
+In the last two cases,
+either $q=\parent(p)$ or $p=\parent(q)$.
 
@@
 and from \cref{lemma:minextset,lemma:minextorder} we know that $B'\equiv B$.
-From the construction and destruction laws we also know that a command on $q$
-must precede $\cxy(p, V_Y)$ just as it does so in $A$.
+% TODO Use when describing ordering:
+Considering the eight construction and destruction pairs we see that the command
+on the parent path determines which group the pair belongs to.
+This in turn determines whether the command on the child path must
+precede or follow the other command as otherwise the sequence would break all filesystems.
+This argument holds for both $A$ and $B$, and so the command on $q$ must be on
+the same side of the command on $p$ in both sequences.
 
 If $B$ has no command on $q$, then let $B'$ be $B$, but with an extra command added to it just before $\cxy$
-according to the construction or destruction assertion laws, from which we know
+according to \cref{ax_child_assert,ax_parent_assert}, from which we know
 that $B'\equiv B$.
-We also know that $B'$ is still minimal.
+We also know that $B'$ is still minimal (but no longer simple).
 
@@
 \begin{gather*}
-A = [\cdots; \czw(q, V_W); \cxy(p, V_Y); \cdots] \\
-B' = [\cdots; \cqr(q, V_R); \cxy(p, V_Y); \cdots]
+A = \cdots; \czw(q, V_W); \cxy(p, V_Y); \cdots \\
+B' = \cdots; \cqr(q, V_R); \cxy(p, V_Y); \cdots
 \end{gather*}
 
-As $A\coworks B\equiv B'$, 
-from \cref{lemma:cowinputmatch}
+As $\works{A,B}$ and so $\works{A,B'}$ (via \cref{r_eq_ex,r_ex_w,r_w_w}), 
+from \cref{worksinputmatch}
 we know that $Q=Z$.
 
-Going back to the construction and destruction laws we see that the output type of the first command
-is always the same, and it is either $D$ or $\empt$. Therefore $R=W$ and $\cqr(q, V_R)=\czw(q, V_W)$
+Going back to the construction and destruction pairs we see that the output type of the first command
+is always the same, and it is either $D$ or $\empt$ depending on the relationship between $p$ and $q$.
+Therefore $R=W$ and $\cqr(q, V_R)=\czw(q, V_W)$
 as $|\setd|=|\setb|=1$. 
@@
 If $B$ had no command on $q$,
-this is a contradiction because the command added to $B$ is an assertion command, so $Z=Q=R=W$, 
+this is a contradiction because the command on $q$ in $B'$ is an assertion command, so $Z=Q=R=W$, 
 but $A$ contained no assertion commands.
@@
 are at the beginning, and therefore 
-from \cref{axiom:wrextpostfix}
-$A\wrext \ordered{A\cap B}$ and by symmetry $B\wrext \ordered{A\cap B}$.
+from \cref{worksextpostfix}
+$\worksc{\ordered{A\cap B}}{A}$ and by symmetry $\worksc{\ordered{A\cap B}}{B}$.
 \end{proof}

### 2015-11-18 2015/paper.tex
Proof completed

@@
 \newcommand{\cxy}{\fscommand{X}{Y}}
+\newcommand{\cyx}{\fscommand{Y}{X}}
 \newcommand{\cyz}{\fscommand{Y}{Z}}
@@
 \newcommand{\nequiv}{\not\equiv}
+\newcommand{\indep}{\not\sim}
 
-\newcommand{\works}[1]{\dot{\mathbf{w}}({#1})}
-\newcommand{\worksc}[2]{\dot{\mathbf{w}}({#1}|{#2})}
+\newcommand{\works}[1]{{\mathbf{w}}({#1})}
+\newcommand{\worksc}[2]{{\mathbf{w}}({#1}|{#2})}
 
@@
 \newcommand{\inferr}[3]{\begin{array}{c}{#1}\\{#2}\\\hline{#3}\end{array}}
+\newcommand{\inferrr}[4]{\begin{array}{c}{#1}\\{#2}\\{#3}\\\hline{#4}\end{array}}
 
@@
 \begin{mydef}
-Using $\FS\{p\mapsto V\}$ we denote a filesystem derived from $\FS$:
+Using $\FS[V/p]$ we denote a filesystem derived from $\FS$:
 \[ \FS\{p\mapsto V\}(q) :=
@@
    \fsbroken &\mbox{if~} \FS(p)\not\in\setvx{X}\\
-   \fsbroken &\mbox{if~} \FS\{p\mapsto V_Y\} \mbox{~violates the tree property}\\
-   \FS\{p\mapsto V_Y\} &\mbox{otherwise.}
+   \fsbroken &\mbox{if~} \FS[V/p] \mbox{~violates the tree property}\\
+   \FS[V/p] &\mbox{otherwise.}
    \end{cases}
@@
 \begin{mydef}{$p\descendant q$.}
-$p\descendant q$ if $p$ is the ancestor of $q$ ($p=\parent^n(q)$).
+$p\descendant q$ if $p$ is the ancestor of $q$ ($p=\parent^n(q)$). (the transitive closure of the $\parent$ relation)
 \end{mydef}
@@
 $A\equiv B$ means that $A$ and $B$ are equivalent.
+We assume that it is a reflexive, commutative and transitive relation.
 Its intended interpretation is that they behave in the same way on
 all filesystems: $\forall \FS: A\FS=B\FS$.
-It is a commutative and transitive relation.
 \end{mydef}
@@
 $A\eqext B$ means that $B$ extends $A$.
+It is a reflexive and transitive relation.
 Its intended interpretation is that they behave in the same way
@@
 $\forall \FS: A\FS\neq\fsbroken\Rightarrow A\FS=B\FS$
-It is a transitive relation.
 \end{mydef}
@@
 $A_1,A_2,\ldots,A_n$ work at the same time.
+TODO: $A_i$ is a set (order not important).
 Its intended interpretation is
@@
 $\worksc{A_1,A_2,\ldots,A_n}{B_1,B_2,\ldots,B_n}$ means that 
-$A_1,A_2,\ldots,A_n$ work where $B_1,B_2,\ldots,B_n$ work.
+all of $A_1,A_2,\ldots,A_n$ work where all of $B_1,B_2,\ldots,B_n$ work.
+TODO: $A$s $B$s are sets.
+We assume that the arguments $A_i$ and $B_i$ commute among each other,
+and that the relation is reflexive, that is, $\worksc{B}{B}$ is true for all sequences.
 Its intended interpretation is
@@
 \begin{myrul}\label{r_ex_w}
-\[\infer{A\eqnrw B}{\worksc{A}{B}}\]
+\[\infer{B\eqext A}{\worksc{A}{B}}\]
 \end{myrul}
@@
 
-\begin{myrul}
-\[\infer{\worksc{A_1,\ldots,A_i,\ldots,A_n}{B_1,\ldots,B_n}}{\worksc{A_i,A_1,\ldots,A_{i-1},A_{i+1},\ldots,A_n}{B_1,\ldots,B_n}}\]
+% \begin{myrul}
+% \[\infer{\worksc{A_1,\ldots,A_i,\ldots,A_n}{B_1,\ldots,B_n}}{\worksc{A_i,A_1,\ldots,A_{i-1},A_{i+1},\ldots,A_n}{B_1,\ldots,B_n}}\]
+% \end{myrul}
+
+\begin{myrul}\label{r_w_combine}
+\[\inferr{\worksc{A_1,\ldots,A_n}{B_1,\ldots,B_n}}{\worksc{C}{B_1,\ldots,B_n}}{\worksc{A_1,\ldots,A_n,C}{B_1,\ldots,B_n}}\]
 \end{myrul}
@@
 \end{myrul}
+
+% \begin{myrul}\label{r_w_replacecond}
+% \[\inferr{\worksc{A_1,\ldots,A_n}{B_1,\ldots,B_n}}{\worksc{C}{B_n}}{\worksc{A_1,\ldots,A_n}{B_1,\ldots,B_{n-1},C}}\]
+% \end{myrul}
 
@@
 \end{mylem}
+
+\begin{mydef}{Inverse commands and sequences.}
+The inverse of command $\cxy(p,V_Y)$ is $\cxy(p,V_Y)^{-1} = \cyx(p,V_X)$
+where $V_X$ is an arbitrary value from $\setvx{X}$.
+The inverse of sequence $S$, $S^{-1}$, consists of the inverses of the commands in $S$
+in reverse order.
+\end{mydef}
+
+\begin{myrul}\label{r_invmove}
+\[ \infer{\worksc{S;A}{B}}{\worksc{A}{S^{-1};B}} \]
+To see the soundness of this rule...
+Sequences are bijections on filesystems over type-equality.
+TODO: $A,S,B$ need to be simple?
+\end{myrul}
+
+\begin{mydef}{Independent commands, sequences and sets.}
+For two commands $\cxy$ and $\czw$ we write $\cxy\indep\czw$ if $\cxy;\czw\equiv\czw;\cxy\nequiv\cbrk$.
+% TODO use w() instead of nequiv break
+For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
+$\forall a\in A \mbox{and~} \forall b\in B: a\indep b$.
+\end{mydef}
+
+\begin{myrul}\label{r_indep_combine}
+\[ \inferrr{\worksc{T}{S}}{\worksc{U}{S}}{T\indep U}{\worksc{T;U}{S}} \]
+To see the soundness of this rule...
+\end{myrul}
+
+\begin{mylem}\label{indep_prefix_combine}
+\[ \inferrr{\worksc{A;B}{S}}{\worksc{A;C}{S}}{B\indep C}{\worksc{A;B;C}{S}} \]
+\end{mylem}
+\begin{proof}
+From \cref{r_invmove,r_indep_combine}
+TODO reverse of /cref{r_invmove} needed
+\end{proof}
 
@@
 $\cxy(p,V_Y); \czw(q,V_W) \equiv \czw(q,V_W); \cxy(p,V_Y)$ where $p\not\descendant q$ and $q\not\descendant p$.
+TODO $p\neq q$
 \end{myax}
@@
 $\cxy(p,V_Y); \czw(q,V_W) \nequiv \cbrk$ where $p\not\descendant q$ and $q\not\descendant p$.
+TODO $p\neq q$
 \end{myax}
+
+% TODO Use 'node' instead of 'path'
 
@@
 $\cxy(p,V_Y); \czw(\pp,V_W) \equiv \cbrk$ where $p\ancestor \pp$ and $\parent(p)\neq \pp$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$.
+TODO merge into previous
 \end{myax}
@@
 & \wedge \\
-& \forall c'\in B\setminus A: [c;c']\equiv[c';c]\\
+& \forall c'\in B\setminus A: c\indep c'\\
 \} & \\
@@
 In other words, the sequence $\reca$ we apply to $\FS_B$ consists of all commands from $A\setminus B$
-that commute with every command in $B\setminus A$.
+that independent from every command in $B\setminus A$.
 \end{mydef}
@@
 \begin{myth}
-If $A, B$ are simple, then $\worksc{[B;\reca]}{A,B}$
+If $A, B$ are simple, then $\worksc{B;\reca}{A,B}$
 \end{myth}
@@
 \medskip
+
+TODO: unmarked-marked can be reversed -- but induction is wrong
 
@@
 
+We would like to prove that $\worksc{B;\reca}{A,B}$.
+From above we know that this is equivalent to
+$\worksc{\ordered{A\cap B};\ordered{B\setminus A};\reca}{A,B}$.
+As we already know that $\reca\indep B\setminus A$
+and that $\worksc{\ordered{A\cap B};\ordered{B\setminus A}}{A,B}$
+(as $\worksc{B}{A,B}$),
+based on \cref{indep_prefix_combine}
+we only need to prove that
+$\worksc{\ordered{A\cap B};\reca}{A,B}$.
+
+\newcommand{\acbi}{\ordered{A\cap B}^{-1}}
+\newcommand{\amb}{A\setminus B}
+\newcommand{\bma}{B\setminus A}
+Using \cref{r_invmove} we can rephrase this as
+% TODO axiom doesn't specify multiple conditions
+$\worksc{\reca}{\acbi;A,\acbi;B}$.
+
+We already know the following things:
+\begin{itemize}
+\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
+% \item $\amb \cap \bma = \emptyset$
+\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
+\item $\worksc{\ordered{\amb};\ordered{\bma}}{\acbi;A,\acbi;B}$ as $\worksc{A,B}{A,B}$ based on \cref{r_invmove}
+\end{itemize}
+
+Our theorem is therefore proven if we prove the following lemma:
+
 \begin{mylem}
-If $S\coworks T$ and $\forall s\in S, t\in T: [s;t]\equiv[t;s]$
-then $[S;T]\coworks S$.
-In this case we also know
-$\forall \FS: S\FS\neq\fsbroken \wedge T\FS\neq\fsbroken \Rightarrow [S;T]\FS\neq\fsbroken$
-(but we can't yet express this in the algebra).
+If
+   \begin{itemize}
+   \item \newcommand{\condSimple}{(1)} \condSimple $S$ and $T$ are simple sequences
+   % \item \newcommand{\condDisj}{(4)} \condDisj $S\cap T=\emptyset$
+   \item \newcommand{\condApr}{(2)} \condApr $S^*$ is the largest subset of $S$ where $S^*\indep T$
+   \item \newcommand{\condWork}{(3)} \condWork $\worksc{S,T}{C_1,\ldots,C_n}$
+   \end{itemize}
+then
+\[ \worksc{S^*}{C_1,\ldots,C_n} \]
 \end{mylem}
 
-\begin{mylem}
-$[S;T]\coworks[S;U]\Rightarrow T\coworks U$.
-TODO Is this an axiom?
-\end{mylem}
+\begin{proof}
+% TODO Refer back to conditions!
+This is trivial unless $\works{C_1,\ldots,C_n}$, so we will assume that it is true
+and therefore $\works{S,T}$.
+% TODO This probably needs an axiom
 
-Turning back to reconciliation we know
-$A\equiv[\ordered{A\cap B};A_0]$
-where $A_0=\ordered{A\setminus B}$.
-We define $B_0$ similarly.
-As $A\coworks B$ we know $A_0\coworks B_0$.
+Similarly to above, we prove that $S$ can be transformed into $S'$ by equivalences
+so that all commands in $S^*$ would be at its beginning.
+If so then based on \cref{worksextpostfix}
+$\worksc{S^*}{C_1,\ldots,C_n}$ as $\worksc{S'}{C_1,\ldots,C_n}$.
 
-We also know commands in $A_0$ and $\recb$ commute, that is,
-$\forall a\in A_0, b\in\recb: [a;b]\equiv[b;a]$.
+Also similarly to above,
+we proceed by induction on the number of commands in $S$ that are not in $S^*$, but which precede
+the last command in $S$ that is also in $S^*$.
+If the number is 0, the lemma is true.
+Otherwise let the last command in $S$ also in $S^*$ be $\cxy(p,V_Y)$
+and the preceding command in $S$ be $\czw(q,V_W)$.
+
+As $S$ is simple and $\works{S}$, from 
+\cref{ax_distantchild_breaks,ax_distantparent_breaks,ax_directchild_breaks,ax_directparent_breaks}
+we know that these commands can only be on unrelated paths or form a construction or destruction pair.
+In the first case, swapping the commands results in a sequence equivalent to $S$,
+with the number on relevant commands not in $S^*$ reduced by one.
+In the last two cases,
+either $q=\parent(p)$ or $p=\parent(q)$.
+
+We also know that there must be a command $\cqr(r,V_R)$ in $T$ which is not independent of $\czw(q,V_W)$.
+By definition this means that one of the following must be true:
+\begin{itemize}
+\item $\czw(q,V_W);\cqr(r,V_R) \equiv\cbrk$
+\item $\cqr(r,V_R);\czw(q,V_W) \equiv\cbrk$
+\item $\czw(q,V_W);\cqr(r,V_R) \nequiv \cqr(r,V_R);\czw(q,V_W)$
+\end{itemize}
+From these and \cref{ax_separate_commute,ax_separate_nobreaks} we also know that
+either $q\descendant r$ or $r\descendant q$.
+By definition we also know that $\cxy(p,V_Y)\indep \cqr(r,V_R)$,
+and the same argument shows that therefore
+$p\not\descendant r$ and $r\not\descendant p$ and $p\neq r$. TODO CHECK
+
+We therefore have four cases considering the relationships between $p,q$ and $r$:
+\begin{itemize}
+\item $p=\parent(q) \wedge r\descendant q$.
+   This would mean that $r\descendant p$ or $r=p$, which is a contradiction.
+\item $p=\parent(q) \wedge q\descendant r$.
+   This would mean that $p\descendant r$, which is a contradiction.
+\item $q=\parent(p) \wedge r\descendant q$.
+   This would mean that $r\descendant p$, which is a contradiction.  
+\item $q=\parent(p) \wedge q\descendant r$.
+   Let us continue with this case.
+\end{itemize}
+
+We know that $T$ cannot have a command on $q$ as $q=\parent(p)$ and $\cxy(p,V_Y)\indep T$.
+Create $T'\equiv T$ by inserting a command on $q$ before $\cqr(r,V_R)$
+into $T$ according to \cref{ax_parent_assert}.
+We now have $\cxy(p,V_Y)\indep T\equiv T'$ which is a contradiction as
+$T'$ has a command on $q$ and $q=\parent(p)$.
+% TODO axiom? A \~ B == C  =>  A \~ C
+\end{proof}
+
+TODO $\reca$ is maximal
 

### 2015-11-19 2015/paper.tex
Minor improvements

@@
 
-\newcommand{\typeset}{\{\fsregcommandchar{D},\fsregcommandchar{F},\empt\}}
-
+\newcommand{\typeset}{\{\fsregcommandchar{D},\fsregcommandchar{F},\empt\}} % Set of types in commands
+\newcommand{\cc}{\circ}
 \newcommand{\descendant}{\prec}
@@
 \newcommand{\nequiv}{\not\equiv}
-\newcommand{\indep}{\not\sim}
+\newcommand{\indep}{\wr\!\!\wr\,} % Independent
 
@@
 
-% TODO: delete:
-\newcommand{\np}{p_{\centernot\leftrightarrow}} % path not related to p TODO change this
-\newcommand{\wrext}{\stackrel{\mathtt{br}}{\sqsubseteq}}
-\newcommand{\wrnrw}{\stackrel{\mathtt{br}}{\sqsupseteq}}
-\newcommand{\coworks}{\circ}
-\newcommand{\ncoworks}{\centernot\circ}
-
-\newcommand{\emptyseq}{[\,]}
+\newcommand{\emptyseq}{[\,]} % TODO change
 
@@
 \newcommand{\orderset}[1]{\vec{\wp}({#1})}
-\newcommand{\ordered}[1]{\vec{\mathbf{o}}({#1})}
+\newcommand{\ordered}[1]{#1}
 
 \newcommand{\recchar}[3]{{#1}^{#3}_{\mathcal{R}|{#2}}}
-\newcommand{\reca}{\recchar{A}{B}{}} % Reconciliation
+\newcommand{\reca}{\recchar{A}{B}{}} % Reconciled from A
 \newcommand{\recb}{\recchar{B}{A}{}}
@@
 \crefname{myax}{axiom}{axioms}
+% \creflabelformat{myax}{A#2#1#3}
 
@@
 \crefname{mylem}{lemma}{lemmas}
+% \creflabelformat{mylem}{L#2#1#3}
 
@@
 \crefname{myrul}{rule}{rules}
+% \creflabelformat{myrul}{R#2#1#3}
 
@@
 Using $\FS[V/p]$ we denote a filesystem derived from $\FS$:
-\[ \FS\{p\mapsto V\}(q) :=
+\[ \FS[V/p](q) :=
    \begin{cases}
@@
 
-\begin{mydef}{Minimal set / sequence.}
+\begin{mydef}{Minimal set or sequence.}
 A sequence or set of commands is minimal if it contains at most one command on every path.
@@
 
-\begin{mydef}{Simple set / sequence.}
+\begin{mydef}{Simple set or sequence.}
 A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
@@
 
-% TODO A=B -> B=A; A=B B=C -> A=C; etc.
-
 \begin{myrul}\label{r_eq_ex}
@@
 \begin{myrul}
-\[\infer{A\equiv B}{S;A;T\equiv S;B;T}\]
+\[\infer{A\equiv B}{S\cc A\cc T\equiv S\cc B\cc T}\]
 \end{myrul}
@@
 \begin{myrul}
-\[\infer{A\eqext B}{S;A;T\eqext S;B;T}\]
+\[\infer{A\eqext B}{S\cc A\cc T\eqext S\cc B\cc T}\]
 \end{myrul}
@@
 
-% \begin{myrul}
-% \[\infer{\worksc{A_1,\ldots,A_i,\ldots,A_n}{B_1,\ldots,B_n}}{\worksc{A_i,A_1,\ldots,A_{i-1},A_{i+1},\ldots,A_n}{B_1,\ldots,B_n}}\]
-% \end{myrul}
-
 \begin{myrul}\label{r_w_combine}
@@
 \end{myrul}
-
-% \begin{myrul}\label{r_w_replacecond}
-% \[\inferr{\worksc{A_1,\ldots,A_n}{B_1,\ldots,B_n}}{\worksc{C}{B_n}}{\worksc{A_1,\ldots,A_n}{B_1,\ldots,B_{n-1},C}}\]
-% \end{myrul}
 
@@
 \begin{myrul}\label{r_invmove}
-\[ \infer{\worksc{S;A}{B}}{\worksc{A}{S^{-1};B}} \]
+\[ \infer{\worksc{S\cc A}{B}}{\worksc{A}{S^{-1}\cc B}} \]
 To see the soundness of this rule...
@@
 \begin{mydef}{Independent commands, sequences and sets.}
-For two commands $\cxy$ and $\czw$ we write $\cxy\indep\czw$ if $\cxy;\czw\equiv\czw;\cxy\nequiv\cbrk$.
+For two commands $\cxy$ and $\czw$ we write $\cxy\indep\czw$ if $\cxy\cc \czw\equiv\czw\cc \cxy\nequiv\cbrk$.
 % TODO use w() instead of nequiv break
@@
 \begin{myrul}\label{r_indep_combine}
-\[ \inferrr{\worksc{T}{S}}{\worksc{U}{S}}{T\indep U}{\worksc{T;U}{S}} \]
+\[ \inferrr{\worksc{T}{S}}{\worksc{U}{S}}{T\indep U}{\worksc{T\cc U}{S}} \]
 To see the soundness of this rule...
@@
 \begin{mylem}\label{indep_prefix_combine}
-\[ \inferrr{\worksc{A;B}{S}}{\worksc{A;C}{S}}{B\indep C}{\worksc{A;B;C}{S}} \]
+\[ \inferrr{\worksc{A\cc B}{S}}{\worksc{A\cc C}{S}}{B\indep C}{\worksc{A\cc B\cc C}{S}} \]
 \end{mylem}
@@
 From \cref{r_invmove,r_indep_combine}
-TODO reverse of /cref{r_invmove} needed
+TODO reverse of \cref{r_invmove} needed
 \end{proof}
@@
 Pairs of commands in general will have the form
-\[ \cxy(p,V_Y); \czw(q,V_W) \]
+\[ \cxy(p,V_Y)\cc  \czw(q,V_W) \]
 where $X,Y,Z,W\in\typeset$, $p,q\in\setp$, 
@@
 Commands on unrelated paths commute:
-$\cxy(p,V_Y); \czw(q,V_W) \equiv \czw(q,V_W); \cxy(p,V_Y)$ where $p\not\descendant q$ and $q\not\descendant p$.
+$\cxy(p,V_Y)\cc  \czw(q,V_W) \equiv \czw(q,V_W)\cc  \cxy(p,V_Y)$ where $p\not\descendant q$ and $q\not\descendant p$.
 TODO $p\neq q$
@@
 Commands on unrelated paths do not break every filesystem:
-$\cxy(p,V_Y); \czw(q,V_W) \nequiv \cbrk$ where $p\not\descendant q$ and $q\not\descendant p$.
+$\cxy(p,V_Y)\cc  \czw(q,V_W) \nequiv \cbrk$ where $p\not\descendant q$ and $q\not\descendant p$.
 TODO $p\neq q$
@@
 Commands on the same path break every filesystem if incompatible:
-$\cxy(p,V_Y); \czw(p,V_W) \equiv \cbrk$ where $Y\ne Z$.
+$\cxy(p,V_Y)\cc  \czw(p,V_W) \equiv \cbrk$ where $Y\ne Z$.
 \end{myax}
@@
 Commands on the same path simplify:
-$\cxy(p,V_Y); \czw(p,V_W) \eqext \emptyseq$ where $Y=Z$ and $X=W=\fsregcommandchar{\empt}$ or $X=W=\fsregcommandchar{D}$.
+$\cxy(p,V_Y)\cc  \czw(p,V_W) \eqext \emptyseq$ where $Y=Z$ and $X=W=\fsregcommandchar{\empt}$ or $X=W=\fsregcommandchar{D}$.
 \end{myax}
@@
 Commands on the same path simplify:
-$\cxy(p,V_Y); \czw(p,V_W) \equiv \cxw(p,V_W)$ where $Y=Z$ and $XW\neq\cbb$ and $XW\neq\cdd$.
+$\cxy(p,V_Y)\cc  \czw(p,V_W) \equiv \cxw(p,V_W)$ where $Y=Z$ and $XW\neq\cbb$ and $XW\neq\cdd$.
 \end{myax}
@@
 \begin{myax}\label{ax_distantchild_breaks}
-$\cxy(\pp,V_Y); \czw(p,V_W) \equiv \cbrk$ where $\pp\descendant p$ and $\pp\neq\parent(p)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
+$\cxy(\pp,V_Y)\cc  \czw(p,V_W) \equiv \cbrk$ where $\pp\descendant p$ and $\pp\neq\parent(p)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
 \end{myax}
@@
 \begin{myax}\label{ax_distantparent_breaks}
-$\cxy(p,V_Y); \czw(\pp,V_W) \equiv \cbrk$ where $p\ancestor \pp$ and $\parent(p)\neq \pp$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$.
+$\cxy(p,V_Y)\cc  \czw(\pp,V_W) \equiv \cbrk$ where $p\ancestor \pp$ and $\parent(p)\neq \pp$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$.
 TODO merge into previous
@@
    % bd>bf
-            [\cbd(\pp, D); \cbf(p, F)] \\
+            [\cbd(\pp, D)\cc  \cbf(p, F)] \\
    % bd>bd
-            [\cbd(\pp, D_1); \cbd(p, D_2)] \\
+            [\cbd(\pp, D_1)\cc  \cbd(p, D_2)] \\
    % fd>bf
-            [\cfd(\pp, D); \cbf(p, F)] \\
+            [\cfd(\pp, D)\cc  \cbf(p, F)] \\
    % fd>bd
-            [\cfd(\pp, D_1); \cbd(p, D_2)]
+            [\cfd(\pp, D_1)\cc  \cbd(p, D_2)]
    \end{gather*}
@@
    % fb<db ??
-            [\cfb(p); \cdb(\pp)] \\
+            [\cfb(p)\cc  \cdb(\pp)] \\
    % fb<df ??
-            [\cfb(p); \cdf(\pp, F)] \\
+            [\cfb(p)\cc  \cdf(\pp, F)] \\
    % db<db ??
-            [\cdb(p); \cdb(\pp)] \\
+            [\cdb(p)\cc  \cdb(\pp)] \\
    % db<df ??
-            [\cdb(p); \cdf(\pp, F)]
+            [\cdb(p)\cc  \cdf(\pp, F)]
    \end{gather*}
@@
 \begin{myax}\label{ax_directchild_breaks}
-$\cxy(\pp,V_Y); \czw(p,V_W) \equiv \cbrk$ where $\pp=\parent(p)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
+$\cxy(\pp,V_Y)\cc  \czw(p,V_W) \equiv \cbrk$ where $\pp=\parent(p)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
 and the pair is not a construction pair.
@@
 \begin{myax}\label{ax_directparent_breaks}
-$\cxy(p,V_Y); \czw(\pp,V_W) \equiv \cbrk$ where $\parent(p)=\pp$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
+$\cxy(p,V_Y)\cc  \czw(\pp,V_W) \equiv \cbrk$ where $\parent(p)=\pp$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
 and the pair is not a destruction pair.
@@
 An assertion command can be added on a child path:
-$\cbb(p);\cxy(\pp,V_Y) \equiv \cxy(\pp,V_Y) \equiv \cxy(\pp,V_Y);\cbb(p)$ where $\pp\descendant p$ and $\cxy\neq\cdd$.
+$\cbb(p)\cc \cxy(\pp,V_Y) \equiv \cxy(\pp,V_Y) \equiv \cxy(\pp,V_Y)\cc \cbb(p)$ where $\pp\descendant p$ and $\cxy\neq\cdd$.
 \end{myax}
@@
 An assertion command can be added on the parent path:
-$\cdd(\pp);\cxy(p,V_Y) \equiv \cxy(p,V_Y) \equiv \cxy(p,V_Y);\cdd(\pp)$ where $\pp\descendant p$ and $\cxy\neq\cbb$.
+$\cdd(\pp)\cc \cxy(p,V_Y) \equiv \cxy(p,V_Y) \equiv \cxy(p,V_Y)\cc \cdd(\pp)$ where $\pp\descendant p$ and $\cxy\neq\cbb$.
 \end{myax}
@@
 \begin{myax}\label{worksextpostfix}
-$\worksc{A}{A;S}$ where $A$ and $S$ are arbitrary sequences of commands
+$\worksc{A}{A\cc S}$ where $A$ and $S$ are arbitrary sequences of commands
 \end{myax}
@@
 \begin{myth}
-If $A, B$ are simple, then $\worksc{B;\reca}{A,B}$
+If $A, B$ are simple, then $\worksc{B\cc \reca}{A,B}$
 \end{myth}
@@
 \begin{gather*}
-A = \cdots; \czw(q, V_W); \cxy(p, V_Y); \cdots \\
-B' = \cdots; \cqr(q, V_R); \cxy(p, V_Y); \cdots
+A = \cdots\cc  \czw(q, V_W)\cc  \cxy(p, V_Y)\cc  \cdots \\
+B' = \cdots\cc  \cqr(q, V_R)\cc  \cxy(p, V_Y)\cc  \cdots
 \end{gather*}
@@
 
-We would like to prove that $\worksc{B;\reca}{A,B}$.
+We would like to prove that $\worksc{B\cc \reca}{A,B}$.
 From above we know that this is equivalent to
-$\worksc{\ordered{A\cap B};\ordered{B\setminus A};\reca}{A,B}$.
+$\worksc{\ordered{A\cap B}\cc \ordered{B\setminus A}\cc \reca}{A,B}$.
 As we already know that $\reca\indep B\setminus A$
-and that $\worksc{\ordered{A\cap B};\ordered{B\setminus A}}{A,B}$
+and that $\worksc{\ordered{A\cap B}\cc \ordered{B\setminus A}}{A,B}$
 (as $\worksc{B}{A,B}$),
@@
 we only need to prove that
-$\worksc{\ordered{A\cap B};\reca}{A,B}$.
+$\worksc{\ordered{A\cap B}\cc \reca}{A,B}$.
 
@@
 % TODO axiom doesn't specify multiple conditions
-$\worksc{\reca}{\acbi;A,\acbi;B}$.
+$\worksc{\reca}{\acbi\cc A,\acbi\cc B}$.
 
@@
 \item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
-\item $\worksc{\ordered{\amb};\ordered{\bma}}{\acbi;A,\acbi;B}$ as $\worksc{A,B}{A,B}$ based on \cref{r_invmove}
+\item $\worksc{\ordered{\amb}\cc \ordered{\bma}}{\acbi\cc A,\acbi\cc B}$ as $\worksc{A,B}{A,B}$ based on \cref{r_invmove}
 \end{itemize}
@@
 \begin{itemize}
-\item $\czw(q,V_W);\cqr(r,V_R) \equiv\cbrk$
-\item $\cqr(r,V_R);\czw(q,V_W) \equiv\cbrk$
-\item $\czw(q,V_W);\cqr(r,V_R) \nequiv \cqr(r,V_R);\czw(q,V_W)$
+\item $\czw(q,V_W)\cc \cqr(r,V_R) \equiv\cbrk$
+\item $\cqr(r,V_R)\cc \czw(q,V_W) \equiv\cbrk$
+\item $\czw(q,V_W)\cc \cqr(r,V_R) \nequiv \cqr(r,V_R)\cc \czw(q,V_W)$
 \end{itemize}
@@
 $T'$ has a command on $q$ and $q=\parent(p)$.
-% TODO axiom? A \~ B == C  =>  A \~ C
+
 \end{proof}

### 2015-11-20 2015/paper.tex
Finalizing text

@@
 
-% \usepackage{alltt}
-% \usepackage{comment}
 \usepackage{amsmath}
@@
 \usepackage{amsthm}
-% \usepackage{graphicx}
 \usepackage{centernot}
@@
 
-\newcommand{\setv}{\mathcal{V}}
+\newcommand{\setv}{\mathcal{V}} % Set of values
 \newcommand{\setvx}[1]{\mathcal{V}_{#1}}
-\newcommand{\setf}{\setvx{F}}
-\newcommand{\setd}{\setvx{D}}
-\newcommand{\setb}{\setvx{\empt}}
-\newcommand{\setp}{\mathcal{P}}
+\newcommand{\setf}{\setvx{F}} % Set of file values
+\newcommand{\setd}{\setvx{D}} % Set of directory values
+\newcommand{\setb}{\setvx{\empt}} % Set of empty values
+\newcommand{\setn}{\mathcal{N}} % Set of nodes / paths
 \newcommand{\empt}{\bot}
 \newcommand{\parent}{\mathtt{parent}}
-\newcommand{\toppath}{\mathtt{None}} % return value of parent()
+\newcommand{\topnode}{\mathtt{None}} % return value of parent()
 \newcommand{\fsbroken}{\mathtt{Broken}} % broken FS value
@@
 \newcommand{\typeset}{\{\fsregcommandchar{D},\fsregcommandchar{F},\empt\}} % Set of types in commands
-\newcommand{\cc}{\circ}
+\newcommand{\cc}{\circ} % Command / sequence concatenation
 \newcommand{\descendant}{\prec}
@@
 
-\title{A More Complete Algebra for File Synchronization}
+\title{Correctness of Algebraic File Synchronization}
 
@@
 
+Synchronizing data structures, and filesystems in particular,
+is a task that we encounter more and more often in our world
+of multiple mobile devices, cloud solutions and distributed systems.
+Applications of synchronization ranges from
+solutions for end users who expect to access personal data seamlessly
+on multiple devices and personal clouds to geographically distributed server networks
+that need to synchronize themselves with low latency to serve the 
+same content.
+
+In this paper we
+continue the work in \cite{NREC:alg} and add to the theoretical understanding
+of synchronization based not on filesystem states, but filesystem changes or commands.
+
 % Synchronization:
@@
 
+% New:
+% better command (instruction) set
+% simpler reconciliation algorithm
+% proof of correctness
+
 \section{Definition of a Filesystem}
 
-We model a filesystem using a function $\FS$ with a set of paths $\setp$ as its domain,
+We model a filesystem using a function $\FS$ with a set of nodes (filesystem paths) $\setn$ as its domain,
 and a set of possible contents $\setv$ as its codomain:
 \[ \FS : \setp \rightarrow \setv \] 
-In our model, $\setp$ contains all possible paths, and $\setv$ contains a special
-element, $\empt$, which is the value of $\FS$ at paths where there are no files
-or directories.
+In our model, $\setn$ contains all possible nodes, including the ones where there is no file or directory,
+and $\setv$ contains a special element, $\empt$, which is the value of $\FS$ at an empty node.
 We consider the contents of files, as well as any meta-information of files
@@
 
-The paths of a filesystem form a disjoint union of rooted directed trees.
+The nodes form a disjoint union of rooted directed trees.
 \begin{mydef}
-The function $\parent(p)$ returns the parent path of $p$, or
-returns $\toppath$ if $p$ is the root of a tree.
+The function $\parent(n)$ returns the parent node of $n$, or
+returns $\topnode$ if $n$ is the root of a tree.
 \end{mydef}
@@
 Every filesystem has a so-called \textbf{tree property}, which means that
-if the filesystem is not empty at a path, and the path has a parent,
-then there must be a directory at the parent path.
+if the filesystem is not empty at a node, and the node has a parent,
+then there must be a directory at the parent node.
 
@@
 The tree propety can then be defined as
-\[ \forall p\in\setp : \FS(p) \neq \empt \wedge \parent(p) \neq \toppath \Rightarrow \FS(\parent(p)) \in \setd \]
+\[ \forall n\in\setn : \FS(n) \neq \empt \wedge \parent(n) \neq \topnode \Rightarrow \FS(\parent(n)) \in \setd \]
 
-This means that as we move from a path to its child, its grandchild, and so on,
+This means that as we move down from the root of a tree of nodes,
 the types of values we encounter in the filesystem can only change according to the following
@@
 In this paper, we write $F$ for an arbitrary element of $\setf$, and $D$ for an arbitrary element
-of $\setd$. $V$ is usually a value from $\setv$ and $p$ and $q$ are paths in $\setp$.
+of $\setd$. $V$ is a value from $\setv$ and $n$ and $m$ are nodes in $\setn$.
 
@@
 
-Next we need to define instructions or commands on the filesystem about which we will reason
+Next we need to define commands on the filesystem.
+
+% <<<<<<<< TODO Rewrite: no algebra
+ about which we will reason
 using our algebra.
@@
 of potential filesystems on which they can meaningfully operate.
+% >>>>>>>>>> to here
 
@@
 A usual set of commands, based on the most frequent tools implemented by filesystems,
-might be $create(p,V)$, $edit(p,V)$ and $remove(p)$ where $p\in\setp$ and $V\in\setv$ (but $V\neq\empt$).
-Clearly the commands need to contain information about the state they leave the filesystem
-in at the path on which they operate, that is, they need to contain their output value, $V$.
-Notice, however, that the commands above also encode some information about the filesystem
-\emph{before} the command is applied; namely, $create$ requires that there are no files
-or directories at $p$, while $edit$ and $remove$ require the opposite.
+might be $create(n,V)$, $edit(n,V)$ and $remove(n)$ where $n\in\setn$ and $V\in\setv$ (but $V\neq\empt$).
+Regarding what we know of their output, that is, the state of the filesystem at $n$
+after applying the command,
+we know that after $create$ or $edit$, $\FS(n)\neq\empt$, whereas after $remove$,
+$\FS(n)$ will be $\empt$. 
+However, from \cite{NREC:alg} we know that a useful set of axioms
+will in some cases need to distinguish between edits that result in directories ($edit(n,D)$) and
+ones that result in files ($edit(n,F)$), and treat them as separate commands.
+Indeed, Bill Zissimopoulos suggested (\cite{BZ}) that extending this distinction to more commands
+utlimately simplifies
+the definition of conflicting commands, as our model will then able to predict the behavior of commands
+more precisely.
+In other words, encoding the type of the output ($D$, $F$ or $\empt$) in the commands is definitely useful.
+At the same time, there is never any need to encode information about the
+\emph{exact} output value of a command,
+as the success or failure of filesystem commands only depend on the types of values in the filesystem.
 
-We also know that after $create$ or $edit$, $\FS(p)\neq\empt$, whereas after $remove$,
-$\FS(p)$ will be $\empt$. However, from \cite{NREC:alg} we know that a useful set of axioms
-will in some cases need to distinguish between edits that result in directories ($edit(p,D)$) and
-ones that result in files ($edit(p,F)$);
-and Bill Zissimopoulos suggested in \cite{BZ} that extending this distinction simplifies
-definitions based on our algebra, as it is then able to predict the behaviour of commands
-more precisely. 
-In other words, encoding this information in the commands is definitely useful,
-but it creates a seemingly arbitrary asymmetry where
-there is more information encoded into commands about their results than about the
-original state of the filesystem.
-
-In line with the aim to encode as much information as possible in the commands,
+Notice, however, that the commands listed above also encode some information about 
+their input, the filesystem
+\emph{before} the command is applied; namely, $create(n,V)$ requires that there are no files
+or directories at $n$, while $edit(n,V)$ and $remove(n)$ require the opposite.
+This creates an arbitrary asymmetry where
+there is now more information encoded into commands about their output than about their input.
+In line with the aim to encode as much information as possible in the commands, % TODO Where is this mentioned?
 and in order to resolve this asymmetry, we propose a set of commands that encode
-the type of the original state of $\FS(p)$ as well.
+the type of the original state of $\FS(n)$ as well.
 (Some real-life filesystem commands like $rmdir$ do this already.)
-Please note that there is never any need to encode information about the
-\emph{exact} value of path $p$ in a command, merely its type ($D$, $F$ or $\empt$),
-as the success or failure of filesystem commands only depend on the type of the value.
 
@@
 two of $\fsregcommandchar{D}$, $\fsregcommandchar{F}$ and $\fsregcommandchar{\empt}$, 
-where the left sign notes the type of value
-in the filesystem before the command is applied, and the right sign notes the type
-afterwards. For example $mkdir(p,D)$ is $\cbd(p,D)$ and $rmdir(p)$ is $\cdb(p)$.
+where the left sign denotes the type of value
+required in the filesystem before the command is applied, and the right sign notes the type
+afterwards. For example, $mkdir(n,D)$ will be $\cbd(n,D)$, and $rmdir(n)$ will be $\cdb(n)$.
 
-When we describe multiple or unknown commands, we may substitute one or both
-types with a variable, e.g. $\cxy(p,V)$. In this context,
-if we write that $\cxy=\czw$, we mean that their input and output types
-are the same ($X=Z$ and $Y=W$).
-
-% TODO No "move"
-
-% TODO Only one directory value
-In real-life applications, we often do not want to consider metadata stored in
-directories (\cite{BZ}). In other words, the contents of directories are all equal,
-which can be modelled by assuming that $|\setd|=1$.
-Note that this creates a convenient symmetry where there is only a single value
-for each type that can be repeated as we move from a path to its child ($D$ and $\empt$).
-
-\section{Applying Commands}
-
-The commands can only succeed if the original value at $p$ has a type that matches
-the type required by a command. If this is not the case, or if the resulting
+A command can only succeeds if the original value at node $n$ has a type that matches
+the input type of the command. If this is not the case, or if the resulting
 filesystem no longer has the tree property, then we say that the command
@@
 We note that a command or a sequence of commands is applied to a filsystem
-by prefixing the command or sequence to it, for example: $\cbrk\FS$, $\cbd(p,D)\FS$, 
+by prefixing the command or sequence to it, for example: $\cbrk\FS$, $\cbd(n,D)\FS$, 
 or $S\FS$ if $S$ is a sequence of commands.
@@
 \begin{mydef}
-Using $\FS[V/p]$ we denote a filesystem derived from $\FS$:
-\[ \FS[V/p](q) :=
+Using $\FS[V/n]$ we denote a filesystem derived from $\FS$:
+\[ \FS[V/n](m) :=
    \begin{cases}
-   V &\mbox{if~} q=p\\
-   \FS(q) &\mbox{otherwise.}
+   V &\mbox{if~} m=n\\
+   \FS(m) &\mbox{otherwise.}
    \end{cases}
@@
 
-The exact behaviour of our commands is as follows:
+The exact behavior of our commands is as follows:
 \begin{itemize}
@@
 \item
-All other commands have the generic form $\cxy(p,V_Y)$ where
-$X$ and $Y$ are types ($\fsregcommandchar{D}$, $\fsregcommandchar{F}$ or $\fsregcommandchar{\empt}$),
-$p\in\setp$ and $V_Y$ is a value of the appropriate type from $\setvx{Y}$.
+All other commands have the generic form $\cxy(n,V_Y)$ where
+$X$ and $Y$ are types in $\typeset$,
+$n\in\setn$ and $V_Y$ is a value of the appropriate type from $\setvx{Y}$.
 At times we omit $V_Y$ if there is only one suitable value.
-\[ \cxy(p,V_Y)\FS = 
+\[ \cxy(n,V_Y)\FS = 
    \begin{cases}
    \fsbroken &\mbox{if~} \FS=\fsbroken\\
-   \fsbroken &\mbox{if~} \FS(p)\not\in\setvx{X}\\
-   \fsbroken &\mbox{if~} \FS[V/p] \mbox{~violates the tree property}\\
-   \FS[V/p] &\mbox{otherwise.}
+   \fsbroken &\mbox{if~} \FS(n)\not\in\setvx{X}\\
+   \fsbroken &\mbox{if~} \FS[V/n] \mbox{~violates the tree property}\\
+   \FS[V/n] &\mbox{otherwise.}
    \end{cases}
@@
 
-\section{Notation and definitions}
+When we describe multiple or unknown commands, we may substitute one or both
+types with a variable, for example by writing $\cxy(n,V)$. In this context,
+if we write that $\cxy=\czw$, we mean that their input and output types
+are the same ($X=Z$ and $Y=W$).
 
-\begin{mydef}{$p\descendant q$.}
-$p\descendant q$ if $p$ is the ancestor of $q$ ($p=\parent^n(q)$). (the transitive closure of the $\parent$ relation)
+% Simplifications
+% ---------------
+
+For reasons also listed in \cite{NREC:alg}, in this paper we will not consider
+a $move$ or $rename$ command. Regarding the theoretical reasoning we aim to follow,
+this turns out to be useful because these would be the only commands that affect
+filesystems at two nodes at once, therefore describing 
+the dependencies affecting these commands
+would call for a more complicated model.
+From a pragmatic perspective, this restriction does not mean that in an application
+implementing conflict resolution using the algorithm described here would not be
+able to handle renames by pre- and post-processing changes in the filesystem to
+discover them, which (especially when a rename is combined with changes to the content)
+is a non-trivial problem in itself.
+
+Another simplification we will assume in this paper is regarding directories.
+As Bill Zissimopoulos pointed out (\cite{BZ}), we often do not want to consider metadata stored in
+directories during synchronization. In other words, the contents of directories are all equal,
+which can be modelled by assuming that $|\setd|=1$.
+% This also creates a convenient symmetry where there is only a single value
+% for each type that can be repeated as we move from a path to its child ($D$ and $\empt$).
+
+\section{Describing the behavior of commands}
+
+So that we could describe the effects of commands on a filesystem, let us introduce some notation
+and note some observations.
+
+The commands we aim to investigate do not occur in isolation:
+for example, when comparing to filesystems to determine the commands needed to transform one into the other,
+we receive a set of commands with uncertain ordering.
+Applying commands to a filesystem, however, happens in time,
+so for this we need a sequence of commands.
+We use $\cc$ to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence:
+$S=\cbd(n)\cc \cbf(m,F)$, or $S'=S\cc\cbb(o)$.
+
+The following concepts will allow us to investigate sequences independently of filesystems.
+In the definitions, $A,B,S,T$ stand for arbitrary sequences of commands.
+The first two relations echo the ones defined in \cite{NREC:alg}.
+
+\begin{mydef}
+% Relation in the algebra
+$A\equiv B$ means that $A$ and $B$ are equivalent,
+% intended interpretation:
+that is, they behave in the same way on
+all filesystems: $\forall \FS: A\FS=B\FS$.
+It is a reflexive, commutative and transitive relation,
+and clearly
+% inference rule:
+$ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.
 \end{mydef}
 
-\begin{mydef}{Unrelated paths.}
-Paths $p$ and $q$ are unrelated if $p\not\descendant q$ and $p\not\ancestor q$.
+\begin{mydef}
+% Relation in the algebra
+$A\eqext B$ means that $B$ extends $A$,
+% intended interpretation:
+that is, they behave in the same way
+on any filesystem $A$ does not break:
+$\forall \FS: A\FS\neq\fsbroken\Rightarrow A\FS=B\FS$.
+It is a reflexive and transitive relation,
+and we can see that
+% inference rules:
+$ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$
+and
+$ A\equiv B \Rightarrow A\eqext B$.
+\end{mydef}
+
+\begin{mydef}{$n\descendant m$.}
+We write $n\descendant m$ if $n$ is the ancestor of $m$ ($n=\parent^n(m)$). % TODO (the transitive closure of the $\parent$ relation)
 \end{mydef}
@@
 and there must also be only one possible value for their output.
-Accordingly in our current algebra $\cbb$ and $\cdd$ are the only two assertion commands.
-As $|\setb|=|\setd|=1$, we do not note their exact output value.
+Accordingly, in our current algebra, $\cbb(n)$ and $\cdd(n)$ are the only two assertion commands,
+and we do not note their output value as it is determined.
 \end{mydef}
@@
 \begin{mydef}{Minimal set or sequence.}
-A sequence or set of commands is minimal if it contains at most one command on every path.
+A sequence or set of commands is minimal if it contains at most one command on every node.
 \end{mydef}
@@
 
-In the following sections $A$ and $B$ stand for arbitrary sequences of commands.
-The first two relations echo the ones defined in \cite{NREC:alg}.
+% -----------.........-------------.............--------------..............
 
 \begin{mydef}
-$A\equiv B$ means that $A$ and $B$ are equivalent.
-We assume that it is a reflexive, commutative and transitive relation.
-Its intended interpretation is that they behave in the same way on
-all filesystems: $\forall \FS: A\FS=B\FS$.
-\end{mydef}
-
-\begin{mydef}
-$A\eqext B$ means that $B$ extends $A$.
-It is a reflexive and transitive relation.
-Its intended interpretation is that they behave in the same way
-on any filesystem $A$ does not break:
-$\forall \FS: A\FS\neq\fsbroken\Rightarrow A\FS=B\FS$
-\end{mydef}
-
-\begin{mydef}
-$\works{A_1,A_2,\ldots,A_n}$ means that 
-$A_1,A_2,\ldots,A_n$ work at the same time.
-TODO: $A_i$ is a set (order not important).
-Its intended interpretation is
-\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_n\FS\neq\fsbroken\]
+% Unsure if this relation should be in the algebra.
+For a set of $k$ sequences
+$\works{A_1,A_2,\ldots,A_k}$ means that 
+$A_1,A_2,\ldots,A_k$ work at the same time, that is,
+% intended interpretation:
+\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_k\FS\neq\fsbroken\]
+As the sequences form a set, their order is irrelevant.
+% inference rules:
+Also, we see that 
 \end{mydef}
@@
 
-We have the following inference rules, in which $A,B,A_i,B_i,S$ and $T$ stand for all possible sequences of commands:
-
-\begin{myrul}\label{r_eq_ex}
-\[\infer{A\equiv B}{A\eqext B}\]
-\end{myrul}
-
-\begin{myrul}
-\[\infer{A\equiv B}{S\cc A\cc T\equiv S\cc B\cc T}\]
-\end{myrul}
-
-\begin{myrul}
-\[\infer{A\eqext B}{S\cc A\cc T\eqext S\cc B\cc T}\]
-\end{myrul}
+% INFERENCE RULES
 
@@
 \end{myrul}
+
+We say that the nodes $n$ and $m$ are \textbf{unrelated} if $n\not\descendant m$ and $n\not\ancestor m$
+and $n\new m$.
 

### 2015-11-21 2015/paper.tex
Finalizing text II

@@
 \newcommand{\nequiv}{\not\equiv}
-\newcommand{\indep}{\wr\!\!\wr\,} % Independent
+\newcommand{\indep}{\wr\!\!\wr\,} % Independent commands, sequences
+\newcommand{\unrel}{\indep} % Unrelated nodes
 
@@
 % Problems: conflict detection, ordering
+
+% Insight: (Prof. Norman Ramsey)
+% - updates where two orders are not equivalent are incompatible
+% - we only have a set of updates and need to create an order
 
@@
 
+% Definitions for command pairs and ordering
+% ------------------------------------------
+
 So that we could describe the effects of commands on a filesystem, let us introduce some notation
@@
 
+Let us also define the following relations between nodes:
+
 \begin{mydef}{$n\descendant m$.}
@@
 
-\begin{mydef}{Assertion command.}
-A command is an assertion command if
-for every filesystem it either breaks it or leaves it in the same state.
-In other words, assertion commands have the same input and output type,
-and there must also be only one possible value for their output.
-Accordingly, in our current algebra, $\cbb(n)$ and $\cdd(n)$ are the only two assertion commands,
-and we do not note their output value as it is determined.
+\begin{mydef}{$n\unrel m$.}
+We write $n\unrel m$, or ``$n$ and $m$ are unrelated'' if $n\not\descendant m$ and $n\not\ancestor m$
+and $n\new m$.
 \end{mydef}
 
-\begin{mydef}{Minimal set or sequence.}
-A sequence or set of commands is minimal if it contains at most one command on every node.
-\end{mydef}
+% Command pairs - Axioms
+% ----------------------
 
-\begin{mydef}{Simple set or sequence.}
-A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
-\end{mydef}
+\section{Investigating command pairs}
 
-\section{Defining the Algebra}
+Our aim is to derive information about the effects of sequences
+of commands independently of that actual filesystems.
+In order to make this possible, we investigate the smallest building
+blocks of sequences: pairs of commands that act on a filesystem directly one after the other.
+This approach is useful as there are a limited number of command pairs,
+because, as we arguad above, we can disregard the exact output value of commands apart from its type,
+and we can also abstract the relationship between the nodes in the two commands
+to a finite number of cases.
 
-% -----------.........-------------.............--------------..............
+We methodically investigated of all possibilities using a computer program
+to determine
+which pairs of commands cause errors all the time,
+which can be simplified to one or no commands, and which can be reversed
+without any change in their overall effect.
+% TODO: Footnote: URL
+Our basis for this investigation was the model of filesystems introduced in this paper.
+These properties of command pairs are crucial as they determine
+how a set of commands can be re-ordered to be applied to a filesystem
+during synchronization, and what commands will never be compatible.
 
-\begin{mydef}
-% Unsure if this relation should be in the algebra.
-For a set of $k$ sequences
-$\works{A_1,A_2,\ldots,A_k}$ means that 
-$A_1,A_2,\ldots,A_k$ work at the same time, that is,
-% intended interpretation:
-\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_k\FS\neq\fsbroken\]
-As the sequences form a set, their order is irrelevant.
-% inference rules:
-Also, we see that 
-\end{mydef}
+Below we list a number of statements derived using this method.
+Although they can be proven by investigating all relevant possibilities
+in a filesystem, we refer to these in axioms because in a secondary algebraic model
+that describes commands without reference to an underlying filesystem,
+these would function as meta-rules generating statements we would accept as true.
+See section (TODO) for more about such a model.
 
-\begin{mydef}
-$\worksc{A_1,A_2,\ldots,A_n}{B_1,B_2,\ldots,B_n}$ means that 
-all of $A_1,A_2,\ldots,A_n$ work where all of $B_1,B_2,\ldots,B_n$ work.
-TODO: $A$s $B$s are sets.
-We assume that the arguments $A_i$ and $B_i$ commute among each other,
-and that the relation is reflexive, that is, $\worksc{B}{B}$ is true for all sequences.
-Its intended interpretation is
-\begin{align*}
-\forall \FS:&\\ 
-&B_1\FS\neq\fsbroken \wedge \cdots \wedge B_n\FS\neq\fsbroken\\
-&\Rightarrow\\
-&A_1\FS\neq\fsbroken \wedge \cdots \wedge A_n\FS\neq\fsbroken
-\end{align*}
-\end{mydef}
+\medskip
 
-% INFERENCE RULES
-
-\begin{myrul}\label{r_ex_w}
-\[\infer{B\eqext A}{\worksc{A}{B}}\]
-\end{myrul}
-
-These rules also apply if the second, conditional part of $\worksc{\ldots}{B_1,\ldots,B_n}$ is empty:
-
-\begin{myrul}
-\[\infer{\worksc{A_1,\ldots,A_{n-1},A_n}{B_1,\ldots,B_n}}{\worksc{A_1,\ldots,A_{n-1}}{B_1,\ldots,B_n}}\]
-\end{myrul}
-
-\begin{myrul}\label{r_w_combine}
-\[\inferr{\worksc{A_1,\ldots,A_n}{B_1,\ldots,B_n}}{\worksc{C}{B_1,\ldots,B_n}}{\worksc{A_1,\ldots,A_n,C}{B_1,\ldots,B_n}}\]
-\end{myrul}
-
-\begin{myrul}\label{r_w_w}
-\[\inferr{\worksc{A_1,\ldots,A_n}{B_1,\ldots,B_n}}{\worksc{C}{A_n}}{\worksc{A_1,\ldots,A_n,C}{B_1,\ldots,B_n}}\]
-\end{myrul}
-
-\begin{myrul}{??? - and vice versa}
-\[\infer{\works{A}}{A\nequiv\cbrk}\]
-\end{myrul}
-
-\begin{mylem}\label{worksinputmatch}
-If $A$ and $B$ are minimal sequences, $\works{A,B}$,
-and there are commands on path $p$ in both $A$ ($\cxy(p, V_Y)\in A$) and $B$ ($\czw(p, V_W)\in B$)
-then their input types must match ($X=Z$).
-TODO: Is this an axiom?
-\end{mylem}
-
-\begin{mydef}{Inverse commands and sequences.}
-The inverse of command $\cxy(p,V_Y)$ is $\cxy(p,V_Y)^{-1} = \cyx(p,V_X)$
-where $V_X$ is an arbitrary value from $\setvx{X}$.
-The inverse of sequence $S$, $S^{-1}$, consists of the inverses of the commands in $S$
-in reverse order.
-\end{mydef}
-
-\begin{myrul}\label{r_invmove}
-\[ \infer{\worksc{S\cc A}{B}}{\worksc{A}{S^{-1}\cc B}} \]
-To see the soundness of this rule...
-Sequences are bijections on filesystems over type-equality.
-TODO: $A,S,B$ need to be simple?
-\end{myrul}
-
-We say that the nodes $n$ and $m$ are \textbf{unrelated} if $n\not\descendant m$ and $n\not\ancestor m$
-and $n\new m$.
-
-\begin{mydef}{Independent commands, sequences and sets.}
-For two commands $\cxy$ and $\czw$ we write $\cxy\indep\czw$ if $\cxy\cc \czw\equiv\czw\cc \cxy\nequiv\cbrk$.
-% TODO use w() instead of nequiv break
-For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
-$\forall a\in A \mbox{and~} \forall b\in B: a\indep b$.
-\end{mydef}
-
-\begin{myrul}\label{r_indep_combine}
-\[ \inferrr{\worksc{T}{S}}{\worksc{U}{S}}{T\indep U}{\worksc{T\cc U}{S}} \]
-To see the soundness of this rule...
-\end{myrul}
-
-\begin{mylem}\label{indep_prefix_combine}
-\[ \inferrr{\worksc{A\cc B}{S}}{\worksc{A\cc C}{S}}{B\indep C}{\worksc{A\cc B\cc C}{S}} \]
-\end{mylem}
-\begin{proof}
-From \cref{r_invmove,r_indep_combine}
-TODO reverse of \cref{r_invmove} needed
-\end{proof}
-
-We aim to use our algebra to define and implement algorithms for conflict detection
-and ordering commands before we can apply them to all replicas.
-Conflicts and ordering all happen between commands, therefore in our algebra
-we will reason about sequences of commands, 
-and do so based on a set of axioms about pairs of neighbouring commands.
-We are interested to see which pairs of commands cause errors all the time,
-and which can be simplified or reversed
-in order to see under what circumstances commands conflict or can be reordered.
-
-Pairs of commands in general will have the form
-\[ \cxy(p,V_Y)\cc  \czw(q,V_W) \]
-where $X,Y,Z,W\in\typeset$, $p,q\in\setp$, 
+Pairs of commands in general have the form
+\[ \cxy(n,V_Y)\cc  \czw(m,V_W) \]
+where $X,Y,Z,W\in\typeset$, $n,m\in\setn$, 
 and values are of the appropriate type: 
@@
 
-The following axioms describe multiple statements
-that we accept as true in the algebra.
-These statements are generated by substituting 
-all possible values for
-$X,Y,Z,W\in\typeset$; $p,q,\pp\in\setp$; $V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$
-under the conditions noted in the axiom.
-
 \begin{myax}\label{ax_separate_commute}
-Commands on unrelated paths commute:
-$\cxy(p,V_Y)\cc  \czw(q,V_W) \equiv \czw(q,V_W)\cc  \cxy(p,V_Y)$ where $p\not\descendant q$ and $q\not\descendant p$.
-TODO $p\neq q$
+Commands on unrelated nodes commute:
+$\cxy(n,V_Y)\cc  \czw(m,V_W) \equiv \czw(m,V_W)\cc \cxy(n,V_Y)$ where $n\unrel m$.
 \end{myax}
@@
 \begin{myax}\label{ax_separate_nobreaks}
-Commands on unrelated paths do not break every filesystem:
-$\cxy(p,V_Y)\cc  \czw(q,V_W) \nequiv \cbrk$ where $p\not\descendant q$ and $q\not\descendant p$.
-TODO $p\neq q$
+Commands on unrelated nodes do not break every filesystem:
+$\cxy(n,V_Y)\cc  \czw(m,V_W) \nequiv \cbrk$ where $n\unrel m$.
 \end{myax}
 
-% TODO Use 'node' instead of 'path'
-
 \begin{myax}\label{ax_same_breaks}
-Commands on the same path break every filesystem if incompatible:
-$\cxy(p,V_Y)\cc  \czw(p,V_W) \equiv \cbrk$ where $Y\ne Z$.
+Commands on the same node break every filesystem if their types are incompatible:
+$\cxy(n,V_Y)\cc \czw(n,V_W) \equiv \cbrk$ where $Y\ne Z$.
 \end{myax}
@@
 \begin{myax}\label{ax_same_emptyseq}
-Commands on the same path simplify:
-$\cxy(p,V_Y)\cc  \czw(p,V_W) \eqext \emptyseq$ where $Y=Z$ and $X=W=\fsregcommandchar{\empt}$ or $X=W=\fsregcommandchar{D}$.
+Commands on the same node simplify:
+$\cxy(n,V_Y)\cc \czw(n,V_W) \eqext \emptyseq$ where $Y=Z$ and $X=W=\fsregcommandchar{\empt}$ or $X=W=\fsregcommandchar{D}$.
 \end{myax}
@@
 \begin{myax}\label{ax_same_singlec}
-Commands on the same path simplify:
-$\cxy(p,V_Y)\cc  \czw(p,V_W) \equiv \cxw(p,V_W)$ where $Y=Z$ and $XW\neq\cbb$ and $XW\neq\cdd$.
+Commands on the same node simplify:
+$\cxy(n,V_Y)\cc  \czw(n,V_W) \equiv \cxw(n,V_W)$ where $Y=Z$ and $XW\neq\cbb$ and $XW\neq\cdd$.
 \end{myax}
+
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
@@
 \end{myax}
+
+\begin{mydef}{Inverse commands and sequences.}
+The inverse of command $\cxy(p,V_Y)$ is $\cxy(p,V_Y)^{-1} = \cyx(p,V_X)$
+where $V_X$ is an arbitrary value from $\setvx{X}$.
+The inverse of sequence $S$, $S^{-1}$, consists of the inverses of the commands in $S$
+in reverse order.
+\end{mydef}
+
+\begin{mylem}\label{r_invmove}
+\[ \infer{\worksc{S\cc A}{B}}{\worksc{A}{S^{-1}\cc B}} \]
+To see the soundness of this rule...
+Sequences are bijections on filesystems over type-equality.
+TODO: $A,S,B$ need to be simple?
+\end{mylem}
+
+\begin{mydef}{Assertion command.}
+A command is an assertion command if
+for every filesystem it either breaks it or leaves it in the same state.
+In other words, assertion commands have the same input and output type,
+and there must also be only one possible value for their output.
+Accordingly, in our current algebra, $\cbb(n)$ and $\cdd(n)$ are the only two assertion commands,
+and we do not note their output value as it is determined.
+\end{mydef}
+
+\begin{mydef}{Minimal set or sequence.}
+A sequence or set of commands is minimal if it contains at most one command on every node.
+\end{mydef}
+
+\begin{mydef}{Simple set or sequence.}
+A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
+\end{mydef}
+
+\begin{mydef}{Independent commands, sequences and sets.}
+For two commands $\cxy$ and $\czw$ we write $\cxy\indep\czw$ if $\cxy\cc \czw\equiv\czw\cc \cxy\nequiv\cbrk$.
+% TODO use w() instead of nequiv break
+For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
+$\forall a\in A \mbox{and~} \forall b\in B: a\indep b$.
+\end{mydef}
+
+\begin{myrul}\label{r_indep_combine}
+\[ \inferrr{\worksc{T}{S}}{\worksc{U}{S}}{T\indep U}{\worksc{T\cc U}{S}} \]
+To see the soundness of this rule...
+\end{myrul}
+
+\begin{mylem}\label{indep_prefix_combine}
+\[ \inferrr{\worksc{A\cc B}{S}}{\worksc{A\cc C}{S}}{B\indep C}{\worksc{A\cc B\cc C}{S}} \]
+\end{mylem}
+\begin{proof}
+From \cref{r_invmove,r_indep_combine}
+TODO reverse of \cref{r_invmove} needed
+\end{proof}
 
@@
 Now we prove that $\reca\FS_B\neq\fsbroken$, and, in general:
+
+% Introducing 'works'
+% -------------------
+
+So that we can formalise statements (TODO) needed to prove this,
+let us introduce two relations that describe under what conditions
+sequences of commands work, that is, do not break a filesystem.
+
+\begin{mydef}
+% Unsure if this relation should be in the algebra.
+For a set of $k$ sequences
+$\works{A_1,A_2,\ldots,A_k}$ means that 
+$A_1,A_2,\ldots,A_k$ work at the same time, that is,
+% intended interpretation:
+\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_k\FS\neq\fsbroken\]
+As the sequences form a set, their order is irrelevant.
+% inference rules:
+We also see that $\works{A} \Leftrightarrow A\nequiv \cbrk$. 
+\end{mydef}
+
+\begin{mydef}
+For two sets of sequences, $\worksc{A_1,A_2,\ldots,A_k}{B_1,B_2,\ldots,B_l}$ means that 
+all of $A_1,A_2,\ldots,A_k$ work where all of $B_1,B_2,\ldots,B_l$ work,
+that is,
+% intended interpretation:
+\begin{align*}
+\forall \FS:&\\ 
+&B_1\FS\neq\fsbroken \wedge \cdots \wedge B_k\FS\neq\fsbroken\\
+&\Rightarrow\\
+&A_1\FS\neq\fsbroken \wedge \cdots \wedge A_l\FS\neq\fsbroken
+\end{align*}
+As above, the order of the sequences in the sets is not relevant.
+% inference rules:
+It is easy to see that 
+% $\worksc{X}{X}$ is always true for any set of sequences $X$,
+$B\eqext A \Rightarrow \worksc{A}{B}$
+and that this relation can be chained:
+$ \worksc{A_1,\ldots,A_k}{B_1,\ldots,B_l} \wedge \worksc{C_1,\ldots,C_j}{A_1} \Rightarrow \worksc{A_1,\ldots,A_k,C_1,\ldots,C_j}{B_1,\ldots,B_l} $
+\end{mydef}
+
+\begin{mylem}\label{worksinputmatch}
+If $A$ and $B$ are minimal sequences, $\works{A,B}$,
+and there are commands on node $n$ in both $A$ ($\cxy(n, V_Y)\in A$) and $B$ ($\czw(n, V_W)\in B$)
+then their input types must match ($X=Z$).
+\end{mylem}
+\begin{proof}
+This is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
+$\cxy(n, V_Y)$ or $\czw(n, V_W)$ would not break, and consequently $A$ and $B$ could not work on the same filesystem.
+\end{proof}
 
@@
 
-TODO $\reca$ is maximal
+% TODO $\reca$ is maximal
+
+% TODO Talk about setting up an algebra / calculus
 

### 2015-11-22 2015/paper.tex
Describe ordering in detail

@@
 \newcommand{\GS}{\Xi} % another filesystem
-\newcommand{\pp}{p^*} % parent path
+\newcommand{\nn}{n^*} % parent node
 
@@
 
+% ORDERING - because when taking updates from different replicas we get an essentially unordered set
 % Insight: (Prof. Norman Ramsey)
-% - updates where two orders are not equivalent are incompatible
+% - updates where two orders (AB vs BA) are not equivalent are incompatible
 % - we only have a set of updates and need to create an order
@@
 
-The following concepts will allow us to investigate sequences independently of filesystems.
+The following concepts allow us to investigate sequences independently of filesystems.
 In the definitions, $A,B,S,T$ stand for arbitrary sequences of commands.
-The first two relations echo the ones defined in \cite{NREC:alg}.
+These relations echo the ones defined in \cite{NREC:alg}.
 
@@
 
-% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-
-\begin{myax}\label{ax_distantchild_breaks}
-$\cxy(\pp,V_Y)\cc  \czw(p,V_W) \equiv \cbrk$ where $\pp\descendant p$ and $\pp\neq\parent(p)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
-\end{myax}
-
-\begin{myax}\label{ax_distantparent_breaks}
-$\cxy(p,V_Y)\cc  \czw(\pp,V_W) \equiv \cbrk$ where $p\ancestor \pp$ and $\parent(p)\neq \pp$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$.
-TODO merge into previous
+\begin{myax}\label{ax_distantrel_breaks}
+Commands on distant relatives break all filesystems:
+$\cxy(\nn,V_Y)\cc  \czw(n,V_W) \equiv \cbrk$
+and $\czw(n,V_W)\cc \cxy(\nn,V_Y) \equiv\cbrk$
+where $\nn\descendant n$ and $\nn\neq\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
 \end{myax}
@@
 \begin{mydef}{Construction pair.}
-A pair of commands on paths $\pp$ and $p$ is a construction pair if $\pp=\parent(p)$ and the commands are one
+A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parent(n)$ and the commands are one
 of the following:
@@
    % bd>bf
-            [\cbd(\pp, D)\cc  \cbf(p, F)] \\
+            \cbd(\nn, D)\cc  \cbf(n, F) \\
    % bd>bd
-            [\cbd(\pp, D_1)\cc  \cbd(p, D_2)] \\
+            \cbd(\nn, D_1)\cc  \cbd(n, D_2) \\
    % fd>bf
-            [\cfd(\pp, D)\cc  \cbf(p, F)] \\
+            \cfd(\nn, D)\cc  \cbf(n, F) \\
    % fd>bd
-            [\cfd(\pp, D_1)\cc  \cbd(p, D_2)]
-   \end{gather*}
-\end{mydef}
-
-\begin{mydef}{Destruction pair.}
-A pair of commands on paths $p$ and $\pp$ is a destruction pair if $\parent(p)=\pp$ and the commands are one
-of the following:
-   \begin{gather*}
-   % fb<db ??
-            [\cfb(p)\cc  \cdb(\pp)] \\
-   % fb<df ??
-            [\cfb(p)\cc  \cdf(\pp, F)] \\
-   % db<db ??
-            [\cdb(p)\cc  \cdb(\pp)] \\
-   % db<df ??
-            [\cdb(p)\cc  \cdf(\pp, F)]
+            \cfd(\nn, D_1)\cc  \cbd(n, D_2)
    \end{gather*}
@@
 \begin{myax}\label{ax_directchild_breaks}
-$\cxy(\pp,V_Y)\cc  \czw(p,V_W) \equiv \cbrk$ where $\pp=\parent(p)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
+All other commands on a child break every filesystem:
+$\cxy(\nn,V_Y)\cc  \czw(n,V_W) \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
 and the pair is not a construction pair.
@@
 
+\begin{mydef}{Destruction pair.}
+A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parent(n)=\nn$ and the commands are one
+of the following:
+   \begin{gather*}
+   % fb<db ??
+            \cfb(n)\cc  \cdb(\nn) \\
+   % fb<df ??
+            \cfb(n)\cc  \cdf(\nn, F) \\
+   % db<db ??
+            \cdb(n)\cc  \cdb(\nn) \\
+   % db<df ??
+            \cdb(n)\cc  \cdf(\nn, F)
+   \end{gather*}
+\end{mydef}
+
 \begin{myax}\label{ax_directparent_breaks}
-$\cxy(p,V_Y)\cc  \czw(\pp,V_W) \equiv \cbrk$ where $\parent(p)=\pp$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
+All other commands on a parent break every filsystem:
+$\cxy(n,V_Y)\cc  \czw(\nn,V_W) \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
 and the pair is not a destruction pair.
@@
 
+\begin{mydef}{Assertion command.}
+A command is an assertion command if
+for every filesystem it either breaks it or leaves it in the same state.
+In other words, assertion commands have the same input and output type,
+and there must also be only one possible value for their output.
+Accordingly, in our current algebra, $\cbb(n)$ and $\cdd(n)$ are the only two assertion commands,
+and we do not note their output value as it is determined.
+\end{mydef}
+
 \begin{myax}\label{ax_child_assert}
-An assertion command can be added on a child path:
-$\cbb(p)\cc \cxy(\pp,V_Y) \equiv \cxy(\pp,V_Y) \equiv \cxy(\pp,V_Y)\cc \cbb(p)$ where $\pp\descendant p$ and $\cxy\neq\cdd$.
+An assertion command can be added on a descendant node:
+$\cbb(n)\cc \cxy(\nn,V_Y) \equiv \cxy(\nn,V_Y) \equiv \cxy(\nn,V_Y)\cc \cbb(n)$ where $\nn\descendant n$ and $\cxy\neq\cdd$.
 \end{myax}
@@
 \begin{myax}\label{ax_parent_assert}
-An assertion command can be added on the parent path:
-$\cdd(\pp)\cc \cxy(p,V_Y) \equiv \cxy(p,V_Y) \equiv \cxy(p,V_Y)\cc \cdd(\pp)$ where $\pp\descendant p$ and $\cxy\neq\cbb$.
+An assertion command can be added on an ancestor node:
+$\cdd(\nn)\cc \cxy(n,V_Y) \equiv \cxy(n,V_Y) \equiv \cxy(n,V_Y)\cc \cdd(\nn)$ where $\nn\descendant n$ and $\cxy\neq\cbb$.
 \end{myax}
+
+\begin{myax}\label{ax_assert}
+Assertion commands can be removed:
+$\cxy(n,V_Y) \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
+\end{myax}
+
+% Update detection
+% ----------------
+
+\section{Update detection}
+
+In a command-based reconciliation solution we assume that we have two sequences of commands
+$A$ and $B$ that have modified a single filesystem $\FS$ yielding two different replicas $\FS_A$ and $\FS_B$ that we
+need to reconcile. While it is conceivable that the sequences would be based on a record of
+all operations that modified the two filesystems, in most filesystem implementations
+such records are not implemented, and therefore we must construct suitable sequences
+by comparing $\FS_A$ and $\FS_B$ to their common ancestor, $\FS$. This is called update detection.
+
+A sequence that transforms $\FS$ into $\FS_A$ must contain at least one command on each node
+that changes between the two states of the filesystem. Also, it is easy to see that this is also
+sufficient, as there are commands available for any input and output value. 
+Specifically, if at node $n$, $\FS(n)=X'$ and $\FS_A(n)=Y'\neq X'$, then we add the command $\cxy(n,Y')$ to $A$
+where $X'\in\setvx{X}$ and $Y'\in\setvx{Y}$.
+
+To be able to describe such sequences better, let us introduce the following properties:
+
+\begin{mydef}{Minimal set or sequence.}
+% TODO Don't introduce?
+A sequence or set of commands is minimal if it contains at most one command on every node.
+\end{mydef}
+
+\begin{mydef}{Simple set or sequence.}
+A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
+\end{mydef}
+
+This update detector therefore yields a simple set of commands because we only add a single command
+for each node, and we only add commands that are necessary, that is, there will be no 
+assertion commands in the set.
+
+The next step in generating the sequences is to order the commands collected.
+As this task is at the heart of reconciliation itself independently of update detection,
+we discuss it in the next section.
+
+% TODO Proof of correctness of update detection - the generated order will work
+
+% Ordering commands
+% ----------------
+
+\section{Ordering commands}
+
+We often encounter the case where we only have a set of commands without a specified order.
+As we have seen above, this can occur after the first stage of update detection,
+but, more importantly,
+it is actually the task of the reconciler to determine whether there is an order,
+and if yes, what order,
+in which updates from multiple replicas can be applied to a filesystem.
+
+In this section we describe an algorithm with which all possible orderings of a
+set of sequences can be generated, but before doing so, let us consider the following lemma.
+
+\begin{mylem}\label{connected_changes}
+If a simple set of commands that can be applied to a filesystem in some order without breaking it
+contains commands on $n$ and $\nn$ where $\nn\descendant n$
+but $\nn\neq\parent(n)$, then the set must also contain a command on $\parent(n)$.
+\end{mylem}
+\begin{proof}
+We will prove this statement for simple sequences, as if all sequences must contain a command on $\parent(n)$
+under the given conditions, then so must sets because otherwise there would be no order in which thay can be
+applied to any filesystem.
+
+Let $A$ be a sequence that satisfies the conditions;
+we therefore know that it contains a command $\cxy(n,V_Y)$ on $n$
+and another command $\czw(\nn,V_W)$ on $\nn$.
+We use an indirect proof and assume that there are no commands on $\parent(n)$ in $A$.
+Next, we create a new sequence $A'\equiv A$ in which $\cxy$ and $\czw$ are next to each other.
+If they are already next to each other in $A$, there is nothing to do.
+Otherwise, consider the command next to $\cxy(n,V_Y)$ in the direction where $\czw(\nn,V_W)$ is.
+Let this command be $\cqr(m,V_R)$.
+If $\czw$ is to the right, the $A$ looks like the following:
+\[ A = \cdots\cc\cxy(n,V_Y)\cc\cqr(m,V_R)\cc\cdots\cc\czw(\nn,V_W)\cc\cdots \]
+If $n\unrel m$, reverse $\cxy$ and $\cqr$. Based on \cref{ax_separate_commute} we know that the new
+sequence is equivalent to $A$.
+Otherwise, we know $m\neq\parent(n)$ as there are no commands on $\parent(n)$, and so
+from \cref{ax_distantrel_breaks} we get $A\equiv\cbrk$ which contradicts our assumptions.
+(Note that $A$ cannot contains assertion commands.)
+By repeating this step we can therefore convert $A$ into $A'$ where $\cxy$ and $\czw$ are neighboring commands.
+However, then \cref{ax_distantrel_breaks} applies to the sequence and therefore $A\equiv A'\equiv\cbrk$ which
+is again a contradiction.
+\end{proof}
+
+By applying \cref{connected_changes} multiple times we see that if a simple set of commands
+contains two commands on related nodes, then it must contain a command on each
+node that is between these two nodes in the parent--child tree.
+
+We can now define our algorithm to generate orders of sets of commands.
+
+Let $U$ be a simple set of commands
+that we know can be applied to at least one filesystem in some order without breaking it.
+Then we can split $U$ into a maximum number of disjunct subsets
+(components) so that the nodes of two commands from two different subsets are unrelated.
+These will simply be the components of the subset of the node forest that contains the nodes affected by the set.
+
+From \cref{ax_separate_commute} we know that commands from different 
+components can be applied in any order.
+Therefore once we have ordered the commands inside a component, we generate
+all permutations of the components themselves, including the ones
+in which commands from separate components mix and overlap
+(but where the possible orders determined for the components are respected).
+
+Next, consider the ordering inside a component.
+
+This is not a problem in the case of components containing a single command only.
+(Note that $\cff$ can only appear in a component of one.)
+
+In each component that is larger than one, 
+we know that all nodes are related, and from \cref{connected_changes}
+we also know that it must contain commands on all nodes in between.
+Therefore the nodes
+form a rooted ordered tree,
+and the pairs of commands connected by the edges in the tree 
+must be construction or destruction pairs.
+(Otherwise, there would be no ordering of the component that is not equivalent to $\cbrk$
+and via \cref{ax_separate_commute} there would be no ordering of the whole set, either.)
+
+To order the commands in the component,
+select the command with the topmost node, so that there would be no command
+on its parent node (if there is one). 
+If the command removes content at this node (it is of the form $\fsregcommand{X}{\empt}$), 
+then it must follow all other commands in the component, and
+all parent--child pairs in the whole component must be destruction pairs.
+Otherwise, the command with the topmost node needs to precede the other commands,
+and the component must be made of construction pairs.
+These follow from the patterns of construction and destruction pairs, which
+at no point can mix without causing any sequence to break all filesystems.
+
+Then move the command with the topmost node to the beginning or the end of
+the sequence we are creating out of the component,
+and recursively start the whole algorithm again on the commands in the component that remain.
+The result of this process is a set of possible orders for each component,
+which are then combined into a set of possible orders for the whole set of commands.
+
+\begin{mydef}{$\orderset{U}$}
+We use $\orderset{U}$ to denote the set of sequences that contain all commands in
+the simple set $U$
+and represent all orders generated by this algorithm.
+\end{mydef}
+
+As a specific case, we can regard a sequence of commands $S$
+as a set and determine its $\orderset{S}$.
+Let us investigate the properties of simple sequences and this set a bit further.
+
+\begin{mydef}{$\extset{S}$.}
+For any sequence $S$ we can consider all sequences that extend it:
+$\extset{S} := \{S'|S\eqext S'\}$
+\end{mydef}
+
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+\begin{mylem}\label{simple_is_max}
+For any simple sequence $S\neq\cbrk$, $\forall T: S\eqext T \Rightarrow S\equiv T$;
+that is, the domains of simple sequences cannot be extended further.
+This is equivalent to $\extset{S} = \{S'|S\equiv S'\}$.
+\end{mylem}
+\begin{proof}
+TODO
+% TODO
+\end{proof}
+
+\begin{mylem}\label{lemma:minextorder}
+% TODO orderset only defined on simple
+For any minimal sequence $S\neq\cbrk$, $\orderset{S} = \extset{S}$.
+\end{mylem}
+\begin{proof}
+TODO
+% TODO
+\end{proof}
+
+\begin{mylem}
+All sequences in $\orderset{S}$ of a simple sequence $S$ are equivalent.
+\end{mylem}
+\begin{proof}
+This follows from \cref{simple_is_max,lemma:minextorder}.
+\end{proof}
+
+TODO: we'll treat sequences as sets and sets as sequences
+once we know they can be applied.
+
+\begin{mylem}\label{lemma:neighbor}
+If $U$ contains commands on both $n$ and $\parent(n)$, then
+there is a $U'\in\orderset{U}$ where they are next to each other.
+\end{mylem}
 
@@
 \end{mylem}
-
-\begin{mydef}{Assertion command.}
-A command is an assertion command if
-for every filesystem it either breaks it or leaves it in the same state.
-In other words, assertion commands have the same input and output type,
-and there must also be only one possible value for their output.
-Accordingly, in our current algebra, $\cbb(n)$ and $\cdd(n)$ are the only two assertion commands,
-and we do not note their output value as it is determined.
-\end{mydef}
-
-\begin{mydef}{Minimal set or sequence.}
-A sequence or set of commands is minimal if it contains at most one command on every node.
-\end{mydef}
-
-\begin{mydef}{Simple set or sequence.}
-A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
-\end{mydef}
 
@@
 
-\begin{myax}\label{ax_assert}
-$\cxy(p,V_Y) \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
-\end{myax}
-
 \begin{myax}\label{worksextpostfix}
@@
 \end{myax}
-
-\section{Ordering commands}
-
-We often encounter the case where we only have a set of commands without a specified order.
-Indeed, it is actually the task of the reconciler to determine whether there is an order
-in which updates from multiple replicas can be applied to a filesystem.
-
-If $U$ is a minimal set of commands
-that we know can be applied to at least one filesystem in some order without breaking it,
-then we can split $U$ into a maximum number of disjunct subsets
-(components) so that the paths of two commands from two different subsets are never directly related.
-If we aim to order the commands in $U$, then we can allow any permutation of 
-the components as the commands in them will commute freely.
-
-Components containing a single command do not pose a problem when determining
-possible orders.
-(Note that $\cff$ can only appear in a component of one.)
-
-In each component that is larger than one, the paths 
-form a rooted ordered tree via the parent--child relationships,
-and the pairs connected by edges will be like pairs in the
-construction or destruction laws.
-To order the commands in a component,
-select the command with the topmost path, so that there would be no command
-on its parent path (if there is one). 
-If the command removes content at this path (it is of the form $\fsregcommand{X}{\empt}$), then it
-needs to follow all other commands in the component, and
-the component is made of destruction pairs.
-Otherwise the command with the topmost component needs to precede other commands
-in the component, and it is made of construction pairs.
-Move the command with the topmost path in place, and
-repeat the process of splitting commands into subsets on the remaining commands
-in the component. Recursively, this way we can determine all allowed orders of the commands.
-
-\begin{mydef}{$\orderset{U}$}
-We use $\orderset{U}$ to denote the set of sequences that contain all commands in $U$
-and represent all orders generated by this algorithm.
-By $\ordered{U}$ we mean an arbitrary sequence in the set.
-\end{mydef}
-
-As a specific case, we can regard a sequence of commands $S$
-as a set and determine its $\orderset{S}$.
-
-\begin{mylem}\label{lemma:neighbour}
-If $U$ contains commands on both $p$ and $\pp$, then
-there is a $U'\in\orderset{U}$ where they are next to each other.
-\end{mylem}
-
-\begin{mydef}
-$\extset{S} := \{S'|S\eqext S'\}$
-\end{mydef}
-
-\begin{mylem}\label{lemma:minextset}
-For any minimal sequence $S$ not equivalent to $\cbrk$, $\extset{S} = \{S'|S\equiv S'\}$.
-\end{mylem}
-\begin{proof}
-This is because as $S$ has at most one command on each path, only equivalence axioms
-can be applied to it.
-\end{proof}
-
-\begin{mylem}\label{lemma:minextorder}
-For any minimal sequence $S$ not equivalent to $\cbrk$,
-$\orderset{S} = \extset{S}$.
-\end{mylem}
-
-% TODO Can these be derived from the algebra?
-
-\section{Soundness}
-
-\section{Completeness}
-
-\begin{mylem}
-\((\forall\FS: S\FS = \empt) \Rightarrow S \equiv \cbrk\)
-\end{mylem}
-
-\section{Update detection}
 
@@
 If $B$ has a command on $q$, then
-from \cref{lemma:neighbour}
+from \cref{lemma:neighbor}
 we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxy$,
@@
 As $S$ is simple and $\works{S}$, from 
-\cref{ax_distantchild_breaks,ax_distantparent_breaks,ax_directchild_breaks,ax_directparent_breaks}
+\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
 we know that these commands can only be on unrelated paths or form a construction or destruction pair.

### 2015-11-22 2000/abstract.tex
Moving source of 2000 paper

--- 2015-09-15 abstract.tex
@@
 created an implementation which was tested on various filesystems. This
-method turned out to be an effective way to create the specification of a
+method turned out to be an effective way of creating the specification of a
 synchronizer since it simplified both the definition and the
@@
 The methods used in the proofs for soundness and completeness are likely
-be usable on other algebras, too. Thus using algebraic approach could make
-it possible to extend the synchronizer to other types of datasystems and
+be usable on other algebras, too. Thus using this algebraic approach could make
+it possible to extend synchronization to other types of datasystems and
 to create a general theory of synchronization in the future.

### 2015-11-22 2000/ack.tex
Moving source of 2000 paper

--- 2015-09-15 ack.tex
@@
 
-%I would like to thank everybody who made it possible for me to write
-%this paper. 
 I would like to thank my mentor, 
@@
 %Engineering and Computer Science).}
-for offering me such a fascinating project and for giving me a hand when
-all the theorems and proofs seemed to be incorrect. I also appreciate the
+for allowing me to work on such a fascinating project,
+and for always being ready to discuss and help me overcome
+whatever difficulties I ran into during my work.
+I also appreciate the
 constructive criticism of my tutor, {Jenny Sendova} 
-who was so kind as to read
-through the drafts several times and tirelessly untangle my absolutely
-confusing complex sentences. I thank {LeeAnn Tzeng} for her remarks
-on the paper which helped me a lot to make it more understandable.
+who kindly read my drafts
+several times tirelessly untangling my 
+sentences fraugh with overcomplicated grammar.
+I thank {LeeAnn Tzeng} for her remarks
+on the paper which helped to make it more accessible.
 

### 2015-11-22 2000/algorithm.tex
Moving source of 2000 paper

--- 2015-09-15 algorithm.tex
@@
 In this section we provide an algorithm for reconciliation. The reconciler
-algorithm takes sequences leading from the original filesystem to the
+algorithm takes the sequences leading from the original filesystem to the
 replicas (\(S_1, S_2, \ldots S_n\)) and creates sequences of commands for
@@
 filesystems as close as possible.
-%%%\(S_i^*\) contains all
-%%%non--conflicting commands from \(S_1, S_2, \ldots S_n\) which is not
-%%%already applied to \(S_i\). 
-%%%\begin{notrsi}
-%%%We also would like to be sure that if there
-%%%are no conflicting commands, then after synchronization, all replicas
-%%%should be the same.
-%%%\end{notrsi}
 
-%%%Thus, 
 When creating the algorithm, we keep in mind the following:\\
@@
 
-\medskip
-{\small{
+\medskip\noindent{\small{
 Why do we need the last criterion? Consider the following case: in the
-original replica we had \(O(\pi)=\cfile{X}\). 
+original replica we had \(O(\pi)=\cfile{W}\). 
 We modified replica \(A\) with the following
-commands: \(edit(\pi,\cdir{Y}); create(\pi\cdot p,\cfile{W})\).
-Replica \(B\) was modified by the command \(edit(\pi,\cfile{Z})\).
-Now \(edit(\pi,\cdir{Y})\) and \(edit(\pi,\cfile{Z})\) are
-conflicting commands, so we cannot apply \(edit(\pi,\cdir{Y})\) to replica
-\(B\). But that way, we cannot propagate
-\(create(\pi\cdot p,\cfile{W})\) to it either.
-\remark{However, if \(O(\pi)\) was a directory, it could be.}
+commands: \(edit(\pi,\cdir{X}); create(\pi\cdot p,\cfile{Z})\).
+Replica \(B\) was modified by the command \(edit(\pi,\cdir{Y})\).
+A third replica \(C\) was not modified.
+Now \(edit(\pi,\cdir{X})\) and \(edit(\pi,\cdir{Y})\) are
+conflicting commands. \(create(\pi\cdot p,\cfile{Z})\) has no conflicts.
+Although we could propagate this \(create\) to replica \(B\), we
+cannot apply it to replica \(C\) as we would not know whether to apply
+\(edit(\pi,\cdir{X})\) from \(A\) or \(edit(\pi,\cdir{Y})\) from \(B\) to
+it. I thank Bill Zissimopoulos for calling my attention to the third
+condition in the reconciliation algorithm. --- EC, 2015
 }}\medskip
 
-%We also need to determine which commands must precede another
-%one. Clearly
-A
-command \(C_1\) must precede command \(C_2\) iff 
-\(\neg(C_1; C_2\eqifnbr C_2; C_1)\), it originally preceded \(C_2\),
+A command \(C_1\) must precede command \(C_2\) iff 
+\(C_1; C_2\neqifnbr C_2; C_1\), it originally preceded \(C_2\),
 and they appear in the same sequence \(S_i\). 
@@
 Now, in order to preserve the order of commands in sequences 
-\(S_1, S_2, \ldots S_n\), we define the algorithm as follows:
+\(S_1, S_2, \ldots S_n\), we define the reconciliation algorithm as follows:
 \begin{notrsi}
@@
 \item Detect conflicting commands between sequences
-\item Detect must--follow conflicting commands
+\item Detect commands which must follow conflicting commands
 \item Omit these commands from all sequences
-\item Omit commands in \(S_i\) from all other sequences
 \item Define \(S_i^*\) as 
@@
 FOR every sequence \(S\sb{i}\)
-  FOR each command \(C\in S\sb{i}\)  
+  FOR each command \(C\in{S}\sb{i}\)  
     FOR every sequence \(S\sb{j}\)
@@
 
-We can get the sequence of conflicting commands using a similar
-algorithm. The reconciler produces two sequences for every replica: the
+We can get sequences of conflicting commands using a similar
+algorithm. This way the reconciler can produce two sequences for every replica: the
 first one (\(S_i^*\)) can be applied to the replica immediately, while
-the second one (conflicting commands, \(S_i^C\)) needs the user's or
+the second one containing the conflicting commands (\(S_i^C\)) needs the user's or
 other algorithms' help to be resolved.

### 2015-11-22 2000/intro.tex
Moving source of 2000 paper

%% Introduction
\section{Introduction}

If we have multiple copies (called \emph{replicas}) of a filesystem or a
part of a filesystem (for example on a laptop and on a desktop
computer), it is often the case that changes are made to each
replica independently and as a result they no longer contain the same
information. In that case, a \emph{file synchronizer} is used to make them
similar (consistent) again, without losing any information.

The goal of a file synchronizer is to \emph{detect conflicting updates}
and \emph{propagate non--conflicting updates on each replica.} Due to the
various cases of file updates and the various behaviors of filesystem
commands it is difficult to give a complete and correct definition of its
behavior.

It can be helpful in solving this problem if we have a
formalized mathematical model for describing file synchronization.

We investigated algebraic models of synchronization in a specific case to
see the properties of such a system and the method of proving theorems in
it, which will hopefully aid us to create a general theory of
synchronization based on algebraic structures in the future. This specific
case was the synchronization of filesystems.

In the paper we develop an algebraic representation of filesystem
commands. Then we show that this model is both complete and sound,
and we define the expected behavior of a file synchronizer and
create its specification with the help of our algebra.

This method will
hopefully simplify the specification as well as the implementation of the
synchronizer, and it might make it possible to extend the synchronizer to
other types of datasystems, such as mail folders or databases.

\subsection{The main idea of synchronization}

In general, there are two phases of synchronization:
\emph{update detection}, when the program recognizes where updates have
been made since the last synchronization, and \emph{reconciliation}, when
it combines updates to yield a new, synchronized version of each replica.
If there are no conflicting updates, then at the end of the
synchronization the replicas will be the same. Otherwise, a synchronizer
may leave them unchanged at paths where conflicts occurred and warn the
user.
In this paper,
we focus on the commands that were applied to these replicas while they
were modified independently, as the main aim of a synchronizer is to
propagate and perform
the most possible commands on all replicas.

%\remark{Explanation why we DO need O?}
Let us introduce some notation. We have the original system, \(O\); 
and the current replicas \(R_1, R_2, \ldots R_n\).
Let us assume that we already know the sequences of commands which have been applied to
\(O\) in each replica (for example, from the update detector). These
sequences are
\(S_1, S_2, \ldots S_n\). The synchronizer algorithm will neeed to provide us
with new sequences of commands for each replica (\(S_1^*, S_2^*, \cdots S_n^*\))
that will move each
replica to a common state \(O'\), or as close to it as possible.
%, that is, 
%\(S_1^*R_1=S_2^*R_2=\cdots=S_n^*R_n=O'\).

In order to determine each sequence \(S_i^*\), we take all commands
applied
to the systems (\(S_1\cup S_2\cup \cdots\cup S_n\)) and omit commands
in \(S_i\) which have already been applied to replica \(R_i\).

However, this way we only gain a \emph{set} of commands which we
need to order to be able to apply the commands to the
system. It is possible that some orders cause errors in a filesystem
(for example, trying to remove a directory before removing the files in
it). It is also possible that not all error--free orders have the same
effect on the filesystem. For example, modifying the contents of a file to
``xxx'' and modifying them to ``yyy'' in a different replica are not commutable commands: they
leave the system in different states if applied in different order.
In this case the synchronizer cannot synchronize the systems fully, since
``last modification wins'' is not a preferable solution in every case.  
Therefore, a better aim of the synchronizer is to find commands for which 
\emph{all error--free orders have
the same effect} and apply these to the system.

The reason we may have two differently ordered sequences of commands which
do not lead a system to the same state is that we have incommutable pairs
of commands in them. This is because if all pairs of commands
commuted (that is, a pair of commands \(C_1; C_2\) had the same effect on
a system as \(C_2; C_1\)) then clearly one of the sequences could be
transformed into the other one by commuting commands
without any change in the effect of the sequence on the system.

Because of this, we focus on the commutability of pairs of commands.  
We define this property with the help of an algebraic 
proof system on commands.% for commutivity. %%%

%\subsection{Synchronizing filesystems}
%This specific case was the synchronization of a filesystem.

### 2015-11-24 2015/paper.tex
Finalizing text

@@
 \newcommand{\recb}{\recchar{B}{A}{}}
-\newcommand{\recaset}{\recchar{A}{B}{*}}
-\newcommand{\recbset}{\recchar{B}{A}{*}}
 
@@
 
-\section{Ordering commands}
+\section{Ordering commands}\label{ordering}
 
@@
 
+It follows from the algorithm that:
+\begin{mylem}\label{lemma:neighbor}
+If $U$ contains commands on both $n$ and $\parent(n)$, then
+there is a $U'\in\orderset{U}$ where they are next to each other.
+\end{mylem}
+
 As a specific case, we can regard a sequence of commands $S$
@@
 \end{mydef}
-
-% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
@@
 
-TODO: we'll treat sequences as sets and sets as sequences
-once we know they can be applied.
-
-\begin{mylem}\label{lemma:neighbor}
-If $U$ contains commands on both $n$ and $\parent(n)$, then
-there is a $U'\in\orderset{U}$ where they are next to each other.
-\end{mylem}
+It follows from this that given a simple set,
+we can simply assume that it has an order.
+Accordingly, we will at times treat not only sequences as sets,
+but simple sets as sequences.
+
+\section{Reconciliation}
+
+If we start with two copies of the filesystem $\FS$,
+and two different sequences are applied to the copies to yield $\FS_A:=A\FS$
+and $\FS_B:=B\FS$, then our aim is to define sequences of commands $\reca$ and $\recb$
+so that $\recb\FS_A$ and $\reca\FS_B$ would be as close to each other as possible.
+
+We work based on the assumption that to achieve this, we need
+to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
+As some commands may have been applied to both filesystems, our first approximation
+is $\reca = A\setminus B$ and $\recb = B\setminus A$
+(in some suitable order).
+This, however, will break both filesystems if there have been incompatible updates
+in $A$ and $B$. 
+Our aim is therefore to provide an algorithm that selects the commands 
+$\reca \subset A\setminus B$
+and $\recb \subset B\setminus A$ 
+so that $\reca\FS_B\neq\fsbroken$ and $\recb\FS_A\neq\fsbroken$,
+and show that these are the longest sequences with this property, that is,
+adding any command left out from $\reca$ or $\recb$ will break the filesystems.
+
+We assume that $A$ and $B$ are returned by an update detector,
+and so they are simple sequences.
+(Otherwise, they can be simplified to become simple sequences.)
+We also assume that $\FS_A$ and $\FS_B$ are not broken.
+With these assumptions,
+we can now define independent sequences and
+our reconciliation algorithm.
+
+\begin{mydef}{Independent commands, sequences and sets.}
+For two commands $\cxy$ and $\czw$ we write $\cxy\indep\czw$ if $\cxy\cc \czw\equiv\czw\cc \cxy\nequiv\cbrk$.
+For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
+$\forall a\in A \mbox{and~} \forall b\in B: a\indep b$.
+\end{mydef}
+
+\begin{mydef}{Reconciliation}\label{def:reconciliation}
+\begin{align*}
+\reca = \{c| & \\
+& c\in A\setminus B \\
+& \wedge \\
+& \forall c'\in B\setminus A: c\indep c'\\
+\} &
+\end{align*}
+
+In other words, the sequence $\reca$ we apply to $\FS_B$ consists of all commands from $A\setminus B$
+that are independent of every command in $B\setminus A$.
+The order of commands in the sequence can be determined using the algorithm described in
+\cref{ordering} as any subset of $A$ is also simple.
+\end{mydef}
+
+Now we prove that $\reca\FS_B\neq\fsbroken$, and, in general:
+
+% 'Works'
+% -------
 
@@
 \end{mylem}
-
-\begin{mydef}{Independent commands, sequences and sets.}
-For two commands $\cxy$ and $\czw$ we write $\cxy\indep\czw$ if $\cxy\cc \czw\equiv\czw\cc \cxy\nequiv\cbrk$.
-% TODO use w() instead of nequiv break
-For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
-$\forall a\in A \mbox{and~} \forall b\in B: a\indep b$.
-\end{mydef}
 
@@
 \end{myax}
-
-\section{Reconciliation}
-
-If we start with two copies of the filesystem $\FS$,
-and two different sequences are applied to the copies to yield $\FS_A:=A\FS$
-and $\FS_B:=B\FS$, then our aim is to define sequences of commands $\reca$ and $\recb$
-so that $\recb\FS_A$ and $\reca\FS_B$ would be as close to each other as possible.
-
-We work based on the assumption that to achieve this, we need
-to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
-As some commands may have been applied to both filesystems, our first approximation
-is $\reca = \ordered{A\setminus B}$ and $\recb = \ordered{B\setminus A}$.
-This, however, will break both filesystems if there have been incompatible updates
-in $A$ and $B$. 
-Our aim is therefore to provide an algorithm that selects the commands 
-$\reca = \ordered{\recaset}$  where $\recaset \subset A\setminus B$
-and $\recb = \ordered{\recbset}$ where $\recbset \subset B\setminus A$ 
-so that $\reca\FS_B\neq\fsbroken$ and $\recb\FS_A\neq\fsbroken$,
-and show that these are the longest sequences with this property, that is,
-adding any command left out from $\reca$ or $\recb$ will break the filesystems.
-
-We assume that $A$ and $B$ are returned by an update detector,
-and so they are simple sequences.
-We also assume that $\FS_A$ and $\FS_B$ are not broken and therefore $\works{A,B}$.
-
-Our reconciliation algorithm is as follows.
-
-\begin{mydef}{Reconciliation}\label{def:reconciliation}
-\begin{align*}
-\recaset = \{c| & \\
-& c\in A\setminus B \\
-& \wedge \\
-& \forall c'\in B\setminus A: c\indep c'\\
-\} & \\
-\reca = \ordered{\recaset}&
-\end{align*}
-
-In other words, the sequence $\reca$ we apply to $\FS_B$ consists of all commands from $A\setminus B$
-that independent from every command in $B\setminus A$.
-\end{mydef}
-
-Now we prove that $\reca\FS_B\neq\fsbroken$, and, in general:
 

### 2015-11-25 2015/paper.tex
Finalizing text and references

@@
 \crefname{myax}{axiom}{axioms}
-% \creflabelformat{myax}{A#2#1#3}
 
@@
 \crefname{mylem}{lemma}{lemmas}
-% \creflabelformat{mylem}{L#2#1#3}
 
@@
 
+\newtheorem{mycor}{Corollary}
+\crefname{mycor}{corollary}{corollaries}
+
+% TODO delete:
 \newtheorem{myrul}{Rule}
 \crefname{myrul}{rule}{rules}
-% \creflabelformat{myrul}{R#2#1#3}
 
@@
 and a set of possible contents $\setv$ as its codomain:
-\[ \FS : \setp \rightarrow \setv \] 
+\[ \FS : \setn \rightarrow \setv \] 
 In our model, $\setn$ contains all possible nodes, including the ones where there is no file or directory,
@@
 We write $n\unrel m$, or ``$n$ and $m$ are unrelated'' if $n\not\descendant m$ and $n\not\ancestor m$
-and $n\new m$.
+and $n\neq m$.
 \end{mydef}
@@
 \begin{mydef}{Minimal set or sequence.}
-% TODO Don't introduce?
 A sequence or set of commands is minimal if it contains at most one command on every node.
@@
 
+\medskip
+
 We can now define our algorithm to generate orders of sets of commands.
@@
 in which commands from separate components mix and overlap
-(but where the possible orders determined for the components are respected).
+(but where the possible orders determined for commands inside the components are respected).
 
@@
 that is, the domains of simple sequences cannot be extended further.
-This is equivalent to $\extset{S} = \{S'|S\equiv S'\}$.
+This is equivalent to the proposition that $\extset{S} = \{S'|S\equiv S'\}$.
 \end{mylem}
@@
 For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
-$\forall a\in A \mbox{and~} \forall b\in B: a\indep b$.
+$\forall a\in A \mbox{~and~} \forall b\in B: a\indep b$.
 \end{mydef}
@@
 The order of commands in the sequence can be determined using the algorithm described in
-\cref{ordering} as any subset of $A$ is also simple.
-\end{mydef}
-
-Now we prove that $\reca\FS_B\neq\fsbroken$, and, in general:
-
-% 'Works'
-% -------
-
-\begin{mydef}{Inverse commands and sequences.}
-The inverse of command $\cxy(p,V_Y)$ is $\cxy(p,V_Y)^{-1} = \cyx(p,V_X)$
-where $V_X$ is an arbitrary value from $\setvx{X}$.
-The inverse of sequence $S$, $S^{-1}$, consists of the inverses of the commands in $S$
-in reverse order.
-\end{mydef}
-
-\begin{mylem}\label{r_invmove}
-\[ \infer{\worksc{S\cc A}{B}}{\worksc{A}{S^{-1}\cc B}} \]
-To see the soundness of this rule...
-Sequences are bijections on filesystems over type-equality.
-TODO: $A,S,B$ need to be simple?
-\end{mylem}
-
-\begin{myrul}\label{r_indep_combine}
-\[ \inferrr{\worksc{T}{S}}{\worksc{U}{S}}{T\indep U}{\worksc{T\cc U}{S}} \]
-To see the soundness of this rule...
-\end{myrul}
-
-\begin{mylem}\label{indep_prefix_combine}
-\[ \inferrr{\worksc{A\cc B}{S}}{\worksc{A\cc C}{S}}{B\indep C}{\worksc{A\cc B\cc C}{S}} \]
-\end{mylem}
-\begin{proof}
-From \cref{r_invmove,r_indep_combine}
-TODO reverse of \cref{r_invmove} needed
-\end{proof}
-
-\begin{myax}\label{worksextpostfix}
-$\worksc{A}{A\cc S}$ where $A$ and $S$ are arbitrary sequences of commands
-\end{myax}
-
-% Introducing 'works'
-% -------------------
-
-So that we can formalise statements (TODO) needed to prove this,
+\cref{ordering} as any subset of $A$ is also simple,
+and $\recb$ can be obtained in a similar way by reversing $A$ and $B$.
+\end{mydef}
+
+We would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
+that is, without loss of generality,
+\[ \reca\FS_B\neq\fsbroken. \]
+So that we can formalise statements needed to prove this,
 let us introduce two relations that describe under what conditions
 sequences of commands work, that is, do not break a filesystem.
+
+% Works
+% -----
 
@@
 % inference rules:
-We also see that $\works{A} \Leftrightarrow A\nequiv \cbrk$. 
+We also know that $\works{A} \Leftrightarrow A\nequiv \cbrk$. 
 \end{mydef}
@@
 As above, the order of the sequences in the sets is not relevant.
-% inference rules:
-It is easy to see that 
+\end{mydef}
+
+% An inference rule in the algebra
 % $\worksc{X}{X}$ is always true for any set of sequences $X$,
+
+It is easy to see that the following corollaries are true:
+
+\begin{mycor}
+% An inference rule in the algebra
 $B\eqext A \Rightarrow \worksc{A}{B}$
-and that this relation can be chained:
+\end{mycor}
+
+\begin{mycor}\label{worksextpostfix}
+% An inference rule in the algebra
+$\forall A,S: \worksc{A}{A\cc S}$
+\end{mycor}
+
+\begin{mycor}
+% An inference rule in the algebra
+$\worksc{S}{T}$ can be chained:
 $ \worksc{A_1,\ldots,A_k}{B_1,\ldots,B_l} \wedge \worksc{C_1,\ldots,C_j}{A_1} \Rightarrow \worksc{A_1,\ldots,A_k,C_1,\ldots,C_j}{B_1,\ldots,B_l} $
-\end{mydef}
+\end{mycor}
 
@@
 
+\begin{mylem}\label{r_indep_combine}
+% An inference rule in the algebra
+\[ \worksc{T}{S} \wedge \worksc{U}{S} \wedge T\indep U \Rightarrow \worksc{T\cc U}{S} \]
+\end{mylem}
+\begin{proof}
+% TODO Proof
+TODO
+\end{proof}
+
+\medskip
+
+We continue by defining inverse commands and sequences
+which allow us to move parts of sequences between the
+two sets of $\worksc{S}{T}$.
+
+\begin{mydef}{Inverse commands and sequences.}
+The inverse of command $\cxy(n,V_Y)$ is $\cxy(n,V_Y)^{-1} = \cyx(n,V_X)$
+where $V_X$ is an arbitrary value from $\setvx{X}$.
+We write $S^{-1}$ for the inverse of sequence $S$, which consists of the inverses of the commands in $S$
+in reverse order.
+%
+Clearly, $(S^{-1})^{-1}\equiv S$ for any sequence.
+\end{mydef}
+
+\begin{mylem}\label{r_invmove}
+\begin{gather*}
+\worksc{B\cc A}{S} \Rightarrow \worksc{A}{B^{-1}\cc S} \\
+\worksc{A}{B\cc S} \Rightarrow \worksc{B^{-1}\cc A}{S}
+\end{gather*}
+% TODO Proof
+TODO.
+Sequences are bijections on filesystems over type-equality.
+TODO: $A,S,B$ need to be simple?
+\end{mylem}
+
+\begin{mylem}\label{indep_prefix_combine}
+\[ \worksc{A\cc B}{S} \wedge \worksc{A\cc C}{S} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{S} \]
+\end{mylem}
+\begin{proof}
+Based on \cref{r_invmove} we know
+$\worksc{B}{A^{-1}\cc S}$ and $\worksc{C}{A^{-1}\cc S}$,
+and from \cref{r_indep_combine} we know
+$\worksc{B\cc C}{A^{-1}\cc S}$. Applying the second line of \cref{r_invmove} we get
+$\worksc{(A^{-1})^{-1}\cc B\cc C}{S}$, which proves our lemma as $(A^{-1})^{-1}\equiv A$.
+\end{proof}
+
+\medskip
+
+% Correctness of reconciliation
+% -----------------------------
+
+We are now ready to prove that the proposed algorithm for reconciliation is correct,
+that is, applying its result is not going to break the replicas.
+We reformulate the original proposition, $\reca\FS_B\neq\fsbroken$,
+based on $\FS_B=B\FS$ and so we aim to prove that
+$B\cc\reca$ works wherever $A$ and $B$ work:
+
 \begin{myth}
@@
 \end{myth}
-
-This is trivial unless $\works{A,B}$.
+where, to restate the definition,
+{ % scope
+\renewcommand{\themydef}{\ref{def:reconciliation}}
+\begin{mydef}
+\begin{align*}
+\reca = \{c| & \\
+& c\in A\setminus B \\
+& \wedge \\
+& \forall c'\in B\setminus A: c\indep c'\\
+\}. &
+\end{align*}
+\end{mydef}
+} % scope
+
+This is trivial unless $\works{A,B}$, so we assume that it is true.
+Let us first investigate the part of $A$ and $B$ that is excluded from
+$\reca$: their intersection.
 
@@
 either of them works on:
-$\worksc{\ordered{A\cap B}}{A}$, and, by symmetry, for $B$.
+$\worksc{A\cap B}{A}$, and, by symmetry,
+$\worksc{A\cap B}{B}$.
 \end{mylem}
@@
 Mark all commands in $A$ that also appear in $B$.
-Then there is an $A'$ in $\orderset{A}$ in which the marked commands are at the beginning.
+Then there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.
+We show $A$ can be transformed via equivalences so that this would be true.
+Our proposition is that if the marked commands are not at the beginning, then
+the sequence contains an unmarked command followed by a marked command.
+We show that these can be reversed resulting in an equivalent sequence.
+Then, by repeating this process similarly to bubble sorting, we can generate 
+a suitable $A'$.
 
@@
 
-TODO: unmarked-marked can be reversed -- but induction is wrong
-
-We show $A$ can be transformed via equivalences so that this would be true,
-by induction on the number of non-marked commands preceding the last marked command.
-If it is 0, no transformation is needed.
-For the induction step, consider the last marked command preceded by a non-marked command,
-and the non-marked command itself.
+Let us consider therefore the marked command preceded by an unmarked command in $A$.
+and let the marked command be $\cxy(n, V_Y)$, 
+and the preceding unmarked command be $\czw(m, V_W)$.
 As $A$ is a simple command and $\works{A}$, from 
-\cref{ax_distantchild_breaks,ax_distantparent_breaks,ax_directchild_breaks,ax_directparent_breaks}
+\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
 we know that these commands can only be on unrelated paths or form a construction or destruction pair.
 In the first case, swapping the commands results in a sequence equivalent to $A$,
-with the number on relevant non-marked commands reduced by one.
-In the last two cases,
-either $q=\parent(p)$ or $p=\parent(q)$.
-
-Let the marked command be $\cxy(p, V_Y)$ and the preceding unmarked command in $A$ be $\czw(q, V_W)$.
-
-If $B$ has a command on $q$, then
+and we show that the last two cases are impossible as they would lead to contradiction.
+
+In these cases, either $m=\parent(n)$ or $p=\parent(m)$.
+If $B$ has a command on $m$, then
 from \cref{lemma:neighbor}
-we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxy$,
-and from \cref{lemma:minextset,lemma:minextorder} we know that $B'\equiv B$.
-% TODO Use when describing ordering:
-Considering the eight construction and destruction pairs we see that the command
-on the parent path determines which group the pair belongs to.
-This in turn determines whether the command on the child path must
+we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxy$ (also in $B$),
+and from \cref{simple_is_max,lemma:minextorder} we know that $B'\equiv B$.
+When describing our ordering algorithm in \cref{ordering} we saw
+that the command on the parent path deremines whether a pair of commands
+is a construction or destruction pair,
+and that this, in turn, determines whether the command on the child path must
 precede or follow the other command as otherwise the sequence would break all filesystems.
-This argument holds for both $A$ and $B$, and so the command on $q$ must be on
-the same side of the command on $p$ in both sequences.
-
-If $B$ has no command on $q$, then let $B'$ be $B$, but with an extra command added to it just before $\cxy$
-according to \cref{ax_child_assert,ax_parent_assert}, from which we know
-that $B'\equiv B$.
+This argument holds for both $A$ and $B$, and so the command on $m$ must be on
+the same side of the command on $n$ in both sequences.
+
+If $B$ has no command on $m$, then let $B'$ be $B$, 
+but with an extra command added to it just before $\cxy$
+according to \cref{ax_child_assert,ax_parent_assert}, 
+from which we know that $B'\equiv B$.
 We also know that $B'$ is still minimal (but no longer simple).
 
-We therefore have a minimal $B'$ which has a command on $q$ just before $\cxy(p, V_Y)$ and $B'\equiv B$.
-Let this command on $q$ be $\cqr(q, V_R)$.
+In either case, therefore,
+we have a minimal $B'$ which has a command on $m$ just before $\cxy(n, V_Y)$ and $B'\equiv B$.
+Let this command on $m$ be $\cqr(m, V_R)$.
 \begin{gather*}
@@
 
-As $\works{A,B}$ and so $\works{A,B'}$ (via \cref{r_eq_ex,r_ex_w,r_w_w}), 
+As $\works{A,B}$ and so $\works{A,B'}$, 
 from \cref{worksinputmatch}
@@
 Going back to the construction and destruction pairs we see that the output type of the first command
-is always the same, and it is either $D$ or $\empt$ depending on the relationship between $p$ and $q$.
-Therefore $R=W$ and $\cqr(q, V_R)=\czw(q, V_W)$
+is always the same, and it is either $D$ or $\empt$ depending on the relationship between $n$ and $m$.
+Therefore $R=W$ and $\cqr(m, V_R)=\czw(m, V_W)$
 as $|\setd|=|\setb|=1$. 
-If $B$ originally had a command on $q$,
+If $B$ originally had a command on $m$,
 this is a contradiction as $\czw$ was not marked, but we see it must also be in $B'$ and therefore in $B$.
-If $B$ had no command on $q$,
-this is a contradiction because the command on $q$ in $B'$ is an assertion command, so $Z=Q=R=W$, 
+If $B$ had no command on $m$,
+this is a contradiction because the command on $m$ in $B'$ is an assertion command, so $Z=Q=R=W$, 
 but $A$ contained no assertion commands.
@@
 from \cref{worksextpostfix}
-$\worksc{\ordered{A\cap B}}{A}$ and by symmetry $\worksc{\ordered{A\cap B}}{B}$.
+$\worksc{A\cap B}{A}$ and by symmetry $\worksc{A\cap B}{B}$.
 \end{proof}
@@
 We would like to prove that $\worksc{B\cc \reca}{A,B}$.
-From above we know that this is equivalent to
-$\worksc{\ordered{A\cap B}\cc \ordered{B\setminus A}\cc \reca}{A,B}$.
-As we already know that $\reca\indep B\setminus A$
-and that $\worksc{\ordered{A\cap B}\cc \ordered{B\setminus A}}{A,B}$
+From the above we know that this is equivalent to
+$\worksc{(A\cap B)\cc (B\setminus A)\cc \reca}{A,B}$.
+As we already know that $\reca\indep (B\setminus A)$
+and that $\worksc{(A\cap B)\cc(B\setminus A)}{A,B}$
 (as $\worksc{B}{A,B}$),
@@
 we only need to prove that
-$\worksc{\ordered{A\cap B}\cc \reca}{A,B}$.
-
-\newcommand{\acbi}{\ordered{A\cap B}^{-1}}
-\newcommand{\amb}{A\setminus B}
-\newcommand{\bma}{B\setminus A}
+$\worksc{(A\cap B)\cc \reca}{A,B}$.
+
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+\newcommand{\acbi}{(A\cap B)^{-1}}
+\newcommand{\amb}{(A\setminus B)}
+\newcommand{\bma}{(B\setminus A)}
 Using \cref{r_invmove} we can rephrase this as
@@
 so that all commands in $S^*$ would be at its beginning.
-If so then based on \cref{worksextpostfix}
-$\worksc{S^*}{C_1,\ldots,C_n}$ as $\worksc{S'}{C_1,\ldots,C_n}$.
+If so, then based on \cref{worksextpostfix}
+$\worksc{S^*}{C_1,\ldots,C_n}$ as $\worksc{S'}{C_1,\ldots,C_n}$ and .
 

### 2015-11-25 2015/paper.tex
Finalising text done

@@
 \newcommand{\descendant}{\prec}
+\newcommand{\descendantEq}{\preceq}
 \newcommand{\ancestor}{\succ}
+\newcommand{\ancestorEq}{\succeq}
 
@@
 
-\newcommand{\works}[1]{{\mathbf{w}}({#1})}
-\newcommand{\worksc}[2]{{\mathbf{w}}({#1}|{#2})}
+\newcommand{\workssign}{\mathbf{w}}
+\newcommand{\works}[1]{\workssign({#1})}
+\newcommand{\worksc}[2]{\workssign({#1}|{#2})}
 
@@
 \newcommand{\ordered}[1]{#1}
+\newcommand{\seqset}[1]{\underline{#1}} % Set of sequences
 
@@
 \newcommand{\reca}{\recchar{A}{B}{}} % Reconciled from A
-\newcommand{\recb}{\recchar{B}{A}{}}
-
+\newcommand{\recb}{\recchar{B}{A}{}} % Reconciled from B
+
+% TODO delete:
 \newcommand{\infer}[2]{\begin{array}{c}{#1}\\\hline{#2}\end{array}}
@@
 We write $n\descendant m$ if $n$ is the ancestor of $m$ ($n=\parent^n(m)$). % TODO (the transitive closure of the $\parent$ relation)
+We write $n\descendantEq m$ if $n\descendant m$ or $n=m$.
 \end{mydef}
@@
 \begin{mydef}{$n\unrel m$.}
-We write $n\unrel m$, or ``$n$ and $m$ are unrelated'' if $n\not\descendant m$ and $n\not\ancestor m$
-and $n\neq m$.
+We write $n\unrel m$, or ``$n$ and $m$ are unrelated'' if $n\not\descendantEq m$ and $n\not\ancestorEq m$.
 \end{mydef}
@@
 For two sets of sequences, $\worksc{A_1,A_2,\ldots,A_k}{B_1,B_2,\ldots,B_l}$ means that 
-all of $A_1,A_2,\ldots,A_k$ work where all of $B_1,B_2,\ldots,B_l$ work,
+all of $A_1,\ldots,A_k$ work where all of $B_1,\ldots,B_l$ work,
 that is,
@@
 
+\begin{mydef}{Sets of sequences.}
+For brevity, we will use $\seqset{S}$ to note an arbitrary set of sequences,
+and $A\cc\seqset{S}$ to note the set of sequences $\{A\cc S|S\in\seqset{S}\}$.
+\end{mydef}
+
+It is easy to see that the following corollaries are true:
+
 % An inference rule in the algebra
 % $\worksc{X}{X}$ is always true for any set of sequences $X$,
-
-It is easy to see that the following corollaries are true:
 
@@
 % An inference rule in the algebra
-$\worksc{S}{T}$ can be chained:
-$ \worksc{A_1,\ldots,A_k}{B_1,\ldots,B_l} \wedge \worksc{C_1,\ldots,C_j}{A_1} \Rightarrow \worksc{A_1,\ldots,A_k,C_1,\ldots,C_j}{B_1,\ldots,B_l} $
+$\workssign$ can be chained:
+if $A_1\in\seqset{A}$, then
+$ \worksc{\seqset{A}}{\seqset{B}} \wedge \worksc{\seqset{C}}{A_1} \Rightarrow \worksc{\seqset{A}\cup\seqset{C}}{\seqset{B}} $
 \end{mycor}
+
+We will also prove the following lemmas.
 
@@
 % An inference rule in the algebra
-\[ \worksc{T}{S} \wedge \worksc{U}{S} \wedge T\indep U \Rightarrow \worksc{T\cc U}{S} \]
+\[ \worksc{T}{\seqset{S}} \wedge \worksc{U}{\seqset{S}} \wedge T\indep U \Rightarrow \worksc{T\cc U}{\seqset{S}} \]
 \end{mylem}
@@
 
+\begin{mylem}\label{unrelated_is_independent}
+Two different commands that are not assertion commands are independent iff the nodes they change are unrelated:
+$\cxy(n,V_Y)\indep\czw(m,V_W) \Leftrightarrow n\unrel m$ 
+if $\cxy(n,V_Y)\neq\czw(m,V_W)$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
+\end{mylem}
+\begin{proof}
+We proceed in two steps; first, we prove that
+$\cxy(n,V_Y)\not\indep\czw(m,V_W) \wedge n\unrel m$ would lead to contradiction.
+By definition, if the two commands are not independent, then one of the following holds:
+\begin{itemize}
+\item $\czw(m,V_W)\cc \cqr(o,V_R) \equiv\cbrk$
+\item $\cqr(o,V_R)\cc \czw(m,V_W) \equiv\cbrk$
+\item $\czw(m,V_W)\cc \cqr(o,V_R) \nequiv \cqr(o,V_R)\cc \czw(m,V_W)$
+\end{itemize}
+However, from \cref{ax_separate_commute,ax_separate_nobreaks} we also know that
+if $n\unrel m$ then none of the above can be true.
+
+Next, we prove that
+$\cxy(n,V_Y)\indep\czw(m,V_W) \wedge n\not\unrel m$ would lead to contradiction.
+As $n\not\unrel m$
+we know that $n=m$, $n\descendant m$ or $m\descendant n$.
+
+If $n=m$, then from \cref{ax_same_breaks} we know $Y=Z$ and $W=X$
+as otherwise the commands, in one order or the other, would break all filesystems
+and they could not be independent.
+The commands are not assertion commands, and so from \cref{ax_same_singlec}
+we know that $\cxy(n,V_Y)\cc\czw(n,V_W)\equiv\czw(n,V_W)\cc\cxy(n,V_Y)$ can only happen if $Y=W$ and $V_Y=V_W$.
+Therefore $X=Y=Z=W$ which is only possible if both commands are $\cff$ and have the same
+output value. This, however, contradicts our assumption that they are different.
+
+If $n\descendant m$ or $m\descendant n$, then
+from \cref{ax_distantrel_breaks} we know that if they are not directly related,
+then $\cxy(n,V_Y)\cc\czw(m,V_W)$ breaks all filesystems, and they cannot be independent.
+From the construction and destruction pairs and 
+\cref{ax_directchild_breaks,ax_directparent_breaks} we also see that
+even if they are directly related, either
+$\cxy(n,V_Y)\cc\czw(m,V_W)$ or $\czw(m,V_W)\cc\cxy(n,V_Y)$ 
+breaks all filesystems, so they again cannot be independent.
+\end{proof}
+
 \medskip
@@
 which allow us to move parts of sequences between the
-two sets of $\worksc{S}{T}$.
+condition and consequence parts of $\workssign$.
 
@@
 \begin{gather*}
-\worksc{B\cc A}{S} \Rightarrow \worksc{A}{B^{-1}\cc S} \\
-\worksc{A}{B\cc S} \Rightarrow \worksc{B^{-1}\cc A}{S}
+\worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \\
+\worksc{\seqset{A}}{B\cc \seqset{S}} \Rightarrow \worksc{B^{-1}\cc \seqset{A}}{\seqset{S}}
 \end{gather*}
@@
 \begin{mylem}\label{indep_prefix_combine}
-\[ \worksc{A\cc B}{S} \wedge \worksc{A\cc C}{S} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{S} \]
+\[ \worksc{A\cc B}{\seqset{S}} \wedge \worksc{A\cc C}{\seqset{S}} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{\seqset{S}} \]
 \end{mylem}
@@
 Based on \cref{r_invmove} we know
-$\worksc{B}{A^{-1}\cc S}$ and $\worksc{C}{A^{-1}\cc S}$,
+$\worksc{B}{A^{-1}\cc \seqset{S}}$ and $\worksc{C}{A^{-1}\cc \seqset{S}}$,
 and from \cref{r_indep_combine} we know
-$\worksc{B\cc C}{A^{-1}\cc S}$. Applying the second line of \cref{r_invmove} we get
-$\worksc{(A^{-1})^{-1}\cc B\cc C}{S}$, which proves our lemma as $(A^{-1})^{-1}\equiv A$.
+$\worksc{B\cc C}{A^{-1}\cc \seqset{S}}$. Applying the second line of \cref{r_invmove} we get
+$\worksc{(A^{-1})^{-1}\cc B\cc C}{\seqset{S}}$, which proves our lemma as $(A^{-1})^{-1}\equiv A$.
 \end{proof}
@@
 
-\begin{mylem}
+\begin{mylem}\label{can_move_intersection}
 Let $A$ and $B$ be two simple sequences so that $\works{A, B}$.
@@
 \begin{proof}
-First we prove the following.
-Mark all commands in $A$ that also appear in $B$.
-Then there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.
-We show $A$ can be transformed via equivalences so that this would be true.
+First we prove the following:
+if all commands are marked in $A$ that also appear in $B$,
+then there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.
+
+We show that $A$ can be transformed via equivalences so that this would be true.
 Our proposition is that if the marked commands are not at the beginning, then
 the sequence contains an unmarked command followed by a marked command.
-We show that these can be reversed resulting in an equivalent sequence.
+We show that these can be swapped resulting in an equivalent sequence.
 Then, by repeating this process similarly to bubble sorting, we can generate 
@@
 
-In these cases, either $m=\parent(n)$ or $p=\parent(m)$.
+In these cases, either $m=\parent(n)$ or $n=\parent(m)$.
 If $B$ has a command on $m$, then
@@
 \begin{gather*}
-A = \cdots\cc  \czw(q, V_W)\cc  \cxy(p, V_Y)\cc  \cdots \\
-B' = \cdots\cc  \cqr(q, V_R)\cc  \cxy(p, V_Y)\cc  \cdots
+A = \cdots\cc  \czw(m, V_W)\cc  \cxy(n, V_Y)\cc  \cdots \\
+B' = \cdots\cc  \cqr(m, V_R)\cc  \cxy(n, V_Y)\cc  \cdots
 \end{gather*}
@@
 
+\newcommand{\acb}{(A\cap B)}
+\newcommand{\acbi}{\acb^{-1}}
+\newcommand{\amb}{(A\setminus B)}
+\newcommand{\bma}{(B\setminus A)}
 We would like to prove that $\worksc{B\cc \reca}{A,B}$.
 From the above we know that this is equivalent to
-$\worksc{(A\cap B)\cc (B\setminus A)\cc \reca}{A,B}$.
-As we already know that $\reca\indep (B\setminus A)$
-and that $\worksc{(A\cap B)\cc(B\setminus A)}{A,B}$
+$\worksc{\acb\cc \bma\cc \reca}{A,B}$.
+As we already know that $\reca\indep\bma$
+and that $\worksc{\acb\cc \bma}{A,B}$
 (as $\worksc{B}{A,B}$),
@@
 we only need to prove that
-$\worksc{(A\cap B)\cc \reca}{A,B}$.
-
-% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-
-\newcommand{\acbi}{(A\cap B)^{-1}}
-\newcommand{\amb}{(A\setminus B)}
-\newcommand{\bma}{(B\setminus A)}
+$\worksc{\acb\cc \reca}{A,B}$.
+
 Using \cref{r_invmove} we can rephrase this as
-% TODO axiom doesn't specify multiple conditions
 $\worksc{\reca}{\acbi\cc A,\acbi\cc B}$.
 
-We already know the following things:
+To restate some results above, we therefore already know the following things:
 \begin{itemize}
 \item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
-% \item $\amb \cap \bma = \emptyset$
+\item $\amb \cap \bma = \emptyset$
 \item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
-\item $\worksc{\ordered{\amb}\cc \ordered{\bma}}{\acbi\cc A,\acbi\cc B}$ as $\worksc{A,B}{A,B}$ based on \cref{r_invmove}
+\item $\worksc{\amb, \bma}{\acbi\cc A,\acbi\cc B}$ 
+based on \cref{r_invmove}
+as $\worksc{A,B}{A,B}$
+and $A\equiv\acb\cc\amb$, $B\equiv\acb\cc\bma$.
 \end{itemize}
@@
 Our theorem is therefore proven if we prove the following lemma:
-
+\newcommand{\condSimple}{(c1)}
+\newcommand{\condDisj}{(c2)}
+\newcommand{\condApr}{(c3)}
+\newcommand{\condWork}{(c4)}
 \begin{mylem}
@@
    \begin{itemize}
-   \item \newcommand{\condSimple}{(1)} \condSimple $S$ and $T$ are simple sequences
-   % \item \newcommand{\condDisj}{(4)} \condDisj $S\cap T=\emptyset$
-   \item \newcommand{\condApr}{(2)} \condApr $S^*$ is the largest subset of $S$ where $S^*\indep T$
-   \item \newcommand{\condWork}{(3)} \condWork $\worksc{S,T}{C_1,\ldots,C_n}$
+   \item[\condSimple] $S$ and $T$ are simple sequences,
+   \item[\condDisj] $S\cap T=\emptyset$,
+   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
+   \item[\condWork] $\worksc{S,T}{\seqset{C}}$ for some set of sequences $\seqset{C}$,
    \end{itemize}
 then
-\[ \worksc{S^*}{C_1,\ldots,C_n} \]
+\[ \worksc{S^*}{\seqset{C}}. \]
 \end{mylem}
@@
 \begin{proof}
-% TODO Refer back to conditions!
-This is trivial unless $\works{C_1,\ldots,C_n}$, so we will assume that it is true
+This is trivial unless $\works{\seqset{C}}$, so we will assume that it is true
 and therefore $\works{S,T}$.
-% TODO This probably needs an axiom
-
-Similarly to above, we prove that $S$ can be transformed into $S'$ by equivalences
-so that all commands in $S^*$ would be at its beginning.
+
+The proof is similar to that of \cref{can_move_intersection}.
+We mark all commands in $S$ that are in its subset $S^*$, and
+we prove that $S$ can be transformed into $S'$ via equivalences
+so that all marked commands would be at its beginning.
 If so, then based on \cref{worksextpostfix}
-$\worksc{S^*}{C_1,\ldots,C_n}$ as $\worksc{S'}{C_1,\ldots,C_n}$ and .
-
-Also similarly to above,
-we proceed by induction on the number of commands in $S$ that are not in $S^*$, but which precede
-the last command in $S$ that is also in $S^*$.
-If the number is 0, the lemma is true.
-Otherwise let the last command in $S$ also in $S^*$ be $\cxy(p,V_Y)$
-and the preceding command in $S$ be $\czw(q,V_W)$.
-
+$\worksc{S^*}{\seqset{C}}$ as $\worksc{S'}{\seqset{C}}$ and $S'=S^*\cc S_0$ 
+where $S_0$ contains the remaining (conflicting) commands.
+
+Again we know that if $S$ does not already have all marked commands at its beginning,
+then there is an unmarked command followed by a marked one.
+We show that these commands are independent and so they can be swapped
+resulting in an equivalent sequence.
+By repeating this process we can generate a suitable $S'$.
+
+Let therefore the marked command in $S$ be $\cxy(n,V_Y)$
+and the preceding unmarked command be $\czw(m,V_W)$.
 As $S$ is simple and $\works{S}$, from 
@@
 we know that these commands can only be on unrelated paths or form a construction or destruction pair.
-In the first case, swapping the commands results in a sequence equivalent to $S$,
-with the number on relevant commands not in $S^*$ reduced by one.
-In the last two cases,
-either $q=\parent(p)$ or $p=\parent(q)$.
-
-We also know that there must be a command $\cqr(r,V_R)$ in $T$ which is not independent of $\czw(q,V_W)$.
-By definition this means that one of the following must be true:
+In the first case, swapping the commands results in a sequence equivalent to $S$;
+we only need to show that the other two cases are not possible as they would lead to a contradiction.
+
+In the last two cases, we know that either $m=\parent(n)$ or $n=\parent(m)$.
+We also know that because of {\condApr} there must be 
+a command $\cqr(o,V_R)$ in $T$ which is not independent of $\czw(m,V_W)$
+as $\czw(m,V_W)$ is not part of $S^*$.
+\begin{gather*}
+S = \cdots\cc  \czw(m, V_W)\cc  \cxy(n, V_Y)\cc  \cdots \\
+T = \cdots\cc  \cqr(o, V_R)\cc \cdots
+\end{gather*}
+We know none of these commands is an assertion command, and 
+from {\condDisj} that $\cqr(o,V_R)\neq\czw(m,V_W)$.
+Therefore, based on \cref{unrelated_is_independent} we know this means that
+either $m\descendantEq o$ or $o\descendantEq m$.
+From {\condApr} we also know that $\cxy(n,V_Y)\indep \cqr(o,V_R)$,
+and so because of \cref{unrelated_is_independent},
+$n\unrel o$.
+
+We therefore have four cases considering the relationships between $n,m$ and $o$:
 \begin{itemize}
-\item $\czw(q,V_W)\cc \cqr(r,V_R) \equiv\cbrk$
-\item $\cqr(r,V_R)\cc \czw(q,V_W) \equiv\cbrk$
-\item $\czw(q,V_W)\cc \cqr(r,V_R) \nequiv \cqr(r,V_R)\cc \czw(q,V_W)$
-\end{itemize}
-From these and \cref{ax_separate_commute,ax_separate_nobreaks} we also know that
-either $q\descendant r$ or $r\descendant q$.
-By definition we also know that $\cxy(p,V_Y)\indep \cqr(r,V_R)$,
-and the same argument shows that therefore
-$p\not\descendant r$ and $r\not\descendant p$ and $p\neq r$. TODO CHECK
-
-We therefore have four cases considering the relationships between $p,q$ and $r$:
-\begin{itemize}
-\item $p=\parent(q) \wedge r\descendant q$.
-   This would mean that $r\descendant p$ or $r=p$, which is a contradiction.
-\item $p=\parent(q) \wedge q\descendant r$.
-   This would mean that $p\descendant r$, which is a contradiction.
-\item $q=\parent(p) \wedge r\descendant q$.
-   This would mean that $r\descendant p$, which is a contradiction.  
-\item $q=\parent(p) \wedge q\descendant r$.
+\item $n=\parent(m) \wedge o\descendantEq m$.
+   This would mean that $o\descendantEq n$ or $n=\parent(o)$, which contradicts $n\unrel o$.
+\item $n=\parent(m) \wedge m\descendantEq o$.
+   This would mean that $n\descendant o$, which contradicts $n\unrel o$.
+\item $m=\parent(n) \wedge o\descendantEq m$.
+   This would mean that $o\descendant n$, which contradicts $n\unrel o$.
+\item $m=\parent(n) \wedge m\descendantEq o$.
    Let us continue with this case.
@@
 
-We know that $T$ cannot have a command on $q$ as $q=\parent(p)$ and $\cxy(p,V_Y)\indep T$.
-Create $T'\equiv T$ by inserting a command on $q$ before $\cqr(r,V_R)$
-into $T$ according to \cref{ax_parent_assert}.
-We now have $\cxy(p,V_Y)\indep T\equiv T'$ which is a contradiction as
-$T'$ has a command on $q$ and $q=\parent(p)$.
-
+We know that $T$ cannot have a command on $m$ as $m=\parent(n)$ and $\cxy(n,V_Y)\indep T$,
+and so $m\neq o$ and therefore $m\descendant o$.
+This means we can create a new sequence $T'\equiv T$ by inserting a command on 
+$m$ into $T$ before $\cqr(o,V_R)$
+according to \cref{ax_parent_assert}.
+We now have $\cxy(n,V_Y)\indep T\equiv T'$ which is a contradiction as
+$T'$ has a command on $m$ and $m=\parent(n)$.
 \end{proof}

### 2015-11-26 2015/paper.tex
More proofs

@@
 \newcommand{\nequiv}{\not\equiv}
-\newcommand{\indep}{\wr\!\!\wr\,} % Independent commands, sequences
+\newcommand{\indep}{\,{\wr\wr}\,} % Independent commands, sequences
 \newcommand{\unrel}{\indep} % Unrelated nodes
+\newcommand{\nindep}{\,{\centernot{\wr\wr}}\,}
+\newcommand{\nunrel}{\nindep}
 
@@
 
-% TODO delete:
-\newcommand{\infer}[2]{\begin{array}{c}{#1}\\\hline{#2}\end{array}}
-\newcommand{\inferr}[3]{\begin{array}{c}{#1}\\{#2}\\\hline{#3}\end{array}}
-\newcommand{\inferrr}[4]{\begin{array}{c}{#1}\\{#2}\\{#3}\\\hline{#4}\end{array}}
-
 \theoremstyle{definition}
@@
 
-% TODO delete:
-\newtheorem{myrul}{Rule}
-\crefname{myrul}{rule}{rules}
-
-\title{Correctness of Algebraic File Synchronization}
+\title{The Correctness of Algebraic File Synchronization}
 
@@
 % <<<<<<<< TODO Rewrite: no algebra
+TODO: Rewrite:
  about which we will reason
@@
 
-% TODO Proof of correctness of update detection - the generated order will work
+% TODO
+TODO: Proof of correctness of update detection - the generated order will work
 
@@
 
-\begin{mydef}{$\orderset{U}$}
+\begin{mydef}{$\orderset{U}$.}
 We use $\orderset{U}$ to denote the set of sequences that contain all commands in
@@
 It follows from the algorithm that:
-\begin{mylem}\label{lemma:neighbor}
+\begin{mycor}\label{lemma:neighbor}
 If $U$ contains commands on both $n$ and $\parent(n)$, then
 there is a $U'\in\orderset{U}$ where they are next to each other.
-\end{mylem}
+\end{mycor}
 
@@
 that is, the domains of simple sequences cannot be extended further.
-This is equivalent to the proposition that $\extset{S} = \{S'|S\equiv S'\}$.
+This is equivalent to the proposition that for simple sequences $\extset{S} = \{S'|S\equiv S'\}$.
 \end{mylem}
@@
 
-\begin{mydef}{Reconciliation}\label{def:reconciliation}
+\begin{mydef}{Reconciliation.}\label{def:reconciliation}
 \begin{align*}
@@
 The order of commands in the sequence can be determined using the algorithm described in
-\cref{ordering} as any subset of $A$ is also simple,
-and $\recb$ can be obtained in a similar way by reversing $A$ and $B$.
+\cref{ordering} as any subset of $A$ is also simple.
+In a similar way, $\recb$ can be obtained by reversing $A$ and $B$.
 \end{mydef}
@@
 \[ \reca\FS_B\neq\fsbroken. \]
-So that we can formalise statements needed to prove this,
+So that we can formalize statements needed to prove this,
 let us introduce two relations that describe under what conditions
@@
 % An inference rule in the algebra
-$B\eqext A \Rightarrow \worksc{A}{B}$
+$B\eqext A \Rightarrow \worksc{A}{B}$.
 \end{mycor}
@@
 % An inference rule in the algebra
-$\forall A,S: \worksc{A}{A\cc S}$
+$\forall A,S: \worksc{A}{A\cc S}$, that is, if a sequence works, its prefix also works.
 \end{mycor}
 
-\begin{mycor}
+\begin{mycor}\label{workschained}
 % An inference rule in the algebra
@@
 if $A_1\in\seqset{A}$, then
-$ \worksc{\seqset{A}}{\seqset{B}} \wedge \worksc{\seqset{C}}{A_1} \Rightarrow \worksc{\seqset{A}\cup\seqset{C}}{\seqset{B}} $
+$ \worksc{\seqset{A}}{\seqset{B}} \wedge \worksc{\seqset{C}}{A_1} \Rightarrow \worksc{\seqset{A}\cup\seqset{C}}{\seqset{B}}$.
 \end{mycor}
 
-We will also prove the following lemmas.
-
-\begin{mylem}\label{worksinputmatch}
-If $A$ and $B$ are minimal sequences, $\works{A,B}$,
-and there are commands on node $n$ in both $A$ ($\cxy(n, V_Y)\in A$) and $B$ ($\czw(n, V_W)\in B$)
-then their input types must match ($X=Z$).
-\end{mylem}
-\begin{proof}
-This is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
-$\cxy(n, V_Y)$ or $\czw(n, V_W)$ would not break, and consequently $A$ and $B$ could not work on the same filesystem.
-\end{proof}
-
-\begin{mylem}\label{r_indep_combine}
-% An inference rule in the algebra
-\[ \worksc{T}{\seqset{S}} \wedge \worksc{U}{\seqset{S}} \wedge T\indep U \Rightarrow \worksc{T\cc U}{\seqset{S}} \]
-\end{mylem}
-\begin{proof}
-% TODO Proof
-TODO
-\end{proof}
+We also prove the following lemmas.
 
@@
 Two different commands that are not assertion commands are independent iff the nodes they change are unrelated:
-$\cxy(n,V_Y)\indep\czw(m,V_W) \Leftrightarrow n\unrel m$ 
+\[ \cxy(n,V_Y)\indep\czw(m,V_W) \Leftrightarrow n\unrel m \]
 if $\cxy(n,V_Y)\neq\czw(m,V_W)$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
@@
 We proceed in two steps; first, we prove that
-$\cxy(n,V_Y)\not\indep\czw(m,V_W) \wedge n\unrel m$ would lead to contradiction.
+\[ \cxy(n,V_Y)\nindep\czw(m,V_W) \wedge n\unrel m \] would lead to contradiction.
 By definition, if the two commands are not independent, then one of the following holds:
@@
 Next, we prove that
-$\cxy(n,V_Y)\indep\czw(m,V_W) \wedge n\not\unrel m$ would lead to contradiction.
-As $n\not\unrel m$
+\[ \cxy(n,V_Y)\indep\czw(m,V_W) \wedge n\nunrel m \] would lead to contradiction.
+As $n\nunrel m$
 we know that $n=m$, $n\descendant m$ or $m\descendant n$.
@@
 
+\begin{myax}\label{combine_independent_commands}
+The combination of independent commands works wherever the original commands work:
+\begin{align*}
+\forall\FS: &\cxy(n,C_Y)\indep \czw(m,C_W) \\
+&\wedge \cxy(n,C_Y)\FS\neq\fsbroken \\
+&\wedge \czw(m,C_W)\FS\neq\fsbroken \\
+\Rightarrow &\cxy(n,C_Y)\cc \czw(m,C_W)\FS\neq\fsbroken.
+\end{align*}
+\end{myax}
+\begin{proof}
+We name this proposition an axiom for the same reason as above,
+but it is easy to provide an indirect proof based on our filesystem model.
+Assume that $\cxy(n,C_Y)\cc \czw(m,C_W)\FS=\fsbroken$.
+We know $\cxy(m,C_Y)\FS\neq\fsbroken$ so it must be applying 
+$\czw(m,C_W)$ that breaks it.
+Applying a command can only result in a broken filesystem in three cases.
+First, if the filesystem was already broken, which cannot be the case here.
+Second, if there the input type does not match the filesystem,
+but we know $\FS(m)\in\setvx{W}$ and so
+$(\cxy(m,C_Y)\FS)(m)\in\setvx{W}$ as based on \cref{unrelated_is_independent}, $n\neq m$.
+Third, if the new filesystem violates the tree property.
+This again cannot be the case because we also know that $n\unrel m$
+and the tree property only depends on the types of the parent and children of $m$,
+which therefore cannot be changed by $\cxy(m,C_Y)$.
+\end{proof}
+
+This result can be extended to sequences:
+
+\begin{mylem}\label{combine_independent_sequences}
+The combination of independent sequences works wherever the original sequences work:
+\[ S\indep T \Rightarrow \worksc{S\cc T}{S,T}. \]
+\end{mylem}
+\begin{proof}
+Assume that there is a filesystem $\FS$ so that
+$S\FS\neq\fsbroken$ and $T\FS\neq\fsbroken$, but
+$(S\cc T)\FS=\fsbroken$.
+
+From \cref{unrelated_is_independent,ax_separate_commute} we know that
+the commands in $S$ and $T$ pairwise commute, and so any sequence
+that contains the commands from $S$ and $T$ preserving their original order,
+but in any permutation between $S$ and $T$ is equivalent to $S\cc T$ on all filesystems.
+
+Let the command that breaks $\FS$ in $T$ be $t$
+so that $T=T_0\cc t\cc T_1$.
+It is still true that $(T_0 \cc t)\FS\neq\fsbroken$,
+and by definition $(S\cc T_0)\FS\neq\fsbroken$,
+but $(S\cc T_0\cc t)\FS=\fsbroken$.
+Also, from above we know that $S\cc T_0\equiv T_0\cc S$
+and so $(T_0 \cc S)\FS\neq\fsbroken$.
+
+If we denote the first command in $S$ with $s_1$,
+this means that $(T_0 \cc s_1)\FS\neq\fsbroken$,
+which we can combine with $(T_0 \cc t)\FS\neq\fsbroken$, $t\indep s_1$ and
+\cref{combine_independent_commands}
+(using $T_0\FS$ as the reference filesystem)
+to arrive at $(T_0 \cc s_1\cc t)\FS\neq\fsbroken$.
+
+We can repeat this step for $s_2$, the next command in $S$,
+and from 
+$(T_0 \cc s_1\cc t)\FS\neq\fsbroken$
+and
+$(T_0 \cc s_1\cc s_2)\FS\neq\fsbroken$
+arrive at
+$(T_0 \cc s_1\cc s_2\cc t)\FS\neq\fsbroken$.
+This can be repeated until $S$ is exhausted and we get
+$(T_0 \cc S\cc t)\FS\neq\fsbroken$, which is a contradiction.
+
+\end{proof}
+
+From this and \cref{workschained} it follows that:
+
+\begin{mycor}\label{r_indep_combine}
+% An inference rule in the algebra
+The combination of independent sequences continues to work under the same conditions:
+\[ \worksc{S}{\seqset{U}} \wedge \worksc{T}{\seqset{U}} \wedge S\indep T \Rightarrow \worksc{S\cc T}{\seqset{U}} \]
+\end{mycor}
+
+\begin{mylem}\label{worksinputmatch}
+If $A$ and $B$ are minimal sequences, $\works{A,B}$,
+and there are commands on node $n$ in both $A$ ($\cxy(n, V_Y)\in A$) and $B$ ($\czw(n, V_W)\in B$)
+then their input types must match ($X=Z$).
+\end{mylem}
+\begin{proof}
+This is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
+either $\cxy(n, V_Y)$ or $\czw(n, V_W)$ would not break, 
+and consequently $A$ and $B$ cannot work on the same filesystem.
+\end{proof}
+
 \medskip
@@
 \begin{mylem}\label{r_invmove}
+A common prefix of sequences can be moved to the other side of $\workssign$ by inverting it:
 \begin{gather*}
@@
 \begin{mylem}\label{indep_prefix_combine}
+The combination of sequences with a common head and independent tail continues to work:
 \[ \worksc{A\cc B}{\seqset{S}} \wedge \worksc{A\cc C}{\seqset{S}} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{\seqset{S}} \]
@@
 \end{myth}
-where, to restate the definition,
-{ % scope
-\renewcommand{\themydef}{\ref{def:reconciliation}}
-\begin{mydef}
+where, to restate \cref{def:reconciliation},
+% { % scope
+% \renewcommand{\themydef}{\ref{def:reconciliation}}
+% \begin{mydef}
 \begin{align*}
@@
 \end{align*}
-\end{mydef}
-} % scope
+% \end{mydef}
+% } % scope
 
@@
 
-Let us consider therefore the marked command preceded by an unmarked command in $A$.
+Let us consider therefore the marked command preceded by an unmarked command in $A$,
 and let the marked command be $\cxy(n, V_Y)$, 
 and the preceding unmarked command be $\czw(m, V_W)$.
-As $A$ is a simple command and $\works{A}$, from 
+As $A$ is simple and $\works{A}$, from 
 \cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
@@
 From the above we know that this is equivalent to
-$\worksc{\acb\cc \bma\cc \reca}{A,B}$.
+\[ \worksc{\acb\cc \bma\cc \reca}{A,B}. \]
 As we already know that $\reca\indep\bma$
@@
 we only need to prove that
-$\worksc{\acb\cc \reca}{A,B}$.
-
+\[ \worksc{\acb\cc \reca}{A,B}. \]
 Using \cref{r_invmove} we can rephrase this as
-$\worksc{\reca}{\acbi\cc A,\acbi\cc B}$.
+\[ \worksc{\reca}{\acbi\cc A,\acbi\cc B}. \]
 
@@
 based on \cref{r_invmove}
-as $\worksc{A,B}{A,B}$
-and $A\equiv\acb\cc\amb$, $B\equiv\acb\cc\bma$.
+as $\worksc{A,B}{A,B}$,
+and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
 \end{itemize}
@@
 
-% TODO $\reca$ is maximal
-
-% TODO Talk about setting up an algebra / calculus
+% TODO
+TODO: $\reca$ is maximal
+
+% TODO
+TODO: About setting up an algebra / calculus
 

### 2015-11-27 2015/paper.tex
Proof for moving inverse sequences

@@
 
-\newcommand{\cbrk}{\mathtt{break}}
+\newcommand{\cbrk}{\mathtt{break}} % 'break' command
 \newcommand{\fscommand}[2]{{#1#2}}
@@
 
-\newcommand{\eqext}{\sqsubseteq}
-\newcommand{\eqnrw}{\sqsupseteq}
+\newcommand{\eqext}{\sqsubseteq} % equivalent to
+\newcommand{\eqnrw}{\sqsupseteq} % extended by
 \newcommand{\nequiv}{\not\equiv}
-\newcommand{\indep}{\,{\wr\wr}\,} % Independent commands, sequences
+\newcommand{\indep}{\mathrel{\wr\wr}} % Independent commands, sequences
 \newcommand{\unrel}{\indep} % Unrelated nodes
-\newcommand{\nindep}{\,{\centernot{\wr\wr}}\,}
-\newcommand{\nunrel}{\nindep}
+\newcommand{\nindep}{\,{\centernot{\wr\wr}}\,} % not \indep
+\newcommand{\nunrel}{\nindep} % not \unrel
 
@@
 \newcommand{\works}[1]{\workssign({#1})}
-\newcommand{\worksc}[2]{\workssign({#1}|{#2})}
-
-\newcommand{\emptyseq}{[\,]} % TODO change
-
-\newcommand{\extset}[1]{\wp({#1})}
+\newcommand{\worksc}[2]{\workssign({#1}\mathrel{|}{#2})}
+
+\newcommand{\typeeq}{\stackrel{t}{=}}
+\newcommand{\ntypeeq}{\centernot{\stackrel{t}{=}}}
+
+\newcommand{\emptyseq}{\lambda} % empty sequence
+
 \newcommand{\orderset}[1]{\vec{\wp}({#1})}
-\newcommand{\ordered}[1]{#1}
 \newcommand{\seqset}[1]{\underline{#1}} % Set of sequences
@@
 The tree propety can then be defined as
-\[ \forall n\in\setn : \FS(n) \neq \empt \wedge \parent(n) \neq \topnode \Rightarrow \FS(\parent(n)) \in \setd \]
-
+\begin{align*}
+\forall n\in\setn: &\FS(n) \neq \empt \\ % TODO alignment problem
+&\quad\wedge \parent(n) \neq \topnode \\
+&\Rightarrow \FS(\parent(n)) \in \setd 
+\end{align*}
 This means that as we move down from the root of a tree of nodes,
@@
 % <<<<<<<< TODO Rewrite: no algebra
-TODO: Rewrite:
- about which we will reason
-using our algebra.
-We will aim to draw conclusions or judgements about commands and sequences of commands
-based on the algebra we are aiming to construct.
-For example, if we believe that two sequences of commands are equivalent as their effect
-is the same, then we aim to be able to derive this from the axioms and inference rules of the
-algebra.
-As the algebra operates on commands only,
-these judgements, by definition, need to hold regardless of the filesystem the commands are applied to.
-Accordingly, we expect that the more information one encodes into the commands and the sequences,
-the better predicitons we will be able to make using our algebra,
-as then the commands and sequences will be more specific, and will select a smaller subset
-of potential filesystems on which they can meaningfully operate.
+%  about which we will reason
+% using our algebra.
+% We will aim to draw conclusions or judgements about commands and sequences of commands
+% based on the algebra we are aiming to construct.
+% For example, if we believe that two sequences of commands are equivalent as their effect
+% is the same, then we aim to be able to derive this from the axioms and inference rules of the
+% algebra.
+% As the algebra operates on commands only,
+% these judgements, by definition, need to hold regardless of the filesystem the commands are applied to.
+% Accordingly, we expect that the more information one encodes into the commands and the sequences,
+% the better predicitons we will be able to make using our algebra,
+% as then the commands and sequences will be more specific, and will select a smaller subset
+% of potential filesystems on which they can meaningfully operate.
 % >>>>>>>>>> to here
+
+...
 
@@
 might be $create(n,V)$, $edit(n,V)$ and $remove(n)$ where $n\in\setn$ and $V\in\setv$ (but $V\neq\empt$).
-Regarding what we know of their output, that is, the state of the filesystem at $n$
+Regarding their output, that is, the state of the filesystem at $n$
 after applying the command,
@@
 required in the filesystem before the command is applied, and the right sign notes the type
-afterwards. For example, $mkdir(n,D)$ will be $\cbd(n,D)$, and $rmdir(n)$ will be $\cdb(n)$.
-
-A command can only succeeds if the original value at node $n$ has a type that matches
+afterwards. For example, $mkdir(n,D)$ is $\cbd(n,D)$, and $rmdir(n)$ is $\cdb(n)$.
+
+A command can only succeed if the original value at node $n$ has a type that matches
 the input type of the command. If this is not the case, or if the resulting
 filesystem no longer has the tree property, then we say that the command
-\textbf{breaks} the filesystem. Broken filesystems are considered equal
+{\em breaks} the filesystem. Broken filesystems are considered equal
 (but not equal to any working filesystem), and we note them by $\FS=\fsbroken$.
@@
 
-When we describe multiple or unknown commands, we may substitute one or both
-types with a variable, for example by writing $\cxy(n,V)$. In this context,
-if we write that $\cxy=\czw$, we mean that their input and output types
-are the same ($X=Z$ and $Y=W$).
+In general, when we describe multiple or unknown commands, we may substitute one or both
+of their types with variables, as we did with $\cxy(n,V_Y)$. In this context,
+if we write that $\cxy=\czw$, we mean that the input and output types
+of the commands are the same ($X=Z$ and $Y=W$), while a full equiality 
+($\cxy(n,V_Y)=\czw(n,V_W)$)
+implies
+that their output value is also the same.
 
@@
 The commands we aim to investigate do not occur in isolation:
-for example, when comparing to filesystems to determine the commands needed to transform one into the other,
+for example, when comparing filesystems to determine the commands needed to transform one into the other,
 we receive a set of commands with uncertain ordering.
@@
 $S=\cbd(n)\cc \cbf(m,F)$, or $S'=S\cc\cbb(o)$.
+We write $\emptyseq$ for the empty sequence.
+
+TODO: Sequences of commands, in the usual way,  form a free
+semigroup
 
@@
 This approach is useful as there are a limited number of command pairs,
-because, as we arguad above, we can disregard the exact output value of commands apart from its type,
+because, as we argued above, we can disregard the exact output values of commands apart from their type,
 and we can also abstract the relationship between the nodes in the two commands
@@
 Although they can be proven by investigating all relevant possibilities
-in a filesystem, we refer to these in axioms because in a secondary algebraic model
+in a filesystem, we refer to these as axioms because in a secondary algebraic model
 that describes commands without reference to an underlying filesystem,
@@
 In this section we describe an algorithm with which all possible orderings of a
-set of sequences can be generated, but before doing so, let us consider the following lemma.
+simple set of commands can be generated, but before doing so, let us consider the following lemma.
 
 \begin{mylem}\label{connected_changes}
-If a simple set of commands that can be applied to a filesystem in some order without breaking it
+If a simple set of commands, which can be applied to a filesystem in some order without breaking it,
 contains commands on $n$ and $\nn$ where $\nn\descendant n$
@@
 Let this command be $\cqr(m,V_R)$.
-If $\czw$ is to the right, the $A$ looks like the following:
+If $\czw$ is to the right, then $A$ looks like the following:
 \[ A = \cdots\cc\cxy(n,V_Y)\cc\cqr(m,V_R)\cc\cdots\cc\czw(\nn,V_W)\cc\cdots \]
@@
 contains two commands on related nodes, then it must contain a command on each
-node that is between these two nodes in the parent--child tree.
+node that is between these two nodes in the node tree.
 
@@
 on its parent node (if there is one). 
-If the command removes content at this node (it is of the form $\fsregcommand{X}{\empt}$), 
+If the command removes content at this node (it is of the form $X\empt$), 
 then it must follow all other commands in the component, and
@@
 the sequence we are creating out of the component,
-and recursively start the whole algorithm again on the commands in the component that remain.
+and recursively start the whole algorithm again on the commands in the component that remain,
+potentially splitting them into sub-components.
 The result of this process is a set of possible orders for each component,
@@
 as a set and determine its $\orderset{S}$.
-Let us investigate the properties of simple sequences and this set a bit further.
-
-\begin{mydef}{$\extset{S}$.}
-For any sequence $S$ we can consider all sequences that extend it:
-$\extset{S} := \{S'|S\eqext S'\}$
-\end{mydef}
-
-\begin{mylem}\label{simple_is_max}
-For any simple sequence $S\neq\cbrk$, $\forall T: S\eqext T \Rightarrow S\equiv T$;
-that is, the domains of simple sequences cannot be extended further.
-This is equivalent to the proposition that for simple sequences $\extset{S} = \{S'|S\equiv S'\}$.
-\end{mylem}
-\begin{proof}
-TODO
+
+From the algorithm we also see that if a simple sequence $S$ works, then
+all sequences in $\orderset{S}$ are equivalent to it.
+As the sequences contain a single command on each node,
+their output must be the same on the same input unless
+they break the filesystem.
+However, the algorithm ensures that that will not be the case.
 % TODO
-\end{proof}
-
-\begin{mylem}\label{lemma:minextorder}
-% TODO orderset only defined on simple
-For any minimal sequence $S\neq\cbrk$, $\orderset{S} = \extset{S}$.
-\end{mylem}
-\begin{proof}
-TODO
-% TODO
-\end{proof}
-
-\begin{mylem}
-All sequences in $\orderset{S}$ of a simple sequence $S$ are equivalent.
-\end{mylem}
-\begin{proof}
-This follows from \cref{simple_is_max,lemma:minextorder}.
-\end{proof}
+(TODO: Is this enough?)
+Therefore:
+
+\begin{mycor}\label{simple_reorder_equiv}
+For any simple sequence $S\neq\cbrk$,
+all sequences in $\orderset{S}$ are equivalent.
+\end{mycor}
 
@@
 $\workssign$ can be chained:
-if $A_1\in\seqset{A}$, then
-$ \worksc{\seqset{A}}{\seqset{B}} \wedge \worksc{\seqset{C}}{A_1} \Rightarrow \worksc{\seqset{A}\cup\seqset{C}}{\seqset{B}}$.
+if $\seqset{A'}\subset\seqset{A}$, then
+$ \worksc{\seqset{C}}{\seqset{A'}} \wedge \worksc{\seqset{A}}{\seqset{B}} \Rightarrow \worksc{\seqset{A}\cup\seqset{C}}{\seqset{B}}$.
 \end{mycor}
@@
 \[ \cxy(n,V_Y)\nindep\czw(m,V_W) \wedge n\unrel m \] would lead to contradiction.
-By definition, if the two commands are not independent, then one of the following holds:
+By definition, if the two commands are not independent, then at least one of the following holds:
 \begin{itemize}
@@
 \forall\FS: &\cxy(n,C_Y)\indep \czw(m,C_W) \\
-&\wedge \cxy(n,C_Y)\FS\neq\fsbroken \\
-&\wedge \czw(m,C_W)\FS\neq\fsbroken \\
-\Rightarrow &\cxy(n,C_Y)\cc \czw(m,C_W)\FS\neq\fsbroken.
+&\quad\wedge \cxy(n,C_Y)\FS\neq\fsbroken \\
+&\quad\wedge \czw(m,C_W)\FS\neq\fsbroken \\
+&\Rightarrow \cxy(n,C_Y)\cc \czw(m,C_W)\FS\neq\fsbroken.
 \end{align*}
@@
 First, if the filesystem was already broken, which cannot be the case here.
-Second, if there the input type does not match the filesystem,
+Second, if the input type does not match the filesystem,
 but we know $\FS(m)\in\setvx{W}$ and so
@@
 the commands in $S$ and $T$ pairwise commute, and so any sequence
-that contains the commands from $S$ and $T$ preserving their original order,
-but in any permutation between $S$ and $T$ is equivalent to $S\cc T$ on all filesystems.
-
-Let the command that breaks $\FS$ in $T$ be $t$
+that contains the commands from $S$ and $T$ and preserve their original partial order
+is equivalent to $S\cc T$ on all filesystems.
+
+Let the command that breaks $\FS$ in $T$ when applying $S\cc T$ be $t$
 so that $T=T_0\cc t\cc T_1$.
@@
 $(T_0 \cc S\cc t)\FS\neq\fsbroken$, which is a contradiction.
-
 \end{proof}
 
-From this and \cref{workschained} it follows that:
-
-\begin{mycor}\label{r_indep_combine}
-% An inference rule in the algebra
-The combination of independent sequences continues to work under the same conditions:
-\[ \worksc{S}{\seqset{U}} \wedge \worksc{T}{\seqset{U}} \wedge S\indep T \Rightarrow \worksc{S\cc T}{\seqset{U}} \]
-\end{mycor}
+Separately, we prove the following:
 
@@
 in reverse order.
-%
-Clearly, $(S^{-1})^{-1}\equiv S$ for any sequence.
-\end{mydef}
+\end{mydef}
+
+\begin{mydef}{$\typeeq$.}
+For two filesystems we write $\FS\typeeq\GS$
+iff 
+at all nodes the types of their values are the same, or they are both broken.
+\end{mydef}
+
+From the definitions we can clearly see that
+\begin{mycor}\label{negneg_is_typeeq}
+$\forall \FS: (S^{-1})^{-1}\FS\typeeq \FS$.
+\end{mycor}
 
@@
 \end{gather*}
-% TODO Proof
-TODO.
-Sequences are bijections on filesystems over type-equality.
-TODO: $A,S,B$ need to be simple?
 \end{mylem}
+\begin{proof}
+This is based on the fact that in our model, unless they break a filesystem,
+commands change one type of value into another, but never merge types.
+That is,
+sequences---as functions mapping filesystems to filesystems---are
+essentially bijections over type-equality
+with the only ``sink'' being $\fsbroken$:
+\begin{align*}
+\forall S,\FS,\GS: &S\FS\neq\fsbroken \Rightarrow \\
+&(S\FS\ntypeeq S\GS \Leftrightarrow \FS\ntypeeq \GS).
+\end{align*}
+
+For
+\[ \worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \]
+the rest of the proof is illustrated by the diagram below
+where Dom($x$), the domain of $x$, represents the set of filesystems
+the sequence $x$ does not break, or neither of the sequences in the set $x$ breaks.
+
+\input{inverse-works} % TODO arrows to small
+
+We see that the set of filesystems the sequences in $\seqset{A}$ do not break intersect with the range of $B$.
+As $B$ is a bijection between its domain and range, we can use $B^{-1}$ to map this intersection back
+onto the domain of $B$.
+As $\worksc{B\cc \seqset{A}}{\seqset{S}}$ the domain of $\seqset{S}$ must be a subset of this
+projected intersection.
+If so, then we can use $B$ to map the domain of $\seqset{S}$, which yields the domain of $B^{-1}\cc \seqset{S}$.
+As it is also a part of the domain of $A$, we get $\worksc{\seqset{A}}{B^{-1}\cc \seqset{S}}$.
+
+The second part of the lemma can be proven in a similar way.
+\end{proof}
 
 \begin{mylem}\label{indep_prefix_combine}
-The combination of sequences with a common head and independent tail continues to work:
+The combination of sequences with a common head and independent tails continues to work under the same conditions:
 \[ \worksc{A\cc B}{\seqset{S}} \wedge \worksc{A\cc C}{\seqset{S}} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{\seqset{S}} \]
@@
 $\worksc{B}{A^{-1}\cc \seqset{S}}$ and $\worksc{C}{A^{-1}\cc \seqset{S}}$,
-and from \cref{r_indep_combine} we know
-$\worksc{B\cc C}{A^{-1}\cc \seqset{S}}$. Applying the second line of \cref{r_invmove} we get
-$\worksc{(A^{-1})^{-1}\cc B\cc C}{\seqset{S}}$, which proves our lemma as $(A^{-1})^{-1}\equiv A$.
+and from \cref{combine_independent_sequences} we know
+$\worksc{B\cc C}{B,C}$.
+Combining these using \cref{workschained}
+we get
+$\worksc{B\cc C}{A^{-1}\cc \seqset{S}}$. 
+Finally, applying the second line of \cref{r_invmove} yields
+$\worksc{(A^{-1})^{-1}\cc B\cc C}{\seqset{S}}$, which proves our lemma 
+as $(A^{-1})^{-1}\typeeq A$. % \cref{negneg_is_typeeq}.
 \end{proof}
@@
 \begin{myth}
-If $A, B$ are simple, then $\worksc{B\cc \reca}{A,B}$
-\end{myth}
+If $A, B$ are simple, then $\worksc{B\cc \reca}{A,B}$,
 where, to restate \cref{def:reconciliation},
@@
 % } % scope
+\end{myth}
 
@@
 we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxy$ (also in $B$),
-and from \cref{simple_is_max,lemma:minextorder} we know that $B'\equiv B$.
+and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
 When describing our ordering algorithm in \cref{ordering} we saw
@@
 \item $\worksc{\amb, \bma}{\acbi\cc A,\acbi\cc B}$ 
-based on \cref{r_invmove}
+because of \cref{r_invmove}
 as $\worksc{A,B}{A,B}$,
@@
 
+% TODO
+TODO: Are these results quite obvious as this is a well-known kind of algebra or system?
+
 \begin{thebibliography}{99}

### 2015-11-27 2015/paper.tex
Minor changes

@@
 Commands on the same node simplify:
-$\cxy(n,V_Y)\cc \czw(n,V_W) \eqext \emptyseq$ where $Y=Z$ and $X=W=\fsregcommandchar{\empt}$ or $X=W=\fsregcommandchar{D}$.
+$\cxy(n,V_Y)\cc \czw(n,V_W) \eqext \emptyseq$ where $Y=Z$ and $X=W=\fsregcommandchar{\empt}$ 
+or $X=W=\fsregcommandchar{D}$.
 \end{myax}
@@
 \begin{mydef}{Construction pair.}
-A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parent(n)$ and the commands are one
+A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parent(n)$ 
+and the commands are one
 of the following:
@@
 An assertion command can be added on a descendant node:
-$\cbb(n)\cc \cxy(\nn,V_Y) \equiv \cxy(\nn,V_Y) \equiv \cxy(\nn,V_Y)\cc \cbb(n)$ where $\nn\descendant n$ and $\cxy\neq\cdd$.
+$\cbb(n)\cc \cxy(\nn,V_Y) \equiv \cxy(\nn,V_Y) \equiv \cxy(\nn,V_Y)\cc \cbb(n)$ 
+where $\nn\descendant n$ and $\cxy\neq\cdd$.
 \end{myax}
@@
 An assertion command can be added on an ancestor node:
-$\cdd(\nn)\cc \cxy(n,V_Y) \equiv \cxy(n,V_Y) \equiv \cxy(n,V_Y)\cc \cdd(\nn)$ where $\nn\descendant n$ and $\cxy\neq\cbb$.
+$\cdd(\nn)\cc \cxy(n,V_Y) \equiv \cxy(n,V_Y) \equiv \cxy(n,V_Y)\cc \cdd(\nn)$ 
+where $\nn\descendant n$ and $\cxy\neq\cbb$.
 \end{myax}
@@
 
-\input{inverse-works} % TODO arrows to small
+\input{inverse-works} % TODO arrows too small
 
@@
 Let $A$ and $B$ be two simple sequences so that $\works{A, B}$.
-Then their intersection works on any filesystem
+Then their intersection, in some suitable order, also works on any filesystem
 either of them works on:
@@
 \begin{proof}
-First we prove the following:
+The difficulty is that commands in $A\cap B$ can occur anywhere in $A$.
+Therefore, first we prove the following:
 if all commands are marked in $A$ that also appear in $B$,

### 2015-11-27 2015/paper.tex
Bugfix: equality is not equivalence

@@
 $\worksc{(A^{-1})^{-1}\cc B\cc C}{\seqset{S}}$, which proves our lemma 
-as $(A^{-1})^{-1}\typeeq A$. % \cref{negneg_is_typeeq}.
+as $\forall\FS: (A^{-1})^{-1}\FS\typeeq A\FS$ (\cref{negneg_is_typeeq}).
 \end{proof}

### 2015-11-28 2015/paper.tex
Proof for correctness of update detection

@@
 we discuss it in the next section.
-
-% TODO
-TODO: Proof of correctness of update detection - the generated order will work
+Then, in \cref{update_works}, we prove that the resulting sequence actually
+works without breaking the filesystem.
 
@@
 \begin{mylem}\label{connected_changes}
-If a simple set of commands, which can be applied to a filesystem in some order without breaking it,
-contains commands on $n$ and $\nn$ where $\nn\descendant n$
-but $\nn\neq\parent(n)$, then the set must also contain a command on $\parent(n)$.
+Given a set of commands that
+does not contain assertion commands,
+and which can be applied to a filesystem in some order without breaking it,
+and which contains commands on $n$ and $\nn$ where $\nn\descendant n$
+but $\nn\neq\parent(n)$, then the set must also contain a commands
+on each node between $n$ and $\nn$.
 \end{mylem}
 \begin{proof}
-We will prove this statement for simple sequences, as if all sequences must contain a command on $\parent(n)$
-under the given conditions, then so must sets because otherwise there would be no order in which thay can be
+We prove that under the given conditions, the set must contain a command on $\parent(n)$.
+Then, by repeating this statement, we how that the set must contain commands on every
+ancestor of $n$ up to $\nn$.
+
+Furthermore,
+we prove this proposition for sequences, not sets, as if all sequences must contain a command on $\parent(n)$,
+then so must sets because otherwise there would be no order in which they can be
 applied to any filesystem.
@@
 \[ A = \cdots\cc\cxy(n,V_Y)\cc\cqr(m,V_R)\cc\cdots\cc\czw(\nn,V_W)\cc\cdots \]
-If $n\unrel m$, reverse $\cxy$ and $\cqr$. Based on \cref{ax_separate_commute} we know that the new
+If $n\unrel m$, swap $\cxy$ and $\cqr$. Based on \cref{ax_separate_commute} we know that the new
 sequence is equivalent to $A$.
@@
 \end{proof}
-
-By applying \cref{connected_changes} multiple times we see that if a simple set of commands
-contains two commands on related nodes, then it must contain a command on each
-node that is between these two nodes in the node tree.
 
@@
 as a set and determine its $\orderset{S}$.
-
-From the algorithm we also see that if a simple sequence $S$ works, then
-all sequences in $\orderset{S}$ are equivalent to it.
-As the sequences contain a single command on each node,
-their output must be the same on the same input unless
-they break the filesystem.
-However, the algorithm ensures that that will not be the case.
-% TODO
-(TODO: Is this enough?)
-Therefore:
-
-\begin{mycor}\label{simple_reorder_equiv}
+An important property of simple sequences is that
+all of their valid permutations are equivalent,
+and all equivalent sequences are mere permutations:
+
+\begin{mylem}\label{simple_reorder_equiv}
 For any simple sequence $S\neq\cbrk$,
-all sequences in $\orderset{S}$ are equivalent.
-\end{mycor}
+$T\equiv S \Leftrightarrow T\in\orderset{S}$.
+\end{mylem}
+\begin{proof}
+TODO
+\end{proof}
 
@@
 but simple sets as sequences.
+
+\medskip
+
+% Correctness of update detection
+% -------------------------------
+
+Based on \cref{connected_changes} we can also show that
+the update detector does function as intended as:
+
+\begin{mylem}\label{update_works}
+A sequence returned by the update detector
+when comparing $\FS^*$ to the original $\FS$
+will not break $\FS$ if it is applied to it.
+\end{mylem}
+\begin{proof}
+Let $\FS\neq\fsbroken$ be the original filesystem, and $\FS^*\neq\fsbroken$
+be the filesystem after the changes we intend to detect.
+Let us assume that some mechanism recorded all changes that occurred
+to $\FS$ until it reached the state $\FS^*$.
+Our set if commands is sufficient to record any change, as
+there are commands for every input and output type pair, therefore
+we know that the changes can be recorded as a sequence of commands $S$
+where $S\FS=\FS^*$.
+Note that $S$ will not contain assertion commands, as they do not
+represent an actual change in the filesystem.
+
+Therefore, \cref{connected_changes} applies to $S$ and we know
+if it contains commands on $\nn$ and $n$ where $\nn\descendant n$,
+then it also contains commands on nodes in between;
+which is equivalent to saying that if $\FS$ changed
+at node $\nn$ and $n$, then it had to change on the nodes in between.
+
+If so, then, similarly to what happens in the ordering algorithm,
+we can separate $S$ into components of commands on related nodes,
+as commands from separate components freely commute yielding an equivalent sequence.
+From the arguments above, we also know that each component
+must be made up of only desctruction or only construction pairs,
+but not a mixture of the two.
+This means that in each component, parents either strictly precede or succeed child nodes
+(as otherwise $S\equiv\cbrk$ would hold),
+from which it follows that once the components are separated
+in a new sequence $S'\equiv S$,
+commands on the same nodes are next to each other in $S'$.
+
+Based on \cref{ax_same_emptyseq,ax_same_singlec} there is
+an $S''\eqnrw S'$ in which multiple commands on the same nodes
+are simplified into a single command or an empty sequence,
+and therefore $S''$ is simple and $S\equiv S'\eqext S''$.
+It is easy to see that $S''$ must contain the same commands
+as the output of the update detector, $U$, as both are simple
+but reflect all changes between $\FS$ and $\FS^*$.
+If so, then based on \cref{simple_reorder_equiv}
+we have $S''\in\orderset{U}$, from which
+$S\equiv S'\eqext S''\equiv U$, and as $S\FS = \FS^* \neq \fsbroken$,
+therefore $U\FS\neq\fsbroken$.
+\end{proof}
 

### 2015-11-28 2015/paper.tex
Correctness of update detection is a theorem

@@
 For any simple sequence $S\neq\cbrk$,
-$T\equiv S \Leftrightarrow T\in\orderset{S}$.
+$\forall T: T\equiv S \Leftrightarrow T\in\orderset{S}$.
 \end{mylem}
@@
 
-\begin{mylem}\label{update_works}
-A sequence returned by the update detector
+\begin{myth}\label{update_works}
+A sequence of commands returned by the update detector
 when comparing $\FS^*$ to the original $\FS$
 will not break $\FS$ if it is applied to it.
-\end{mylem}
+\end{myth}
 \begin{proof}
@@
 
-For
+For the proposition
 \[ \worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \]

### 2015-11-30 2015/paper.tex
New notation for commands

@@
 \newcommand{\setv}{\mathcal{V}} % Set of values
-\newcommand{\setvx}[1]{\mathcal{V}_{#1}}
+\newcommand{\setvx}[1]{\mathcal{V}_{#1}} % Set of values with custom index
 \newcommand{\setf}{\setvx{F}} % Set of file values
@@
 \newcommand{\cbrk}{\mathtt{break}} % 'break' command
-\newcommand{\fscommand}[2]{{#1#2}}
-\newcommand{\fsregcommandchar}[1]{\mathtt{#1}}
-\newcommand{\fsregcommand}[2]{\fscommand{\fsregcommandchar{#1}}{\fsregcommandchar{#2}}}
-\newcommand{\cbb}{\fsregcommand{\empt}{\empt}}
-\newcommand{\cbf}{\fsregcommand{\empt}{F}}
-\newcommand{\cbd}{\fsregcommand{\empt}{D}}
-\newcommand{\cfb}{\fsregcommand{F}{\empt}}
-\newcommand{\cff}{\fsregcommand{F}{F}}
-\newcommand{\cfd}{\fsregcommand{F}{D}}
-\newcommand{\cdb}{\fsregcommand{D}{\empt}}
-\newcommand{\cdf}{\fsregcommand{D}{F}}
-\newcommand{\cdd}{\fsregcommand{D}{D}}
-\newcommand{\cxy}{\fscommand{X}{Y}}
-\newcommand{\cyx}{\fscommand{Y}{X}}
-\newcommand{\cyz}{\fscommand{Y}{Z}}
-\newcommand{\cxz}{\fscommand{X}{Z}}
-\newcommand{\cxw}{\fscommand{X}{W}}
-\newcommand{\czw}{\fscommand{Z}{W}}
-\newcommand{\cqr}{\fscommand{Q}{R}}
-\newcommand{\cqq}{\fscommand{Q}{Q}}
-
-\newcommand{\typeset}{\{\fsregcommandchar{D},\fsregcommandchar{F},\empt\}} % Set of types in commands
+\newcommand{\ccharb}{\empt}
+\newcommand{\ccharf}{\mathtt{F}}
+\newcommand{\cchard}{\mathtt{D}}
+\newcommand{\vald}{d} % Directory value
+\newcommand{\valdi}{d_1}
+\newcommand{\valdii}{d_2}
+\newcommand{\valf}{f} % File value
+\newcommand{\valvx}{v_X} % Value of type X
+\newcommand{\valvy}{v_Y} % Value of type Y
+\newcommand{\valvw}{v_W}
+\newcommand{\valvr}{v_R}
+\newcommand{\typeset}{\{\cchard,\ccharf,\ccharb\}} % Set of types in commands
+\newcommand{\caa}[2]{\langle{#1,#2}\rangle}
+\newcommand{\caaa}[3]{\langle{#1,#2,#3}\rangle}
+\newcommand{\caaaa}[4]{\langle{#1,#2,#3,#4}\rangle}
+\newcommand{\cbb}{\caa{\ccharb}{\ccharb}}
+\newcommand{\cbba}[1]{\caaa{\ccharb}{\ccharb}{#1}}
+\newcommand{\cbf}{\caa{\ccharb}{\ccharf}}
+\newcommand{\cbfaa}[2]{\caaaa{\ccharb}{\ccharf}{#1}{#2}}
+\newcommand{\cbd}{\caa{\ccharb}{\cchard}}
+\newcommand{\cbdaa}[2]{\caaaa{\ccharb}{\cchard}{#1}{#2}}
+\newcommand{\cfb}{\caa{\ccharf}{\ccharb}}
+\newcommand{\cfba}[1]{\caaa{\ccharf}{\ccharb}{#1}}
+\newcommand{\cff}{\caa{\ccharf}{\ccharf}}
+\newcommand{\cfd}{\caa{\ccharf}{\cchard}}
+\newcommand{\cfdaa}[2]{\caaaa{\ccharf}{\cchard}{#1}{#2}}
+\newcommand{\cdb}{\caa{\cchard}{\ccharb}}
+\newcommand{\cdba}[1]{\caaa{\cchard}{\ccharb}{#1}}
+\newcommand{\cdf}{\caa{\cchard}{\ccharf}}
+\newcommand{\cdfaa}[2]{\caaaa{\cchard}{\ccharf}{#1}{#2}}
+\newcommand{\cdd}{\caa{\cchard}{\cchard}}
+\newcommand{\cdda}[1]{\caaa{\cchard}{\cchard}{#1}}
+\newcommand{\cxy}{\caa{X}{Y}}
+\newcommand{\cxyaa}[2]{\caaaa{X}{Y}{#1}{#2}}
+\newcommand{\cxynv}{\caaaa{X}{Y}{n}{\valvy}}
+\newcommand{\cxynnv}{\caaaa{X}{Y}{\nn}{\valvy}}
+\newcommand{\cxw}{\caa{X}{W}}
+\newcommand{\cxwnv}{\caaaa{X}{W}{n}{\valvw}}
+\newcommand{\czw}{\caa{Z}{W}}
+\newcommand{\czwnv}{\caaaa{Z}{W}{n}{\valvw}}
+\newcommand{\czwnnv}{\caaaa{Z}{W}{\nn}{\valvw}}
+\newcommand{\czwmv}{\caaaa{Z}{W}{m}{\valvw}}
+\newcommand{\cqr}{\caa{Q}{R}}
+\newcommand{\cqrmv}{\caaaa{Q}{R}{m}{\valvr}}
+\newcommand{\cqrov}{\caaaa{Q}{R}{o}{\valvr}}
+
 \newcommand{\cc}{\circ} % Command / sequence concatenation
@@
 
-In this paper, we write $F$ for an arbitrary element of $\setf$, and $D$ for an arbitrary element
-of $\setd$. $V$ is a value from $\setv$ and $n$ and $m$ are nodes in $\setn$.
+In this paper, we write $\valf$ for an arbitrary element of $\setf$, and $\vald$ for an arbitrary element
+of $\setd$. $TODO$ is a value from $\setv$ and $n$ and $m$ are nodes in $\setn$.
 
@@
 
+% TODO: tuple / quadruple
 We therefore propose to have a command for each pair of types.
 For want of a better system, we will name our commands by concatenating
-two of $\fsregcommandchar{D}$, $\fsregcommandchar{F}$ and $\fsregcommandchar{\empt}$, 
+two of $\cchard$, $\ccharf$ and $\ccharb$, 
 where the left sign denotes the type of value
 required in the filesystem before the command is applied, and the right sign notes the type
-afterwards. For example, $mkdir(n,D)$ is $\cbd(n,D)$, and $rmdir(n)$ is $\cdb(n)$.
+afterwards. For example, $mkdir(n,D)$ is $\cbdaa{n}{D}$, and $rmdir(n)$ is $\cdba{n}$.
 
@@
 We note that a command or a sequence of commands is applied to a filsystem
-by prefixing the command or sequence to it, for example: $\cbrk\FS$, $\cbd(n,D)\FS$, 
+by prefixing the command or sequence to it, for example: $\cbrk\FS$, $\cbdaa{n}{\vald}\FS$, 
 or $S\FS$ if $S$ is a sequence of commands.
@@
 \item
-All other commands have the generic form $\cxy(n,V_Y)$ where
+All other commands have the generic form $\cxynv$ where
 $X$ and $Y$ are types in $\typeset$,
-$n\in\setn$ and $V_Y$ is a value of the appropriate type from $\setvx{Y}$.
-At times we omit $V_Y$ if there is only one suitable value.
-\[ \cxy(n,V_Y)\FS = 
+$n\in\setn$ and $\valvy$ is a value of the appropriate type from $\setvx{Y}$.
+At times we omit $\valvy$ if there is only one suitable value.
+\[ \cxynv\FS = 
    \begin{cases}
@@
 In general, when we describe multiple or unknown commands, we may substitute one or both
-of their types with variables, as we did with $\cxy(n,V_Y)$. In this context,
-if we write that $\cxy=\czw$, we mean that the input and output types
+of their types with variables, as we did with $\cxynv$. In this context,
+if we write that $\cxy=\czw$, we mean that the input and output types % TODO needed?
 of the commands are the same ($X=Z$ and $Y=W$), while a full equiality 
-($\cxy(n,V_Y)=\czw(n,V_W)$)
+($\cxynv=\czwmv$)
 implies
@@
 We use $\cc$ to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence:
-$S=\cbd(n)\cc \cbf(m,F)$, or $S'=S\cc\cbb(o)$.
+$S=\cbdaa{n}{\vald}\cc\cbfaa{m}{\valf}$, or $S'=S\cc\cbba{o}$.
 We write $\emptyseq$ for the empty sequence.
@@
 Pairs of commands in general have the form
-\[ \cxy(n,V_Y)\cc  \czw(m,V_W) \]
+\[ \cxynv\cc  \czwmv \]
 where $X,Y,Z,W\in\typeset$, $n,m\in\setn$, 
 and values are of the appropriate type: 
-$V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$.
+$\valvy\in\setvx{Y}$ and $\valvw\in\setvx{W}$.
 
@@
 Commands on unrelated nodes commute:
-$\cxy(n,V_Y)\cc \czw(m,V_W) \equiv \czw(m,V_W)\cc \cxy(n,V_Y)$ where $n\unrel m$.
+$\cxynv\cc\czwmv \equiv \czwmv\cc\cxynv$ where $n\unrel m$.
 \end{myax}
@@
 Commands on unrelated nodes do not break every filesystem:
-$\cxy(n,V_Y)\cc \czw(m,V_W) \nequiv \cbrk$ where $n\unrel m$.
+$\cxynv\cc\czwmv \nequiv \cbrk$ where $n\unrel m$.
 \end{myax}
@@
 Commands on the same node break every filesystem if their types are incompatible:
-$\cxy(n,V_Y)\cc \czw(n,V_W) \equiv \cbrk$ where $Y\ne Z$.
+$\cxynv\cc\czwnv \equiv \cbrk$ where $Y\ne Z$.
 \end{myax}
@@
 Commands on the same node simplify:
-$\cxy(n,V_Y)\cc \czw(n,V_W) \eqext \emptyseq$ where $Y=Z$ and $X=W=\fsregcommandchar{\empt}$ 
-or $X=W=\fsregcommandchar{D}$.
+$\cxynv\cc\czwnv \eqext \emptyseq$ where $Y=Z$ and $X=W=\ccharb$ 
+or $X=W=\cchard$.
 \end{myax}
@@
 Commands on the same node simplify:
-$\cxy(n,V_Y)\cc  \czw(n,V_W) \equiv \cxw(n,V_W)$ where $Y=Z$ and $XW\neq\cbb$ and $XW\neq\cdd$.
+$\cxynv\cc \czwnv \equiv \cxwnv$ where $Y=Z$ and $\cxw\neq\cbb$ and $\cxw\neq\cdd$.
 \end{myax}
@@
 Commands on distant relatives break all filesystems:
-$\cxy(\nn,V_Y)\cc  \czw(n,V_W) \equiv \cbrk$
-and $\czw(n,V_W)\cc \cxy(\nn,V_Y) \equiv\cbrk$
+$\cxynnv\cc\czwnv \equiv \cbrk$
+and $\czwnv\cc\cxynnv \equiv\cbrk$
 where $\nn\descendant n$ and $\nn\neq\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
@@
    % bd>bf
-            \cbd(\nn, D)\cc  \cbf(n, F) \\
+            \cbdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
    % bd>bd
-            \cbd(\nn, D_1)\cc  \cbd(n, D_2) \\
+            \cbdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii} \\
    % fd>bf
-            \cfd(\nn, D)\cc  \cbf(n, F) \\
+            \cfdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
    % fd>bd
-            \cfd(\nn, D_1)\cc  \cbd(n, D_2)
+            \cfdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii}
    \end{gather*}
@@
 All other commands on a child break every filesystem:
-$\cxy(\nn,V_Y)\cc  \czw(n,V_W) \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
+$\cxynnv\cc\czwnv \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
 and the pair is not a construction pair.
@@
    % fb<db ??
-            \cfb(n)\cc  \cdb(\nn) \\
+            \cfba{n}\cc  \cdba{\nn} \\
    % fb<df ??
-            \cfb(n)\cc  \cdf(\nn, F) \\
+            \cfba{n}\cc  \cdfaa{\nn}{\valf} \\
    % db<db ??
-            \cdb(n)\cc  \cdb(\nn) \\
+            \cdba{n}\cc  \cdba{\nn} \\
    % db<df ??
-            \cdb(n)\cc  \cdf(\nn, F)
+            \cdba{n}\cc  \cdfaa{\nn}{\valf}
    \end{gather*}
@@
 All other commands on a parent break every filsystem:
-$\cxy(n,V_Y)\cc  \czw(\nn,V_W) \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
+$\cxynv\cc\czwnnv \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
 and the pair is not a destruction pair.
@@
 and there must also be only one possible value for their output.
-Accordingly, in our current algebra, $\cbb(n)$ and $\cdd(n)$ are the only two assertion commands,
+Accordingly, in our current algebra, $\cbba{n}$ and $\cdda{n}$ are the only two assertion commands,
 and we do not note their output value as it is determined.
@@
 An assertion command can be added on a descendant node:
-$\cbb(n)\cc \cxy(\nn,V_Y) \equiv \cxy(\nn,V_Y) \equiv \cxy(\nn,V_Y)\cc \cbb(n)$ 
+$\cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n}$ 
 where $\nn\descendant n$ and $\cxy\neq\cdd$.
@@
 An assertion command can be added on an ancestor node:
-$\cdd(\nn)\cc \cxy(n,V_Y) \equiv \cxy(n,V_Y) \equiv \cxy(n,V_Y)\cc \cdd(\nn)$ 
+$\cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn}$ 
 where $\nn\descendant n$ and $\cxy\neq\cbb$.
@@
 Assertion commands can be removed:
-$\cxy(n,V_Y) \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
+$\cxynv \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
 \end{myax}
@@
 sufficient, as there are commands available for any input and output value. 
-Specifically, if at node $n$, $\FS(n)=X'$ and $\FS_A(n)=Y'\neq X'$, then we add the command $\cxy(n,Y')$ to $A$
+Specifically, if at node $n$, $\FS(n)=X'$ and $\FS_A(n)=Y'\neq X'$, then we add the command $\cxyaa{n}{Y'}$ to $A$
 where $X'\in\setvx{X}$ and $Y'\in\setvx{Y}$.
@@
 Let $A$ be a sequence that satisfies the conditions;
-we therefore know that it contains a command $\cxy(n,V_Y)$ on $n$
-and another command $\czw(\nn,V_W)$ on $\nn$.
+we therefore know that it contains a command $\cxynv$ on $n$
+and another command $\czwnnv$ on $\nn$.
 We use an indirect proof and assume that there are no commands on $\parent(n)$ in $A$.
@@
 If they are already next to each other in $A$, there is nothing to do.
-Otherwise, consider the command next to $\cxy(n,V_Y)$ in the direction where $\czw(\nn,V_W)$ is.
-Let this command be $\cqr(m,V_R)$.
+Otherwise, consider the command next to $\cxynv$ in the direction where $\czwnnv$ is.
+Let this command be $\cqrmv$.
 If $\czw$ is to the right, then $A$ looks like the following:
-\[ A = \cdots\cc\cxy(n,V_Y)\cc\cqr(m,V_R)\cc\cdots\cc\czw(\nn,V_W)\cc\cdots \]
-If $n\unrel m$, swap $\cxy$ and $\cqr$. Based on \cref{ax_separate_commute} we know that the new
+\[ A = \cdots\cc\cxynv\cc\cqrmv\cc\cdots\cc\czwnnv\cc\cdots \]
+If $n\unrel m$, swap $\cxynv$ and $\cqrmv$. Based on \cref{ax_separate_commute} we know that the new
 sequence is equivalent to $A$.
@@
 (Note that $A$ cannot contains assertion commands.)
-By repeating this step we can therefore convert $A$ into $A'$ where $\cxy$ and $\czw$ are neighboring commands.
+By repeating this step we can therefore convert $A$ into $A'$ where $\cxynv$ and $\czwnnv$ are neighboring commands.
 However, then \cref{ax_distantrel_breaks} applies to the sequence and therefore $A\equiv A'\equiv\cbrk$ which
@@
 An important property of simple sequences is that
-all of their valid permutations are equivalent,
-and all equivalent sequences are mere permutations:
+all of their valid orderings are equivalent,
+and all equivalent sequences are mere reorderings:
 
@@
 \begin{mydef}{Independent commands, sequences and sets.}
-For two commands $\cxy$ and $\czw$ we write $\cxy\indep\czw$ if $\cxy\cc \czw\equiv\czw\cc \cxy\nequiv\cbrk$.
+For two commands $\cxynv$ and $\czwmv$ we write $\cxynv\indep\czwmv$ if $\cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk$.
 For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
@@
 Two different commands that are not assertion commands are independent iff the nodes they change are unrelated:
-\[ \cxy(n,V_Y)\indep\czw(m,V_W) \Leftrightarrow n\unrel m \]
-if $\cxy(n,V_Y)\neq\czw(m,V_W)$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
+\[ \cxynv\indep\czwmv \Leftrightarrow n\unrel m \]
+if $\cxynv\neq\czwmv$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
 \end{mylem}
@@
 We proceed in two steps; first, we prove that
-\[ \cxy(n,V_Y)\nindep\czw(m,V_W) \wedge n\unrel m \] would lead to contradiction.
+\[ \cxynv\nindep\czwmv \wedge n\unrel m \] would lead to contradiction.
 By definition, if the two commands are not independent, then at least one of the following holds:
 \begin{itemize}
-\item $\czw(m,V_W)\cc \cqr(o,V_R) \equiv\cbrk$
-\item $\cqr(o,V_R)\cc \czw(m,V_W) \equiv\cbrk$
-\item $\czw(m,V_W)\cc \cqr(o,V_R) \nequiv \cqr(o,V_R)\cc \czw(m,V_W)$
+\item $\czwmv\cc \cqrov \equiv\cbrk$
+\item $\cqrov\cc \czwmv \equiv\cbrk$
+\item $\czwmv\cc \cqrov \nequiv \cqrov\cc \czwmv$
 \end{itemize}
@@
 Next, we prove that
-\[ \cxy(n,V_Y)\indep\czw(m,V_W) \wedge n\nunrel m \] would lead to contradiction.
+\[ \cxynv\indep\czwmv \wedge n\nunrel m \] would lead to contradiction.
 As $n\nunrel m$
@@
 The commands are not assertion commands, and so from \cref{ax_same_singlec}
-we know that $\cxy(n,V_Y)\cc\czw(n,V_W)\equiv\czw(n,V_W)\cc\cxy(n,V_Y)$ can only happen if $Y=W$ and $V_Y=V_W$.
+we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $Y=W$ and $\valvy=\valvw$.
 Therefore $X=Y=Z=W$ which is only possible if both commands are $\cff$ and have the same
@@
 from \cref{ax_distantrel_breaks} we know that if they are not directly related,
-then $\cxy(n,V_Y)\cc\czw(m,V_W)$ breaks all filesystems, and they cannot be independent.
+then $\cxynv\cc\czwmv$ breaks all filesystems, and they cannot be independent.
 From the construction and destruction pairs and 
@@
 even if they are directly related, either
-$\cxy(n,V_Y)\cc\czw(m,V_W)$ or $\czw(m,V_W)\cc\cxy(n,V_Y)$ 
+$\cxynv\cc\czwmv$ or $\czwmv\cc\cxynv$ 
 breaks all filesystems, so they again cannot be independent.
@@
 \begin{align*}
-\forall\FS: &\cxy(n,C_Y)\indep \czw(m,C_W) \\
-&\quad\wedge \cxy(n,C_Y)\FS\neq\fsbroken \\
-&\quad\wedge \czw(m,C_W)\FS\neq\fsbroken \\
-&\Rightarrow \cxy(n,C_Y)\cc \czw(m,C_W)\FS\neq\fsbroken.
+\forall\FS: &\cxynv\indep \czwmv \\
+&\quad\wedge \cxynv\FS\neq\fsbroken \\
+&\quad\wedge \czwmv\FS\neq\fsbroken \\
+&\Rightarrow \cxynv\cc \czwmv\FS\neq\fsbroken.
 \end{align*}
@@
 but it is easy to provide an indirect proof based on our filesystem model.
-Assume that $\cxy(n,C_Y)\cc \czw(m,C_W)\FS=\fsbroken$.
-We know $\cxy(m,C_Y)\FS\neq\fsbroken$ so it must be applying 
-$\czw(m,C_W)$ that breaks it.
+Assume that $\cxynv\cc \czwmv\FS=\fsbroken$.
+We know $\cxynv\FS\neq\fsbroken$ so it must be applying 
+$\czwmv$ that breaks it.
 Applying a command can only result in a broken filesystem in three cases.
@@
 but we know $\FS(m)\in\setvx{W}$ and so
-$(\cxy(m,C_Y)\FS)(m)\in\setvx{W}$ as based on \cref{unrelated_is_independent}, $n\neq m$.
+$(\cxynv\FS)(m)\in\setvx{W}$ as based on \cref{unrelated_is_independent}, $n\neq m$.
 Third, if the new filesystem violates the tree property.
@@
 and the tree property only depends on the types of the parent and children of $m$,
-which therefore cannot be changed by $\cxy(m,C_Y)$.
+which therefore cannot be changed by $\cxynv$.
 \end{proof}
@@
 If $A$ and $B$ are minimal sequences, $\works{A,B}$,
-and there are commands on node $n$ in both $A$ ($\cxy(n, V_Y)\in A$) and $B$ ($\czw(n, V_W)\in B$)
+and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$)
 then their input types must match ($X=Z$).
@@
 This is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
-either $\cxy(n, V_Y)$ or $\czw(n, V_W)$ would not break, 
+either $\cxynv$ or $\czwnv$ would not break, 
 and consequently $A$ and $B$ cannot work on the same filesystem.
@@
 \begin{mydef}{Inverse commands and sequences.}
-The inverse of command $\cxy(n,V_Y)$ is $\cxy(n,V_Y)^{-1} = \cyx(n,V_X)$
+The inverse of command $\cxynv$ is $\cxynv^{-1} = \caaaa{Y}{X}{n}{\valvx}$
 where $V_X$ is an arbitrary value from $\setvx{X}$.
@@
 Let us consider therefore the marked command preceded by an unmarked command in $A$,
-and let the marked command be $\cxy(n, V_Y)$, 
-and the preceding unmarked command be $\czw(m, V_W)$.
+and let the marked command be $\cxynv$, 
+and the preceding unmarked command be $\czwmv$.
 As $A$ is simple and $\works{A}$, from 
@@
 In either case, therefore,
-we have a minimal $B'$ which has a command on $m$ just before $\cxy(n, V_Y)$ and $B'\equiv B$.
-Let this command on $m$ be $\cqr(m, V_R)$.
+we have a minimal $B'$ which has a command on $m$ just before $\cxynv$ and $B'\equiv B$.
+Let this command on $m$ be $\cqrmv$.
 \begin{gather*}
-A = \cdots\cc  \czw(m, V_W)\cc  \cxy(n, V_Y)\cc  \cdots \\
-B' = \cdots\cc  \cqr(m, V_R)\cc  \cxy(n, V_Y)\cc  \cdots
+A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
+B' = \cdots\cc  \cqrmv\cc  \cxynv\cc  \cdots
 \end{gather*}
@@
 is always the same, and it is either $D$ or $\empt$ depending on the relationship between $n$ and $m$.
-Therefore $R=W$ and $\cqr(m, V_R)=\czw(m, V_W)$
+Therefore $R=W$ and $\cqrmv=\czwmv$
 as $|\setd|=|\setb|=1$. 
@@
 
-Let therefore the marked command in $S$ be $\cxy(n,V_Y)$
-and the preceding unmarked command be $\czw(m,V_W)$.
+Let therefore the marked command in $S$ be $\cxynv$
+and the preceding unmarked command be $\czwmv$.
 As $S$ is simple and $\works{S}$, from 
@@
 We also know that because of {\condApr} there must be 
-a command $\cqr(o,V_R)$ in $T$ which is not independent of $\czw(m,V_W)$
-as $\czw(m,V_W)$ is not part of $S^*$.
+a command $\cqrov$ in $T$ which is not independent of $\czwmv$
+as $\czwmv$ is not part of $S^*$.
 \begin{gather*}
-S = \cdots\cc  \czw(m, V_W)\cc  \cxy(n, V_Y)\cc  \cdots \\
-T = \cdots\cc  \cqr(o, V_R)\cc \cdots
+S = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
+T = \cdots\cc  \cqrov\cc \cdots
 \end{gather*}
 We know none of these commands is an assertion command, and 
-from {\condDisj} that $\cqr(o,V_R)\neq\czw(m,V_W)$.
+from {\condDisj} that $\cqrov\neq\czwmv$.
 Therefore, based on \cref{unrelated_is_independent} we know this means that
 either $m\descendantEq o$ or $o\descendantEq m$.
-From {\condApr} we also know that $\cxy(n,V_Y)\indep \cqr(o,V_R)$,
+From {\condApr} we also know that $\cxynv\indep \cqrov$,
 and so because of \cref{unrelated_is_independent},
@@
 
-We know that $T$ cannot have a command on $m$ as $m=\parent(n)$ and $\cxy(n,V_Y)\indep T$,
+We know that $T$ cannot have a command on $m$ as $m=\parent(n)$ and $\cxynv\indep T$,
 and so $m\neq o$ and therefore $m\descendant o$.
 This means we can create a new sequence $T'\equiv T$ by inserting a command on 
-$m$ into $T$ before $\cqr(o,V_R)$
+$m$ into $T$ before $\cqrov$
 according to \cref{ax_parent_assert}.
-We now have $\cxy(n,V_Y)\indep T\equiv T'$ which is a contradiction as
+We now have $\cxynv\indep T\equiv T'$ which is a contradiction as
 $T'$ has a command on $m$ and $m=\parent(n)$.
@@
 
+\medskip
+
+% Reconciliation is maximal
+% -------------------------
+% This is where we're using |D|=1
+% C.f. strict / liberal etc. reconciliation in references
+
 % TODO

### 2015-12-02 2015/paper.tex
Proof for the completeness of reconciliation. Only one more proof to go!

@@
 
-\newcommand{\typeeq}{\stackrel{t}{=}}
+\newcommand{\typeeq}{\stackrel{t}{=}} % Type equality
 \newcommand{\ntypeeq}{\centernot{\stackrel{t}{=}}}
@@
 
+\newcommand{\acb}{(A\cap B)}
+\newcommand{\acbi}{\acb^{-1}}
+\newcommand{\amb}{(A\setminus B)}
+\newcommand{\bma}{(B\setminus A)}
+
 \theoremstyle{definition}
@@
 
-\newtheorem{myax}{Axiom}
-\crefname{myax}{axiom}{axioms}
+\newtheorem{myax}{Rule}
+\crefname{myax}{rule}{rules}
 
@@
 
-\title{The Correctness of Algebraic File Synchronization}
-
+\title{Complete Algebraic File Synchronization}
 \author{Elod Pal Csirmaz}
@@
 \section{Introduction}
+
+% TODO Thank-you Laszlo Csirmaz, Bill Zissimopoulos
 
@@
 
-In this paper, we write $\valf$ for an arbitrary element of $\setf$, and $\vald$ for an arbitrary element
-of $\setd$. $TODO$ is a value from $\setv$ and $n$ and $m$ are nodes in $\setn$.
+In this paper, 
+we write $n$ and $m$ for nodes in $\setn$,
+and use lowercase Greek letters to denote commands. % TODO but very rarely
+We use $\valf$ for an arbitrary element of $\setf$, and $\vald$ for an arbitrary element
+of $\setd$. $TODO$ is a value from $\setv$ .
 
@@
 
-\section{Investigating command pairs}
+\section{Investigating command pairs}\label{section_axioms}
 
@@
 We use an indirect proof and assume that there are no commands on $\parent(n)$ in $A$.
-Next, we create a new sequence $A'\equiv A$ in which $\cxy$ and $\czw$ are next to each other.
+Next, we create a new sequence $A'\equiv A$ in which $\cxynv$ and $\czwnnv$ are next to each other.
 If they are already next to each other in $A$, there is nothing to do.
@@
 Let this command be $\cqrmv$.
-If $\czw$ is to the right, then $A$ looks like the following:
+If $\czwnnv$ is to the right, then $A$ looks like the following:
 \[ A = \cdots\cc\cxynv\cc\cqrmv\cc\cdots\cc\czwnnv\cc\cdots \]
@@
 on its parent node (if there is one). 
-If the command removes content at this node (it is of the form $X\empt$), 
+If the command removes content at this node (it is of the form $\caa{X}{\ccharb}$), 
 then it must follow all other commands in the component, and
@@
 but reflect all changes between $\FS$ and $\FS^*$.
-If so, then based on \cref{simple_reorder_equiv}
-we have $S''\in\orderset{U}$, from which
+If so, then $S''\in\orderset{U}$ and based on \cref{simple_reorder_equiv}
+we have
 $S\equiv S'\eqext S''\equiv U$, and as $S\FS = \FS^* \neq \fsbroken$,
@@
 For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
-$\forall a\in A \mbox{~and~} \forall b\in B: a\indep b$.
+$\forall \alpha\in A \mbox{~and~} \forall \beta\in B: \alpha\indep\beta$.
 \end{mydef}
@@
 \begin{align*}
-\reca = \{c| & \\
-& c\in A\setminus B \\
+\reca = \{\alpha| & \\
+& \alpha\in A\setminus B \\
 & \wedge \\
-& \forall c'\in B\setminus A: c\indep c'\\
+& \forall \beta\in B\setminus A: \alpha\indep\beta\\
 \} &
@@
 
-In other words, the sequence $\reca$ we apply to $\FS_B$ consists of all commands from $A\setminus B$
-that are independent of every command in $B\setminus A$.
+In other words, the sequence $\reca$ we apply to $\FS_B$ 
+is the largest subset of $A\setminus B$
+that is independent of $B\setminus A$.
 The order of commands in the sequence can be determined using the algorithm described in
@@
 \begin{proof}
-We proceed in two steps; first, we prove that
-\[ \cxynv\nindep\czwmv \wedge n\unrel m \] would lead to contradiction.
-By definition, if the two commands are not independent, then at least one of the following holds:
-\begin{itemize}
-\item $\czwmv\cc \cqrov \equiv\cbrk$
-\item $\cqrov\cc \czwmv \equiv\cbrk$
-\item $\czwmv\cc \cqrov \nequiv \cqrov\cc \czwmv$
-\end{itemize}
-However, from \cref{ax_separate_commute,ax_separate_nobreaks} we also know that
-if $n\unrel m$ then none of the above can be true.
+This is easy to show based on the output of the software that investigates the behavior of command pairs,
+and which we used to derive the \namecrefs{ax_separate_commute} in \cref{section_axioms}.
+However, this proposition can also be derived from the \namecrefs{ax_separate_commute} already listed
+in the following way.
+
+We proceed in two steps. First, we note that
+from \cref{ax_separate_commute,ax_separate_nobreaks} we know that
+if $n\unrel m$, then $\cxynv$ and $\czwmv$ must necessarily be independent, and therefore
+$ \cxynv\nindep\czwmv \wedge n\unrel m $ cannot be the case.
 
 Next, we prove that
-\[ \cxynv\indep\czwmv \wedge n\nunrel m \] would lead to contradiction.
+\[ \cxynv\indep\czwmv \wedge n\nunrel m \] is also impossible as it would lead to contradiction.
 As $n\nunrel m$
@@
 \begin{mylem}\label{indep_prefix_combine}
-The combination of sequences with a common head and independent tails continues to work under the same conditions:
+The combination of sequences with a common head and independent tails 
+continues to work under the same conditions:
 \[ \worksc{A\cc B}{\seqset{S}} \wedge \worksc{A\cc C}{\seqset{S}} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{\seqset{S}} \]
@@
 \begin{align*}
-\reca = \{c| & \\
-& c\in A\setminus B \\
+\reca = \{\alpha| & \\
+& \alpha\in A\setminus B \\
 & \wedge \\
-& \forall c'\in B\setminus A: c\indep c'\\
+& \forall \beta\in B\setminus A: \alpha\indep\beta\\
 \}. &
@@
 from \cref{lemma:neighbor}
-we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxy$ (also in $B$),
+we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxynv$ (also in $B$),
 and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
@@
 If $B$ has no command on $m$, then let $B'$ be $B$, 
-but with an extra command added to it just before $\cxy$
+but with an extra command added to it just before $\cxynv$
 according to \cref{ax_child_assert,ax_parent_assert}, 
@@
 If $B$ originally had a command on $m$,
-this is a contradiction as $\czw$ was not marked, but we see it must also be in $B'$ and therefore in $B$.
+this is a contradiction as $\czwmv$ was not marked, but we see it must also be in $B'$ and therefore in $B$.
 If $B$ had no command on $m$,
@@
 
-\newcommand{\acb}{(A\cap B)}
-\newcommand{\acbi}{\acb^{-1}}
-\newcommand{\amb}{(A\setminus B)}
-\newcommand{\bma}{(B\setminus A)}
 We would like to prove that $\worksc{B\cc \reca}{A,B}$.
@@
 
-\medskip
+\subsection{Reconciliation is complete}
 
@@
 % This is where we're using |D|=1
-% C.f. strict / liberal etc. reconciliation in references
-
-% TODO
-TODO: $\reca$ is maximal
+% TODO C.f. strict / liberal etc. reconciliation in references
+
+The reconciliation algorithm defined above is also complete, that is,
+it is not possible to apply any further commands from $A\setminus B$ to $\FS_B$.
+To show this, we are going to prove the following \namecref{rec_is_complete}:
+
+\begin{myth}\label{rec_is_complete}
+If $A$ and $B$ are simple sequences,
+and we select a sequence $S\subset \amb$ so that
+it contains a command $\cxynv$ for which $\cxynv\nindep\bma$,
+then $B\cc S$ either breaks all filesystems $A$ and $B$ do not break
+(that is, $S$ breaks all possible $\FS_B$ replicas),
+or it overrides incompatible changes introduced in the replica by $B$.
+\end{myth}
+Overriding changes is not desirable as in these cases the reconciler
+does not have enough information to decide whether to promote
+the change introduced by $A$ over that introduced by $B$ or vice versa.
+These cases should be treated as conflicts and
+the affected nodes or commands marked for review
+by a human or a different system.
+\begin{proof}
+The proof is similar to the ones we have seen above.
+Without loss of generality, we assume that $\cxynv$ is the first command in $S$
+that is not independent of $\bma$.
+If so, we can split $S$ into $S_0\cc\cxynv\cc S_1$ where $S_0\indep\bma$.
+Let us also split $\bma$ into $T_0\cc\czwmv\cc T_1$ where $T_1\indep\cxynv$.
+From \cref{can_move_intersection} we know that
+$B\cc S \equiv \acb\cc\bma\cc S$.
+We also know commands in $S_0$ and $\bma$ commute, and so this is equivalent to
+$\acb\cc S_0\cc\bma\cc\cxynv\cc S_1$.
+Expanding $\bma$ and swapping $T_1$ and $\cxynv$ we get
+\[ \acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv\cc T_1\cc S_1. \]
+
+First, we prove that this sequence breaks all filesystems
+unless $n=m$.
+Let us therefore suppose $n\neq m$ and, to use an inverse proof,
+that the sequence works on $\FS$ where $A\FS\neq\fsbroken$.
+If so, its prefix, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also work.
+
+We know $\cxynv\nindep\czwmv$, and so from \cref{unrelated_is_independent}, $n\nunrel m$.
+As the sequence works, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
+As $\czwmv$ and $T_0$ originate from $B\setminus A$ and $B$ is simple, we also know there are
+no commands on $m$ in $A\cap B$ or $T_0$,
+and that there are no commands on $m$ in $S_0$ as $S_0\indep\bma$.
+
+On the one hand we therefore know that $\FS(m)$ must be of type $Z$,
+but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},
+we also know that $\cxynv$ cannot be applied to $\FS$ without
+changing $\FS(m)$ first.
+As $A\FS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
+Let this command be $\cqrmv$.
+
+Clearly $Q=Z$ (from \cref{worksinputmatch}), and from the construction and destruction
+pairs we also see that $R=W$ must hold, where $W=\cchard$ or $W=\ccharb$.
+As $|\setd|=1$ and $|\setb|=1$, this also means that $v_R=v_W$ and therefore
+$\cqrmv = \czwmv$.
+This is a contradiction as $\cqrmv\in A$, but $\czwmv\in\bma$.
+
+The only possibility is therefore $n=m$.
+As $A$ and $B$ are simple, we therefore know that these are the first commands on $n$,
+and so (again from \cref{worksinputmatch}) $Z=X$.
+We also know $\valvw\neq\valvy$ as otherwise the two commands would be equal and
+would be included in $A\cap B$,
+but this means that $\cxynv$, from $A$, overrides a change introduced 
+by $\czwnv$, from $B$, which should be treated as a conflict.
+\end{proof}
+
+From the proof it is apparent that this result depends on $|\setd|=1$.
 
@@
 
-% TODO
-TODO: Are these results quite obvious as this is a well-known kind of algebra or system?
+TODO: next steps. multiple replicas
 

### 2015-12-03 2015/paper.tex
Final proof

@@
 \begin{proof}
-TODO
+First, as $S$ only has at most one command on each node,
+any sequence in $\orderset{S}$ either breaks a filesystem,
+or it leaves it in the same state as $S$.
+
+Second, based on the algorithm we also know that $\orderset{S}$ contains
+all possible orderings of $S$ as the only ordering between commands
+it prescribes are when the commands in the reverse order would break every filesystem.
+
+If, for example, in a component or sub-component
+made up of construction pairs,
+the command on the topmost node, $\cxynv$, was not before all other commands
+in the component as described by the algorithm,
+then any resulting sequence would necessarily contain
+a $\czwmv$ where $n\descendant m$, potentially followed by commands
+on unrelated paths, and then followed by $\cxynv$.
+From \cref{ax_separate_commute} we know we can convert this sequence
+to an equivalent sequence by swapping the unrelated commands with
+$\czmv$, which sequence would therefore have the commands on
+$m$ and $n$ next to each other. Then from \cref{ax_distantrel_breaks,ax_directparent_breaks}
+we know the sequence would break all filesystems
+as a reversed construction pair is never a valid destruction pair.
+
+We can prove that an order not generated by the algorithm
+in case of components made of destruction pairs breaks all filesystems
+in a similar way.
+
+Also, from \cref{ax_separate_commute} we know
+that the order between any other command pairs is not fixed in the sense
+that if one order works, so will the other.
+
+From these we know that all sequences in $\orderset{S}$
+are equivalent, and that any sequence $T$ outside it
+necessarily breaks all filesystems.
+
+Therefore if $S\nequiv\cbrk$ then $S\in\orderset{S}$,
+and $S$ cannot equivalent to any sequence of the same commands
+not in $\orderset{S}$.
 \end{proof}

### 2015-12-04 2015/axioms.tex
Split source into sections

--- 2015-11-30 2015/paper.tex
@@
-\documentclass[12pt]{article}
-
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{centernot}
-\usepackage{tikz}
-\usepackage{cleveref}
-
-\newcommand{\setv}{\mathcal{V}} % Set of values
-\newcommand{\setvx}[1]{\mathcal{V}_{#1}} % Set of values with custom index
-\newcommand{\setf}{\setvx{F}} % Set of file values
-\newcommand{\setd}{\setvx{D}} % Set of directory values
-\newcommand{\setb}{\setvx{\empt}} % Set of empty values
-\newcommand{\setn}{\mathcal{N}} % Set of nodes / paths
-\newcommand{\empt}{\bot}
-\newcommand{\parent}{\mathtt{parent}}
-\newcommand{\topnode}{\mathtt{None}} % return value of parent()
-\newcommand{\fsbroken}{\mathtt{Broken}} % broken FS value
-\newcommand{\FS}{\Phi} % a filesystem
-\newcommand{\GS}{\Xi} % another filesystem
-\newcommand{\nn}{n^*} % parent node
-
-\newcommand{\cbrk}{\mathtt{break}} % 'break' command
-\newcommand{\ccharb}{\empt}
-\newcommand{\ccharf}{\mathtt{F}}
-\newcommand{\cchard}{\mathtt{D}}
-\newcommand{\vald}{d} % Directory value
-\newcommand{\valdi}{d_1}
-\newcommand{\valdii}{d_2}
-\newcommand{\valf}{f} % File value
-\newcommand{\valvx}{v_X} % Value of type X
-\newcommand{\valvy}{v_Y} % Value of type Y
-\newcommand{\valvw}{v_W}
-\newcommand{\valvr}{v_R}
-\newcommand{\typeset}{\{\cchard,\ccharf,\ccharb\}} % Set of types in commands
-\newcommand{\caa}[2]{\langle{#1,#2}\rangle}
-\newcommand{\caaa}[3]{\langle{#1,#2,#3}\rangle}
-\newcommand{\caaaa}[4]{\langle{#1,#2,#3,#4}\rangle}
-\newcommand{\cbb}{\caa{\ccharb}{\ccharb}}
-\newcommand{\cbba}[1]{\caaa{\ccharb}{\ccharb}{#1}}
-\newcommand{\cbf}{\caa{\ccharb}{\ccharf}}
-\newcommand{\cbfaa}[2]{\caaaa{\ccharb}{\ccharf}{#1}{#2}}
-\newcommand{\cbd}{\caa{\ccharb}{\cchard}}
-\newcommand{\cbdaa}[2]{\caaaa{\ccharb}{\cchard}{#1}{#2}}
-\newcommand{\cfb}{\caa{\ccharf}{\ccharb}}
-\newcommand{\cfba}[1]{\caaa{\ccharf}{\ccharb}{#1}}
-\newcommand{\cff}{\caa{\ccharf}{\ccharf}}
-\newcommand{\cfd}{\caa{\ccharf}{\cchard}}
-\newcommand{\cfdaa}[2]{\caaaa{\ccharf}{\cchard}{#1}{#2}}
-\newcommand{\cdb}{\caa{\cchard}{\ccharb}}
-\newcommand{\cdba}[1]{\caaa{\cchard}{\ccharb}{#1}}
-\newcommand{\cdf}{\caa{\cchard}{\ccharf}}
-\newcommand{\cdfaa}[2]{\caaaa{\cchard}{\ccharf}{#1}{#2}}
-\newcommand{\cdd}{\caa{\cchard}{\cchard}}
-\newcommand{\cdda}[1]{\caaa{\cchard}{\cchard}{#1}}
-\newcommand{\cxy}{\caa{X}{Y}}
-\newcommand{\cxyaa}[2]{\caaaa{X}{Y}{#1}{#2}}
-\newcommand{\cxynv}{\caaaa{X}{Y}{n}{\valvy}}
-\newcommand{\cxynnv}{\caaaa{X}{Y}{\nn}{\valvy}}
-\newcommand{\cxw}{\caa{X}{W}}
-\newcommand{\cxwnv}{\caaaa{X}{W}{n}{\valvw}}
-\newcommand{\czw}{\caa{Z}{W}}
-\newcommand{\czwnv}{\caaaa{Z}{W}{n}{\valvw}}
-\newcommand{\czwnnv}{\caaaa{Z}{W}{\nn}{\valvw}}
-\newcommand{\czwmv}{\caaaa{Z}{W}{m}{\valvw}}
-\newcommand{\cqr}{\caa{Q}{R}}
-\newcommand{\cqrmv}{\caaaa{Q}{R}{m}{\valvr}}
-\newcommand{\cqrov}{\caaaa{Q}{R}{o}{\valvr}}
-
-\newcommand{\cc}{\circ} % Command / sequence concatenation
-\newcommand{\descendant}{\prec}
-\newcommand{\descendantEq}{\preceq}
-\newcommand{\ancestor}{\succ}
-\newcommand{\ancestorEq}{\succeq}
-
-\newcommand{\eqext}{\sqsubseteq} % equivalent to
-\newcommand{\eqnrw}{\sqsupseteq} % extended by
-\newcommand{\nequiv}{\not\equiv}
-\newcommand{\indep}{\mathrel{\wr\wr}} % Independent commands, sequences
-\newcommand{\unrel}{\indep} % Unrelated nodes
-\newcommand{\nindep}{\,{\centernot{\wr\wr}}\,} % not \indep
-\newcommand{\nunrel}{\nindep} % not \unrel
-
-\newcommand{\workssign}{\mathbf{w}}
-\newcommand{\works}[1]{\workssign({#1})}
-\newcommand{\worksc}[2]{\workssign({#1}\mathrel{|}{#2})}
-
-\newcommand{\typeeq}{\stackrel{t}{=}}
-\newcommand{\ntypeeq}{\centernot{\stackrel{t}{=}}}
-
-\newcommand{\emptyseq}{\lambda} % empty sequence
-
-\newcommand{\orderset}[1]{\vec{\wp}({#1})}
-\newcommand{\seqset}[1]{\underline{#1}} % Set of sequences
-
-\newcommand{\recchar}[3]{{#1}^{#3}_{\mathcal{R}|{#2}}}
-\newcommand{\reca}{\recchar{A}{B}{}} % Reconciled from A
-\newcommand{\recb}{\recchar{B}{A}{}} % Reconciled from B
-
-\theoremstyle{definition}
-
-\newtheorem{mydef}{Definition}
-\crefname{mydef}{definition}{definitions}
-
-\newtheorem{myax}{Axiom}
-\crefname{myax}{axiom}{axioms}
-
-\newtheorem{mylem}{Lemma}
-\crefname{mylem}{lemma}{lemmas}
-
-\newtheorem{myth}{Theorem}
-\crefname{myth}{theorem}{theorems}
-
-\newtheorem{mycor}{Corollary}
-\crefname{mycor}{corollary}{corollaries}
-
-\title{The Correctness of Algebraic File Synchronization}
-
-\author{Elod Pal Csirmaz}
-
-\begin{document}
-\maketitle
-\begin{abstract}
-Abstract goes here
-\end{abstract}
-
-\section{Introduction}
-
-Synchronizing data structures, and filesystems in particular,
-is a task that we encounter more and more often in our world
-of multiple mobile devices, cloud solutions and distributed systems.
-Applications of synchronization ranges from
-solutions for end users who expect to access personal data seamlessly
-on multiple devices and personal clouds to geographically distributed server networks
-that need to synchronize themselves with low latency to serve the 
-same content.
-
-In this paper we
-continue the work in \cite{NREC:alg} and add to the theoretical understanding
-of synchronization based not on filesystem states, but filesystem changes or commands.
-
-% Synchronization:
-% Main aim: apply updates (where possible) from other replicas
-% update detection -> conflict detection -> merging updates -> ordering updates -> apply updates from other replicas
-% Problems: conflict detection, ordering
-
-% ORDERING - because when taking updates from different replicas we get an essentially unordered set
-% Insight: (Prof. Norman Ramsey)
-% - updates where two orders (AB vs BA) are not equivalent are incompatible
-% - we only have a set of updates and need to create an order
-
-% New:
-% better command (instruction) set
-% simpler reconciliation algorithm
-% proof of correctness
-
-\section{Definition of a Filesystem}
-
-We model a filesystem using a function $\FS$ with a set of nodes (filesystem paths) $\setn$ as its domain,
-and a set of possible contents $\setv$ as its codomain:
-\[ \FS : \setn \rightarrow \setv \] 
-In our model, $\setn$ contains all possible nodes, including the ones where there is no file or directory,
-and $\setv$ contains a special element, $\empt$, which is the value of $\FS$ at an empty node.
-We consider the contents of files, as well as any meta-information of files
-and directories (e.g. permissions or flags) part of the values in $\setv$.
-
-The nodes form a disjoint union of rooted directed trees.
-\begin{mydef}
-The function $\parent(n)$ returns the parent node of $n$, or
-returns $\topnode$ if $n$ is the root of a tree.
-\end{mydef}
-
-Every filesystem has a so-called \textbf{tree property}, which means that
-if the filesystem is not empty at a node, and the node has a parent,
-then there must be a directory at the parent node.
-
-To model this, in $\setv$ we distinguish between files ($\setf$) and directories ($\setd$), that is,
-if $\setb = \{\empt\}$ then:
-\[ \setv = \setb \cup \setf \cup \setd \]
-The tree propety can then be defined as
-\begin{align*}
-\forall n\in\setn: &\FS(n) \neq \empt \\ % TODO alignment problem
-&\quad\wedge \parent(n) \neq \topnode \\
-&\Rightarrow \FS(\parent(n)) \in \setd 
-\end{align*}
-This means that as we move down from the root of a tree of nodes,
-the types of values we encounter in the filesystem can only change according to the following
-transition diagram:
-
-\input{type-transition}
-
-In this paper, we write $\valf$ for an arbitrary element of $\setf$, and $\vald$ for an arbitrary element
-of $\setd$. $TODO$ is a value from $\setv$ and $n$ and $m$ are nodes in $\setn$.
-
-\section{Introducing commands}
-
-Next we need to define commands on the filesystem.
-
-% <<<<<<<< TODO Rewrite: no algebra
-%  about which we will reason
-% using our algebra.
-% We will aim to draw conclusions or judgements about commands and sequences of commands
-% based on the algebra we are aiming to construct.
-% For example, if we believe that two sequences of commands are equivalent as their effect
-% is the same, then we aim to be able to derive this from the axioms and inference rules of the
-% algebra.
-% As the algebra operates on commands only,
-% these judgements, by definition, need to hold regardless of the filesystem the commands are applied to.
-% Accordingly, we expect that the more information one encodes into the commands and the sequences,
-% the better predicitons we will be able to make using our algebra,
-% as then the commands and sequences will be more specific, and will select a smaller subset
-% of potential filesystems on which they can meaningfully operate.
-% >>>>>>>>>> to here
-
-...
-
-Let us consider what kind of information may be encoded in the commands.
-A usual set of commands, based on the most frequent tools implemented by filesystems,
-might be $create(n,V)$, $edit(n,V)$ and $remove(n)$ where $n\in\setn$ and $V\in\setv$ (but $V\neq\empt$).
-Regarding their output, that is, the state of the filesystem at $n$
-after applying the command,
-we know that after $create$ or $edit$, $\FS(n)\neq\empt$, whereas after $remove$,
-$\FS(n)$ will be $\empt$. 
-However, from \cite{NREC:alg} we know that a useful set of axioms
-will in some cases need to distinguish between edits that result in directories ($edit(n,D)$) and
-ones that result in files ($edit(n,F)$), and treat them as separate commands.
-Indeed, Bill Zissimopoulos suggested (\cite{BZ}) that extending this distinction to more commands
-utlimately simplifies
-the definition of conflicting commands, as our model will then able to predict the behavior of commands
-more precisely.
-In other words, encoding the type of the output ($D$, $F$ or $\empt$) in the commands is definitely useful.
-At the same time, there is never any need to encode information about the
-\emph{exact} output value of a command,
-as the success or failure of filesystem commands only depend on the types of values in the filesystem.
-
-Notice, however, that the commands listed above also encode some information about 
-their input, the filesystem
-\emph{before} the command is applied; namely, $create(n,V)$ requires that there are no files
-or directories at $n$, while $edit(n,V)$ and $remove(n)$ require the opposite.
-This creates an arbitrary asymmetry where
-there is now more information encoded into commands about their output than about their input.
-In line with the aim to encode as much information as possible in the commands, % TODO Where is this mentioned?
-and in order to resolve this asymmetry, we propose a set of commands that encode
-the type of the original state of $\FS(n)$ as well.
-(Some real-life filesystem commands like $rmdir$ do this already.)
-
-% TODO: tuple / quadruple
-We therefore propose to have a command for each pair of types.
-For want of a better system, we will name our commands by concatenating
-two of $\cchard$, $\ccharf$ and $\ccharb$, 
-where the left sign denotes the type of value
-required in the filesystem before the command is applied, and the right sign notes the type
-afterwards. For example, $mkdir(n,D)$ is $\cbdaa{n}{D}$, and $rmdir(n)$ is $\cdba{n}$.
-
-A command can only succeed if the original value at node $n$ has a type that matches
-the input type of the command. If this is not the case, or if the resulting
-filesystem no longer has the tree property, then we say that the command
-{\em breaks} the filesystem. Broken filesystems are considered equal
-(but not equal to any working filesystem), and we note them by $\FS=\fsbroken$.
-
-So that we could reason about sequences of commands that break every filesystem
-in the algebra, we introduce the command $\cbrk$ that simply breaks every filesystem.
-
-We note that a command or a sequence of commands is applied to a filsystem
-by prefixing the command or sequence to it, for example: $\cbrk\FS$, $\cbdaa{n}{\vald}\FS$, 
-or $S\FS$ if $S$ is a sequence of commands.
-
-\begin{mydef}
-Using $\FS[V/n]$ we denote a filesystem derived from $\FS$:
-\[ \FS[V/n](m) :=
-   \begin{cases}
-   V &\mbox{if~} m=n\\
-   \FS(m) &\mbox{otherwise.}
-   \end{cases}
-\]
-\end{mydef}
-
-The exact behavior of our commands is as follows:
-\begin{itemize}
-\item $\cbrk\FS = \fsbroken$
-\item
-All other commands have the generic form $\cxynv$ where
-$X$ and $Y$ are types in $\typeset$,
-$n\in\setn$ and $\valvy$ is a value of the appropriate type from $\setvx{Y}$.
-At times we omit $\valvy$ if there is only one suitable value.
-\[ \cxynv\FS = 
-   \begin{cases}
-   \fsbroken &\mbox{if~} \FS=\fsbroken\\
-   \fsbroken &\mbox{if~} \FS(n)\not\in\setvx{X}\\
-   \fsbroken &\mbox{if~} \FS[V/n] \mbox{~violates the tree property}\\
-   \FS[V/n] &\mbox{otherwise.}
-   \end{cases}
-\]
-\end{itemize}
-
-In general, when we describe multiple or unknown commands, we may substitute one or both
-of their types with variables, as we did with $\cxynv$. In this context,
-if we write that $\cxy=\czw$, we mean that the input and output types % TODO needed?
-of the commands are the same ($X=Z$ and $Y=W$), while a full equiality 
-($\cxynv=\czwmv$)
-implies
-that their output value is also the same.
-
-% Simplifications
-% ---------------
-
-For reasons also listed in \cite{NREC:alg}, in this paper we will not consider
-a $move$ or $rename$ command. Regarding the theoretical reasoning we aim to follow,
-this turns out to be useful because these would be the only commands that affect
-filesystems at two nodes at once, therefore describing 
-the dependencies affecting these commands
-would call for a more complicated model.
-From a pragmatic perspective, this restriction does not mean that in an application
-implementing conflict resolution using the algorithm described here would not be
-able to handle renames by pre- and post-processing changes in the filesystem to
-discover them, which (especially when a rename is combined with changes to the content)
-is a non-trivial problem in itself.
-
-Another simplification we will assume in this paper is regarding directories.
-As Bill Zissimopoulos pointed out (\cite{BZ}), we often do not want to consider metadata stored in
-directories during synchronization. In other words, the contents of directories are all equal,
-which can be modelled by assuming that $|\setd|=1$.
-% This also creates a convenient symmetry where there is only a single value
-% for each type that can be repeated as we move from a path to its child ($D$ and $\empt$).
-
-\section{Describing the behavior of commands}
-
-% Definitions for command pairs and ordering
-% ------------------------------------------
+\section{Investigating Command Pairs}\label{section_axioms}
 
@@
 \end{mydef}
-
-% Command pairs - Axioms
-% ----------------------
-
-\section{Investigating command pairs}
 
@@
 \end{myax}
-
-% Update detection
-% ----------------
-
-\section{Update detection}
-
-In a command-based reconciliation solution we assume that we have two sequences of commands
-$A$ and $B$ that have modified a single filesystem $\FS$ yielding two different replicas $\FS_A$ and $\FS_B$ that we
-need to reconcile. While it is conceivable that the sequences would be based on a record of
-all operations that modified the two filesystems, in most filesystem implementations
-such records are not implemented, and therefore we must construct suitable sequences
-by comparing $\FS_A$ and $\FS_B$ to their common ancestor, $\FS$. This is called update detection.
-
-A sequence that transforms $\FS$ into $\FS_A$ must contain at least one command on each node
-that changes between the two states of the filesystem. Also, it is easy to see that this is also
-sufficient, as there are commands available for any input and output value. 
-Specifically, if at node $n$, $\FS(n)=X'$ and $\FS_A(n)=Y'\neq X'$, then we add the command $\cxyaa{n}{Y'}$ to $A$
-where $X'\in\setvx{X}$ and $Y'\in\setvx{Y}$.
-
-To be able to describe such sequences better, let us introduce the following properties:
-
-\begin{mydef}{Minimal set or sequence.}
-A sequence or set of commands is minimal if it contains at most one command on every node.
-\end{mydef}
-
-\begin{mydef}{Simple set or sequence.}
-A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
-\end{mydef}
-
-This update detector therefore yields a simple set of commands because we only add a single command
-for each node, and we only add commands that are necessary, that is, there will be no 
-assertion commands in the set.
-
-The next step in generating the sequences is to order the commands collected.
-As this task is at the heart of reconciliation itself independently of update detection,
-we discuss it in the next section.
-Then, in \cref{update_works}, we prove that the resulting sequence actually
-works without breaking the filesystem.
-
-% Ordering commands
-% ----------------
-
-\section{Ordering commands}\label{ordering}
-
-We often encounter the case where we only have a set of commands without a specified order.
-As we have seen above, this can occur after the first stage of update detection,
-but, more importantly,
-it is actually the task of the reconciler to determine whether there is an order,
-and if yes, what order,
-in which updates from multiple replicas can be applied to a filesystem.
-
-In this section we describe an algorithm with which all possible orderings of a
-simple set of commands can be generated, but before doing so, let us consider the following lemma.
-
-\begin{mylem}\label{connected_changes}
-Given a set of commands that
-does not contain assertion commands,
-and which can be applied to a filesystem in some order without breaking it,
-and which contains commands on $n$ and $\nn$ where $\nn\descendant n$
-but $\nn\neq\parent(n)$, then the set must also contain a commands
-on each node between $n$ and $\nn$.
-\end{mylem}
-\begin{proof}
-We prove that under the given conditions, the set must contain a command on $\parent(n)$.
-Then, by repeating this statement, we how that the set must contain commands on every
-ancestor of $n$ up to $\nn$.
-
-Furthermore,
-we prove this proposition for sequences, not sets, as if all sequences must contain a command on $\parent(n)$,
-then so must sets because otherwise there would be no order in which they can be
-applied to any filesystem.
-
-Let $A$ be a sequence that satisfies the conditions;
-we therefore know that it contains a command $\cxynv$ on $n$
-and another command $\czwnnv$ on $\nn$.
-We use an indirect proof and assume that there are no commands on $\parent(n)$ in $A$.
-Next, we create a new sequence $A'\equiv A$ in which $\cxy$ and $\czw$ are next to each other.
-If they are already next to each other in $A$, there is nothing to do.
-Otherwise, consider the command next to $\cxynv$ in the direction where $\czwnnv$ is.
-Let this command be $\cqrmv$.
-If $\czw$ is to the right, then $A$ looks like the following:
-\[ A = \cdots\cc\cxynv\cc\cqrmv\cc\cdots\cc\czwnnv\cc\cdots \]
-If $n\unrel m$, swap $\cxynv$ and $\cqrmv$. Based on \cref{ax_separate_commute} we know that the new
-sequence is equivalent to $A$.
-Otherwise, we know $m\neq\parent(n)$ as there are no commands on $\parent(n)$, and so
-from \cref{ax_distantrel_breaks} we get $A\equiv\cbrk$ which contradicts our assumptions.
-(Note that $A$ cannot contains assertion commands.)
-By repeating this step we can therefore convert $A$ into $A'$ where $\cxynv$ and $\czwnnv$ are neighboring commands.
-However, then \cref{ax_distantrel_breaks} applies to the sequence and therefore $A\equiv A'\equiv\cbrk$ which
-is again a contradiction.
-\end{proof}
-
-\medskip
-
-We can now define our algorithm to generate orders of sets of commands.
-
-Let $U$ be a simple set of commands
-that we know can be applied to at least one filesystem in some order without breaking it.
-Then we can split $U$ into a maximum number of disjunct subsets
-(components) so that the nodes of two commands from two different subsets are unrelated.
-These will simply be the components of the subset of the node forest that contains the nodes affected by the set.
-
-From \cref{ax_separate_commute} we know that commands from different 
-components can be applied in any order.
-Therefore once we have ordered the commands inside a component, we generate
-all permutations of the components themselves, including the ones
-in which commands from separate components mix and overlap
-(but where the possible orders determined for commands inside the components are respected).
-
-Next, consider the ordering inside a component.
-
-This is not a problem in the case of components containing a single command only.
-(Note that $\cff$ can only appear in a component of one.)
-
-In each component that is larger than one, 
-we know that all nodes are related, and from \cref{connected_changes}
-we also know that it must contain commands on all nodes in between.
-Therefore the nodes
-form a rooted ordered tree,
-and the pairs of commands connected by the edges in the tree 
-must be construction or destruction pairs.
-(Otherwise, there would be no ordering of the component that is not equivalent to $\cbrk$
-and via \cref{ax_separate_commute} there would be no ordering of the whole set, either.)
-
-To order the commands in the component,
-select the command with the topmost node, so that there would be no command
-on its parent node (if there is one). 
-If the command removes content at this node (it is of the form $X\empt$), 
-then it must follow all other commands in the component, and
-all parent--child pairs in the whole component must be destruction pairs.
-Otherwise, the command with the topmost node needs to precede the other commands,
-and the component must be made of construction pairs.
-These follow from the patterns of construction and destruction pairs, which
-at no point can mix without causing any sequence to break all filesystems.
-
-Then move the command with the topmost node to the beginning or the end of
-the sequence we are creating out of the component,
-and recursively start the whole algorithm again on the commands in the component that remain,
-potentially splitting them into sub-components.
-The result of this process is a set of possible orders for each component,
-which are then combined into a set of possible orders for the whole set of commands.
-
-\begin{mydef}{$\orderset{U}$.}
-We use $\orderset{U}$ to denote the set of sequences that contain all commands in
-the simple set $U$
-and represent all orders generated by this algorithm.
-\end{mydef}
-
-It follows from the algorithm that:
-\begin{mycor}\label{lemma:neighbor}
-If $U$ contains commands on both $n$ and $\parent(n)$, then
-there is a $U'\in\orderset{U}$ where they are next to each other.
-\end{mycor}
-
-As a specific case, we can regard a sequence of commands $S$
-as a set and determine its $\orderset{S}$.
-An important property of simple sequences is that
-all of their valid orderings are equivalent,
-and all equivalent sequences are mere reorderings:
-
-\begin{mylem}\label{simple_reorder_equiv}
-For any simple sequence $S\neq\cbrk$,
-$\forall T: T\equiv S \Leftrightarrow T\in\orderset{S}$.
-\end{mylem}
-\begin{proof}
-TODO
-\end{proof}
-
-It follows from this that given a simple set,
-we can simply assume that it has an order.
-Accordingly, we will at times treat not only sequences as sets,
-but simple sets as sequences.
-
-\medskip
-
-% Correctness of update detection
-% -------------------------------
-
-Based on \cref{connected_changes} we can also show that
-the update detector does function as intended as:
-
-\begin{myth}\label{update_works}
-A sequence of commands returned by the update detector
-when comparing $\FS^*$ to the original $\FS$
-will not break $\FS$ if it is applied to it.
-\end{myth}
-\begin{proof}
-Let $\FS\neq\fsbroken$ be the original filesystem, and $\FS^*\neq\fsbroken$
-be the filesystem after the changes we intend to detect.
-Let us assume that some mechanism recorded all changes that occurred
-to $\FS$ until it reached the state $\FS^*$.
-Our set if commands is sufficient to record any change, as
-there are commands for every input and output type pair, therefore
-we know that the changes can be recorded as a sequence of commands $S$
-where $S\FS=\FS^*$.
-Note that $S$ will not contain assertion commands, as they do not
-represent an actual change in the filesystem.
-
-Therefore, \cref{connected_changes} applies to $S$ and we know
-if it contains commands on $\nn$ and $n$ where $\nn\descendant n$,
-then it also contains commands on nodes in between;
-which is equivalent to saying that if $\FS$ changed
-at node $\nn$ and $n$, then it had to change on the nodes in between.
-
-If so, then, similarly to what happens in the ordering algorithm,
-we can separate $S$ into components of commands on related nodes,
-as commands from separate components freely commute yielding an equivalent sequence.
-From the arguments above, we also know that each component
-must be made up of only desctruction or only construction pairs,
-but not a mixture of the two.
-This means that in each component, parents either strictly precede or succeed child nodes
-(as otherwise $S\equiv\cbrk$ would hold),
-from which it follows that once the components are separated
-in a new sequence $S'\equiv S$,
-commands on the same nodes are next to each other in $S'$.
-
-Based on \cref{ax_same_emptyseq,ax_same_singlec} there is
-an $S''\eqnrw S'$ in which multiple commands on the same nodes
-are simplified into a single command or an empty sequence,
-and therefore $S''$ is simple and $S\equiv S'\eqext S''$.
-It is easy to see that $S''$ must contain the same commands
-as the output of the update detector, $U$, as both are simple
-but reflect all changes between $\FS$ and $\FS^*$.
-If so, then based on \cref{simple_reorder_equiv}
-we have $S''\in\orderset{U}$, from which
-$S\equiv S'\eqext S''\equiv U$, and as $S\FS = \FS^* \neq \fsbroken$,
-therefore $U\FS\neq\fsbroken$.
-\end{proof}
-
-\section{Reconciliation}
-
-If we start with two copies of the filesystem $\FS$,
-and two different sequences are applied to the copies to yield $\FS_A:=A\FS$
-and $\FS_B:=B\FS$, then our aim is to define sequences of commands $\reca$ and $\recb$
-so that $\recb\FS_A$ and $\reca\FS_B$ would be as close to each other as possible.
-
-We work based on the assumption that to achieve this, we need
-to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
-As some commands may have been applied to both filesystems, our first approximation
-is $\reca = A\setminus B$ and $\recb = B\setminus A$
-(in some suitable order).
-This, however, will break both filesystems if there have been incompatible updates
-in $A$ and $B$. 
-Our aim is therefore to provide an algorithm that selects the commands 
-$\reca \subset A\setminus B$
-and $\recb \subset B\setminus A$ 
-so that $\reca\FS_B\neq\fsbroken$ and $\recb\FS_A\neq\fsbroken$,
-and show that these are the longest sequences with this property, that is,
-adding any command left out from $\reca$ or $\recb$ will break the filesystems.
-
-We assume that $A$ and $B$ are returned by an update detector,
-and so they are simple sequences.
-(Otherwise, they can be simplified to become simple sequences.)
-We also assume that $\FS_A$ and $\FS_B$ are not broken.
-With these assumptions,
-we can now define independent sequences and
-our reconciliation algorithm.
-
-\begin{mydef}{Independent commands, sequences and sets.}
-For two commands $\cxynv$ and $\czwmv$ we write $\cxynv\indep\czwmv$ if $\cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk$.
-For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
-$\forall a\in A \mbox{~and~} \forall b\in B: a\indep b$.
-\end{mydef}
-
-\begin{mydef}{Reconciliation.}\label{def:reconciliation}
-\begin{align*}
-\reca = \{c| & \\
-& c\in A\setminus B \\
-& \wedge \\
-& \forall c'\in B\setminus A: c\indep c'\\
-\} &
-\end{align*}
-
-In other words, the sequence $\reca$ we apply to $\FS_B$ consists of all commands from $A\setminus B$
-that are independent of every command in $B\setminus A$.
-The order of commands in the sequence can be determined using the algorithm described in
-\cref{ordering} as any subset of $A$ is also simple.
-In a similar way, $\recb$ can be obtained by reversing $A$ and $B$.
-\end{mydef}
-
-We would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
-that is, without loss of generality,
-\[ \reca\FS_B\neq\fsbroken. \]
-So that we can formalize statements needed to prove this,
-let us introduce two relations that describe under what conditions
-sequences of commands work, that is, do not break a filesystem.
-
-% Works
-% -----
-
-\begin{mydef}
-% Unsure if this relation should be in the algebra.
-For a set of $k$ sequences
-$\works{A_1,A_2,\ldots,A_k}$ means that 
-$A_1,A_2,\ldots,A_k$ work at the same time, that is,
-% intended interpretation:
-\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_k\FS\neq\fsbroken\]
-As the sequences form a set, their order is irrelevant.
-% inference rules:
-We also know that $\works{A} \Leftrightarrow A\nequiv \cbrk$. 
-\end{mydef}
-
-\begin{mydef}
-For two sets of sequences, $\worksc{A_1,A_2,\ldots,A_k}{B_1,B_2,\ldots,B_l}$ means that 
-all of $A_1,\ldots,A_k$ work where all of $B_1,\ldots,B_l$ work,
-that is,
-% intended interpretation:
-\begin{align*}
-\forall \FS:&\\ 
-&B_1\FS\neq\fsbroken \wedge \cdots \wedge B_k\FS\neq\fsbroken\\
-&\Rightarrow\\
-&A_1\FS\neq\fsbroken \wedge \cdots \wedge A_l\FS\neq\fsbroken
-\end{align*}
-As above, the order of the sequences in the sets is not relevant.
-\end{mydef}
-
-\begin{mydef}{Sets of sequences.}
-For brevity, we will use $\seqset{S}$ to note an arbitrary set of sequences,
-and $A\cc\seqset{S}$ to note the set of sequences $\{A\cc S|S\in\seqset{S}\}$.
-\end{mydef}
-
-It is easy to see that the following corollaries are true:
-
-% An inference rule in the algebra
-% $\worksc{X}{X}$ is always true for any set of sequences $X$,
-
-\begin{mycor}
-% An inference rule in the algebra
-$B\eqext A \Rightarrow \worksc{A}{B}$.
-\end{mycor}
-
-\begin{mycor}\label{worksextpostfix}
-% An inference rule in the algebra
-$\forall A,S: \worksc{A}{A\cc S}$, that is, if a sequence works, its prefix also works.
-\end{mycor}
-
-\begin{mycor}\label{workschained}
-% An inference rule in the algebra
-$\workssign$ can be chained:
-if $\seqset{A'}\subset\seqset{A}$, then
-$ \worksc{\seqset{C}}{\seqset{A'}} \wedge \worksc{\seqset{A}}{\seqset{B}} \Rightarrow \worksc{\seqset{A}\cup\seqset{C}}{\seqset{B}}$.
-\end{mycor}
-
-We also prove the following lemmas.
-
-\begin{mylem}\label{unrelated_is_independent}
-Two different commands that are not assertion commands are independent iff the nodes they change are unrelated:
-\[ \cxynv\indep\czwmv \Leftrightarrow n\unrel m \]
-if $\cxynv\neq\czwmv$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
-\end{mylem}
-\begin{proof}
-We proceed in two steps; first, we prove that
-\[ \cxynv\nindep\czwmv \wedge n\unrel m \] would lead to contradiction.
-By definition, if the two commands are not independent, then at least one of the following holds:
-\begin{itemize}
-\item $\czwmv\cc \cqrov \equiv\cbrk$
-\item $\cqrov\cc \czwmv \equiv\cbrk$
-\item $\czwmv\cc \cqrov \nequiv \cqrov\cc \czwmv$
-\end{itemize}
-However, from \cref{ax_separate_commute,ax_separate_nobreaks} we also know that
-if $n\unrel m$ then none of the above can be true.
-
-Next, we prove that
-\[ \cxynv\indep\czwmv \wedge n\nunrel m \] would lead to contradiction.
-As $n\nunrel m$
-we know that $n=m$, $n\descendant m$ or $m\descendant n$.
-
-If $n=m$, then from \cref{ax_same_breaks} we know $Y=Z$ and $W=X$
-as otherwise the commands, in one order or the other, would break all filesystems
-and they could not be independent.
-The commands are not assertion commands, and so from \cref{ax_same_singlec}
-we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $Y=W$ and $\valvy=\valvw$.
-Therefore $X=Y=Z=W$ which is only possible if both commands are $\cff$ and have the same
-output value. This, however, contradicts our assumption that they are different.
-
-If $n\descendant m$ or $m\descendant n$, then
-from \cref{ax_distantrel_breaks} we know that if they are not directly related,
-then $\cxynv\cc\czwmv$ breaks all filesystems, and they cannot be independent.
-From the construction and destruction pairs and 
-\cref{ax_directchild_breaks,ax_directparent_breaks} we also see that
-even if they are directly related, either
-$\cxynv\cc\czwmv$ or $\czwmv\cc\cxynv$ 
-breaks all filesystems, so they again cannot be independent.
-\end{proof}
-
-\begin{myax}\label{combine_independent_commands}
-The combination of independent commands works wherever the original commands work:
-\begin{align*}
-\forall\FS: &\cxynv\indep \czwmv \\
-&\quad\wedge \cxynv\FS\neq\fsbroken \\
-&\quad\wedge \czwmv\FS\neq\fsbroken \\
-&\Rightarrow \cxynv\cc \czwmv\FS\neq\fsbroken.
-\end{align*}
-\end{myax}
-\begin{proof}
-We name this proposition an axiom for the same reason as above,
-but it is easy to provide an indirect proof based on our filesystem model.
-Assume that $\cxynv\cc \czwmv\FS=\fsbroken$.
-We know $\cxynv\FS\neq\fsbroken$ so it must be applying 
-$\czwmv$ that breaks it.
-Applying a command can only result in a broken filesystem in three cases.
-First, if the filesystem was already broken, which cannot be the case here.
-Second, if the input type does not match the filesystem,
-but we know $\FS(m)\in\setvx{W}$ and so
-$(\cxynv\FS)(m)\in\setvx{W}$ as based on \cref{unrelated_is_independent}, $n\neq m$.
-Third, if the new filesystem violates the tree property.
-This again cannot be the case because we also know that $n\unrel m$
-and the tree property only depends on the types of the parent and children of $m$,
-which therefore cannot be changed by $\cxynv$.
-\end{proof}
-
-This result can be extended to sequences:
-
-\begin{mylem}\label{combine_independent_sequences}
-The combination of independent sequences works wherever the original sequences work:
-\[ S\indep T \Rightarrow \worksc{S\cc T}{S,T}. \]
-\end{mylem}
-\begin{proof}
-Assume that there is a filesystem $\FS$ so that
-$S\FS\neq\fsbroken$ and $T\FS\neq\fsbroken$, but
-$(S\cc T)\FS=\fsbroken$.
-
-From \cref{unrelated_is_independent,ax_separate_commute} we know that
-the commands in $S$ and $T$ pairwise commute, and so any sequence
-that contains the commands from $S$ and $T$ and preserve their original partial order
-is equivalent to $S\cc T$ on all filesystems.
-
-Let the command that breaks $\FS$ in $T$ when applying $S\cc T$ be $t$
-so that $T=T_0\cc t\cc T_1$.
-It is still true that $(T_0 \cc t)\FS\neq\fsbroken$,
-and by definition $(S\cc T_0)\FS\neq\fsbroken$,
-but $(S\cc T_0\cc t)\FS=\fsbroken$.
-Also, from above we know that $S\cc T_0\equiv T_0\cc S$
-and so $(T_0 \cc S)\FS\neq\fsbroken$.
-
-If we denote the first command in $S$ with $s_1$,
-this means that $(T_0 \cc s_1)\FS\neq\fsbroken$,
-which we can combine with $(T_0 \cc t)\FS\neq\fsbroken$, $t\indep s_1$ and
-\cref{combine_independent_commands}
-(using $T_0\FS$ as the reference filesystem)
-to arrive at $(T_0 \cc s_1\cc t)\FS\neq\fsbroken$.
-
-We can repeat this step for $s_2$, the next command in $S$,
-and from 
-$(T_0 \cc s_1\cc t)\FS\neq\fsbroken$
-and
-$(T_0 \cc s_1\cc s_2)\FS\neq\fsbroken$
-arrive at
-$(T_0 \cc s_1\cc s_2\cc t)\FS\neq\fsbroken$.
-This can be repeated until $S$ is exhausted and we get
-$(T_0 \cc S\cc t)\FS\neq\fsbroken$, which is a contradiction.
-\end{proof}
-
-Separately, we prove the following:
-
-\begin{mylem}\label{worksinputmatch}
-If $A$ and $B$ are minimal sequences, $\works{A,B}$,
-and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$)
-then their input types must match ($X=Z$).
-\end{mylem}
-\begin{proof}
-This is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
-either $\cxynv$ or $\czwnv$ would not break, 
-and consequently $A$ and $B$ cannot work on the same filesystem.
-\end{proof}
-
-\medskip
-
-We continue by defining inverse commands and sequences
-which allow us to move parts of sequences between the
-condition and consequence parts of $\workssign$.
-
-\begin{mydef}{Inverse commands and sequences.}
-The inverse of command $\cxynv$ is $\cxynv^{-1} = \caaaa{Y}{X}{n}{\valvx}$
-where $V_X$ is an arbitrary value from $\setvx{X}$.
-We write $S^{-1}$ for the inverse of sequence $S$, which consists of the inverses of the commands in $S$
-in reverse order.
-\end{mydef}
-
-\begin{mydef}{$\typeeq$.}
-For two filesystems we write $\FS\typeeq\GS$
-iff 
-at all nodes the types of their values are the same, or they are both broken.
-\end{mydef}
-
-From the definitions we can clearly see that
-\begin{mycor}\label{negneg_is_typeeq}
-$\forall \FS: (S^{-1})^{-1}\FS\typeeq \FS$.
-\end{mycor}
-
-\begin{mylem}\label{r_invmove}
-A common prefix of sequences can be moved to the other side of $\workssign$ by inverting it:
-\begin{gather*}
-\worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \\
-\worksc{\seqset{A}}{B\cc \seqset{S}} \Rightarrow \worksc{B^{-1}\cc \seqset{A}}{\seqset{S}}
-\end{gather*}
-\end{mylem}
-\begin{proof}
-This is based on the fact that in our model, unless they break a filesystem,
-commands change one type of value into another, but never merge types.
-That is,
-sequences---as functions mapping filesystems to filesystems---are
-essentially bijections over type-equality
-with the only ``sink'' being $\fsbroken$:
-\begin{align*}
-\forall S,\FS,\GS: &S\FS\neq\fsbroken \Rightarrow \\
-&(S\FS\ntypeeq S\GS \Leftrightarrow \FS\ntypeeq \GS).
-\end{align*}
-
-For the proposition
-\[ \worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \]
-the rest of the proof is illustrated by the diagram below
-where Dom($x$), the domain of $x$, represents the set of filesystems
-the sequence $x$ does not break, or neither of the sequences in the set $x$ breaks.
-
-\input{inverse-works} % TODO arrows too small
-
-We see that the set of filesystems the sequences in $\seqset{A}$ do not break intersect with the range of $B$.
-As $B$ is a bijection between its domain and range, we can use $B^{-1}$ to map this intersection back
-onto the domain of $B$.
-As $\worksc{B\cc \seqset{A}}{\seqset{S}}$ the domain of $\seqset{S}$ must be a subset of this
-projected intersection.
-If so, then we can use $B$ to map the domain of $\seqset{S}$, which yields the domain of $B^{-1}\cc \seqset{S}$.
-As it is also a part of the domain of $A$, we get $\worksc{\seqset{A}}{B^{-1}\cc \seqset{S}}$.
-
-The second part of the lemma can be proven in a similar way.
-\end{proof}
-
-\begin{mylem}\label{indep_prefix_combine}
-The combination of sequences with a common head and independent tails continues to work under the same conditions:
-\[ \worksc{A\cc B}{\seqset{S}} \wedge \worksc{A\cc C}{\seqset{S}} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{\seqset{S}} \]
-\end{mylem}
-\begin{proof}
-Based on \cref{r_invmove} we know
-$\worksc{B}{A^{-1}\cc \seqset{S}}$ and $\worksc{C}{A^{-1}\cc \seqset{S}}$,
-and from \cref{combine_independent_sequences} we know
-$\worksc{B\cc C}{B,C}$.
-Combining these using \cref{workschained}
-we get
-$\worksc{B\cc C}{A^{-1}\cc \seqset{S}}$. 
-Finally, applying the second line of \cref{r_invmove} yields
-$\worksc{(A^{-1})^{-1}\cc B\cc C}{\seqset{S}}$, which proves our lemma 
-as $\forall\FS: (A^{-1})^{-1}\FS\typeeq A\FS$ (\cref{negneg_is_typeeq}).
-\end{proof}
-
-\medskip
-
-% Correctness of reconciliation
-% -----------------------------
-
-We are now ready to prove that the proposed algorithm for reconciliation is correct,
-that is, applying its result is not going to break the replicas.
-We reformulate the original proposition, $\reca\FS_B\neq\fsbroken$,
-based on $\FS_B=B\FS$ and so we aim to prove that
-$B\cc\reca$ works wherever $A$ and $B$ work:
-
-\begin{myth}
-If $A, B$ are simple, then $\worksc{B\cc \reca}{A,B}$,
-where, to restate \cref{def:reconciliation},
-% { % scope
-% \renewcommand{\themydef}{\ref{def:reconciliation}}
-% \begin{mydef}
-\begin{align*}
-\reca = \{c| & \\
-& c\in A\setminus B \\
-& \wedge \\
-& \forall c'\in B\setminus A: c\indep c'\\
-\}. &
-\end{align*}
-% \end{mydef}
-% } % scope
-\end{myth}
-
-This is trivial unless $\works{A,B}$, so we assume that it is true.
-Let us first investigate the part of $A$ and $B$ that is excluded from
-$\reca$: their intersection.
-
-\begin{mylem}\label{can_move_intersection}
-Let $A$ and $B$ be two simple sequences so that $\works{A, B}$.
-Then their intersection, in some suitable order, also works on any filesystem
-either of them works on:
-$\worksc{A\cap B}{A}$, and, by symmetry,
-$\worksc{A\cap B}{B}$.
-\end{mylem}
-
-\begin{proof}
-The difficulty is that commands in $A\cap B$ can occur anywhere in $A$.
-Therefore, first we prove the following:
-if all commands are marked in $A$ that also appear in $B$,
-then there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.
-
-We show that $A$ can be transformed via equivalences so that this would be true.
-Our proposition is that if the marked commands are not at the beginning, then
-the sequence contains an unmarked command followed by a marked command.
-We show that these can be swapped resulting in an equivalent sequence.
-Then, by repeating this process similarly to bubble sorting, we can generate 
-a suitable $A'$.
-
-\medskip
-
-Let us consider therefore the marked command preceded by an unmarked command in $A$,
-and let the marked command be $\cxynv$, 
-and the preceding unmarked command be $\czwmv$.
-As $A$ is simple and $\works{A}$, from 
-\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
-we know that these commands can only be on unrelated paths or form a construction or destruction pair.
-In the first case, swapping the commands results in a sequence equivalent to $A$,
-and we show that the last two cases are impossible as they would lead to contradiction.
-
-In these cases, either $m=\parent(n)$ or $n=\parent(m)$.
-If $B$ has a command on $m$, then
-from \cref{lemma:neighbor}
-we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxy$ (also in $B$),
-and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
-When describing our ordering algorithm in \cref{ordering} we saw
-that the command on the parent path deremines whether a pair of commands
-is a construction or destruction pair,
-and that this, in turn, determines whether the command on the child path must
-precede or follow the other command as otherwise the sequence would break all filesystems.
-This argument holds for both $A$ and $B$, and so the command on $m$ must be on
-the same side of the command on $n$ in both sequences.
-
-If $B$ has no command on $m$, then let $B'$ be $B$, 
-but with an extra command added to it just before $\cxy$
-according to \cref{ax_child_assert,ax_parent_assert}, 
-from which we know that $B'\equiv B$.
-We also know that $B'$ is still minimal (but no longer simple).
-
-In either case, therefore,
-we have a minimal $B'$ which has a command on $m$ just before $\cxynv$ and $B'\equiv B$.
-Let this command on $m$ be $\cqrmv$.
-\begin{gather*}
-A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
-B' = \cdots\cc  \cqrmv\cc  \cxynv\cc  \cdots
-\end{gather*}
-
-As $\works{A,B}$ and so $\works{A,B'}$, 
-from \cref{worksinputmatch}
-we know that $Q=Z$.
-
-Going back to the construction and destruction pairs we see that the output type of the first command
-is always the same, and it is either $D$ or $\empt$ depending on the relationship between $n$ and $m$.
-Therefore $R=W$ and $\cqrmv=\czwmv$
-as $|\setd|=|\setb|=1$. 
-If $B$ originally had a command on $m$,
-this is a contradiction as $\czw$ was not marked, but we see it must also be in $B'$ and therefore in $B$.
-If $B$ had no command on $m$,
-this is a contradiction because the command on $m$ in $B'$ is an assertion command, so $Z=Q=R=W$, 
-but $A$ contained no assertion commands.
-
-\medskip
-
-We now know that there is an $A'\equiv A$ in which commands in $A\cap B$
-are at the beginning, and therefore 
-from \cref{worksextpostfix}
-$\worksc{A\cap B}{A}$ and by symmetry $\worksc{A\cap B}{B}$.
-\end{proof}
-
-\medskip
-
-\newcommand{\acb}{(A\cap B)}
-\newcommand{\acbi}{\acb^{-1}}
-\newcommand{\amb}{(A\setminus B)}
-\newcommand{\bma}{(B\setminus A)}
-We would like to prove that $\worksc{B\cc \reca}{A,B}$.
-From the above we know that this is equivalent to
-\[ \worksc{\acb\cc \bma\cc \reca}{A,B}. \]
-As we already know that $\reca\indep\bma$
-and that $\worksc{\acb\cc \bma}{A,B}$
-(as $\worksc{B}{A,B}$),
-based on \cref{indep_prefix_combine}
-we only need to prove that
-\[ \worksc{\acb\cc \reca}{A,B}. \]
-Using \cref{r_invmove} we can rephrase this as
-\[ \worksc{\reca}{\acbi\cc A,\acbi\cc B}. \]
-
-To restate some results above, we therefore already know the following things:
-\begin{itemize}
-\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
-\item $\amb \cap \bma = \emptyset$
-\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
-\item $\worksc{\amb, \bma}{\acbi\cc A,\acbi\cc B}$ 
-because of \cref{r_invmove}
-as $\worksc{A,B}{A,B}$,
-and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
-\end{itemize}
-
-Our theorem is therefore proven if we prove the following lemma:
-\newcommand{\condSimple}{(c1)}
-\newcommand{\condDisj}{(c2)}
-\newcommand{\condApr}{(c3)}
-\newcommand{\condWork}{(c4)}
-\begin{mylem}
-If
-   \begin{itemize}
-   \item[\condSimple] $S$ and $T$ are simple sequences,
-   \item[\condDisj] $S\cap T=\emptyset$,
-   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
-   \item[\condWork] $\worksc{S,T}{\seqset{C}}$ for some set of sequences $\seqset{C}$,
-   \end{itemize}
-then
-\[ \worksc{S^*}{\seqset{C}}. \]
-\end{mylem}
-
-\begin{proof}
-This is trivial unless $\works{\seqset{C}}$, so we will assume that it is true
-and therefore $\works{S,T}$.
-
-The proof is similar to that of \cref{can_move_intersection}.
-We mark all commands in $S$ that are in its subset $S^*$, and
-we prove that $S$ can be transformed into $S'$ via equivalences
-so that all marked commands would be at its beginning.
-If so, then based on \cref{worksextpostfix}
-$\worksc{S^*}{\seqset{C}}$ as $\worksc{S'}{\seqset{C}}$ and $S'=S^*\cc S_0$ 
-where $S_0$ contains the remaining (conflicting) commands.
-
-Again we know that if $S$ does not already have all marked commands at its beginning,
-then there is an unmarked command followed by a marked one.
-We show that these commands are independent and so they can be swapped
-resulting in an equivalent sequence.
-By repeating this process we can generate a suitable $S'$.
-
-Let therefore the marked command in $S$ be $\cxynv$
-and the preceding unmarked command be $\czwmv$.
-As $S$ is simple and $\works{S}$, from 
-\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
-we know that these commands can only be on unrelated paths or form a construction or destruction pair.
-In the first case, swapping the commands results in a sequence equivalent to $S$;
-we only need to show that the other two cases are not possible as they would lead to a contradiction.
-
-In the last two cases, we know that either $m=\parent(n)$ or $n=\parent(m)$.
-We also know that because of {\condApr} there must be 
-a command $\cqrov$ in $T$ which is not independent of $\czwmv$
-as $\czwmv$ is not part of $S^*$.
-\begin{gather*}
-S = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
-T = \cdots\cc  \cqrov\cc \cdots
-\end{gather*}
-We know none of these commands is an assertion command, and 
-from {\condDisj} that $\cqrov\neq\czwmv$.
-Therefore, based on \cref{unrelated_is_independent} we know this means that
-either $m\descendantEq o$ or $o\descendantEq m$.
-From {\condApr} we also know that $\cxynv\indep \cqrov$,
-and so because of \cref{unrelated_is_independent},
-$n\unrel o$.
-
-We therefore have four cases considering the relationships between $n,m$ and $o$:
-\begin{itemize}
-\item $n=\parent(m) \wedge o\descendantEq m$.
-   This would mean that $o\descendantEq n$ or $n=\parent(o)$, which contradicts $n\unrel o$.
-\item $n=\parent(m) \wedge m\descendantEq o$.
-   This would mean that $n\descendant o$, which contradicts $n\unrel o$.
-\item $m=\parent(n) \wedge o\descendantEq m$.
-   This would mean that $o\descendant n$, which contradicts $n\unrel o$.
-\item $m=\parent(n) \wedge m\descendantEq o$.
-   Let us continue with this case.
-\end{itemize}
-
-We know that $T$ cannot have a command on $m$ as $m=\parent(n)$ and $\cxynv\indep T$,
-and so $m\neq o$ and therefore $m\descendant o$.
-This means we can create a new sequence $T'\equiv T$ by inserting a command on 
-$m$ into $T$ before $\cqrov$
-according to \cref{ax_parent_assert}.
-We now have $\cxynv\indep T\equiv T'$ which is a contradiction as
-$T'$ has a command on $m$ and $m=\parent(n)$.
-\end{proof}
-
-\medskip
-
-% Reconciliation is maximal
-% -------------------------
-% This is where we're using |D|=1
-% C.f. strict / liberal etc. reconciliation in references
-
-% TODO
-TODO: $\reca$ is maximal
-
-% TODO
-TODO: About setting up an algebra / calculus
-
-% TODO
-TODO: Are these results quite obvious as this is a well-known kind of algebra or system?
-
-\begin{thebibliography}{99}
-
-\bibitem{NREC:alg} Ramsey, Norman and Elod Csirmaz: {\it An algebraic approach to
-file synchronization...}
-
-\bibitem{BZ} Bill Zissimopoulos, personal communication, ...
-
-\end{thebibliography}
-
-\end{document}

### 2015-12-04 2015/def-commands.tex
Split source into sections

--- 2015-11-30 2015/paper.tex
@@
-\documentclass[12pt]{article}
-
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{centernot}
-\usepackage{tikz}
-\usepackage{cleveref}
-
-\newcommand{\setv}{\mathcal{V}} % Set of values
-\newcommand{\setvx}[1]{\mathcal{V}_{#1}} % Set of values with custom index
-\newcommand{\setf}{\setvx{F}} % Set of file values
-\newcommand{\setd}{\setvx{D}} % Set of directory values
-\newcommand{\setb}{\setvx{\empt}} % Set of empty values
-\newcommand{\setn}{\mathcal{N}} % Set of nodes / paths
-\newcommand{\empt}{\bot}
-\newcommand{\parent}{\mathtt{parent}}
-\newcommand{\topnode}{\mathtt{None}} % return value of parent()
-\newcommand{\fsbroken}{\mathtt{Broken}} % broken FS value
-\newcommand{\FS}{\Phi} % a filesystem
-\newcommand{\GS}{\Xi} % another filesystem
-\newcommand{\nn}{n^*} % parent node
-
-\newcommand{\cbrk}{\mathtt{break}} % 'break' command
-\newcommand{\ccharb}{\empt}
-\newcommand{\ccharf}{\mathtt{F}}
-\newcommand{\cchard}{\mathtt{D}}
-\newcommand{\vald}{d} % Directory value
-\newcommand{\valdi}{d_1}
-\newcommand{\valdii}{d_2}
-\newcommand{\valf}{f} % File value
-\newcommand{\valvx}{v_X} % Value of type X
-\newcommand{\valvy}{v_Y} % Value of type Y
-\newcommand{\valvw}{v_W}
-\newcommand{\valvr}{v_R}
-\newcommand{\typeset}{\{\cchard,\ccharf,\ccharb\}} % Set of types in commands
-\newcommand{\caa}[2]{\langle{#1,#2}\rangle}
-\newcommand{\caaa}[3]{\langle{#1,#2,#3}\rangle}
-\newcommand{\caaaa}[4]{\langle{#1,#2,#3,#4}\rangle}
-\newcommand{\cbb}{\caa{\ccharb}{\ccharb}}
-\newcommand{\cbba}[1]{\caaa{\ccharb}{\ccharb}{#1}}
-\newcommand{\cbf}{\caa{\ccharb}{\ccharf}}
-\newcommand{\cbfaa}[2]{\caaaa{\ccharb}{\ccharf}{#1}{#2}}
-\newcommand{\cbd}{\caa{\ccharb}{\cchard}}
-\newcommand{\cbdaa}[2]{\caaaa{\ccharb}{\cchard}{#1}{#2}}
-\newcommand{\cfb}{\caa{\ccharf}{\ccharb}}
-\newcommand{\cfba}[1]{\caaa{\ccharf}{\ccharb}{#1}}
-\newcommand{\cff}{\caa{\ccharf}{\ccharf}}
-\newcommand{\cfd}{\caa{\ccharf}{\cchard}}
-\newcommand{\cfdaa}[2]{\caaaa{\ccharf}{\cchard}{#1}{#2}}
-\newcommand{\cdb}{\caa{\cchard}{\ccharb}}
-\newcommand{\cdba}[1]{\caaa{\cchard}{\ccharb}{#1}}
-\newcommand{\cdf}{\caa{\cchard}{\ccharf}}
-\newcommand{\cdfaa}[2]{\caaaa{\cchard}{\ccharf}{#1}{#2}}
-\newcommand{\cdd}{\caa{\cchard}{\cchard}}
-\newcommand{\cdda}[1]{\caaa{\cchard}{\cchard}{#1}}
-\newcommand{\cxy}{\caa{X}{Y}}
-\newcommand{\cxyaa}[2]{\caaaa{X}{Y}{#1}{#2}}
-\newcommand{\cxynv}{\caaaa{X}{Y}{n}{\valvy}}
-\newcommand{\cxynnv}{\caaaa{X}{Y}{\nn}{\valvy}}
-\newcommand{\cxw}{\caa{X}{W}}
-\newcommand{\cxwnv}{\caaaa{X}{W}{n}{\valvw}}
-\newcommand{\czw}{\caa{Z}{W}}
-\newcommand{\czwnv}{\caaaa{Z}{W}{n}{\valvw}}
-\newcommand{\czwnnv}{\caaaa{Z}{W}{\nn}{\valvw}}
-\newcommand{\czwmv}{\caaaa{Z}{W}{m}{\valvw}}
-\newcommand{\cqr}{\caa{Q}{R}}
-\newcommand{\cqrmv}{\caaaa{Q}{R}{m}{\valvr}}
-\newcommand{\cqrov}{\caaaa{Q}{R}{o}{\valvr}}
-
-\newcommand{\cc}{\circ} % Command / sequence concatenation
-\newcommand{\descendant}{\prec}
-\newcommand{\descendantEq}{\preceq}
-\newcommand{\ancestor}{\succ}
-\newcommand{\ancestorEq}{\succeq}
-
-\newcommand{\eqext}{\sqsubseteq} % equivalent to
-\newcommand{\eqnrw}{\sqsupseteq} % extended by
-\newcommand{\nequiv}{\not\equiv}
-\newcommand{\indep}{\mathrel{\wr\wr}} % Independent commands, sequences
-\newcommand{\unrel}{\indep} % Unrelated nodes
-\newcommand{\nindep}{\,{\centernot{\wr\wr}}\,} % not \indep
-\newcommand{\nunrel}{\nindep} % not \unrel
-
-\newcommand{\workssign}{\mathbf{w}}
-\newcommand{\works}[1]{\workssign({#1})}
-\newcommand{\worksc}[2]{\workssign({#1}\mathrel{|}{#2})}
-
-\newcommand{\typeeq}{\stackrel{t}{=}}
-\newcommand{\ntypeeq}{\centernot{\stackrel{t}{=}}}
-
-\newcommand{\emptyseq}{\lambda} % empty sequence
-
-\newcommand{\orderset}[1]{\vec{\wp}({#1})}
-\newcommand{\seqset}[1]{\underline{#1}} % Set of sequences
-
-\newcommand{\recchar}[3]{{#1}^{#3}_{\mathcal{R}|{#2}}}
-\newcommand{\reca}{\recchar{A}{B}{}} % Reconciled from A
-\newcommand{\recb}{\recchar{B}{A}{}} % Reconciled from B
-
-\theoremstyle{definition}
-
-\newtheorem{mydef}{Definition}
-\crefname{mydef}{definition}{definitions}
-
-\newtheorem{myax}{Axiom}
-\crefname{myax}{axiom}{axioms}
-
-\newtheorem{mylem}{Lemma}
-\crefname{mylem}{lemma}{lemmas}
-
-\newtheorem{myth}{Theorem}
-\crefname{myth}{theorem}{theorems}
-
-\newtheorem{mycor}{Corollary}
-\crefname{mycor}{corollary}{corollaries}
-
-\title{The Correctness of Algebraic File Synchronization}
-
-\author{Elod Pal Csirmaz}
-
-\begin{document}
-\maketitle
-\begin{abstract}
-Abstract goes here
-\end{abstract}
-
-\section{Introduction}
-
-Synchronizing data structures, and filesystems in particular,
-is a task that we encounter more and more often in our world
-of multiple mobile devices, cloud solutions and distributed systems.
-Applications of synchronization ranges from
-solutions for end users who expect to access personal data seamlessly
-on multiple devices and personal clouds to geographically distributed server networks
-that need to synchronize themselves with low latency to serve the 
-same content.
-
-In this paper we
-continue the work in \cite{NREC:alg} and add to the theoretical understanding
-of synchronization based not on filesystem states, but filesystem changes or commands.
-
-% Synchronization:
-% Main aim: apply updates (where possible) from other replicas
-% update detection -> conflict detection -> merging updates -> ordering updates -> apply updates from other replicas
-% Problems: conflict detection, ordering
-
-% ORDERING - because when taking updates from different replicas we get an essentially unordered set
-% Insight: (Prof. Norman Ramsey)
-% - updates where two orders (AB vs BA) are not equivalent are incompatible
-% - we only have a set of updates and need to create an order
-
-% New:
-% better command (instruction) set
-% simpler reconciliation algorithm
-% proof of correctness
-
-\section{Definition of a Filesystem}
-
-We model a filesystem using a function $\FS$ with a set of nodes (filesystem paths) $\setn$ as its domain,
-and a set of possible contents $\setv$ as its codomain:
-\[ \FS : \setn \rightarrow \setv \] 
-In our model, $\setn$ contains all possible nodes, including the ones where there is no file or directory,
-and $\setv$ contains a special element, $\empt$, which is the value of $\FS$ at an empty node.
-We consider the contents of files, as well as any meta-information of files
-and directories (e.g. permissions or flags) part of the values in $\setv$.
-
-The nodes form a disjoint union of rooted directed trees.
-\begin{mydef}
-The function $\parent(n)$ returns the parent node of $n$, or
-returns $\topnode$ if $n$ is the root of a tree.
-\end{mydef}
-
-Every filesystem has a so-called \textbf{tree property}, which means that
-if the filesystem is not empty at a node, and the node has a parent,
-then there must be a directory at the parent node.
-
-To model this, in $\setv$ we distinguish between files ($\setf$) and directories ($\setd$), that is,
-if $\setb = \{\empt\}$ then:
-\[ \setv = \setb \cup \setf \cup \setd \]
-The tree propety can then be defined as
-\begin{align*}
-\forall n\in\setn: &\FS(n) \neq \empt \\ % TODO alignment problem
-&\quad\wedge \parent(n) \neq \topnode \\
-&\Rightarrow \FS(\parent(n)) \in \setd 
-\end{align*}
-This means that as we move down from the root of a tree of nodes,
-the types of values we encounter in the filesystem can only change according to the following
-transition diagram:
-
-\input{type-transition}
-
-In this paper, we write $\valf$ for an arbitrary element of $\setf$, and $\vald$ for an arbitrary element
-of $\setd$. $TODO$ is a value from $\setv$ and $n$ and $m$ are nodes in $\setn$.
-
-\section{Introducing commands}
+\subsection{Commands on Filesystems}
 
 Next we need to define commands on the filesystem.
-
-% <<<<<<<< TODO Rewrite: no algebra
-%  about which we will reason
-% using our algebra.
-% We will aim to draw conclusions or judgements about commands and sequences of commands
-% based on the algebra we are aiming to construct.
-% For example, if we believe that two sequences of commands are equivalent as their effect
-% is the same, then we aim to be able to derive this from the axioms and inference rules of the
-% algebra.
-% As the algebra operates on commands only,
-% these judgements, by definition, need to hold regardless of the filesystem the commands are applied to.
-% Accordingly, we expect that the more information one encodes into the commands and the sequences,
-% the better predicitons we will be able to make using our algebra,
-% as then the commands and sequences will be more specific, and will select a smaller subset
-% of potential filesystems on which they can meaningfully operate.
-% >>>>>>>>>> to here
 
@@
 is a non-trivial problem in itself.
-
-Another simplification we will assume in this paper is regarding directories.
-As Bill Zissimopoulos pointed out (\cite{BZ}), we often do not want to consider metadata stored in
-directories during synchronization. In other words, the contents of directories are all equal,
-which can be modelled by assuming that $|\setd|=1$.
-% This also creates a convenient symmetry where there is only a single value
-% for each type that can be repeated as we move from a path to its child ($D$ and $\empt$).
-
-\section{Describing the behavior of commands}
-
-% Definitions for command pairs and ordering
-% ------------------------------------------
-
-So that we could describe the effects of commands on a filesystem, let us introduce some notation
-and note some observations.
-
-The commands we aim to investigate do not occur in isolation:
-for example, when comparing filesystems to determine the commands needed to transform one into the other,
-we receive a set of commands with uncertain ordering.
-Applying commands to a filesystem, however, happens in time,
-so for this we need a sequence of commands.
-We use $\cc$ to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence:
-$S=\cbdaa{n}{\vald}\cc\cbfaa{m}{\valf}$, or $S'=S\cc\cbba{o}$.
-We write $\emptyseq$ for the empty sequence.
-
-TODO: Sequences of commands, in the usual way,  form a free
-semigroup
-
-The following concepts allow us to investigate sequences independently of filesystems.
-In the definitions, $A,B,S,T$ stand for arbitrary sequences of commands.
-These relations echo the ones defined in \cite{NREC:alg}.
-
-\begin{mydef}
-% Relation in the algebra
-$A\equiv B$ means that $A$ and $B$ are equivalent,
-% intended interpretation:
-that is, they behave in the same way on
-all filesystems: $\forall \FS: A\FS=B\FS$.
-It is a reflexive, commutative and transitive relation,
-and clearly
-% inference rule:
-$ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.
-\end{mydef}
-
-\begin{mydef}
-% Relation in the algebra
-$A\eqext B$ means that $B$ extends $A$,
-% intended interpretation:
-that is, they behave in the same way
-on any filesystem $A$ does not break:
-$\forall \FS: A\FS\neq\fsbroken\Rightarrow A\FS=B\FS$.
-It is a reflexive and transitive relation,
-and we can see that
-% inference rules:
-$ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$
-and
-$ A\equiv B \Rightarrow A\eqext B$.
-\end{mydef}
-
-Let us also define the following relations between nodes:
-
-\begin{mydef}{$n\descendant m$.}
-We write $n\descendant m$ if $n$ is the ancestor of $m$ ($n=\parent^n(m)$). % TODO (the transitive closure of the $\parent$ relation)
-We write $n\descendantEq m$ if $n\descendant m$ or $n=m$.
-\end{mydef}
-
-\begin{mydef}{$n\unrel m$.}
-We write $n\unrel m$, or ``$n$ and $m$ are unrelated'' if $n\not\descendantEq m$ and $n\not\ancestorEq m$.
-\end{mydef}
-
-% Command pairs - Axioms
-% ----------------------
-
-\section{Investigating command pairs}
-
-Our aim is to derive information about the effects of sequences
-of commands independently of that actual filesystems.
-In order to make this possible, we investigate the smallest building
-blocks of sequences: pairs of commands that act on a filesystem directly one after the other.
-This approach is useful as there are a limited number of command pairs,
-because, as we argued above, we can disregard the exact output values of commands apart from their type,
-and we can also abstract the relationship between the nodes in the two commands
-to a finite number of cases.
-
-We methodically investigated of all possibilities using a computer program
-to determine
-which pairs of commands cause errors all the time,
-which can be simplified to one or no commands, and which can be reversed
-without any change in their overall effect.
-% TODO: Footnote: URL
-Our basis for this investigation was the model of filesystems introduced in this paper.
-These properties of command pairs are crucial as they determine
-how a set of commands can be re-ordered to be applied to a filesystem
-during synchronization, and what commands will never be compatible.
-
-Below we list a number of statements derived using this method.
-Although they can be proven by investigating all relevant possibilities
-in a filesystem, we refer to these as axioms because in a secondary algebraic model
-that describes commands without reference to an underlying filesystem,
-these would function as meta-rules generating statements we would accept as true.
-See section (TODO) for more about such a model.
-
-\medskip
-
-Pairs of commands in general have the form
-\[ \cxynv\cc  \czwmv \]
-where $X,Y,Z,W\in\typeset$, $n,m\in\setn$, 
-and values are of the appropriate type: 
-$\valvy\in\setvx{Y}$ and $\valvw\in\setvx{W}$.
-
-\begin{myax}\label{ax_separate_commute}
-Commands on unrelated nodes commute:
-$\cxynv\cc\czwmv \equiv \czwmv\cc\cxynv$ where $n\unrel m$.
-\end{myax}
-
-\begin{myax}\label{ax_separate_nobreaks}
-Commands on unrelated nodes do not break every filesystem:
-$\cxynv\cc\czwmv \nequiv \cbrk$ where $n\unrel m$.
-\end{myax}
-
-\begin{myax}\label{ax_same_breaks}
-Commands on the same node break every filesystem if their types are incompatible:
-$\cxynv\cc\czwnv \equiv \cbrk$ where $Y\ne Z$.
-\end{myax}
-
-\begin{myax}\label{ax_same_emptyseq}
-Commands on the same node simplify:
-$\cxynv\cc\czwnv \eqext \emptyseq$ where $Y=Z$ and $X=W=\ccharb$ 
-or $X=W=\cchard$.
-\end{myax}
-
-\begin{myax}\label{ax_same_singlec}
-Commands on the same node simplify:
-$\cxynv\cc \czwnv \equiv \cxwnv$ where $Y=Z$ and $\cxw\neq\cbb$ and $\cxw\neq\cdd$.
-\end{myax}
-
-\begin{myax}\label{ax_distantrel_breaks}
-Commands on distant relatives break all filesystems:
-$\cxynnv\cc\czwnv \equiv \cbrk$
-and $\czwnv\cc\cxynnv \equiv\cbrk$
-where $\nn\descendant n$ and $\nn\neq\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
-\end{myax}
-
-\begin{mydef}{Construction pair.}
-A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parent(n)$ 
-and the commands are one
-of the following:
-   \begin{gather*}
-   % bd>bf
-            \cbdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
-   % bd>bd
-            \cbdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii} \\
-   % fd>bf
-            \cfdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
-   % fd>bd
-            \cfdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii}
-   \end{gather*}
-\end{mydef}
-
-\begin{myax}\label{ax_directchild_breaks}
-All other commands on a child break every filesystem:
-$\cxynnv\cc\czwnv \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
-and the pair is not a construction pair.
-\end{myax}
-
-\begin{mydef}{Destruction pair.}
-A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parent(n)=\nn$ and the commands are one
-of the following:
-   \begin{gather*}
-   % fb<db ??
-            \cfba{n}\cc  \cdba{\nn} \\
-   % fb<df ??
-            \cfba{n}\cc  \cdfaa{\nn}{\valf} \\
-   % db<db ??
-            \cdba{n}\cc  \cdba{\nn} \\
-   % db<df ??
-            \cdba{n}\cc  \cdfaa{\nn}{\valf}
-   \end{gather*}
-\end{mydef}
-
-\begin{myax}\label{ax_directparent_breaks}
-All other commands on a parent break every filsystem:
-$\cxynv\cc\czwnnv \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
-and the pair is not a destruction pair.
-\end{myax}
-
-\begin{mydef}{Assertion command.}
-A command is an assertion command if
-for every filesystem it either breaks it or leaves it in the same state.
-In other words, assertion commands have the same input and output type,
-and there must also be only one possible value for their output.
-Accordingly, in our current algebra, $\cbba{n}$ and $\cdda{n}$ are the only two assertion commands,
-and we do not note their output value as it is determined.
-\end{mydef}
-
-\begin{myax}\label{ax_child_assert}
-An assertion command can be added on a descendant node:
-$\cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n}$ 
-where $\nn\descendant n$ and $\cxy\neq\cdd$.
-\end{myax}
-
-\begin{myax}\label{ax_parent_assert}
-An assertion command can be added on an ancestor node:
-$\cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn}$ 
-where $\nn\descendant n$ and $\cxy\neq\cbb$.
-\end{myax}
-
-\begin{myax}\label{ax_assert}
-Assertion commands can be removed:
-$\cxynv \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
-\end{myax}
-
-% Update detection
-% ----------------
-
-\section{Update detection}
-
-In a command-based reconciliation solution we assume that we have two sequences of commands
-$A$ and $B$ that have modified a single filesystem $\FS$ yielding two different replicas $\FS_A$ and $\FS_B$ that we
-need to reconcile. While it is conceivable that the sequences would be based on a record of
-all operations that modified the two filesystems, in most filesystem implementations
-such records are not implemented, and therefore we must construct suitable sequences
-by comparing $\FS_A$ and $\FS_B$ to their common ancestor, $\FS$. This is called update detection.
-
-A sequence that transforms $\FS$ into $\FS_A$ must contain at least one command on each node
-that changes between the two states of the filesystem. Also, it is easy to see that this is also
-sufficient, as there are commands available for any input and output value. 
-Specifically, if at node $n$, $\FS(n)=X'$ and $\FS_A(n)=Y'\neq X'$, then we add the command $\cxyaa{n}{Y'}$ to $A$
-where $X'\in\setvx{X}$ and $Y'\in\setvx{Y}$.
-
-To be able to describe such sequences better, let us introduce the following properties:
-
-\begin{mydef}{Minimal set or sequence.}
-A sequence or set of commands is minimal if it contains at most one command on every node.
-\end{mydef}
-
-\begin{mydef}{Simple set or sequence.}
-A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
-\end{mydef}
-
-This update detector therefore yields a simple set of commands because we only add a single command
-for each node, and we only add commands that are necessary, that is, there will be no 
-assertion commands in the set.
-
-The next step in generating the sequences is to order the commands collected.
-As this task is at the heart of reconciliation itself independently of update detection,
-we discuss it in the next section.
-Then, in \cref{update_works}, we prove that the resulting sequence actually
-works without breaking the filesystem.
-
-% Ordering commands
-% ----------------
-
-\section{Ordering commands}\label{ordering}
-
-We often encounter the case where we only have a set of commands without a specified order.
-As we have seen above, this can occur after the first stage of update detection,
-but, more importantly,
-it is actually the task of the reconciler to determine whether there is an order,
-and if yes, what order,
-in which updates from multiple replicas can be applied to a filesystem.
-
-In this section we describe an algorithm with which all possible orderings of a
-simple set of commands can be generated, but before doing so, let us consider the following lemma.
-
-\begin{mylem}\label{connected_changes}
-Given a set of commands that
-does not contain assertion commands,
-and which can be applied to a filesystem in some order without breaking it,
-and which contains commands on $n$ and $\nn$ where $\nn\descendant n$
-but $\nn\neq\parent(n)$, then the set must also contain a commands
-on each node between $n$ and $\nn$.
-\end{mylem}
-\begin{proof}
-We prove that under the given conditions, the set must contain a command on $\parent(n)$.
-Then, by repeating this statement, we how that the set must contain commands on every
-ancestor of $n$ up to $\nn$.
-
-Furthermore,
-we prove this proposition for sequences, not sets, as if all sequences must contain a command on $\parent(n)$,
-then so must sets because otherwise there would be no order in which they can be
-applied to any filesystem.
-
-Let $A$ be a sequence that satisfies the conditions;
-we therefore know that it contains a command $\cxynv$ on $n$
-and another command $\czwnnv$ on $\nn$.
-We use an indirect proof and assume that there are no commands on $\parent(n)$ in $A$.
-Next, we create a new sequence $A'\equiv A$ in which $\cxy$ and $\czw$ are next to each other.
-If they are already next to each other in $A$, there is nothing to do.
-Otherwise, consider the command next to $\cxynv$ in the direction where $\czwnnv$ is.
-Let this command be $\cqrmv$.
-If $\czw$ is to the right, then $A$ looks like the following:
-\[ A = \cdots\cc\cxynv\cc\cqrmv\cc\cdots\cc\czwnnv\cc\cdots \]
-If $n\unrel m$, swap $\cxynv$ and $\cqrmv$. Based on \cref{ax_separate_commute} we know that the new
-sequence is equivalent to $A$.
-Otherwise, we know $m\neq\parent(n)$ as there are no commands on $\parent(n)$, and so
-from \cref{ax_distantrel_breaks} we get $A\equiv\cbrk$ which contradicts our assumptions.
-(Note that $A$ cannot contains assertion commands.)
-By repeating this step we can therefore convert $A$ into $A'$ where $\cxynv$ and $\czwnnv$ are neighboring commands.
-However, then \cref{ax_distantrel_breaks} applies to the sequence and therefore $A\equiv A'\equiv\cbrk$ which
-is again a contradiction.
-\end{proof}
-
-\medskip
-
-We can now define our algorithm to generate orders of sets of commands.
-
-Let $U$ be a simple set of commands
-that we know can be applied to at least one filesystem in some order without breaking it.
-Then we can split $U$ into a maximum number of disjunct subsets
-(components) so that the nodes of two commands from two different subsets are unrelated.
-These will simply be the components of the subset of the node forest that contains the nodes affected by the set.
-
-From \cref{ax_separate_commute} we know that commands from different 
-components can be applied in any order.
-Therefore once we have ordered the commands inside a component, we generate
-all permutations of the components themselves, including the ones
-in which commands from separate components mix and overlap
-(but where the possible orders determined for commands inside the components are respected).
-
-Next, consider the ordering inside a component.
-
-This is not a problem in the case of components containing a single command only.
-(Note that $\cff$ can only appear in a component of one.)
-
-In each component that is larger than one, 
-we know that all nodes are related, and from \cref{connected_changes}
-we also know that it must contain commands on all nodes in between.
-Therefore the nodes
-form a rooted ordered tree,
-and the pairs of commands connected by the edges in the tree 
-must be construction or destruction pairs.
-(Otherwise, there would be no ordering of the component that is not equivalent to $\cbrk$
-and via \cref{ax_separate_commute} there would be no ordering of the whole set, either.)
-
-To order the commands in the component,
-select the command with the topmost node, so that there would be no command
-on its parent node (if there is one). 
-If the command removes content at this node (it is of the form $X\empt$), 
-then it must follow all other commands in the component, and
-all parent--child pairs in the whole component must be destruction pairs.
-Otherwise, the command with the topmost node needs to precede the other commands,
-and the component must be made of construction pairs.
-These follow from the patterns of construction and destruction pairs, which
-at no point can mix without causing any sequence to break all filesystems.
-
-Then move the command with the topmost node to the beginning or the end of
-the sequence we are creating out of the component,
-and recursively start the whole algorithm again on the commands in the component that remain,
-potentially splitting them into sub-components.
-The result of this process is a set of possible orders for each component,
-which are then combined into a set of possible orders for the whole set of commands.
-
-\begin{mydef}{$\orderset{U}$.}
-We use $\orderset{U}$ to denote the set of sequences that contain all commands in
-the simple set $U$
-and represent all orders generated by this algorithm.
-\end{mydef}
-
-It follows from the algorithm that:
-\begin{mycor}\label{lemma:neighbor}
-If $U$ contains commands on both $n$ and $\parent(n)$, then
-there is a $U'\in\orderset{U}$ where they are next to each other.
-\end{mycor}
-
-As a specific case, we can regard a sequence of commands $S$
-as a set and determine its $\orderset{S}$.
-An important property of simple sequences is that
-all of their valid orderings are equivalent,
-and all equivalent sequences are mere reorderings:
-
-\begin{mylem}\label{simple_reorder_equiv}
-For any simple sequence $S\neq\cbrk$,
-$\forall T: T\equiv S \Leftrightarrow T\in\orderset{S}$.
-\end{mylem}
-\begin{proof}
-TODO
-\end{proof}
-
-It follows from this that given a simple set,
-we can simply assume that it has an order.
-Accordingly, we will at times treat not only sequences as sets,
-but simple sets as sequences.
-
-\medskip
-
-% Correctness of update detection
-% -------------------------------
-
-Based on \cref{connected_changes} we can also show that
-the update detector does function as intended as:
-
-\begin{myth}\label{update_works}
-A sequence of commands returned by the update detector
-when comparing $\FS^*$ to the original $\FS$
-will not break $\FS$ if it is applied to it.
-\end{myth}
-\begin{proof}
-Let $\FS\neq\fsbroken$ be the original filesystem, and $\FS^*\neq\fsbroken$
-be the filesystem after the changes we intend to detect.
-Let us assume that some mechanism recorded all changes that occurred
-to $\FS$ until it reached the state $\FS^*$.
-Our set if commands is sufficient to record any change, as
-there are commands for every input and output type pair, therefore
-we know that the changes can be recorded as a sequence of commands $S$
-where $S\FS=\FS^*$.
-Note that $S$ will not contain assertion commands, as they do not
-represent an actual change in the filesystem.
-
-Therefore, \cref{connected_changes} applies to $S$ and we know
-if it contains commands on $\nn$ and $n$ where $\nn\descendant n$,
-then it also contains commands on nodes in between;
-which is equivalent to saying that if $\FS$ changed
-at node $\nn$ and $n$, then it had to change on the nodes in between.
-
-If so, then, similarly to what happens in the ordering algorithm,
-we can separate $S$ into components of commands on related nodes,
-as commands from separate components freely commute yielding an equivalent sequence.
-From the arguments above, we also know that each component
-must be made up of only desctruction or only construction pairs,
-but not a mixture of the two.
-This means that in each component, parents either strictly precede or succeed child nodes
-(as otherwise $S\equiv\cbrk$ would hold),
-from which it follows that once the components are separated
-in a new sequence $S'\equiv S$,
-commands on the same nodes are next to each other in $S'$.
-
-Based on \cref{ax_same_emptyseq,ax_same_singlec} there is
-an $S''\eqnrw S'$ in which multiple commands on the same nodes
-are simplified into a single command or an empty sequence,
-and therefore $S''$ is simple and $S\equiv S'\eqext S''$.
-It is easy to see that $S''$ must contain the same commands
-as the output of the update detector, $U$, as both are simple
-but reflect all changes between $\FS$ and $\FS^*$.
-If so, then based on \cref{simple_reorder_equiv}
-we have $S''\in\orderset{U}$, from which
-$S\equiv S'\eqext S''\equiv U$, and as $S\FS = \FS^* \neq \fsbroken$,
-therefore $U\FS\neq\fsbroken$.
-\end{proof}
-
-\section{Reconciliation}
-
-If we start with two copies of the filesystem $\FS$,
-and two different sequences are applied to the copies to yield $\FS_A:=A\FS$
-and $\FS_B:=B\FS$, then our aim is to define sequences of commands $\reca$ and $\recb$
-so that $\recb\FS_A$ and $\reca\FS_B$ would be as close to each other as possible.
-
-We work based on the assumption that to achieve this, we need
-to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
-As some commands may have been applied to both filesystems, our first approximation
-is $\reca = A\setminus B$ and $\recb = B\setminus A$
-(in some suitable order).
-This, however, will break both filesystems if there have been incompatible updates
-in $A$ and $B$. 
-Our aim is therefore to provide an algorithm that selects the commands 
-$\reca \subset A\setminus B$
-and $\recb \subset B\setminus A$ 
-so that $\reca\FS_B\neq\fsbroken$ and $\recb\FS_A\neq\fsbroken$,
-and show that these are the longest sequences with this property, that is,
-adding any command left out from $\reca$ or $\recb$ will break the filesystems.
-
-We assume that $A$ and $B$ are returned by an update detector,
-and so they are simple sequences.
-(Otherwise, they can be simplified to become simple sequences.)
-We also assume that $\FS_A$ and $\FS_B$ are not broken.
-With these assumptions,
-we can now define independent sequences and
-our reconciliation algorithm.
-
-\begin{mydef}{Independent commands, sequences and sets.}
-For two commands $\cxynv$ and $\czwmv$ we write $\cxynv\indep\czwmv$ if $\cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk$.
-For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
-$\forall a\in A \mbox{~and~} \forall b\in B: a\indep b$.
-\end{mydef}
-
-\begin{mydef}{Reconciliation.}\label{def:reconciliation}
-\begin{align*}
-\reca = \{c| & \\
-& c\in A\setminus B \\
-& \wedge \\
-& \forall c'\in B\setminus A: c\indep c'\\
-\} &
-\end{align*}
-
-In other words, the sequence $\reca$ we apply to $\FS_B$ consists of all commands from $A\setminus B$
-that are independent of every command in $B\setminus A$.
-The order of commands in the sequence can be determined using the algorithm described in
-\cref{ordering} as any subset of $A$ is also simple.
-In a similar way, $\recb$ can be obtained by reversing $A$ and $B$.
-\end{mydef}
-
-We would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
-that is, without loss of generality,
-\[ \reca\FS_B\neq\fsbroken. \]
-So that we can formalize statements needed to prove this,
-let us introduce two relations that describe under what conditions
-sequences of commands work, that is, do not break a filesystem.
-
-% Works
-% -----
-
-\begin{mydef}
-% Unsure if this relation should be in the algebra.
-For a set of $k$ sequences
-$\works{A_1,A_2,\ldots,A_k}$ means that 
-$A_1,A_2,\ldots,A_k$ work at the same time, that is,
-% intended interpretation:
-\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_k\FS\neq\fsbroken\]
-As the sequences form a set, their order is irrelevant.
-% inference rules:
-We also know that $\works{A} \Leftrightarrow A\nequiv \cbrk$. 
-\end{mydef}
-
-\begin{mydef}
-For two sets of sequences, $\worksc{A_1,A_2,\ldots,A_k}{B_1,B_2,\ldots,B_l}$ means that 
-all of $A_1,\ldots,A_k$ work where all of $B_1,\ldots,B_l$ work,
-that is,
-% intended interpretation:
-\begin{align*}
-\forall \FS:&\\ 
-&B_1\FS\neq\fsbroken \wedge \cdots \wedge B_k\FS\neq\fsbroken\\
-&\Rightarrow\\
-&A_1\FS\neq\fsbroken \wedge \cdots \wedge A_l\FS\neq\fsbroken
-\end{align*}
-As above, the order of the sequences in the sets is not relevant.
-\end{mydef}
-
-\begin{mydef}{Sets of sequences.}
-For brevity, we will use $\seqset{S}$ to note an arbitrary set of sequences,
-and $A\cc\seqset{S}$ to note the set of sequences $\{A\cc S|S\in\seqset{S}\}$.
-\end{mydef}
-
-It is easy to see that the following corollaries are true:
-
-% An inference rule in the algebra
-% $\worksc{X}{X}$ is always true for any set of sequences $X$,
-
-\begin{mycor}
-% An inference rule in the algebra
-$B\eqext A \Rightarrow \worksc{A}{B}$.
-\end{mycor}
-
-\begin{mycor}\label{worksextpostfix}
-% An inference rule in the algebra
-$\forall A,S: \worksc{A}{A\cc S}$, that is, if a sequence works, its prefix also works.
-\end{mycor}
-
-\begin{mycor}\label{workschained}
-% An inference rule in the algebra
-$\workssign$ can be chained:
-if $\seqset{A'}\subset\seqset{A}$, then
-$ \worksc{\seqset{C}}{\seqset{A'}} \wedge \worksc{\seqset{A}}{\seqset{B}} \Rightarrow \worksc{\seqset{A}\cup\seqset{C}}{\seqset{B}}$.
-\end{mycor}
-
-We also prove the following lemmas.
-
-\begin{mylem}\label{unrelated_is_independent}
-Two different commands that are not assertion commands are independent iff the nodes they change are unrelated:
-\[ \cxynv\indep\czwmv \Leftrightarrow n\unrel m \]
-if $\cxynv\neq\czwmv$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
-\end{mylem}
-\begin{proof}
-We proceed in two steps; first, we prove that
-\[ \cxynv\nindep\czwmv \wedge n\unrel m \] would lead to contradiction.
-By definition, if the two commands are not independent, then at least one of the following holds:
-\begin{itemize}
-\item $\czwmv\cc \cqrov \equiv\cbrk$
-\item $\cqrov\cc \czwmv \equiv\cbrk$
-\item $\czwmv\cc \cqrov \nequiv \cqrov\cc \czwmv$
-\end{itemize}
-However, from \cref{ax_separate_commute,ax_separate_nobreaks} we also know that
-if $n\unrel m$ then none of the above can be true.
-
-Next, we prove that
-\[ \cxynv\indep\czwmv \wedge n\nunrel m \] would lead to contradiction.
-As $n\nunrel m$
-we know that $n=m$, $n\descendant m$ or $m\descendant n$.
-
-If $n=m$, then from \cref{ax_same_breaks} we know $Y=Z$ and $W=X$
-as otherwise the commands, in one order or the other, would break all filesystems
-and they could not be independent.
-The commands are not assertion commands, and so from \cref{ax_same_singlec}
-we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $Y=W$ and $\valvy=\valvw$.
-Therefore $X=Y=Z=W$ which is only possible if both commands are $\cff$ and have the same
-output value. This, however, contradicts our assumption that they are different.
-
-If $n\descendant m$ or $m\descendant n$, then
-from \cref{ax_distantrel_breaks} we know that if they are not directly related,
-then $\cxynv\cc\czwmv$ breaks all filesystems, and they cannot be independent.
-From the construction and destruction pairs and 
-\cref{ax_directchild_breaks,ax_directparent_breaks} we also see that
-even if they are directly related, either
-$\cxynv\cc\czwmv$ or $\czwmv\cc\cxynv$ 
-breaks all filesystems, so they again cannot be independent.
-\end{proof}
-
-\begin{myax}\label{combine_independent_commands}
-The combination of independent commands works wherever the original commands work:
-\begin{align*}
-\forall\FS: &\cxynv\indep \czwmv \\
-&\quad\wedge \cxynv\FS\neq\fsbroken \\
-&\quad\wedge \czwmv\FS\neq\fsbroken \\
-&\Rightarrow \cxynv\cc \czwmv\FS\neq\fsbroken.
-\end{align*}
-\end{myax}
-\begin{proof}
-We name this proposition an axiom for the same reason as above,
-but it is easy to provide an indirect proof based on our filesystem model.
-Assume that $\cxynv\cc \czwmv\FS=\fsbroken$.
-We know $\cxynv\FS\neq\fsbroken$ so it must be applying 
-$\czwmv$ that breaks it.
-Applying a command can only result in a broken filesystem in three cases.
-First, if the filesystem was already broken, which cannot be the case here.
-Second, if the input type does not match the filesystem,
-but we know $\FS(m)\in\setvx{W}$ and so
-$(\cxynv\FS)(m)\in\setvx{W}$ as based on \cref{unrelated_is_independent}, $n\neq m$.
-Third, if the new filesystem violates the tree property.
-This again cannot be the case because we also know that $n\unrel m$
-and the tree property only depends on the types of the parent and children of $m$,
-which therefore cannot be changed by $\cxynv$.
-\end{proof}
-
-This result can be extended to sequences:
-
-\begin{mylem}\label{combine_independent_sequences}
-The combination of independent sequences works wherever the original sequences work:
-\[ S\indep T \Rightarrow \worksc{S\cc T}{S,T}. \]
-\end{mylem}
-\begin{proof}
-Assume that there is a filesystem $\FS$ so that
-$S\FS\neq\fsbroken$ and $T\FS\neq\fsbroken$, but
-$(S\cc T)\FS=\fsbroken$.
-
-From \cref{unrelated_is_independent,ax_separate_commute} we know that
-the commands in $S$ and $T$ pairwise commute, and so any sequence
-that contains the commands from $S$ and $T$ and preserve their original partial order
-is equivalent to $S\cc T$ on all filesystems.
-
-Let the command that breaks $\FS$ in $T$ when applying $S\cc T$ be $t$
-so that $T=T_0\cc t\cc T_1$.
-It is still true that $(T_0 \cc t)\FS\neq\fsbroken$,
-and by definition $(S\cc T_0)\FS\neq\fsbroken$,
-but $(S\cc T_0\cc t)\FS=\fsbroken$.
-Also, from above we know that $S\cc T_0\equiv T_0\cc S$
-and so $(T_0 \cc S)\FS\neq\fsbroken$.
-
-If we denote the first command in $S$ with $s_1$,
-this means that $(T_0 \cc s_1)\FS\neq\fsbroken$,
-which we can combine with $(T_0 \cc t)\FS\neq\fsbroken$, $t\indep s_1$ and
-\cref{combine_independent_commands}
-(using $T_0\FS$ as the reference filesystem)
-to arrive at $(T_0 \cc s_1\cc t)\FS\neq\fsbroken$.
-
-We can repeat this step for $s_2$, the next command in $S$,
-and from 
-$(T_0 \cc s_1\cc t)\FS\neq\fsbroken$
-and
-$(T_0 \cc s_1\cc s_2)\FS\neq\fsbroken$
-arrive at
-$(T_0 \cc s_1\cc s_2\cc t)\FS\neq\fsbroken$.
-This can be repeated until $S$ is exhausted and we get
-$(T_0 \cc S\cc t)\FS\neq\fsbroken$, which is a contradiction.
-\end{proof}
-
-Separately, we prove the following:
-
-\begin{mylem}\label{worksinputmatch}
-If $A$ and $B$ are minimal sequences, $\works{A,B}$,
-and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$)
-then their input types must match ($X=Z$).
-\end{mylem}
-\begin{proof}
-This is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
-either $\cxynv$ or $\czwnv$ would not break, 
-and consequently $A$ and $B$ cannot work on the same filesystem.
-\end{proof}
-
-\medskip
-
-We continue by defining inverse commands and sequences
-which allow us to move parts of sequences between the
-condition and consequence parts of $\workssign$.
-
-\begin{mydef}{Inverse commands and sequences.}
-The inverse of command $\cxynv$ is $\cxynv^{-1} = \caaaa{Y}{X}{n}{\valvx}$
-where $V_X$ is an arbitrary value from $\setvx{X}$.
-We write $S^{-1}$ for the inverse of sequence $S$, which consists of the inverses of the commands in $S$
-in reverse order.
-\end{mydef}
-
-\begin{mydef}{$\typeeq$.}
-For two filesystems we write $\FS\typeeq\GS$
-iff 
-at all nodes the types of their values are the same, or they are both broken.
-\end{mydef}
-
-From the definitions we can clearly see that
-\begin{mycor}\label{negneg_is_typeeq}
-$\forall \FS: (S^{-1})^{-1}\FS\typeeq \FS$.
-\end{mycor}
-
-\begin{mylem}\label{r_invmove}
-A common prefix of sequences can be moved to the other side of $\workssign$ by inverting it:
-\begin{gather*}
-\worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \\
-\worksc{\seqset{A}}{B\cc \seqset{S}} \Rightarrow \worksc{B^{-1}\cc \seqset{A}}{\seqset{S}}
-\end{gather*}
-\end{mylem}
-\begin{proof}
-This is based on the fact that in our model, unless they break a filesystem,
-commands change one type of value into another, but never merge types.
-That is,
-sequences---as functions mapping filesystems to filesystems---are
-essentially bijections over type-equality
-with the only ``sink'' being $\fsbroken$:
-\begin{align*}
-\forall S,\FS,\GS: &S\FS\neq\fsbroken \Rightarrow \\
-&(S\FS\ntypeeq S\GS \Leftrightarrow \FS\ntypeeq \GS).
-\end{align*}
-
-For the proposition
-\[ \worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \]
-the rest of the proof is illustrated by the diagram below
-where Dom($x$), the domain of $x$, represents the set of filesystems
-the sequence $x$ does not break, or neither of the sequences in the set $x$ breaks.
-
-\input{inverse-works} % TODO arrows too small
-
-We see that the set of filesystems the sequences in $\seqset{A}$ do not break intersect with the range of $B$.
-As $B$ is a bijection between its domain and range, we can use $B^{-1}$ to map this intersection back
-onto the domain of $B$.
-As $\worksc{B\cc \seqset{A}}{\seqset{S}}$ the domain of $\seqset{S}$ must be a subset of this
-projected intersection.
-If so, then we can use $B$ to map the domain of $\seqset{S}$, which yields the domain of $B^{-1}\cc \seqset{S}$.
-As it is also a part of the domain of $A$, we get $\worksc{\seqset{A}}{B^{-1}\cc \seqset{S}}$.
-
-The second part of the lemma can be proven in a similar way.
-\end{proof}
-
-\begin{mylem}\label{indep_prefix_combine}
-The combination of sequences with a common head and independent tails continues to work under the same conditions:
-\[ \worksc{A\cc B}{\seqset{S}} \wedge \worksc{A\cc C}{\seqset{S}} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{\seqset{S}} \]
-\end{mylem}
-\begin{proof}
-Based on \cref{r_invmove} we know
-$\worksc{B}{A^{-1}\cc \seqset{S}}$ and $\worksc{C}{A^{-1}\cc \seqset{S}}$,
-and from \cref{combine_independent_sequences} we know
-$\worksc{B\cc C}{B,C}$.
-Combining these using \cref{workschained}
-we get
-$\worksc{B\cc C}{A^{-1}\cc \seqset{S}}$. 
-Finally, applying the second line of \cref{r_invmove} yields
-$\worksc{(A^{-1})^{-1}\cc B\cc C}{\seqset{S}}$, which proves our lemma 
-as $\forall\FS: (A^{-1})^{-1}\FS\typeeq A\FS$ (\cref{negneg_is_typeeq}).
-\end{proof}
-
-\medskip
-
-% Correctness of reconciliation
-% -----------------------------
-
-We are now ready to prove that the proposed algorithm for reconciliation is correct,
-that is, applying its result is not going to break the replicas.
-We reformulate the original proposition, $\reca\FS_B\neq\fsbroken$,
-based on $\FS_B=B\FS$ and so we aim to prove that
-$B\cc\reca$ works wherever $A$ and $B$ work:
-
-\begin{myth}
-If $A, B$ are simple, then $\worksc{B\cc \reca}{A,B}$,
-where, to restate \cref{def:reconciliation},
-% { % scope
-% \renewcommand{\themydef}{\ref{def:reconciliation}}
-% \begin{mydef}
-\begin{align*}
-\reca = \{c| & \\
-& c\in A\setminus B \\
-& \wedge \\
-& \forall c'\in B\setminus A: c\indep c'\\
-\}. &
-\end{align*}
-% \end{mydef}
-% } % scope
-\end{myth}
-
-This is trivial unless $\works{A,B}$, so we assume that it is true.
-Let us first investigate the part of $A$ and $B$ that is excluded from
-$\reca$: their intersection.
-
-\begin{mylem}\label{can_move_intersection}
-Let $A$ and $B$ be two simple sequences so that $\works{A, B}$.
-Then their intersection, in some suitable order, also works on any filesystem
-either of them works on:
-$\worksc{A\cap B}{A}$, and, by symmetry,
-$\worksc{A\cap B}{B}$.
-\end{mylem}
-
-\begin{proof}
-The difficulty is that commands in $A\cap B$ can occur anywhere in $A$.
-Therefore, first we prove the following:
-if all commands are marked in $A$ that also appear in $B$,
-then there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.
-
-We show that $A$ can be transformed via equivalences so that this would be true.
-Our proposition is that if the marked commands are not at the beginning, then
-the sequence contains an unmarked command followed by a marked command.
-We show that these can be swapped resulting in an equivalent sequence.
-Then, by repeating this process similarly to bubble sorting, we can generate 
-a suitable $A'$.
-
-\medskip
-
-Let us consider therefore the marked command preceded by an unmarked command in $A$,
-and let the marked command be $\cxynv$, 
-and the preceding unmarked command be $\czwmv$.
-As $A$ is simple and $\works{A}$, from 
-\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
-we know that these commands can only be on unrelated paths or form a construction or destruction pair.
-In the first case, swapping the commands results in a sequence equivalent to $A$,
-and we show that the last two cases are impossible as they would lead to contradiction.
-
-In these cases, either $m=\parent(n)$ or $n=\parent(m)$.
-If $B$ has a command on $m$, then
-from \cref{lemma:neighbor}
-we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxy$ (also in $B$),
-and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
-When describing our ordering algorithm in \cref{ordering} we saw
-that the command on the parent path deremines whether a pair of commands
-is a construction or destruction pair,
-and that this, in turn, determines whether the command on the child path must
-precede or follow the other command as otherwise the sequence would break all filesystems.
-This argument holds for both $A$ and $B$, and so the command on $m$ must be on
-the same side of the command on $n$ in both sequences.
-
-If $B$ has no command on $m$, then let $B'$ be $B$, 
-but with an extra command added to it just before $\cxy$
-according to \cref{ax_child_assert,ax_parent_assert}, 
-from which we know that $B'\equiv B$.
-We also know that $B'$ is still minimal (but no longer simple).
-
-In either case, therefore,
-we have a minimal $B'$ which has a command on $m$ just before $\cxynv$ and $B'\equiv B$.
-Let this command on $m$ be $\cqrmv$.
-\begin{gather*}
-A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
-B' = \cdots\cc  \cqrmv\cc  \cxynv\cc  \cdots
-\end{gather*}
-
-As $\works{A,B}$ and so $\works{A,B'}$, 
-from \cref{worksinputmatch}
-we know that $Q=Z$.
-
-Going back to the construction and destruction pairs we see that the output type of the first command
-is always the same, and it is either $D$ or $\empt$ depending on the relationship between $n$ and $m$.
-Therefore $R=W$ and $\cqrmv=\czwmv$
-as $|\setd|=|\setb|=1$. 
-If $B$ originally had a command on $m$,
-this is a contradiction as $\czw$ was not marked, but we see it must also be in $B'$ and therefore in $B$.
-If $B$ had no command on $m$,
-this is a contradiction because the command on $m$ in $B'$ is an assertion command, so $Z=Q=R=W$, 
-but $A$ contained no assertion commands.
-
-\medskip
-
-We now know that there is an $A'\equiv A$ in which commands in $A\cap B$
-are at the beginning, and therefore 
-from \cref{worksextpostfix}
-$\worksc{A\cap B}{A}$ and by symmetry $\worksc{A\cap B}{B}$.
-\end{proof}
-
-\medskip
-
-\newcommand{\acb}{(A\cap B)}
-\newcommand{\acbi}{\acb^{-1}}
-\newcommand{\amb}{(A\setminus B)}
-\newcommand{\bma}{(B\setminus A)}
-We would like to prove that $\worksc{B\cc \reca}{A,B}$.
-From the above we know that this is equivalent to
-\[ \worksc{\acb\cc \bma\cc \reca}{A,B}. \]
-As we already know that $\reca\indep\bma$
-and that $\worksc{\acb\cc \bma}{A,B}$
-(as $\worksc{B}{A,B}$),
-based on \cref{indep_prefix_combine}
-we only need to prove that
-\[ \worksc{\acb\cc \reca}{A,B}. \]
-Using \cref{r_invmove} we can rephrase this as
-\[ \worksc{\reca}{\acbi\cc A,\acbi\cc B}. \]
-
-To restate some results above, we therefore already know the following things:
-\begin{itemize}
-\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
-\item $\amb \cap \bma = \emptyset$
-\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
-\item $\worksc{\amb, \bma}{\acbi\cc A,\acbi\cc B}$ 
-because of \cref{r_invmove}
-as $\worksc{A,B}{A,B}$,
-and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
-\end{itemize}
-
-Our theorem is therefore proven if we prove the following lemma:
-\newcommand{\condSimple}{(c1)}
-\newcommand{\condDisj}{(c2)}
-\newcommand{\condApr}{(c3)}
-\newcommand{\condWork}{(c4)}
-\begin{mylem}
-If
-   \begin{itemize}
-   \item[\condSimple] $S$ and $T$ are simple sequences,
-   \item[\condDisj] $S\cap T=\emptyset$,
-   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
-   \item[\condWork] $\worksc{S,T}{\seqset{C}}$ for some set of sequences $\seqset{C}$,
-   \end{itemize}
-then
-\[ \worksc{S^*}{\seqset{C}}. \]
-\end{mylem}
-
-\begin{proof}
-This is trivial unless $\works{\seqset{C}}$, so we will assume that it is true
-and therefore $\works{S,T}$.
-
-The proof is similar to that of \cref{can_move_intersection}.
-We mark all commands in $S$ that are in its subset $S^*$, and
-we prove that $S$ can be transformed into $S'$ via equivalences
-so that all marked commands would be at its beginning.
-If so, then based on \cref{worksextpostfix}
-$\worksc{S^*}{\seqset{C}}$ as $\worksc{S'}{\seqset{C}}$ and $S'=S^*\cc S_0$ 
-where $S_0$ contains the remaining (conflicting) commands.
-
-Again we know that if $S$ does not already have all marked commands at its beginning,
-then there is an unmarked command followed by a marked one.
-We show that these commands are independent and so they can be swapped
-resulting in an equivalent sequence.
-By repeating this process we can generate a suitable $S'$.
-
-Let therefore the marked command in $S$ be $\cxynv$
-and the preceding unmarked command be $\czwmv$.
-As $S$ is simple and $\works{S}$, from 
-\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
-we know that these commands can only be on unrelated paths or form a construction or destruction pair.
-In the first case, swapping the commands results in a sequence equivalent to $S$;
-we only need to show that the other two cases are not possible as they would lead to a contradiction.
-
-In the last two cases, we know that either $m=\parent(n)$ or $n=\parent(m)$.
-We also know that because of {\condApr} there must be 
-a command $\cqrov$ in $T$ which is not independent of $\czwmv$
-as $\czwmv$ is not part of $S^*$.
-\begin{gather*}
-S = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
-T = \cdots\cc  \cqrov\cc \cdots
-\end{gather*}
-We know none of these commands is an assertion command, and 
-from {\condDisj} that $\cqrov\neq\czwmv$.
-Therefore, based on \cref{unrelated_is_independent} we know this means that
-either $m\descendantEq o$ or $o\descendantEq m$.
-From {\condApr} we also know that $\cxynv\indep \cqrov$,
-and so because of \cref{unrelated_is_independent},
-$n\unrel o$.
-
-We therefore have four cases considering the relationships between $n,m$ and $o$:
-\begin{itemize}
-\item $n=\parent(m) \wedge o\descendantEq m$.
-   This would mean that $o\descendantEq n$ or $n=\parent(o)$, which contradicts $n\unrel o$.
-\item $n=\parent(m) \wedge m\descendantEq o$.
-   This would mean that $n\descendant o$, which contradicts $n\unrel o$.
-\item $m=\parent(n) \wedge o\descendantEq m$.
-   This would mean that $o\descendant n$, which contradicts $n\unrel o$.
-\item $m=\parent(n) \wedge m\descendantEq o$.
-   Let us continue with this case.
-\end{itemize}
-
-We know that $T$ cannot have a command on $m$ as $m=\parent(n)$ and $\cxynv\indep T$,
-and so $m\neq o$ and therefore $m\descendant o$.
-This means we can create a new sequence $T'\equiv T$ by inserting a command on 
-$m$ into $T$ before $\cqrov$
-according to \cref{ax_parent_assert}.
-We now have $\cxynv\indep T\equiv T'$ which is a contradiction as
-$T'$ has a command on $m$ and $m=\parent(n)$.
-\end{proof}
-
-\medskip
-
-% Reconciliation is maximal
-% -------------------------
-% This is where we're using |D|=1
-% C.f. strict / liberal etc. reconciliation in references
-
-% TODO
-TODO: $\reca$ is maximal
-
-% TODO
-TODO: About setting up an algebra / calculus
-
-% TODO
-TODO: Are these results quite obvious as this is a well-known kind of algebra or system?
-
-\begin{thebibliography}{99}
-
-\bibitem{NREC:alg} Ramsey, Norman and Elod Csirmaz: {\it An algebraic approach to
-file synchronization...}
-
-\bibitem{BZ} Bill Zissimopoulos, personal communication, ...
-
-\end{thebibliography}
-
-\end{document}

### 2015-12-04 2015/def-filesystem.tex
Split source into sections

--- 2015-11-30 2015/paper.tex
@@
-\documentclass[12pt]{article}
-
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{centernot}
-\usepackage{tikz}
-\usepackage{cleveref}
-
-\newcommand{\setv}{\mathcal{V}} % Set of values
-\newcommand{\setvx}[1]{\mathcal{V}_{#1}} % Set of values with custom index
-\newcommand{\setf}{\setvx{F}} % Set of file values
-\newcommand{\setd}{\setvx{D}} % Set of directory values
-\newcommand{\setb}{\setvx{\empt}} % Set of empty values
-\newcommand{\setn}{\mathcal{N}} % Set of nodes / paths
-\newcommand{\empt}{\bot}
-\newcommand{\parent}{\mathtt{parent}}
-\newcommand{\topnode}{\mathtt{None}} % return value of parent()
-\newcommand{\fsbroken}{\mathtt{Broken}} % broken FS value
-\newcommand{\FS}{\Phi} % a filesystem
-\newcommand{\GS}{\Xi} % another filesystem
-\newcommand{\nn}{n^*} % parent node
-
-\newcommand{\cbrk}{\mathtt{break}} % 'break' command
-\newcommand{\ccharb}{\empt}
-\newcommand{\ccharf}{\mathtt{F}}
-\newcommand{\cchard}{\mathtt{D}}
-\newcommand{\vald}{d} % Directory value
-\newcommand{\valdi}{d_1}
-\newcommand{\valdii}{d_2}
-\newcommand{\valf}{f} % File value
-\newcommand{\valvx}{v_X} % Value of type X
-\newcommand{\valvy}{v_Y} % Value of type Y
-\newcommand{\valvw}{v_W}
-\newcommand{\valvr}{v_R}
-\newcommand{\typeset}{\{\cchard,\ccharf,\ccharb\}} % Set of types in commands
-\newcommand{\caa}[2]{\langle{#1,#2}\rangle}
-\newcommand{\caaa}[3]{\langle{#1,#2,#3}\rangle}
-\newcommand{\caaaa}[4]{\langle{#1,#2,#3,#4}\rangle}
-\newcommand{\cbb}{\caa{\ccharb}{\ccharb}}
-\newcommand{\cbba}[1]{\caaa{\ccharb}{\ccharb}{#1}}
-\newcommand{\cbf}{\caa{\ccharb}{\ccharf}}
-\newcommand{\cbfaa}[2]{\caaaa{\ccharb}{\ccharf}{#1}{#2}}
-\newcommand{\cbd}{\caa{\ccharb}{\cchard}}
-\newcommand{\cbdaa}[2]{\caaaa{\ccharb}{\cchard}{#1}{#2}}
-\newcommand{\cfb}{\caa{\ccharf}{\ccharb}}
-\newcommand{\cfba}[1]{\caaa{\ccharf}{\ccharb}{#1}}
-\newcommand{\cff}{\caa{\ccharf}{\ccharf}}
-\newcommand{\cfd}{\caa{\ccharf}{\cchard}}
-\newcommand{\cfdaa}[2]{\caaaa{\ccharf}{\cchard}{#1}{#2}}
-\newcommand{\cdb}{\caa{\cchard}{\ccharb}}
-\newcommand{\cdba}[1]{\caaa{\cchard}{\ccharb}{#1}}
-\newcommand{\cdf}{\caa{\cchard}{\ccharf}}
-\newcommand{\cdfaa}[2]{\caaaa{\cchard}{\ccharf}{#1}{#2}}
-\newcommand{\cdd}{\caa{\cchard}{\cchard}}
-\newcommand{\cdda}[1]{\caaa{\cchard}{\cchard}{#1}}
-\newcommand{\cxy}{\caa{X}{Y}}
-\newcommand{\cxyaa}[2]{\caaaa{X}{Y}{#1}{#2}}
-\newcommand{\cxynv}{\caaaa{X}{Y}{n}{\valvy}}
-\newcommand{\cxynnv}{\caaaa{X}{Y}{\nn}{\valvy}}
-\newcommand{\cxw}{\caa{X}{W}}
-\newcommand{\cxwnv}{\caaaa{X}{W}{n}{\valvw}}
-\newcommand{\czw}{\caa{Z}{W}}
-\newcommand{\czwnv}{\caaaa{Z}{W}{n}{\valvw}}
-\newcommand{\czwnnv}{\caaaa{Z}{W}{\nn}{\valvw}}
-\newcommand{\czwmv}{\caaaa{Z}{W}{m}{\valvw}}
-\newcommand{\cqr}{\caa{Q}{R}}
-\newcommand{\cqrmv}{\caaaa{Q}{R}{m}{\valvr}}
-\newcommand{\cqrov}{\caaaa{Q}{R}{o}{\valvr}}
-
-\newcommand{\cc}{\circ} % Command / sequence concatenation
-\newcommand{\descendant}{\prec}
-\newcommand{\descendantEq}{\preceq}
-\newcommand{\ancestor}{\succ}
-\newcommand{\ancestorEq}{\succeq}
-
-\newcommand{\eqext}{\sqsubseteq} % equivalent to
-\newcommand{\eqnrw}{\sqsupseteq} % extended by
-\newcommand{\nequiv}{\not\equiv}
-\newcommand{\indep}{\mathrel{\wr\wr}} % Independent commands, sequences
-\newcommand{\unrel}{\indep} % Unrelated nodes
-\newcommand{\nindep}{\,{\centernot{\wr\wr}}\,} % not \indep
-\newcommand{\nunrel}{\nindep} % not \unrel
-
-\newcommand{\workssign}{\mathbf{w}}
-\newcommand{\works}[1]{\workssign({#1})}
-\newcommand{\worksc}[2]{\workssign({#1}\mathrel{|}{#2})}
-
-\newcommand{\typeeq}{\stackrel{t}{=}}
-\newcommand{\ntypeeq}{\centernot{\stackrel{t}{=}}}
-
-\newcommand{\emptyseq}{\lambda} % empty sequence
-
-\newcommand{\orderset}[1]{\vec{\wp}({#1})}
-\newcommand{\seqset}[1]{\underline{#1}} % Set of sequences
-
-\newcommand{\recchar}[3]{{#1}^{#3}_{\mathcal{R}|{#2}}}
-\newcommand{\reca}{\recchar{A}{B}{}} % Reconciled from A
-\newcommand{\recb}{\recchar{B}{A}{}} % Reconciled from B
-
-\theoremstyle{definition}
-
-\newtheorem{mydef}{Definition}
-\crefname{mydef}{definition}{definitions}
-
-\newtheorem{myax}{Axiom}
-\crefname{myax}{axiom}{axioms}
-
-\newtheorem{mylem}{Lemma}
-\crefname{mylem}{lemma}{lemmas}
-
-\newtheorem{myth}{Theorem}
-\crefname{myth}{theorem}{theorems}
-
-\newtheorem{mycor}{Corollary}
-\crefname{mycor}{corollary}{corollaries}
-
-\title{The Correctness of Algebraic File Synchronization}
-
-\author{Elod Pal Csirmaz}
-
-\begin{document}
-\maketitle
-\begin{abstract}
-Abstract goes here
-\end{abstract}
-
-\section{Introduction}
-
-Synchronizing data structures, and filesystems in particular,
-is a task that we encounter more and more often in our world
-of multiple mobile devices, cloud solutions and distributed systems.
-Applications of synchronization ranges from
-solutions for end users who expect to access personal data seamlessly
-on multiple devices and personal clouds to geographically distributed server networks
-that need to synchronize themselves with low latency to serve the 
-same content.
-
-In this paper we
-continue the work in \cite{NREC:alg} and add to the theoretical understanding
-of synchronization based not on filesystem states, but filesystem changes or commands.
-
-% Synchronization:
-% Main aim: apply updates (where possible) from other replicas
-% update detection -> conflict detection -> merging updates -> ordering updates -> apply updates from other replicas
-% Problems: conflict detection, ordering
-
-% ORDERING - because when taking updates from different replicas we get an essentially unordered set
-% Insight: (Prof. Norman Ramsey)
-% - updates where two orders (AB vs BA) are not equivalent are incompatible
-% - we only have a set of updates and need to create an order
-
-% New:
-% better command (instruction) set
-% simpler reconciliation algorithm
-% proof of correctness
-
-\section{Definition of a Filesystem}
+\subsection{The Filesystem}
 
@@
 \[ \FS : \setn \rightarrow \setv \] 
-In our model, $\setn$ contains all possible nodes, including the ones where there is no file or directory,
-and $\setv$ contains a special element, $\empt$, which is the value of $\FS$ at an empty node.
+In our model, $\setn$ 
+serves as a ``skeleton'' of the filesystem, and it
+contains all possible nodes, including the ones where there is no file or directory.
+To mark empty nodes, $\setv$ contains a special element, $\empt$, which is the value of $\FS$ at these nodes.
 We consider the contents of files, as well as any meta-information of files
-and directories (e.g. permissions or flags) part of the values in $\setv$.
+and directories (e.g. permissions and other flags) part of the values in $\setv$.
 
@@
 
-To model this, in $\setv$ we distinguish between files ($\setf$) and directories ($\setd$), that is,
+To model this, in $\setv$ we distinguish between 
+file contents ($\setf$) and directory contents ($\setd$), that is,
 if $\setb = \{\empt\}$ then:
@@
 
-In this paper, we write $\valf$ for an arbitrary element of $\setf$, and $\vald$ for an arbitrary element
-of $\setd$. $TODO$ is a value from $\setv$ and $n$ and $m$ are nodes in $\setn$.
-
-\section{Introducing commands}
-
-Next we need to define commands on the filesystem.
-
-% <<<<<<<< TODO Rewrite: no algebra
-%  about which we will reason
-% using our algebra.
-% We will aim to draw conclusions or judgements about commands and sequences of commands
-% based on the algebra we are aiming to construct.
-% For example, if we believe that two sequences of commands are equivalent as their effect
-% is the same, then we aim to be able to derive this from the axioms and inference rules of the
-% algebra.
-% As the algebra operates on commands only,
-% these judgements, by definition, need to hold regardless of the filesystem the commands are applied to.
-% Accordingly, we expect that the more information one encodes into the commands and the sequences,
-% the better predicitons we will be able to make using our algebra,
-% as then the commands and sequences will be more specific, and will select a smaller subset
-% of potential filesystems on which they can meaningfully operate.
-% >>>>>>>>>> to here
-
-...
-
-Let us consider what kind of information may be encoded in the commands.
-A usual set of commands, based on the most frequent tools implemented by filesystems,
-might be $create(n,V)$, $edit(n,V)$ and $remove(n)$ where $n\in\setn$ and $V\in\setv$ (but $V\neq\empt$).
-Regarding their output, that is, the state of the filesystem at $n$
-after applying the command,
-we know that after $create$ or $edit$, $\FS(n)\neq\empt$, whereas after $remove$,
-$\FS(n)$ will be $\empt$. 
-However, from \cite{NREC:alg} we know that a useful set of axioms
-will in some cases need to distinguish between edits that result in directories ($edit(n,D)$) and
-ones that result in files ($edit(n,F)$), and treat them as separate commands.
-Indeed, Bill Zissimopoulos suggested (\cite{BZ}) that extending this distinction to more commands
-utlimately simplifies
-the definition of conflicting commands, as our model will then able to predict the behavior of commands
-more precisely.
-In other words, encoding the type of the output ($D$, $F$ or $\empt$) in the commands is definitely useful.
-At the same time, there is never any need to encode information about the
-\emph{exact} output value of a command,
-as the success or failure of filesystem commands only depend on the types of values in the filesystem.
-
-Notice, however, that the commands listed above also encode some information about 
-their input, the filesystem
-\emph{before} the command is applied; namely, $create(n,V)$ requires that there are no files
-or directories at $n$, while $edit(n,V)$ and $remove(n)$ require the opposite.
-This creates an arbitrary asymmetry where
-there is now more information encoded into commands about their output than about their input.
-In line with the aim to encode as much information as possible in the commands, % TODO Where is this mentioned?
-and in order to resolve this asymmetry, we propose a set of commands that encode
-the type of the original state of $\FS(n)$ as well.
-(Some real-life filesystem commands like $rmdir$ do this already.)
-
-% TODO: tuple / quadruple
-We therefore propose to have a command for each pair of types.
-For want of a better system, we will name our commands by concatenating
-two of $\cchard$, $\ccharf$ and $\ccharb$, 
-where the left sign denotes the type of value
-required in the filesystem before the command is applied, and the right sign notes the type
-afterwards. For example, $mkdir(n,D)$ is $\cbdaa{n}{D}$, and $rmdir(n)$ is $\cdba{n}$.
-
-A command can only succeed if the original value at node $n$ has a type that matches
-the input type of the command. If this is not the case, or if the resulting
-filesystem no longer has the tree property, then we say that the command
-{\em breaks} the filesystem. Broken filesystems are considered equal
-(but not equal to any working filesystem), and we note them by $\FS=\fsbroken$.
-
-So that we could reason about sequences of commands that break every filesystem
-in the algebra, we introduce the command $\cbrk$ that simply breaks every filesystem.
-
-We note that a command or a sequence of commands is applied to a filsystem
-by prefixing the command or sequence to it, for example: $\cbrk\FS$, $\cbdaa{n}{\vald}\FS$, 
-or $S\FS$ if $S$ is a sequence of commands.
-
-\begin{mydef}
-Using $\FS[V/n]$ we denote a filesystem derived from $\FS$:
-\[ \FS[V/n](m) :=
-   \begin{cases}
-   V &\mbox{if~} m=n\\
-   \FS(m) &\mbox{otherwise.}
-   \end{cases}
-\]
-\end{mydef}
-
-The exact behavior of our commands is as follows:
-\begin{itemize}
-\item $\cbrk\FS = \fsbroken$
-\item
-All other commands have the generic form $\cxynv$ where
-$X$ and $Y$ are types in $\typeset$,
-$n\in\setn$ and $\valvy$ is a value of the appropriate type from $\setvx{Y}$.
-At times we omit $\valvy$ if there is only one suitable value.
-\[ \cxynv\FS = 
-   \begin{cases}
-   \fsbroken &\mbox{if~} \FS=\fsbroken\\
-   \fsbroken &\mbox{if~} \FS(n)\not\in\setvx{X}\\
-   \fsbroken &\mbox{if~} \FS[V/n] \mbox{~violates the tree property}\\
-   \FS[V/n] &\mbox{otherwise.}
-   \end{cases}
-\]
-\end{itemize}
-
-In general, when we describe multiple or unknown commands, we may substitute one or both
-of their types with variables, as we did with $\cxynv$. In this context,
-if we write that $\cxy=\czw$, we mean that the input and output types % TODO needed?
-of the commands are the same ($X=Z$ and $Y=W$), while a full equiality 
-($\cxynv=\czwmv$)
-implies
-that their output value is also the same.
-
-% Simplifications
-% ---------------
-
-For reasons also listed in \cite{NREC:alg}, in this paper we will not consider
-a $move$ or $rename$ command. Regarding the theoretical reasoning we aim to follow,
-this turns out to be useful because these would be the only commands that affect
-filesystems at two nodes at once, therefore describing 
-the dependencies affecting these commands
-would call for a more complicated model.
-From a pragmatic perspective, this restriction does not mean that in an application
-implementing conflict resolution using the algorithm described here would not be
-able to handle renames by pre- and post-processing changes in the filesystem to
-discover them, which (especially when a rename is combined with changes to the content)
-is a non-trivial problem in itself.
+In this paper, $n$, $m$ and $o$ denote nodes in $\setn$.
+We use $\valf$ for an arbitrary element in $\setf$, 
+and $\vald$ for an arbitrary element in $\setd$,
+and by $\valvx$ we mean a value of type $X$ in $\setvx{X}$.
 
@@
 % for each type that can be repeated as we move from a path to its child ($D$ and $\empt$).
-
-\section{Describing the behavior of commands}
-
-% Definitions for command pairs and ordering
-% ------------------------------------------
-
-So that we could describe the effects of commands on a filesystem, let us introduce some notation
-and note some observations.
-
-The commands we aim to investigate do not occur in isolation:
-for example, when comparing filesystems to determine the commands needed to transform one into the other,
-we receive a set of commands with uncertain ordering.
-Applying commands to a filesystem, however, happens in time,
-so for this we need a sequence of commands.
-We use $\cc$ to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence:
-$S=\cbdaa{n}{\vald}\cc\cbfaa{m}{\valf}$, or $S'=S\cc\cbba{o}$.
-We write $\emptyseq$ for the empty sequence.
-
-TODO: Sequences of commands, in the usual way,  form a free
-semigroup
-
-The following concepts allow us to investigate sequences independently of filesystems.
-In the definitions, $A,B,S,T$ stand for arbitrary sequences of commands.
-These relations echo the ones defined in \cite{NREC:alg}.
-
-\begin{mydef}
-% Relation in the algebra
-$A\equiv B$ means that $A$ and $B$ are equivalent,
-% intended interpretation:
-that is, they behave in the same way on
-all filesystems: $\forall \FS: A\FS=B\FS$.
-It is a reflexive, commutative and transitive relation,
-and clearly
-% inference rule:
-$ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.
-\end{mydef}
-
-\begin{mydef}
-% Relation in the algebra
-$A\eqext B$ means that $B$ extends $A$,
-% intended interpretation:
-that is, they behave in the same way
-on any filesystem $A$ does not break:
-$\forall \FS: A\FS\neq\fsbroken\Rightarrow A\FS=B\FS$.
-It is a reflexive and transitive relation,
-and we can see that
-% inference rules:
-$ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$
-and
-$ A\equiv B \Rightarrow A\eqext B$.
-\end{mydef}
-
-Let us also define the following relations between nodes:
-
-\begin{mydef}{$n\descendant m$.}
-We write $n\descendant m$ if $n$ is the ancestor of $m$ ($n=\parent^n(m)$). % TODO (the transitive closure of the $\parent$ relation)
-We write $n\descendantEq m$ if $n\descendant m$ or $n=m$.
-\end{mydef}
-
-\begin{mydef}{$n\unrel m$.}
-We write $n\unrel m$, or ``$n$ and $m$ are unrelated'' if $n\not\descendantEq m$ and $n\not\ancestorEq m$.
-\end{mydef}
-
-% Command pairs - Axioms
-% ----------------------
-
-\section{Investigating command pairs}
-
-Our aim is to derive information about the effects of sequences
-of commands independently of that actual filesystems.
-In order to make this possible, we investigate the smallest building
-blocks of sequences: pairs of commands that act on a filesystem directly one after the other.
-This approach is useful as there are a limited number of command pairs,
-because, as we argued above, we can disregard the exact output values of commands apart from their type,
-and we can also abstract the relationship between the nodes in the two commands
-to a finite number of cases.
-
-We methodically investigated of all possibilities using a computer program
-to determine
-which pairs of commands cause errors all the time,
-which can be simplified to one or no commands, and which can be reversed
-without any change in their overall effect.
-% TODO: Footnote: URL
-Our basis for this investigation was the model of filesystems introduced in this paper.
-These properties of command pairs are crucial as they determine
-how a set of commands can be re-ordered to be applied to a filesystem
-during synchronization, and what commands will never be compatible.
-
-Below we list a number of statements derived using this method.
-Although they can be proven by investigating all relevant possibilities
-in a filesystem, we refer to these as axioms because in a secondary algebraic model
-that describes commands without reference to an underlying filesystem,
-these would function as meta-rules generating statements we would accept as true.
-See section (TODO) for more about such a model.
-
-\medskip
-
-Pairs of commands in general have the form
-\[ \cxynv\cc  \czwmv \]
-where $X,Y,Z,W\in\typeset$, $n,m\in\setn$, 
-and values are of the appropriate type: 
-$\valvy\in\setvx{Y}$ and $\valvw\in\setvx{W}$.
-
-\begin{myax}\label{ax_separate_commute}
-Commands on unrelated nodes commute:
-$\cxynv\cc\czwmv \equiv \czwmv\cc\cxynv$ where $n\unrel m$.
-\end{myax}
-
-\begin{myax}\label{ax_separate_nobreaks}
-Commands on unrelated nodes do not break every filesystem:
-$\cxynv\cc\czwmv \nequiv \cbrk$ where $n\unrel m$.
-\end{myax}
-
-\begin{myax}\label{ax_same_breaks}
-Commands on the same node break every filesystem if their types are incompatible:
-$\cxynv\cc\czwnv \equiv \cbrk$ where $Y\ne Z$.
-\end{myax}
-
-\begin{myax}\label{ax_same_emptyseq}
-Commands on the same node simplify:
-$\cxynv\cc\czwnv \eqext \emptyseq$ where $Y=Z$ and $X=W=\ccharb$ 
-or $X=W=\cchard$.
-\end{myax}
-
-\begin{myax}\label{ax_same_singlec}
-Commands on the same node simplify:
-$\cxynv\cc \czwnv \equiv \cxwnv$ where $Y=Z$ and $\cxw\neq\cbb$ and $\cxw\neq\cdd$.
-\end{myax}
-
-\begin{myax}\label{ax_distantrel_breaks}
-Commands on distant relatives break all filesystems:
-$\cxynnv\cc\czwnv \equiv \cbrk$
-and $\czwnv\cc\cxynnv \equiv\cbrk$
-where $\nn\descendant n$ and $\nn\neq\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
-\end{myax}
-
-\begin{mydef}{Construction pair.}
-A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parent(n)$ 
-and the commands are one
-of the following:
-   \begin{gather*}
-   % bd>bf
-            \cbdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
-   % bd>bd
-            \cbdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii} \\
-   % fd>bf
-            \cfdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
-   % fd>bd
-            \cfdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii}
-   \end{gather*}
-\end{mydef}
-
-\begin{myax}\label{ax_directchild_breaks}
-All other commands on a child break every filesystem:
-$\cxynnv\cc\czwnv \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
-and the pair is not a construction pair.
-\end{myax}
-
-\begin{mydef}{Destruction pair.}
-A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parent(n)=\nn$ and the commands are one
-of the following:
-   \begin{gather*}
-   % fb<db ??
-            \cfba{n}\cc  \cdba{\nn} \\
-   % fb<df ??
-            \cfba{n}\cc  \cdfaa{\nn}{\valf} \\
-   % db<db ??
-            \cdba{n}\cc  \cdba{\nn} \\
-   % db<df ??
-            \cdba{n}\cc  \cdfaa{\nn}{\valf}
-   \end{gather*}
-\end{mydef}
-
-\begin{myax}\label{ax_directparent_breaks}
-All other commands on a parent break every filsystem:
-$\cxynv\cc\czwnnv \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
-and the pair is not a destruction pair.
-\end{myax}
-
-\begin{mydef}{Assertion command.}
-A command is an assertion command if
-for every filesystem it either breaks it or leaves it in the same state.
-In other words, assertion commands have the same input and output type,
-and there must also be only one possible value for their output.
-Accordingly, in our current algebra, $\cbba{n}$ and $\cdda{n}$ are the only two assertion commands,
-and we do not note their output value as it is determined.
-\end{mydef}
-
-\begin{myax}\label{ax_child_assert}
-An assertion command can be added on a descendant node:
-$\cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n}$ 
-where $\nn\descendant n$ and $\cxy\neq\cdd$.
-\end{myax}
-
-\begin{myax}\label{ax_parent_assert}
-An assertion command can be added on an ancestor node:
-$\cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn}$ 
-where $\nn\descendant n$ and $\cxy\neq\cbb$.
-\end{myax}
-
-\begin{myax}\label{ax_assert}
-Assertion commands can be removed:
-$\cxynv \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
-\end{myax}
-
-% Update detection
-% ----------------
-
-\section{Update detection}
-
-In a command-based reconciliation solution we assume that we have two sequences of commands
-$A$ and $B$ that have modified a single filesystem $\FS$ yielding two different replicas $\FS_A$ and $\FS_B$ that we
-need to reconcile. While it is conceivable that the sequences would be based on a record of
-all operations that modified the two filesystems, in most filesystem implementations
-such records are not implemented, and therefore we must construct suitable sequences
-by comparing $\FS_A$ and $\FS_B$ to their common ancestor, $\FS$. This is called update detection.
-
-A sequence that transforms $\FS$ into $\FS_A$ must contain at least one command on each node
-that changes between the two states of the filesystem. Also, it is easy to see that this is also
-sufficient, as there are commands available for any input and output value. 
-Specifically, if at node $n$, $\FS(n)=X'$ and $\FS_A(n)=Y'\neq X'$, then we add the command $\cxyaa{n}{Y'}$ to $A$
-where $X'\in\setvx{X}$ and $Y'\in\setvx{Y}$.
-
-To be able to describe such sequences better, let us introduce the following properties:
-
-\begin{mydef}{Minimal set or sequence.}
-A sequence or set of commands is minimal if it contains at most one command on every node.
-\end{mydef}
-
-\begin{mydef}{Simple set or sequence.}
-A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
-\end{mydef}
-
-This update detector therefore yields a simple set of commands because we only add a single command
-for each node, and we only add commands that are necessary, that is, there will be no 
-assertion commands in the set.
-
-The next step in generating the sequences is to order the commands collected.
-As this task is at the heart of reconciliation itself independently of update detection,
-we discuss it in the next section.
-Then, in \cref{update_works}, we prove that the resulting sequence actually
-works without breaking the filesystem.
-
-% Ordering commands
-% ----------------
-
-\section{Ordering commands}\label{ordering}
-
-We often encounter the case where we only have a set of commands without a specified order.
-As we have seen above, this can occur after the first stage of update detection,
-but, more importantly,
-it is actually the task of the reconciler to determine whether there is an order,
-and if yes, what order,
-in which updates from multiple replicas can be applied to a filesystem.
-
-In this section we describe an algorithm with which all possible orderings of a
-simple set of commands can be generated, but before doing so, let us consider the following lemma.
-
-\begin{mylem}\label{connected_changes}
-Given a set of commands that
-does not contain assertion commands,
-and which can be applied to a filesystem in some order without breaking it,
-and which contains commands on $n$ and $\nn$ where $\nn\descendant n$
-but $\nn\neq\parent(n)$, then the set must also contain a commands
-on each node between $n$ and $\nn$.
-\end{mylem}
-\begin{proof}
-We prove that under the given conditions, the set must contain a command on $\parent(n)$.
-Then, by repeating this statement, we how that the set must contain commands on every
-ancestor of $n$ up to $\nn$.
-
-Furthermore,
-we prove this proposition for sequences, not sets, as if all sequences must contain a command on $\parent(n)$,
-then so must sets because otherwise there would be no order in which they can be
-applied to any filesystem.
-
-Let $A$ be a sequence that satisfies the conditions;
-we therefore know that it contains a command $\cxynv$ on $n$
-and another command $\czwnnv$ on $\nn$.
-We use an indirect proof and assume that there are no commands on $\parent(n)$ in $A$.
-Next, we create a new sequence $A'\equiv A$ in which $\cxy$ and $\czw$ are next to each other.
-If they are already next to each other in $A$, there is nothing to do.
-Otherwise, consider the command next to $\cxynv$ in the direction where $\czwnnv$ is.
-Let this command be $\cqrmv$.
-If $\czw$ is to the right, then $A$ looks like the following:
-\[ A = \cdots\cc\cxynv\cc\cqrmv\cc\cdots\cc\czwnnv\cc\cdots \]
-If $n\unrel m$, swap $\cxynv$ and $\cqrmv$. Based on \cref{ax_separate_commute} we know that the new
-sequence is equivalent to $A$.
-Otherwise, we know $m\neq\parent(n)$ as there are no commands on $\parent(n)$, and so
-from \cref{ax_distantrel_breaks} we get $A\equiv\cbrk$ which contradicts our assumptions.
-(Note that $A$ cannot contains assertion commands.)
-By repeating this step we can therefore convert $A$ into $A'$ where $\cxynv$ and $\czwnnv$ are neighboring commands.
-However, then \cref{ax_distantrel_breaks} applies to the sequence and therefore $A\equiv A'\equiv\cbrk$ which
-is again a contradiction.
-\end{proof}
-
-\medskip
-
-We can now define our algorithm to generate orders of sets of commands.
-
-Let $U$ be a simple set of commands
-that we know can be applied to at least one filesystem in some order without breaking it.
-Then we can split $U$ into a maximum number of disjunct subsets
-(components) so that the nodes of two commands from two different subsets are unrelated.
-These will simply be the components of the subset of the node forest that contains the nodes affected by the set.
-
-From \cref{ax_separate_commute} we know that commands from different 
-components can be applied in any order.
-Therefore once we have ordered the commands inside a component, we generate
-all permutations of the components themselves, including the ones
-in which commands from separate components mix and overlap
-(but where the possible orders determined for commands inside the components are respected).
-
-Next, consider the ordering inside a component.
-
-This is not a problem in the case of components containing a single command only.
-(Note that $\cff$ can only appear in a component of one.)
-
-In each component that is larger than one, 
-we know that all nodes are related, and from \cref{connected_changes}
-we also know that it must contain commands on all nodes in between.
-Therefore the nodes
-form a rooted ordered tree,
-and the pairs of commands connected by the edges in the tree 
-must be construction or destruction pairs.
-(Otherwise, there would be no ordering of the component that is not equivalent to $\cbrk$
-and via \cref{ax_separate_commute} there would be no ordering of the whole set, either.)
-
-To order the commands in the component,
-select the command with the topmost node, so that there would be no command
-on its parent node (if there is one). 
-If the command removes content at this node (it is of the form $X\empt$), 
-then it must follow all other commands in the component, and
-all parent--child pairs in the whole component must be destruction pairs.
-Otherwise, the command with the topmost node needs to precede the other commands,
-and the component must be made of construction pairs.
-These follow from the patterns of construction and destruction pairs, which
-at no point can mix without causing any sequence to break all filesystems.
-
-Then move the command with the topmost node to the beginning or the end of
-the sequence we are creating out of the component,
-and recursively start the whole algorithm again on the commands in the component that remain,
-potentially splitting them into sub-components.
-The result of this process is a set of possible orders for each component,
-which are then combined into a set of possible orders for the whole set of commands.
-
-\begin{mydef}{$\orderset{U}$.}
-We use $\orderset{U}$ to denote the set of sequences that contain all commands in
-the simple set $U$
-and represent all orders generated by this algorithm.
-\end{mydef}
-
-It follows from the algorithm that:
-\begin{mycor}\label{lemma:neighbor}
-If $U$ contains commands on both $n$ and $\parent(n)$, then
-there is a $U'\in\orderset{U}$ where they are next to each other.
-\end{mycor}
-
-As a specific case, we can regard a sequence of commands $S$
-as a set and determine its $\orderset{S}$.
-An important property of simple sequences is that
-all of their valid orderings are equivalent,
-and all equivalent sequences are mere reorderings:
-
-\begin{mylem}\label{simple_reorder_equiv}
-For any simple sequence $S\neq\cbrk$,
-$\forall T: T\equiv S \Leftrightarrow T\in\orderset{S}$.
-\end{mylem}
-\begin{proof}
-TODO
-\end{proof}
-
-It follows from this that given a simple set,
-we can simply assume that it has an order.
-Accordingly, we will at times treat not only sequences as sets,
-but simple sets as sequences.
-
-\medskip
-
-% Correctness of update detection
-% -------------------------------
-
-Based on \cref{connected_changes} we can also show that
-the update detector does function as intended as:
-
-\begin{myth}\label{update_works}
-A sequence of commands returned by the update detector
-when comparing $\FS^*$ to the original $\FS$
-will not break $\FS$ if it is applied to it.
-\end{myth}
-\begin{proof}
-Let $\FS\neq\fsbroken$ be the original filesystem, and $\FS^*\neq\fsbroken$
-be the filesystem after the changes we intend to detect.
-Let us assume that some mechanism recorded all changes that occurred
-to $\FS$ until it reached the state $\FS^*$.
-Our set if commands is sufficient to record any change, as
-there are commands for every input and output type pair, therefore
-we know that the changes can be recorded as a sequence of commands $S$
-where $S\FS=\FS^*$.
-Note that $S$ will not contain assertion commands, as they do not
-represent an actual change in the filesystem.
-
-Therefore, \cref{connected_changes} applies to $S$ and we know
-if it contains commands on $\nn$ and $n$ where $\nn\descendant n$,
-then it also contains commands on nodes in between;
-which is equivalent to saying that if $\FS$ changed
-at node $\nn$ and $n$, then it had to change on the nodes in between.
-
-If so, then, similarly to what happens in the ordering algorithm,
-we can separate $S$ into components of commands on related nodes,
-as commands from separate components freely commute yielding an equivalent sequence.
-From the arguments above, we also know that each component
-must be made up of only desctruction or only construction pairs,
-but not a mixture of the two.
-This means that in each component, parents either strictly precede or succeed child nodes
-(as otherwise $S\equiv\cbrk$ would hold),
-from which it follows that once the components are separated
-in a new sequence $S'\equiv S$,
-commands on the same nodes are next to each other in $S'$.
-
-Based on \cref{ax_same_emptyseq,ax_same_singlec} there is
-an $S''\eqnrw S'$ in which multiple commands on the same nodes
-are simplified into a single command or an empty sequence,
-and therefore $S''$ is simple and $S\equiv S'\eqext S''$.
-It is easy to see that $S''$ must contain the same commands
-as the output of the update detector, $U$, as both are simple
-but reflect all changes between $\FS$ and $\FS^*$.
-If so, then based on \cref{simple_reorder_equiv}
-we have $S''\in\orderset{U}$, from which
-$S\equiv S'\eqext S''\equiv U$, and as $S\FS = \FS^* \neq \fsbroken$,
-therefore $U\FS\neq\fsbroken$.
-\end{proof}
-
-\section{Reconciliation}
-
-If we start with two copies of the filesystem $\FS$,
-and two different sequences are applied to the copies to yield $\FS_A:=A\FS$
-and $\FS_B:=B\FS$, then our aim is to define sequences of commands $\reca$ and $\recb$
-so that $\recb\FS_A$ and $\reca\FS_B$ would be as close to each other as possible.
-
-We work based on the assumption that to achieve this, we need
-to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
-As some commands may have been applied to both filesystems, our first approximation
-is $\reca = A\setminus B$ and $\recb = B\setminus A$
-(in some suitable order).
-This, however, will break both filesystems if there have been incompatible updates
-in $A$ and $B$. 
-Our aim is therefore to provide an algorithm that selects the commands 
-$\reca \subset A\setminus B$
-and $\recb \subset B\setminus A$ 
-so that $\reca\FS_B\neq\fsbroken$ and $\recb\FS_A\neq\fsbroken$,
-and show that these are the longest sequences with this property, that is,
-adding any command left out from $\reca$ or $\recb$ will break the filesystems.
-
-We assume that $A$ and $B$ are returned by an update detector,
-and so they are simple sequences.
-(Otherwise, they can be simplified to become simple sequences.)
-We also assume that $\FS_A$ and $\FS_B$ are not broken.
-With these assumptions,
-we can now define independent sequences and
-our reconciliation algorithm.
-
-\begin{mydef}{Independent commands, sequences and sets.}
-For two commands $\cxynv$ and $\czwmv$ we write $\cxynv\indep\czwmv$ if $\cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk$.
-For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
-$\forall a\in A \mbox{~and~} \forall b\in B: a\indep b$.
-\end{mydef}
-
-\begin{mydef}{Reconciliation.}\label{def:reconciliation}
-\begin{align*}
-\reca = \{c| & \\
-& c\in A\setminus B \\
-& \wedge \\
-& \forall c'\in B\setminus A: c\indep c'\\
-\} &
-\end{align*}
-
-In other words, the sequence $\reca$ we apply to $\FS_B$ consists of all commands from $A\setminus B$
-that are independent of every command in $B\setminus A$.
-The order of commands in the sequence can be determined using the algorithm described in
-\cref{ordering} as any subset of $A$ is also simple.
-In a similar way, $\recb$ can be obtained by reversing $A$ and $B$.
-\end{mydef}
-
-We would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
-that is, without loss of generality,
-\[ \reca\FS_B\neq\fsbroken. \]
-So that we can formalize statements needed to prove this,
-let us introduce two relations that describe under what conditions
-sequences of commands work, that is, do not break a filesystem.
-
-% Works
-% -----
-
-\begin{mydef}
-% Unsure if this relation should be in the algebra.
-For a set of $k$ sequences
-$\works{A_1,A_2,\ldots,A_k}$ means that 
-$A_1,A_2,\ldots,A_k$ work at the same time, that is,
-% intended interpretation:
-\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_k\FS\neq\fsbroken\]
-As the sequences form a set, their order is irrelevant.
-% inference rules:
-We also know that $\works{A} \Leftrightarrow A\nequiv \cbrk$. 
-\end{mydef}
-
-\begin{mydef}
-For two sets of sequences, $\worksc{A_1,A_2,\ldots,A_k}{B_1,B_2,\ldots,B_l}$ means that 
-all of $A_1,\ldots,A_k$ work where all of $B_1,\ldots,B_l$ work,
-that is,
-% intended interpretation:
-\begin{align*}
-\forall \FS:&\\ 
-&B_1\FS\neq\fsbroken \wedge \cdots \wedge B_k\FS\neq\fsbroken\\
-&\Rightarrow\\
-&A_1\FS\neq\fsbroken \wedge \cdots \wedge A_l\FS\neq\fsbroken
-\end{align*}
-As above, the order of the sequences in the sets is not relevant.
-\end{mydef}
-
-\begin{mydef}{Sets of sequences.}
-For brevity, we will use $\seqset{S}$ to note an arbitrary set of sequences,
-and $A\cc\seqset{S}$ to note the set of sequences $\{A\cc S|S\in\seqset{S}\}$.
-\end{mydef}
-
-It is easy to see that the following corollaries are true:
-
-% An inference rule in the algebra
-% $\worksc{X}{X}$ is always true for any set of sequences $X$,
-
-\begin{mycor}
-% An inference rule in the algebra
-$B\eqext A \Rightarrow \worksc{A}{B}$.
-\end{mycor}
-
-\begin{mycor}\label{worksextpostfix}
-% An inference rule in the algebra
-$\forall A,S: \worksc{A}{A\cc S}$, that is, if a sequence works, its prefix also works.
-\end{mycor}
-
-\begin{mycor}\label{workschained}
-% An inference rule in the algebra
-$\workssign$ can be chained:
-if $\seqset{A'}\subset\seqset{A}$, then
-$ \worksc{\seqset{C}}{\seqset{A'}} \wedge \worksc{\seqset{A}}{\seqset{B}} \Rightarrow \worksc{\seqset{A}\cup\seqset{C}}{\seqset{B}}$.
-\end{mycor}
-
-We also prove the following lemmas.
-
-\begin{mylem}\label{unrelated_is_independent}
-Two different commands that are not assertion commands are independent iff the nodes they change are unrelated:
-\[ \cxynv\indep\czwmv \Leftrightarrow n\unrel m \]
-if $\cxynv\neq\czwmv$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
-\end{mylem}
-\begin{proof}
-We proceed in two steps; first, we prove that
-\[ \cxynv\nindep\czwmv \wedge n\unrel m \] would lead to contradiction.
-By definition, if the two commands are not independent, then at least one of the following holds:
-\begin{itemize}
-\item $\czwmv\cc \cqrov \equiv\cbrk$
-\item $\cqrov\cc \czwmv \equiv\cbrk$
-\item $\czwmv\cc \cqrov \nequiv \cqrov\cc \czwmv$
-\end{itemize}
-However, from \cref{ax_separate_commute,ax_separate_nobreaks} we also know that
-if $n\unrel m$ then none of the above can be true.
-
-Next, we prove that
-\[ \cxynv\indep\czwmv \wedge n\nunrel m \] would lead to contradiction.
-As $n\nunrel m$
-we know that $n=m$, $n\descendant m$ or $m\descendant n$.
-
-If $n=m$, then from \cref{ax_same_breaks} we know $Y=Z$ and $W=X$
-as otherwise the commands, in one order or the other, would break all filesystems
-and they could not be independent.
-The commands are not assertion commands, and so from \cref{ax_same_singlec}
-we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $Y=W$ and $\valvy=\valvw$.
-Therefore $X=Y=Z=W$ which is only possible if both commands are $\cff$ and have the same
-output value. This, however, contradicts our assumption that they are different.
-
-If $n\descendant m$ or $m\descendant n$, then
-from \cref{ax_distantrel_breaks} we know that if they are not directly related,
-then $\cxynv\cc\czwmv$ breaks all filesystems, and they cannot be independent.
-From the construction and destruction pairs and 
-\cref{ax_directchild_breaks,ax_directparent_breaks} we also see that
-even if they are directly related, either
-$\cxynv\cc\czwmv$ or $\czwmv\cc\cxynv$ 
-breaks all filesystems, so they again cannot be independent.
-\end{proof}
-
-\begin{myax}\label{combine_independent_commands}
-The combination of independent commands works wherever the original commands work:
-\begin{align*}
-\forall\FS: &\cxynv\indep \czwmv \\
-&\quad\wedge \cxynv\FS\neq\fsbroken \\
-&\quad\wedge \czwmv\FS\neq\fsbroken \\
-&\Rightarrow \cxynv\cc \czwmv\FS\neq\fsbroken.
-\end{align*}
-\end{myax}
-\begin{proof}
-We name this proposition an axiom for the same reason as above,
-but it is easy to provide an indirect proof based on our filesystem model.
-Assume that $\cxynv\cc \czwmv\FS=\fsbroken$.
-We know $\cxynv\FS\neq\fsbroken$ so it must be applying 
-$\czwmv$ that breaks it.
-Applying a command can only result in a broken filesystem in three cases.
-First, if the filesystem was already broken, which cannot be the case here.
-Second, if the input type does not match the filesystem,
-but we know $\FS(m)\in\setvx{W}$ and so
-$(\cxynv\FS)(m)\in\setvx{W}$ as based on \cref{unrelated_is_independent}, $n\neq m$.
-Third, if the new filesystem violates the tree property.
-This again cannot be the case because we also know that $n\unrel m$
-and the tree property only depends on the types of the parent and children of $m$,
-which therefore cannot be changed by $\cxynv$.
-\end{proof}
-
-This result can be extended to sequences:
-
-\begin{mylem}\label{combine_independent_sequences}
-The combination of independent sequences works wherever the original sequences work:
-\[ S\indep T \Rightarrow \worksc{S\cc T}{S,T}. \]
-\end{mylem}
-\begin{proof}
-Assume that there is a filesystem $\FS$ so that
-$S\FS\neq\fsbroken$ and $T\FS\neq\fsbroken$, but
-$(S\cc T)\FS=\fsbroken$.
-
-From \cref{unrelated_is_independent,ax_separate_commute} we know that
-the commands in $S$ and $T$ pairwise commute, and so any sequence
-that contains the commands from $S$ and $T$ and preserve their original partial order
-is equivalent to $S\cc T$ on all filesystems.
-
-Let the command that breaks $\FS$ in $T$ when applying $S\cc T$ be $t$
-so that $T=T_0\cc t\cc T_1$.
-It is still true that $(T_0 \cc t)\FS\neq\fsbroken$,
-and by definition $(S\cc T_0)\FS\neq\fsbroken$,
-but $(S\cc T_0\cc t)\FS=\fsbroken$.
-Also, from above we know that $S\cc T_0\equiv T_0\cc S$
-and so $(T_0 \cc S)\FS\neq\fsbroken$.
-
-If we denote the first command in $S$ with $s_1$,
-this means that $(T_0 \cc s_1)\FS\neq\fsbroken$,
-which we can combine with $(T_0 \cc t)\FS\neq\fsbroken$, $t\indep s_1$ and
-\cref{combine_independent_commands}
-(using $T_0\FS$ as the reference filesystem)
-to arrive at $(T_0 \cc s_1\cc t)\FS\neq\fsbroken$.
-
-We can repeat this step for $s_2$, the next command in $S$,
-and from 
-$(T_0 \cc s_1\cc t)\FS\neq\fsbroken$
-and
-$(T_0 \cc s_1\cc s_2)\FS\neq\fsbroken$
-arrive at
-$(T_0 \cc s_1\cc s_2\cc t)\FS\neq\fsbroken$.
-This can be repeated until $S$ is exhausted and we get
-$(T_0 \cc S\cc t)\FS\neq\fsbroken$, which is a contradiction.
-\end{proof}
-
-Separately, we prove the following:
-
-\begin{mylem}\label{worksinputmatch}
-If $A$ and $B$ are minimal sequences, $\works{A,B}$,
-and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$)
-then their input types must match ($X=Z$).
-\end{mylem}
-\begin{proof}
-This is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
-either $\cxynv$ or $\czwnv$ would not break, 
-and consequently $A$ and $B$ cannot work on the same filesystem.
-\end{proof}
-
-\medskip
-
-We continue by defining inverse commands and sequences
-which allow us to move parts of sequences between the
-condition and consequence parts of $\workssign$.
-
-\begin{mydef}{Inverse commands and sequences.}
-The inverse of command $\cxynv$ is $\cxynv^{-1} = \caaaa{Y}{X}{n}{\valvx}$
-where $V_X$ is an arbitrary value from $\setvx{X}$.
-We write $S^{-1}$ for the inverse of sequence $S$, which consists of the inverses of the commands in $S$
-in reverse order.
-\end{mydef}
-
-\begin{mydef}{$\typeeq$.}
-For two filesystems we write $\FS\typeeq\GS$
-iff 
-at all nodes the types of their values are the same, or they are both broken.
-\end{mydef}
-
-From the definitions we can clearly see that
-\begin{mycor}\label{negneg_is_typeeq}
-$\forall \FS: (S^{-1})^{-1}\FS\typeeq \FS$.
-\end{mycor}
-
-\begin{mylem}\label{r_invmove}
-A common prefix of sequences can be moved to the other side of $\workssign$ by inverting it:
-\begin{gather*}
-\worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \\
-\worksc{\seqset{A}}{B\cc \seqset{S}} \Rightarrow \worksc{B^{-1}\cc \seqset{A}}{\seqset{S}}
-\end{gather*}
-\end{mylem}
-\begin{proof}
-This is based on the fact that in our model, unless they break a filesystem,
-commands change one type of value into another, but never merge types.
-That is,
-sequences---as functions mapping filesystems to filesystems---are
-essentially bijections over type-equality
-with the only ``sink'' being $\fsbroken$:
-\begin{align*}
-\forall S,\FS,\GS: &S\FS\neq\fsbroken \Rightarrow \\
-&(S\FS\ntypeeq S\GS \Leftrightarrow \FS\ntypeeq \GS).
-\end{align*}
-
-For the proposition
-\[ \worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \]
-the rest of the proof is illustrated by the diagram below
-where Dom($x$), the domain of $x$, represents the set of filesystems
-the sequence $x$ does not break, or neither of the sequences in the set $x$ breaks.
-
-\input{inverse-works} % TODO arrows too small
-
-We see that the set of filesystems the sequences in $\seqset{A}$ do not break intersect with the range of $B$.
-As $B$ is a bijection between its domain and range, we can use $B^{-1}$ to map this intersection back
-onto the domain of $B$.
-As $\worksc{B\cc \seqset{A}}{\seqset{S}}$ the domain of $\seqset{S}$ must be a subset of this
-projected intersection.
-If so, then we can use $B$ to map the domain of $\seqset{S}$, which yields the domain of $B^{-1}\cc \seqset{S}$.
-As it is also a part of the domain of $A$, we get $\worksc{\seqset{A}}{B^{-1}\cc \seqset{S}}$.
-
-The second part of the lemma can be proven in a similar way.
-\end{proof}
-
-\begin{mylem}\label{indep_prefix_combine}
-The combination of sequences with a common head and independent tails continues to work under the same conditions:
-\[ \worksc{A\cc B}{\seqset{S}} \wedge \worksc{A\cc C}{\seqset{S}} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{\seqset{S}} \]
-\end{mylem}
-\begin{proof}
-Based on \cref{r_invmove} we know
-$\worksc{B}{A^{-1}\cc \seqset{S}}$ and $\worksc{C}{A^{-1}\cc \seqset{S}}$,
-and from \cref{combine_independent_sequences} we know
-$\worksc{B\cc C}{B,C}$.
-Combining these using \cref{workschained}
-we get
-$\worksc{B\cc C}{A^{-1}\cc \seqset{S}}$. 
-Finally, applying the second line of \cref{r_invmove} yields
-$\worksc{(A^{-1})^{-1}\cc B\cc C}{\seqset{S}}$, which proves our lemma 
-as $\forall\FS: (A^{-1})^{-1}\FS\typeeq A\FS$ (\cref{negneg_is_typeeq}).
-\end{proof}
-
-\medskip
-
-% Correctness of reconciliation
-% -----------------------------
-
-We are now ready to prove that the proposed algorithm for reconciliation is correct,
-that is, applying its result is not going to break the replicas.
-We reformulate the original proposition, $\reca\FS_B\neq\fsbroken$,
-based on $\FS_B=B\FS$ and so we aim to prove that
-$B\cc\reca$ works wherever $A$ and $B$ work:
-
-\begin{myth}
-If $A, B$ are simple, then $\worksc{B\cc \reca}{A,B}$,
-where, to restate \cref{def:reconciliation},
-% { % scope
-% \renewcommand{\themydef}{\ref{def:reconciliation}}
-% \begin{mydef}
-\begin{align*}
-\reca = \{c| & \\
-& c\in A\setminus B \\
-& \wedge \\
-& \forall c'\in B\setminus A: c\indep c'\\
-\}. &
-\end{align*}
-% \end{mydef}
-% } % scope
-\end{myth}
-
-This is trivial unless $\works{A,B}$, so we assume that it is true.
-Let us first investigate the part of $A$ and $B$ that is excluded from
-$\reca$: their intersection.
-
-\begin{mylem}\label{can_move_intersection}
-Let $A$ and $B$ be two simple sequences so that $\works{A, B}$.
-Then their intersection, in some suitable order, also works on any filesystem
-either of them works on:
-$\worksc{A\cap B}{A}$, and, by symmetry,
-$\worksc{A\cap B}{B}$.
-\end{mylem}
-
-\begin{proof}
-The difficulty is that commands in $A\cap B$ can occur anywhere in $A$.
-Therefore, first we prove the following:
-if all commands are marked in $A$ that also appear in $B$,
-then there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.
-
-We show that $A$ can be transformed via equivalences so that this would be true.
-Our proposition is that if the marked commands are not at the beginning, then
-the sequence contains an unmarked command followed by a marked command.
-We show that these can be swapped resulting in an equivalent sequence.
-Then, by repeating this process similarly to bubble sorting, we can generate 
-a suitable $A'$.
-
-\medskip
-
-Let us consider therefore the marked command preceded by an unmarked command in $A$,
-and let the marked command be $\cxynv$, 
-and the preceding unmarked command be $\czwmv$.
-As $A$ is simple and $\works{A}$, from 
-\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
-we know that these commands can only be on unrelated paths or form a construction or destruction pair.
-In the first case, swapping the commands results in a sequence equivalent to $A$,
-and we show that the last two cases are impossible as they would lead to contradiction.
-
-In these cases, either $m=\parent(n)$ or $n=\parent(m)$.
-If $B$ has a command on $m$, then
-from \cref{lemma:neighbor}
-we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxy$ (also in $B$),
-and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
-When describing our ordering algorithm in \cref{ordering} we saw
-that the command on the parent path deremines whether a pair of commands
-is a construction or destruction pair,
-and that this, in turn, determines whether the command on the child path must
-precede or follow the other command as otherwise the sequence would break all filesystems.
-This argument holds for both $A$ and $B$, and so the command on $m$ must be on
-the same side of the command on $n$ in both sequences.
-
-If $B$ has no command on $m$, then let $B'$ be $B$, 
-but with an extra command added to it just before $\cxy$
-according to \cref{ax_child_assert,ax_parent_assert}, 
-from which we know that $B'\equiv B$.
-We also know that $B'$ is still minimal (but no longer simple).
-
-In either case, therefore,
-we have a minimal $B'$ which has a command on $m$ just before $\cxynv$ and $B'\equiv B$.
-Let this command on $m$ be $\cqrmv$.
-\begin{gather*}
-A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
-B' = \cdots\cc  \cqrmv\cc  \cxynv\cc  \cdots
-\end{gather*}
-
-As $\works{A,B}$ and so $\works{A,B'}$, 
-from \cref{worksinputmatch}
-we know that $Q=Z$.
-
-Going back to the construction and destruction pairs we see that the output type of the first command
-is always the same, and it is either $D$ or $\empt$ depending on the relationship between $n$ and $m$.
-Therefore $R=W$ and $\cqrmv=\czwmv$
-as $|\setd|=|\setb|=1$. 
-If $B$ originally had a command on $m$,
-this is a contradiction as $\czw$ was not marked, but we see it must also be in $B'$ and therefore in $B$.
-If $B$ had no command on $m$,
-this is a contradiction because the command on $m$ in $B'$ is an assertion command, so $Z=Q=R=W$, 
-but $A$ contained no assertion commands.
-
-\medskip
-
-We now know that there is an $A'\equiv A$ in which commands in $A\cap B$
-are at the beginning, and therefore 
-from \cref{worksextpostfix}
-$\worksc{A\cap B}{A}$ and by symmetry $\worksc{A\cap B}{B}$.
-\end{proof}
-
-\medskip
-
-\newcommand{\acb}{(A\cap B)}
-\newcommand{\acbi}{\acb^{-1}}
-\newcommand{\amb}{(A\setminus B)}
-\newcommand{\bma}{(B\setminus A)}
-We would like to prove that $\worksc{B\cc \reca}{A,B}$.
-From the above we know that this is equivalent to
-\[ \worksc{\acb\cc \bma\cc \reca}{A,B}. \]
-As we already know that $\reca\indep\bma$
-and that $\worksc{\acb\cc \bma}{A,B}$
-(as $\worksc{B}{A,B}$),
-based on \cref{indep_prefix_combine}
-we only need to prove that
-\[ \worksc{\acb\cc \reca}{A,B}. \]
-Using \cref{r_invmove} we can rephrase this as
-\[ \worksc{\reca}{\acbi\cc A,\acbi\cc B}. \]
-
-To restate some results above, we therefore already know the following things:
-\begin{itemize}
-\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
-\item $\amb \cap \bma = \emptyset$
-\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
-\item $\worksc{\amb, \bma}{\acbi\cc A,\acbi\cc B}$ 
-because of \cref{r_invmove}
-as $\worksc{A,B}{A,B}$,
-and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
-\end{itemize}
-
-Our theorem is therefore proven if we prove the following lemma:
-\newcommand{\condSimple}{(c1)}
-\newcommand{\condDisj}{(c2)}
-\newcommand{\condApr}{(c3)}
-\newcommand{\condWork}{(c4)}
-\begin{mylem}
-If
-   \begin{itemize}
-   \item[\condSimple] $S$ and $T$ are simple sequences,
-   \item[\condDisj] $S\cap T=\emptyset$,
-   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
-   \item[\condWork] $\worksc{S,T}{\seqset{C}}$ for some set of sequences $\seqset{C}$,
-   \end{itemize}
-then
-\[ \worksc{S^*}{\seqset{C}}. \]
-\end{mylem}
-
-\begin{proof}
-This is trivial unless $\works{\seqset{C}}$, so we will assume that it is true
-and therefore $\works{S,T}$.
-
-The proof is similar to that of \cref{can_move_intersection}.
-We mark all commands in $S$ that are in its subset $S^*$, and
-we prove that $S$ can be transformed into $S'$ via equivalences
-so that all marked commands would be at its beginning.
-If so, then based on \cref{worksextpostfix}
-$\worksc{S^*}{\seqset{C}}$ as $\worksc{S'}{\seqset{C}}$ and $S'=S^*\cc S_0$ 
-where $S_0$ contains the remaining (conflicting) commands.
-
-Again we know that if $S$ does not already have all marked commands at its beginning,
-then there is an unmarked command followed by a marked one.
-We show that these commands are independent and so they can be swapped
-resulting in an equivalent sequence.
-By repeating this process we can generate a suitable $S'$.
-
-Let therefore the marked command in $S$ be $\cxynv$
-and the preceding unmarked command be $\czwmv$.
-As $S$ is simple and $\works{S}$, from 
-\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
-we know that these commands can only be on unrelated paths or form a construction or destruction pair.
-In the first case, swapping the commands results in a sequence equivalent to $S$;
-we only need to show that the other two cases are not possible as they would lead to a contradiction.
-
-In the last two cases, we know that either $m=\parent(n)$ or $n=\parent(m)$.
-We also know that because of {\condApr} there must be 
-a command $\cqrov$ in $T$ which is not independent of $\czwmv$
-as $\czwmv$ is not part of $S^*$.
-\begin{gather*}
-S = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
-T = \cdots\cc  \cqrov\cc \cdots
-\end{gather*}
-We know none of these commands is an assertion command, and 
-from {\condDisj} that $\cqrov\neq\czwmv$.
-Therefore, based on \cref{unrelated_is_independent} we know this means that
-either $m\descendantEq o$ or $o\descendantEq m$.
-From {\condApr} we also know that $\cxynv\indep \cqrov$,
-and so because of \cref{unrelated_is_independent},
-$n\unrel o$.
-
-We therefore have four cases considering the relationships between $n,m$ and $o$:
-\begin{itemize}
-\item $n=\parent(m) \wedge o\descendantEq m$.
-   This would mean that $o\descendantEq n$ or $n=\parent(o)$, which contradicts $n\unrel o$.
-\item $n=\parent(m) \wedge m\descendantEq o$.
-   This would mean that $n\descendant o$, which contradicts $n\unrel o$.
-\item $m=\parent(n) \wedge o\descendantEq m$.
-   This would mean that $o\descendant n$, which contradicts $n\unrel o$.
-\item $m=\parent(n) \wedge m\descendantEq o$.
-   Let us continue with this case.
-\end{itemize}
-
-We know that $T$ cannot have a command on $m$ as $m=\parent(n)$ and $\cxynv\indep T$,
-and so $m\neq o$ and therefore $m\descendant o$.
-This means we can create a new sequence $T'\equiv T$ by inserting a command on 
-$m$ into $T$ before $\cqrov$
-according to \cref{ax_parent_assert}.
-We now have $\cxynv\indep T\equiv T'$ which is a contradiction as
-$T'$ has a command on $m$ and $m=\parent(n)$.
-\end{proof}
-
-\medskip
-
-% Reconciliation is maximal
-% -------------------------
-% This is where we're using |D|=1
-% C.f. strict / liberal etc. reconciliation in references
-
-% TODO
-TODO: $\reca$ is maximal
-
-% TODO
-TODO: About setting up an algebra / calculus
-
-% TODO
-TODO: Are these results quite obvious as this is a well-known kind of algebra or system?
-
-\begin{thebibliography}{99}
-
-\bibitem{NREC:alg} Ramsey, Norman and Elod Csirmaz: {\it An algebraic approach to
-file synchronization...}
-
-\bibitem{BZ} Bill Zissimopoulos, personal communication, ...
-
-\end{thebibliography}
-
-\end{document}

### 2015-12-04 2015/paper.tex
Split source into sections

@@
 
-\newcommand{\setv}{\mathcal{V}} % Set of values
-\newcommand{\setvx}[1]{\mathcal{V}_{#1}} % Set of values with custom index
-\newcommand{\setf}{\setvx{F}} % Set of file values
-\newcommand{\setd}{\setvx{D}} % Set of directory values
-\newcommand{\setb}{\setvx{\empt}} % Set of empty values
-\newcommand{\setn}{\mathcal{N}} % Set of nodes / paths
-\newcommand{\empt}{\bot}
-\newcommand{\parent}{\mathtt{parent}}
-\newcommand{\topnode}{\mathtt{None}} % return value of parent()
-\newcommand{\fsbroken}{\mathtt{Broken}} % broken FS value
-\newcommand{\FS}{\Phi} % a filesystem
-\newcommand{\GS}{\Xi} % another filesystem
-\newcommand{\nn}{n^*} % parent node
-
-\newcommand{\cbrk}{\mathtt{break}} % 'break' command
-\newcommand{\ccharb}{\empt}
-\newcommand{\ccharf}{\mathtt{F}}
-\newcommand{\cchard}{\mathtt{D}}
-\newcommand{\vald}{d} % Directory value
-\newcommand{\valdi}{d_1}
-\newcommand{\valdii}{d_2}
-\newcommand{\valf}{f} % File value
-\newcommand{\valvx}{v_X} % Value of type X
-\newcommand{\valvy}{v_Y} % Value of type Y
-\newcommand{\valvw}{v_W}
-\newcommand{\valvr}{v_R}
-\newcommand{\typeset}{\{\cchard,\ccharf,\ccharb\}} % Set of types in commands
-\newcommand{\caa}[2]{\langle{#1,#2}\rangle}
-\newcommand{\caaa}[3]{\langle{#1,#2,#3}\rangle}
-\newcommand{\caaaa}[4]{\langle{#1,#2,#3,#4}\rangle}
-\newcommand{\cbb}{\caa{\ccharb}{\ccharb}}
-\newcommand{\cbba}[1]{\caaa{\ccharb}{\ccharb}{#1}}
-\newcommand{\cbf}{\caa{\ccharb}{\ccharf}}
-\newcommand{\cbfaa}[2]{\caaaa{\ccharb}{\ccharf}{#1}{#2}}
-\newcommand{\cbd}{\caa{\ccharb}{\cchard}}
-\newcommand{\cbdaa}[2]{\caaaa{\ccharb}{\cchard}{#1}{#2}}
-\newcommand{\cfb}{\caa{\ccharf}{\ccharb}}
-\newcommand{\cfba}[1]{\caaa{\ccharf}{\ccharb}{#1}}
-\newcommand{\cff}{\caa{\ccharf}{\ccharf}}
-\newcommand{\cfd}{\caa{\ccharf}{\cchard}}
-\newcommand{\cfdaa}[2]{\caaaa{\ccharf}{\cchard}{#1}{#2}}
-\newcommand{\cdb}{\caa{\cchard}{\ccharb}}
-\newcommand{\cdba}[1]{\caaa{\cchard}{\ccharb}{#1}}
-\newcommand{\cdf}{\caa{\cchard}{\ccharf}}
-\newcommand{\cdfaa}[2]{\caaaa{\cchard}{\ccharf}{#1}{#2}}
-\newcommand{\cdd}{\caa{\cchard}{\cchard}}
-\newcommand{\cdda}[1]{\caaa{\cchard}{\cchard}{#1}}
-\newcommand{\cxy}{\caa{X}{Y}}
-\newcommand{\cxyaa}[2]{\caaaa{X}{Y}{#1}{#2}}
-\newcommand{\cxynv}{\caaaa{X}{Y}{n}{\valvy}}
-\newcommand{\cxynnv}{\caaaa{X}{Y}{\nn}{\valvy}}
-\newcommand{\cxw}{\caa{X}{W}}
-\newcommand{\cxwnv}{\caaaa{X}{W}{n}{\valvw}}
-\newcommand{\czw}{\caa{Z}{W}}
-\newcommand{\czwnv}{\caaaa{Z}{W}{n}{\valvw}}
-\newcommand{\czwnnv}{\caaaa{Z}{W}{\nn}{\valvw}}
-\newcommand{\czwmv}{\caaaa{Z}{W}{m}{\valvw}}
-\newcommand{\cqr}{\caa{Q}{R}}
-\newcommand{\cqrmv}{\caaaa{Q}{R}{m}{\valvr}}
-\newcommand{\cqrov}{\caaaa{Q}{R}{o}{\valvr}}
-
-\newcommand{\cc}{\circ} % Command / sequence concatenation
-\newcommand{\descendant}{\prec}
-\newcommand{\descendantEq}{\preceq}
-\newcommand{\ancestor}{\succ}
-\newcommand{\ancestorEq}{\succeq}
-
-\newcommand{\eqext}{\sqsubseteq} % equivalent to
-\newcommand{\eqnrw}{\sqsupseteq} % extended by
-\newcommand{\nequiv}{\not\equiv}
-\newcommand{\indep}{\mathrel{\wr\wr}} % Independent commands, sequences
-\newcommand{\unrel}{\indep} % Unrelated nodes
-\newcommand{\nindep}{\,{\centernot{\wr\wr}}\,} % not \indep
-\newcommand{\nunrel}{\nindep} % not \unrel
-
-\newcommand{\workssign}{\mathbf{w}}
-\newcommand{\works}[1]{\workssign({#1})}
-\newcommand{\worksc}[2]{\workssign({#1}\mathrel{|}{#2})}
-
-\newcommand{\typeeq}{\stackrel{t}{=}} % Type equality
-\newcommand{\ntypeeq}{\centernot{\stackrel{t}{=}}}
-
-\newcommand{\emptyseq}{\lambda} % empty sequence
-
-\newcommand{\orderset}[1]{\vec{\wp}({#1})}
-\newcommand{\seqset}[1]{\underline{#1}} % Set of sequences
-
-\newcommand{\recchar}[3]{{#1}^{#3}_{\mathcal{R}|{#2}}}
-\newcommand{\reca}{\recchar{A}{B}{}} % Reconciled from A
-\newcommand{\recb}{\recchar{B}{A}{}} % Reconciled from B
-
-\newcommand{\acb}{(A\cap B)}
-\newcommand{\acbi}{\acb^{-1}}
-\newcommand{\amb}{(A\setminus B)}
-\newcommand{\bma}{(B\setminus A)}
-
-\theoremstyle{definition}
-
-\newtheorem{mydef}{Definition}
-\crefname{mydef}{definition}{definitions}
-
-\newtheorem{myax}{Rule}
-\crefname{myax}{rule}{rules}
-
-\newtheorem{mylem}{Lemma}
-\crefname{mylem}{lemma}{lemmas}
-
-\newtheorem{myth}{Theorem}
-\crefname{myth}{theorem}{theorems}
-
-\newtheorem{mycor}{Corollary}
-\crefname{mycor}{corollary}{corollaries}
+\input{macros}
 
@@
 
-\section{Definition of a Filesystem}
-
-We model a filesystem using a function $\FS$ with a set of nodes (filesystem paths) $\setn$ as its domain,
-and a set of possible contents $\setv$ as its codomain:
-\[ \FS : \setn \rightarrow \setv \] 
-In our model, $\setn$ contains all possible nodes, including the ones where there is no file or directory,
-and $\setv$ contains a special element, $\empt$, which is the value of $\FS$ at an empty node.
-We consider the contents of files, as well as any meta-information of files
-and directories (e.g. permissions or flags) part of the values in $\setv$.
-
-The nodes form a disjoint union of rooted directed trees.
-\begin{mydef}
-The function $\parent(n)$ returns the parent node of $n$, or
-returns $\topnode$ if $n$ is the root of a tree.
-\end{mydef}
-
-Every filesystem has a so-called \textbf{tree property}, which means that
-if the filesystem is not empty at a node, and the node has a parent,
-then there must be a directory at the parent node.
-
-To model this, in $\setv$ we distinguish between files ($\setf$) and directories ($\setd$), that is,
-if $\setb = \{\empt\}$ then:
-\[ \setv = \setb \cup \setf \cup \setd \]
-The tree propety can then be defined as
-\begin{align*}
-\forall n\in\setn: &\FS(n) \neq \empt \\ % TODO alignment problem
-&\quad\wedge \parent(n) \neq \topnode \\
-&\Rightarrow \FS(\parent(n)) \in \setd 
-\end{align*}
-This means that as we move down from the root of a tree of nodes,
-the types of values we encounter in the filesystem can only change according to the following
-transition diagram:
-
-\input{type-transition}
-
-In this paper, 
-we write $n$ and $m$ for nodes in $\setn$,
-and use lowercase Greek letters to denote commands. % TODO but very rarely
-We use $\valf$ for an arbitrary element of $\setf$, and $\vald$ for an arbitrary element
-of $\setd$. $TODO$ is a value from $\setv$ .
-
-\section{Introducing commands}
-
-Next we need to define commands on the filesystem.
+\section{Definitions}
+\input{def-filesystem}
+\input{def-commands}
+
+\input{axioms}
 
@@
 % >>>>>>>>>> to here
-
-...
-
-Let us consider what kind of information may be encoded in the commands.
-A usual set of commands, based on the most frequent tools implemented by filesystems,
-might be $create(n,V)$, $edit(n,V)$ and $remove(n)$ where $n\in\setn$ and $V\in\setv$ (but $V\neq\empt$).
-Regarding their output, that is, the state of the filesystem at $n$
-after applying the command,
-we know that after $create$ or $edit$, $\FS(n)\neq\empt$, whereas after $remove$,
-$\FS(n)$ will be $\empt$. 
-However, from \cite{NREC:alg} we know that a useful set of axioms
-will in some cases need to distinguish between edits that result in directories ($edit(n,D)$) and
-ones that result in files ($edit(n,F)$), and treat them as separate commands.
-Indeed, Bill Zissimopoulos suggested (\cite{BZ}) that extending this distinction to more commands
-utlimately simplifies
-the definition of conflicting commands, as our model will then able to predict the behavior of commands
-more precisely.
-In other words, encoding the type of the output ($D$, $F$ or $\empt$) in the commands is definitely useful.
-At the same time, there is never any need to encode information about the
-\emph{exact} output value of a command,
-as the success or failure of filesystem commands only depend on the types of values in the filesystem.
-
-Notice, however, that the commands listed above also encode some information about 
-their input, the filesystem
-\emph{before} the command is applied; namely, $create(n,V)$ requires that there are no files
-or directories at $n$, while $edit(n,V)$ and $remove(n)$ require the opposite.
-This creates an arbitrary asymmetry where
-there is now more information encoded into commands about their output than about their input.
-In line with the aim to encode as much information as possible in the commands, % TODO Where is this mentioned?
-and in order to resolve this asymmetry, we propose a set of commands that encode
-the type of the original state of $\FS(n)$ as well.
-(Some real-life filesystem commands like $rmdir$ do this already.)
-
-% TODO: tuple / quadruple
-We therefore propose to have a command for each pair of types.
-For want of a better system, we will name our commands by concatenating
-two of $\cchard$, $\ccharf$ and $\ccharb$, 
-where the left sign denotes the type of value
-required in the filesystem before the command is applied, and the right sign notes the type
-afterwards. For example, $mkdir(n,D)$ is $\cbdaa{n}{D}$, and $rmdir(n)$ is $\cdba{n}$.
-
-A command can only succeed if the original value at node $n$ has a type that matches
-the input type of the command. If this is not the case, or if the resulting
-filesystem no longer has the tree property, then we say that the command
-{\em breaks} the filesystem. Broken filesystems are considered equal
-(but not equal to any working filesystem), and we note them by $\FS=\fsbroken$.
-
-So that we could reason about sequences of commands that break every filesystem
-in the algebra, we introduce the command $\cbrk$ that simply breaks every filesystem.
-
-We note that a command or a sequence of commands is applied to a filsystem
-by prefixing the command or sequence to it, for example: $\cbrk\FS$, $\cbdaa{n}{\vald}\FS$, 
-or $S\FS$ if $S$ is a sequence of commands.
-
-\begin{mydef}
-Using $\FS[V/n]$ we denote a filesystem derived from $\FS$:
-\[ \FS[V/n](m) :=
-   \begin{cases}
-   V &\mbox{if~} m=n\\
-   \FS(m) &\mbox{otherwise.}
-   \end{cases}
-\]
-\end{mydef}
-
-The exact behavior of our commands is as follows:
-\begin{itemize}
-\item $\cbrk\FS = \fsbroken$
-\item
-All other commands have the generic form $\cxynv$ where
-$X$ and $Y$ are types in $\typeset$,
-$n\in\setn$ and $\valvy$ is a value of the appropriate type from $\setvx{Y}$.
-At times we omit $\valvy$ if there is only one suitable value.
-\[ \cxynv\FS = 
-   \begin{cases}
-   \fsbroken &\mbox{if~} \FS=\fsbroken\\
-   \fsbroken &\mbox{if~} \FS(n)\not\in\setvx{X}\\
-   \fsbroken &\mbox{if~} \FS[V/n] \mbox{~violates the tree property}\\
-   \FS[V/n] &\mbox{otherwise.}
-   \end{cases}
-\]
-\end{itemize}
-
-In general, when we describe multiple or unknown commands, we may substitute one or both
-of their types with variables, as we did with $\cxynv$. In this context,
-if we write that $\cxy=\czw$, we mean that the input and output types % TODO needed?
-of the commands are the same ($X=Z$ and $Y=W$), while a full equiality 
-($\cxynv=\czwmv$)
-implies
-that their output value is also the same.
-
-% Simplifications
-% ---------------
-
-For reasons also listed in \cite{NREC:alg}, in this paper we will not consider
-a $move$ or $rename$ command. Regarding the theoretical reasoning we aim to follow,
-this turns out to be useful because these would be the only commands that affect
-filesystems at two nodes at once, therefore describing 
-the dependencies affecting these commands
-would call for a more complicated model.
-From a pragmatic perspective, this restriction does not mean that in an application
-implementing conflict resolution using the algorithm described here would not be
-able to handle renames by pre- and post-processing changes in the filesystem to
-discover them, which (especially when a rename is combined with changes to the content)
-is a non-trivial problem in itself.
-
-Another simplification we will assume in this paper is regarding directories.
-As Bill Zissimopoulos pointed out (\cite{BZ}), we often do not want to consider metadata stored in
-directories during synchronization. In other words, the contents of directories are all equal,
-which can be modelled by assuming that $|\setd|=1$.
-% This also creates a convenient symmetry where there is only a single value
-% for each type that can be repeated as we move from a path to its child ($D$ and $\empt$).
-
-\section{Describing the behavior of commands}
-
-% Definitions for command pairs and ordering
-% ------------------------------------------
-
-So that we could describe the effects of commands on a filesystem, let us introduce some notation
-and note some observations.
-
-The commands we aim to investigate do not occur in isolation:
-for example, when comparing filesystems to determine the commands needed to transform one into the other,
-we receive a set of commands with uncertain ordering.
-Applying commands to a filesystem, however, happens in time,
-so for this we need a sequence of commands.
-We use $\cc$ to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence:
-$S=\cbdaa{n}{\vald}\cc\cbfaa{m}{\valf}$, or $S'=S\cc\cbba{o}$.
-We write $\emptyseq$ for the empty sequence.
-
-TODO: Sequences of commands, in the usual way,  form a free
-semigroup
-
-The following concepts allow us to investigate sequences independently of filesystems.
-In the definitions, $A,B,S,T$ stand for arbitrary sequences of commands.
-These relations echo the ones defined in \cite{NREC:alg}.
-
-\begin{mydef}
-% Relation in the algebra
-$A\equiv B$ means that $A$ and $B$ are equivalent,
-% intended interpretation:
-that is, they behave in the same way on
-all filesystems: $\forall \FS: A\FS=B\FS$.
-It is a reflexive, commutative and transitive relation,
-and clearly
-% inference rule:
-$ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.
-\end{mydef}
-
-\begin{mydef}
-% Relation in the algebra
-$A\eqext B$ means that $B$ extends $A$,
-% intended interpretation:
-that is, they behave in the same way
-on any filesystem $A$ does not break:
-$\forall \FS: A\FS\neq\fsbroken\Rightarrow A\FS=B\FS$.
-It is a reflexive and transitive relation,
-and we can see that
-% inference rules:
-$ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$
-and
-$ A\equiv B \Rightarrow A\eqext B$.
-\end{mydef}
-
-Let us also define the following relations between nodes:
-
-\begin{mydef}{$n\descendant m$.}
-We write $n\descendant m$ if $n$ is the ancestor of $m$ ($n=\parent^n(m)$). % TODO (the transitive closure of the $\parent$ relation)
-We write $n\descendantEq m$ if $n\descendant m$ or $n=m$.
-\end{mydef}
-
-\begin{mydef}{$n\unrel m$.}
-We write $n\unrel m$, or ``$n$ and $m$ are unrelated'' if $n\not\descendantEq m$ and $n\not\ancestorEq m$.
-\end{mydef}
-
-% Command pairs - Axioms
-% ----------------------
-
-\section{Investigating command pairs}\label{section_axioms}
-
-Our aim is to derive information about the effects of sequences
-of commands independently of that actual filesystems.
-In order to make this possible, we investigate the smallest building
-blocks of sequences: pairs of commands that act on a filesystem directly one after the other.
-This approach is useful as there are a limited number of command pairs,
-because, as we argued above, we can disregard the exact output values of commands apart from their type,
-and we can also abstract the relationship between the nodes in the two commands
-to a finite number of cases.
-
-We methodically investigated of all possibilities using a computer program
-to determine
-which pairs of commands cause errors all the time,
-which can be simplified to one or no commands, and which can be reversed
-without any change in their overall effect.
-% TODO: Footnote: URL
-Our basis for this investigation was the model of filesystems introduced in this paper.
-These properties of command pairs are crucial as they determine
-how a set of commands can be re-ordered to be applied to a filesystem
-during synchronization, and what commands will never be compatible.
-
-Below we list a number of statements derived using this method.
-Although they can be proven by investigating all relevant possibilities
-in a filesystem, we refer to these as axioms because in a secondary algebraic model
-that describes commands without reference to an underlying filesystem,
-these would function as meta-rules generating statements we would accept as true.
-See section (TODO) for more about such a model.
-
-\medskip
-
-Pairs of commands in general have the form
-\[ \cxynv\cc  \czwmv \]
-where $X,Y,Z,W\in\typeset$, $n,m\in\setn$, 
-and values are of the appropriate type: 
-$\valvy\in\setvx{Y}$ and $\valvw\in\setvx{W}$.
-
-\begin{myax}\label{ax_separate_commute}
-Commands on unrelated nodes commute:
-$\cxynv\cc\czwmv \equiv \czwmv\cc\cxynv$ where $n\unrel m$.
-\end{myax}
-
-\begin{myax}\label{ax_separate_nobreaks}
-Commands on unrelated nodes do not break every filesystem:
-$\cxynv\cc\czwmv \nequiv \cbrk$ where $n\unrel m$.
-\end{myax}
-
-\begin{myax}\label{ax_same_breaks}
-Commands on the same node break every filesystem if their types are incompatible:
-$\cxynv\cc\czwnv \equiv \cbrk$ where $Y\ne Z$.
-\end{myax}
-
-\begin{myax}\label{ax_same_emptyseq}
-Commands on the same node simplify:
-$\cxynv\cc\czwnv \eqext \emptyseq$ where $Y=Z$ and $X=W=\ccharb$ 
-or $X=W=\cchard$.
-\end{myax}
-
-\begin{myax}\label{ax_same_singlec}
-Commands on the same node simplify:
-$\cxynv\cc \czwnv \equiv \cxwnv$ where $Y=Z$ and $\cxw\neq\cbb$ and $\cxw\neq\cdd$.
-\end{myax}
-
-\begin{myax}\label{ax_distantrel_breaks}
-Commands on distant relatives break all filesystems:
-$\cxynnv\cc\czwnv \equiv \cbrk$
-and $\czwnv\cc\cxynnv \equiv\cbrk$
-where $\nn\descendant n$ and $\nn\neq\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
-\end{myax}
-
-\begin{mydef}{Construction pair.}
-A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parent(n)$ 
-and the commands are one
-of the following:
-   \begin{gather*}
-   % bd>bf
-            \cbdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
-   % bd>bd
-            \cbdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii} \\
-   % fd>bf
-            \cfdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
-   % fd>bd
-            \cfdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii}
-   \end{gather*}
-\end{mydef}
-
-\begin{myax}\label{ax_directchild_breaks}
-All other commands on a child break every filesystem:
-$\cxynnv\cc\czwnv \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
-and the pair is not a construction pair.
-\end{myax}
-
-\begin{mydef}{Destruction pair.}
-A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parent(n)=\nn$ and the commands are one
-of the following:
-   \begin{gather*}
-   % fb<db ??
-            \cfba{n}\cc  \cdba{\nn} \\
-   % fb<df ??
-            \cfba{n}\cc  \cdfaa{\nn}{\valf} \\
-   % db<db ??
-            \cdba{n}\cc  \cdba{\nn} \\
-   % db<df ??
-            \cdba{n}\cc  \cdfaa{\nn}{\valf}
-   \end{gather*}
-\end{mydef}
-
-\begin{myax}\label{ax_directparent_breaks}
-All other commands on a parent break every filsystem:
-$\cxynv\cc\czwnnv \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
-and the pair is not a destruction pair.
-\end{myax}
-
-\begin{mydef}{Assertion command.}
-A command is an assertion command if
-for every filesystem it either breaks it or leaves it in the same state.
-In other words, assertion commands have the same input and output type,
-and there must also be only one possible value for their output.
-Accordingly, in our current algebra, $\cbba{n}$ and $\cdda{n}$ are the only two assertion commands,
-and we do not note their output value as it is determined.
-\end{mydef}
-
-\begin{myax}\label{ax_child_assert}
-An assertion command can be added on a descendant node:
-$\cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n}$ 
-where $\nn\descendant n$ and $\cxy\neq\cdd$.
-\end{myax}
-
-\begin{myax}\label{ax_parent_assert}
-An assertion command can be added on an ancestor node:
-$\cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn}$ 
-where $\nn\descendant n$ and $\cxy\neq\cbb$.
-\end{myax}
-
-\begin{myax}\label{ax_assert}
-Assertion commands can be removed:
-$\cxynv \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
-\end{myax}
 
@@
 
-% Works
-% -----
-
-\begin{mydef}
-% Unsure if this relation should be in the algebra.
-For a set of $k$ sequences
-$\works{A_1,A_2,\ldots,A_k}$ means that 
-$A_1,A_2,\ldots,A_k$ work at the same time, that is,
-% intended interpretation:
-\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_k\FS\neq\fsbroken\]
-As the sequences form a set, their order is irrelevant.
-% inference rules:
-We also know that $\works{A} \Leftrightarrow A\nequiv \cbrk$. 
-\end{mydef}
-
-\begin{mydef}
-For two sets of sequences, $\worksc{A_1,A_2,\ldots,A_k}{B_1,B_2,\ldots,B_l}$ means that 
-all of $A_1,\ldots,A_k$ work where all of $B_1,\ldots,B_l$ work,
-that is,
-% intended interpretation:
-\begin{align*}
-\forall \FS:&\\ 
-&B_1\FS\neq\fsbroken \wedge \cdots \wedge B_k\FS\neq\fsbroken\\
-&\Rightarrow\\
-&A_1\FS\neq\fsbroken \wedge \cdots \wedge A_l\FS\neq\fsbroken
-\end{align*}
-As above, the order of the sequences in the sets is not relevant.
-\end{mydef}
-
-\begin{mydef}{Sets of sequences.}
-For brevity, we will use $\seqset{S}$ to note an arbitrary set of sequences,
-and $A\cc\seqset{S}$ to note the set of sequences $\{A\cc S|S\in\seqset{S}\}$.
-\end{mydef}
-
-It is easy to see that the following corollaries are true:
-
-% An inference rule in the algebra
-% $\worksc{X}{X}$ is always true for any set of sequences $X$,
-
-\begin{mycor}
-% An inference rule in the algebra
-$B\eqext A \Rightarrow \worksc{A}{B}$.
-\end{mycor}
-
-\begin{mycor}\label{worksextpostfix}
-% An inference rule in the algebra
-$\forall A,S: \worksc{A}{A\cc S}$, that is, if a sequence works, its prefix also works.
-\end{mycor}
-
-\begin{mycor}\label{workschained}
-% An inference rule in the algebra
-$\workssign$ can be chained:
-if $\seqset{A'}\subset\seqset{A}$, then
-$ \worksc{\seqset{C}}{\seqset{A'}} \wedge \worksc{\seqset{A}}{\seqset{B}} \Rightarrow \worksc{\seqset{A}\cup\seqset{C}}{\seqset{B}}$.
-\end{mycor}
-
-We also prove the following lemmas.
-
-\begin{mylem}\label{unrelated_is_independent}
-Two different commands that are not assertion commands are independent iff the nodes they change are unrelated:
-\[ \cxynv\indep\czwmv \Leftrightarrow n\unrel m \]
-if $\cxynv\neq\czwmv$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
-\end{mylem}
-\begin{proof}
-This is easy to show based on the output of the software that investigates the behavior of command pairs,
-and which we used to derive the \namecrefs{ax_separate_commute} in \cref{section_axioms}.
-However, this proposition can also be derived from the \namecrefs{ax_separate_commute} already listed
-in the following way.
-
-We proceed in two steps. First, we note that
-from \cref{ax_separate_commute,ax_separate_nobreaks} we know that
-if $n\unrel m$, then $\cxynv$ and $\czwmv$ must necessarily be independent, and therefore
-$ \cxynv\nindep\czwmv \wedge n\unrel m $ cannot be the case.
-
-Next, we prove that
-\[ \cxynv\indep\czwmv \wedge n\nunrel m \] is also impossible as it would lead to contradiction.
-As $n\nunrel m$
-we know that $n=m$, $n\descendant m$ or $m\descendant n$.
-
-If $n=m$, then from \cref{ax_same_breaks} we know $Y=Z$ and $W=X$
-as otherwise the commands, in one order or the other, would break all filesystems
-and they could not be independent.
-The commands are not assertion commands, and so from \cref{ax_same_singlec}
-we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $Y=W$ and $\valvy=\valvw$.
-Therefore $X=Y=Z=W$ which is only possible if both commands are $\cff$ and have the same
-output value. This, however, contradicts our assumption that they are different.
-
-If $n\descendant m$ or $m\descendant n$, then
-from \cref{ax_distantrel_breaks} we know that if they are not directly related,
-then $\cxynv\cc\czwmv$ breaks all filesystems, and they cannot be independent.
-From the construction and destruction pairs and 
-\cref{ax_directchild_breaks,ax_directparent_breaks} we also see that
-even if they are directly related, either
-$\cxynv\cc\czwmv$ or $\czwmv\cc\cxynv$ 
-breaks all filesystems, so they again cannot be independent.
-\end{proof}
-
-\begin{myax}\label{combine_independent_commands}
-The combination of independent commands works wherever the original commands work:
-\begin{align*}
-\forall\FS: &\cxynv\indep \czwmv \\
-&\quad\wedge \cxynv\FS\neq\fsbroken \\
-&\quad\wedge \czwmv\FS\neq\fsbroken \\
-&\Rightarrow \cxynv\cc \czwmv\FS\neq\fsbroken.
-\end{align*}
-\end{myax}
-\begin{proof}
-We name this proposition an axiom for the same reason as above,
-but it is easy to provide an indirect proof based on our filesystem model.
-Assume that $\cxynv\cc \czwmv\FS=\fsbroken$.
-We know $\cxynv\FS\neq\fsbroken$ so it must be applying 
-$\czwmv$ that breaks it.
-Applying a command can only result in a broken filesystem in three cases.
-First, if the filesystem was already broken, which cannot be the case here.
-Second, if the input type does not match the filesystem,
-but we know $\FS(m)\in\setvx{W}$ and so
-$(\cxynv\FS)(m)\in\setvx{W}$ as based on \cref{unrelated_is_independent}, $n\neq m$.
-Third, if the new filesystem violates the tree property.
-This again cannot be the case because we also know that $n\unrel m$
-and the tree property only depends on the types of the parent and children of $m$,
-which therefore cannot be changed by $\cxynv$.
-\end{proof}
-
-This result can be extended to sequences:
-
-\begin{mylem}\label{combine_independent_sequences}
-The combination of independent sequences works wherever the original sequences work:
-\[ S\indep T \Rightarrow \worksc{S\cc T}{S,T}. \]
-\end{mylem}
-\begin{proof}
-Assume that there is a filesystem $\FS$ so that
-$S\FS\neq\fsbroken$ and $T\FS\neq\fsbroken$, but
-$(S\cc T)\FS=\fsbroken$.
-
-From \cref{unrelated_is_independent,ax_separate_commute} we know that
-the commands in $S$ and $T$ pairwise commute, and so any sequence
-that contains the commands from $S$ and $T$ and preserve their original partial order
-is equivalent to $S\cc T$ on all filesystems.
-
-Let the command that breaks $\FS$ in $T$ when applying $S\cc T$ be $t$
-so that $T=T_0\cc t\cc T_1$.
-It is still true that $(T_0 \cc t)\FS\neq\fsbroken$,
-and by definition $(S\cc T_0)\FS\neq\fsbroken$,
-but $(S\cc T_0\cc t)\FS=\fsbroken$.
-Also, from above we know that $S\cc T_0\equiv T_0\cc S$
-and so $(T_0 \cc S)\FS\neq\fsbroken$.
-
-If we denote the first command in $S$ with $s_1$,
-this means that $(T_0 \cc s_1)\FS\neq\fsbroken$,
-which we can combine with $(T_0 \cc t)\FS\neq\fsbroken$, $t\indep s_1$ and
-\cref{combine_independent_commands}
-(using $T_0\FS$ as the reference filesystem)
-to arrive at $(T_0 \cc s_1\cc t)\FS\neq\fsbroken$.
-
-We can repeat this step for $s_2$, the next command in $S$,
-and from 
-$(T_0 \cc s_1\cc t)\FS\neq\fsbroken$
-and
-$(T_0 \cc s_1\cc s_2)\FS\neq\fsbroken$
-arrive at
-$(T_0 \cc s_1\cc s_2\cc t)\FS\neq\fsbroken$.
-This can be repeated until $S$ is exhausted and we get
-$(T_0 \cc S\cc t)\FS\neq\fsbroken$, which is a contradiction.
-\end{proof}
-
-Separately, we prove the following:
-
-\begin{mylem}\label{worksinputmatch}
-If $A$ and $B$ are minimal sequences, $\works{A,B}$,
-and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$)
-then their input types must match ($X=Z$).
-\end{mylem}
-\begin{proof}
-This is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
-either $\cxynv$ or $\czwnv$ would not break, 
-and consequently $A$ and $B$ cannot work on the same filesystem.
-\end{proof}
-
-\medskip
-
-We continue by defining inverse commands and sequences
-which allow us to move parts of sequences between the
-condition and consequence parts of $\workssign$.
-
-\begin{mydef}{Inverse commands and sequences.}
-The inverse of command $\cxynv$ is $\cxynv^{-1} = \caaaa{Y}{X}{n}{\valvx}$
-where $V_X$ is an arbitrary value from $\setvx{X}$.
-We write $S^{-1}$ for the inverse of sequence $S$, which consists of the inverses of the commands in $S$
-in reverse order.
-\end{mydef}
-
-\begin{mydef}{$\typeeq$.}
-For two filesystems we write $\FS\typeeq\GS$
-iff 
-at all nodes the types of their values are the same, or they are both broken.
-\end{mydef}
-
-From the definitions we can clearly see that
-\begin{mycor}\label{negneg_is_typeeq}
-$\forall \FS: (S^{-1})^{-1}\FS\typeeq \FS$.
-\end{mycor}
-
-\begin{mylem}\label{r_invmove}
-A common prefix of sequences can be moved to the other side of $\workssign$ by inverting it:
-\begin{gather*}
-\worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \\
-\worksc{\seqset{A}}{B\cc \seqset{S}} \Rightarrow \worksc{B^{-1}\cc \seqset{A}}{\seqset{S}}
-\end{gather*}
-\end{mylem}
-\begin{proof}
-This is based on the fact that in our model, unless they break a filesystem,
-commands change one type of value into another, but never merge types.
-That is,
-sequences---as functions mapping filesystems to filesystems---are
-essentially bijections over type-equality
-with the only ``sink'' being $\fsbroken$:
-\begin{align*}
-\forall S,\FS,\GS: &S\FS\neq\fsbroken \Rightarrow \\
-&(S\FS\ntypeeq S\GS \Leftrightarrow \FS\ntypeeq \GS).
-\end{align*}
-
-For the proposition
-\[ \worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \]
-the rest of the proof is illustrated by the diagram below
-where Dom($x$), the domain of $x$, represents the set of filesystems
-the sequence $x$ does not break, or neither of the sequences in the set $x$ breaks.
-
-\input{inverse-works} % TODO arrows too small
-
-We see that the set of filesystems the sequences in $\seqset{A}$ do not break intersect with the range of $B$.
-As $B$ is a bijection between its domain and range, we can use $B^{-1}$ to map this intersection back
-onto the domain of $B$.
-As $\worksc{B\cc \seqset{A}}{\seqset{S}}$ the domain of $\seqset{S}$ must be a subset of this
-projected intersection.
-If so, then we can use $B$ to map the domain of $\seqset{S}$, which yields the domain of $B^{-1}\cc \seqset{S}$.
-As it is also a part of the domain of $A$, we get $\worksc{\seqset{A}}{B^{-1}\cc \seqset{S}}$.
-
-The second part of the lemma can be proven in a similar way.
-\end{proof}
-
-\begin{mylem}\label{indep_prefix_combine}
-The combination of sequences with a common head and independent tails 
-continues to work under the same conditions:
-\[ \worksc{A\cc B}{\seqset{S}} \wedge \worksc{A\cc C}{\seqset{S}} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{\seqset{S}} \]
-\end{mylem}
-\begin{proof}
-Based on \cref{r_invmove} we know
-$\worksc{B}{A^{-1}\cc \seqset{S}}$ and $\worksc{C}{A^{-1}\cc \seqset{S}}$,
-and from \cref{combine_independent_sequences} we know
-$\worksc{B\cc C}{B,C}$.
-Combining these using \cref{workschained}
-we get
-$\worksc{B\cc C}{A^{-1}\cc \seqset{S}}$. 
-Finally, applying the second line of \cref{r_invmove} yields
-$\worksc{(A^{-1})^{-1}\cc B\cc C}{\seqset{S}}$, which proves our lemma 
-as $\forall\FS: (A^{-1})^{-1}\FS\typeeq A\FS$ (\cref{negneg_is_typeeq}).
-\end{proof}
+\input{works-inverse}
 

### 2015-12-04 2015/works-inverse.tex
Split source into sections

% Works
% -----

\begin{mydef}
% Unsure if this relation should be in the algebra.
For a set of $k$ sequences
$\works{A_1,A_2,\ldots,A_k}$ means that 
$A_1,A_2,\ldots,A_k$ work at the same time, that is,
% intended interpretation:
\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_k\FS\neq\fsbroken\]
As the sequences form a set, their order is irrelevant.
% inference rules:
We also know that $\works{A} \Leftrightarrow A\nequiv \cbrk$. 
\end{mydef}

\begin{mydef}
For two sets of sequences, $\worksc{A_1,A_2,\ldots,A_k}{B_1,B_2,\ldots,B_l}$ means that 
all of $A_1,\ldots,A_k$ work where all of $B_1,\ldots,B_l$ work,
that is,
% intended interpretation:
\begin{align*}
\forall \FS:&\\ 
&B_1\FS\neq\fsbroken \wedge \cdots \wedge B_k\FS\neq\fsbroken\\
&\Rightarrow\\
&A_1\FS\neq\fsbroken \wedge \cdots \wedge A_l\FS\neq\fsbroken
\end{align*}
As above, the order of the sequences in the sets is not relevant.
\end{mydef}

\begin{mydef}{Sets of sequences.}
For brevity, we will use $\seqset{S}$ to note an arbitrary set of sequences,
and $A\cc\seqset{S}$ to note the set of sequences $\{A\cc S|S\in\seqset{S}\}$.
\end{mydef}

It is easy to see that the following corollaries are true:

% An inference rule in the algebra
% $\worksc{X}{X}$ is always true for any set of sequences $X$,

\begin{mycor}
% An inference rule in the algebra
$B\eqext A \Rightarrow \worksc{A}{B}$.
\end{mycor}

\begin{mycor}\label{worksextpostfix}
% An inference rule in the algebra
$\forall A,S: \worksc{A}{A\cc S}$, that is, if a sequence works, its prefix also works.
\end{mycor}

\begin{mycor}\label{workschained}
% An inference rule in the algebra
$\workssign$ can be chained:
if $\seqset{A'}\subset\seqset{A}$, then
$ \worksc{\seqset{C}}{\seqset{A'}} \wedge \worksc{\seqset{A}}{\seqset{B}} \Rightarrow \worksc{\seqset{A}\cup\seqset{C}}{\seqset{B}}$.
\end{mycor}

We also prove the following lemmas.

\begin{mylem}\label{unrelated_is_independent}
Two different commands that are not assertion commands are independent iff the nodes they change are unrelated:
\[ \cxynv\indep\czwmv \Leftrightarrow n\unrel m \]
if $\cxynv\neq\czwmv$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
\end{mylem}
\begin{proof}
This is easy to show based on the output of the software that investigates the behavior of command pairs,
and which we used to derive the \namecrefs{ax_separate_commute} in \cref{section_axioms}.
However, this proposition can also be derived from the \namecrefs{ax_separate_commute} already listed
in the following way.

We proceed in two steps. First, we note that
from \cref{ax_separate_commute,ax_separate_nobreaks} we know that
if $n\unrel m$, then $\cxynv$ and $\czwmv$ must necessarily be independent, and therefore
$ \cxynv\nindep\czwmv \wedge n\unrel m $ cannot be the case.

Next, we prove that
\[ \cxynv\indep\czwmv \wedge n\nunrel m \] is also impossible as it would lead to contradiction.
As $n\nunrel m$
we know that $n=m$, $n\descendant m$ or $m\descendant n$.

If $n=m$, then from \cref{ax_same_breaks} we know $Y=Z$ and $W=X$
as otherwise the commands, in one order or the other, would break all filesystems
and they could not be independent.
The commands are not assertion commands, and so from \cref{ax_same_singlec}
we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $Y=W$ and $\valvy=\valvw$.
Therefore $X=Y=Z=W$ which is only possible if both commands are $\cff$ and have the same
output value. This, however, contradicts our assumption that they are different.

If $n\descendant m$ or $m\descendant n$, then
from \cref{ax_distantrel_breaks} we know that if they are not directly related,
then $\cxynv\cc\czwmv$ breaks all filesystems, and they cannot be independent.
From the construction and destruction pairs and 
\cref{ax_directchild_breaks,ax_directparent_breaks} we also see that
even if they are directly related, either
$\cxynv\cc\czwmv$ or $\czwmv\cc\cxynv$ 
breaks all filesystems, so they again cannot be independent.
\end{proof}

\begin{myax}\label{combine_independent_commands}
The combination of independent commands works wherever the original commands work:
\begin{align*}
\forall\FS: &\cxynv\indep \czwmv \\
&\quad\wedge \cxynv\FS\neq\fsbroken \\
&\quad\wedge \czwmv\FS\neq\fsbroken \\
&\Rightarrow \cxynv\cc \czwmv\FS\neq\fsbroken.
\end{align*}
\end{myax}
\begin{proof}
We name this proposition an axiom (TODO) for the same reason as above,
but it is easy to provide an indirect proof based on our filesystem model.
Assume that $\cxynv\cc \czwmv\FS=\fsbroken$.
We know $\cxynv\FS\neq\fsbroken$ so it must be applying 
$\czwmv$ that breaks it.
Applying a command can only result in a broken filesystem in three cases.
First, if the filesystem was already broken, which cannot be the case here.
Second, if the input type does not match the filesystem,
but we know $\FS(m)\in\setvx{W}$ and so
$(\cxynv\FS)(m)\in\setvx{W}$ as based on \cref{unrelated_is_independent}, $n\neq m$.
Third, if the new filesystem violates the tree property.
This again cannot be the case because we also know that $n\unrel m$
and the tree property only depends on the types of the parent and children of $m$,
which therefore cannot be changed by $\cxynv$.
\end{proof}

This result can be extended to sequences:

\begin{mylem}\label{combine_independent_sequences}
The combination of independent sequences works wherever the original sequences work:
\[ S\indep T \Rightarrow \worksc{S\cc T}{S,T}. \]
\end{mylem}
\begin{proof}
Assume that there is a filesystem $\FS$ so that
$S\FS\neq\fsbroken$ and $T\FS\neq\fsbroken$, but
$(S\cc T)\FS=\fsbroken$.

From \cref{unrelated_is_independent,ax_separate_commute} we know that
the commands in $S$ and $T$ pairwise commute, and so any sequence
that contains the commands from $S$ and $T$ and preserve their original partial order
is equivalent to $S\cc T$ on all filesystems.

Let the command that breaks $\FS$ in $T$ when applying $S\cc T$ be $t$
so that $T=T_0\cc t\cc T_1$.
It is still true that $(T_0 \cc t)\FS\neq\fsbroken$,
and by definition $(S\cc T_0)\FS\neq\fsbroken$,
but $(S\cc T_0\cc t)\FS=\fsbroken$.
Also, from above we know that $S\cc T_0\equiv T_0\cc S$
and so $(T_0 \cc S)\FS\neq\fsbroken$.

If we denote the first command in $S$ with $s_1$,
this means that $(T_0 \cc s_1)\FS\neq\fsbroken$,
which we can combine with $(T_0 \cc t)\FS\neq\fsbroken$, $t\indep s_1$ and
\cref{combine_independent_commands}
(using $T_0\FS$ as the reference filesystem)
to arrive at $(T_0 \cc s_1\cc t)\FS\neq\fsbroken$.

We can repeat this step for $s_2$, the next command in $S$,
and from 
$(T_0 \cc s_1\cc t)\FS\neq\fsbroken$
and
$(T_0 \cc s_1\cc s_2)\FS\neq\fsbroken$
arrive at
$(T_0 \cc s_1\cc s_2\cc t)\FS\neq\fsbroken$.
This can be repeated until $S$ is exhausted and we get
$(T_0 \cc S\cc t)\FS\neq\fsbroken$, which is a contradiction.
\end{proof}

Separately, we prove the following:

\begin{mylem}\label{worksinputmatch}
If $A$ and $B$ are minimal sequences, $\works{A,B}$,
and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$)
then their input types must match ($X=Z$).
\end{mylem}
\begin{proof}
This is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
either $\cxynv$ or $\czwnv$ would not break, 
and consequently $A$ and $B$ cannot work on the same filesystem.
\end{proof}

\medskip

We continue by defining inverse commands and sequences
which allow us to move parts of sequences between the
condition and consequence parts of $\workssign$.

\begin{mydef}{Inverse commands and sequences.}
The inverse of command $\cxynv$ is $\cxynv^{-1} = \caaaa{Y}{X}{n}{\valvx}$
where $V_X$ is an arbitrary value from $\setvx{X}$.
We write $S^{-1}$ for the inverse of sequence $S$, which consists of the inverses of the commands in $S$
in reverse order.
\end{mydef}

\begin{mydef}{$\typeeq$.}
For two filesystems we write $\FS\typeeq\GS$
iff 
at all nodes the types of their values are the same, or they are both broken.
\end{mydef}

From the definitions we can clearly see that
\begin{mycor}\label{negneg_is_typeeq}
$\forall \FS: (S^{-1})^{-1}\FS\typeeq \FS$.
\end{mycor}

\begin{mylem}\label{r_invmove}
A common prefix of sequences can be moved to the other side of $\workssign$ by inverting it:
\begin{gather*}
\worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \\
\worksc{\seqset{A}}{B\cc \seqset{S}} \Rightarrow \worksc{B^{-1}\cc \seqset{A}}{\seqset{S}}
\end{gather*}
\end{mylem}
\begin{proof}
This is based on the fact that in our model, unless they break a filesystem,
commands change one type of value into another, but never merge types.
That is,
sequences---as functions mapping filesystems to filesystems---are
essentially bijections over type-equality
with the only ``sink'' being $\fsbroken$:
\begin{align*}
\forall S,\FS,\GS: &S\FS\neq\fsbroken \Rightarrow \\
&(S\FS\ntypeeq S\GS \Leftrightarrow \FS\ntypeeq \GS).
\end{align*}

For the proposition
\[ \worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \]
the rest of the proof is illustrated by the diagram below
where Dom($x$), the domain of $x$, represents the set of filesystems
the sequence $x$ does not break, or neither of the sequences in the set $x$ breaks.

\input{inverse-works} % TODO arrows too small

We see that the set of filesystems the sequences in $\seqset{A}$ do not break intersect with the range of $B$.
As $B$ is a bijection between its domain and range, we can use $B^{-1}$ to map this intersection back
onto the domain of $B$.
As $\worksc{B\cc \seqset{A}}{\seqset{S}}$ the domain of $\seqset{S}$ must be a subset of this
projected intersection.
If so, then we can use $B$ to map the domain of $\seqset{S}$, which yields the domain of $B^{-1}\cc \seqset{S}$.
As it is also a part of the domain of $A$, we get $\worksc{\seqset{A}}{B^{-1}\cc \seqset{S}}$.

The second part of the lemma can be proven in a similar way.
\end{proof}

\begin{mylem}\label{indep_prefix_combine}
The combination of sequences with a common head and independent tails 
continues to work under the same conditions:
\[ \worksc{A\cc B}{\seqset{S}} \wedge \worksc{A\cc C}{\seqset{S}} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{\seqset{S}} \]
\end{mylem}
\begin{proof}
Based on \cref{r_invmove} we know
$\worksc{B}{A^{-1}\cc \seqset{S}}$ and $\worksc{C}{A^{-1}\cc \seqset{S}}$,
and from \cref{combine_independent_sequences} we know
$\worksc{B\cc C}{B,C}$.
Combining these using \cref{workschained}
we get
$\worksc{B\cc C}{A^{-1}\cc \seqset{S}}$. 
Finally, applying the second line of \cref{r_invmove} yields
$\worksc{(A^{-1})^{-1}\cc B\cc C}{\seqset{S}}$, which proves our lemma 
as $\forall\FS: (A^{-1})^{-1}\FS\typeeq A\FS$ (\cref{negneg_is_typeeq}).
\end{proof}

### 2015-12-06 2015/ordering.tex
Split paper into sections

--- 2015-12-04 2015/paper.tex
@@
-\documentclass[12pt]{article}
-
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{centernot}
-\usepackage{tikz}
-\usepackage{cleveref}
-
-\input{macros}
-
-\title{Complete Algebraic File Synchronization}
-\author{Elod Pal Csirmaz}
-
-\begin{document}
-\maketitle
-\begin{abstract}
-Abstract goes here
-\end{abstract}
-
-\section{Introduction}
-
-% TODO Thank-you Laszlo Csirmaz, Bill Zissimopoulos
-
-Synchronizing data structures, and filesystems in particular,
-is a task that we encounter more and more often in our world
-of multiple mobile devices, cloud solutions and distributed systems.
-Applications of synchronization ranges from
-solutions for end users who expect to access personal data seamlessly
-on multiple devices and personal clouds to geographically distributed server networks
-that need to synchronize themselves with low latency to serve the 
-same content.
-
-In this paper we
-continue the work in \cite{NREC:alg} and add to the theoretical understanding
-of synchronization based not on filesystem states, but filesystem changes or commands.
-
-% Synchronization:
-% Main aim: apply updates (where possible) from other replicas
-% update detection -> conflict detection -> merging updates -> ordering updates -> apply updates from other replicas
-% Problems: conflict detection, ordering
-
-% ORDERING - because when taking updates from different replicas we get an essentially unordered set
-% Insight: (Prof. Norman Ramsey)
-% - updates where two orders (AB vs BA) are not equivalent are incompatible
-% - we only have a set of updates and need to create an order
-
-% New:
-% better command (instruction) set
-% simpler reconciliation algorithm
-% proof of correctness
-
-\section{Definitions}
-\input{def-filesystem}
-\input{def-commands}
-
-\input{axioms}
-
-% <<<<<<<< TODO Rewrite: no algebra
-%  about which we will reason
-% using our algebra.
-% We will aim to draw conclusions or judgements about commands and sequences of commands
-% based on the algebra we are aiming to construct.
-% For example, if we believe that two sequences of commands are equivalent as their effect
-% is the same, then we aim to be able to derive this from the axioms and inference rules of the
-% algebra.
-% As the algebra operates on commands only,
-% these judgements, by definition, need to hold regardless of the filesystem the commands are applied to.
-% Accordingly, we expect that the more information one encodes into the commands and the sequences,
-% the better predicitons we will be able to make using our algebra,
-% as then the commands and sequences will be more specific, and will select a smaller subset
-% of potential filesystems on which they can meaningfully operate.
-% >>>>>>>>>> to here
-
-% Update detection
-% ----------------
-
-\section{Update detection}
-
-In a command-based reconciliation solution we assume that we have two sequences of commands
-$A$ and $B$ that have modified a single filesystem $\FS$ yielding two different replicas $\FS_A$ and $\FS_B$ that we
-need to reconcile. While it is conceivable that the sequences would be based on a record of
-all operations that modified the two filesystems, in most filesystem implementations
-such records are not implemented, and therefore we must construct suitable sequences
-by comparing $\FS_A$ and $\FS_B$ to their common ancestor, $\FS$. This is called update detection.
-
-A sequence that transforms $\FS$ into $\FS_A$ must contain at least one command on each node
-that changes between the two states of the filesystem. Also, it is easy to see that this is also
-sufficient, as there are commands available for any input and output value. 
-Specifically, if at node $n$, $\FS(n)=X'$ and $\FS_A(n)=Y'\neq X'$, then we add the command $\cxyaa{n}{Y'}$ to $A$
-where $X'\in\setvx{X}$ and $Y'\in\setvx{Y}$.
-
-To be able to describe such sequences better, let us introduce the following properties:
-
-\begin{mydef}{Minimal set or sequence.}
-A sequence or set of commands is minimal if it contains at most one command on every node.
-\end{mydef}
-
-\begin{mydef}{Simple set or sequence.}
-A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
-\end{mydef}
-
-This update detector therefore yields a simple set of commands because we only add a single command
-for each node, and we only add commands that are necessary, that is, there will be no 
-assertion commands in the set.
-
-The next step in generating the sequences is to order the commands collected.
-As this task is at the heart of reconciliation itself independently of update detection,
-we discuss it in the next section.
-Then, in \cref{update_works}, we prove that the resulting sequence actually
-works without breaking the filesystem.
-
-% Ordering commands
-% ----------------
-
 \section{Ordering commands}\label{ordering}
@@
 but simple sets as sequences.
-
-\medskip
-
-% Correctness of update detection
-% -------------------------------
-
-Based on \cref{connected_changes} we can also show that
-the update detector does function as intended as:
-
-\begin{myth}\label{update_works}
-A sequence of commands returned by the update detector
-when comparing $\FS^*$ to the original $\FS$
-will not break $\FS$ if it is applied to it.
-\end{myth}
-\begin{proof}
-Let $\FS\neq\fsbroken$ be the original filesystem, and $\FS^*\neq\fsbroken$
-be the filesystem after the changes we intend to detect.
-Let us assume that some mechanism recorded all changes that occurred
-to $\FS$ until it reached the state $\FS^*$.
-Our set if commands is sufficient to record any change, as
-there are commands for every input and output type pair, therefore
-we know that the changes can be recorded as a sequence of commands $S$
-where $S\FS=\FS^*$.
-Note that $S$ will not contain assertion commands, as they do not
-represent an actual change in the filesystem.
-
-Therefore, \cref{connected_changes} applies to $S$ and we know
-if it contains commands on $\nn$ and $n$ where $\nn\descendant n$,
-then it also contains commands on nodes in between;
-which is equivalent to saying that if $\FS$ changed
-at node $\nn$ and $n$, then it had to change on the nodes in between.
-
-If so, then, similarly to what happens in the ordering algorithm,
-we can separate $S$ into components of commands on related nodes,
-as commands from separate components freely commute yielding an equivalent sequence.
-From the arguments above, we also know that each component
-must be made up of only desctruction or only construction pairs,
-but not a mixture of the two.
-This means that in each component, parents either strictly precede or succeed child nodes
-(as otherwise $S\equiv\cbrk$ would hold),
-from which it follows that once the components are separated
-in a new sequence $S'\equiv S$,
-commands on the same nodes are next to each other in $S'$.
-
-Based on \cref{ax_same_emptyseq,ax_same_singlec} there is
-an $S''\eqnrw S'$ in which multiple commands on the same nodes
-are simplified into a single command or an empty sequence,
-and therefore $S''$ is simple and $S\equiv S'\eqext S''$.
-It is easy to see that $S''$ must contain the same commands
-as the output of the update detector, $U$, as both are simple
-but reflect all changes between $\FS$ and $\FS^*$.
-If so, then $S''\in\orderset{U}$ and based on \cref{simple_reorder_equiv}
-we have
-$S\equiv S'\eqext S''\equiv U$, and as $S\FS = \FS^* \neq \fsbroken$,
-therefore $U\FS\neq\fsbroken$.
-\end{proof}
-
-\section{Reconciliation}
-
-If we start with two copies of the filesystem $\FS$,
-and two different sequences are applied to the copies to yield $\FS_A:=A\FS$
-and $\FS_B:=B\FS$, then our aim is to define sequences of commands $\reca$ and $\recb$
-so that $\recb\FS_A$ and $\reca\FS_B$ would be as close to each other as possible.
-
-We work based on the assumption that to achieve this, we need
-to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
-As some commands may have been applied to both filesystems, our first approximation
-is $\reca = A\setminus B$ and $\recb = B\setminus A$
-(in some suitable order).
-This, however, will break both filesystems if there have been incompatible updates
-in $A$ and $B$. 
-Our aim is therefore to provide an algorithm that selects the commands 
-$\reca \subset A\setminus B$
-and $\recb \subset B\setminus A$ 
-so that $\reca\FS_B\neq\fsbroken$ and $\recb\FS_A\neq\fsbroken$,
-and show that these are the longest sequences with this property, that is,
-adding any command left out from $\reca$ or $\recb$ will break the filesystems.
-
-We assume that $A$ and $B$ are returned by an update detector,
-and so they are simple sequences.
-(Otherwise, they can be simplified to become simple sequences.)
-We also assume that $\FS_A$ and $\FS_B$ are not broken.
-With these assumptions,
-we can now define independent sequences and
-our reconciliation algorithm.
-
-\begin{mydef}{Independent commands, sequences and sets.}
-For two commands $\cxynv$ and $\czwmv$ we write $\cxynv\indep\czwmv$ if $\cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk$.
-For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
-$\forall \alpha\in A \mbox{~and~} \forall \beta\in B: \alpha\indep\beta$.
-\end{mydef}
-
-\begin{mydef}{Reconciliation.}\label{def:reconciliation}
-\begin{align*}
-\reca = \{\alpha| & \\
-& \alpha\in A\setminus B \\
-& \wedge \\
-& \forall \beta\in B\setminus A: \alpha\indep\beta\\
-\} &
-\end{align*}
-
-In other words, the sequence $\reca$ we apply to $\FS_B$ 
-is the largest subset of $A\setminus B$
-that is independent of $B\setminus A$.
-The order of commands in the sequence can be determined using the algorithm described in
-\cref{ordering} as any subset of $A$ is also simple.
-In a similar way, $\recb$ can be obtained by reversing $A$ and $B$.
-\end{mydef}
-
-We would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
-that is, without loss of generality,
-\[ \reca\FS_B\neq\fsbroken. \]
-So that we can formalize statements needed to prove this,
-let us introduce two relations that describe under what conditions
-sequences of commands work, that is, do not break a filesystem.
-
-\input{works-inverse}
-
-\medskip
-
-% Correctness of reconciliation
-% -----------------------------
-
-We are now ready to prove that the proposed algorithm for reconciliation is correct,
-that is, applying its result is not going to break the replicas.
-We reformulate the original proposition, $\reca\FS_B\neq\fsbroken$,
-based on $\FS_B=B\FS$ and so we aim to prove that
-$B\cc\reca$ works wherever $A$ and $B$ work:
-
-\begin{myth}
-If $A, B$ are simple, then $\worksc{B\cc \reca}{A,B}$,
-where, to restate \cref{def:reconciliation},
-% { % scope
-% \renewcommand{\themydef}{\ref{def:reconciliation}}
-% \begin{mydef}
-\begin{align*}
-\reca = \{\alpha| & \\
-& \alpha\in A\setminus B \\
-& \wedge \\
-& \forall \beta\in B\setminus A: \alpha\indep\beta\\
-\}. &
-\end{align*}
-% \end{mydef}
-% } % scope
-\end{myth}
-
-This is trivial unless $\works{A,B}$, so we assume that it is true.
-Let us first investigate the part of $A$ and $B$ that is excluded from
-$\reca$: their intersection.
-
-\begin{mylem}\label{can_move_intersection}
-Let $A$ and $B$ be two simple sequences so that $\works{A, B}$.
-Then their intersection, in some suitable order, also works on any filesystem
-either of them works on:
-$\worksc{A\cap B}{A}$, and, by symmetry,
-$\worksc{A\cap B}{B}$.
-\end{mylem}
-
-\begin{proof}
-The difficulty is that commands in $A\cap B$ can occur anywhere in $A$.
-Therefore, first we prove the following:
-if all commands are marked in $A$ that also appear in $B$,
-then there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.
-
-We show that $A$ can be transformed via equivalences so that this would be true.
-Our proposition is that if the marked commands are not at the beginning, then
-the sequence contains an unmarked command followed by a marked command.
-We show that these can be swapped resulting in an equivalent sequence.
-Then, by repeating this process similarly to bubble sorting, we can generate 
-a suitable $A'$.
-
-\medskip
-
-Let us consider therefore the marked command preceded by an unmarked command in $A$,
-and let the marked command be $\cxynv$, 
-and the preceding unmarked command be $\czwmv$.
-As $A$ is simple and $\works{A}$, from 
-\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
-we know that these commands can only be on unrelated paths or form a construction or destruction pair.
-In the first case, swapping the commands results in a sequence equivalent to $A$,
-and we show that the last two cases are impossible as they would lead to contradiction.
-
-In these cases, either $m=\parent(n)$ or $n=\parent(m)$.
-If $B$ has a command on $m$, then
-from \cref{lemma:neighbor}
-we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxynv$ (also in $B$),
-and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
-When describing our ordering algorithm in \cref{ordering} we saw
-that the command on the parent path deremines whether a pair of commands
-is a construction or destruction pair,
-and that this, in turn, determines whether the command on the child path must
-precede or follow the other command as otherwise the sequence would break all filesystems.
-This argument holds for both $A$ and $B$, and so the command on $m$ must be on
-the same side of the command on $n$ in both sequences.
-
-If $B$ has no command on $m$, then let $B'$ be $B$, 
-but with an extra command added to it just before $\cxynv$
-according to \cref{ax_child_assert,ax_parent_assert}, 
-from which we know that $B'\equiv B$.
-We also know that $B'$ is still minimal (but no longer simple).
-
-In either case, therefore,
-we have a minimal $B'$ which has a command on $m$ just before $\cxynv$ and $B'\equiv B$.
-Let this command on $m$ be $\cqrmv$.
-\begin{gather*}
-A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
-B' = \cdots\cc  \cqrmv\cc  \cxynv\cc  \cdots
-\end{gather*}
-
-As $\works{A,B}$ and so $\works{A,B'}$, 
-from \cref{worksinputmatch}
-we know that $Q=Z$.
-
-Going back to the construction and destruction pairs we see that the output type of the first command
-is always the same, and it is either $D$ or $\empt$ depending on the relationship between $n$ and $m$.
-Therefore $R=W$ and $\cqrmv=\czwmv$
-as $|\setd|=|\setb|=1$. 
-If $B$ originally had a command on $m$,
-this is a contradiction as $\czwmv$ was not marked, but we see it must also be in $B'$ and therefore in $B$.
-If $B$ had no command on $m$,
-this is a contradiction because the command on $m$ in $B'$ is an assertion command, so $Z=Q=R=W$, 
-but $A$ contained no assertion commands.
-
-\medskip
-
-We now know that there is an $A'\equiv A$ in which commands in $A\cap B$
-are at the beginning, and therefore 
-from \cref{worksextpostfix}
-$\worksc{A\cap B}{A}$ and by symmetry $\worksc{A\cap B}{B}$.
-\end{proof}
-
-\medskip
-
-We would like to prove that $\worksc{B\cc \reca}{A,B}$.
-From the above we know that this is equivalent to
-\[ \worksc{\acb\cc \bma\cc \reca}{A,B}. \]
-As we already know that $\reca\indep\bma$
-and that $\worksc{\acb\cc \bma}{A,B}$
-(as $\worksc{B}{A,B}$),
-based on \cref{indep_prefix_combine}
-we only need to prove that
-\[ \worksc{\acb\cc \reca}{A,B}. \]
-Using \cref{r_invmove} we can rephrase this as
-\[ \worksc{\reca}{\acbi\cc A,\acbi\cc B}. \]
-
-To restate some results above, we therefore already know the following things:
-\begin{itemize}
-\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
-\item $\amb \cap \bma = \emptyset$
-\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
-\item $\worksc{\amb, \bma}{\acbi\cc A,\acbi\cc B}$ 
-because of \cref{r_invmove}
-as $\worksc{A,B}{A,B}$,
-and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
-\end{itemize}
-
-Our theorem is therefore proven if we prove the following lemma:
-\newcommand{\condSimple}{(c1)}
-\newcommand{\condDisj}{(c2)}
-\newcommand{\condApr}{(c3)}
-\newcommand{\condWork}{(c4)}
-\begin{mylem}
-If
-   \begin{itemize}
-   \item[\condSimple] $S$ and $T$ are simple sequences,
-   \item[\condDisj] $S\cap T=\emptyset$,
-   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
-   \item[\condWork] $\worksc{S,T}{\seqset{C}}$ for some set of sequences $\seqset{C}$,
-   \end{itemize}
-then
-\[ \worksc{S^*}{\seqset{C}}. \]
-\end{mylem}
-
-\begin{proof}
-This is trivial unless $\works{\seqset{C}}$, so we will assume that it is true
-and therefore $\works{S,T}$.
-
-The proof is similar to that of \cref{can_move_intersection}.
-We mark all commands in $S$ that are in its subset $S^*$, and
-we prove that $S$ can be transformed into $S'$ via equivalences
-so that all marked commands would be at its beginning.
-If so, then based on \cref{worksextpostfix}
-$\worksc{S^*}{\seqset{C}}$ as $\worksc{S'}{\seqset{C}}$ and $S'=S^*\cc S_0$ 
-where $S_0$ contains the remaining (conflicting) commands.
-
-Again we know that if $S$ does not already have all marked commands at its beginning,
-then there is an unmarked command followed by a marked one.
-We show that these commands are independent and so they can be swapped
-resulting in an equivalent sequence.
-By repeating this process we can generate a suitable $S'$.
-
-Let therefore the marked command in $S$ be $\cxynv$
-and the preceding unmarked command be $\czwmv$.
-As $S$ is simple and $\works{S}$, from 
-\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
-we know that these commands can only be on unrelated paths or form a construction or destruction pair.
-In the first case, swapping the commands results in a sequence equivalent to $S$;
-we only need to show that the other two cases are not possible as they would lead to a contradiction.
-
-In the last two cases, we know that either $m=\parent(n)$ or $n=\parent(m)$.
-We also know that because of {\condApr} there must be 
-a command $\cqrov$ in $T$ which is not independent of $\czwmv$
-as $\czwmv$ is not part of $S^*$.
-\begin{gather*}
-S = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
-T = \cdots\cc  \cqrov\cc \cdots
-\end{gather*}
-We know none of these commands is an assertion command, and 
-from {\condDisj} that $\cqrov\neq\czwmv$.
-Therefore, based on \cref{unrelated_is_independent} we know this means that
-either $m\descendantEq o$ or $o\descendantEq m$.
-From {\condApr} we also know that $\cxynv\indep \cqrov$,
-and so because of \cref{unrelated_is_independent},
-$n\unrel o$.
-
-We therefore have four cases considering the relationships between $n,m$ and $o$:
-\begin{itemize}
-\item $n=\parent(m) \wedge o\descendantEq m$.
-   This would mean that $o\descendantEq n$ or $n=\parent(o)$, which contradicts $n\unrel o$.
-\item $n=\parent(m) \wedge m\descendantEq o$.
-   This would mean that $n\descendant o$, which contradicts $n\unrel o$.
-\item $m=\parent(n) \wedge o\descendantEq m$.
-   This would mean that $o\descendant n$, which contradicts $n\unrel o$.
-\item $m=\parent(n) \wedge m\descendantEq o$.
-   Let us continue with this case.
-\end{itemize}
-
-We know that $T$ cannot have a command on $m$ as $m=\parent(n)$ and $\cxynv\indep T$,
-and so $m\neq o$ and therefore $m\descendant o$.
-This means we can create a new sequence $T'\equiv T$ by inserting a command on 
-$m$ into $T$ before $\cqrov$
-according to \cref{ax_parent_assert}.
-We now have $\cxynv\indep T\equiv T'$ which is a contradiction as
-$T'$ has a command on $m$ and $m=\parent(n)$.
-\end{proof}
-
-\subsection{Reconciliation is complete}
-
-% Reconciliation is maximal
-% -------------------------
-% This is where we're using |D|=1
-% TODO C.f. strict / liberal etc. reconciliation in references
-
-The reconciliation algorithm defined above is also complete, that is,
-it is not possible to apply any further commands from $A\setminus B$ to $\FS_B$.
-To show this, we are going to prove the following \namecref{rec_is_complete}:
-
-\begin{myth}\label{rec_is_complete}
-If $A$ and $B$ are simple sequences,
-and we select a sequence $S\subset \amb$ so that
-it contains a command $\cxynv$ for which $\cxynv\nindep\bma$,
-then $B\cc S$ either breaks all filesystems $A$ and $B$ do not break
-(that is, $S$ breaks all possible $\FS_B$ replicas),
-or it overrides incompatible changes introduced in the replica by $B$.
-\end{myth}
-Overriding changes is not desirable as in these cases the reconciler
-does not have enough information to decide whether to promote
-the change introduced by $A$ over that introduced by $B$ or vice versa.
-These cases should be treated as conflicts and
-the affected nodes or commands marked for review
-by a human or a different system.
-\begin{proof}
-The proof is similar to the ones we have seen above.
-Without loss of generality, we assume that $\cxynv$ is the first command in $S$
-that is not independent of $\bma$.
-If so, we can split $S$ into $S_0\cc\cxynv\cc S_1$ where $S_0\indep\bma$.
-Let us also split $\bma$ into $T_0\cc\czwmv\cc T_1$ where $T_1\indep\cxynv$.
-From \cref{can_move_intersection} we know that
-$B\cc S \equiv \acb\cc\bma\cc S$.
-We also know commands in $S_0$ and $\bma$ commute, and so this is equivalent to
-$\acb\cc S_0\cc\bma\cc\cxynv\cc S_1$.
-Expanding $\bma$ and swapping $T_1$ and $\cxynv$ we get
-\[ \acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv\cc T_1\cc S_1. \]
-
-First, we prove that this sequence breaks all filesystems
-unless $n=m$.
-Let us therefore suppose $n\neq m$ and, to use an inverse proof,
-that the sequence works on $\FS$ where $A\FS\neq\fsbroken$.
-If so, its prefix, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also work.
-
-We know $\cxynv\nindep\czwmv$, and so from \cref{unrelated_is_independent}, $n\nunrel m$.
-As the sequence works, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
-As $\czwmv$ and $T_0$ originate from $B\setminus A$ and $B$ is simple, we also know there are
-no commands on $m$ in $A\cap B$ or $T_0$,
-and that there are no commands on $m$ in $S_0$ as $S_0\indep\bma$.
-
-On the one hand we therefore know that $\FS(m)$ must be of type $Z$,
-but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},
-we also know that $\cxynv$ cannot be applied to $\FS$ without
-changing $\FS(m)$ first.
-As $A\FS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
-Let this command be $\cqrmv$.
-
-Clearly $Q=Z$ (from \cref{worksinputmatch}), and from the construction and destruction
-pairs we also see that $R=W$ must hold, where $W=\cchard$ or $W=\ccharb$.
-As $|\setd|=1$ and $|\setb|=1$, this also means that $v_R=v_W$ and therefore
-$\cqrmv = \czwmv$.
-This is a contradiction as $\cqrmv\in A$, but $\czwmv\in\bma$.
-
-The only possibility is therefore $n=m$.
-As $A$ and $B$ are simple, we therefore know that these are the first commands on $n$,
-and so (again from \cref{worksinputmatch}) $Z=X$.
-We also know $\valvw\neq\valvy$ as otherwise the two commands would be equal and
-would be included in $A\cap B$,
-but this means that $\cxynv$, from $A$, overrides a change introduced 
-by $\czwnv$, from $B$, which should be treated as a conflict.
-\end{proof}
-
-From the proof it is apparent that this result depends on $|\setd|=1$.
-
-% TODO
-TODO: About setting up an algebra / calculus
-
-TODO: next steps. multiple replicas
-
-\begin{thebibliography}{99}
-
-\bibitem{NREC:alg} Ramsey, Norman and Elod Csirmaz: {\it An algebraic approach to
-file synchronization...}
-
-\bibitem{BZ} Bill Zissimopoulos, personal communication, ...
-
-\end{thebibliography}
-
-\end{document}

### 2015-12-06 2015/paper.tex
Split paper into sections

@@
 \section{Definitions}
+
 \input{def-filesystem}
+
 \input{def-commands}
@@
 
-% Ordering commands
-% ----------------
-
-\section{Ordering commands}\label{ordering}
-
-We often encounter the case where we only have a set of commands without a specified order.
-As we have seen above, this can occur after the first stage of update detection,
-but, more importantly,
-it is actually the task of the reconciler to determine whether there is an order,
-and if yes, what order,
-in which updates from multiple replicas can be applied to a filesystem.
-
-In this section we describe an algorithm with which all possible orderings of a
-simple set of commands can be generated, but before doing so, let us consider the following lemma.
-
-\begin{mylem}\label{connected_changes}
-Given a set of commands that
-does not contain assertion commands,
-and which can be applied to a filesystem in some order without breaking it,
-and which contains commands on $n$ and $\nn$ where $\nn\descendant n$
-but $\nn\neq\parent(n)$, then the set must also contain a commands
-on each node between $n$ and $\nn$.
-\end{mylem}
-\begin{proof}
-We prove that under the given conditions, the set must contain a command on $\parent(n)$.
-Then, by repeating this statement, we how that the set must contain commands on every
-ancestor of $n$ up to $\nn$.
-
-Furthermore,
-we prove this proposition for sequences, not sets, as if all sequences must contain a command on $\parent(n)$,
-then so must sets because otherwise there would be no order in which they can be
-applied to any filesystem.
-
-Let $A$ be a sequence that satisfies the conditions;
-we therefore know that it contains a command $\cxynv$ on $n$
-and another command $\czwnnv$ on $\nn$.
-We use an indirect proof and assume that there are no commands on $\parent(n)$ in $A$.
-Next, we create a new sequence $A'\equiv A$ in which $\cxynv$ and $\czwnnv$ are next to each other.
-If they are already next to each other in $A$, there is nothing to do.
-Otherwise, consider the command next to $\cxynv$ in the direction where $\czwnnv$ is.
-Let this command be $\cqrmv$.
-If $\czwnnv$ is to the right, then $A$ looks like the following:
-\[ A = \cdots\cc\cxynv\cc\cqrmv\cc\cdots\cc\czwnnv\cc\cdots \]
-If $n\unrel m$, swap $\cxynv$ and $\cqrmv$. Based on \cref{ax_separate_commute} we know that the new
-sequence is equivalent to $A$.
-Otherwise, we know $m\neq\parent(n)$ as there are no commands on $\parent(n)$, and so
-from \cref{ax_distantrel_breaks} we get $A\equiv\cbrk$ which contradicts our assumptions.
-(Note that $A$ cannot contains assertion commands.)
-By repeating this step we can therefore convert $A$ into $A'$ where $\cxynv$ and $\czwnnv$ are neighboring commands.
-However, then \cref{ax_distantrel_breaks} applies to the sequence and therefore $A\equiv A'\equiv\cbrk$ which
-is again a contradiction.
-\end{proof}
-
-\medskip
-
-We can now define our algorithm to generate orders of sets of commands.
-
-Let $U$ be a simple set of commands
-that we know can be applied to at least one filesystem in some order without breaking it.
-Then we can split $U$ into a maximum number of disjunct subsets
-(components) so that the nodes of two commands from two different subsets are unrelated.
-These will simply be the components of the subset of the node forest that contains the nodes affected by the set.
-
-From \cref{ax_separate_commute} we know that commands from different 
-components can be applied in any order.
-Therefore once we have ordered the commands inside a component, we generate
-all permutations of the components themselves, including the ones
-in which commands from separate components mix and overlap
-(but where the possible orders determined for commands inside the components are respected).
-
-Next, consider the ordering inside a component.
-
-This is not a problem in the case of components containing a single command only.
-(Note that $\cff$ can only appear in a component of one.)
-
-In each component that is larger than one, 
-we know that all nodes are related, and from \cref{connected_changes}
-we also know that it must contain commands on all nodes in between.
-Therefore the nodes
-form a rooted ordered tree,
-and the pairs of commands connected by the edges in the tree 
-must be construction or destruction pairs.
-(Otherwise, there would be no ordering of the component that is not equivalent to $\cbrk$
-and via \cref{ax_separate_commute} there would be no ordering of the whole set, either.)
-
-To order the commands in the component,
-select the command with the topmost node, so that there would be no command
-on its parent node (if there is one). 
-If the command removes content at this node (it is of the form $\caa{X}{\ccharb}$), 
-then it must follow all other commands in the component, and
-all parent--child pairs in the whole component must be destruction pairs.
-Otherwise, the command with the topmost node needs to precede the other commands,
-and the component must be made of construction pairs.
-These follow from the patterns of construction and destruction pairs, which
-at no point can mix without causing any sequence to break all filesystems.
-
-Then move the command with the topmost node to the beginning or the end of
-the sequence we are creating out of the component,
-and recursively start the whole algorithm again on the commands in the component that remain,
-potentially splitting them into sub-components.
-The result of this process is a set of possible orders for each component,
-which are then combined into a set of possible orders for the whole set of commands.
-
-\begin{mydef}{$\orderset{U}$.}
-We use $\orderset{U}$ to denote the set of sequences that contain all commands in
-the simple set $U$
-and represent all orders generated by this algorithm.
-\end{mydef}
-
-It follows from the algorithm that:
-\begin{mycor}\label{lemma:neighbor}
-If $U$ contains commands on both $n$ and $\parent(n)$, then
-there is a $U'\in\orderset{U}$ where they are next to each other.
-\end{mycor}
-
-As a specific case, we can regard a sequence of commands $S$
-as a set and determine its $\orderset{S}$.
-An important property of simple sequences is that
-all of their valid orderings are equivalent,
-and all equivalent sequences are mere reorderings:
-
-\begin{mylem}\label{simple_reorder_equiv}
-For any simple sequence $S\neq\cbrk$,
-$\forall T: T\equiv S \Leftrightarrow T\in\orderset{S}$.
-\end{mylem}
-\begin{proof}
-First, as $S$ only has at most one command on each node,
-any sequence in $\orderset{S}$ either breaks a filesystem,
-or it leaves it in the same state as $S$.
-
-Second, based on the algorithm we also know that $\orderset{S}$ contains
-all possible orderings of $S$ as the only ordering between commands
-it prescribes are when the commands in the reverse order would break every filesystem.
-
-If, for example, in a component or sub-component
-made up of construction pairs,
-the command on the topmost node, $\cxynv$, was not before all other commands
-in the component as described by the algorithm,
-then any resulting sequence would necessarily contain
-a $\czwmv$ where $n\descendant m$, potentially followed by commands
-on unrelated paths, and then followed by $\cxynv$.
-From \cref{ax_separate_commute} we know we can convert this sequence
-to an equivalent sequence by swapping the unrelated commands with
-$\czmv$, which sequence would therefore have the commands on
-$m$ and $n$ next to each other. Then from \cref{ax_distantrel_breaks,ax_directparent_breaks}
-we know the sequence would break all filesystems
-as a reversed construction pair is never a valid destruction pair.
-
-We can prove that an order not generated by the algorithm
-in case of components made of destruction pairs breaks all filesystems
-in a similar way.
-
-Also, from \cref{ax_separate_commute} we know
-that the order between any other command pairs is not fixed in the sense
-that if one order works, so will the other.
-
-From these we know that all sequences in $\orderset{S}$
-are equivalent, and that any sequence $T$ outside it
-necessarily breaks all filesystems.
-
-Therefore if $S\nequiv\cbrk$ then $S\in\orderset{S}$,
-and $S$ cannot equivalent to any sequence of the same commands
-not in $\orderset{S}$.
-\end{proof}
-
-It follows from this that given a simple set,
-we can simply assume that it has an order.
-Accordingly, we will at times treat not only sequences as sets,
-but simple sets as sequences.
+\input{ordering}
 
@@
 
-If we start with two copies of the filesystem $\FS$,
-and two different sequences are applied to the copies to yield $\FS_A:=A\FS$
-and $\FS_B:=B\FS$, then our aim is to define sequences of commands $\reca$ and $\recb$
-so that $\recb\FS_A$ and $\reca\FS_B$ would be as close to each other as possible.
-
-We work based on the assumption that to achieve this, we need
-to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
-As some commands may have been applied to both filesystems, our first approximation
-is $\reca = A\setminus B$ and $\recb = B\setminus A$
-(in some suitable order).
-This, however, will break both filesystems if there have been incompatible updates
-in $A$ and $B$. 
-Our aim is therefore to provide an algorithm that selects the commands 
-$\reca \subset A\setminus B$
-and $\recb \subset B\setminus A$ 
-so that $\reca\FS_B\neq\fsbroken$ and $\recb\FS_A\neq\fsbroken$,
-and show that these are the longest sequences with this property, that is,
-adding any command left out from $\reca$ or $\recb$ will break the filesystems.
-
-We assume that $A$ and $B$ are returned by an update detector,
-and so they are simple sequences.
-(Otherwise, they can be simplified to become simple sequences.)
-We also assume that $\FS_A$ and $\FS_B$ are not broken.
-With these assumptions,
-we can now define independent sequences and
-our reconciliation algorithm.
-
-\begin{mydef}{Independent commands, sequences and sets.}
-For two commands $\cxynv$ and $\czwmv$ we write $\cxynv\indep\czwmv$ if $\cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk$.
-For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
-$\forall \alpha\in A \mbox{~and~} \forall \beta\in B: \alpha\indep\beta$.
-\end{mydef}
-
-\begin{mydef}{Reconciliation.}\label{def:reconciliation}
-\begin{align*}
-\reca = \{\alpha| & \\
-& \alpha\in A\setminus B \\
-& \wedge \\
-& \forall \beta\in B\setminus A: \alpha\indep\beta\\
-\} &
-\end{align*}
-
-In other words, the sequence $\reca$ we apply to $\FS_B$ 
-is the largest subset of $A\setminus B$
-that is independent of $B\setminus A$.
-The order of commands in the sequence can be determined using the algorithm described in
-\cref{ordering} as any subset of $A$ is also simple.
-In a similar way, $\recb$ can be obtained by reversing $A$ and $B$.
-\end{mydef}
-
-We would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
-that is, without loss of generality,
-\[ \reca\FS_B\neq\fsbroken. \]
-So that we can formalize statements needed to prove this,
-let us introduce two relations that describe under what conditions
-sequences of commands work, that is, do not break a filesystem.
+\input{rec-intro}
 
@@
 
-\medskip
+\input{rec-sound}
 
-% Correctness of reconciliation
-% -----------------------------
-
-We are now ready to prove that the proposed algorithm for reconciliation is correct,
-that is, applying its result is not going to break the replicas.
-We reformulate the original proposition, $\reca\FS_B\neq\fsbroken$,
-based on $\FS_B=B\FS$ and so we aim to prove that
-$B\cc\reca$ works wherever $A$ and $B$ work:
-
-\begin{myth}
-If $A, B$ are simple, then $\worksc{B\cc \reca}{A,B}$,
-where, to restate \cref{def:reconciliation},
-% { % scope
-% \renewcommand{\themydef}{\ref{def:reconciliation}}
-% \begin{mydef}
-\begin{align*}
-\reca = \{\alpha| & \\
-& \alpha\in A\setminus B \\
-& \wedge \\
-& \forall \beta\in B\setminus A: \alpha\indep\beta\\
-\}. &
-\end{align*}
-% \end{mydef}
-% } % scope
-\end{myth}
-
-This is trivial unless $\works{A,B}$, so we assume that it is true.
-Let us first investigate the part of $A$ and $B$ that is excluded from
-$\reca$: their intersection.
-
-\begin{mylem}\label{can_move_intersection}
-Let $A$ and $B$ be two simple sequences so that $\works{A, B}$.
-Then their intersection, in some suitable order, also works on any filesystem
-either of them works on:
-$\worksc{A\cap B}{A}$, and, by symmetry,
-$\worksc{A\cap B}{B}$.
-\end{mylem}
-
-\begin{proof}
-The difficulty is that commands in $A\cap B$ can occur anywhere in $A$.
-Therefore, first we prove the following:
-if all commands are marked in $A$ that also appear in $B$,
-then there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.
-
-We show that $A$ can be transformed via equivalences so that this would be true.
-Our proposition is that if the marked commands are not at the beginning, then
-the sequence contains an unmarked command followed by a marked command.
-We show that these can be swapped resulting in an equivalent sequence.
-Then, by repeating this process similarly to bubble sorting, we can generate 
-a suitable $A'$.
-
-\medskip
-
-Let us consider therefore the marked command preceded by an unmarked command in $A$,
-and let the marked command be $\cxynv$, 
-and the preceding unmarked command be $\czwmv$.
-As $A$ is simple and $\works{A}$, from 
-\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
-we know that these commands can only be on unrelated paths or form a construction or destruction pair.
-In the first case, swapping the commands results in a sequence equivalent to $A$,
-and we show that the last two cases are impossible as they would lead to contradiction.
-
-In these cases, either $m=\parent(n)$ or $n=\parent(m)$.
-If $B$ has a command on $m$, then
-from \cref{lemma:neighbor}
-we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxynv$ (also in $B$),
-and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
-When describing our ordering algorithm in \cref{ordering} we saw
-that the command on the parent path deremines whether a pair of commands
-is a construction or destruction pair,
-and that this, in turn, determines whether the command on the child path must
-precede or follow the other command as otherwise the sequence would break all filesystems.
-This argument holds for both $A$ and $B$, and so the command on $m$ must be on
-the same side of the command on $n$ in both sequences.
-
-If $B$ has no command on $m$, then let $B'$ be $B$, 
-but with an extra command added to it just before $\cxynv$
-according to \cref{ax_child_assert,ax_parent_assert}, 
-from which we know that $B'\equiv B$.
-We also know that $B'$ is still minimal (but no longer simple).
-
-In either case, therefore,
-we have a minimal $B'$ which has a command on $m$ just before $\cxynv$ and $B'\equiv B$.
-Let this command on $m$ be $\cqrmv$.
-\begin{gather*}
-A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
-B' = \cdots\cc  \cqrmv\cc  \cxynv\cc  \cdots
-\end{gather*}
-
-As $\works{A,B}$ and so $\works{A,B'}$, 
-from \cref{worksinputmatch}
-we know that $Q=Z$.
-
-Going back to the construction and destruction pairs we see that the output type of the first command
-is always the same, and it is either $D$ or $\empt$ depending on the relationship between $n$ and $m$.
-Therefore $R=W$ and $\cqrmv=\czwmv$
-as $|\setd|=|\setb|=1$. 
-If $B$ originally had a command on $m$,
-this is a contradiction as $\czwmv$ was not marked, but we see it must also be in $B'$ and therefore in $B$.
-If $B$ had no command on $m$,
-this is a contradiction because the command on $m$ in $B'$ is an assertion command, so $Z=Q=R=W$, 
-but $A$ contained no assertion commands.
-
-\medskip
-
-We now know that there is an $A'\equiv A$ in which commands in $A\cap B$
-are at the beginning, and therefore 
-from \cref{worksextpostfix}
-$\worksc{A\cap B}{A}$ and by symmetry $\worksc{A\cap B}{B}$.
-\end{proof}
-
-\medskip
-
-We would like to prove that $\worksc{B\cc \reca}{A,B}$.
-From the above we know that this is equivalent to
-\[ \worksc{\acb\cc \bma\cc \reca}{A,B}. \]
-As we already know that $\reca\indep\bma$
-and that $\worksc{\acb\cc \bma}{A,B}$
-(as $\worksc{B}{A,B}$),
-based on \cref{indep_prefix_combine}
-we only need to prove that
-\[ \worksc{\acb\cc \reca}{A,B}. \]
-Using \cref{r_invmove} we can rephrase this as
-\[ \worksc{\reca}{\acbi\cc A,\acbi\cc B}. \]
-
-To restate some results above, we therefore already know the following things:
-\begin{itemize}
-\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
-\item $\amb \cap \bma = \emptyset$
-\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
-\item $\worksc{\amb, \bma}{\acbi\cc A,\acbi\cc B}$ 
-because of \cref{r_invmove}
-as $\worksc{A,B}{A,B}$,
-and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
-\end{itemize}
-
-Our theorem is therefore proven if we prove the following lemma:
-\newcommand{\condSimple}{(c1)}
-\newcommand{\condDisj}{(c2)}
-\newcommand{\condApr}{(c3)}
-\newcommand{\condWork}{(c4)}
-\begin{mylem}
-If
-   \begin{itemize}
-   \item[\condSimple] $S$ and $T$ are simple sequences,
-   \item[\condDisj] $S\cap T=\emptyset$,
-   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
-   \item[\condWork] $\worksc{S,T}{\seqset{C}}$ for some set of sequences $\seqset{C}$,
-   \end{itemize}
-then
-\[ \worksc{S^*}{\seqset{C}}. \]
-\end{mylem}
-
-\begin{proof}
-This is trivial unless $\works{\seqset{C}}$, so we will assume that it is true
-and therefore $\works{S,T}$.
-
-The proof is similar to that of \cref{can_move_intersection}.
-We mark all commands in $S$ that are in its subset $S^*$, and
-we prove that $S$ can be transformed into $S'$ via equivalences
-so that all marked commands would be at its beginning.
-If so, then based on \cref{worksextpostfix}
-$\worksc{S^*}{\seqset{C}}$ as $\worksc{S'}{\seqset{C}}$ and $S'=S^*\cc S_0$ 
-where $S_0$ contains the remaining (conflicting) commands.
-
-Again we know that if $S$ does not already have all marked commands at its beginning,
-then there is an unmarked command followed by a marked one.
-We show that these commands are independent and so they can be swapped
-resulting in an equivalent sequence.
-By repeating this process we can generate a suitable $S'$.
-
-Let therefore the marked command in $S$ be $\cxynv$
-and the preceding unmarked command be $\czwmv$.
-As $S$ is simple and $\works{S}$, from 
-\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
-we know that these commands can only be on unrelated paths or form a construction or destruction pair.
-In the first case, swapping the commands results in a sequence equivalent to $S$;
-we only need to show that the other two cases are not possible as they would lead to a contradiction.
-
-In the last two cases, we know that either $m=\parent(n)$ or $n=\parent(m)$.
-We also know that because of {\condApr} there must be 
-a command $\cqrov$ in $T$ which is not independent of $\czwmv$
-as $\czwmv$ is not part of $S^*$.
-\begin{gather*}
-S = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
-T = \cdots\cc  \cqrov\cc \cdots
-\end{gather*}
-We know none of these commands is an assertion command, and 
-from {\condDisj} that $\cqrov\neq\czwmv$.
-Therefore, based on \cref{unrelated_is_independent} we know this means that
-either $m\descendantEq o$ or $o\descendantEq m$.
-From {\condApr} we also know that $\cxynv\indep \cqrov$,
-and so because of \cref{unrelated_is_independent},
-$n\unrel o$.
-
-We therefore have four cases considering the relationships between $n,m$ and $o$:
-\begin{itemize}
-\item $n=\parent(m) \wedge o\descendantEq m$.
-   This would mean that $o\descendantEq n$ or $n=\parent(o)$, which contradicts $n\unrel o$.
-\item $n=\parent(m) \wedge m\descendantEq o$.
-   This would mean that $n\descendant o$, which contradicts $n\unrel o$.
-\item $m=\parent(n) \wedge o\descendantEq m$.
-   This would mean that $o\descendant n$, which contradicts $n\unrel o$.
-\item $m=\parent(n) \wedge m\descendantEq o$.
-   Let us continue with this case.
-\end{itemize}
-
-We know that $T$ cannot have a command on $m$ as $m=\parent(n)$ and $\cxynv\indep T$,
-and so $m\neq o$ and therefore $m\descendant o$.
-This means we can create a new sequence $T'\equiv T$ by inserting a command on 
-$m$ into $T$ before $\cqrov$
-according to \cref{ax_parent_assert}.
-We now have $\cxynv\indep T\equiv T'$ which is a contradiction as
-$T'$ has a command on $m$ and $m=\parent(n)$.
-\end{proof}
-
-\subsection{Reconciliation is complete}
-
-% Reconciliation is maximal
-% -------------------------
-% This is where we're using |D|=1
-% TODO C.f. strict / liberal etc. reconciliation in references
-
-The reconciliation algorithm defined above is also complete, that is,
-it is not possible to apply any further commands from $A\setminus B$ to $\FS_B$.
-To show this, we are going to prove the following \namecref{rec_is_complete}:
-
-\begin{myth}\label{rec_is_complete}
-If $A$ and $B$ are simple sequences,
-and we select a sequence $S\subset \amb$ so that
-it contains a command $\cxynv$ for which $\cxynv\nindep\bma$,
-then $B\cc S$ either breaks all filesystems $A$ and $B$ do not break
-(that is, $S$ breaks all possible $\FS_B$ replicas),
-or it overrides incompatible changes introduced in the replica by $B$.
-\end{myth}
-Overriding changes is not desirable as in these cases the reconciler
-does not have enough information to decide whether to promote
-the change introduced by $A$ over that introduced by $B$ or vice versa.
-These cases should be treated as conflicts and
-the affected nodes or commands marked for review
-by a human or a different system.
-\begin{proof}
-The proof is similar to the ones we have seen above.
-Without loss of generality, we assume that $\cxynv$ is the first command in $S$
-that is not independent of $\bma$.
-If so, we can split $S$ into $S_0\cc\cxynv\cc S_1$ where $S_0\indep\bma$.
-Let us also split $\bma$ into $T_0\cc\czwmv\cc T_1$ where $T_1\indep\cxynv$.
-From \cref{can_move_intersection} we know that
-$B\cc S \equiv \acb\cc\bma\cc S$.
-We also know commands in $S_0$ and $\bma$ commute, and so this is equivalent to
-$\acb\cc S_0\cc\bma\cc\cxynv\cc S_1$.
-Expanding $\bma$ and swapping $T_1$ and $\cxynv$ we get
-\[ \acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv\cc T_1\cc S_1. \]
-
-First, we prove that this sequence breaks all filesystems
-unless $n=m$.
-Let us therefore suppose $n\neq m$ and, to use an inverse proof,
-that the sequence works on $\FS$ where $A\FS\neq\fsbroken$.
-If so, its prefix, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also work.
-
-We know $\cxynv\nindep\czwmv$, and so from \cref{unrelated_is_independent}, $n\nunrel m$.
-As the sequence works, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
-As $\czwmv$ and $T_0$ originate from $B\setminus A$ and $B$ is simple, we also know there are
-no commands on $m$ in $A\cap B$ or $T_0$,
-and that there are no commands on $m$ in $S_0$ as $S_0\indep\bma$.
-
-On the one hand we therefore know that $\FS(m)$ must be of type $Z$,
-but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},
-we also know that $\cxynv$ cannot be applied to $\FS$ without
-changing $\FS(m)$ first.
-As $A\FS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
-Let this command be $\cqrmv$.
-
-Clearly $Q=Z$ (from \cref{worksinputmatch}), and from the construction and destruction
-pairs we also see that $R=W$ must hold, where $W=\cchard$ or $W=\ccharb$.
-As $|\setd|=1$ and $|\setb|=1$, this also means that $v_R=v_W$ and therefore
-$\cqrmv = \czwmv$.
-This is a contradiction as $\cqrmv\in A$, but $\czwmv\in\bma$.
-
-The only possibility is therefore $n=m$.
-As $A$ and $B$ are simple, we therefore know that these are the first commands on $n$,
-and so (again from \cref{worksinputmatch}) $Z=X$.
-We also know $\valvw\neq\valvy$ as otherwise the two commands would be equal and
-would be included in $A\cap B$,
-but this means that $\cxynv$, from $A$, overrides a change introduced 
-by $\czwnv$, from $B$, which should be treated as a conflict.
-\end{proof}
-
-From the proof it is apparent that this result depends on $|\setd|=1$.
+\input{rec-complete}
 

### 2015-12-06 2015/rec-complete.tex
Split paper into sections

\subsection{Completeness of Reconciliation}

% Reconciliation is maximal
% -------------------------
% This is where we're using |D|=1
% TODO C.f. strict / liberal etc. reconciliation in references

The reconciliation algorithm defined above is also complete, that is,
it is not possible to apply any further commands from $A\setminus B$ to $\FS_B$.
To show this, we are going to prove the following \namecref{rec_is_complete}:

\begin{myth}\label{rec_is_complete}
If $A$ and $B$ are simple sequences,
and we select a sequence $S\subset \amb$ so that
it contains a command $\cxynv$ for which $\cxynv\nindep\bma$,
then $B\cc S$ either breaks all filesystems $A$ and $B$ do not break
(that is, $S$ breaks all possible $\FS_B$ replicas),
or it overrides incompatible changes introduced in the replica by $B$.
\end{myth}
Overriding changes is not desirable as in these cases the reconciler
does not have enough information to decide whether to promote
the change introduced by $A$ over that introduced by $B$ or vice versa.
These cases should be treated as conflicts and
the affected nodes or commands marked for review
by a human or a different system.
\begin{proof}
The proof is similar to the ones we have seen above.
Without loss of generality, we assume that $\cxynv$ is the first command in $S$
that is not independent of $\bma$.
If so, we can split $S$ into $S_0\cc\cxynv\cc S_1$ where $S_0\indep\bma$.
Let us also split $\bma$ into $T_0\cc\czwmv\cc T_1$ where $T_1\indep\cxynv$.
From \cref{can_move_intersection} we know that
$B\cc S \equiv \acb\cc\bma\cc S$.
We also know commands in $S_0$ and $\bma$ commute, and so this is equivalent to
$\acb\cc S_0\cc\bma\cc\cxynv\cc S_1$.
Expanding $\bma$ and swapping $T_1$ and $\cxynv$ we get
\[ \acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv\cc T_1\cc S_1. \]

First, we prove that this sequence breaks all filesystems
unless $n=m$.
Let us therefore suppose $n\neq m$ and, to use an inverse proof,
that the sequence works on $\FS$ where $A\FS\neq\fsbroken$.
If so, its prefix, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also work.

We know $\cxynv\nindep\czwmv$, and so from \cref{unrelated_is_independent}, $n\nunrel m$.
As the sequence works, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
As $\czwmv$ and $T_0$ originate from $B\setminus A$ and $B$ is simple, we also know there are
no commands on $m$ in $A\cap B$ or $T_0$,
and that there are no commands on $m$ in $S_0$ as $S_0\indep\bma$.

On the one hand we therefore know that $\FS(m)$ must be of type $Z$,
but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},
we also know that $\cxynv$ cannot be applied to $\FS$ without
changing $\FS(m)$ first.
As $A\FS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
Let this command be $\cqrmv$.

Clearly $Q=Z$ (from \cref{worksinputmatch}), and from the construction and destruction
pairs we also see that $R=W$ must hold, where $W=\cchard$ or $W=\ccharb$.
As $|\setd|=1$ and $|\setb|=1$, this also means that $v_R=v_W$ and therefore
$\cqrmv = \czwmv$.
This is a contradiction as $\cqrmv\in A$, but $\czwmv\in\bma$.

The only possibility is therefore $n=m$.
As $A$ and $B$ are simple, we therefore know that these are the first commands on $n$,
and so (again from \cref{worksinputmatch}) $Z=X$.
We also know $\valvw\neq\valvy$ as otherwise the two commands would be equal and
would be included in $A\cap B$,
but this means that $\cxynv$, from $A$, overrides a change introduced 
by $\czwnv$, from $B$, which should be treated as a conflict.
\end{proof}

From the proof it is apparent that this result depends on $|\setd|=1$.

### 2015-12-06 2015/rec-intro.tex
Split paper into sections

If we start with two copies of the filesystem $\FS$,
and two different sequences are applied to the copies to yield $\FS_A:=A\FS$
and $\FS_B:=B\FS$, then our aim is to define sequences of commands $\reca$ and $\recb$
so that $\recb\FS_A$ and $\reca\FS_B$ would be as close to each other as possible.

We work based on the assumption that to achieve this, we need
to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
As some commands may have been applied to both filesystems, our first approximation
is $\reca = A\setminus B$ and $\recb = B\setminus A$
(in some suitable order).
This, however, will break both filesystems if there have been incompatible updates
in $A$ and $B$. 
Our aim is therefore to provide an algorithm that selects the commands 
$\reca \subset A\setminus B$
and $\recb \subset B\setminus A$ 
so that $\reca\FS_B\neq\fsbroken$ and $\recb\FS_A\neq\fsbroken$,
and show that these are the longest sequences with this property, that is,
adding any command left out from $\reca$ or $\recb$ will break the filesystems.

We assume that $A$ and $B$ are returned by an update detector,
and so they are simple sequences.
(Otherwise, they can be simplified to become simple sequences.)
We also assume that $\FS_A$ and $\FS_B$ are not broken.
With these assumptions,
we can now define independent sequences and
our reconciliation algorithm.

\begin{mydef}{Independent commands, sequences and sets.}
For two commands $\cxynv$ and $\czwmv$ we write $\cxynv\indep\czwmv$ if $\cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk$.
For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
$\forall \alpha\in A \mbox{~and~} \forall \beta\in B: \alpha\indep\beta$.
\end{mydef}

\begin{mydef}{Reconciliation.}\label{def:reconciliation}
\begin{align*}
\reca = \{\alpha| & \\
& \alpha\in A\setminus B \\
& \wedge \\
& \forall \beta\in B\setminus A: \alpha\indep\beta\\
\} &
\end{align*}

In other words, the sequence $\reca$ we apply to $\FS_B$ 
is the largest subset of $A\setminus B$
that is independent of $B\setminus A$.
The order of commands in the sequence can be determined using the algorithm described in
\cref{ordering} as any subset of $A$ is also simple.
In a similar way, $\recb$ can be obtained by reversing $A$ and $B$.
\end{mydef}

We would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
that is, without loss of generality,
\[ \reca\FS_B\neq\fsbroken. \]
So that we can formalize statements needed to prove this,
let us introduce two relations that describe under what conditions
sequences of commands work, that is, do not break a filesystem.

### 2015-12-06 2015/rec-sound.tex
Split paper into sections

\subsection{The Correctness of Reconciliation}

% Correctness of reconciliation
% -----------------------------

We are now ready to prove that the proposed algorithm for reconciliation is correct,
that is, applying its result is not going to break the replicas.
We reformulate the original proposition, $\reca\FS_B\neq\fsbroken$,
based on $\FS_B=B\FS$ and so we aim to prove that
$B\cc\reca$ works wherever $A$ and $B$ work:

\begin{myth}
If $A, B$ are simple, then $\worksc{B\cc \reca}{A,B}$,
where, to restate \cref{def:reconciliation},
% { % scope
% \renewcommand{\themydef}{\ref{def:reconciliation}}
% \begin{mydef}
\begin{align*}
\reca = \{\alpha| & \\
& \alpha\in A\setminus B \\
& \wedge \\
& \forall \beta\in B\setminus A: \alpha\indep\beta\\
\}. &
\end{align*}
% \end{mydef}
% } % scope
\end{myth}

This is trivial unless $\works{A,B}$, so we assume that it is true.
Let us first investigate the part of $A$ and $B$ that is excluded from
$\reca$: their intersection.

\begin{mylem}\label{can_move_intersection}
Let $A$ and $B$ be two simple sequences so that $\works{A, B}$.
Then their intersection, in some suitable order, also works on any filesystem
either of them works on:
$\worksc{A\cap B}{A}$, and, by symmetry,
$\worksc{A\cap B}{B}$.
\end{mylem}

\begin{proof}
The difficulty is that commands in $A\cap B$ can occur anywhere in $A$.
Therefore, first we prove the following:
if all commands are marked in $A$ that also appear in $B$,
then there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.

We show that $A$ can be transformed via equivalences so that this would be true.
Our proposition is that if the marked commands are not at the beginning, then
the sequence contains an unmarked command followed by a marked command.
We show that these can be swapped resulting in an equivalent sequence.
Then, by repeating this process similarly to bubble sorting, we can generate 
a suitable $A'$.

\medskip

Let us consider therefore the marked command preceded by an unmarked command in $A$,
and let the marked command be $\cxynv$, 
and the preceding unmarked command be $\czwmv$.
As $A$ is simple and $\works{A}$, from 
\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
we know that these commands can only be on unrelated paths or form a construction or destruction pair.
In the first case, swapping the commands results in a sequence equivalent to $A$,
and we show that the last two cases are impossible as they would lead to contradiction.

In these cases, either $m=\parent(n)$ or $n=\parent(m)$.
If $B$ has a command on $m$, then
from \cref{lemma:neighbor}
we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxynv$ (also in $B$),
and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
When describing our ordering algorithm in \cref{ordering} we saw
that the command on the parent path deremines whether a pair of commands
is a construction or destruction pair,
and that this, in turn, determines whether the command on the child path must
precede or follow the other command as otherwise the sequence would break all filesystems.
This argument holds for both $A$ and $B$, and so the command on $m$ must be on
the same side of the command on $n$ in both sequences.

If $B$ has no command on $m$, then let $B'$ be $B$, 
but with an extra command added to it just before $\cxynv$
according to \cref{ax_child_assert,ax_parent_assert}, 
from which we know that $B'\equiv B$.
We also know that $B'$ is still minimal (but no longer simple).

In either case, therefore,
we have a minimal $B'$ which has a command on $m$ just before $\cxynv$ and $B'\equiv B$.
Let this command on $m$ be $\cqrmv$.
\begin{gather*}
A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
B' = \cdots\cc  \cqrmv\cc  \cxynv\cc  \cdots
\end{gather*}

As $\works{A,B}$ and so $\works{A,B'}$, 
from \cref{worksinputmatch}
we know that $Q=Z$.

Going back to the construction and destruction pairs we see that the output type of the first command
is always the same, and it is either $D$ or $\empt$ depending on the relationship between $n$ and $m$.
Therefore $R=W$ and $\cqrmv=\czwmv$
as $|\setd|=|\setb|=1$. 
If $B$ originally had a command on $m$,
this is a contradiction as $\czwmv$ was not marked, but we see it must also be in $B'$ and therefore in $B$.
If $B$ had no command on $m$,
this is a contradiction because the command on $m$ in $B'$ is an assertion command, so $Z=Q=R=W$, 
but $A$ contained no assertion commands.

\medskip

We now know that there is an $A'\equiv A$ in which commands in $A\cap B$
are at the beginning, and therefore 
from \cref{worksextpostfix}
$\worksc{A\cap B}{A}$ and by symmetry $\worksc{A\cap B}{B}$.
\end{proof}

\medskip

We would like to prove that $\worksc{B\cc \reca}{A,B}$.
From the above we know that this is equivalent to
\[ \worksc{\acb\cc \bma\cc \reca}{A,B}. \]
As we already know that $\reca\indep\bma$
and that $\worksc{\acb\cc \bma}{A,B}$
(as $\worksc{B}{A,B}$),
based on \cref{indep_prefix_combine}
we only need to prove that
\[ \worksc{\acb\cc \reca}{A,B}. \]
Using \cref{r_invmove} we can rephrase this as
\[ \worksc{\reca}{\acbi\cc A,\acbi\cc B}. \]

To restate some results above, we therefore already know the following things:
\begin{itemize}
\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
\item $\amb \cap \bma = \emptyset$
\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
\item $\worksc{\amb, \bma}{\acbi\cc A,\acbi\cc B}$ 
because of \cref{r_invmove}
as $\worksc{A,B}{A,B}$,
and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
\end{itemize}

Our theorem is therefore proven if we prove the following lemma:
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\newcommand{\condWork}{(c4)}
\begin{mylem}
If
   \begin{itemize}
   \item[\condSimple] $S$ and $T$ are simple sequences,
   \item[\condDisj] $S\cap T=\emptyset$,
   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
   \item[\condWork] $\worksc{S,T}{\seqset{C}}$ for some set of sequences $\seqset{C}$,
   \end{itemize}
then
\[ \worksc{S^*}{\seqset{C}}. \]
\end{mylem}

\begin{proof}
This is trivial unless $\works{\seqset{C}}$, so we will assume that it is true
and therefore $\works{S,T}$.

The proof is similar to that of \cref{can_move_intersection}.
We mark all commands in $S$ that are in its subset $S^*$, and
we prove that $S$ can be transformed into $S'$ via equivalences
so that all marked commands would be at its beginning.
If so, then based on \cref{worksextpostfix}
$\worksc{S^*}{\seqset{C}}$ as $\worksc{S'}{\seqset{C}}$ and $S'=S^*\cc S_0$ 
where $S_0$ contains the remaining (conflicting) commands.

Again we know that if $S$ does not already have all marked commands at its beginning,
then there is an unmarked command followed by a marked one.
We show that these commands are independent and so they can be swapped
resulting in an equivalent sequence.
By repeating this process we can generate a suitable $S'$.

Let therefore the marked command in $S$ be $\cxynv$
and the preceding unmarked command be $\czwmv$.
As $S$ is simple and $\works{S}$, from 
\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
we know that these commands can only be on unrelated paths or form a construction or destruction pair.
In the first case, swapping the commands results in a sequence equivalent to $S$;
we only need to show that the other two cases are not possible as they would lead to a contradiction.

In the last two cases, we know that either $m=\parent(n)$ or $n=\parent(m)$.
We also know that because of {\condApr} there must be 
a command $\cqrov$ in $T$ which is not independent of $\czwmv$
as $\czwmv$ is not part of $S^*$.
\begin{gather*}
S = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
T = \cdots\cc  \cqrov\cc \cdots
\end{gather*}
We know none of these commands is an assertion command, and 
from {\condDisj} that $\cqrov\neq\czwmv$.
Therefore, based on \cref{unrelated_is_independent} we know this means that
either $m\descendantEq o$ or $o\descendantEq m$.
From {\condApr} we also know that $\cxynv\indep \cqrov$,
and so because of \cref{unrelated_is_independent},
$n\unrel o$.

We therefore have four cases considering the relationships between $n,m$ and $o$:
\begin{itemize}
\item $n=\parent(m) \wedge o\descendantEq m$.
   This would mean that $o\descendantEq n$ or $n=\parent(o)$, which contradicts $n\unrel o$.
\item $n=\parent(m) \wedge m\descendantEq o$.
   This would mean that $n\descendant o$, which contradicts $n\unrel o$.
\item $m=\parent(n) \wedge o\descendantEq m$.
   This would mean that $o\descendant n$, which contradicts $n\unrel o$.
\item $m=\parent(n) \wedge m\descendantEq o$.
   Let us continue with this case.
\end{itemize}

We know that $T$ cannot have a command on $m$ as $m=\parent(n)$ and $\cxynv\indep T$,
and so $m\neq o$ and therefore $m\descendant o$.
This means we can create a new sequence $T'\equiv T$ by inserting a command on 
$m$ into $T$ before $\cqrov$
according to \cref{ax_parent_assert}.
We now have $\cxynv\indep T\equiv T'$ which is a contradiction as
$T'$ has a command on $m$ and $m=\parent(n)$.
\end{proof}

### 2015-12-06 2015/def-commands.tex
Reconciliation policy comparison

@@
 $\FS(n)$ will be $\empt$. 
-However, from \cite{NREC:alg} we know that a useful set of axioms
+However, from \cite{NREC} and \cite{CBNR} we know that a useful set of axioms
 will in some cases need to distinguish between edits that result in directories ($edit(n,D)$) and

### 2015-12-06 2015/ordering.tex
Reconciliation policy comparison

@@
 to an equivalent sequence by swapping the unrelated commands with
-$\czmv$, which sequence would therefore have the commands on
+$\czwmv$, which sequence would therefore have the commands on
 $m$ and $n$ next to each other. Then from \cref{ax_distantrel_breaks,ax_directparent_breaks}

### 2015-12-06 2015/paper.tex
Reconciliation policy comparison

@@
 In this paper we
-continue the work in \cite{NREC:alg} and add to the theoretical understanding
+continue the work in \cite{NREC} and add to the theoretical understanding
 of synchronization based not on filesystem states, but filesystem changes or commands.
@@
 
+\section{Comparisons}
+
+We consider the reconciliation algorithm described here an improvement over
+the one derved during our previous research (see \cite{NREC})
+as the previous algorithm not only fails to propagate all possible commands
+wherever it is possible (that is, where it does not break the filesystem),
+but the current algorithm is also simpler.
+This is because the previous reconciliation algorithm excludes
+commands from being propagated which must be preceded by a command that conflicts.
+
+The former observation is supported by Berzan and Ramsey, who in \cite{CBNR} 
+describe between different reconciliation policies.
+The liberal (maximal) policy propagates all updates to all replicas where
+the command does not break the filesystem, while a conservative policy
+refrains from updating any node that is below a node with conflicting commands.
+They show that the reconciliation algorithm in \cite{NREC} implements
+an intermediate policy as one can easily construct two- or three-replica scenarios
+where an update could clearly be propagated, but it is excluded.
+To rephrase the example in \cite{CBNR}, consider the following two
+update sequences that have been applied to replicas $\FS_A$ and $\FS_B$:
+\begin{align*}
+A&=\cbdaa{\nn}{\valdi}\cc\cbfaa{n}{\valf} \\
+B&=\cbdaa{\nn}{\valdii}
+\end{align*}
+where $\parent(n)=\nn$ (\cite{NREC} did not require all directories to have the same value).
+Clearly $\cbfaa{n}{\valf}$ could be applied to $\FS_B$, but it is not as
+it must be preceded by creating the directory, which conflicts with the same operation in $B$
+due to the different value.
+(Introducing a third replica which has not changed at all further complicates the picture.)
+The current algorithm no longer needs to specify that there can be no conflicts
+on preceding commands, and, to use the above terminology, implements a fully liberal policy.
+
 % TODO
@@
 
+\section{Acknowledgments}
+
+I thank Laszlo Csirmaz for his invaluable input on previous drafts of this paper,
+and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.
+
 \begin{thebibliography}{99}
 
-\bibitem{NREC:alg} Ramsey, Norman and Elod Csirmaz: {\it An algebraic approach to
+\bibitem{NREC} Ramsey, Norman and Elod Csirmaz: {\it An algebraic approach to
 file synchronization...}
 
-\bibitem{BZ} Bill Zissimopoulos, personal communication, ...
+\bibitem{CBNR} Constantin Berzan, Norman Ramsey: Summer Scholars Technical Report
+Tufts University, Medford, MA, USA, 2010
+http://thirld.com/files/summerscholars\_techreport.pdf
+Accessed 29 November 2015
 

### 2015-12-11 2015/paper.tex
Minor changes

@@
 
+% TODO operation-based vs state-based
+
 % Synchronization:
@@
 % simpler reconciliation algorithm
-% proof of correctness
+% proof of correctness and completeness
+
+% rigorous proof, non-trivial
+
+% Update detection
+% - ordering
+% Reconciliation
+% - conditional operation & inverse sequences
 
@@
 
-\medskip
-
-% Correctness of update detection
-% -------------------------------
+\subsection{The Correctness of Update Detection}
 
@@
 A sequence of commands returned by the update detector
-when comparing $\FS^*$ to the original $\FS$
+when comparing the non-broken $\FS^*$ to the original $\FS$
 will not break $\FS$ if it is applied to it.

### 2015-12-11 2015/prove.py
Added documentation to the script; log single commands; new command syntax

@@ -1,43 +1,100 @@
 from itertools import chain
 import sys
 
+"""
+This script is part of the paper available at
+...
+
+It is used to test pairs of commands on filesystems and determine
+(1) if they break all filesystems, 
+(2) or they are equivalent to (or extended by) an empty sequence of commands
+(3) or they are equivalent to (or extended by) a single command
+(4) or they are equivalent to (or extended by) the same commands applied in reverse order.
+
+The commands are tested on minimal model of a filesystem that includes information
+about two nodes, their immediate surroundings that determine the tree-property
+the filesystem needs to satisfy, and the relationship between the nodes.
+
+The script considers the following possible relationships between the nodes
+to which the commands are applied:
+"""
+
+# Constants for Filesystem.rel and CommandPair.rel:
+DISTANT_PARENT     = 'DistantParent'     # p2 is an ancestor of p1 but not its parent
+DIRECT_PARENT      = 'DirectParent'      # p2 is the parent of p1 and p1 is not the only child
+DIRECT_PARENT_ONLY = 'DirectParentOnly'  # p2 is the parent of p1 and p1 is the only child
+DISTANT_CHILD      = 'DistantChild'      # p2 is the descendant of p1 but not its child
+DIRECT_CHILD       = 'DirectChild'       # p2 is the child of p2 and p2 is not the only child
+DIRECT_CHILD_ONLY  = 'DirectChildOnly'   # p2 is the child of p1 and p2 is the only child
+SAME               = 'Same'              # two paths are the same (used for command pairs)
+SEPARATE           = 'Separate'          # all other cases
+
+"""
+For each relationship, the script outputs 4 matrices according to the four properties
+to investigate. In each matrix, the rows represent the first command, and columns
+represent the second command. The notation for the commands is derived from the paper,
+and the first character notes the input type, while the second character notes the
+output type:
+b - Empty
+F - File
+D - Directory
+
+Each cell in the matrix has one of the following values:
+BR - the command pair breaks all filesystems (for (1) and (3))
+== - the pair is equivalent to the empty sequence, single command or reversed pair
+[[ - the pair is extended by the empty sequence, single command or reversed pair
+.. - none of the above is true    
+
[…]

### 2015-12-16 2015/prove.py
Added licence to the script

@@ -3,7 +3,7 @@ import sys
 
 """
 This script is part of the paper available at
-...
+https://github.com/csirmaz/AlgebraicSyncPaper
 
 It is used to test pairs of commands on filesystems and determine
 (1) if they break all filesystems, 
@@ -47,6 +47,27 @@ BR - the command pair breaks all filesystems (for (1) and (3))
 
 Finally, the script prints rules for substituting command pairs with single commands
 whenever the single command is not "break".
+
+
+Copyright (c) 2015 Elod Pal Csirmaz
+
+Permission is hereby granted, free of charge, to any person obtaining a copy
+of this software and associated documentation files (the "Software"), to deal
+in the Software without restriction, including without limitation the rights
+to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
+copies of the Software, and to permit persons to whom the Software is
+furnished to do so, subject to the following conditions:
+
+The above copyright notice and this permission notice shall be included in
+all copies or substantial portions of the Software.
+
+THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.  IN NO EVENT SHALL THE
+AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
+LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
+OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
+THE SOFTWARE.
 """
 
 # CONFIGURATION STARTS

### 2015-12-18 2015/algebra.tex
Description of the algebra

\subsection{Towards and Algebraic System}

Similarly to \cite{NREC} we can consider creating an algebra over command sequences
which will enable us to draw conclusions about the behaviours of the sequences
independently of filesystems.
This would provide a secondary model of (filesystem) commands above the model a filesystems
defined in this paper. The new model would no longer describe filesystems as such,
but use known relationships between sequences as its starting point.

In this algebra, equivalence ($\equiv$) and extension ($\eqext$) would become relations,
and logical rules involving them
(e.g. $ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $) would be re-cast as inference rules.
In addition to these, the \namecrefs{ax_separate_commute} listed in \cref{section_axioms}
would become axioms that we accept as true, and from which other true statements can be derived
using the inference rules.
Such a system can allow us to deduce, for example, whether two sequences are equivalent
or one extends the other
without reference to filesystems.

We note, however, that the \namecrefs{ax_separate_commute} to be used as axioms 
specify the relationships between the nodes
the commands act on, which would require a more complicated set of symbols to represent
in the algebra.
To avoid this, we think it will be more fruitful to regard commands (and sequences)
on different nodes as different, and, in effect, have nine times as many commands 
in the algebra as there are nodes in the namespace of the filesystems.
This allows us to reduce the number of types of symbols in our algebra, and regard
the \namecrefs{ax_separate_commute} not as axioms, but as templates for axioms
from which all axioms (for pairs of separate nodes, etc.) can be generated.

We expect that the soundness and completeness of such an algebra can be proven
similarly to the proofs described in \cite{NREC}.
Indeed, results in the current paper can serve as building blocks of such a proof:
the computer program used to check the \namecrefs{ax_separate_commute}
in effect proves the soundness of all axioms,
and \cref{simple_reorder_equiv} proves completeness in a limited sense.
It is also worth noting that the majority of proofs presented in this paper
do not actually refer to specific filesystems or the definition of commands,
but draw on known relationships and the
\namecrefs{ax_separate_commute} in \cref{section_axioms}.
In other words, many proofs are transferable to the algebra that we describe here.

In a more complete algebra from which the correctness and completeness
of reconciliation could also be derived,
one can also include symbols, inference rules and axioms for 
$\works{x}$ and $\worksc{x}{y}$.
We see proving the soundness and completeness of this extended algebra
an intriguing problem that is worthy of further research.

### 2015-12-18 2015/axioms.tex
Reconciliation policy comparison
Description of the algebra

@@
 
-The following concepts allow us to investigate sequences independently of filesystems.
+The following concepts 
+(which echo the ones defined in \cite{NREC})
+allow us to investigate sequences independently of filesystems.
 In the definitions, $A,B,S,T$ stand for arbitrary sequences of commands.
-These relations echo the ones defined in \cite{NREC:alg}.
 
@@
 Our aim is to derive information about the effects of sequences
-of commands independently of that actual filesystems.
+of commands independently of the actual filesystems.
 In order to make this possible, we investigate the smallest building
@@
 without any change in their overall effect.
-% TODO: Footnote: URL
+% TODO: Footnote: https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/2015/prove.py
 Our basis for this investigation was the model of filesystems introduced in this paper.
@@
    % bd>bd
-            \cbdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii} \\
+            \cbdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii} \\ % TODO all directories are the same?
    % fd>bf
@@
    % fd>bd
-            \cfdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii}
+            \cfdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii} % TODO all directories are the same?
    \end{gather*}

### 2015-12-18 2015/intro.tex
Description of the algebra

--- 2015-12-06 2015/paper.tex
@@
-\documentclass[12pt]{article}
-
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{centernot}
-\usepackage{tikz}
-\usepackage{cleveref}
-
-\input{macros}
-
-\title{Complete Algebraic File Synchronization}
-\author{Elod Pal Csirmaz}
-
-\begin{document}
-\maketitle
-\begin{abstract}
-Abstract goes here
-\end{abstract}
-
 \section{Introduction}
-
-% TODO Thank-you Laszlo Csirmaz, Bill Zissimopoulos
 
@@
 In this paper we
-continue the work in \cite{NREC:alg} and add to the theoretical understanding
+continue the work in \cite{NREC} and add to the theoretical understanding
 of synchronization based not on filesystem states, but filesystem changes or commands.
+
+% TODO operation-based vs state-based
 
@@
 % simpler reconciliation algorithm
-% proof of correctness
+% proof of correctness and completeness
 
-\section{Definitions}
-
-\input{def-filesystem}
-
-\input{def-commands}
-
-\input{axioms}
-
-% <<<<<<<< TODO Rewrite: no algebra
-%  about which we will reason
-% using our algebra.
-% We will aim to draw conclusions or judgements about commands and sequences of commands
-% based on the algebra we are aiming to construct.
-% For example, if we believe that two sequences of commands are equivalent as their effect
-% is the same, then we aim to be able to derive this from the axioms and inference rules of the
-% algebra.
-% As the algebra operates on commands only,
-% these judgements, by definition, need to hold regardless of the filesystem the commands are applied to.
-% Accordingly, we expect that the more information one encodes into the commands and the sequences,
-% the better predicitons we will be able to make using our algebra,
-% as then the commands and sequences will be more specific, and will select a smaller subset
-% of potential filesystems on which they can meaningfully operate.
-% >>>>>>>>>> to here
+% rigorous proof, non-trivial
 
 % Update detection
-% ----------------
-
-\section{Update detection}
-
-In a command-based reconciliation solution we assume that we have two sequences of commands
-$A$ and $B$ that have modified a single filesystem $\FS$ yielding two different replicas $\FS_A$ and $\FS_B$ that we
-need to reconcile. While it is conceivable that the sequences would be based on a record of
-all operations that modified the two filesystems, in most filesystem implementations
-such records are not implemented, and therefore we must construct suitable sequences
-by comparing $\FS_A$ and $\FS_B$ to their common ancestor, $\FS$. This is called update detection.
-
-A sequence that transforms $\FS$ into $\FS_A$ must contain at least one command on each node
-that changes between the two states of the filesystem. Also, it is easy to see that this is also
-sufficient, as there are commands available for any input and output value. 
-Specifically, if at node $n$, $\FS(n)=X'$ and $\FS_A(n)=Y'\neq X'$, then we add the command $\cxyaa{n}{Y'}$ to $A$
-where $X'\in\setvx{X}$ and $Y'\in\setvx{Y}$.
-
-To be able to describe such sequences better, let us introduce the following properties:
-
-\begin{mydef}{Minimal set or sequence.}
-A sequence or set of commands is minimal if it contains at most one command on every node.
-\end{mydef}
-
-\begin{mydef}{Simple set or sequence.}
-A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
-\end{mydef}
-
-This update detector therefore yields a simple set of commands because we only add a single command
-for each node, and we only add commands that are necessary, that is, there will be no 
-assertion commands in the set.
-
-The next step in generating the sequences is to order the commands collected.
-As this task is at the heart of reconciliation itself independently of update detection,
-we discuss it in the next section.
-Then, in \cref{update_works}, we prove that the resulting sequence actually
-works without breaking the filesystem.
-
-\input{ordering}
-
-\medskip
-
-% Correctness of update detection
-% -------------------------------
-
-Based on \cref{connected_changes} we can also show that
-the update detector does function as intended as:
-
-\begin{myth}\label{update_works}
-A sequence of commands returned by the update detector
-when comparing $\FS^*$ to the original $\FS$
-will not break $\FS$ if it is applied to it.
-\end{myth}
-\begin{proof}
-Let $\FS\neq\fsbroken$ be the original filesystem, and $\FS^*\neq\fsbroken$
-be the filesystem after the changes we intend to detect.
-Let us assume that some mechanism recorded all changes that occurred
-to $\FS$ until it reached the state $\FS^*$.
-Our set if commands is sufficient to record any change, as
-there are commands for every input and output type pair, therefore
-we know that the changes can be recorded as a sequence of commands $S$
-where $S\FS=\FS^*$.
-Note that $S$ will not contain assertion commands, as they do not
-represent an actual change in the filesystem.
-
-Therefore, \cref{connected_changes} applies to $S$ and we know
-if it contains commands on $\nn$ and $n$ where $\nn\descendant n$,
-then it also contains commands on nodes in between;
-which is equivalent to saying that if $\FS$ changed
-at node $\nn$ and $n$, then it had to change on the nodes in between.
-
-If so, then, similarly to what happens in the ordering algorithm,
-we can separate $S$ into components of commands on related nodes,
-as commands from separate components freely commute yielding an equivalent sequence.
-From the arguments above, we also know that each component
-must be made up of only desctruction or only construction pairs,
-but not a mixture of the two.
-This means that in each component, parents either strictly precede or succeed child nodes
-(as otherwise $S\equiv\cbrk$ would hold),
-from which it follows that once the components are separated
-in a new sequence $S'\equiv S$,
-commands on the same nodes are next to each other in $S'$.
-
-Based on \cref{ax_same_emptyseq,ax_same_singlec} there is
-an $S''\eqnrw S'$ in which multiple commands on the same nodes
-are simplified into a single command or an empty sequence,
-and therefore $S''$ is simple and $S\equiv S'\eqext S''$.
-It is easy to see that $S''$ must contain the same commands
-as the output of the update detector, $U$, as both are simple
-but reflect all changes between $\FS$ and $\FS^*$.
-If so, then $S''\in\orderset{U}$ and based on \cref{simple_reorder_equiv}
-we have
-$S\equiv S'\eqext S''\equiv U$, and as $S\FS = \FS^* \neq \fsbroken$,
-therefore $U\FS\neq\fsbroken$.
-\end{proof}
-
-\section{Reconciliation}
-
-\input{rec-intro}
-
-\input{works-inverse}
-
-\input{rec-sound}
-
-\input{rec-complete}
-
-% TODO
-TODO: About setting up an algebra / calculus
-
-TODO: next steps. multiple replicas
-
-\begin{thebibliography}{99}
-
-\bibitem{NREC:alg} Ramsey, Norman and Elod Csirmaz: {\it An algebraic approach to
-file synchronization...}
-
-\bibitem{BZ} Bill Zissimopoulos, personal communication, ...
-
-\end{thebibliography}
-
-\end{document}
+% - ordering
+% Reconciliation
+% - conditional operation & inverse sequences

### 2015-12-18 2015/paper.tex
Description of the algebra

--- 2015-12-06 2015/paper.tex
@@
 
-\section{Introduction}
-
-% TODO Thank-you Laszlo Csirmaz, Bill Zissimopoulos
-
-Synchronizing data structures, and filesystems in particular,
-is a task that we encounter more and more often in our world
-of multiple mobile devices, cloud solutions and distributed systems.
-Applications of synchronization ranges from
-solutions for end users who expect to access personal data seamlessly
-on multiple devices and personal clouds to geographically distributed server networks
-that need to synchronize themselves with low latency to serve the 
-same content.
-
-In this paper we
-continue the work in \cite{NREC} and add to the theoretical understanding
-of synchronization based not on filesystem states, but filesystem changes or commands.
-
-% Synchronization:
-% Main aim: apply updates (where possible) from other replicas
-% update detection -> conflict detection -> merging updates -> ordering updates -> apply updates from other replicas
-% Problems: conflict detection, ordering
-
-% ORDERING - because when taking updates from different replicas we get an essentially unordered set
-% Insight: (Prof. Norman Ramsey)
-% - updates where two orders (AB vs BA) are not equivalent are incompatible
-% - we only have a set of updates and need to create an order
-
-% New:
-% better command (instruction) set
-% simpler reconciliation algorithm
-% proof of correctness
+\input{intro}
 
@@
 
-% <<<<<<<< TODO Rewrite: no algebra
-%  about which we will reason
-% using our algebra.
-% We will aim to draw conclusions or judgements about commands and sequences of commands
-% based on the algebra we are aiming to construct.
-% For example, if we believe that two sequences of commands are equivalent as their effect
-% is the same, then we aim to be able to derive this from the axioms and inference rules of the
-% algebra.
-% As the algebra operates on commands only,
-% these judgements, by definition, need to hold regardless of the filesystem the commands are applied to.
-% Accordingly, we expect that the more information one encodes into the commands and the sequences,
-% the better predicitons we will be able to make using our algebra,
-% as then the commands and sequences will be more specific, and will select a smaller subset
-% of potential filesystems on which they can meaningfully operate.
-% >>>>>>>>>> to here
-
-% Update detection
-% ----------------
-
 \section{Update detection}
 
-In a command-based reconciliation solution we assume that we have two sequences of commands
-$A$ and $B$ that have modified a single filesystem $\FS$ yielding two different replicas $\FS_A$ and $\FS_B$ that we
-need to reconcile. While it is conceivable that the sequences would be based on a record of
-all operations that modified the two filesystems, in most filesystem implementations
-such records are not implemented, and therefore we must construct suitable sequences
-by comparing $\FS_A$ and $\FS_B$ to their common ancestor, $\FS$. This is called update detection.
-
-A sequence that transforms $\FS$ into $\FS_A$ must contain at least one command on each node
-that changes between the two states of the filesystem. Also, it is easy to see that this is also
-sufficient, as there are commands available for any input and output value. 
-Specifically, if at node $n$, $\FS(n)=X'$ and $\FS_A(n)=Y'\neq X'$, then we add the command $\cxyaa{n}{Y'}$ to $A$
-where $X'\in\setvx{X}$ and $Y'\in\setvx{Y}$.
-
-To be able to describe such sequences better, let us introduce the following properties:
-
-\begin{mydef}{Minimal set or sequence.}
-A sequence or set of commands is minimal if it contains at most one command on every node.
-\end{mydef}
-
-\begin{mydef}{Simple set or sequence.}
-A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
-\end{mydef}
-
-This update detector therefore yields a simple set of commands because we only add a single command
-for each node, and we only add commands that are necessary, that is, there will be no 
-assertion commands in the set.
-
-The next step in generating the sequences is to order the commands collected.
-As this task is at the heart of reconciliation itself independently of update detection,
-we discuss it in the next section.
-Then, in \cref{update_works}, we prove that the resulting sequence actually
-works without breaking the filesystem.
+\input{upd-def}
 
@@
 
-\medskip
-
-% Correctness of update detection
-% -------------------------------
-
-Based on \cref{connected_changes} we can also show that
-the update detector does function as intended as:
-
-\begin{myth}\label{update_works}
-A sequence of commands returned by the update detector
-when comparing $\FS^*$ to the original $\FS$
-will not break $\FS$ if it is applied to it.
-\end{myth}
-\begin{proof}
-Let $\FS\neq\fsbroken$ be the original filesystem, and $\FS^*\neq\fsbroken$
-be the filesystem after the changes we intend to detect.
-Let us assume that some mechanism recorded all changes that occurred
-to $\FS$ until it reached the state $\FS^*$.
-Our set if commands is sufficient to record any change, as
-there are commands for every input and output type pair, therefore
-we know that the changes can be recorded as a sequence of commands $S$
-where $S\FS=\FS^*$.
-Note that $S$ will not contain assertion commands, as they do not
-represent an actual change in the filesystem.
-
-Therefore, \cref{connected_changes} applies to $S$ and we know
-if it contains commands on $\nn$ and $n$ where $\nn\descendant n$,
-then it also contains commands on nodes in between;
-which is equivalent to saying that if $\FS$ changed
-at node $\nn$ and $n$, then it had to change on the nodes in between.
-
-If so, then, similarly to what happens in the ordering algorithm,
-we can separate $S$ into components of commands on related nodes,
-as commands from separate components freely commute yielding an equivalent sequence.
-From the arguments above, we also know that each component
-must be made up of only desctruction or only construction pairs,
-but not a mixture of the two.
-This means that in each component, parents either strictly precede or succeed child nodes
-(as otherwise $S\equiv\cbrk$ would hold),
-from which it follows that once the components are separated
-in a new sequence $S'\equiv S$,
-commands on the same nodes are next to each other in $S'$.
-
-Based on \cref{ax_same_emptyseq,ax_same_singlec} there is
-an $S''\eqnrw S'$ in which multiple commands on the same nodes
-are simplified into a single command or an empty sequence,
-and therefore $S''$ is simple and $S\equiv S'\eqext S''$.
-It is easy to see that $S''$ must contain the same commands
-as the output of the update detector, $U$, as both are simple
-but reflect all changes between $\FS$ and $\FS^*$.
-If so, then $S''\in\orderset{U}$ and based on \cref{simple_reorder_equiv}
-we have
-$S\equiv S'\eqext S''\equiv U$, and as $S\FS = \FS^* \neq \fsbroken$,
-therefore $U\FS\neq\fsbroken$.
-\end{proof}
+\input{upd-correct}
 
@@
 
-% TODO
-TODO: About setting up an algebra / calculus
+% TODO Conclusions
+
+\section{Further Research}
 
 TODO: next steps. multiple replicas
+
+\input{algebra}
 

### 2015-12-18 2015/upd-correct.tex
Description of the algebra

\subsection{The Correctness of Update Detection}

Based on \cref{connected_changes} we can also show that
the update detector does function as intended as:

\begin{myth}\label{update_works}
A sequence of commands returned by the update detector
when comparing the non-broken $\FS^*$ to the original $\FS$
will not break $\FS$ if it is applied to it.
\end{myth}
\begin{proof}
Let $\FS\neq\fsbroken$ be the original filesystem, and $\FS^*\neq\fsbroken$
be the filesystem after the changes we intend to detect.
Let us assume that some mechanism recorded all changes that occurred
to $\FS$ until it reached the state $\FS^*$.
Our set if commands is sufficient to record any change, as
there are commands for every input and output type pair, therefore
we know that the changes can be recorded as a sequence of commands $S$
where $S\FS=\FS^*$.
Note that $S$ will not contain assertion commands, as they do not
represent an actual change in the filesystem.

Therefore, \cref{connected_changes} applies to $S$ and we know
if it contains commands on $\nn$ and $n$ where $\nn\descendant n$,
then it also contains commands on nodes in between;
which is equivalent to saying that if $\FS$ changed
at node $\nn$ and $n$, then it had to change on the nodes in between.

If so, then, similarly to what happens in the ordering algorithm,
we can separate $S$ into components of commands on related nodes,
as commands from separate components freely commute yielding an equivalent sequence.
From the arguments above, we also know that each component
must be made up of only desctruction or only construction pairs,
but not a mixture of the two.
This means that in each component, parents either strictly precede or succeed child nodes
(as otherwise $S\equiv\cbrk$ would hold),
from which it follows that once the components are separated
in a new sequence $S'\equiv S$,
commands on the same nodes are next to each other in $S'$.

Based on \cref{ax_same_emptyseq,ax_same_singlec} there is
an $S''\eqnrw S'$ in which multiple commands on the same nodes
are simplified into a single command or an empty sequence,
and therefore $S''$ is simple and $S\equiv S'\eqext S''$.
It is easy to see that $S''$ must contain the same commands
as the output of the update detector, $U$, as both are simple
but reflect all changes between $\FS$ and $\FS^*$.
If so, then $S''\in\orderset{U}$ and based on \cref{simple_reorder_equiv}
we have
$S\equiv S'\eqext S''\equiv U$, and as $S\FS = \FS^* \neq \fsbroken$,
therefore $U\FS\neq\fsbroken$.
\end{proof}

### 2015-12-18 2015/upd-def.tex
Description of the algebra

In a command-based reconciliation solution we assume that we have two sequences of commands
$A$ and $B$ that have modified a single filesystem $\FS$ yielding two different replicas $\FS_A$ and $\FS_B$ that we
need to reconcile. While it is conceivable that the sequences would be based on a record of
all operations that modified the two filesystems, in most filesystem implementations
such records are not implemented, and therefore we must construct suitable sequences
by comparing $\FS_A$ and $\FS_B$ to their common ancestor, $\FS$. This is called update detection.

A sequence that transforms $\FS$ into $\FS_A$ must contain at least one command on each node
that changes between the two states of the filesystem. Also, it is easy to see that this is also
sufficient, as there are commands available for any input and output value. 
Specifically, if at node $n$, $\FS(n)=X'$ and $\FS_A(n)=Y'\neq X'$, then we add the command $\cxyaa{n}{Y'}$ to $A$
where $X'\in\setvx{X}$ and $Y'\in\setvx{Y}$.

To be able to describe such sequences better, let us introduce the following properties:

\begin{mydef}{Minimal set or sequence.}
A sequence or set of commands is minimal if it contains at most one command on every node.
\end{mydef}

\begin{mydef}{Simple set or sequence.}
A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
\end{mydef}

This update detector therefore yields a simple set of commands because we only add a single command
for each node, and we only add commands that are necessary, that is, there will be no 
assertion commands in the set.

The next step in generating the sequences is to order the commands collected.
As this task is at the heart of reconciliation itself independently of update detection,
we discuss it in the next section.
Then, in \cref{update_works}, we prove that the resulting sequence actually
works without breaking the filesystem.

### 2015-12-19 2015/algebra.tex
Minor improvements

@@
-\subsection{Towards and Algebraic System}
+\subsection{Towards and Algebraic System}\label{sec_algebra}
 
@@
 one can also include symbols, inference rules and axioms for 
-$\works{x}$ and $\worksc{x}{y}$.
+$\works{\seqset{X}}$ and $\worksc{\seqset{X}}{\seqset{Y}}$.
 We see proving the soundness and completeness of this extended algebra

### 2015-12-19 2015/def-commands.tex
Description of the algebra
Minor improvements

--- 2015-12-04 2015/def-commands.tex
@@
 
-...
+... TODO ...
 
@@
 $\FS(n)$ will be $\empt$. 
-However, from \cite{NREC:alg} we know that a useful set of axioms
-will in some cases need to distinguish between edits that result in directories ($edit(n,D)$) and
+However, from \cite{NREC} and \cite{CBNR} we know that a useful set of axioms
+will in some cases need to distinguish between, for example,
+edits that result in directories ($edit(n,D)$) and
 ones that result in files ($edit(n,F)$), and treat them as separate commands.
-Indeed, Bill Zissimopoulos suggested (\cite{BZ}) that extending this distinction to more commands
+Indeed, Bill Zissimopoulos suggested (TODO) that extending this distinction to more commands
 utlimately simplifies
@@
 At the same time, there is never any need to encode information about the
-\emph{exact} output value of a command,
+output \emph{value} of a command,
 as the success or failure of filesystem commands only depend on the types of values in the filesystem.
@@
 Notice, however, that the commands listed above also encode some information about 
-their input, the filesystem
-\emph{before} the command is applied; namely, $create(n,V)$ requires that there are no files
+their input, the state of the filesystem
+before the command is applied. In particular, $create(n,V)$ requires that there are no files
 or directories at $n$, while $edit(n,V)$ and $remove(n)$ require the opposite.
@@
 
-% TODO: tuple / quadruple
-We therefore propose to have a command for each pair of types.
-For want of a better system, we will name our commands by concatenating
-two of $\cchard$, $\ccharf$ and $\ccharb$, 
-where the left sign denotes the type of value
-required in the filesystem before the command is applied, and the right sign notes the type
-afterwards. For example, $mkdir(n,D)$ is $\cbdaa{n}{D}$, and $rmdir(n)$ is $\cdba{n}$.
+We therefore have four pieces of information related to each command:
+its input type, its output type, the node to which it is applied, and finally
+the value that it stores at the node.
+We will denote commands using quadruples that list these,
+and use $\cchard$, $\ccharf$ or $\ccharb$ to represent the different
+input and output types. In this system, $\cbdaa{n}{\vald}$ 
+is what represents $mkdir(n,\vald)$.
+Alternatively, we use a triple of the two types and a node if 
+there is only a single suitable output value for the given type (e.g. $\empt$).
+For example, $\cdba{n}$ represents $rmdir(n)$.
+
+\medskip
 
@@
 
-So that we could reason about sequences of commands that break every filesystem
-in the algebra, we introduce the command $\cbrk$ that simply breaks every filesystem.
+So that we could reason about sequences of commands that break every filesystem, 
+we introduce the command $\cbrk$ that simply breaks every filesystem.
 
@@
 by prefixing the command or sequence to it, for example: $\cbrk\FS$, $\cbdaa{n}{\vald}\FS$, 
-or $S\FS$ if $S$ is a sequence of commands.
+or simply $S\FS$ if $S$ is a sequence of commands.
 
@@
 $n\in\setn$ and $\valvy$ is a value of the appropriate type from $\setvx{Y}$.
-At times we omit $\valvy$ if there is only one suitable value.
 \[ \cxynv\FS = 
@@
 of their types with variables, as we did with $\cxynv$. In this context,
-if we write that $\cxy=\czw$, we mean that the input and output types % TODO needed?
-of the commands are the same ($X=Z$ and $Y=W$), while a full equiality 
+if we write that $\cxy=\czw$, we mean that the input and output types
+of the commands are the same ($X=Z$ and $Y=W$), while a full equality 
 ($\cxynv=\czwmv$)
 implies
-that their output value is also the same.
+that their nodes and output value is also the same.
 
@@
 
-For reasons also listed in \cite{NREC:alg}, in this paper we will not consider
+For reasons also listed in \cite{NREC}, in this paper we will not consider
 a $move$ or $rename$ command. Regarding the theoretical reasoning we aim to follow,

### 2015-12-19 2015/def-filesystem.tex
Minor changes
Minor improvements

@@
 
+% TODO namespace, data objects / inodes
+
 We model a filesystem using a function $\FS$ with a set of nodes (filesystem paths) $\setn$ as its domain,
-and a set of possible contents $\setv$ as its codomain:
+and a set of possible contents or values, $\setv$, as its codomain:
 \[ \FS : \setn \rightarrow \setv \] 
 In our model, $\setn$ 
-serves as a ``skeleton'' of the filesystem, and it
+serves as a namespace or ``skeleton'' for the filesystem, and it
 contains all possible nodes, including the ones where there is no file or directory.
-To mark empty nodes, $\setv$ contains a special element, $\empt$, which is the value of $\FS$ at these nodes.
+To model empty nodes, $\setv$ 
+contains a special element ($\empt$) which is the value of $\FS$ at these nodes.
 We consider the contents of files, as well as any meta-information of files

### 2015-12-19 2015/works-inverse.tex
Split paper into sections
Minor improvements

@@
 % -----
+
+\subsection{Conditional Operation and Inverse Sequences}
 
@@
 \begin{proof}
-We name this proposition an axiom (TODO) for the same reason as above,
+We name this proposition a \namecrefs{combine_independent_commands} for the same reason as above,
 but it is easy to provide an indirect proof based on our filesystem model.
@@
 The inverse of command $\cxynv$ is $\cxynv^{-1} = \caaaa{Y}{X}{n}{\valvx}$
-where $V_X$ is an arbitrary value from $\setvx{X}$.
+where $\valvx$ is an arbitrary value from $\setvx{X}$.
 We write $S^{-1}$ for the inverse of sequence $S$, which consists of the inverses of the commands in $S$
@@
 sequences---as functions mapping filesystems to filesystems---are
-essentially bijections over type-equality
+essentially bijections over type-equality ($\typeeq$)
 with the only ``sink'' being $\fsbroken$:

### 2015-12-19 2015/intro.tex
New introduction

@@
 
-Synchronizing data structures, and filesystems in particular,
-is a task that we encounter more and more often in our world
-of multiple mobile devices, cloud solutions and distributed systems.
-Applications of synchronization ranges from
-solutions for end users who expect to access personal data seamlessly
-on multiple devices and personal clouds to geographically distributed server networks
-that need to synchronize themselves with low latency to serve the 
-same content.
+Synchronization of data structures
+is a mechanism behind many services we take for granted today:
+accessing and editing calendar events, documents and spreadsheets
+on multiple devices, version control systems and
+geographically distributed internet and web services that
+guarantee a fast and responsive user experience.
 
-In this paper we
-continue the work in \cite{NREC} and add to the theoretical understanding
-of synchronization based not on filesystem states, but filesystem changes or commands.
+In this paper we investigate an operation- or command-based approach
+to filesystem synchronization.
+Presented with multiple copies (replicas) of a filesystem that have been independently modified,
+we regard the aim of the synchronizer to modify these replicas further
+to make them as similar as possible.
+The synchronization algorithm we describe
+follows the two main steps described by Balasubramaniam and Pierce (\cite{BP}):
+update detection, where we identify modifications that have been applied to the replicas
+since they diverged,
+and reconciliation, where we identify updates that can be propagated to other replicas and do so.
+The remaining updates, which could not be propagated, are conflicting updates;
+resolving these requires a separate system or human intervention.
 
-% TODO operation-based vs state-based
+In this paper we build on the work done 
+on command-based algebraic file synchronization
+in \cite{NREC} and add to the theoretical understanding
+of synchronization by providing rigorous proofs that the algorithms
+we describe work as intended
+and offer a solution in our framework that cannot be improved on.
 
-% Synchronization:
-% Main aim: apply updates (where possible) from other replicas
-% update detection -> conflict detection -> merging updates -> ordering updates -> apply updates from other replicas
-% Problems: conflict detection, ordering
+A central problem of command-based synchronisers during both update detection and reconciliation
+is ordering.
+If update detection is based on comparing the original state of the filesystem
+to its new state, then we can easily collect a set of updates,
+but we need to order these in a way that they could be applied in
+without causing an error 
+(for example, a directory needs to be created first before a file can be created under it).
+Similarly, during reconciliation when we consider all the updates that
+have been applied to the different replicas, we need to find a way of
+merging these and creating a global ordering that we can apply
+to the filesystems.
+In fact, an insight in \cite{NREC} is that
+if the ordering changes the effect of two commands,
+then under certain circumstances they are not compatible and will give rise to conflicts.
+Accordingly, in this paper command-pairs and their properties
+play a special role.
 
-% ORDERING - because when taking updates from different replicas we get an essentially unordered set
-% Insight: (Prof. Norman Ramsey)
-% - updates where two orders (AB vs BA) are not equivalent are incompatible
-% - we only have a set of updates and need to create an order
+In \cref{sec_def} we define a model of filesystems and a set of commands
+that we will use to describe updates and modifications.
+This is followed by investigating the properties and behaviors
+of command pairs in \cref{section_axioms}.
+\Cref{sec_update} describes update detection, and it is
+in \cref{ordering} that we describe how commands can be ordered
+and prove that under some conditions are valid orders
+have the same effect.
 
-% New:
-% better command (instruction) set
-% simpler reconciliation algorithm
-% proof of correctness and completeness
+Finally, \cref{sec_rec} defines our reconciliation algorithm
+and when two updates from different replicas give rise to a conflict.
+We then proceed to prove that the output of this algorithm
+is sound in the sense that 
+it can be applied to the replicas without causing an error,
+and that the described algorithm provides a complete solution
+inasmuch as no further updates can be applied under any circumstances.
+In order to be able to do this, we introduce
+the concept of {\emph conditional operation} of commands,
+and show that it has a number of highly convenient properties.
 
-% rigorous proof, non-trivial
+The approach in the present paper offers an improvement
+over rersults presented in \cite{NREC} in multiple ways.
+We introduce a new set of commands that is symmetric and
+captures more information about the updates.
+This has the effect that reasoning about commands
+becomes simpler as there are fewer edge cases,
+and more powerful as with the additional information
+content predictions made by the reasoning are more accurate.
+In fact, the new command set not only simplifies
+our reconciliation algorithm, but also makes it complete.
 
-% Update detection
-% - ordering
-% Reconciliation
-% - conditional operation & inverse sequences
+The previous work also lacked proofs that the update detection
+and reconciliation algorithms it presented work as intended,
+which we provide in the current paper.
+While the results are intuitive, providing rigorous proofs
+is far from trivial.
+During the process, we define a number of useful concepts
+and show their relationships and the properties they possess.
+In our view these construct an algebraic model
+that is worthy of interest and further research on its own.

### 2015-12-19 2015/axioms.tex
Minor improvements
New introduction
Fixed typos

@@
 
+% TODO Ref back to intro; further abstraction - no need to go the FS. break-all, equiv, extend
 So that we could describe the effects of commands on a filesystem, let us introduce some notation
@@
 these would function as meta-rules generating statements we would accept as true.
-See section (TODO) for more about such a model.
+See \cref{sec_algebra} for more about such a model.
 
@@
 \begin{myax}\label{ax_directparent_breaks}
-All other commands on a parent break every filsystem:
+All other commands on a parent break every filesystem:
 $\cxynv\cc\czwnnv \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$

### 2015-12-19 2015/def-commands.tex
Fixed typos

@@
 Indeed, Bill Zissimopoulos suggested (TODO) that extending this distinction to more commands
-utlimately simplifies
+ultimately simplifies
 the definition of conflicting commands, as our model will then able to predict the behavior of commands
@@
 
-We note that a command or a sequence of commands is applied to a filsystem
+We note that a command or a sequence of commands is applied to a filesystem
 by prefixing the command or sequence to it, for example: $\cbrk\FS$, $\cbdaa{n}{\vald}\FS$, 

### 2015-12-19 2015/intro.tex
Fixed typos

@@
 
-A central problem of command-based synchronisers during both update detection and reconciliation
+A central problem of command-based synchronizers during both update detection and reconciliation
 is ordering.
@@
 The approach in the present paper offers an improvement
-over rersults presented in \cite{NREC} in multiple ways.
+over results presented in \cite{NREC} in multiple ways.
 We introduce a new set of commands that is symmetric and

### 2015-12-19 2015/upd-correct.tex
Fixed typos

@@
 From the arguments above, we also know that each component
-must be made up of only desctruction or only construction pairs,
+must be made up of only destruction or only construction pairs,
 but not a mixture of the two.

### 2015-12-20 2015/def-filesystem.tex
Fixed typos
New figures

@@
 \[ \setv = \setb \cup \setf \cup \setd \]
-The tree propety can then be defined as
+The tree property can then be defined as
 \begin{align*}
@@
 This means that as we move down from the root of a tree of nodes,
-the types of values we encounter in the filesystem can only change according to the following
-transition diagram:
+the types of values we encounter in the filesystem can only change according to the
+transition diagram in \cref{fig_transition}.
 
-\input{type-transition}
+\begin{figure}[htb]
+\input{fig-type-transition}
+\caption{Transitions between types of values in a filesystem}\label{fig_transition}
+\end{figure}
 

### 2015-12-20 2015/fig-type-transition.tex
New figures

\begin{center}\begin{tikzpicture}
 [bend angle=45,
 sq/.style={rectangle,inner sep=3pt, minimum size=7mm,
fill=black!3,draw=black}]
\node[sq] (dnode) at (0,0) {$D$};
\node[sq] (fnode) at (2,0) {$F$};
\node[sq] (enode) at (4,0) {$\bot$};
%\node at (dnode) {$D$};
%\node at (fnode) {$F$};
%\node at (enode) {$\bot$};
\draw[->,line width=1.8pt] (dnode) -- (fnode);
\draw[->,line width=1.8pt] (fnode) -- (enode);
\draw[->,line width=1.5pt] (-0.35,0.35) arc(35:315:0.7cm and 0.55cm);
\draw[->,line width=1.5pt] (4.35,0.35) arc(145:-135:0.7cm and 0.55cm);
\draw[->,line width=1.5pt] (0.35,-0.35) arc(230:310:2.55cm and 1.4cm);
\end{tikzpicture}\end{center}

### 2015-12-20 2015/works-inverse.tex
New figures

@@
 \[ \worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \]
-the rest of the proof is illustrated by the diagram below
+the rest of the proof is illustrated by \cref{fig_invmove}
 where Dom($x$), the domain of $x$, represents the set of filesystems
@@
 
-\input{inverse-works} % TODO arrows too small
+\begin{figure}[htb]
+\input{fig-inverse-works}
+\caption{Proof of \cref{r_invmove}}\label{fig_invmove}
+\end{figure}
 

### 2015-12-20 2015/fig-type-transition.tex
Modified figures

@@
 \begin{center}\begin{tikzpicture}
- [bend angle=45,
+ [line width=1pt, bend angle=45,
  sq/.style={rectangle,inner sep=3pt, minimum size=7mm,
 fill=black!3,draw=black}]
-\node[sq] (dnode) at (0,0) {$D$};
-\node[sq] (fnode) at (2,0) {$F$};
-\node[sq] (enode) at (4,0) {$\bot$};
-%\node at (dnode) {$D$};
-%\node at (fnode) {$F$};
-%\node at (enode) {$\bot$};
-\draw[->,line width=1.8pt] (dnode) -- (fnode);
-\draw[->,line width=1.8pt] (fnode) -- (enode);
-\draw[->,line width=1.5pt] (-0.35,0.35) arc(35:315:0.7cm and 0.55cm);
-\draw[->,line width=1.5pt] (4.35,0.35) arc(145:-135:0.7cm and 0.55cm);
-\draw[->,line width=1.5pt] (0.35,-0.35) arc(230:310:2.55cm and 1.4cm);
+\node[sq] (dnode) at (0,0) {$\cchard$};
+\node[sq] (fnode) at (2,0) {$\ccharf$};
+\node[sq] (bnode) at (4,0) {$\ccharb$};
+\draw[-latex] (dnode) -- (fnode);
+\draw[-latex] (fnode) -- (bnode);
+\draw[-latex] (-0.35,  0.35) arc(35:315:0.7cm and 0.55cm);
+\draw[-latex] ( 4.35,  0.35) arc(145:-135:0.7cm and 0.55cm);
+\draw[-latex] ( 0.35, -0.35) arc(230:310:2.55cm and 1.4cm);
 \end{tikzpicture}\end{center}

### 2015-12-20 2015/def-filesystem.tex
Minor changes, added references

@@
 the types of values we encounter in the filesystem can only change according to the
-transition diagram in \cref{fig_transition}.
+transition diagram in \cref{fig_transition}, from directories ($\cchard$) to files ($\ccharf$)
+to empty nodes ($\ccharb$).
 

### 2015-12-20 2015/intro.tex
Minor changes, added references

@@
 to its new state, then we can easily collect a set of updates,
-but we need to order these in a way that they could be applied in
+but we need to order these in a way that they could be applied
+to the filesystems
 without causing an error 
@@
 play a special role.
+Other research also shows the essential nature of ordering:
+in IceCube multiple orders are tested to find an acceptable one \cite{KRSD},
+or in Bayou reconciling updates happens by redoing them in an acceptable order \cite{TTPDSH}.
 
@@
 in \cref{ordering} that we describe how commands can be ordered
-and prove that under some conditions are valid orders
+and prove that under some conditions all valid orders
 have the same effect.
 
-Finally, \cref{sec_rec} defines our reconciliation algorithm
-and when two updates from different replicas give rise to a conflict.
-We then proceed to prove that the output of this algorithm
+Finally, \cref{sec_rec} defines our reconciliation 
+and conflict detection algorithms.
+We then proceed to prove that the output of reconciliation
 is sound in the sense that 
@@
 In order to be able to do this, we introduce
-the concept of {\emph conditional operation} of commands,
+the concept of \emph{conditional operation} of sequences of commands,
 and show that it has a number of highly convenient properties.
@@
 becomes simpler as there are fewer edge cases,
-and more powerful as with the additional information
-content predictions made by the reasoning are more accurate.
+and more powerful as 
+predictions made by the reasoning are more accurate
+due to the additional information content.
 In fact, the new command set not only simplifies
@@
 and show their relationships and the properties they possess.
-In our view these construct an algebraic model
-that is worthy of interest and further research on its own.
+In our view these construct a special algebraic model
+that is worthy of interest and of further research on its own.

### 2015-12-20 2015/works-inverse.tex
Minor changes, added references

@@
 the rest of the proof is illustrated by \cref{fig_invmove}
-where Dom($x$), the domain of $x$, represents the set of filesystems
+where $\textrm{Dom}(x)$, the domain of $x$, represents the set of filesystems
 the sequence $x$ does not break, or neither of the sequences in the set $x$ breaks.

### 2015-12-21 2015/algebra.tex
References and improvements

@@
-\subsection{Towards and Algebraic System}\label{sec_algebra}
+\subsection{Towards an Algebra}\label{sec_algebra}
 
@@
 defined in this paper. The new model would no longer describe filesystems as such,
-but use known relationships between sequences as its starting point.
+but use known relationships between sequences of commands as its starting point.
 

### 2015-12-21 2015/axioms.tex
References and improvements

@@
 % TODO Ref back to intro; further abstraction - no need to go the FS. break-all, equiv, extend
+
 So that we could describe the effects of commands on a filesystem, let us introduce some notation
 and note some observations.
-
-The commands we aim to investigate do not occur in isolation:
-for example, when comparing filesystems to determine the commands needed to transform one into the other,
-we receive a set of commands with uncertain ordering.
-Applying commands to a filesystem, however, happens in time,
-so for this we need a sequence of commands.
+We already know that
+commands usually do not occur in isolation,
+and are applied to filesystems in time.
+Therefore we will investigate sequences of commands with a well-defined order
+(which form a free semigroup).
 We use $\cc$ to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence:
@@
 We write $\emptyseq$ for the empty sequence.
-
-TODO: Sequences of commands, in the usual way,  form a free
-semigroup
 
@@
 
-We methodically investigated of all possibilities using a computer program
+We methodically investigated of all possibilities using a computer 
+program\footnote{The program is accessible on-line at \\
+https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/2015/prove.py.}
 to determine
@@
 without any change in their overall effect.
-% TODO: Footnote: https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/2015/prove.py
 Our basis for this investigation was the model of filesystems introduced in this paper.
@@
    \begin{gather*}
-   % bd>bf
             \cbdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
-   % bd>bd
             \cbdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii} \\ % TODO all directories are the same?
-   % fd>bf
             \cfdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
-   % fd>bd
             \cfdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii} % TODO all directories are the same?
@@
    \begin{gather*}
-   % fb<db ??
             \cfba{n}\cc  \cdba{\nn} \\
-   % fb<df ??
             \cfba{n}\cc  \cdfaa{\nn}{\valf} \\
-   % db<db ??
             \cdba{n}\cc  \cdba{\nn} \\
-   % db<df ??
             \cdba{n}\cc  \cdfaa{\nn}{\valf}
@@
 and there must also be only one possible value for their output.
-Accordingly, in our current algebra, $\cbba{n}$ and $\cdda{n}$ are the only two assertion commands,
-and we do not note their output value as it is determined.
+Accordingly, in our current algebra, $\cbba{n}$ and $\cdda{n}$ are the only two assertion commands.
 \end{mydef}

### 2015-12-21 2015/def-commands.tex
References and improvements

@@
 A usual set of commands, based on the most frequent tools implemented by filesystems,
-might be $create(n,V)$, $edit(n,V)$ and $remove(n)$ where $n\in\setn$ and $V\in\setv$ (but $V\neq\empt$).
+might be $create(n,\valv)$, $edit(n,\valv)$ and $remove(n)$ 
+where $n\in\setn$ and $\valv\in\setv$ (but $\valv\neq\empt$).
 Regarding their output, that is, the state of the filesystem at $n$
@@
 will in some cases need to distinguish between, for example,
-edits that result in directories ($edit(n,D)$) and
-ones that result in files ($edit(n,F)$), and treat them as separate commands.
+edits that result in directories ($edit(n,\vald)$) and
+ones that result in files ($edit(n,\valf)$), and treat them as separate commands.
 Indeed, Bill Zissimopoulos suggested (TODO) that extending this distinction to more commands
@@
 more precisely.
-In other words, encoding the type of the output ($D$, $F$ or $\empt$) in the commands is definitely useful.
+In other words, encoding the type of the output ($\cchard$, $\ccharf$ or $\ccharb$) in the commands is definitely useful.
 At the same time, there is never any need to encode information about the
@@
 their input, the state of the filesystem
-before the command is applied. In particular, $create(n,V)$ requires that there are no files
-or directories at $n$, while $edit(n,V)$ and $remove(n)$ require the opposite.
+before the command is applied. In particular, $create(n,\valv)$ requires that there are no files
+or directories at $n$, while $edit(n,\valv)$ and $remove(n)$ require the opposite.
 This creates an arbitrary asymmetry where
@@
 implies
-that their nodes and output value is also the same.
+that their nodes and output values are also the same.
+
+\medskip
 

### 2015-12-21 2015/def-filesystem.tex
References and improvements

@@
 \subsection{The Filesystem}
-
-% TODO namespace, data objects / inodes
 
@@
 Another simplification we will assume in this paper is regarding directories.
-As Bill Zissimopoulos pointed out (\cite{BZ}), we often do not want to consider metadata stored in
+As Bill Zissimopoulos pointed 
+out,\footnote{Bill Zissimopoulos, personal communication, August 2015.} we often do not want to consider metadata stored in
 directories during synchronization. In other words, the contents of directories are all equal,
 which can be modelled by assuming that $|\setd|=1$.
-% This also creates a convenient symmetry where there is only a single value
-% for each type that can be repeated as we move from a path to its child ($D$ and $\empt$).

### 2015-12-21 2015/paper.tex
New introduction
Minor changes, added references
References and improvements

@@
 
-\section{Definitions}
+\section{Definitions}\label{sec_def}
 
@@
 
-\section{Update detection}
+\section{Update Detection}\label{sec_update}
 
@@
 
-\section{Reconciliation}
+\section{Reconciliation}\label{sec_rec}
 
@@
 
-\bibitem{NREC} Ramsey, Norman and Elod Csirmaz: {\it An algebraic approach to
-file synchronization...}
-
-\bibitem{CBNR} Constantin Berzan, Norman Ramsey: Summer Scholars Technical Report
-Tufts University, Medford, MA, USA, 2010
-http://thirld.com/files/summerscholars\_techreport.pdf
-Accessed 29 November 2015
+\input{references}
 

### 2015-12-21 2015/rec-sound.tex
References and improvements

@@
 so that all marked commands would be at its beginning.
-If so, then based on \cref{worksextpostfix}
-$\worksc{S^*}{\seqset{C}}$ as $\worksc{S'}{\seqset{C}}$ and $S'=S^*\cc S_0$ 
+If so, then 
+$\worksc{S^*}{\seqset{C}}$ 
+based on \cref{worksextpostfix}
+as $\worksc{S'}{\seqset{C}}$ and $S'=S^*\cc S_0$ 
 where $S_0$ contains the remaining (conflicting) commands.

### 2015-12-21 2015/references.tex
References and improvements

\bibitem{NREC} 
Norman Ramsey and Elod Csirmaz,
``An Algebraic Approach to File Synchronization,''
in \emph{Proceedings of the Joint 8\textsuperscript{th} European Software Engineering Conference 
and 9\textsuperscript{th} ACM SIGSOFT Symposium on the Foundations of Software Engineering,}
New York: ACM, 2001, pp. 175--185.

\bibitem{CBNR} 
Constantin Berzan and Norman Ramsey,
``Summer Scholars Technical Report,''
Medford, MA: Tufts University, 2010.
Accessed 29 November 2015.
http://thirld.com/files/summerscholars\_techreport.pdf.

% 5
\bibitem{TTPDSH}
% D. B. Terry and M. M. Theimer and Karin Petersen and A. J. Demers and M. J. Spreitzer and C. H. Hauser
D. B. Terry et al.,
``Managing Update Conflicts in Bayou, a Weakly Connected Replicated Storage System,''
in \emph{Proceedings of the Fifteenth ACM Symposium on Operating Systems Principles,}
New York, NY: ACM, 1995, pp. 172--182.

% 4
\bibitem{BP}
S. Balasubramaniam and Benjamin C. Pierce,
``What is a File Synchronizer?''
in \emph{Proceedings of the 4\textsuperscript{th} Annual 
ACM/IEEE International Conference on Mobile Computing and Networking,}
New York: ACM, 1998, pp. 98--108.

% 3
\bibitem{KRSD}
Anne-Marie Kermarrec and Antony Rowstron and Marc Shapiro and Peter Druschel,
``The IceCube Approach to the Reconciliation of Divergent Replicas,''
in \emph{Proceedings of the Twentieth Annual ACM Symposium on Principles of Distributed Computing,}
New York: ACM, 2001, pp. 210--218.

### 2015-12-22 2015/comparisons.tex
More improvements and references

--- 2015-12-21 2015/paper.tex
@@
-\documentclass[12pt]{article}
-
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{centernot}
-\usepackage{tikz}
-\usepackage{cleveref}
-
-\input{macros}
-
-\title{Complete Algebraic File Synchronization}
-\author{Elod Pal Csirmaz}
-
-\begin{document}
-\maketitle
-\begin{abstract}
-Abstract goes here
-\end{abstract}
-
-\input{intro}
-
-\section{Definitions}\label{sec_def}
-
-\input{def-filesystem}
-
-\input{def-commands}
-
-\input{axioms}
-
-\section{Update Detection}\label{sec_update}
-
-\input{upd-def}
-
-\input{ordering}
-
-\input{upd-correct}
-
-\section{Reconciliation}\label{sec_rec}
-
-\input{rec-intro}
-
-\input{works-inverse}
-
-\input{rec-sound}
-
-\input{rec-complete}
-
 \section{Comparisons}
 
+\subsection{Liberal and conservative Reconciliation}
 We consider the reconciliation algorithm described here an improvement over
@@
 on preceding commands, and, to use the above terminology, implements a fully liberal policy.
-
-% TODO Conclusions
-
-\section{Further Research}
-
-TODO: next steps. multiple replicas
-
-\input{algebra}
-
-\section{Acknowledgments}
-
-I thank Laszlo Csirmaz for his invaluable input on previous drafts of this paper,
-and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.
-
-\begin{thebibliography}{99}
-
-\input{references}
-
-\end{thebibliography}
-
-\end{document}

### 2015-12-22 2015/def-commands.tex
More improvements and references

@@
 
-Next we need to define commands on the filesystem.
+Next we define commands on the filesystem.
+As described above, we aimed to select a set of commands
+that capture as much information as possible
+about the operations, and is also symmetric.
+We start by summarizing our reasons for doing so.
 
-... TODO ...
-
-Let us consider what kind of information may be encoded in the commands.
+Let us consider what kind of information is usually encoded in filesystem operations.
 A usual set of commands, based on the most frequent tools implemented by filesystems,
-might be $create(n,\valv)$, $edit(n,\valv)$ and $remove(n)$ 
+may be $create(n,\valv)$---create the object $\valv$ at node $n$,
+$edit(n,\valv)$---modify the object at $n$ to become $\valv$,
+and $remove(n)$---delete the object at node $n$; 
 where $n\in\setn$ and $\valv\in\setv$ (but $\valv\neq\empt$).
@@
 edits that result in directories ($edit(n,\vald)$) and
-ones that result in files ($edit(n,\valf)$), and treat them as separate commands.
-Indeed, Bill Zissimopoulos suggested (TODO) that extending this distinction to more commands
-ultimately simplifies
+ones that result in files ($edit(n,\valf)$), and treat them as separate commands,
+as their behaviors when combined with other commands are quite different.
+Indeed, Bill Zissimopoulos' work 
+demonstrated\footnote{Bill Zissimopoulos, personal communication, August 2015.}
+that extending this distinction to more commands ultimately simplifies
 the definition of conflicting commands, as our model will then able to predict the behavior of commands
@@
 there is now more information encoded into commands about their output than about their input.
-In line with the aim to encode as much information as possible in the commands, % TODO Where is this mentioned?
-and in order to resolve this asymmetry, we propose a set of commands that encode
+As, based on the above, we expect that encoding more information in the commands
+results in a model with greater predictive powers,
+and in order to resolve this asymmetry, 
+we propose a set of commands that encode
 the type of the original state of $\FS(n)$ as well.
@@
 and use $\cchard$, $\ccharf$ or $\ccharb$ to represent the different
-input and output types. In this system, $\cbdaa{n}{\vald}$ 
-is what represents $mkdir(n,\vald)$.
+input and output types. For example, $\cbdaa{n}{\vald}$ 
+will represent $mkdir(n,\vald)$.
 Alternatively, we use a triple of the two types and a node if 
 there is only a single suitable output value for the given type (e.g. $\empt$).
-For example, $\cdba{n}$ represents $rmdir(n)$.
+That is, $\cdba{n}$ will represent $rmdir(n)$.
 
@@
 
-The exact behavior of our commands is as follows:
+The exact behavior of the commands is as follows:
 \begin{itemize}
@@
 
-% Simplifications
-% ---------------
+% Simplification
+% --------------
 

### 2015-12-22 2015/def-filesystem.tex
More improvements and references

@@
 The nodes form a disjoint union of rooted directed trees.
+Tao et al. in \cite{TSR} describe a similar filesystem model, although
+they also model inodes and restrict the filesystem to a just single tree.
 \begin{mydef}
@@
 
-Another simplification we will assume in this paper is regarding directories.
+% Simplification
+% --------------
+
+A simplification we will assume in this paper is regarding directories.
 As Bill Zissimopoulos pointed 
-out,\footnote{Bill Zissimopoulos, personal communication, August 2015.} we often do not want to consider metadata stored in
-directories during synchronization. In other words, the contents of directories are all equal,
+out,\footnote{Bill Zissimopoulos, personal communication, August 2015.} 
+we often do not want to consider metadata stored in
+directories (e.g. permission settings) during synchronization,
+as these are not generally understood by users,
+and, if needed, conflict resolution on these settings can be easily automated.
+In other words, the contents of directories are all equal,
 which can be modelled by assuming that $|\setd|=1$.

### 2015-12-22 2015/ordering.tex
Minor changes
Minor improvements
More improvements and references

@@
-\section{Ordering commands}\label{ordering}
+\subsection{Ordering commands}\label{ordering}
 
@@
 and if yes, what order,
-in which updates from multiple replicas can be applied to a filesystem.
+in which updates from different replicas can be applied to a filesystem.
 
@@
 and which contains commands on $n$ and $\nn$ where $\nn\descendant n$
-but $\nn\neq\parent(n)$, then the set must also contain a commands
+but $\nn\neq\parent(n)$, then the set must also contain a command
 on each node between $n$ and $\nn$.
@@
 We prove that under the given conditions, the set must contain a command on $\parent(n)$.
-Then, by repeating this statement, we how that the set must contain commands on every
+Then, by repapplying this result, we how that the set must contain commands on every
 ancestor of $n$ up to $\nn$.
@@
 This is not a problem in the case of components containing a single command only.
-(Note that $\cff$ can only appear in a component of one.)
+(Note that a file-to-file command ($\cff$) can only appear in a component of one.)
 

### 2015-12-22 2015/paper.tex
More improvements and references

@@
 
-\section{Comparisons}
-
-We consider the reconciliation algorithm described here an improvement over
-the one derved during our previous research (see \cite{NREC})
-as the previous algorithm not only fails to propagate all possible commands
-wherever it is possible (that is, where it does not break the filesystem),
-but the current algorithm is also simpler.
-This is because the previous reconciliation algorithm excludes
-commands from being propagated which must be preceded by a command that conflicts.
-
-The former observation is supported by Berzan and Ramsey, who in \cite{CBNR} 
-describe between different reconciliation policies.
-The liberal (maximal) policy propagates all updates to all replicas where
-the command does not break the filesystem, while a conservative policy
-refrains from updating any node that is below a node with conflicting commands.
-They show that the reconciliation algorithm in \cite{NREC} implements
-an intermediate policy as one can easily construct two- or three-replica scenarios
-where an update could clearly be propagated, but it is excluded.
-To rephrase the example in \cite{CBNR}, consider the following two
-update sequences that have been applied to replicas $\FS_A$ and $\FS_B$:
-\begin{align*}
-A&=\cbdaa{\nn}{\valdi}\cc\cbfaa{n}{\valf} \\
-B&=\cbdaa{\nn}{\valdii}
-\end{align*}
-where $\parent(n)=\nn$ (\cite{NREC} did not require all directories to have the same value).
-Clearly $\cbfaa{n}{\valf}$ could be applied to $\FS_B$, but it is not as
-it must be preceded by creating the directory, which conflicts with the same operation in $B$
-due to the different value.
-(Introducing a third replica which has not changed at all further complicates the picture.)
-The current algorithm no longer needs to specify that there can be no conflicts
-on preceding commands, and, to use the above terminology, implements a fully liberal policy.
-
-% TODO Conclusions
+\input{comparisons}
 
@@
 \input{algebra}
+
+\section{Conclusions}
+
+% TODO
+Conclusions go here
 

### 2015-12-23 2015/axioms.tex
Further research, conflict comparison, renaming unrelated to incomparable

@@
 \begin{mydef}{$n\unrel m$.}
-We write $n\unrel m$, or ``$n$ and $m$ are unrelated'' if $n\not\descendantEq m$ and $n\not\ancestorEq m$.
+We write $n\unrel m$, or ``$n$ and $m$ are incomparable'' if $n\not\descendantEq m$ and $n\not\ancestorEq m$.
 \end{mydef}
@@
 \begin{myax}\label{ax_separate_commute}
-Commands on unrelated nodes commute:
+Commands on incomparable nodes commute:
 $\cxynv\cc\czwmv \equiv \czwmv\cc\cxynv$ where $n\unrel m$.
@@
 \begin{myax}\label{ax_separate_nobreaks}
-Commands on unrelated nodes do not break every filesystem:
+Commands on incomparable nodes do not break every filesystem:
 $\cxynv\cc\czwmv \nequiv \cbrk$ where $n\unrel m$.

### 2015-12-23 2015/comparisons.tex
Further research, conflict comparison, renaming unrelated to incomparable

@@
 on preceding commands, and, to use the above terminology, implements a fully liberal policy.
+
+\subsection{Comparing Definitions of Conflicts}
+As a test of the proposed reconciliation algorithm, we compare our definition of conflicting
+updates to how conflicts are defined by Balasubramaniam and Pierce (\cite{BP}).
+The update detector described in \cite{BP} provides a safe estimate of nodes
+(paths) at which updates occurred.
+It marks some nodes as \emph{dirty} in a way that we know that at non-dirty paths
+the filesystem has not changed between its original and current states
+(see their Definition 3.1.1).
+The \emph{dirty} marks are also up-closed, that is, all ancestor nodes of a dirty node
+are also dirty (their Fact 3.1.3).
+And finally, a conflict is detected between replicas $\FS_A$ and $\FS_B$ at node $n$
+if $n$ is marked as dirty in both $\FS_A$ and $\FS_B$, and
+$\FS_A(n)\neq\FS_B(n)$, and $n$ does not point to a directory in both replicas
+($\FS_A(n)\not\in\setd \vee \FS_B(n)\not\in\setd$; see section 4.1 in \cite{BP}).
+
+It can be easily seen that not all conflicts detected based on the above definition
+entails a conflict based on our system; that is, \cite{BP} describes a more
+conservative policy.
+For example, if $\nn=\parent(n)$ and $\FS(\nn)=\vald$ and $\FS(n)=\valf$, and
+the two replicas are derived in the following way:
+\begin{gather*}
+\FS_A = \cfba{n} \cc \cdba{\nn} \FS \\
+\FS_B = \cfba{n} \FS,
+\end{gather*}
+then $\nn$ is dirty in both replicas:
+in $\FS_A$ it was modified, and in $\FS_B$ one of its descendants was modified.
+Moreover, $\FS_A(\nn)\neq\FS_B(\nn)$ and $\FS_A(\nn)=\empt\not\in\setd$,
+and therefore a conflict is detected at $\nn$.
+Our reconciliation algorithm detects no conflicts;
+instead, it propagates $\cdba{\nn}$ to $\FS_B$, which we think is as expected
+and desired.
+
+At the same time, it can be shown that if our command-based reconciler
+detects a conflict, it entails a conflict based on the \emph{dirty}
+property.
+Balasubramaniam and Pierce also suppose that all directories are equal,
+therefore we are safe to continue to assume that $|\setd|=1$.
+Let $A$ and $B$ be two simple sequences returned by the update detector
+for the two replicas $\FS_A$ and $\FS_B$.
+A conflict between the commands $\cxynv\in A$ and $\czwmv\in B$
+means that even though $\cxynv\in A\setminus B$
+and $\czwmv\in B\setminus A$, they cannot be included in
+$\reca$ and $\recb$, respectively, because
+$\cxynv\nindep\czwmv$ (see \cref{def:reconciliation}).
+
+From \cref{incomparable_is_independent} we therefore know that $n\nunrel m$.
+Without loss of generality we can assume that $n\descendantEq m$.
+From this we see that $n$ is \emph{dirty} in both $\FS_A$ and $\FS_B$,
+as the filesystem changes at $n$ in $\FS_A$ and at a descendant in $\FS_B$
+(none of the commands are assertion commands).
+
+We now only need to show that $\FS_A(n)\neq\FS_B(n)$, as from this we will also
+know that at least one of these values is not a directory.
+If $n=m$, this follows from the fact that $\cxynv\neq\czwmv$ (as they are not in
+$A\cap B$), which in this case can only be if $\FS_A(n)=\valvy\neq\valvw=\FS_B(n)$.
+If $n\descendant m$ and there is no command on $n$ in $B$, then it is also
+true as $\cxynv$ is not an assertion command, and therefore 
+$\FS_A(n)\neq\FS(n)=\FS_B(n)$.
+The final case is when there is a command on $n$ in $B$; let it be $\cqrnv$.

### 2015-12-23 2015/ordering.tex
Further research, conflict comparison, renaming unrelated to incomparable

@@
 Then we can split $U$ into a maximum number of disjunct subsets
-(components) so that the nodes of two commands from two different subsets are unrelated.
+(components) so that the nodes of two commands from two different subsets are incomparable.
 These will simply be the components of the subset of the node forest that contains the nodes affected by the set.
@@
 a $\czwmv$ where $n\descendant m$, potentially followed by commands
-on unrelated paths, and then followed by $\cxynv$.
+on incomparable nodes, and then followed by $\cxynv$.
 From \cref{ax_separate_commute} we know we can convert this sequence
-to an equivalent sequence by swapping the unrelated commands with
+to an equivalent sequence by swapping the commands on incomparable nodes with
 $\czwmv$, which sequence would therefore have the commands on

### 2015-12-23 2015/paper.tex
Further research, conflict comparison, renaming unrelated to incomparable

@@
 
-\section{Further Research}
-
-TODO: next steps. multiple replicas
-
 \input{algebra}
 
-\section{Conclusions}
+\section{Conclusions and Further Research}
 
 % TODO
-Conclusions go here
+Conclusions go here -- same approach to other systems
+\medskip
+
+% Further research
+
+Apart from constructing an algebra,
+there are many other ways in which further work can extend the current results.
+We think one of the most interesting extensions would be to
+consider reconciling not only two, but more replicas in a single step and
+prove the correctness of the algorithm proposed.
+A related problem is to model cases where reconciliation cannot
+complete fully (due to a system or network failure, for example)
+or if only a subset of the replicas are reconciled,
+both of which would result in a state where different replicas
+have different common ancestors, that is,
+the updates specific to the replicas start from different points
+in the update history of the filesystem.
+Identifying the information one needs to keep to perform
+update detection is such cases and devising a suitable algorithm
+will be an essential part of any implementation of a reconciler
+based on the ideas presented here.
+
+An extension of these results could also entail relaxing
+the simplifying assumptions we used.
+Identifying which results depend on assuming that $|\setd|=1$
+and devising updated proofs or algorithms,
+or a pre-processing step that reconciles meta-information in directories
+can enable the algebraic system or an implementation
+to identify and resolve a wider range of conflicts.
+Similarly, designing pre- and post-processors that
+present certain changes not as removal and creation of a node,
+but as a rename,
+could contribute to the user-friendliness of the reconciler
+and help avoid human error.
 

### 2015-12-23 2015/rec-sound.tex
Further research, conflict comparison, renaming unrelated to incomparable

@@
 \cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
-we know that these commands can only be on unrelated paths or form a construction or destruction pair.
+we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
 In the first case, swapping the commands results in a sequence equivalent to $A$,
@@
 \cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
-we know that these commands can only be on unrelated paths or form a construction or destruction pair.
+we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
 In the first case, swapping the commands results in a sequence equivalent to $S$;
@@
 from {\condDisj} that $\cqrov\neq\czwmv$.
-Therefore, based on \cref{unrelated_is_independent} we know this means that
+Therefore, based on \cref{incomparable_is_independent} we know this means that
 either $m\descendantEq o$ or $o\descendantEq m$.
 From {\condApr} we also know that $\cxynv\indep \cqrov$,
-and so because of \cref{unrelated_is_independent},
+and so because of \cref{incomparable_is_independent},
 $n\unrel o$.

### 2015-12-23 2015/works-inverse.tex
Further research, conflict comparison, renaming unrelated to incomparable

@@
 
-\begin{mylem}\label{unrelated_is_independent}
-Two different commands that are not assertion commands are independent iff the nodes they change are unrelated:
+\begin{mylem}\label{incomparable_is_independent}
+Two different commands that are not assertion commands are independent iff the nodes they change are incomparable:
 \[ \cxynv\indep\czwmv \Leftrightarrow n\unrel m \]
@@
 but we know $\FS(m)\in\setvx{W}$ and so
-$(\cxynv\FS)(m)\in\setvx{W}$ as based on \cref{unrelated_is_independent}, $n\neq m$.
+$(\cxynv\FS)(m)\in\setvx{W}$ as based on \cref{incomparable_is_independent}, $n\neq m$.
 Third, if the new filesystem violates the tree property.
@@
 
-From \cref{unrelated_is_independent,ax_separate_commute} we know that
+From \cref{incomparable_is_independent,ax_separate_commute} we know that
 the commands in $S$ and $T$ pairwise commute, and so any sequence

### 2015-12-23 2015/axioms.tex
Comparison proof and text improvements

@@
 (which form a free semigroup).
-We use $\cc$ to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence:
+We use ``$\cc$'' to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence:
 $S=\cbdaa{n}{\vald}\cc\cbfaa{m}{\valf}$, or $S'=S\cc\cbba{o}$.
@@
 during synchronization, and what commands will never be compatible.
+Below we list a number of statements derived using this method.
 
-Below we list a number of statements derived using this method.
-Although they can be proven by investigating all relevant possibilities
-in a filesystem, we refer to these as axioms because in a secondary algebraic model
-that describes commands without reference to an underlying filesystem,
-these would function as meta-rules generating statements we would accept as true.
-See \cref{sec_algebra} for more about such a model.
+\bigskip
 
-\medskip
-
+\noindent
 Pairs of commands in general have the form
@@
             \cbdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
-            \cbdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii} \\ % TODO all directories are the same?
+            \cbdaa{\nn}{\vald}\cc  \cbdaa{n}{\vald} \\
             \cfdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
-            \cfdaa{\nn}{\valdi}\cc  \cbdaa{n}{\valdii} % TODO all directories are the same?
+            \cfdaa{\nn}{\vald}\cc  \cbdaa{n}{\vald}
    \end{gather*}
@@
 and there must also be only one possible value for their output.
-Accordingly, in our current algebra, $\cbba{n}$ and $\cdda{n}$ are the only two assertion commands.
+Accordingly, $\cbba{n}$ and $\cdda{n}$ are the only two assertion commands.
 \end{mydef}
@@
 where $\nn\descendant n$ and $\cxy\neq\cdd$.
+(Note that this and next rule is true because the assertion command is
+adjacent to the original command.)
 \end{myax}

### 2015-12-23 2015/comparisons.tex
Comparison proof and text improvements

--- 2015-12-22 2015/comparisons.tex
@@
 \subsection{Liberal and conservative Reconciliation}
+
 We consider the reconciliation algorithm described here an improvement over
@@
 on preceding commands, and, to use the above terminology, implements a fully liberal policy.
+
+\subsection{Comparing Definitions of Conflicts}
+
+As a test of the proposed reconciliation algorithm, 
+we compare our definition of conflicting
+updates to how conflicts are defined by Balasubramaniam and Pierce
+in their state-based approach (\cite{BP}).
+The update detector described in \cite{BP} provides a safe estimate of nodes
+(paths) at which updates occurred.
+It marks some nodes as \emph{dirty} in a way that we know that at non-dirty nodes
+the filesystem have not changed between their original and current states
+(see Definition 3.1.1 in \cite{BP}).
+The \emph{dirty} marks are also up-closed, that is, all ancestor nodes of a dirty node
+are also dirty (Fact 3.1.3 in \cite{BP}).
+And finally, a conflict is detected between replicas $\FS_A$ and $\FS_B$ at node $n$
+if $n$ is marked as dirty in both $\FS_A$ and $\FS_B$, and
+$\FS_A(n)\neq\FS_B(n)$, and $n$ does not point to a directory in both replicas
+($\FS_A(n)\not\in\setd \vee \FS_B(n)\not\in\setd$; see section 4.1 in \cite{BP}).
+
+It can be easily seen that not all conflicts detected based on the above definition
+entails a conflict based on our system; that is, \cite{BP} describes a more
+conservative policy.
+For example, if $\nn=\parent(n)$ and $\FS(\nn)=\vald$ and $\FS(n)=\valf$, and
+the two replicas are derived in the following way:
+\begin{gather*}
+\FS_A = \cfba{n} \cc \cdba{\nn} \FS \\
+\FS_B = \cfba{n} \FS,
+\end{gather*}
+then $\nn$ is dirty in both replicas:
+in $\FS_A$ it was modified, and in $\FS_B$ one of its descendants was modified.
+Moreover, $\FS_A(\nn)\neq\FS_B(\nn)$ and $\FS_A(\nn)=\empt\not\in\setd$,
+and therefore a conflict is detected at $\nn$.
+Our reconciliation algorithm detects no conflicts;
+instead, it propagates $\cdba{\nn}$ to $\FS_B$, which we think is as expected
+and desired.
+
+At the same time, it can be shown that if our command-based reconciler
+detects a conflict, it entails a conflict in the state-based reconciler.
+We note here that Balasubramaniam and Pierce also suppose that all directories are equal,
+therefore, as elsewhere, we are safe to continue to assume that $|\setd|=1$.
+
+\begin{proof}
+Let $A$ and $B$ be two simple sequences returned by the update detector
+for the two replicas $\FS_A$ and $\FS_B$.
+A conflict between the commands $\cxynv\in A$ and $\czwmv\in B$
+means that even though $\cxynv\in A\setminus B$
+and $\czwmv\in B\setminus A$, they cannot be included in
+$\reca$ and $\recb$, respectively, because
+$\cxynv\nindep\czwmv$ (see \cref{def:reconciliation}).
+
+From \cref{incomparable_is_independent} we therefore know that $n\nunrel m$.
+Without loss of generality we can assume that $n\descendantEq m$.
+From this we see that $n$ is \emph{dirty} in both $\FS_A$ and $\FS_B$,
+as the filesystem changes at $n$ in $\FS_A$ and at $n$ or its descendant in $\FS_B$
+(and none of the commands are assertion commands).
+
+Now we only need to show that $\FS_A(n)\neq\FS_B(n)$, because from this 
+and $|\setd|=1$ we will also
+know that at least one of these values is not a directory,
+and therefore there is a conflict at $n$ in the state-based reconciler.
+If $n=m$, this follows from the fact that $\cxynv\neq\czwmv$ 
+(because they are not in $A\cap B$),
+as from \cref{worksinputmatch} we have $X=Z$,
+and therefore the above can only be true
+if $\FS_A(n)=\valvy\neq\valvw=\FS_B(n)$.
+If $n\descendant m$ and there is no command on $n$ in $B$, then it is also
+true as $\cxynv$ is not an assertion command, and therefore 
+$\FS_A(n)\neq\FS(n)=\FS_B(n)$, where $\FS$ is the common ancestor of the replicas.
+Finally, if there is a command on $n$ in $B$, then 
+from $\cxynv\in A\setminus B$ we know
+it must be different from $\cxynv$, and similarly to the first case,
+we have $\FS_A(n)\neq\FS_B(n)$.
+\end{proof}

### 2015-12-23 2015/def-commands.tex
Comparison proof and text improvements

@@
 
-Next we define commands on the filesystem.
+Next we define commands on filesystems.
 As described above, we aimed to select a set of commands
-that capture as much information as possible
+that captures as much information as possible
 about the operations, and is also symmetric.
@@
 A usual set of commands, based on the most frequent tools implemented by filesystems,
-may be $create(n,\valv)$---create the object $\valv$ at node $n$,
-$edit(n,\valv)$---modify the object at $n$ to become $\valv$,
-and $remove(n)$---delete the object at node $n$; 
+may be $create(n,\valv)$---create the value $\valv$ at node $n$,
+$edit(n,\valv)$---modify the value at $n$ to become $\valv$,
+and $remove(n)$---delete the value at node $n$; 
 where $n\in\setn$ and $\valv\in\setv$ (but $\valv\neq\empt$).
@@
 will in some cases need to distinguish between, for example,
-edits that result in directories ($edit(n,\vald)$) and
+$edit$s that result in directories ($edit(n,\vald)$) and
 ones that result in files ($edit(n,\valf)$), and treat them as separate commands,
-as their behaviors when combined with other commands are quite different.
+as their behaviors are quite different when combined with other commands.
 Indeed, Bill Zissimopoulos' work 
@@
 In other words, encoding the type of the output ($\cchard$, $\ccharf$ or $\ccharb$) in the commands is definitely useful.
-At the same time, there is never any need to encode information about the
-output \emph{value} of a command,
+At the same time, there is never any need to consider the
+exact output \emph{value} of a command,
 as the success or failure of filesystem commands only depend on the types of values in the filesystem.
@@
 This creates an arbitrary asymmetry where
-there is now more information encoded into commands about their output than about their input.
+there is now more information available about their output than about their input.
 As, based on the above, we expect that encoding more information in the commands
@@
 the value that it stores at the node.
-We will denote commands using quadruples that list these,
-and use $\cchard$, $\ccharf$ or $\ccharb$ to represent the different
-input and output types. For example, $\cbdaa{n}{\vald}$ 
+We will denote commands using quadruples that list these
+in a the following format:
+\[ \cxynv, \]
+where $X$ is the input type, $Y$ is the output type, $n$ is the node,
+and $\valvy$ is a value of the appropriate type from $\setvx{Y}$.
+We use $\cchard$, $\ccharf$ or $\ccharb$ to represent the different
+types. For example, $\cbdaa{n}{\vald}$ 
 will represent $mkdir(n,\vald)$.
@@
 
-\medskip
+\bigskip
 
+\noindent
 A command can only succeed if the original value at node $n$ has a type that matches
@@
 by prefixing the command or sequence to it, for example: $\cbrk\FS$, $\cbdaa{n}{\vald}\FS$, 
-or simply $S\FS$ if $S$ is a sequence of commands.
+or simply $S\FS$ if $S$ is a sequence of commands. % TODO Add space between command and FS
 
@@
 \item
-All other commands have the generic form $\cxynv$ where
-$X$ and $Y$ are types in $\typeset$,
-$n\in\setn$ and $\valvy$ is a value of the appropriate type from $\setvx{Y}$.
 \[ \cxynv\FS = 
@@
 
-\medskip
-
 % Simplification
@@
 
+\bigskip
+
+\noindent
 For reasons also listed in \cite{NREC}, in this paper we will not consider
 a $move$ or $rename$ command. Regarding the theoretical reasoning we aim to follow,
-this turns out to be useful because these would be the only commands that affect
+this turns out to be useful because this would be the only command that affects
 filesystems at two nodes at once, therefore describing 
-the dependencies affecting these commands
-would call for a more complicated model.
+the dependencies for $move$ would call for a more complicated model.
 From a pragmatic perspective, this restriction does not mean that in an application
@@
 able to handle renames by pre- and post-processing changes in the filesystem to
-discover them, which (especially when a rename is combined with changes to the content)
+discover them, which can enhance usability, but which
+(especially when a rename is combined with changes to the content)
 is a non-trivial problem in itself.

### 2015-12-23 2015/def-filesystem.tex
Comparison proof and text improvements

@@
 To model this, in $\setv$ we distinguish between 
-file contents ($\setf$) and directory contents ($\setd$), that is,
+file values ($\setf$) and directory values ($\setd$), that is,
 if $\setb = \{\empt\}$ then:
@@
 directories (e.g. permission settings) during synchronization,
-as these are not generally understood by users,
+as these are not generally understood well by users,
 and, if needed, conflict resolution on these settings can be easily automated.

### 2015-12-23 2015/intro.tex
More improvements and references
Comparison proof and text improvements

@@
 but we need to order these in a way that they could be applied
-to the filesystems
-without causing an error 
-(for example, a directory needs to be created first before a file can be created under it).
+to the filesystems without causing an error 
+(for example, a directory needs to be created before a file can be created under it).
 Similarly, during reconciliation when we consider all the updates that
@@
 in \cref{ordering} that we describe how commands can be ordered
-and prove that under some conditions all valid orders
+and prove that under some simple conditions all valid orders
 have the same effect.
 
-Finally, \cref{sec_rec} defines our reconciliation 
+\Cref{sec_rec} defines our reconciliation 
 and conflict detection algorithms.
@@
 it can be applied to the replicas without causing an error,
-and that the described algorithm provides a complete solution
+and it is complete
 inasmuch as no further updates can be applied under any circumstances.
@@
 and show that it has a number of highly convenient properties.
+We finish by comparing our results to other research
+and outlining directions for further work
+on the introduced algebraic system.
 

### 2015-12-23 2015/ordering.tex
Comparison proof and text improvements

@@
 We prove that under the given conditions, the set must contain a command on $\parent(n)$.
-Then, by repapplying this result, we how that the set must contain commands on every
+Then, by repapplying this result, we know that the set must contain commands on every
 ancestor of $n$ up to $\nn$.
@@
 \[ A = \cdots\cc\cxynv\cc\cqrmv\cc\cdots\cc\czwnnv\cc\cdots \]
-If $n\unrel m$, swap $\cxynv$ and $\cqrmv$. Based on \cref{ax_separate_commute} we know that the new
+If $n\unrel m$, then swap $\cxynv$ and $\cqrmv$. Based on \cref{ax_separate_commute} we know that the new
 sequence is equivalent to $A$.
@@
 (components) so that the nodes of two commands from two different subsets are incomparable.
-These will simply be the components of the subset of the node forest that contains the nodes affected by the set.
+These will simply be the components of the subset of the node forest that contains 
+the nodes affected by $U$.
 
@@
 components can be applied in any order.
-Therefore once we have ordered the commands inside a component, we generate
+Therefore once we have ordered the commands inside the components, we generate
 all permutations of the components themselves, including the ones
@@
 we know that all nodes are related, and from \cref{connected_changes}
-we also know that it must contain commands on all nodes in between.
+we also know that it must contain commands on nodes in between the related nodes.
 Therefore the nodes
@@
 These follow from the patterns of construction and destruction pairs, which
-at no point can mix without causing any sequence to break all filesystems.
+at no point can mix without causing any ordering to break all filesystems.
 
@@
 
-As a specific case, we can regard a sequence of commands $S$
+As a specific case, we can regard a simple sequence of commands $S$
 as a set and determine its $\orderset{S}$.
@@
 \begin{mylem}\label{simple_reorder_equiv}
-For any simple sequence $S\neq\cbrk$,
+For any simple sequence $S\nequiv\cbrk$,
 $\forall T: T\equiv S \Leftrightarrow T\in\orderset{S}$.
@@
 Therefore if $S\nequiv\cbrk$ then $S\in\orderset{S}$,
-and $S$ cannot equivalent to any sequence of the same commands
+and $S$ cannot be equivalent to any sequence of the same commands
 not in $\orderset{S}$.

### 2015-12-23 2015/rec-intro.tex
Comparison proof and text improvements

@@
 and so they are simple sequences.
-(Otherwise, they can be simplified to become simple sequences.)
+(Otherwise, they can be simplified to become simple sequences; see \cref{update_works}.)
 We also assume that $\FS_A$ and $\FS_B$ are not broken.
@@
 \begin{mydef}{Independent commands, sequences and sets.}
-For two commands $\cxynv$ and $\czwmv$ we write $\cxynv\indep\czwmv$ if $\cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk$.
+Two commands $\cxynv$ and $\czwmv$ 
+are independent, and we write $\cxynv\indep\czwmv$ if 
+they have the same effect in either order and do not break all filesystems:
+$\cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk$.
 For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
@@
 In other words, the sequence $\reca$ we apply to $\FS_B$ 
+to reconcile it with $\FS_A$
 is the largest subset of $A\setminus B$
@@
 \cref{ordering} as any subset of $A$ is also simple.
-In a similar way, $\recb$ can be obtained by reversing $A$ and $B$.
+In a similar way, $\recb$ can be obtained by reversing $A$ and $B$
+in the definition.
 \end{mydef}

### 2015-12-23 2015/rec-sound.tex
Comparison proof and text improvements

@@
 
-We show that $A$ can be transformed via equivalences so that this would be true.
+We show that $A$ can be transformed via equivalences into $A'$ for which it is true.
 Our proposition is that if the marked commands are not at the beginning, then
@@
 
-\medskip
-
 Let us consider therefore the marked command preceded by an unmarked command in $A$,
@@
 and the preceding unmarked command be $\czwmv$.
+\begin{gather*}
+A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots
+\end{gather*}
 As $A$ is simple and $\works{A}$, from 
@@
 When describing our ordering algorithm in \cref{ordering} we saw
-that the command on the parent path deremines whether a pair of commands
+that the command on the parent path determines whether a pair of commands
 is a construction or destruction pair,
@@
 Going back to the construction and destruction pairs we see that the output type of the first command
-is always the same, and it is either $D$ or $\empt$ depending on the relationship between $n$ and $m$.
+is always the same, and it is either $\cchard$ or $\ccharb$ depending on the relationship between $n$ and $m$.
 Therefore $R=W$ and $\cqrmv=\czwmv$
@@
 
-\medskip
-
 We now know that there is an $A'\equiv A$ in which commands in $A\cap B$
 are at the beginning, and therefore 
-from \cref{worksextpostfix}
+from \cref{worksextpostfix} we know that
 $\worksc{A\cap B}{A}$ and by symmetry $\worksc{A\cap B}{B}$.
@@
 
-\medskip
+\bigskip
 
+\noindent
 We would like to prove that $\worksc{B\cc \reca}{A,B}$.
-From the above we know that this is equivalent to
+From the above we know that we can move commands in $A\cap B$
+to the beginning of $B$ and so this is equivalent to
 \[ \worksc{\acb\cc \bma\cc \reca}{A,B}. \]
@@
 (as $\worksc{B}{A,B}$),
-based on \cref{indep_prefix_combine}
-we only need to prove that
+we can prove our theorem based on \cref{indep_prefix_combine}
+if we can prove that
 \[ \worksc{\acb\cc \reca}{A,B}. \]
@@
 
-Our theorem is therefore proven if we prove the following lemma:
+Our theorem is therefore proven if we prove the following lemma,
+in which we rename $A\setminus B$ to $S$ and $B\setminus A$ to $T$:
 \newcommand{\condSimple}{(c1)}
@@
 we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
-In the first case, swapping the commands results in a sequence equivalent to $S$;
-we only need to show that the other two cases are not possible as they would lead to a contradiction.
+In the first case, swapping the commands results in a sequence equivalent to $S$,
+and we show that the other two cases are not possible as they would lead to a contradiction.
 

### 2015-12-23 2015/upd-correct.tex
Comparison proof and text improvements

@@
 we can separate $S$ into components of commands on related nodes,
-as commands from separate components freely commute yielding an equivalent sequence.
-From the arguments above, we also know that each component
+as commands from separate components freely commute yielding equivalent sequences.
+From the arguments above we also know that each component
 must be made up of only destruction or only construction pairs,
 but not a mixture of the two.
-This means that in each component, parents either strictly precede or succeed child nodes
+This means that in each component, commands on parents 
+either strictly precede or succeed child nodes
 (as otherwise $S\equiv\cbrk$ would hold),

### 2015-12-23 2015/upd-def.tex
Comparison proof and text improvements

@@
 sufficient, as there are commands available for any input and output value. 
-Specifically, if at node $n$, $\FS(n)=X'$ and $\FS_A(n)=Y'\neq X'$, then we add the command $\cxyaa{n}{Y'}$ to $A$
-where $X'\in\setvx{X}$ and $Y'\in\setvx{Y}$.
+Specifically, if at node $n$, $\FS(n)=\valvx$ and $\FS_A(n)=\valvy\neq \valvx$, then we add the command $\cxyaa{n}{\valvy}$ to $A$
+where $\valvx\in\setvx{X}$ and $\valvy\in\setvx{Y}$.
 
@@
 \begin{mydef}{Minimal set or sequence.}
-A sequence or set of commands is minimal if it contains at most one command on every node.
+A sequence or set of commands is minimal if it contains at most one command on each node.
 \end{mydef}
@@
 we discuss it in the next section.
-Then, in \cref{update_works}, we prove that the resulting sequence actually
-works without breaking the filesystem.
+Then, in \cref{update_works}, we prove that the resulting sequence 
+returned by the update detector actually works without breaking the filesystem.

### 2015-12-23 2015/works-inverse.tex
Comparison proof and text improvements

@@
 \begin{proof}
-We name this proposition a \namecrefs{combine_independent_commands} for the same reason as above,
-but it is easy to provide an indirect proof based on our filesystem model.
-Assume that $\cxynv\cc \czwmv\FS=\fsbroken$.
+We name this proposition a \namecref{combine_independent_commands} 
+because to prove it, we must reach back to our filesystem model.
+We proceed in an indirect way and
+assume that $\cxynv\cc \czwmv\FS=\fsbroken$.
 We know $\cxynv\FS\neq\fsbroken$ so it must be applying 
@@
 
-\medskip
+\bigskip
 
+\noindent
 We continue by defining inverse commands and sequences
@@
 This is based on the fact that in our model, unless they break a filesystem,
-commands change one type of value into another, but never merge types.
+commands leave the type of the filesystem value unchanged 
+or change one type into another, but never merge types.
 That is,

### 2015-12-24 2015/comparisons.tex
Improved text

@@
-\section{Comparisons}
+\section{Related Work}
 
-\subsection{Liberal and conservative Reconciliation}
+\subsection{Liberal and Conservative Reconciliation}
 
 We consider the reconciliation algorithm described here an improvement over
-the one derved during our previous research (see \cite{NREC})
+the one derved during our previous research (\cite{NREC})
 as the previous algorithm not only fails to propagate all possible commands
@@
 The former observation is supported by Berzan and Ramsey, who in \cite{CBNR} 
-describe between different reconciliation policies.
+describe different general reconciliation policies.
 The liberal (maximal) policy propagates all updates to all replicas where
-the command does not break the filesystem, while a conservative policy
+the update does not break the filesystem, while a conservative policy
 refrains from updating any node that is below a node with conflicting commands.
@@
 in their state-based approach (\cite{BP}).
-The update detector described in \cite{BP} provides a safe estimate of nodes
+The update detector they describe provides a safe estimate of nodes
 (paths) at which updates occurred.
 It marks some nodes as \emph{dirty} in a way that we know that at non-dirty nodes
-the filesystem have not changed between their original and current states
+the filesystems (replicas) have not changed between their common original state and current state
 (see Definition 3.1.1 in \cite{BP}).

### 2015-12-24 2015/paper.tex
Improved text

@@
 % TODO
-Conclusions go here -- same approach to other systems
+Conclusions go here --- same approach to other systems
 \medskip
@@
 consider reconciling not only two, but more replicas in a single step and
-prove the correctness of the algorithm proposed.
+prove the correctness and completeness of the algorithm proposed.
 A related problem is to model cases where reconciliation cannot
@@
 Identifying the information one needs to keep to perform
-update detection is such cases and devising a suitable algorithm
-will be an essential part of any implementation of a reconciler
+update detection in such cases and devising a suitable algorithm
+would be beneficial for any implementation of a reconciler
 based on the ideas presented here.
@@
 the simplifying assumptions we used.
-Identifying which results depend on assuming that $|\setd|=1$
+Identifying which results depend on the assumption that $|\setd|=1$
 and devising updated proofs or algorithms,

### 2015-12-24 2015/rec-complete.tex
Minor changes
More improvements and references
Further research, conflict comparison, renaming unrelated to incomparable
Improved text

@@
-\subsection{Completeness of Reconciliation}
+\subsection{The Completeness of Reconciliation}
 
@@
 % This is where we're using |D|=1
-% TODO C.f. strict / liberal etc. reconciliation in references
 
@@
 (that is, $S$ breaks all possible $\FS_B$ replicas),
-or it overrides incompatible changes introduced in the replica by $B$.
+or it changes a node that $B$ has already changed to a different value,
+that is, it overrides a change in $\FS_B$.
 \end{myth}
-Overriding changes is not desirable as in these cases the reconciler
-does not have enough information to decide whether to promote
-the change introduced by $A$ over that introduced by $B$ or vice versa.
-These cases should be treated as conflicts and
-the affected nodes or commands marked for review
+Such an override could occur if a given node was modified differently in
+$A$ and $B$ (to different values but the same type), which is clearly
+a conflict that should be marked for review
 by a human or a different system.
@@
 $B\cc S \equiv \acb\cc\bma\cc S$.
-We also know commands in $S_0$ and $\bma$ commute, and so this is equivalent to
+We also know that commands in $S_0$ and $\bma$ commute, and so this is equivalent to
 $\acb\cc S_0\cc\bma\cc\cxynv\cc S_1$.
@@
 
-We know $\cxynv\nindep\czwmv$, and so from \cref{unrelated_is_independent}, $n\nunrel m$.
+We know $\cxynv\nindep\czwmv$, and so from \cref{incomparable_is_independent}, $n\nunrel m$.
 As the sequence works, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.

### 2015-12-25 2015/axioms.tex
More text improvements

@@
 and are applied to filesystems in time.
-Therefore we will investigate sequences of commands with a well-defined order
-(which form a free semigroup).
+Therefore we will investigate sequences of commands with a well-defined order.
+\begin{mydef}[$\cc$ and $\emptyseq$]
 We use ``$\cc$'' to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence:
-$S=\cbdaa{n}{\vald}\cc\cbfaa{m}{\valf}$, or $S'=S\cc\cbba{o}$.
-We write $\emptyseq$ for the empty sequence.
+$S=\cbdaa{n}{\vald}\cc\cbfaa{m}{\valf}$, or $S'=S\cc\cbba{o}$,
+with the meaning that the command on the left is applied first:
+\[ \alpha\cc\beta\FS = \beta(\alpha\FS). \]
+Sequences of commands form a free semigroup, and, as usual,
+$\emptyseq$ denotes its unit element, the empty sequence,
+which by definition leaves all filesystems unchanged.
+\end{mydef}
 
@@
 
-\begin{mydef}
+\begin{mydef}[$\equiv$]
 % Relation in the algebra
@@
 
-\begin{mydef}
+\begin{mydef}[$\eqext$]
 % Relation in the algebra
@@
 
-\begin{mydef}{$n\descendant m$.}
-We write $n\descendant m$ if $n$ is the ancestor of $m$ ($n=\parent^n(m)$). % TODO (the transitive closure of the $\parent$ relation)
+\begin{mydef}[$n\descendant m$]
+The partial ordering determined by the parent relation is denoted by $\descendant$:
+we write $n\descendant m$ if $n$ is the ancestor of $m$ ($n=\parent^n(m)$),
+that is, the path name of $n$ is an initial segment of that of $m$. 
 We write $n\descendantEq m$ if $n\descendant m$ or $n=m$.
@@
 
-\begin{mydef}{$n\unrel m$.}
+\begin{mydef}[$n\unrel m$]
 We write $n\unrel m$, or ``$n$ and $m$ are incomparable'' if $n\not\descendantEq m$ and $n\not\ancestorEq m$.
+incomparable nodes are on different branches or on different trees;
+none of the path names describing their location is an initial segment of the other.
 \end{mydef}
@@
 
-\begin{mydef}{Construction pair.}
+\begin{mydef}[Construction pair]
 A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parent(n)$ 
@@
 
-\begin{mydef}{Destruction pair.}
+\begin{mydef}[Destruction pair]
 A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parent(n)=\nn$ and the commands are one
@@
 
-\begin{mydef}{Assertion command.}
+\begin{mydef}[Assertion command]
 A command is an assertion command if

### 2015-12-25 2015/def-commands.tex
More text improvements

@@
 Let us consider what kind of information is usually encoded in filesystem operations.
-A usual set of commands, based on the most frequent tools implemented by filesystems,
-may be $create(n,\valv)$---create the value $\valv$ at node $n$,
-$edit(n,\valv)$---modify the value at $n$ to become $\valv$,
-and $remove(n)$---delete the value at node $n$; 
-where $n\in\setn$ and $\valv\in\setv$ (but $\valv\neq\empt$).
+A minimal set of commands, based on the most frequent tools implemented by filesystems,
+may be $create(n,\valv)$, which creates a file or directory ($\valv$) at the empty node $n$;
+$edit(n,\valv)$, which replaces the earlier value at $n$ with $\valv$;
+and $remove(n)$, which deletes the value at $n$---where 
+$n\in\setn$ and $\valv\in\setv$ (but $\valv\neq\empt$).
 Regarding their output, that is, the state of the filesystem at $n$
@@
 
-\begin{mydef}
+To define the exact effect of the commands we use
+the \emph{replacement operator}  which changes the
+value of the filesystem at a given point only.
+
+\begin{mydef}[Replacement operator]
 Using $\FS[V/n]$ we denote a filesystem derived from $\FS$:
@@
 
-The exact behavior of the commands is as follows:
+The effect of the commands is as follows:
 \begin{itemize}

### 2015-12-25 2015/def-filesystem.tex
More text improvements

@@
 and a set of possible contents or values, $\setv$, as its codomain:
+\begin{mydef}[Filesystem]
 \[ \FS : \setn \rightarrow \setv \] 
+\end{mydef}
 In our model, $\setn$ 
@@
 they also model inodes and restrict the filesystem to a just single tree.
-\begin{mydef}
+\begin{mydef}[$\parent$]
 The function $\parent(n)$ returns the parent node of $n$, or
@@
 
-Every filesystem has a so-called \textbf{tree property}, which means that
+Every filesystem has a so-called \emph{tree property}, which means that
 if the filesystem is not empty at a node, and the node has a parent,
@@
 The tree property can then be defined as
+\begin{mydef}[Tree property]
 \begin{align*}
@@
 &\quad\wedge \parent(n) \neq \topnode \\
-&\Rightarrow \FS(\parent(n)) \in \setd 
+&\Rightarrow \FS(\parent(n)) \in \setd. 
 \end{align*}
+\end{mydef}
 This means that as we move down from the root of a tree of nodes,

### 2015-12-25 2015/ordering.tex
More text improvements

@@
 
-\begin{mydef}{$\orderset{U}$.}
+\begin{mydef}[$\ordersetsign$]
 We use $\orderset{U}$ to denote the set of sequences that contain all commands in

### 2015-12-25 2015/rec-intro.tex
More text improvements

@@
 
-\begin{mydef}{Independent commands, sequences and sets.}
+\begin{mydef}[$A\indep B$: Independent commands, sequences and sets]
 Two commands $\cxynv$ and $\czwmv$ 
@@
 
-\begin{mydef}{Reconciliation.}\label{def:reconciliation}
+\begin{mydef}[Reconciliation]\label{def:reconciliation}
 \begin{align*}

### 2015-12-25 2015/rec-sound.tex
More text improvements

@@
 and let the marked command be $\cxynv$, 
-and the preceding unmarked command be $\czwmv$.
+and the preceding unmarked command be $\czwmv$:
 \begin{gather*}

### 2015-12-25 2015/works-inverse.tex
More text improvements

@@
 
-\begin{mydef}
+\begin{mydef}[$\works{x}$]
 % Unsure if this relation should be in the algebra.
@@
 
-\begin{mydef}
+\begin{mydef}[$\worksc{x}{y}$]
 For two sets of sequences, $\worksc{A_1,A_2,\ldots,A_k}{B_1,B_2,\ldots,B_l}$ means that 
@@
 
-\begin{mydef}{Sets of sequences.}
+\begin{mydef}[Sets of sequences]
 For brevity, we will use $\seqset{S}$ to note an arbitrary set of sequences,
@@
 % An inference rule in the algebra
-$\forall A,S: \worksc{A}{A\cc S}$, that is, if a sequence works, its prefix also works.
+$\forall A,S: \worksc{A}{A\cc S}$, that is, if a sequence works, its initial segment also works.
 \end{mycor}
@@
 
-\begin{mydef}{Inverse commands and sequences.}
+\begin{mydef}[Inverse commands and sequences]
 The inverse of command $\cxynv$ is $\cxynv^{-1} = \caaaa{Y}{X}{n}{\valvx}$
@@
 
-\begin{mydef}{$\typeeq$.}
+\begin{mydef}[$\typeeq$]
 For two filesystems we write $\FS\typeeq\GS$
@@
 \begin{mylem}\label{r_invmove}
-A common prefix of sequences can be moved to the other side of $\workssign$ by inverting it:
+A common initial segment of sequences can be moved to the other side of $\workssign$ by inverting it:
 \begin{gather*}

### 2015-12-25 2015/algebra.tex
Further research, conflict comparison, renaming unrelated to incomparable
Improved text
Reordering; improvements; new notation; improved figure

@@
-\subsection{Towards an Algebra}\label{sec_algebra}
+\section{Towards a Formal Algebra}\label{sec_algebra}
 
@@
 
-In this algebra, equivalence ($\equiv$) and extension ($\eqext$) would become relations,
-and logical rules involving them
+In this algebra, equivalence ($\equiv$) and extension ($\eqext$) would become relations
+between sequences, and logical rules involving them
 (e.g. $ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $) would be re-cast as inference rules.
@@
 one can also include symbols, inference rules and axioms for 
-$\works{\seqset{X}}$ and $\worksc{\seqset{X}}{\seqset{Y}}$.
+$\works{\seqset{A}}$ and $\worksc{\seqset{A}}{\seqset{B}}$.
 We see proving the soundness and completeness of this extended algebra

### 2015-12-25 2015/axioms.tex
Reordering; improvements; new notation; improved figure

@@
 
-% TODO Ref back to intro; further abstraction - no need to go the FS. break-all, equiv, extend
-
-So that we could describe the effects of commands on a filesystem, let us introduce some notation
+So that we could describe the effects of commands in general,
+let us introduce some notation
 and note some observations.
@@
 with the meaning that the command on the left is applied first:
-\[ \alpha\cc\beta\FS = \beta(\alpha\FS). \]
+\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
 Sequences of commands form a free semigroup, and, as usual,
@@
 that is, they behave in the same way on
-all filesystems: $\forall \FS: A\FS=B\FS$.
+all filesystems: $\forall \FS: A\aFS=B\aFS$.
 It is a reflexive, commutative and transitive relation,
@@
 on any filesystem $A$ does not break:
-$\forall \FS: A\FS\neq\fsbroken\Rightarrow A\FS=B\FS$.
+$\forall \FS: A\FS\neq\fsbroken\Rightarrow A\aFS=B\aFS$.
 It is a reflexive and transitive relation,
@@
 An assertion command can be added on a descendant node:
-$\cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n}$ 
+\[ \cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n} \] 
 where $\nn\descendant n$ and $\cxy\neq\cdd$.
@@
 An assertion command can be added on an ancestor node:
-$\cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn}$ 
+\[ \cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn} \]
 where $\nn\descendant n$ and $\cxy\neq\cbb$.
@@
 \end{myax}
+
+% TODO We will only use these except for...
+
+\bigskip
+
+\noindent
+We also define the concept of two commands being independent:
+
+\begin{mydef}[$A\indep B$: Independent commands, sequences and sets]
+Two commands $\cxynv$ and $\czwmv$ 
+are independent, and we write $\cxynv\indep\czwmv$ if 
+they have the same effect in either order and do not break all filesystems:
+\[ \cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk. \]
+For two sequences or unordered sets of commands $A$ and $B$ we write $A\indep B$ if
+for all $\alpha$ in $A$ and all $\beta$ in $B$, $\alpha\indep\beta$.
+\end{mydef}
+
+It is intentional that we use the same symbol for independent commands
+and sequences as for incomparable nodes. As we will in the next
+\namecref{incomparable_is_independent},
+these two concepts are closely related.
+
+\begin{mylem}\label{incomparable_is_independent}
+Two different commands that are not assertion commands are independent iff the nodes they change are incomparable:
+\[ \cxynv\indep\czwmv \Leftrightarrow n\unrel m \]
+if $\cxynv\neq\czwmv$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
+\end{mylem}
+\begin{proof}
+This is easy to show based on the output of the software that investigates the behavior of command pairs.
+However, this proposition can also be derived from the \namecrefs{ax_separate_commute} already listed
+in the following way.
+
+We proceed in two steps. First, we note that
+from \cref{ax_separate_commute,ax_separate_nobreaks} we know that
+if $n\unrel m$, then $\cxynv$ and $\czwmv$ must necessarily be independent, and therefore
+$ \cxynv\nindep\czwmv \wedge n\unrel m $ cannot be the case.
+
+Next, we prove that
+\[ \cxynv\indep\czwmv \wedge n\nunrel m \] is also impossible as it would lead to contradiction.
+As $n\nunrel m$
+we know that $n=m$, $n\descendant m$ or $m\descendant n$.
+
+If $n=m$, then from \cref{ax_same_breaks} we know $Y=Z$ and $W=X$
+as otherwise the commands, in one order or the other, would break all filesystems
+and they could not be independent.
+The commands are not assertion commands, and so from \cref{ax_same_singlec}
+we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $Y=W$ and $\valvy=\valvw$.
+Therefore $X=Y=Z=W$ which is only possible if both commands are $\cff$ and have the same
+output value. This, however, contradicts our assumption that they are different.
+
+If $n\descendant m$ or $m\descendant n$, then
+from \cref{ax_distantrel_breaks} we know that if they are not directly related,
+then $\cxynv\cc\czwmv$ breaks all filesystems, and they cannot be independent.
+From the construction and destruction pairs and 
+\cref{ax_directchild_breaks,ax_directparent_breaks} we also see that
+even if they are directly related, either
+$\cxynv\cc\czwmv$ or $\czwmv\cc\cxynv$ 
+breaks all filesystems, so they again cannot be independent.
+\end{proof}

### 2015-12-25 2015/conclusion.tex
Reordering; improvements; new notation; improved figure

--- 2015-12-24 2015/paper.tex
@@
-\documentclass[12pt]{article}
-
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{centernot}
-\usepackage{tikz}
-\usepackage{cleveref}
-
-\input{macros}
-
-\title{Complete Algebraic File Synchronization}
-\author{Elod Pal Csirmaz}
-
-\begin{document}
-\maketitle
-\begin{abstract}
-Abstract goes here
-\end{abstract}
-
-\input{intro}
-
-\section{Definitions}\label{sec_def}
-
-\input{def-filesystem}
-
-\input{def-commands}
-
-\input{axioms}
-
-\section{Update Detection}\label{sec_update}
-
-\input{upd-def}
-
-\input{ordering}
-
-\input{upd-correct}
-
-\section{Reconciliation}\label{sec_rec}
-
-\input{rec-intro}
-
-\input{works-inverse}
-
-\input{rec-sound}
-
-\input{rec-complete}
-
-\input{comparisons}
-
-\input{algebra}
-
 \section{Conclusions and Further Research}
@@
 % TODO
-Conclusions go here --- same approach to other systems
+... ... ...
+
+(Same approach to other systems)
 \medskip
@@
 consider reconciling not only two, but more replicas in a single step and
-prove the correctness and completeness of the algorithm proposed.
+prove the correctness and maximality of the algorithm proposed.
 A related problem is to model cases where reconciliation cannot
@@
 and help avoid human error.
-
-\section{Acknowledgments}
-
-I thank Laszlo Csirmaz for his invaluable input on previous drafts of this paper,
-and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.
-
-\begin{thebibliography}{99}
-
-\input{references}
-
-\end{thebibliography}
-
-\end{document}

### 2015-12-25 2015/def-commands.tex
Reordering; improvements; new notation; improved figure

@@
 \subsection{Commands on Filesystems}
+
+% TODO identity command?
 
@@
 Indeed, Bill Zissimopoulos' work
-demonstrated\footnote{Bill Zissimopoulos, personal communication, August 2015.}
+demonstrated (\cite{BZ})
 that extending this distinction to more commands ultimately simplifies
@@
 in a the following format:
+% TODO convert into definition
 \[ \cxynv, \]
@@
 will represent $mkdir(n,\vald)$.
+% TODO Just say "omit"
 Alternatively, we use a triple of the two types and a node if 
@@
 We note that a command or a sequence of commands is applied to a filesystem
-by prefixing the command or sequence to it, for example: $\cbrk\FS$, $\cbdaa{n}{\vald}\FS$, 
-or simply $S\FS$ if $S$ is a sequence of commands. % TODO Add space between command and FS
+by prefixing the command or sequence to it, for example: $\cbrk\aFS$, $\cbdaa{n}{\vald}\aFS$, 
+or simply $S\aFS$ if $S$ is a sequence of commands.
 
@@
 
+% TODO include command in def
 \begin{mydef}[Replacement operator]
-Using $\FS[V/n]$ we denote a filesystem derived from $\FS$:
-\[ \FS[V/n](m) :=
+Using $\FS[\valv/n]$ we denote a filesystem derived from $\FS$:
+\[ \FS[\valv/n](m) :=
    \begin{cases}
-   V &\mbox{if~} m=n\\
+   \valv &\mbox{if~} m=n\\
    \FS(m) &\mbox{otherwise.}
@@
 The effect of the commands is as follows:
-\begin{itemize}
-\item $\cbrk\FS = \fsbroken$
-\item
-\[ \cxynv\FS = 
+\begin{align*}
+&\cbrk\aFS = \fsbroken \\
+&\cxynv\aFS = 
    \begin{cases}
@@
    \fsbroken &\mbox{if~} \FS(n)\not\in\setvx{X}\\
-   \fsbroken &\mbox{if~} \FS[V/n] \mbox{~violates the tree property}\\
-   \FS[V/n] &\mbox{otherwise.}
+   \fsbroken &\mbox{if~} \FS[\valvy/n] \mbox{~violates the tree property}\\
+   \FS[\valvy/n] &\mbox{otherwise.}
    \end{cases}
-\]
-\end{itemize}
+\end{align*}
 

### 2015-12-25 2015/intro.tex
Reordering; improvements; new notation; improved figure

@@
 to filesystem synchronization.
-Presented with multiple copies (replicas) of a filesystem that have been independently modified,
+Presented with multiple copies (replicas) of the same filesystem that have been independently modified,
 we regard the aim of the synchronizer to modify these replicas further
@@
 We then proceed to prove that the output of reconciliation
-is sound in the sense that 
+is correct in the sense that 
 it can be applied to the replicas without causing an error,
-and it is complete
+and it is maximal
 inasmuch as no further updates can be applied under any circumstances.
@@
 In fact, the new command set not only simplifies
-our reconciliation algorithm, but also makes it complete.
+our reconciliation algorithm, but also makes it maximal.
 

### 2015-12-25 2015/rec-complete.tex
More text improvements
Reordering; improvements; new notation; improved figure

@@
-\subsection{The Completeness of Reconciliation}
+\subsection{Reconciliation is Maximal}
 
@@
 
-The reconciliation algorithm defined above is also complete, that is,
+The reconciliation algorithm defined above is also maximal, that is,
 it is not possible to apply any further commands from $A\setminus B$ to $\FS_B$.
@@
 Without loss of generality, we assume that $\cxynv$ is the first command in $S$
-that is not independent of $\bma$.
+that is not independent of $\bmanp$.
 If so, we can split $S$ into $S_0\cc\cxynv\cc S_1$ where $S_0\indep\bma$.
-Let us also split $\bma$ into $T_0\cc\czwmv\cc T_1$ where $T_1\indep\cxynv$.
+Let us also split $\bmanp$ into $T_0\cc\czwmv\cc T_1$ where $T_1\indep\cxynv$.
 From \cref{can_move_intersection} we know that
 $B\cc S \equiv \acb\cc\bma\cc S$.
-We also know that commands in $S_0$ and $\bma$ commute, and so this is equivalent to
+We also know that commands in $S_0$ and $\bmanp$ commute, and so this is equivalent to
 $\acb\cc S_0\cc\bma\cc\cxynv\cc S_1$.
-Expanding $\bma$ and swapping $T_1$ and $\cxynv$ we get
+Expanding $\bmanp$ and swapping $T_1$ and $\cxynv$ we get
 \[ \acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv\cc T_1\cc S_1. \]
@@
 that the sequence works on $\FS$ where $A\FS\neq\fsbroken$.
-If so, its prefix, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also work.
+If so, its initial segment, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also work.
 
@@
 As the sequence works, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
-As $\czwmv$ and $T_0$ originate from $B\setminus A$ and $B$ is simple, we also know there are
-no commands on $m$ in $A\cap B$ or $T_0$,
+As $\czwmv$ and $T_0$ originate from $\bmanp$ and $B$ is simple, we also know there are
+no commands on $m$ in $\acbnp$ or $T_0$,
 and that there are no commands on $m$ in $S_0$ as $S_0\indep\bma$.
@@
 $\cqrmv = \czwmv$.
-This is a contradiction as $\cqrmv\in A$, but $\czwmv\in\bma$.
+This is a contradiction as $\cqrmv\in A$, but $\czwmv\in\bmanp$.
 
@@
 We also know $\valvw\neq\valvy$ as otherwise the two commands would be equal and
-would be included in $A\cap B$,
+would be included in $\acbnp$,
 but this means that $\cxynv$, from $A$, overrides a change introduced 

### 2015-12-25 2015/rec-intro.tex
Reordering; improvements; new notation; improved figure

--- 2015-12-23 2015/rec-intro.tex
@@
 If we start with two copies of the filesystem $\FS$,
-and two different sequences are applied to the copies to yield $\FS_A:=A\FS$
-and $\FS_B:=B\FS$, then our aim is to define sequences of commands $\reca$ and $\recb$
-so that $\recb\FS_A$ and $\reca\FS_B$ would be as close to each other as possible.
+and two different sequences are applied to the copies to yield $\FS_A:=A\aFS$
+and $\FS_B:=B\aFS$, then our aim is to define sequences of commands $\reca$ and $\recb$
+so that $\recb\aFS_A$ and $\reca\aFS_B$ would be as close to each other as possible.
 
@@
 and $\recb \subset B\setminus A$ 
-so that $\reca\FS_B\neq\fsbroken$ and $\recb\FS_A\neq\fsbroken$,
+so that $\reca\aFS_B\neq\fsbroken$ and $\recb\aFS_A\neq\fsbroken$,
 and show that these are the longest sequences with this property, that is,
@@
 With these assumptions,
-we can now define independent sequences and
-our reconciliation algorithm.
+we can now define our reconciliation algorithm.
 
-\begin{mydef}{Independent commands, sequences and sets.}
-Two commands $\cxynv$ and $\czwmv$ 
-are independent, and we write $\cxynv\indep\czwmv$ if 
-they have the same effect in either order and do not break all filesystems:
-$\cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk$.
-For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
-$\forall \alpha\in A \mbox{~and~} \forall \beta\in B: \alpha\indep\beta$.
-\end{mydef}
-
-\begin{mydef}{Reconciliation.}\label{def:reconciliation}
+\begin{mydef}[Reconciliation]\label{def:reconciliation}
+We determine $\reca$---which we apply to $\FS_B$ 
+to reconcile it with $\FS_A$---to be
+the largest subset of $A\setminus B$
+that is independent of $B\setminus A$:
 \begin{align*}
-\reca = \{\alpha| & \\
+\reca = \{\alpha|{}& \\
 & \alpha\in A\setminus B \\
@@
 & \forall \beta\in B\setminus A: \alpha\indep\beta\\
-\} &
+\}. &
 \end{align*}
-
-In other words, the sequence $\reca$ we apply to $\FS_B$ 
-to reconcile it with $\FS_A$
-is the largest subset of $A\setminus B$
-that is independent of $B\setminus A$.
 The order of commands in the sequence can be determined using the algorithm described in
@@
 that is, without loss of generality,
-\[ \reca\FS_B\neq\fsbroken. \]
+\[ \reca\aFS_B\neq\fsbroken. \]
 So that we can formalize statements needed to prove this,

### 2015-12-25 2015/rec-sound.tex
Reordering; improvements; new notation; improved figure

@@
 \subsection{The Correctness of Reconciliation}
-
-% Correctness of reconciliation
-% -----------------------------
 
@@
 that is, applying its result is not going to break the replicas.
-We reformulate the original proposition, $\reca\FS_B\neq\fsbroken$,
-based on $\FS_B=B\FS$ and so we aim to prove that
+We reformulate the original proposition, $\reca\aFS_B\neq\fsbroken$,
+based on $\FS_B=B\aFS$ and so we aim to prove that
 $B\cc\reca$ works wherever $A$ and $B$ work:
@@
 \begin{align*}
-\reca = \{\alpha| & \\
+\reca = \{\alpha|{}& \\
 & \alpha\in A\setminus B \\
@@
 either of them works on:
-$\worksc{A\cap B}{A}$, and, by symmetry,
-$\worksc{A\cap B}{B}$.
+$\worksc{\acbnp}{A}$, and, by symmetry,
+$\worksc{\acbnp}{B}$.
 \end{mylem}
@@
 \begin{proof}
-The difficulty is that commands in $A\cap B$ can occur anywhere in $A$.
+The difficulty is that commands in $\acbnp$ can occur anywhere in $A$.
 Therefore, first we prove the following:
@@
 
-We now know that there is an $A'\equiv A$ in which commands in $A\cap B$
+We now know that there is an $A'\equiv A$ in which commands in $\acbnp$
 are at the beginning, and therefore 
 from \cref{worksextpostfix} we know that
-$\worksc{A\cap B}{A}$ and by symmetry $\worksc{A\cap B}{B}$.
+$\worksc{\acbnp}{A}$ and by symmetry $\worksc{\acbnp}{B}$.
 \end{proof}
@@
 We would like to prove that $\worksc{B\cc \reca}{A,B}$.
-From the above we know that we can move commands in $A\cap B$
+From the above we know that we can move commands in $\acbnp$
 to the beginning of $B$ and so this is equivalent to
@@
 Our theorem is therefore proven if we prove the following lemma,
-in which we rename $A\setminus B$ to $S$ and $B\setminus A$ to $T$:
+in which we rename $\ambnp$ to $S$ and $\bmanp$ to $T$:
 \newcommand{\condSimple}{(c1)}
@@
 according to \cref{ax_parent_assert}.
-We now have $\cxynv\indep T\equiv T'$ which is a contradiction as
+We now have $\cxynv\indep T\equiv T'$, which is a contradiction as
 $T'$ has a command on $m$ and $m=\parent(n)$.

### 2015-12-25 2015/references.tex
More improvements and references
Reordering; improvements; new notation; improved figure

@@
+% B 4
+\bibitem{BP}
+S. Balasubramaniam and Benjamin C. Pierce,
+``What is a File Synchronizer?''
+in \emph{Proceedings of the 4\textsuperscript{th} Annual 
+ACM/IEEE International Conference on Mobile Computing and Networking,}
+New York: ACM, 1998, pp. 98--108.
+
+% B 21
+\bibitem{CBNR} 
+Constantin Berzan and Norman Ramsey,
+``Summer Scholars Technical Report,''
+Medford, MA: Tufts University, 2010.
+Accessed 29 November 2015.
+http://thirld.com/files/summerscholars\_techreport.pdf.
+
+% K 3
+\bibitem{KRSD}
+Anne-Marie Kermarrec and Antony Rowstron and Marc Shapiro and Peter Druschel,
+``The IceCube Approach to the Reconciliation of Divergent Replicas,''
+in \emph{Proceedings of the Twentieth Annual ACM Symposium on Principles of Distributed Computing,}
+New York: ACM, 2001, pp. 210--218.
+
+% R
 \bibitem{NREC} 
@@
 
-\bibitem{CBNR} 
-Constantin Berzan and Norman Ramsey,
-``Summer Scholars Technical Report,''
-Medford, MA: Tufts University, 2010.
-Accessed 29 November 2015.
-http://thirld.com/files/summerscholars\_techreport.pdf.
+% T 1
+\bibitem{TSR}
+Vinh Tao and Marc Shapiro and Vianney Rancurel,
+``Merging Semantics for Conflict Updates in Geo-distributed File Systems,''
+in \emph{Proceedings of the 8\textsuperscript{th}
+ ACM International Systems and Storage Conference,}
+New York: ACM, 2015, pp. 10:1--10:12.
 
-% 5
+% T 5
 \bibitem{TTPDSH}
@@
 
-% 4
-\bibitem{BP}
-S. Balasubramaniam and Benjamin C. Pierce,
-``What is a File Synchronizer?''
-in \emph{Proceedings of the 4\textsuperscript{th} Annual 
-ACM/IEEE International Conference on Mobile Computing and Networking,}
-New York: ACM, 1998, pp. 98--108.
-
-% 3
-\bibitem{KRSD}
-Anne-Marie Kermarrec and Antony Rowstron and Marc Shapiro and Peter Druschel,
-``The IceCube Approach to the Reconciliation of Divergent Replicas,''
-in \emph{Proceedings of the Twentieth Annual ACM Symposium on Principles of Distributed Computing,}
-New York: ACM, 2001, pp. 210--218.
+% Z
+\bibitem{BZ}
+Bill Zissimopoulos, personal communication, August 2015.

### 2015-12-25 2015/upd-correct.tex
Reordering; improvements; new notation; improved figure

@@
 we know that the changes can be recorded as a sequence of commands $S$
-where $S\FS=\FS^*$.
+where $S\aFS=\FS^*$.
 Note that $S$ will not contain assertion commands, as they do not
@@
 we have
-$S\equiv S'\eqext S''\equiv U$, and as $S\FS = \FS^* \neq \fsbroken$,
-therefore $U\FS\neq\fsbroken$.
+$S\equiv S'\eqext S''\equiv U$, and as $S\aFS = \FS^* \neq \fsbroken$,
+therefore $U\aFS\neq\fsbroken$.
 \end{proof}

### 2015-12-25 2015/works-inverse.tex
Reordering; improvements; new notation; improved figure

@@
 \begin{align*}
-\forall \FS:&\\ 
-&B_1\FS\neq\fsbroken \wedge \cdots \wedge B_k\FS\neq\fsbroken\\
+\forall \FS:{}& 
+B_1\FS\neq\fsbroken \wedge \cdots \wedge B_k\FS\neq\fsbroken\\
 &\Rightarrow\\
@@
 \begin{mydef}[Sets of sequences]
-For brevity, we will use $\seqset{S}$ to note an arbitrary set of sequences,
-and $A\cc\seqset{S}$ to note the set of sequences $\{A\cc S|S\in\seqset{S}\}$.
+For brevity, we will use calligraphic letters (e.g. $\seqset{A, B, C}$ and $\seqset{S}$)
+to denote sets of sequences,
+and, in general, $A\cc\seqset{B}$ to note the set of sequences $\{A\cc B|B\in\seqset{B}\}$.
 \end{mydef}
@@
 
-\begin{mylem}\label{incomparable_is_independent}
-Two different commands that are not assertion commands are independent iff the nodes they change are incomparable:
-\[ \cxynv\indep\czwmv \Leftrightarrow n\unrel m \]
-if $\cxynv\neq\czwmv$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
-\end{mylem}
-\begin{proof}
-This is easy to show based on the output of the software that investigates the behavior of command pairs,
-and which we used to derive the \namecrefs{ax_separate_commute} in \cref{section_axioms}.
-However, this proposition can also be derived from the \namecrefs{ax_separate_commute} already listed
-in the following way.
-
-We proceed in two steps. First, we note that
-from \cref{ax_separate_commute,ax_separate_nobreaks} we know that
-if $n\unrel m$, then $\cxynv$ and $\czwmv$ must necessarily be independent, and therefore
-$ \cxynv\nindep\czwmv \wedge n\unrel m $ cannot be the case.
-
-Next, we prove that
-\[ \cxynv\indep\czwmv \wedge n\nunrel m \] is also impossible as it would lead to contradiction.
-As $n\nunrel m$
-we know that $n=m$, $n\descendant m$ or $m\descendant n$.
-
-If $n=m$, then from \cref{ax_same_breaks} we know $Y=Z$ and $W=X$
-as otherwise the commands, in one order or the other, would break all filesystems
-and they could not be independent.
-The commands are not assertion commands, and so from \cref{ax_same_singlec}
-we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $Y=W$ and $\valvy=\valvw$.
-Therefore $X=Y=Z=W$ which is only possible if both commands are $\cff$ and have the same
-output value. This, however, contradicts our assumption that they are different.
-
-If $n\descendant m$ or $m\descendant n$, then
-from \cref{ax_distantrel_breaks} we know that if they are not directly related,
-then $\cxynv\cc\czwmv$ breaks all filesystems, and they cannot be independent.
-From the construction and destruction pairs and 
-\cref{ax_directchild_breaks,ax_directparent_breaks} we also see that
-even if they are directly related, either
-$\cxynv\cc\czwmv$ or $\czwmv\cc\cxynv$ 
-breaks all filesystems, so they again cannot be independent.
-\end{proof}
-
 \begin{myax}\label{combine_independent_commands}
@@
 \begin{align*}
-\forall\FS: &\cxynv\indep \czwmv \\
-&\quad\wedge \cxynv\FS\neq\fsbroken \\
-&\quad\wedge \czwmv\FS\neq\fsbroken \\
-&\Rightarrow \cxynv\cc \czwmv\FS\neq\fsbroken.
+\forall\FS:{}&\cxynv\indep \czwmv \\
+&\quad\wedge \cxynv\aFS\neq\fsbroken \\
+&\quad\wedge \czwmv\aFS\neq\fsbroken \\
+&\Rightarrow \cxynv\cc \czwmv\aFS\neq\fsbroken.
 \end{align*}
@@
 We proceed in an indirect way and
-assume that $\cxynv\cc \czwmv\FS=\fsbroken$.
-We know $\cxynv\FS\neq\fsbroken$ so it must be applying 
+assume that $\cxynv\cc \czwmv\aFS=\fsbroken$.
+We know $\cxynv\aFS\neq\fsbroken$ so it must be applying 
 $\czwmv$ that breaks it.
@@
 but we know $\FS(m)\in\setvx{W}$ and so
-$(\cxynv\FS)(m)\in\setvx{W}$ as based on \cref{incomparable_is_independent}, $n\neq m$.
+$(\cxynv\aFS)(m)\in\setvx{W}$ as based on \cref{incomparable_is_independent}, $n\neq m$.
 Third, if the new filesystem violates the tree property.
@@
 Assume that there is a filesystem $\FS$ so that
-$S\FS\neq\fsbroken$ and $T\FS\neq\fsbroken$, but
+$S\aFS\neq\fsbroken$ and $T\aFS\neq\fsbroken$, but
 $(S\cc T)\FS=\fsbroken$.
@@
 
-Separately, we prove the following:
+We also prove the following:
 
@@
 \begin{mycor}\label{negneg_is_typeeq}
-$\forall \FS: (S^{-1})^{-1}\FS\typeeq \FS$.
+$\forall \FS: (S^{-1})^{-1}\aFS\typeeq S\aFS$.
 \end{mycor}
@@
 \begin{mylem}\label{r_invmove}
-A common initial segment of sequences can be moved to the other side of $\workssign$ by inverting it:
+A common initial segment of a set of sequences can be moved to the other side of $\workssign$ by inverting it:
 \begin{gather*}
-\worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \\
-\worksc{\seqset{A}}{B\cc \seqset{S}} \Rightarrow \worksc{B^{-1}\cc \seqset{A}}{\seqset{S}}
+\worksc{B\cc \seqset{A}}{\seqset{C}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{C}} \\
+\worksc{\seqset{A}}{B\cc \seqset{C}} \Rightarrow \worksc{B^{-1}\cc \seqset{A}}{\seqset{C}}
 \end{gather*}
@@
 \begin{align*}
-\forall S,\FS,\GS: &S\FS\neq\fsbroken \Rightarrow \\
-&(S\FS\ntypeeq S\GS \Leftrightarrow \FS\ntypeeq \GS).
+\forall S,\FS,\GS:{}&S\aFS\neq\fsbroken \Rightarrow \\
+&(S\aFS\ntypeeq S\aGS \Longleftrightarrow \FS\ntypeeq \GS).
 \end{align*}
@@
 For the proposition
-\[ \worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \]
+\[ \worksc{B\cc \seqset{A}}{\seqset{C}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{C}} \]
 the rest of the proof is illustrated by \cref{fig_invmove}
@@
 onto the domain of $B$.
-As $\worksc{B\cc \seqset{A}}{\seqset{S}}$ the domain of $\seqset{S}$ must be a subset of this
+As $\worksc{B\cc \seqset{A}}{\seqset{C}}$ the domain of $\seqset{C}$ must be a subset of this
 projected intersection.
-If so, then we can use $B$ to map the domain of $\seqset{S}$, which yields the domain of $B^{-1}\cc \seqset{S}$.
-As it is also a part of the domain of $A$, we get $\worksc{\seqset{A}}{B^{-1}\cc \seqset{S}}$.
+If so, then we can use $B$ to map the domain of $\seqset{C}$, which yields the domain of $B^{-1}\cc \seqset{C}$.
+As it is also a part of the domain of $A$, we get $\worksc{\seqset{A}}{B^{-1}\cc \seqset{C}}$.
 
@@
 $\worksc{(A^{-1})^{-1}\cc B\cc C}{\seqset{S}}$, which proves our lemma 
-as $\forall\FS: (A^{-1})^{-1}\FS\typeeq A\FS$ (\cref{negneg_is_typeeq}).
+as $\forall\FS: (A^{-1})^{-1}\aFS\typeeq A\aFS$ (\cref{negneg_is_typeeq}).
 \end{proof}

### 2015-12-25 2015/prove.py

@@ -750,7 +750,7 @@ class CommandPair(Sequence):
             DIRECT_PARENT_ONLY: '<<-',
             SAME:               '---'
         }
-        return self.commands[0].info() + '  ' + Dsep[self.rel] + '  ' + self.commands[1].info()
+        return self.commands[0].info() + ' ' + Dsep[self.rel] + ' ' + self.commands[1].info()
         
     def label(self):
         """Returns a short string describing some of the object"""
@@ -828,6 +828,8 @@ def checkBreaksAll(sq):
             return False
     return True
 
+
+print "Please see the documentation in the script";
 
 for rel in [SEPARATE, SAME, DISTANT_CHILD, DIRECT_CHILD, DIRECT_CHILD_ONLY, DISTANT_PARENT, DIRECT_PARENT, DIRECT_PARENT_ONLY]:
     pr_s('\n===== Relationship between nodes: ' + rel + ' =====\n')

### 2015-12-25 2015/axioms.tex
Highlighting results that the listed rules are sufficient for an implementation

@@
 
-\begin{mydef}[$A\indep B$: Independent commands, sequences and sets]
+\begin{mydef}[$A\indep B$: Independent commands, sequences and sets]\label{def_indep}
 Two commands $\cxynv$ and $\czwmv$ 

### 2015-12-25 2015/rec-intro.tex
Highlighting results that the listed rules are sufficient for an implementation

@@
 \end{align*}
-The order of commands in the sequence can be determined using the algorithm described in
-\cref{ordering} as any subset of $A$ is also simple.
-In a similar way, $\recb$ can be obtained by reversing $A$ and $B$
-in the definition.
 \end{mydef}
 
-We would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
+Whether two commands are independent is easy to determine programmatically
+either based on \cref{def_indep} and the rules listed in \cref{section_axioms},
+or based on \cref{incomparable_is_independent} 
+in at most $O(x^2)$ time, where $x$ is the number of commands.
+Then, to generate the sequence $\reca$ from the resulting set, 
+we order the commands using the algorithm described in
+\cref{ordering} as any subset of $A$ is also simple.
+
+$\recb$ can be obtained in a similar way by reversing $A$ and $B$
+in the definition.
+
+\bigskip
+
+\noindent
+Next, we would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
 that is, without loss of generality,

### 2015-12-25 2015/works-inverse.tex
Highlighting results that the listed rules are sufficient for an implementation

@@
 % intended interpretation:
-\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_k\FS\neq\fsbroken\]
+\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_k\FS\neq\fsbroken.\]
 As the sequences form a set, their order is irrelevant.
@@
 to denote sets of sequences,
-and, in general, $A\cc\seqset{B}$ to note the set of sequences $\{A\cc B|B\in\seqset{B}\}$.
+and use $A\cc\seqset{B}$ to denote the set of sequences $\{A\cc B|B\in\seqset{B}\}$.
 \end{mydef}

### 2015-12-25 2015/axioms.tex
Improved definitions

@@
 Therefore we will investigate sequences of commands with a well-defined order.
-\begin{mydef}[$\cc$ and $\emptyseq$]
+\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
 We use ``$\cc$'' to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence:

### 2015-12-25 2015/def-commands.tex
Improved definitions

@@
 As described above, we aimed to select a set of commands
-that captures as much information as possible
-about the operations, and is also symmetric.
+that captures as much information
+about the operations as possible, and is also symmetric.
 We start by summarizing our reasons for doing so.
@@
 
-We therefore have four pieces of information related to each command:
-its input type, its output type, the node to which it is applied, and finally
-the value that it stores at the node.
-We will denote commands using quadruples that list these
-in a the following format:
-% TODO convert into definition
+\begin{mydef}[Regular commands]
+Therefore we have four pieces of information related to each command,
+and represent them using quadruples that list
+their input type ($X$), output type ($Y$),
+the node to which they are applied ($n$),
+and the value they store at the node ($\valvy$):
 \[ \cxynv, \]
-where $X$ is the input type, $Y$ is the output type, $n$ is the node,
-and $\valvy$ is a value of the appropriate type from $\setvx{Y}$.
+where $\valvy\in\setvx{Y}$.
+
 We use $\cchard$, $\ccharf$ or $\ccharb$ to represent the different
-types. For example, $\cbdaa{n}{\vald}$ 
-will represent $mkdir(n,\vald)$.
-% TODO Just say "omit"
-Alternatively, we use a triple of the two types and a node if 
-there is only a single suitable output value for the given type (e.g. $\empt$).
-That is, $\cdba{n}$ will represent $rmdir(n)$.
+types, and omit the final value if it is determined by the output type
+(when it is $\empt$ or $\vald$).
+For example, $\cbdaa{n}{\vald}$ will represent $mkdir(n,\vald)$,
+and $\cdba{n}$ will represent $rmdir(n)$.
+\end{mydef}
 
@@
 filesystem no longer has the tree property, then we say that the command
-{\em breaks} the filesystem. Broken filesystems are considered equal
-(but not equal to any working filesystem), and we note them by $\FS=\fsbroken$.
+{\em breaks} the filesystem, and assigns $\fsbroken$ to it.
+Broken filesystems are considered equal, but not equal to any working filesystem.
 
 So that we could reason about sequences of commands that break every filesystem, 
-we introduce the command $\cbrk$ that simply breaks every filesystem.
+we introduce, in addition to the regular commands,
+the command $\cbrk$ that simply breaks every filesystem.
 
@@
 
-% TODO include command in def
-\begin{mydef}[Replacement operator]
-Using $\FS[\valv/n]$ we denote a filesystem derived from $\FS$:
+\begin{mydef}[Effect of commands]
+We use a \emph{replacement operator} of the form
+$\FS[\valv/n]$ to denote a filesystem derived from $\FS$:
 \[ \FS[\valv/n](m) :=
@@
 \]
-\end{mydef}
-
-The effect of the commands is as follows:
+The effect of the commands is then as follows:
 \begin{align*}
@@
 \end{align*}
+\end{mydef}
 

### 2015-12-25 2015/def-filesystem.tex
Reordering; improvements; new notation; improved figure
Improved definitions

@@
 
-We model a filesystem using a function $\FS$ with a set of nodes (filesystem paths) $\setn$ as its domain,
-and a set of possible contents or values, $\setv$, as its codomain:
+We model a working filesystem
+using a function $\FS$ with a set of nodes (filesystem paths) $\setn$ as its domain,
+and a set of possible contents or values $\setv$ as its codomain.
+Alternatively, if the filesystem has encountered a problem and is no longer usable, 
+we assign it the special value $\fsbroken$:
 \begin{mydef}[Filesystem]
-\[ \FS : \setn \rightarrow \setv \] 
+\begin{gather*}
+\FS
+\begin{cases}
+\setn \rightarrow \setv \\
+\fsbroken
+\end{cases}
+\end{gather*}
 \end{mydef}
@@
 serves as a namespace or ``skeleton'' for the filesystem, and it
-contains all possible nodes, including the ones where there is no file or directory.
-To model empty nodes, $\setv$ 
-contains a special element ($\empt$) which is the value of $\FS$ at these nodes.
-We consider the contents of files, as well as any meta-information of files
-and directories (e.g. permissions and other flags) part of the values in $\setv$.
+contains all possible nodes, including the ones where there is no file or directory,
+which we denote using a special value $\empt\in\setv$.
 
-The nodes form a disjoint union of rooted directed trees.
+The nodes form a disjoint union of rooted directed trees,
+which determines the following $\parent$ function.
 Tao et al. in \cite{TSR} describe a similar filesystem model, although
@@
 
-Every filesystem has a so-called \emph{tree property}, which means that
+Every working filesystem has a so-called \emph{tree property}, which means that
 if the filesystem is not empty at a node, and the node has a parent,
 then there must be a directory at the parent node.
+To model this, in $\setv$ we select another special value
+to represent directories, as we assume that apart from their location
+in the filesystem, all directories are equal.
+We do this because, as Bill Zissimopoulos pointed 
+out (\cite{BZ}),
+we often do not want to consider metadata stored in
+directories (e.g. permission settings) during synchronization,
+as these are not generally understood well by users,
+and, if needed, conflict resolution on these settings can be easily automated.
+We will also see that this assumption makes it possible
+to define a maximal reconciliation algorithm.
 
-To model this, in $\setv$ we distinguish between 
-file values ($\setf$) and directory values ($\setd$), that is,
-if $\setb = \{\empt\}$ then:
-\[ \setv = \setb \cup \setf \cup \setd \]
+Let therefore the value representing directories be $\vald$,
+and let us define subsets of $\setv$ for each type of value:
+let $\setd$ be $\{\vald\}$, let $\setb$ be $\{\empt\}$, 
+and let $\setf$ contain all remaining values that represent
+different file contents together with any metadata associated with them:
+\[ \setv = \setb \cup \setf \cup \setd. \]
+
 The tree property can then be defined as
@@
 \begin{align*}
-\forall n\in\setn: &\FS(n) \neq \empt \\ % TODO alignment problem
+\forall n\in\setn:{} &\FS(n) \neq \empt \\
 &\quad\wedge \parent(n) \neq \topnode \\
@@
 We use $\valf$ for an arbitrary element in $\setf$, 
-and $\vald$ for an arbitrary element in $\setd$,
 and by $\valvx$ we mean a value of type $X$ in $\setvx{X}$.
-
-% Simplification
-% --------------
-
-A simplification we will assume in this paper is regarding directories.
-As Bill Zissimopoulos pointed 
-out,\footnote{Bill Zissimopoulos, personal communication, August 2015.} 
-we often do not want to consider metadata stored in
-directories (e.g. permission settings) during synchronization,
-as these are not generally understood well by users,
-and, if needed, conflict resolution on these settings can be easily automated.
-In other words, the contents of directories are all equal,
-which can be modelled by assuming that $|\setd|=1$.

### 2015-12-25 2015/algebra.tex
Fixed typos

@@
 Similarly to \cite{NREC} we can consider creating an algebra over command sequences
-which will enable us to draw conclusions about the behaviours of the sequences
+which will enable us to draw conclusions about the behaviors of the sequences
 independently of filesystems.

### 2015-12-25 2015/comparisons.tex
Reordering; improvements; new notation; improved figure
Fixed typos

@@
 We consider the reconciliation algorithm described here an improvement over
-the one derved during our previous research (\cite{NREC})
+the one derived during our previous research (\cite{NREC})
 as the previous algorithm not only fails to propagate all possible commands
@@
 conservative policy.
-For example, if $\nn=\parent(n)$ and $\FS(\nn)=\vald$ and $\FS(n)=\valf$, and
+For example, if $\nn=\parent(n)$ and $\FS(\nn)$ is a directory and $\FS(n)$ is a file, and
 the two replicas are derived in the following way:
 \begin{gather*}
-\FS_A = \cfba{n} \cc \cdba{\nn} \FS \\
-\FS_B = \cfba{n} \FS,
+\FS_A = \cfba{n} \cc \cdba{\nn} \aFS \\
+\FS_B = \cfba{n} \aFS,
 \end{gather*}

### 2015-12-25 2015/def-commands.tex
More improvements

@@
 exact output \emph{value} of a command,
-as the success or failure of filesystem commands only depend on the types of values in the filesystem.
+as the success or failure of filesystem commands only depends on the types of values in the filesystem.
 

### 2015-12-25 2015/intro.tex
More improvements

@@
 In this paper we build on the work done 
-on command-based algebraic file synchronization
+on an algebraic approach to synchronization
 in \cite{NREC} and add to the theoretical understanding
@@
 
-A central problem of command-based synchronizers during both update detection and reconciliation
+A central problem of command-based synchronizers 
+during both update detection and reconciliation
 is ordering.
@@
 In fact, an insight in \cite{NREC} is that
-if the ordering changes the effect of two commands,
+if the ordering changes the effect of two commands (updates),
 then under certain circumstances they are not compatible and will give rise to conflicts.

### 2015-12-26 2015/axioms.tex
More improvements
Moved more definitions, clarifications

@@
 $ A\equiv B \Rightarrow A\eqext B$.
-\end{mydef}
-
-Let us also define the following relations between nodes:
-
-\begin{mydef}[$n\descendant m$]
-The partial ordering determined by the parent relation is denoted by $\descendant$:
-we write $n\descendant m$ if $n$ is the ancestor of $m$ ($n=\parent^n(m)$),
-that is, the path name of $n$ is an initial segment of that of $m$. 
-We write $n\descendantEq m$ if $n\descendant m$ or $n=m$.
-\end{mydef}
-
-\begin{mydef}[$n\unrel m$]
-We write $n\unrel m$, or ``$n$ and $m$ are incomparable'' if $n\not\descendantEq m$ and $n\not\ancestorEq m$.
-incomparable nodes are on different branches or on different trees;
-none of the path names describing their location is an initial segment of the other.
 \end{mydef}
@@
 It is intentional that we use the same symbol for independent commands
-and sequences as for incomparable nodes. As we will in the next
+and sequences as for incomparable nodes. As we will see in the next
 \namecref{incomparable_is_independent},

### 2015-12-26 2015/comparisons.tex
Moved more definitions, clarifications

@@
 
-It can be easily seen that not all conflicts detected based on the above definition
+Similarly to \cite{NREC},
+it can be easily seen that not all conflicts detected based on the above definition
 entails a conflict based on our system; that is, \cite{BP} describes a more

### 2015-12-26 2015/def-filesystem.tex
Moved more definitions, clarifications

@@
 The nodes form a disjoint union of rooted directed trees,
-which determines the following $\parent$ function.
+which determines the following $\parent$ function,
+and \emph{ancestor / descendant} and \emph{incomparable} relations.
 Tao et al. in \cite{TSR} describe a similar filesystem model, although
@@
 returns $\topnode$ if $n$ is the root of a tree.
+\end{mydef}
+
+\begin{mydef}[$n\descendant m$]
+On $\setn$ the \emph{ancestor / descendant} relation is the
+partial ordering determined by the $\parent$ function.
+We write $n\descendant m$ if $n$ is the ancestor of $m$,
+that is, $n=\parent^n(m)$ for some integer $n\ge 1$.
+% or the path name of $n$ is an initial segment of that of $m$. 
+We write $n\descendantEq m$ if $n\descendant m$ or $n=m$.
+\end{mydef}
+
+\begin{mydef}[$n\unrel m$]
+We write $n\unrel m$, or $n$ and $m$ are \emph{incomparable}
+if $n\not\descendantEq m$ and $n\not\ancestorEq m$;
+that is, incomparable nodes are on different branches or on different trees.
+% none of the path names describing their location is an initial segment of the other.
 \end{mydef}

### 2015-12-26 2015/works-inverse.tex
Moved more definitions, clarifications

@@
 and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$)
-then their input types must match ($X=Z$).
+then the input types of these commands must match ($X=Z$).
 \end{mylem}
@@
 \begin{mycor}\label{negneg_is_typeeq}
-$\forall \FS: (S^{-1})^{-1}\aFS\typeeq S\aFS$.
+$\forall S, \FS: (S^{-1})^{-1}\aFS\typeeq S\aFS$.
 \end{mycor}

### 2016-01-02 2015/abstract.tex
Added abstract

With distributed computing and mobile applications,
synchronizing divergent replicas of data is a more and more common problem.
We investigate an operation-based approach to filesystem synchronization
and further our theoretical understanding of this problem
by presenting rigorous algebraic proofs that the algorithms desribed for
update detection and reconciliation return working solutions
that cannot be improved on.

To do this, we present our filesystem model 
and a novel, symmetric set of filesystem commands
with higher information content,
which allow us to simplify our definition of conflicting updates
compared to our previous approach,
and to ensure that we propagate all updates that do not cause errors.
We also present a number of generally useful properties of sequences of commands
including introducing the concept of inverse sequences and conditional operation.

These results are essential in
determining the outcome of an
application implementing an algebraic approach to synchronization
and in ensuring that it is error-free,
and as a step towards building a more complete algebra
to describe updates to filesystems and other storage protocols.

### 2016-01-03 2015/ordering.tex
Fixed typos
Completed proof for equivalence is reordering

@@
 We prove that under the given conditions, the set must contain a command on $\parent(n)$.
-Then, by repapplying this result, we know that the set must contain commands on every
+Then, by reapplying this result, we know that the set must contain commands on every
 ancestor of $n$ up to $\nn$.
@@
 all of their valid orderings are equivalent,
-and all equivalent sequences are mere reorderings:
+and all equivalent sequences are mere reorderings.
+To prove this, first we prove the following:
+
+\begin{mylem}\label{equiv_simple_same_commands}
+If two simple sequences $A$ and $B$ are equivalent
+and do not break all filesystems ($A\equiv B\nequiv\cbrk$),
+then they must contain the same commands.
+\end{mylem}
+\begin{proof}
+We use an inverse proof. Let $A$ and $B$ simple sequences
+such that $A\equiv B\nequiv\cbrk$,
+and $\FS$ be a filesystem that they do not break.
+
+We also assume that they do not contain the same sequences.
+Without loss of generality, we can assume
+that $A$
+contains $\cxynv$, and $B$ either contains a different command
+$\czwnv$ on $n$, or no command on $n$ at all.
+As $A$ is simple, we know that $\cxynv$ is not an assertion command,
+and therefore $X\neq Y$ and $\FS(n)\neq\valvy$ as it has type $X$.
+If so, then if $B$ has no command on $n$, then $B\aFS(n)=\FS(n)$ and
+$A$ and $B$ cannot be equivalent.
+Otherwise we know that $Z=X$ as $B$ does not break $\FS$ either,
+and that $\valvw=\valvy$ and therefore $W=Y$ as $B\aFS(n)$ must
+be $\valvy$ and $B$ only has one command on $n$.
+However, then $\czwnv=\cxynv$, which is a contradiction.
+\end{proof}
 
 \begin{mylem}\label{simple_reorder_equiv}
-For any simple sequence $S\nequiv\cbrk$,
-$\forall T: T\equiv S \Leftrightarrow T\in\orderset{S}$.
+For all simple sequences $T$ and $S\nequiv\cbrk$,
+$T\equiv S \Leftrightarrow T\in\orderset{S}$.
 \end{mylem}
@@
 From these we know that all sequences in $\orderset{S}$
-are equivalent, and that any sequence $T$ outside it
+are equivalent, and that any sequence of the same commands outside it
 necessarily breaks all filesystems.
+We also know $S\in\orderset{S}$ as $S\nequiv\cbrk$
+and therefore $T\in\orderset{S} \Rightarrow T\equiv S$.
 
-Therefore if $S\nequiv\cbrk$ then $S\in\orderset{S}$,
-and $S$ cannot be equivalent to any sequence of the same commands
-not in $\orderset{S}$.
+From \cref{equiv_simple_same_commands} we know that 
+if $T\equiv S$, then $T$ contains the same commands as $S$,
+from which we see
+that $T\equiv S\Rightarrow T\in\orderset{S}$.
 \end{proof}

### 2016-01-03 2015/abstract.tex
New title, keywords, MSC, ACM classes

@@
 and further our theoretical understanding of this problem
-by presenting rigorous algebraic proofs that the algorithms desribed for
+by presenting rigorous algebraic proofs that the algorithms described for
 update detection and reconciliation return working solutions

### 2016-01-03 2015/paper.tex
Reordering; improvements; new notation; improved figure
More improvements
Added abstract
Added contact info
Capitalised references
New title, keywords, MSC, ACM classes

--- 2015-12-22 2015/paper.tex
@@
 \usepackage{tikz}
-\usepackage{cleveref}
+\usepackage[capitalise]{cleveref}
 
@@
 
-\title{Complete Algebraic File Synchronization}
-\author{Elod Pal Csirmaz}
+% fitness, validity, integrity, well-founded
+% foundation, groundwork
+\title{New Foundations and Fitness of Algebraic File Synchronization}
+\author{Elod Pal Csirmaz\\
+\texttt{\rot{\rot{maz.}{csir}{ep}com}{@}{elod}}}
 
@@
 \begin{abstract}
-Abstract goes here
+
+\input{abstract}
+
+\bigskip\noindent
+{\bf Keywords:} % (4-6)
+file synchronization,
+algebraic approach,
+distributed systems,
+reconciliation,
+data replication
+% conflict detection,
+% operation-based 
+% conflict resolution
+% computer algebra
+
+\bigskip\noindent
+{\bf MSC classes:} % http://www.ams.org/mathscinet/msc/msc2010.html
+08A70, % Applications of universal algebra in computer science
+68M07, % Mathematical problems of computer architecture
+68M14, % Distributed systems
+68P05, % Data structures
+68P20 % Information storage and retrieval
+% 68N25         Operating systems
+
+\bigskip\noindent
+{\bf ACM classes:} % http://www.acm.org/about/class/ccs98-html
+% (D) Software (D.4) Operating systems
+D.4.3, % File systems management
+% (E) Data
+E.5, % Files
+% (F) Theory of computation (F.2) ANALYSIS OF ALGORITHMS AND PROBLEM COMPLEXITY
+F.2.2, % Nonnumerical Algorithms and Problems
+% (G) Mathematics of Computing
+G.2 % DISCRETE MATHEMATICS
+% (H) Information Systems (H.3) INFORMATION STORAGE AND RETRIEVAL
+% H.3.4 % Systems and Software
+
 \end{abstract}
 
+% section
 \input{intro}
@@
 
+% section
 \input{axioms}
@@
 
+% section
 \input{comparisons}
 
-\section{Further Research}
-
-TODO: next steps. multiple replicas
-
+% section
 \input{algebra}
 
-\section{Conclusions}
-
-% TODO
-Conclusions go here
+% section
+\input{conclusion}
 

### 2016-01-03 2015/intro.tex
New title and mentions

@@
 
-In this paper we build on the work done 
+In this paper we build on our previous work done 
+with Prof. Norman Ramsey
 on an algebraic approach to synchronization
-in \cite{NREC} and add to the theoretical understanding
+(\cite{NREC}),
+and add to the theoretical understanding
 of synchronization by providing rigorous proofs that the algorithms

### 2016-01-03 2015/paper.tex
New title and mentions

@@
 
-% fitness, validity, integrity, well-founded
-% foundation, groundwork
-\title{New Foundations and Fitness of Algebraic File Synchronization}
+\title{Algebraic File Synchronization: Adequacy and Completeness}
 \author{Elod Pal Csirmaz\\
@@
 
-I thank Laszlo Csirmaz for his invaluable input on previous drafts of this paper,
+I thank Laszlo Csirmaz for his invaluable input on this paper,
 and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.

### 2016-01-03 2015/abstract.tex
Improved abstract

--- 2016-01-02 2015/abstract.tex
@@
 With distributed computing and mobile applications,
-synchronizing divergent replicas of data is a more and more common problem.
-We investigate an operation-based approach to filesystem synchronization
-and further our theoretical understanding of this problem
-by presenting rigorous algebraic proofs that the algorithms desribed for
-update detection and reconciliation return working solutions
-that cannot be improved on.
+synchronizing divergening replicas of data structures is a more and more common problem.
+We use algebraic methods to reason about filesystem operations, 
+and introduce a simplified definition of conflicting updates.
+We also define algorithms for update detection and reconciliation
+and present rigorous proofs that they not only work as intended,
+but also cannot be improved on.
 
-To do this, we present our filesystem model 
-and a novel, symmetric set of filesystem commands
+To achieve this, we introduce a novel, symmetric set of filesystem commands
 with higher information content,
-which allow us to simplify our definition of conflicting updates
-compared to our previous approach,
-and to ensure that we propagate all updates that do not cause errors.
-We also present a number of generally useful properties of sequences of commands
-including introducing the concept of inverse sequences and conditional operation.
+which removes edge cases
+and increases the predictive powers of our algebraic model.
+We also present a number of generally useful classes and properties
+of sequences of commands.
 
-These results are essential in
-determining the outcome of an
-application implementing an algebraic approach to synchronization
-and in ensuring that it is error-free,
-and as a step towards building a more complete algebra
-to describe updates to filesystems and other storage protocols.
+These results are often intuitive,
+but providing exact proofs for them is far from trivial.
+They contribute to our understanding of this special type of algebraic model,
+and toward building a more complete algebra
+of filesystems and other storage protocols.
+They also form a theoretical basis for
+specifying
+and guaranteeing the error-free operation
+of applications that implement operation-based approaches to synchronization.

### 2016-01-04 i/lawproof.tex
Renamed directories

%% Example proof for law
\section{Soundness proofs for individual laws}
\label{app:soundness}

%{\small{
In this section we provide examples how algebraic laws can be proved.
The method we use is to consider as many cases as necessary to be able to
predict the result of each command in the law. For example, if the law
contains paths \(\pi\) and \(\pisub\) then we'll consider 
22 cases; see below.
\remark{...}
(Note that we listed all cases considering how \(\pisub\) can relate to
\(\pi\) and if they have children or a parent. Also, we considered the
case when \(F(\pi)\) has
only one child and it is \(F(\pisub)\) since in that case, modifying
\(F(\pisub)\) can make \(F(\pi)\) childless.)

If the law contains an \(edit\) command, we also distinguish
between files and directories. If we determine the result of the sequence
of commands of the left side in each case and this is the same as that of
the right side, then the law holds.

Now we provide an example proof on law 18. We will only investigate the
left side of the law, since the right side always gives the broken
filesystem.

\begin{forrsi*}
\begin{singlesp}
\end{forrsi*}
\begin{multicols}{3}
{\tiny{
\input{cases}
}}
\end{multicols}
\begin{forrsi*}   
\end{singlesp}
\end{forrsi*}
%}}

### 2016-01-04 ii/axioms.tex
Renamed directories

--- 2015-12-26 2015/axioms.tex
@@
 program\footnote{The program is accessible on-line at \\
-https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/2015/prove.py.}
+https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/ii/prove.py.}
 to determine

### 2016-01-04 ii/comparisons.tex
Renamed directories

--- 2015-12-25 2015/comparisons.tex
@@
 
+% TODO Transparency in re-use
+
 As a test of the proposed reconciliation algorithm, 
@@
 in their state-based approach (\cite{BP}).
-The update detector they describe provides a safe estimate of nodes
+As we noted in \cite{NREC}, the update detector they describe provides a safe estimate of nodes
 (paths) at which updates occurred.
@@
 conservative policy.
-For example, if $\nn=\parent(n)$ and $\FS(\nn)$ is a directory and $\FS(n)$ is a file, and
+We use the example we described in \cite{NREC},
+where $\nn=\parent(n)$ and $\FS(\nn)$ is a directory and $\FS(n)$ is a file, and
 the two replicas are derived in the following way:
@@
 \FS_A = \cfba{n} \cc \cdba{\nn} \aFS \\
-\FS_B = \cfba{n} \aFS,
+\FS_B = \cfba{n} \aFS.
 \end{gather*}
-then $\nn$ is dirty in both replicas:
+Then, $\nn$ is dirty in both replicas:
 in $\FS_A$ it was modified, and in $\FS_B$ one of its descendants was modified.

### 2016-01-04 ii/ordering.tex
Renamed directories

--- 2016-01-03 2015/ordering.tex
@@
 and which can be applied to a filesystem in some order without breaking it,
-and which contains commands on $n$ and $\nn$ where $\nn\descendant n$
-but $\nn\neq\parent(n)$, then the set must also contain a command
+and which contains commands on $n$ and $\nn$ where $\nn\descendant n$,
+then the set must also contain a command
 on each node between $n$ and $\nn$.
@@
 \begin{proof}
+Without loss of generality, we can assume that $\nn\neq\parent(n)$.
 We prove that under the given conditions, the set must contain a command on $\parent(n)$.

### 2016-01-04 ii/rec-intro.tex
Renamed directories

--- 2015-12-25 2015/rec-intro.tex
@@
 the largest subset of $A\setminus B$
-that is independent of $B\setminus A$:
+that is independent of $B\setminus A$,
+where $A$ and $B$ are simple sequences representing
+the updates applied to replicas $\FS_A$ and $\FS_B$:
 \begin{align*}
@@
 Then, to generate the sequence $\reca$ from the resulting set, 
-we order the commands using the algorithm described in
+we can order the commands using the algorithm described in
 \cref{ordering} as any subset of $A$ is also simple.

### 2016-01-04 ii/upd-def.tex
Renamed directories

--- 2015-12-23 2015/upd-def.tex
@@
 
-\begin{mydef}{Minimal set or sequence.}
+\begin{mydef}[Minimal set or sequence]
 A sequence or set of commands is minimal if it contains at most one command on each node.
@@
 
-\begin{mydef}{Simple set or sequence.}
+\begin{mydef}[Simple set or sequence]
 A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.

### 2016-01-04 ii/works-inverse.tex
Renamed directories

--- 2015-12-26 2015/works-inverse.tex
@@
 \begin{proof}
-This is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
+This result is similar to \cref{equiv_simple_same_commands} and
+is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
 either $\cxynv$ or $\czwnv$ would not break, 

### 2016-01-04 ii/prove.py

@@ -3,7 +3,7 @@ import sys
 
 """
 This script is part of the paper available at
-https://github.com/csirmaz/AlgebraicSyncPaper
+https://github.com/csirmaz/AlgebraicSyncPaper/ii/
 
 It is used to test pairs of commands on filesystems and determine
 (1) if they break all filesystems, 
@@ -49,7 +49,7 @@ Finally, the script prints rules for substituting command pairs with single comm
 whenever the single command is not "break".
 
 
-Copyright (c) 2015 Elod Pal Csirmaz
+Copyright (c) 2016 Elod Pal Csirmaz
 
 Permission is hereby granted, free of charge, to any person obtaining a copy
 of this software and associated documentation files (the "Software"), to deal

### 2016-01-05 ii/comparisons.tex
New reference

@@
 Clearly $\cbfaa{n}{\valf}$ could be applied to $\FS_B$, but it is not as
-it must be preceded by creating the directory, which conflicts with the same operation in $B$
+it must be preceded by creating the directory, which conflicts with the same command in $B$
 due to the different value.
@@
 
-% TODO Transparency in re-use
-
 As a test of the proposed reconciliation algorithm, 
@@
 updates to how conflicts are defined by Balasubramaniam and Pierce
-in their state-based approach (\cite{BP}).
+in their state-based approach implemented in the Unison synchronizer (\cite{BP}).
 As we noted in \cite{NREC}, the update detector they describe provides a safe estimate of nodes
@@
 are also dirty (Fact 3.1.3 in \cite{BP}).
-And finally, a conflict is detected between replicas $\FS_A$ and $\FS_B$ at node $n$
+And finally, in our notation, 
+a conflict is detected between replicas $\FS_A$ and $\FS_B$ at node $n$
 if $n$ is marked as dirty in both $\FS_A$ and $\FS_B$, and
-$\FS_A(n)\neq\FS_B(n)$, and $n$ does not point to a directory in both replicas
-($\FS_A(n)\not\in\setd \vee \FS_B(n)\not\in\setd$; see section 4.1 in \cite{BP}).
+$\FS_A(n)\neq\FS_B(n)$, and $n$ does not point to a directory in both replicas.
+(In other words, 
+$\FS_A(n)\not\in\setd \vee \FS_B(n)\not\in\setd$; see section 4.1 in \cite{BP}.
+Let us not that there is an alternative approach to defining an algorithm for
+the same synchronizer by Pierce and Vouillon in \cite{PV}.)
 
-It can be easily seen that not all conflicts detected based on the above definition
+It can be easily seen that due to an edge case, 
+not all conflicts detected based on the above definition
 entails a conflict based on our system; that is, \cite{BP} describes a more

### 2016-01-05 ii/references.tex
New reference

--- 2015-12-25 2015/references.tex
@@
 
+% C 8
+\bibitem{CJ}
+Russ Cox and William Josephson,
+``File synchronization with Vector Time Pairs,''
+MIT CSAIL Technical Report,
+Cambridge, MA: MIT,
+2005.
+Accessed 22 November 2015.
+http://hdl.handle.net/1721.1/30527.
+
 % K 3
@@
 New York: ACM, 2001, pp. 210--218.
+
+% P 6
+\bibitem{PPRS}
+% Parker, D. S. and Popek, G. J. and Rudisin, G. and Stoughton, A. and Walker, B. J. and Walton, E. and Chow, J. M. and Edwards, D. and Kiser, S. and Kline, C.
+D. S. Parker et al.,
+``Detection of Mutual Inconsistency in Distributed Systems,''
+in \emph{IEEE Trans. Softw. Eng.,}
+vol. 9, no. 3,
+Piscataway, NJ: IEEE Press,
+May 1983,
+pp. 240--247.
+
+% P 14
+\bibitem{PV}
+Benjamin C Pierce and J{\'e}r{\^o}me Vouillon,
+``What's in Unison? A formal specification and reference implementation of a file synchronizer,''
+\emph{Technical Reports (CIS),}
+Paper 40,
+Philadelphia, PA: U of Pennsylvania,
+2004.
+Accessed 23 November 2015.
+http://repository.upenn.edu/cis\texttt{\detokenize{_}}reports/40.
 

### 2016-01-05 p1/conclusion.tex
Renamed directories

%% Conclusion
\section{Conclusion}

We have built an algebra of commands on filesystems. We have proved that the
algebra is sound and complete, that is, sequences of commands which are algebraically
equivalent are also equivalent on real filesystems, and vice
versa.

We have defined conflicts with the help of this algebra, and defined
algorithms for update detection and reconciliation. We have also
implemented these algorithms and tested them on numerous cases (see
Appendix \ref{app:impl}). The results have always been in accordance with what
we expected from the philosophy ``propagate every command possible on
every replica''.  Using algebraical methods in file
synchronization has turned out to be an effective solution.

We have also gained some information about the provability of such theorems and
algebras. The methods we have used in the proofs are likely be able to be used
in proofs for other algebras as well, thus they may form the basis for
a more general theory of synchronization.

### 2016-01-05 p2/abstract.tex
Renamed directories

--- 2016-01-03 2015/abstract.tex
@@
 We use algebraic methods to reason about filesystem operations, 
-and introduce a simplified definition of conflicting updates.
+and introduce a simplified definition of conflicting updates to filesystem trees.
 We also define algorithms for update detection and reconciliation
@@
 and guaranteeing the error-free operation
-of applications that implement operation-based approaches to synchronization.
+of applications that implement an algebraic approach to synchronization.

### 2016-01-05 p2/axioms.tex
Renamed directories

--- 2016-01-04 ii/axioms.tex
@@
 program\footnote{The program is accessible on-line at \\
-https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/ii/prove.py.}
+https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/p2/prove.py.}
 to determine

### 2016-01-05 p2/conclusion.tex
Renamed directories

--- 2015-12-25 2015/conclusion.tex
@@
 A related problem is to model cases where reconciliation cannot
-complete fully (due to a system or network failure, for example)
-or if only a subset of the replicas are reconciled,
+complete fully
+or if only a subset of the replicas are reconciled 
+(e.g. due to network partitioning),
 both of which would result in a state where different replicas
@@
 in the update history of the filesystem.
-Identifying the information one needs to keep to perform
-update detection in such cases and devising a suitable algorithm
-would be beneficial for any implementation of a reconciler
-based on the ideas presented here.
+Parker et al. (\cite{PPRS}) and Cox and Josephson (\cite{CJ})
+describe version vectors (update histories) kept as metadata that could solve this problem.
+Extending the algebraic approach to represent individual updates to files
+in their modification histories (as described in \cite{CJ})
+as separate commands could also enable it to reconcile otherwise
+conflicting updates and resolve partial reconciliations.
 

### 2016-01-05 p2/def-filesystem.tex
Renamed directories

--- 2015-12-26 2015/def-filesystem.tex
@@
 \begin{gather*}
-\FS
+\FS =
 \begin{cases}
@@
 In our model, $\setn$ 
-serves as a namespace or ``skeleton'' for the filesystem, and it
-contains all possible nodes, including the ones where there is no file or directory,
-which we denote using a special value $\empt\in\setv$.
+serves as a namespace or ``skeleton'' for the filesystem.
+It contains all possible nodes, including the ones 
+where the file system contains no file or directory,
+where in our model $\FS$ has a special value, $\empt\in\setv$.
 

### 2016-01-05 p2/intro.tex
Renamed directories

--- 2015-12-25 2015/intro.tex
@@
 
-In this paper we investigate an operation- or command-based approach
-to filesystem synchronization.
+In this paper we investigate a command-based approach
+to synchronizing filesystem trees.
 Presented with multiple copies (replicas) of the same filesystem that have been independently modified,
@@
 
-In this paper we build on the work done 
+In this paper we build on previous work done 
+by Ramsey and Csirmaz
 on an algebraic approach to synchronization
-in \cite{NREC} and add to the theoretical understanding
+(\cite{NREC}),
+and add to the theoretical understanding
 of synchronization by providing rigorous proofs that the algorithms

### 2016-01-05 p2/rec-complete.tex
Renamed directories

--- 2015-12-25 2015/rec-complete.tex
@@
 Let us therefore suppose $n\neq m$ and, to use an inverse proof,
-that the sequence works on $\FS$ where $A\FS\neq\fsbroken$.
+that the sequence works on $\FS$ where $A\aFS\neq\fsbroken$.
 If so, its initial segment, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also work.
@@
 changing $\FS(m)$ first.
-As $A\FS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
+As $A\aFS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
 Let this command be $\cqrmv$.

### 2016-01-05 p2/upd-correct.tex
Renamed directories

--- 2015-12-25 2015/upd-correct.tex
@@
 
-Based on \cref{ax_same_emptyseq,ax_same_singlec} there is
+Applying \cref{ax_same_emptyseq,ax_same_singlec} we can
+convert $S'$ into
 an $S''\eqnrw S'$ in which multiple commands on the same nodes
@@
 \end{proof}
+
+An important consequence of this proof is that any sequence
+of recorded updates that were applied to a filesystem can be
+converted to a simple sequence using the rules listed in
+\cref{section_axioms} alone.

### 2016-01-05 p2/prove.py

@@ -3,7 +3,7 @@ import sys
 
 """
 This script is part of the paper available at
-https://github.com/csirmaz/AlgebraicSyncPaper/ii/
+https://github.com/csirmaz/AlgebraicSyncPaper/p2/
 
 It is used to test pairs of commands on filesystems and determine
 (1) if they break all filesystems, 

### 2016-01-05 p2/rec-intro.tex
Style updates

--- 2016-01-04 ii/rec-intro.tex
@@
 If we start with two copies of the filesystem $\FS$,
-and two different sequences are applied to the copies to yield $\FS_A:=A\aFS$
-and $\FS_B:=B\aFS$, then our aim is to define sequences of commands $\reca$ and $\recb$
+and two different sequences are applied to the copies to yield $\FS_A=A\aFS$
+and $\FS_B=B\aFS$, then our aim is to define sequences of commands $\reca$ and $\recb$
 so that $\recb\aFS_A$ and $\reca\aFS_B$ would be as close to each other as possible.

### 2016-01-05 p2/references.tex
Fixed typos
New reference

--- 2015-12-21 2015/references.tex
@@
-\bibitem{NREC} 
-Norman Ramsey and Elod Csirmaz,
-``An Algebraic Approach to File Synchronization,''
-in \emph{Proceedings of the Joint 8\textsuperscript{th} European Software Engineering Conference 
-and 9\textsuperscript{th} ACM SIGSOFT Symposium on the Foundations of Software Engineering,}
-New York: ACM, 2001, pp. 175--185.
+% B 4
+\bibitem{BP}
+S. Balasubramaniam and Benjamin C. Pierce,
+``What is a File Synchronizer?''
+in \emph{Proceedings of the 4\textsuperscript{th} Annual 
+ACM/IEEE International Conference on Mobile Computing and Networking.}
+New York, NY: ACM, 1998, pp. 98--108.
 
+% B 21
 \bibitem{CBNR} 
@@
 Accessed 29 November 2015.
-http://thirld.com/files/summerscholars\_techreport.pdf.
+http://thirld.com/files/summerscholars\undersc techreport.pdf.
 
-% 5
+% C 8
+\bibitem{CJ}
+Russ Cox and William Josephson,
+``File synchronization with Vector Time Pairs,''
+MIT CSAIL Technical Report.
+Cambridge, MA: MIT,
+2005.
+Accessed 22 November 2015.
+http://hdl.handle.net/1721.1/30527.
+
+% K 3
+\bibitem{KRSD}
+Anne-Marie Kermarrec and Antony Rowstron and Marc Shapiro and Peter Druschel,
+``The IceCube Approach to the Reconciliation of Divergent Replicas,''
+in \emph{Proceedings of the Twentieth Annual ACM Symposium on Principles of Distributed Computing.}
+New York, NY: ACM, 2001, pp. 210--218.
+
+% P 6
+\bibitem{PPRS}
+% Parker, D. S. and Popek, G. J. and Rudisin, G. and Stoughton, A. and Walker, B. J. and Walton, E. and Chow, J. M. and Edwards, D. and Kiser, S. and Kline, C.
+D. S. Parker et al.,
+``Detection of Mutual Inconsistency in Distributed Systems,''
+in \emph{IEEE Trans. Softw. Eng.,}
+vol. 9, no. 3.
+Piscataway, NJ: IEEE Press,
+May 1983,
+pp. 240--247.
+
+% P 14
+\bibitem{PV}
+Benjamin C Pierce and J{\'e}r{\^o}me Vouillon,
+``What's in Unison? A formal specification and reference implementation of a file synchronizer,''
+\emph{Technical Reports (CIS),}
+Paper 40.
+Philadelphia, PA: U of Pennsylvania,
+2004.
+Accessed 23 November 2015.\\
+http://repository.upenn.edu/cis\undersc reports/40.
+
+% R
+\bibitem{NREC} 
+Norman Ramsey and Elod Csirmaz,
+``An Algebraic Approach to File Synchronization,''
+in \emph{Proceedings of the Joint 8\textsuperscript{th} European Software Engineering Conference 
+and 9\textsuperscript{th} ACM SIGSOFT Symposium on the Foundations of Software Engineering.}
+New York, NY: ACM, 2001, pp. 175--185.
+
+% S 12
+\bibitem{SSH}
+Yasushi Saito and Marc Shapiro,
+``Optimistic Replication,''
+in \emph{ACM Computing Surveys,}
+vol. 37, no. 1.
+New York, NY: ACM, March 2005,
+pp. 42--81.
+
+% T 1
+\bibitem{TSR}
+Vinh Tao and Marc Shapiro and Vianney Rancurel,
+``Merging Semantics for Conflict Updates in Geo-distributed File Systems,''
+in \emph{Proceedings of the 8\textsuperscript{th}
+ ACM International Systems and Storage Conference.}
+New York, NY: ACM, 2015, pp. 10:1--10:12.
+
+% T 5
 \bibitem{TTPDSH}
@@
 ``Managing Update Conflicts in Bayou, a Weakly Connected Replicated Storage System,''
-in \emph{Proceedings of the Fifteenth ACM Symposium on Operating Systems Principles,}
+in \emph{Proceedings of the Fifteenth ACM Symposium on Operating Systems Principles.}
 New York, NY: ACM, 1995, pp. 172--182.
 
-% 4
-\bibitem{BP}
-S. Balasubramaniam and Benjamin C. Pierce,
-``What is a File Synchronizer?''
-in \emph{Proceedings of the 4\textsuperscript{th} Annual 
-ACM/IEEE International Conference on Mobile Computing and Networking,}
-New York: ACM, 1998, pp. 98--108.
-
-% 3
-\bibitem{KRSD}
-Anne-Marie Kermarrec and Antony Rowstron and Marc Shapiro and Peter Druschel,
-``The IceCube Approach to the Reconciliation of Divergent Replicas,''
-in \emph{Proceedings of the Twentieth Annual ACM Symposium on Principles of Distributed Computing,}
-New York: ACM, 2001, pp. 210--218.
+% Z
+\bibitem{BZ}
+Bill Zissimopoulos, private communication, August 2015.

### 2016-01-05 p2/conclusion.tex
New source

@@
 % Further research
+% TODO Merge with other ideas?
 
@@
 Parker et al. (\cite{PPRS}) and Cox and Josephson (\cite{CJ})
-describe version vectors (update histories) kept as metadata that could solve this problem.
+describe version vectors (update histories) kept as metadata that could solve this problem,
+while Chong and Hamadi present distributed algorithms that allow incremental synchronization (\cite{CH}).
 Extending the algebraic approach to represent individual updates to files

### 2016-01-05 p2/intro.tex
New reference
New source

@@
 during both update detection and reconciliation
-is ordering.
+is the ordering (scheduling) of commands.
 If update detection is based on comparing the original state of the filesystem
@@
 or in Bayou reconciling updates happens by redoing them in an acceptable order \cite{TTPDSH}.
+Saito and Shapiro offer a survey of so-called optimistic replication algorithms in which
+ordering (scheduling) plays a central role (\cite{SSH}).
 

### 2016-01-05 p2/references.tex
New source

@@
 ``Summer Scholars Technical Report,''
-Medford, MA: Tufts University, 2010.
+Tufts University, Medford, MA, 2010.
 Accessed 29 November 2015.
 http://thirld.com/files/summerscholars\undersc techreport.pdf.
+
+% C 16
+\bibitem{CH}
+Yek Loong Chong and Youssef Hamadi,
+``Distributed Algorithms for Log-based Reconciliation,''
+Microsoft Research, Microsoft Co., Redmond, WA,
+Tech. Rep. MSR-TR-2004-104, 2004.
 
@@
 ``File synchronization with Vector Time Pairs,''
-MIT CSAIL Technical Report.
-Cambridge, MA: MIT,
-2005.
-Accessed 22 November 2015.
-http://hdl.handle.net/1721.1/30527.
+MIT CSAIL, Cambridge, MA, 
+Tech. Rep., MIT-CSAIL-TR-2005-014, 2005.
+% Accessed 22 November 2015.
+% http://hdl.handle.net/1721.1/30527.
 
@@
 ``What's in Unison? A formal specification and reference implementation of a file synchronizer,''
-\emph{Technical Reports (CIS),}
-Paper 40.
-Philadelphia, PA: U of Pennsylvania,
+U of Pennsylvania,
+Philadelphia, PA,
+Technical Reports (CIS),
+Paper 40,
 2004.

### 2016-01-06 p2/intro.tex
New reference

@@
 Accordingly, in this paper command-pairs and their properties
-play a special role.
+play a special role
+as we aim to find valid orderings on filesystem trees
+(also known as semantic scheduling)
+as opposed to syntactic scheduling that follows the strict temporal order
+of updates and may give rise to otherwise resolvable conflicts (\cite{SSH}).
 Other research also shows the essential nature of ordering:
-in IceCube multiple orders are tested to find an acceptable one \cite{KRSD},
+Saito and Shapiro offer a survey of so-called optimistic replication algorithms in which
+it plays a central role (\cite{SSH});
+in IceCube multiple orders are tested to find an acceptable one (\cite{KRSD}, see also \cite{MPV}),
 or in Bayou reconciling updates happens by redoing them in an acceptable order \cite{TTPDSH}.
-Saito and Shapiro offer a survey of so-called optimistic replication algorithms in which
-ordering (scheduling) plays a central role (\cite{SSH}).
 

### 2016-01-06 p2/abstract.tex
Fixed typos
New references and intro

@@
 With distributed computing and mobile applications,
-synchronizing divergening replicas of data structures is a more and more common problem.
+synchronizing diverging replicas of data structures is a more and more common problem.
 We use algebraic methods to reason about filesystem operations, 
@@
 They contribute to our understanding of this special type of algebraic model,
-and toward building a more complete algebra
-of filesystems and other storage protocols.
+and toward building more complete algebras
+of filesystems 
+and extedning algebraic approaches to other data storage protocols.
 They also form a theoretical basis for

### 2016-01-06 p2/comparisons.tex
Fixed typos
New references and intro

--- 2016-01-05 ii/comparisons.tex
@@
 $\FS_A(n)\not\in\setd \vee \FS_B(n)\not\in\setd$; see section 4.1 in \cite{BP}.
-Let us not that there is an alternative approach to defining an algorithm for
+Let us note that there is an alternative approach to defining an algorithm for
 the same synchronizer by Pierce and Vouillon in \cite{PV}.)
@@
 and therefore a conflict is detected at $\nn$.
+(This behaviour is preserved in the more recent Harmony synchronizer.
+See ``delete/delete conflicts'' in \cite{PSG,FGKPS}.)
 Our reconciliation algorithm detects no conflicts;

### 2016-01-06 p2/intro.tex
New references and intro

--- 2016-01-05 p2/intro.tex
@@
 update detection, where we identify modifications that have been applied to the replicas
-since they diverged,
-and reconciliation, where we identify updates that can be propagated to other replicas and do so.
-The remaining updates, which could not be propagated, are conflicting updates;
+since they diverged and represent these as sequences of commands,
+and reconciliation, where we identify commands that can be propagated to other replicas and do so.
+The remaining commands, which could not be propagated, represent conflicting updates;
 resolving these requires a separate system or human intervention.
@@
 (for example, a directory needs to be created before a file can be created under it).
-Similarly, during reconciliation when we consider all the updates that
+Similarly, during reconciliation when we consider all the commands that
 have been applied to the different replicas, we need to find a way of
@@
 In fact, an insight in \cite{NREC} is that
-if the ordering changes the effect of two commands (updates),
+if the ordering changes the effect of two commands,
 then under certain circumstances they are not compatible and will give rise to conflicts.
 Accordingly, in this paper command-pairs and their properties
-play a special role.
-Other research also shows the essential nature of ordering:
-in IceCube multiple orders are tested to find an acceptable one \cite{KRSD},
-or in Bayou reconciling updates happens by redoing them in an acceptable order \cite{TTPDSH}.
-Saito and Shapiro offer a survey of so-called optimistic replication algorithms in which
-ordering (scheduling) plays a central role (\cite{SSH}).
+play a special role
+as we aim to find valid orderings on filesystem trees.
 
-In \cref{sec_def} we define a model of filesystems and a set of commands
-that we will use to describe updates and modifications.
+In terms of the usual classification of synchronizers (\cite{TSR, PV, SSH}),
+our approach to reconciliation is therefore operation-based as we investigate sets of commands,
+while the update detection algorithm makes the full synchronizer 
+similar to state-based synchronizers 
+as its starting point is the states of the replicase themselves.
+Moreover, our ordering algorithms only depend on the properties of commands 
+such as commutativity or idempotence,
+and therefore they can be classified as semantic schedulers.
+This is in opposition to syntactic scheduling, which uses 
+the origin and original temporal order of updates, 
+and which may give rise to otherwise resolvable conflicts (\cite{SSH}).
+Ordering plays a central role in other operation-based synchronizers.
+We refer to a survey by Saito and Shapiro of so-called optimistic replication algorithms (\cite{SSH});
+or, in particular,
+to IceCube, where multiple orders are tested to find an acceptable one (\cite{KRSD}, see also \cite{MPV}),
+or Bayou, where reconciling updates happens by redoing them in a globally determined order \cite{TTPDSH}.
+
+We start by defining a model of filesystems and a set of commands
+that we will use to describe updates and modifications in \cref{sec_def}.
 This is followed by investigating the properties and behaviors

### 2016-01-06 p2/references.tex
New reference
New references and intro

@@
 Tech. Rep., MIT-CSAIL-TR-2005-014, 2005.
-% Accessed 22 November 2015.
-% http://hdl.handle.net/1721.1/30527.
+Accessed 22 November 2015.
+http://hdl.handle.net/1721.1/30527.
+
+% F 18
+\bititem{FGKPS}
+% Foster, J Nathan and Greenwald, Michael B and Kirkegaard, Christian and Pierce, Benjamin C and Schmitt, Alan
+J. Nathan Foster et al.,
+``Schema-directed data synchronization,''
+U of Pennsylvania,
+Philadelphia, PA,
+Technical Reports (CIS),
+Paper 5,
+2005.
+Accessed 23 November 2015.\\
+http://repository.upenn.edu/cis\undersc reports/5.
 
@@
 New York, NY: ACM, 2001, pp. 210--218.
+
+% M 19
+\bibitem{MPV}
+Vidal Martins and Esther Pacitti and Patrick Valduriez,
+``Distributed semantic reconciliation of replicated data,''
+in \emph{Proc. of CDUR.}
+Paris, France: CNAM,
+2005,
+pp. 48--53.
 
@@
 http://repository.upenn.edu/cis\undersc reports/40.
+
+% P 9
+\bibitem{PSG}
+Benjamin C. Pierce, Alan Schmitt, and Michael B. Greenwald, 
+``Bringing Harmony to Optimism: An Experiment in Synchronizing Heterogeneous Tree-Structured Data,''
+U of Pennsylvania,
+Philadelphia, PA,
+Technical Reports (CIS),
+Paper 39,
+2004.
+Accessed 23 November 2015.\\
+http://repository.upenn.edu/cis\undersc reports/39.
 

### 2016-01-06 p2/abstract.tex
Fix typo

@@
 of filesystems 
-and extedning algebraic approaches to other data storage protocols.
+and extending algebraic approaches to other data storage protocols.
 They also form a theoretical basis for

### 2016-01-06 p2/intro.tex
Fix typo

@@
 similar to state-based synchronizers 
-as its starting point is the states of the replicase themselves.
+as its starting point is the states of the replicas themselves.
 Moreover, our ordering algorithms only depend on the properties of commands 

### 2016-01-07 p2/comparisons.tex
Finished conclusion

@@
 We consider the reconciliation algorithm described here an improvement over
-the one derived during our previous research (\cite{NREC})
+the one derived during our previous research \cite{NREC}
 as the previous algorithm not only fails to propagate all possible commands
@@
 updates to how conflicts are defined by Balasubramaniam and Pierce
-in their state-based approach implemented in the Unison synchronizer (\cite{BP}).
+in their state-based approach implemented in the Unison synchronizer \cite{BP}.
 As we noted in \cite{NREC}, the update detector they describe provides a safe estimate of nodes

### 2016-01-07 p2/conclusion.tex
New reference
New references and intro
Finished conclusion

--- 2016-01-05 p2/conclusion.tex
@@
 \section{Conclusions and Further Research}
-
-% TODO
-... ... ...
-
-(Same approach to other systems)
-\medskip
-
-% Further research
 
@@
 there are many other ways in which further work can extend the current results.
-We think one of the most interesting extensions would be to
+An important extension would be to
 consider reconciling not only two, but more replicas in a single step and
 prove the correctness and maximality of the algorithm proposed.
-A related problem is to model cases where reconciliation cannot
+
+A related problem is to extend the system and the proofs
+to allow for cases where reconciliation cannot
 complete fully
@@
 in the update history of the filesystem.
-Parker et al. (\cite{PPRS}) and Cox and Josephson (\cite{CJ})
-describe version vectors (update histories) kept as metadata that could solve this problem.
-Extending the algebraic approach to represent individual updates to files
+Existing research can offer pointers as to how such cases can be modelled
+in our algebraic system.
+Parker et al. \cite{PPRS} and Cox and Josephson \cite{CJ}
+describe version vectors (update histories) kept as metadata,
+while Chong and Hamadi present distributed algorithms that allow incremental synchronization \cite{CH}.
+Representing individual updates to files
 in their modification histories (as described in \cite{CJ})
-as separate commands could also enable it to reconcile otherwise
+as separate commands could also enable an algebraic synchronizer to reconcile otherwise
 conflicting updates and resolve partial reconciliations.
 
-An extension of these results could also entail relaxing
+An extension of our results could also entail relaxing
 the simplifying assumptions we used.
 Identifying which results depend on the assumption that $|\setd|=1$
-and devising updated proofs or algorithms,
-or a pre-processing step that reconciles meta-information in directories
-can enable the algebraic system or an implementation
+and devising updated proofs and algorithms,
+or specifying a pre-processing step that reconciles meta-information in directories
+can enable the synchronizer
 to identify and resolve a wider range of conflicts.
 Similarly, designing pre- and post-processors that
-present certain changes not as removal and creation of a node,
-but as a rename,
+present removing and creating a node
+not as separate updates but as a single rename (move),
 could contribute to the user-friendliness of the reconciler
 and help avoid human error.
+
+And finally, we hope that this work, together with \cite{NREC}, provides
+a blueprint of constructing an algebra of commands for different storage protocols
+(e.g. XML trees, mailbox folders, generic relational databases, etc.),
+and of demonstrating the adequacy and completeness of update and conflict detection and reconciliation
+algorithms defined over it.
+This, in turn, can offer formal verification of the algorithms underlying
+specific implementations in a variety of synchronizers.
+Alternatively, by generalizing the parent--child relationships between filesystem nodes,
+the demonstrated properties of minimal sequences of commands
+and conditional operation of sequences ($\workssign$)
+may also contribute to future research into algebraic structures
+constrained by predefined sparse connections between their elements.

### 2016-01-07 p2/def-commands.tex
Style updates
Finished conclusion

--- 2015-12-25 2015/def-commands.tex
@@
 
-% TODO identity command?
+% TODO identity command instead of the empty sequence?
 
@@
 Indeed, Bill Zissimopoulos' work
-demonstrated (\cite{BZ})
+demonstrated \cite{BZ}
 that extending this distinction to more commands ultimately simplifies
@@
 $\FS[\valv/n]$ to denote a filesystem derived from $\FS$:
-\[ \FS[\valv/n](m) :=
+\[ \FS[\valv/n](m) =
    \begin{cases}

### 2016-01-07 p2/def-filesystem.tex
Style updates
Minor update
Finished conclusion

@@
 We do this because, as Bill Zissimopoulos pointed 
-out (\cite{BZ}),
+out \cite{BZ},
 we often do not want to consider metadata stored in
@@
 
-In this paper, $n$, $m$ and $o$ denote nodes in $\setn$.
+In this paper, $\FS$ and $\GS$ denote filesystems,
+and $n$, $m$ and $o$ are nodes in $\setn$.
 We use $\valf$ for an arbitrary element in $\setf$, 

### 2016-01-07 p2/intro.tex
Finished conclusion

@@
 The synchronization algorithm we describe
-follows the two main steps described by Balasubramaniam and Pierce (\cite{BP}):
+follows the two main steps described by Balasubramaniam and Pierce \cite{BP}:
 update detection, where we identify modifications that have been applied to the replicas
@@
 
-In this paper we build on previous work done 
-by Ramsey and Csirmaz
+In this paper we build on our previous work done 
+with Prof. Norman Ramsey
 on an algebraic approach to synchronization
-(\cite{NREC}),
+\cite{NREC},
 and add to the theoretical understanding
@@
 
-In terms of the usual classification of synchronizers (\cite{TSR, PV, SSH}),
+In terms of the usual classification of synchronizers \cite{TSR, PV, SSH},
 our approach to reconciliation is therefore operation-based as we investigate sets of commands,
@@
 as its starting point is the states of the replicas themselves.
-Moreover, our ordering algorithms only depend on the properties of commands 
+Moreover, our ordering algorithms only depend on properties of commands 
 such as commutativity or idempotence,
@@
 the origin and original temporal order of updates, 
-and which may give rise to otherwise resolvable conflicts (\cite{SSH}).
-Ordering plays a central role in other operation-based synchronizers.
-We refer to a survey by Saito and Shapiro of so-called optimistic replication algorithms (\cite{SSH});
-or, in particular,
+and which may give rise to otherwise resolvable conflicts \cite{SSH}.
+In general, ordering plays a central role in operation-based synchronizers.
+We refer to a survey by Saito and Shapiro of so-called optimistic replication algorithms \cite{SSH};
+and, in particular,
 to IceCube, where multiple orders are tested to find an acceptable one (\cite{KRSD}, see also \cite{MPV}),

### 2016-01-07 p2/ordering.tex
Renamed directories
Finished conclusion

--- 2016-01-04 ii/ordering.tex
@@
 
-\medskip
+\bigskip
 
+\noindent
 We can now define our algorithm to generate orders of sets of commands.
@@
 For all simple sequences $T$ and $S\nequiv\cbrk$,
-$T\equiv S \Leftrightarrow T\in\orderset{S}$.
+\[ T\equiv S \Longleftrightarrow T\in\orderset{S}. \]
 \end{mylem}

### 2016-01-07 p2/def-commands.tex
Minor improvements

@@
 (when it is $\empt$ or $\vald$).
-For example, $\cbdaa{n}{\vald}$ will represent $mkdir(n,\vald)$,
+For example, $\cbfaa{n}{\valf}$ will represent $create(n,\valf)$,
 and $\cdba{n}$ will represent $rmdir(n)$.
@@
 the \emph{replacement operator}  which changes the
-value of the filesystem at a given point only.
+value of the filesystem at a given node only.
 

### 2016-01-07 p2/def-filesystem.tex
Minor improvements

@@
 which determines the following $\parent$ function,
-and \emph{ancestor / descendant} and \emph{incomparable} relations.
-Tao et al. in \cite{TSR} describe a similar filesystem model, although
+and the \emph{ancestor / descendant} and \emph{incomparable} relations.
+Tao et al. \cite{TSR} describe a similar filesystem model, although
 they also model inodes and restrict the filesystem to a just single tree.

### 2016-01-07 p2/abstract.tex
Minor updates

@@
 We use algebraic methods to reason about filesystem operations, 
-and introduce a simplified definition of conflicting updates to filesystem trees.
+and introduce a simplified definition of conflicting updates to filesystems.
 We also define algorithms for update detection and reconciliation
@@
 and toward building more complete algebras
-of filesystems 
+of filesystem trees 
 and extending algebraic approaches to other data storage protocols.

### 2016-01-07 p2/algebra.tex
Minor updates

--- 2015-12-25 2015/algebra.tex
@@
 
-In this algebra, equivalence ($\equiv$) and extension ($\eqext$) would become relations
+In this algebra, equivalence ($\equiv$) and extension ($\eqext$) would become algebraic relations
 between sequences, and logical rules involving them

### 2016-01-07 p2/axioms.tex
Finished conclusion
Minor updates

@@
 
-So that we could describe the effects of commands in general,
+So that we can describe the effects of commands in general,
 let us introduce some notation
@@
 
-The following concepts 
+The following two relations 
 (which echo the ones defined in \cite{NREC})
@@
 % inference rules:
-$ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$
+$ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
 and
@@
 which pairs of commands cause errors all the time,
-which can be simplified to one or no commands, and which can be reversed
+which can be simplified to one or no commands, and which commute and can be reversed
 without any change in their overall effect.
@@
 Commands on the same node simplify:
-$\cxynv\cc\czwnv \eqext \emptyseq$ where $Y=Z$ and $X=W=\ccharb$ 
+$\cxynv\cc\czwnv \eqext \emptyseq$ where $Y=Z$, and $X=W=\ccharb$ 
 or $X=W=\cchard$.
@@
 
-% TODO We will only use these except for...
-
 \bigskip

### 2016-01-07 p2/conclusion.tex
Minor updates

@@
 consider reconciling not only two, but more replicas in a single step and
-prove the correctness and maximality of the algorithm proposed.
+prove the correctness and maximality of the algorithm proposed,
+or show that it is impossible to do so.
 
@@
 Identifying which results depend on the assumption that $|\setd|=1$
-and devising updated proofs and algorithms,
+and devising updated proofs and algorithms for when $|\setd|>1$,
 or specifying a pre-processing step that reconciles meta-information in directories

### 2016-01-07 p2/def-commands.tex
Minor updates

@@
 
-To define the exact effect of the commands we use
-the \emph{replacement operator}  which changes the
-value of the filesystem at a given node only.
-
 \begin{mydef}[Effect of commands]
 We use a \emph{replacement operator} of the form
-$\FS[\valv/n]$ to denote a filesystem derived from $\FS$:
+$\FS[\valv/n]$ to denote a filesystem derived from $\FS$ 
+by replacing its value at $n$ with $\valv$:
 \[ \FS[\valv/n](m) =

### 2016-01-07 p2/intro.tex
Minor updates

@@
 update detection, where we identify modifications that have been applied to the replicas
-since they diverged and represent these as sequences of commands,
+since they diverged and represent them as sequences of commands;
 and reconciliation, where we identify commands that can be propagated to other replicas and do so.
@@
 but we need to order these in a way that they could be applied
-to the filesystems without causing an error 
+to the filesystem without causing an error 
 (for example, a directory needs to be created before a file can be created under it).
@@
 then under certain circumstances they are not compatible and will give rise to conflicts.
-Accordingly, in this paper command-pairs and their properties
-play a special role
-as we aim to find valid orderings on filesystem trees.
+Accordingly, in this paper the commutativity of command pairs and their other properties
+play a special role.
 
@@
 This is in opposition to syntactic scheduling, which uses 
-the origin and original temporal order of updates, 
+the origin and the original temporal order of updates, 
 and which may give rise to otherwise resolvable conflicts \cite{SSH}.
 In general, ordering plays a central role in operation-based synchronizers.
-We refer to a survey by Saito and Shapiro of so-called optimistic replication algorithms \cite{SSH};
-and, in particular,
+We refer to an excellent survey by Saito and Shapiro of so-called optimistic replication algorithms \cite{SSH};
+and, as examples,
 to IceCube, where multiple orders are tested to find an acceptable one (\cite{KRSD}, see also \cite{MPV}),

### 2016-01-07 p2/ordering.tex
Minor updates

@@
 we prove this proposition for sequences, not sets, as if all sequences must contain a command on $\parent(n)$,
-then so must sets because otherwise there would be no order in which they can be
+then so must a set because otherwise there would be no order in which it can be
 applied to any filesystem.
@@
 To order the commands in the component,
-select the command with the topmost node, so that there would be no command
+select the command with the topmost node, so that there is no command
 on its parent node (if there is one). 
@@
 as a set and determine its $\orderset{S}$.
-An important property of simple sequences is that
+\Cref{simple_reorder_equiv} is
+an important property of simple sequences: namely, that
 all of their valid orderings are equivalent,
@@
 \begin{proof}
-We use an inverse proof. Let $A$ and $B$ simple sequences
+We use an inverse proof. Let $A$ and $B$ be simple sequences
 such that $A\equiv B\nequiv\cbrk$,
@@
 
-We also assume that they do not contain the same sequences.
+We also assume that they do not contain the same commands.
 Without loss of generality, we can assume
@@
 the command on the topmost node, $\cxynv$, was not before all other commands
-in the component as described by the algorithm,
+in the component as prescribed by the algorithm,
 then any resulting sequence would necessarily contain
@@
 We can prove that an order not generated by the algorithm
-in case of components made of destruction pairs breaks all filesystems
+in the case of a component made of destruction pairs breaks all filesystems
 in a similar way.

### 2016-01-07 p2/works-inverse.tex
Minor updates

--- 2016-01-04 ii/works-inverse.tex
@@
 &\Rightarrow\\
-&A_1\FS\neq\fsbroken \wedge \cdots \wedge A_l\FS\neq\fsbroken
+&A_1\FS\neq\fsbroken \wedge \cdots \wedge A_l\FS\neq\fsbroken.
 \end{align*}
@@
 If $A$ and $B$ are minimal sequences, $\works{A,B}$,
-and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$)
+and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$),
 then the input types of these commands must match ($X=Z$).

### 2016-01-07 p2/conclusion.tex
Clarification

@@
 prove the correctness and maximality of the algorithm proposed,
-or show that it is impossible to do so.
+or show that it is impossible to satisfy these criteria.
 

### 2016-01-10 p2/prove.py
Updated URL, improved documentation

@@ -3,7 +3,7 @@ import sys
 
 """
 This script is part of the paper available at
-https://github.com/csirmaz/AlgebraicSyncPaper/p2/
+https://github.com/csirmaz/AlgebraicSyncPaper/tree/master/p2
 
 It is used to test pairs of commands on filesystems and determine
 (1) if they break all filesystems, 
@@ -11,16 +11,16 @@ It is used to test pairs of commands on filesystems and determine
 (3) or they are equivalent to (or extended by) a single command
 (4) or they are equivalent to (or extended by) the same commands applied in reverse order.
 
-The commands are tested on minimal model of a filesystem that includes information
+The commands are tested on a minimal model of a filesystem that includes information
 about two nodes, their immediate surroundings that determine the tree-property
 the filesystem needs to satisfy, and the relationship between the nodes.
 
-The script considers the following possible relationships between the nodes
+The script considers the following possible relationships between the nodes (paths)
 to which the commands are applied:
 """
 
 # Constants for Filesystem.rel and CommandPair.rel:
-DISTANT_PARENT     = 'DistantParent'     # p2 is an ancestor of p1 but not its parent
+DISTANT_PARENT     = 'DistantParent'     # path p2 is an ancestor of path p1 but not its parent
 DIRECT_PARENT      = 'DirectParent'      # p2 is the parent of p1 and p1 is not the only child
 DIRECT_PARENT_ONLY = 'DirectParentOnly'  # p2 is the parent of p1 and p1 is the only child
 DISTANT_CHILD      = 'DistantChild'      # p2 is the descendant of p1 but not its child
@@ -239,7 +239,7 @@ class Node:
         """Mark the node as broken.
 
         Args:
-            broken (Optional[str]):
+            reason (Optional[str]):
 
         Returns:
             self

### 2016-10-03 p2/axioms.tex
Improvements; deriving equivalence congruence from the extension preorder

@@
 \begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
-We use ``$\cc$'' to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence:
-$S=\cbdaa{n}{\vald}\cc\cbfaa{m}{\valf}$, or $S'=S\cc\cbba{o}$,
+We use ``$\cc$'' to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence,
 with the meaning that the command on the left is applied first:
 \[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
-Sequences of commands form a free semigroup, and, as usual,
+For example, we will write
+$S=\cbdaa{n}{\vald}\cc\cbfaa{m}{\valf}$, or $S'=S\cc\cbba{o}$.
+% monoid, but not free monoid
+% monoid: semigroup with identity element
+% Sequences of commands form a free semigroup
+Sequences of commands form a monoid, and, as usual,
 $\emptyseq$ denotes its unit element, the empty sequence,
@@
 
-\begin{mydef}[$\equiv$]
-% Relation in the algebra
-$A\equiv B$ means that $A$ and $B$ are equivalent,
-% intended interpretation:
-that is, they behave in the same way on
-all filesystems: $\forall \FS: A\aFS=B\aFS$.
-It is a reflexive, commutative and transitive relation,
-and clearly
-% inference rule:
-$ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.
-\end{mydef}
-
 \begin{mydef}[$\eqext$]
@@
 $\forall \FS: A\FS\neq\fsbroken\Rightarrow A\aFS=B\aFS$.
-It is a reflexive and transitive relation,
-and we can see that
+% preorder: reflexive and transitive
+It is a preorder,
+and as clearly
 % inference rules:
 $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
-and
-$ A\equiv B \Rightarrow A\eqext B$.
+it is a precongruence.
+% precongruence: congruence of a preorder -- TODO -- ?
 \end{mydef}
+
+\begin{mydef}[$\equiv$]
+% Relation in the algebra
+$A\equiv B$,
+or $A$ and $B$ are \emph{equivalent,}
+iff $A\eqext B$ and $B\eqext A$;
+that is, $\equiv$ is the intersection of the preorder $\equext$ with its inverse.
+% symmetric: aRb <=> bRa
+% reflexive: aRa
+% transitive: aRb & bRC => aRc
+It is therefore a congruence, and we can see that
+% inference rule:
+$ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.
+\end{mydef}
+
+It is easy to see that equivalence holds on the level of filesystems:
+
+\begin{mylem}
+$A\equiv B$
+iff $A$ and $B$ behave in the same way on
+all filesystems, that is, $\forall \FS: A\aFS=B\aFS$.
+\end{mylem}
+\begin{proof}
+If $\forall \FS: A\aFS=B\aFS$ then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
+For the reverse statement we assume that $A\equext B$ and $B\equext A$.
+$B\equext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
+Therefore, for every $\FS$ either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
+in which case $B\aFS=\fsbroken$ must be true, and therefore $A\aFS=B\aFS$ still holds.
+\end{proof}
 

### 2016-10-03 p2/def-commands.tex
Improvements; deriving equivalence congruence from the extension preorder

@@
 Next we define commands on filesystems.
-As described above, we aimed to select a set of commands
+As described above, we aim to select a set of commands
 that captures as much information
@@
 A minimal set of commands, based on the most frequent tools implemented by filesystems,
-may be $create(n,\valv)$, which creates a file or directory ($\valv$) at the empty node $n$;
-$edit(n,\valv)$, which replaces the earlier value at $n$ with $\valv$;
-and $remove(n)$, which deletes the value at $n$---where 
-$n\in\setn$ and $\valv\in\setv$ (but $\valv\neq\empt$).
+may be the following, where 
+$n\in\setn$ and $\valv\in\setv$ (but $\valv\neq\empt$):
+\begin{itemize}
+\item $create(n,\valv)$, which creates a file or directory ($\valv$) at $n$
+where the file system contains no file or directory ($\empt$);
+\item $edit(n,\valv)$, which replaces the earlier file or directory at $n$ with $\valv$;
+\item $remove(n)$, which removes the file or directory at $n$, and replaces it with $\empt$.
+\end{itemize}
 Regarding their output, that is, the state of the filesystem at $n$
@@
 by prefixing the command or sequence to it, for example: $\cbrk\aFS$, $\cbdaa{n}{\vald}\aFS$, 
-or simply $S\aFS$ if $S$ is a sequence of commands.
+or $S\aFS$ if $S$ is a sequence of commands.
 
 \begin{mydef}[Effect of commands]
-We use a \emph{replacement operator} of the form
+We use a replacement operator of the form
 $\FS[\valv/n]$ to denote a filesystem derived from $\FS$ 

### 2016-10-03 p2/def-filesystem.tex
Minor updates
Improvements; deriving equivalence congruence from the extension preorder

--- 2016-01-07 p2/def-filesystem.tex
@@
 
-The nodes form a disjoint union of rooted directed trees,
-which determines the following $\parent$ function,
-and \emph{ancestor / descendant} and \emph{incomparable} relations.
-Tao et al. in \cite{TSR} describe a similar filesystem model, although
-they also model inodes and restrict the filesystem to a just single tree.
+There is an ancestor / descendant relation defined over the nodes,
+which arranges them in a (disjoint) union of rooted directed trees,
+and which can be derived from the following $\parent$ function.
+Tao et al. \cite{TSR} describe a similar filesystem model, although
+they also model inodes and restrict the filesystem to just a single tree.
 \begin{mydef}[$\parent$]
@@
 On $\setn$ the \emph{ancestor / descendant} relation is the
-partial ordering determined by the $\parent$ function.
+strict partial ordering determined by the $\parent$ function.
 We write $n\descendant m$ if $n$ is the ancestor of $m$,
-that is, $n=\parent^n(m)$ for some integer $n\ge 1$.
+that is, $n=\parent^a(m)$ for some integer $a\ge 1$.
 % or the path name of $n$ is an initial segment of that of $m$. 
@@
 \input{fig-type-transition}
-\caption{Transitions between types of values in a filesystem}\label{fig_transition}
+\caption{Transitions between types of values from the root of a tree in a filesystem}\label{fig_transition}
 \end{figure}

### 2016-10-04 p2/axioms.tex
Improvements: clarified language, added explanation

@@
 $\forall \FS: A\FS\neq\fsbroken\Rightarrow A\aFS=B\aFS$.
+% old inference rule: $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
+We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\eqext T$.
 % preorder: reflexive and transitive
-It is a preorder,
-and as clearly
-% inference rules:
-$ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
-it is a precongruence.
-% precongruence: congruence of a preorder -- TODO -- ?
+In other words, $\eqext$ is a preorder, and also a precongruence.
 \end{mydef}
@@
 iff $A\eqext B$ and $B\eqext A$;
-that is, $\equiv$ is the intersection of the preorder $\equext$ with its inverse.
+that is, $\equiv$ is the intersection of the preorder $\equext$ with its inverse,
+and so it is a congruence.
 % symmetric: aRb <=> bRa
@@
 % transitive: aRb & bRC => aRc
-It is therefore a congruence, and we can see that
-% inference rule:
-$ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.
+% old inference rule: $ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.
 \end{mydef}
@@
 
-We methodically investigated of all possibilities using a computer 
+We methodically investigate all possibilities using a computer 
 program\footnote{The program is accessible on-line at \\
@@
 which pairs of commands cause errors all the time,
-which can be simplified to one or no commands, and which commute and can be reversed
-without any change in their overall effect.
+which can be simplified to one command or $\emptyseq$,
+and which commute and can be reversed without any change in their overall effect.
 Our basis for this investigation was the model of filesystems introduced in this paper.
@@
 Commands on the same node simplify:
-$\cxynv\cc\czwnv \eqext \emptyseq$ where $Y=Z$, and $X=W=\ccharb$ 
-or $X=W=\cchard$.
+$\cxynv\cc\czwnv \eqext \emptyseq$ where $Y=Z$, and $\cxw=\cbb$ 
+or $\cxw=\cdd$.
 \end{myax}
@@
 and $\czwnv\cc\cxynnv \equiv\cbrk$
-where $\nn\descendant n$ and $\nn\neq\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
+where $\nn\descendant n$ and $\nn\neq\parent(n)$, and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
+(More intuitively, if $\czw\neq\cbb$ then either before or after $\czwnv$, the filesystem at
+$n$ is not empty, and therefore there must be a directory at all ancestors of $n$, including at a child of $\nn$.
+Consequently $\cxynnv$ will break the filesystem as either before or after it the filesystem at $\nn$
+does not have a directory.)
 \end{myax}
@@
 are independent, and we write $\cxynv\indep\czwmv$ if 
-they have the same effect in either order and do not break all filesystems:
+they commute and do not break all filesystems:
 \[ \cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk. \]

### 2016-10-04 p2/def-commands.tex
Improvements: clarified language, added explanation

@@
 We use a replacement operator of the form
-$\FS[\valv/n]$ to denote a filesystem derived from $\FS$ 
+$\FS[\valv/n]$ to denote a filesystem derived from a non-broken $\FS$ 
 by replacing its value at $n$ with $\valv$:

### 2016-10-04 p2/ordering.tex
Improvements: clarified language, added explanation

@@
 we prove this proposition for sequences, not sets, as if all sequences must contain a command on $\parent(n)$,
-then so must a set because otherwise there would be no order in which it can be
+then so must all sets because otherwise there would be no order in which the commands they contain could be
 applied to any filesystem.
@@
 and another command $\czwnnv$ on $\nn$.
-We use an indirect proof and assume that there are no commands on $\parent(n)$ in $A$.
+We use a proof by contradiction and assume that there are no commands on $\parent(n)$ in $A$.
 Next, we create a new sequence $A'\equiv A$ in which $\cxynv$ and $\czwnnv$ are next to each other.
@@
 that we know can be applied to at least one filesystem in some order without breaking it.
-Then we can split $U$ into a maximum number of disjunct subsets
+Then we can split $U$ into a maximum number of disjoint subsets
 (components) so that the nodes of two commands from two different subsets are incomparable.
@@
 \begin{proof}
-We use an inverse proof. Let $A$ and $B$ be simple sequences
+We use a proof by contradiction. Let $A$ and $B$ be simple sequences
 such that $A\equiv B\nequiv\cbrk$,

### 2016-10-05 p2/axioms.tex
Fixed typos

@@
 iff $A\eqext B$ and $B\eqext A$;
-that is, $\equiv$ is the intersection of the preorder $\equext$ with its inverse,
+that is, $\equiv$ is the intersection of the preorder $\eqext$ with its inverse,
 and so it is a congruence.
@@
 If $\forall \FS: A\aFS=B\aFS$ then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
-For the reverse statement we assume that $A\equext B$ and $B\equext A$.
-$B\equext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
+For the reverse statement we assume that $A\eqext B$ and $B\eqext A$.
+$B\eqext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
 Therefore, for every $\FS$ either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,

### 2016-10-05 p2/works-inverse.tex
Aligned proofs
Introducing valueless constructs

@@
 \begin{mydef}[Sets of sequences]
-For brevity, we will use calligraphic letters (e.g. $\seqset{A, B, C}$ and $\seqset{S}$)
-to denote sets of sequences,
-and use $A\cc\seqset{B}$ to denote the set of sequences $\{A\cc B|B\in\seqset{B}\}$.
+As we will frequently refer to sets of fequences,
+we will use calligraphic letters (e.g. $\seqset{A, B, C}$ and $\seqset{S}$)
+to denote such sets for brevity.
+We will use $A\cc\seqset{B}$ to denote the set of sequences $\{A\cc B|B\in\seqset{B}\}$.
 \end{mydef}
@@
 
-\begin{mycor}
-% An inference rule in the algebra
-$B\eqext A \Rightarrow \worksc{A}{B}$.
-\end{mycor}
+% \begin{mycor}
+% % An inference rule in the algebra
+% $B\eqext A \Rightarrow \worksc{A}{B}$.
+% \end{mycor}
 
@@
 The combination of independent commands works wherever the original commands work:
-\begin{align*}
-\forall\FS:{}&\cxynv\indep \czwmv \\
-&\quad\wedge \cxynv\aFS\neq\fsbroken \\
-&\quad\wedge \czwmv\aFS\neq\fsbroken \\
-&\Rightarrow \cxynv\cc \czwmv\aFS\neq\fsbroken.
-\end{align*}
+\[ \cxynv\indep \czwmv \Rightarrow \worksc{\cxynv\cc \czwmv}{\cxynv, \czwmv}. \]
+% \begin{align*}
+% \forall\FS:{}&\cxynv\indep \czwmv \\
+% &\quad\wedge \cxynv\aFS\neq\fsbroken \\
+% &\quad\wedge \czwmv\aFS\neq\fsbroken \\
+% &\Rightarrow \cxynv\cc \czwmv\aFS\neq\fsbroken.
+% \end{align*}
 \end{myax}
@@
 We proceed in an indirect way and
-assume that $\cxynv\cc \czwmv\aFS=\fsbroken$.
+assume that there is a filesystem $\FS$ for which
+$\cxynv\aFS\neq\fsbroken$ and $\czwmv\aFS\neq\fsbroken$, but
+$\cxynv\cc \czwmv\aFS=\fsbroken$.
 We know $\cxynv\aFS\neq\fsbroken$ so it must be applying 
@@
 \noindent
+We know that whether commands break a filesystem depends solely on their input and output
+types and the node, but not their actual output value.
+To represent this, we introduce an equivalence relation between filesystems, commands
+and sequences of commands.
+\begin{mydef}[Equivalence by type: $\typeeq$]
+$ $ % otherwise first list element starts on same line
+\begin{itemize}
+\item For two filesystems we write $\FS\typeeq\GS$ iff they share the same nodes,
+and at all nodes the types of their values are the same, or they are both broken.
+\item For two commands we write $\alpha\typeeq\beta$ iff their input and output values,
+and the node they operate on are the same.
+\item For two sequences of commands we write $A\typeeq B$ iff they contain the same number of commands,
+and pairwise the commands $\alpha\in A$ and $\beta\in B$ at the same indices are equivalent by type ($\alpha\typeeq\beta$).
+\end{itemize}
+\end{mydef}
+
+This relation gives rise to equivalence classes of filesystems, commands, and sequences of commands,
+each of which is associated with a new type of filesystem, command or sequence of commands in which
+only types are noted, but not values.
+(This is also equivalent to assuming $|\setf|=1$.)
+We will call these constructs valueless.
+
+\begin{mydef}[Valueless constructs]
+$ $
+\begin{itemize}
+\item For any filesystem $\FS$, we write $\FS\T$ to denote the valueless filesystem assiociated with
+the equivalenve class of $\FS$ by $\typeeq$; that is, where at each node $n$, $\FS\T$ contains the type of
+$\FS(n)$. In general, a valueless filesystem is one where each node
+is associated with a type, but not a value:
+\begin{gather*}
+\FS\T =
+\begin{cases}
+\setn \rightarrow \typeset \\
+\fsbroken
+\end{cases}
+\end{gather*}
+
+\item Similarly, for any command $\cxynv$ we write $\cxynv\T$ to denote the valueless command
+$\cTxyn$, represented by a triple of the input type, output type and node.
+The command $\cbrk$ has a separate valueless version, $\cbrk\T$.
+
+\item Also, for any sequence of commands $S$ we write $S\T$ to denote the sequence of
+valueless commands associated with the commands in $S$ in the same order; and for a set of sequences $\seqset{S}$
+we write $\seqset{S}\T$ for $\{S\T|S\in\seqset{S}\}$.
+
+\end{itemize}
+\end{mydef}
+
+A valueless command can be applied to a valueless filesystem with the expected outcome
+that $\cTxyn$ will replace the type at $n$ with $Y$ 
+if the original type was $X$ and the tree property still holds after the replacement.
+This means that
+the mapping $\T$ can be extended further to the 
+the relations $\equiv$, $\eqext$ and $\workssign$, where
+${\equiv}\T$, ${\eqext}\T$ and $\workssign\T$ hold or do not hold for sequences of valueless commands
+depending on their behavior on valueless filesystems.
+
+It is easy to see that 
+$A\equiv B \Rightarrow A\T{\equiv}\T B\T$ 
+and
+$A\eqext B \Rightarrow A\T{\eqext}\T B\T$,
+but the reverse is not true as 
+$A\T$ and $B\T$ will have the same effect on all $\FS\T$
+if $A$ and $B$ differ only in some of the values in their commands,
+whereas clearly $A\nequiv B$.
+
+With $\workssign$, however, the situation is different, as it only
+depends on whether sequences break filesystems or not. Therefore the followings hold:
+\begin{mycor}
+\begin{gather*}
+\works{\seqset{A}} \Leftrightarrow \worksT{\seqset{A}\T} \\
+\worksc{\seqset{A}}{\seqset{B}} \Leftrightarrow \workscT{\seqset{A}\T}{\seqset{B}\T}
+\end{gather*}
+\end{mycor}
+
+% ==================================================
+
 We continue by defining inverse commands and sequences
@@
 in reverse order.
-\end{mydef}
-
-\begin{mydef}[$\typeeq$]
-For two filesystems we write $\FS\typeeq\GS$
-iff 
-at all nodes the types of their values are the same, or they are both broken.
 \end{mydef}

### 2016-10-07 p2/ordering.tex
New definitions based on equivalence classes

@@
 
+\begin{mydef}[$\ordersetsign$]
+We use $\orderset{U}$ to denote the set of sequences 
+generated by the algorithm / (all possible orderings)
+from the commands in the simple-? set or sequence $U$.
+\end{mydef}
+
 Let $U$ be a simple set of commands
@@
 
-\begin{mydef}[$\ordersetsign$]
-We use $\orderset{U}$ to denote the set of sequences that contain all commands in
-the simple set $U$
-and represent all orders generated by this algorithm.
-\end{mydef}
+\bigskip
 
-It follows from the algorithm that:
-\begin{mycor}\label{lemma:neighbor}
-If $U$ contains commands on both $n$ and $\parent(n)$, then
-there is a $U'\in\orderset{U}$ where they are next to each other.
-\end{mycor}
-
-As a specific case, we can regard a simple sequence of commands $S$
-as a set and determine its $\orderset{S}$.
+\noindent As a specific case, we can regard a simple sequence $S$
+as a set, and use the above algorithm to generate all possible orderings
+of the commands it contains.
 \Cref{simple_reorder_equiv} is
 an important property of simple sequences: namely, that
-all of their valid orderings are equivalent,
+all of their valid reorderings are equivalent,
 and all equivalent sequences are mere reorderings.
@@
 \begin{mylem}\label{simple_reorder_equiv}
-For all simple sequences $T$ and $S\nequiv\cbrk$,
-\[ T\equiv S \Longleftrightarrow T\in\orderset{S}. \]
+For a simple sequence $S\nequiv\cbrk$,
+\[ \orderset{S} = [S]_\equiv, \]
+where $[S]_\equiv$ denotes the set of simple sequences equivalent to $S$.
 \end{mylem}
@@
 
+%% TODO https://en.wikipedia.org/wiki/Equivalence_class
+
+It follows from the algorithm that:
+\begin{mycor}\label{lemma:neighbor}
+If $U$ contains commands on both $n$ and $\parent(n)$, then
+there is a simple $U'\equiv U$ in which they are next to each other.
+\end{mycor}
+
 It follows from this that given a simple set,

### 2016-10-07 p2/works-inverse.tex
New definitions based on equivalence classes

--- 2016-01-07 p2/works-inverse.tex
@@
 
+%% TODO https://en.wikipedia.org/wiki/Equivalence_class
+
 \noindent
-We continue by defining inverse commands and sequences
-which allow us to move parts of sequences between the
+We know that whether commands break a filesystem depends solely on their input and output
+types and the node, but not their actual output value.
+To represent this, we introduce an equivalence relation between filesystems, commands
+and sequences of commands.
+\begin{mydef}[Equivalence by type: $\typeeq$]
+$ $ % otherwise first list element starts on same line
+\begin{itemize}
+\item For two filesystems we write $\FS\typeeq\GS$ iff they are both broken, or they share the same nodes,
+and at all nodes the types of their values are the same.
+\item For two commands we write $\alpha\typeeq\beta$ iff their input and output types,
+and the node they operate on are the same.
+For example, $\cbfaa{n}{f_1}\typeeq\cbfaa{n}{f_2}$.
+\item For two sequences of commands we write $A\typeeq B$ iff they contain the same number of commands,
+and pairwise the commands $\alpha\in A$ and $\beta\in B$ at the same indices are equivalent by type ($\alpha\typeeq\beta$).
+\end{itemize}
+\end{mydef}
+
+In other words, two type-equivalent objects can only differ in the value they contain,
+but as $|\setb|=|\setd|=1$, this is only possible at values of the type $\ccharf$.
+We select an arbitrary file value $\fil\in\setf$, and choose a representative
+of each $\typeeq$-equivalence class where all (if any) values of the type $\ccharf$ is $\fil$.
+For example, in the case of commands, the representative of $[\cbfaa{n}{f}]_\typeeq$ is $\cbfaa{n}{\fil}$.
+
+\begin{mydef}[$\T$]
+We use $\T$ and write $x\T$ to denote the canonical mapping of 
+filesystems, commands and sequences to the
+representatives of their $\typeeq$-equivalence class.
+$\T$ is also extended to sets of sequences,
+where $\seqset{A}\T = \{S\T | S\in\seqset{A}\}$.
+\end{mydef}
+
+For example, $\cbfaa{n}{f}\T = \cbfaa{n}{\fil}$,
+and for the sequence $S=\alpha\cc\beta$, $S\T=\alpha\T\cc\beta\T$.
+In other words, $\T$ maps our system of filesystems and commands
+into a system where $|\setf|$ is also $1$.
+
+\begin{mycor}
+For any filesystem $\FS$ and command $\alpha$, 
+$\alpha\T(\FS\T) = (\alpha\aFS)\T$.
+\end{mycor}
+
+% It is easy to see that 
+% $A\equiv B \Rightarrow A\T\equiv B\T$ 
+% and
+% $A\eqext B \Rightarrow A\T\eqext B\T$,
+% but the reverse is not true as 
+% $A\T$ and $B\T$ will have the same effect on all filesystems
+% if $A$ and $B$ differ only in some of the values in their commands,
+% whereas clearly $A\nequiv B$.
+
+As whether a sequence of commands breaks a filesystem does not depend on the output values
+of the commands, only the input and output types, we know that
+\begin{mycor}
+\begin{gather*}
+\works{\seqset{A}} \Leftrightarrow \works{\seqset{A}\T} \\
+\worksc{\seqset{A}}{\seqset{B}} \Leftrightarrow \worksc{\seqset{A}\T}{\seqset{B}\T}.
+\end{gather*}
+\end{mycor}
+
+We are now ready to define the inverse of representative commands $\alpha\T$
+which allows us to move parts of sequences between the
 condition and consequence parts of $\workssign$.
+This is based on the following observation.
+
+\begin{mylem}
+Representative functions $\alpha\T$ are injections over representative filesystems ($\FS\T$)
+except for the cases where they break a filesystem, that is,
+\[ \forall\FS,\GS,\alpha: \FS\T\neq\GS\T \wedge \alpha\T(\FS\T)\neq\fsbroken \Longrightarrow \alpha\T(\FS\T) \neq \alpha\T(\GS\T). \]
+\end{mylem}
+\begin{proof}
+This is trivial if $\GS\T=\fsbroken$, so we assume it is not so.
+If $\FS\T$ and $\GS\T$ have different values at any node apart from $n$, then this difference remains
+even after applying the command to $\FS\T$. The only remaining case therefore is where they have the same values
+at all nodes except $n$.
+We know that a representative filesystem can only have values from the set $\rvalueset$.
+As $\alpha\T(\FS\T)\neq\fsbroken$, $\FS\T(n)$ must be the value that matches the input type of $\alpha\T$.
+We know that $\GS\T(n)\neq\FS\T(n)$, and therefore $\GS\T(n)$ must have a different type,
+which implies $\alpha\T(\GS\T)=\fsbroken$ as it cannot match the input type of $\alpha\T$,
+and again we have $\alpha\T(\FS\T) \neq \alpha\T(\GS\T)$.
+\end{proof}
 
 \begin{mydef}[Inverse commands and sequences]
-The inverse of command $\cxynv$ is $\cxynv^{-1} = \caaaa{Y}{X}{n}{\valvx}$
-where $\valvx$ is an arbitrary value from $\setvx{X}$.
-We write $S^{-1}$ for the inverse of sequence $S$, which consists of the inverses of the commands in $S$
+If we regard the representative command $\alpha\T$ a function whose
+domain is the subset of representative filesystems $\{\FS\T | \alpha\aFS\neq\fsbroken\}$,
+then we can define the inverse of $\alpha\T$
+for which we write $\alpha\T^{-1}$.
+We write ${S\T}^{-1}$ for the inverse of the sequence $S\T$, which consists of the inverses of the commands in $S\T$
 in reverse order.
@@
 
-\begin{mydef}[$\typeeq$]
-For two filesystems we write $\FS\typeeq\GS$
-iff 
-at all nodes the types of their values are the same, or they are both broken.
-\end{mydef}
-
 From the definitions we can clearly see that
-\begin{mycor}\label{negneg_is_typeeq}
+\begin{mycor}\label{negneg_is_typeeq} %% TODO Don't use!
 $\forall S, \FS: (S^{-1})^{-1}\aFS\typeeq S\aFS$.
@@
 \begin{proof}
+
+%% TODO see lemma above
+
 This is based on the fact that in our model, unless they break a filesystem,

### 2016-10-08 p2/axioms.tex
New notation for commands

@@
 For example, we will write
-$S=\cbdaa{n}{\vald}\cc\cbfaa{m}{\valf}$, or $S'=S\cc\cbba{o}$.
+$S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
 % monoid, but not free monoid
@@
 % Relation in the algebra
-$A\eqext B$ means that $B$ extends $A$,
+$A\eqext B$ means that $B$ \emph{extends} $A$,
 % intended interpretation:
@@
 \[ \cxynv\cc  \czwmv \]
-where $X,Y,Z,W\in\typeset$, $n,m\in\setn$, 
-and values are of the appropriate type: 
-$\valvy\in\setvx{Y}$ and $\valvw\in\setvx{W}$.
+where $x,y,z,w\in\setv$ and $n,m\in\setn$.
 
@@
 Commands on the same node break every filesystem if their types are incompatible:
-$\cxynv\cc\czwnv \equiv \cbrk$ where $Y\ne Z$.
+$\cxynv\cc\czwnv \equiv \cbrk$ where $[y]\ne [z]$.
 \end{myax}
@@
 Commands on the same node simplify:
-$\cxynv\cc\czwnv \eqext \emptyseq$ where $Y=Z$, and $\cxw=\cbb$ 
+$\cxynv\cc\czwnv \eqext \emptyseq$ where $[y]=[z]$, and $\cxw=\cbb$ 
 or $\cxw=\cdd$.
@@
 Commands on the same node simplify:
-$\cxynv\cc \czwnv \equiv \cxwnv$ where $Y=Z$ and $\cxw\neq\cbb$ and $\cxw\neq\cdd$.
+$\cxynv\cc \czwnv \equiv \cxwnv$ where $[y]=[z]$ and $\cxw\neq\cbb$ and $\cxw\neq\cdd$.
 \end{myax}
@@
    \begin{gather*}
-            \cbdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
-            \cbdaa{\nn}{\vald}\cc  \cbdaa{n}{\vald} \\
-            \cfdaa{\nn}{\vald}\cc  \cbfaa{n}{\valf} \\
-            \cfdaa{\nn}{\vald}\cc  \cbdaa{n}{\vald}
+            \cbdaa{\nn}\cc  \cbfaa{n} \\
+            \cbdaa{\nn}\cc  \cbdaa{n} \\
+            \cfdaa{\nn}\cc  \cbfaa{n} \\
+            \cfdaa{\nn}\cc  \cbdaa{n}
    \end{gather*}
@@
             \cfba{n}\cc  \cdba{\nn} \\
-            \cfba{n}\cc  \cdfaa{\nn}{\valf} \\
+            \cfba{n}\cc  \cdfaa{\nn} \\
             \cdba{n}\cc  \cdba{\nn} \\
-            \cdba{n}\cc  \cdfaa{\nn}{\valf}
+            \cdba{n}\cc  \cdfaa{\nn}
    \end{gather*}
@@
 and there must also be only one possible value for their output.
-Accordingly, $\cbba{n}$ and $\cdda{n}$ are the only two assertion commands.
+Accordingly, $\cbba{n}$ and $\cdda{n}$ are the only two types of assertion commands.
 \end{mydef}
@@
 Assertion commands can be removed:
-$\cxynv \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
+$\cdda{n}\eqext\emptyseq$ and $\cbba{n}\eqext\emptyseq$.
+% $\cxynv \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
 \end{myax}
@@
 
-If $n=m$, then from \cref{ax_same_breaks} we know $Y=Z$ and $W=X$
+If $n=m$, then from \cref{ax_same_breaks} we know $[y]=[z]$ and $[w]=[x]$
 as otherwise the commands, in one order or the other, would break all filesystems
@@
 The commands are not assertion commands, and so from \cref{ax_same_singlec}
-we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $Y=W$ and $\valvy=\valvw$.
-Therefore $X=Y=Z=W$ which is only possible if both commands are $\cff$ and have the same
+we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $y=w$.
+Therefore $[x]=[y]=[z]=[w]$ which is only possible if both commands are $\cff$ and have the same
 output value. This, however, contradicts our assumption that they are different.

### 2016-10-08 p2/def-commands.tex
New notation for commands

--- 2016-10-03 p2/def-commands.tex
@@
 more precisely.
-In other words, encoding the type of the output ($\cchard$, $\ccharf$ or $\ccharb$) in the commands is definitely useful.
-At the same time, there is never any need to consider the
-exact output \emph{value} of a command,
-as the success or failure of filesystem commands only depends on the types of values in the filesystem.
+In other words, encoding the outputvalue in the commands is definitely useful.
+As the success or failure of filesystem commands only depends on the types of values in the filesystem,
+we expect to use the type of their output when modelling their behavior.
 
@@
 we propose a set of commands that encode
-the type of the original state of $\FS(n)$ as well.
+the type of the original value $\FS(n)$ as well.
 (Some real-life filesystem commands like $rmdir$ do this already.)
+Again, as the success of failure of commands depends on types of values,
+it is not necessary to encode the actual input value.
+For example, the behavior of two commands that differ only in what the original file contains
+that they overwrite is never going to be different.
 
 \begin{mydef}[Regular commands]
-Therefore we have four pieces of information related to each command,
-and represent them using quadruples that list
-their input type ($X$), output type ($Y$),
-the node to which they are applied ($n$),
-and the value they store at the node ($\valvy$):
-\[ \cxynv, \]
-where $\valvy\in\setvx{Y}$.
+Therefore we have three pieces of information related to each command,
+and represent them using triples that contain
+their input type ($[v_{in}]$), output value ($v_{out}$),
+and the node to which they are applied ($n$):
+\[ \caaaa{v_{in}}{v_{out}}{n}. \]
+\end{mydef}
 
-We use $\cchard$, $\ccharf$ or $\ccharb$ to represent the different
-types, and omit the final value if it is determined by the output type
-(when it is $\empt$ or $\vald$).
-For example, $\cbfaa{n}{\valf}$ will represent $create(n,\valf)$,
+For example, $\cbfaa{n}$ will represent $create(n,\valf)$,
 and $\cdba{n}$ will represent $rmdir(n)$.
-\end{mydef}
+When describing unknown commands, we substitute one or both
+of their values with variables, and write e.g. $\cxynv$.
+By $\cxynv=\czwmv$ we mean that the commands are identical
+($[x]=[z]$ and $y=z$ and $n=m$).
+As suggested above, we will frequently only investigate
+the types of the input and output values of a command
+(its input and output types), and write
+$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$.
 
@@
 We note that a command or a sequence of commands is applied to a filesystem
-by prefixing the command or sequence to it, for example: $\cbrk\aFS$, $\cbdaa{n}{\vald}\aFS$, 
+by prefixing the command or sequence to it, for example: $\cbrk\aFS$, $\cbdaa{n}\aFS$, 
 or $S\aFS$ if $S$ is a sequence of commands.
@@
 We use a replacement operator of the form
-$\FS[\valv/n]$ to denote a filesystem derived from $\FS$ 
+$\FS_{[\valv/n]}$ to denote a filesystem derived from a non-broken $\FS$ 
 by replacing its value at $n$ with $\valv$:
-\[ \FS[\valv/n](m) =
+\[ \FS_{[\valv/n]}(m) =
    \begin{cases}
@@
    \fsbroken &\mbox{if~} \FS=\fsbroken\\
-   \fsbroken &\mbox{if~} \FS(n)\not\in\setvx{X}\\
-   \fsbroken &\mbox{if~} \FS[\valvy/n] \mbox{~violates the tree property}\\
-   \FS[\valvy/n] &\mbox{otherwise.}
+   \fsbroken &\mbox{if~} [\FS(n)]\neq[x]\\
+   \fsbroken &\mbox{if~} \FS_{[y/n]} \mbox{~violates the tree property}\\
+   \FS_{[y/n]} &\mbox{otherwise.}
    \end{cases}
@@
 \end{mydef}
-
-In general, when we describe multiple or unknown commands, we may substitute one or both
-of their types with variables, as we did with $\cxynv$. In this context,
-if we write that $\cxy=\czw$, we mean that the input and output types
-of the commands are the same ($X=Z$ and $Y=W$), while a full equality 
-($\cxynv=\czwmv$)
-implies
-that their nodes and output values are also the same.
 

### 2016-10-08 p2/def-filesystem.tex
New notation for commands

@@
 We write $n\descendant m$ if $n$ is the ancestor of $m$,
-that is, $n=\parent^a(m)$ for some integer $a\ge 1$.
+that is, $n=\parent^i(m)$ for some integer $i\ge 1$.
 % or the path name of $n$ is an initial segment of that of $m$. 
@@
 We write $n\unrel m$, or $n$ and $m$ are \emph{incomparable}
-if $n\not\descendantEq m$ and $n\not\ancestorEq m$;
+iff $n\not\descendantEq m$ and $n\not\ancestorEq m$;
 that is, incomparable nodes are on different branches or on different trees.
@@
 then there must be a directory at the parent node.
-To model this, in $\setv$ we select another special value
-to represent directories, as we assume that apart from their location
-in the filesystem, all directories are equal.
-We do this because, as Bill Zissimopoulos pointed 
-out \cite{BZ},
-we often do not want to consider metadata stored in
-directories (e.g. permission settings) during synchronization,
-as these are not generally understood well by users,
-and, if needed, conflict resolution on these settings can be easily automated.
-We will also see that this assumption makes it possible
-to define a maximal reconciliation algorithm.
+To model this, we differentiate between files, directories, and the
+empty value in $\setv$, and introduce the equivalence relation
+$\typeeq$.
 
-Let therefore the value representing directories be $\vald$,
-and let us define subsets of $\setv$ for each type of value:
-let $\setd$ be $\{\vald\}$, let $\setb$ be $\{\empt\}$, 
-and let $\setf$ contain all remaining values that represent
-different file contents together with any metadata associated with them:
-\[ \setv = \setb \cup \setf \cup \setd. \]
+\begin{mydef}[Equivalence by type: $\typeeq$]
+We write $v_1\typeeq v_2$ for $v_1,v_2\in\setv$ if $v_1$ and $v_2$ are both files,
+are both directories, or are both $\empt$.
+In other words, if $\setf$ is the set of file values and $\setd$ is the set of directories, then
+with $\{\empt\}$ they form a partition of $\setv$:
+\[ \setv/{\typeeq} = \{\setd,\setf,\{\empt\}\}. \]
+\end{mydef}
 
-The tree property can then be defined as
+As usual, we write $[v]$ for the equivalence class of $v$, which is its type.
+We also regard all file contents including all metadata to be included in the values in $\setf$.
+
+The formal definition of the tree property is therefore
 \begin{mydef}[Tree property]
@@
 \end{mydef}
-This means that as we move down from the root of a tree of nodes,
-the types of values we encounter in the filesystem can only change according to the
-transition diagram in \cref{fig_transition}, from directories ($\cchard$) to files ($\ccharf$)
-to empty nodes ($\ccharb$).
 
-\begin{figure}[htb]
-\input{fig-type-transition}
-\caption{Transitions between types of values from the root of a tree in a filesystem}\label{fig_transition}
-\end{figure}
+To avoid the proliferation of edge cases, we will furthermore suppose that
+$|\setd|=1$, that is, apart from their location, all directories are equal;
+and use $\vald$ to denote the single value of the directory type.
+In appendix TODO we describe why it can be a sensible choice
+for actual synchronizers, and we also present an encoding that makes it possible
+to extend our results to the $|\setd|>1$ case.
+
+%% TODO
+% % To model this, in $\setv$ we select another special value
+% % to represent directories, as we assume that apart from their location
+% % in the filesystem, all directories are equal.
+% % We do this because, as Bill Zissimopoulos pointed 
+% % out \cite{BZ},
+% % we often do not want to consider metadata stored in
+% % directories (e.g. permission settings) during synchronization,
+% % as these are not generally understood well by users,
+% % and, if needed, conflict resolution on these settings can be easily automated.
+% % We will also see that this assumption makes it possible
+% % to define a maximal reconciliation algorithm.
+
+% This means that as we move down from the root of a tree of nodes,
+% the types of values we encounter in the filesystem can only change according to the
+% transition diagram in \cref{fig_transition}, from directories ($\cchard$) to files ($\ccharf$)
+% to empty nodes ($\ccharb$).
+% 
+% \begin{figure}[htb]
+% \input{fig-type-transition}
+% \caption{Transitions between types of values from the root of a tree in a filesystem}\label{fig_transition}
+% \end{figure}
 
@@
 and $n$, $m$ and $o$ are nodes in $\setn$.
-We use $\valf$ for an arbitrary element in $\setf$, 
-and by $\valvx$ we mean a value of type $X$ in $\setvx{X}$.
+We will write $\valf$ for an arbitrary element in $\setf$.

### 2016-10-08 p2/ordering.tex
New notation for commands

@@
 As $A$ is simple, we know that $\cxynv$ is not an assertion command,
-and therefore $X\neq Y$ and $\FS(n)\neq\valvy$ as it has type $X$.
+and therefore $[x]\neq [y]$ and $\FS(n)\neq y$ as $[\FS(n)]=[x]$.
 If so, then if $B$ has no command on $n$, then $B\aFS(n)=\FS(n)$ and
 $A$ and $B$ cannot be equivalent.
-Otherwise we know that $Z=X$ as $B$ does not break $\FS$ either,
-and that $\valvw=\valvy$ and therefore $W=Y$ as $B\aFS(n)$ must
-be $\valvy$ and $B$ only has one command on $n$.
+Otherwise we know that $[z]=[x]$ as $B$ does not break $\FS$ either,
+and that $w=y$ as $B\aFS(n)$ must
+be $y$ and $B$ only has one command on $n$.
 However, then $\czwnv=\cxynv$, which is a contradiction.

### 2016-10-08 p2/works-inverse.tex
New notation for commands

@@
 The combination of independent commands works wherever the original commands work:
-\[ \cxynv\indep \czwmv \Rightarrow \worksc{\cxynv\cc \czwmv}{\cxynv, \czwmv}. \]
+\[ \alpha\indep \beta \Rightarrow \worksc{\alpha\cc \beta}{\alpha, \beta}. \]
 % \begin{align*}
@@
 because to prove it, we must reach back to our filesystem model.
+Let $\alpha=\cxynv$ and $\beta=\czwmv$.
+%% TODO by contradiction
 We proceed in an indirect way and
@@
 Second, if the input type does not match the filesystem,
-but we know $\FS(m)\in\setvx{W}$ and so
-$(\cxynv\aFS)(m)\in\setvx{W}$ as based on \cref{incomparable_is_independent}, $n\neq m$.
+but we know $[\FS(m)]=[w]$ and so
+$[(\cxynv\aFS)(m)]=[w]$ as based on \cref{incomparable_is_independent}, $n\neq m$.
 Third, if the new filesystem violates the tree property.
@@
 and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$),
-then the input types of these commands must match ($X=Z$).
+then the input types of these commands must match ($[x]=[z]$).
 \end{mylem}
@@
 This result is similar to \cref{equiv_simple_same_commands} and
-is easily shown using an indirect proof: if $X\neq Z$, then there is no filesystem that
+%% TODO by contradiction
+is easily shown using an indirect proof: if $[x]\neq [z]$, then there is no filesystem that
 either $\cxynv$ or $\czwnv$ would not break, 
@@
 and sequences of commands.
+%% TODO extending it!
 \begin{mydef}[Equivalence by type: $\typeeq$]
@@
 \begin{itemize}
-\item For two filesystems we write $\FS\typeeq\GS$ iff they are both broken, or they share the same nodes,
-and at all nodes the types of their values are the same.
-\item For two commands we write $\alpha\typeeq\beta$ iff their input and output types,
-and the node they operate on are the same.
-For example, $\cbfaa{n}{f_1}\typeeq\cbfaa{n}{f_2}$.
+\item For two filesystems we write $\FS\typeeq\GS$ iff they are both broken, or they share the same nodes $\setn$,
+and for all $n\in\setn$, $[\FS(n)]=[\GS(n)]$.
+\item For two commands we write $\cxynv\typeeq\czwnv$ iff 
+$[x]=[z]$ and $[y]=[w]$ and $n=m$.
 \item For two sequences of commands we write $A\typeeq B$ iff they contain the same number of commands,
@@
 In other words, two type-equivalent objects can only differ in the value they contain,
-but as $|\setb|=|\setd|=1$, this is only possible at values of the type $\ccharf$.
-We select an arbitrary file value $\fil\in\setf$, and choose a representative
-of each $\typeeq$-equivalence class where all (if any) values of the type $\ccharf$ is $\fil$.
-For example, in the case of commands, the representative of $[\cbfaa{n}{f}]_\typeeq$ is $\cbfaa{n}{\fil}$.
+but as $|\setb|=|\setd|=1$, this is only possible at values of the type $[\valf]$.
+We select an arbitrary file value $\fil\in[\valf]$, and choose a representative
+of each $\typeeq$-equivalence class where all (if any) values of the type $[\valf]$ is $\fil$.
+For example, in the case of commands, the representative of $[\cbfaa{n}]_\typeeq$ is $\caaa{\empt}{\fil}{n}$.
 
 \begin{mydef}[$\T$]
-We use $\T$ and write $x\T$ to denote the canonical mapping of 
+We use $\T$ and write $X\T$ to denote the canonical mapping of 
 filesystems, commands and sequences to the
@@
 
-For example, $\cbfaa{n}{f}\T = \cbfaa{n}{\fil}$,
+For example, $\cbfaa{n}\T = \caaa{\empt}{\fil}{n}$,
 and for the sequence $S=\alpha\cc\beta$, $S\T=\alpha\T\cc\beta\T$.
@@
 into a system where $|\setf|$ is also $1$.
+
+% TODO <[x],y,n> T = <[x],[y],n>
+% one-to-one corresp btw values and types
 
@@
 \begin{mylem}
-Representative functions $\alpha\T$ are injections over representative filesystems ($\FS\T$)
+Representative commands $\alpha\T$ are injections over representative filesystems ($\FS\T$)
 except for the cases where they break a filesystem, that is,
@@
 \end{mydef}
+
+%% TODO
+% Do we need <[x],[y],n>-1 = <[y],[x],n> ?
+% Do we need to prove if a filesystem is not in the image, then a-1 will break it?
 

### 2016-10-08 p2/def-commands.tex
Improvements to the T mapping

@@
 (its input and output types), and write
-$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$.
+$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$
+(or equivalently $x\typeeq z$ and $y\typeeq w$).
 

### 2016-10-08 p2/works-inverse.tex
Improvements to the T mapping

@@
 \begin{itemize}
-\item For two filesystems we write $\FS\typeeq\GS$ iff they are both broken, or they share the same nodes $\setn$,
-and for all $n\in\setn$, $[\FS(n)]=[\GS(n)]$.
-\item For two commands we write $\cxynv\typeeq\czwnv$ iff 
-$[x]=[z]$ and $[y]=[w]$ and $n=m$.
-\item For two sequences of commands we write $A\typeeq B$ iff they contain the same number of commands,
-and pairwise the commands $\alpha\in A$ and $\beta\in B$ at the same indices are equivalent by type ($\alpha\typeeq\beta$).
+\item For two filesystems $\FS\typeeq\GS$ iff they are both broken, or they share the same nodes $\setn$,
+and for all $n\in\setn$, $\FS(n) \typeeq \GS(n)$.
+\item For two commands $\cxynv\typeeq\czwnv$ iff 
+$x\typeeq z$ and $y\typeeq w$ and $n=m$.
+\item For two sequences of commands $\emptyseq\typeeq\emptyseq$, and
+if $A'=\alpha\cc A$ and $B'=\beta\cc B$, then $A'\typeeq B'$ iff $\alpha\typeeq\beta$ and $A\typeeq B$.
 \end{itemize}
@@
 
-In other words, two type-equivalent objects can only differ in the value they contain,
-but as $|\setb|=|\setd|=1$, this is only possible at values of the type $[\valf]$.
-We select an arbitrary file value $\fil\in[\valf]$, and choose a representative
-of each $\typeeq$-equivalence class where all (if any) values of the type $[\valf]$ is $\fil$.
-For example, in the case of commands, the representative of $[\cbfaa{n}]_\typeeq$ is $\caaa{\empt}{\fil}{n}$.
+We select representatives of each $\typeeq$-equivalence class of values:
+for $[\empt]$ and $[\vald]$ this must be $\empt$ and $\vald$; and
+for $[\valf]$ we select an arbitrary file value $\fil\in[\valf]$.
+We then use these representative values to
+select representatives of the equivalence classes of
+other objects in the following way:
 
@@
 We use $\T$ and write $X\T$ to denote the canonical mapping of 
-filesystems, commands and sequences to the
+values, filesystems, commands and sequences to the
 representatives of their $\typeeq$-equivalence class.
-$\T$ is also extended to sets of sequences,
-where $\seqset{A}\T = \{S\T | S\in\seqset{A}\}$.
+\begin{itemize}
+\item For values, $\vald\T=\vald$, $\valf\T=\fil$ and $\empt\T=\empt$.
+\item For filesystems, $\FS\T$ is defined by $\FS\T(n) = \FS(n)\T$.
+\item For commands, $\cxynv\T = \cTxynv$.
+\item For sequences of commands, $\emptyseq\T=\emptyseq$, and if $S'=\alpha\cc S$, then $S'\T=\alpha\T\cc S\T$.
+\item Finally we extend $\T$ to sets of sequences: $\seqset{A}\T = \{S\T | S\in\seqset{A}\}$.
+\end{itemize}
 \end{mydef}
 
-For example, $\cbfaa{n}\T = \caaa{\empt}{\fil}{n}$,
-and for the sequence $S=\alpha\cc\beta$, $S\T=\alpha\T\cc\beta\T$.
+It is easy to see that for all objects where it is defined, $X\T\typeeq X$.
+
 In other words, $\T$ maps our system of filesystems and commands
-into a system where $|\setf|$ is also $1$.
+into a \emph{representative} system where there is a one-to-one correspondence between types
+and values.
+% $|\setf|$ is also $1$.
+At the same time, representative filesystems, commands, sequences, etc.
+are subsets of their non-representative counterparts; hence all
+propositions proven so far apply to them as well.
 
@@
 
-\begin{mylem}
+\begin{mylem}\label{repr_comm_inject}
 Representative commands $\alpha\T$ are injections over representative filesystems ($\FS\T$)
@@
 This is trivial if $\GS\T=\fsbroken$, so we assume it is not so.
+Let $\alpha\T = \cTxynv$.
 If $\FS\T$ and $\GS\T$ have different values at any node apart from $n$, then this difference remains
-even after applying the command to $\FS\T$. The only remaining case therefore is where they have the same values
+even after applying $\cTxynv$ to $\FS\T$. The only remaining case therefore is where they have the same values
 at all nodes except $n$.
-We know that a representative filesystem can only have values from the set $\rvalueset$.
-As $\alpha\T(\FS\T)\neq\fsbroken$, $\FS\T(n)$ must be the value that matches the input type of $\alpha\T$.
-We know that $\GS\T(n)\neq\FS\T(n)$, and therefore $\GS\T(n)$ must have a different type,
-which implies $\alpha\T(\GS\T)=\fsbroken$ as it cannot match the input type of $\alpha\T$,
+As $\cTxynv(\FS\T)\neq\fsbroken$, we know $[\FS\T(n)]=[x]$.
+We also know that $\GS\T(n)\neq\FS\T(n)$, and therefore, as there is a one-to-one correspondence between values and types,
+$[\GS\T(n)]\neq[x]$.
+This implies $\cTxynv(\GS\T)=\fsbroken$,
 and again we have $\alpha\T(\FS\T) \neq \alpha\T(\GS\T)$.
@@
 \begin{mydef}[Inverse commands and sequences]
-If we regard the representative command $\alpha\T$ a function whose
+If based on \cref{repr_comm_inject}
+we regard the representative command $\alpha\T$ a bijective function whose
 domain is the subset of representative filesystems $\{\FS\T | \alpha\aFS\neq\fsbroken\}$,
@@
 for which we write $\alpha\T^{-1}$.
+For any $\GS\T$ outside the range of $\alpha\T$ we define $\alpha\T^{-1}(\GS\T)$ to be $\fsbroken$.
+
 We write ${S\T}^{-1}$ for the inverse of the sequence $S\T$, which consists of the inverses of the commands in $S\T$
@@
 % Do we need to prove if a filesystem is not in the image, then a-1 will break it?
+\begin{mylem}
+For representative commands
+\[ \cTxynv^{-1} = \cTyxnv \]
+\end{mylem}
+TODO
 
 From the definitions we can clearly see that
-\begin{mycor}\label{negneg_is_typeeq} %% TODO Don't use!
-$\forall S, \FS: (S^{-1})^{-1}\aFS\typeeq S\aFS$.
+\begin{mycor}\label{negneg_is_typeeq}
+$\forall S: ({S\T}^{-1})^{-1} = S\T$.
 \end{mycor}

### 2016-10-08 p2/def-commands.tex
Fixed lemma and proof

@@
 and represent them using triples that contain
-their input type ($[v_{in}]$), output value ($v_{out}$),
+their input type ($[v_\textrm{in}]$), output value ($v_\textrm{out}$),
 and the node to which they are applied ($n$):
-\[ \caaaa{v_{in}}{v_{out}}{n}. \]
+\[ \caaaa{v_\textrm{in}}{v_\textrm{out}}{n}. \]
 \end{mydef}

### 2016-10-08 p2/works-inverse.tex
Fixed lemma and proof

@@
 We then use these representative values to
-select representatives of the equivalence classes of
-other objects in the following way:
+introduce the canonical mapping $\T$ that preserves the types of values,
+but maps all objects into a subsystem where there is a one-to-one
+correspondence between types and values.
 
@@
 \item For values, $\vald\T=\vald$, $\valf\T=\fil$ and $\empt\T=\empt$.
-\item For filesystems, $\FS\T$ is defined by $\FS\T(n) = \FS(n)\T$.
-\item For commands, $\cxynv\T = \cTxynv$.
+\item For filesystems, $\fsbroken\T=\fsbroken$ and in other cases $\FS\T$ is defined by $\FS\T(n) = \FS(n)\T$.
+\item For commands, $\cbrk\T=\cbrk$ and $\cxynv\T = \cTxynv$.
 \item For sequences of commands, $\emptyseq\T=\emptyseq$, and if $S'=\alpha\cc S$, then $S'\T=\alpha\T\cc S\T$.
@@
 It is easy to see that for all objects where it is defined, $X\T\typeeq X$.
-
-In other words, $\T$ maps our system of filesystems and commands
-into a \emph{representative} system where there is a one-to-one correspondence between types
-and values.
 % $|\setf|$ is also $1$.
-At the same time, representative filesystems, commands, sequences, etc.
-are subsets of their non-representative counterparts; hence all
+As representatives of filesystems, commands, sequences, etc.
+are subsets of their non-representative counterparts, all
 propositions proven so far apply to them as well.
-
-% TODO <[x],y,n> T = <[x],[y],n>
-% one-to-one corresp btw values and types
 
@@
 $\alpha\T(\FS\T) = (\alpha\aFS)\T$.
+TODO needed?
 \end{mycor}
@@
 of the commands, only the input and output types, we know that
-\begin{mycor}
+\begin{mycor}\label{repr_works_is_same}
 \begin{gather*}
@@
 for which we write $\alpha\T^{-1}$.
-For any $\GS\T$ outside the range of $\alpha\T$ we define $\alpha\T^{-1}(\GS\T)$ to be $\fsbroken$.
+For any $\GS\T$ outside the image of the domain of $\alpha\T$ we define $\alpha\T^{-1}(\GS\T)$ to be $\fsbroken$.
 
@@
 For representative commands
-\[ \cTxynv^{-1} = \cTyxnv \]
+\[ \cTxynv^{-1} = \cTyxnv. \]
 \end{mylem}
-TODO
+TODO needed? -maybe for \cref{negneg_is_typeeq}
 
@@
 
+For brevity, in the following lemma we use $B$, $B'$, $\seqset{A}$ and $\seqset{C}$ to denote
+representative sequences and sets.
+
 \begin{mylem}\label{r_invmove}
-A common initial segment of a set of sequences can be moved to the other side of $\workssign$ by inverting it:
+A common initial segment of a set of \emph{representative} sequences can be moved to the other side of $\workssign$ by inverting it:
 \begin{gather*}
 \worksc{B\cc \seqset{A}}{\seqset{C}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{C}} \\
-\worksc{\seqset{A}}{B\cc \seqset{C}} \Rightarrow \worksc{B^{-1}\cc \seqset{A}}{\seqset{C}}
+\worksc{B}{\seqset{C}} \wedge \worksc{\seqset{A}}{B^{-1}\cc \seqset{C}} \Rightarrow \worksc{B\cc \seqset{A}}{\seqset{C}}
 \end{gather*}
@@
 
-%% TODO see lemma above
-
-This is based on the fact that in our model, unless they break a filesystem,
-commands leave the type of the filesystem value unchanged 
-or change one type into another, but never merge types.
-That is,
-sequences---as functions mapping filesystems to filesystems---are
-essentially bijections over type-equality ($\typeeq$)
-with the only ``sink'' being $\fsbroken$:
-\begin{align*}
-\forall S,\FS,\GS:{}&S\aFS\neq\fsbroken \Rightarrow \\
-&(S\aFS\ntypeeq S\aGS \Longleftrightarrow \FS\ntypeeq \GS).
-\end{align*}
-
-For the proposition
-\[ \worksc{B\cc \seqset{A}}{\seqset{C}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{C}} \]
-the rest of the proof is illustrated by \cref{fig_invmove}
-where $\textrm{Dom}(x)$, the domain of $x$, represents the set of filesystems
-the sequence $x$ does not break, or neither of the sequences in the set $x$ breaks.
+The proof for both propositions is illustrated by \cref{fig_invmove}, where
+$\Dom{X}$, the domain of $X$, represents the set of filesystems
+the sequence $X$ does not break, or neither of the sequences in the set $X$ breaks.
+We write $\Img{X}$ to denote the image of the domain of the sequence $X$.
+We also note that in general $\worksc{\seqset{X}}{\seqset{Y}} \Leftrightarrow \Dom{\seqset{Y}} \subset \Dom{\seqset{X}}$.
 
@@
 
-We see that the set of filesystems the sequences in $\seqset{A}$ do not break intersect with the range of $B$.
-As $B$ is a bijection between its domain and range, we can use $B^{-1}$ to map this intersection back
-onto the domain of $B$.
-As $\worksc{B\cc \seqset{A}}{\seqset{C}}$ the domain of $\seqset{C}$ must be a subset of this
-projected intersection.
-If so, then we can use $B$ to map the domain of $\seqset{C}$, which yields the domain of $B^{-1}\cc \seqset{C}$.
-As it is also a part of the domain of $A$, we get $\worksc{\seqset{A}}{B^{-1}\cc \seqset{C}}$.
+Unless $\works{\seqset{C}}$, both propositions are trivially true. Otherwise,
+for the first proposition
+we know $\works{B\cc\seqset{A}}$, which implies that $\Dom{\seqset{A}}$ intersects with $\Img{B}$ 
+as otherwise $B\cc\seqset{A}$ would break all filesystems.
+As the (representative) $B$ is a bijection between its domain and image,
+we can use $B^{-1}$ to map this intersection back
+onto the domain of $B$ and get $\Dom{B\cc\seqset{A}}$.
+As $\worksc{B\cc \seqset{A}}{\seqset{C}}$, 
+we know that $\Dom{\seqset{C}} \subset \Dom{B\cc\seqset{A}}$.
+We now use $B$ to map both sides of this statement, which yields
+$\Dom{B^{-1}\cc \seqset{C}} \subset \Dom{B^{-1}\cc B\cc\seqset{A}}$,
+but the latter is a subset of $\Dom{\seqset{A}}$,
+and so $\Dom{B^{-1}\cc \seqset{C}} \subset \Dom{\seqset{A}}$,
+from which $\worksc{\seqset{A}}{B^{-1}\cc \seqset{C}}$.
 
-The second part of the lemma can be proven in a similar way.
+For the second proposition, 
+from $\worksc{B}{\seqset{C}}$ we know $\Dom{\seqset{C}} \subset \Dom{B}$.
+Therefore we can project the whole of $\Dom{\seqset{C}}$ using the bijective representative sequence $B$
+to get $\Dom{B^{-1}\cc\seqset{C}}$, and as $\worksc{\seqset{A}}{B^{-1}\cc \seqset{C}}$
+we know
+$\Dom{B^{-1}\cc\seqset{C}} \subset \Dom{\seqset{A}}$.
+We use $B^{-1}$ to project both sides of this statement to get
+$\Dom{B\cc B^{-1}\cc\seqset{C}} \subset \Dom{B\cc\seqset{A}}$.
+But we also know that $\Dom{B\cc B^{-1}\cc\seqset{C}} = \Dom{\seqset{C}}$
+as $\Dom{\seqset{C}} \subset \Dom{B}$,
+and so $\Dom{\seqset{C}} \subset \Dom{B\cc\seqset{A}}$
+from which $\worksc{B\cc \seqset{A}}{\seqset{C}}$.
 \end{proof}
@@
 \begin{proof}
-Based on \cref{r_invmove} we know
-$\worksc{B}{A^{-1}\cc \seqset{S}}$ and $\worksc{C}{A^{-1}\cc \seqset{S}}$,
-and from \cref{combine_independent_sequences} we know
-$\worksc{B\cc C}{B,C}$.
-Combining these using \cref{workschained}
+Based on \cref{repr_works_is_same} we have
+$\worksc{A\T\cc B\T}{\seqset{S\T}}$ and $\worksc{A\T\cc C\T}{\seqset{S\T}}$,
+and from \cref{r_invmove} we know
+$\worksc{B\T}{{A\T}^{-1}\cc \seqset{S\T}}$ and $\worksc{C\T}{{A\T}^{-1}\cc \seqset{S\T}}$.
+Using \cref{combine_independent_sequences} we get
+$\worksc{B\T\cc C\T}{B\T,C\T}$,
+and combining these using \cref{workschained}
 we get
-$\worksc{B\cc C}{A^{-1}\cc \seqset{S}}$. 
-Finally, applying the second line of \cref{r_invmove} yields
-$\worksc{(A^{-1})^{-1}\cc B\cc C}{\seqset{S}}$, which proves our lemma 
-as $\forall\FS: (A^{-1})^{-1}\aFS\typeeq A\aFS$ (\cref{negneg_is_typeeq}).
+$\worksc{B\T\cc C\T}{{A\T}^{-1}\cc \seqset{S\T}}$.
+
+From $\worksc{A\cc B}{\seqset{S}}$ we also know $\worksc{A}{\seqset{S}}$ and $\worksc{A\T}{\seqset{S\T}}$.
+We can combine this and $\worksc{B\T\cc C\T}{{A\T}^{-1}\cc \seqset{S\T}}$ using
+the second proposition of \cref{r_invmove} to get
+$\worksc{A\T\cc B\T\cc C\T}{\seqset{S\T}}$, and from \cref{repr_works_is_same} we know
+$\worksc{A\cc B\cc C}{\seqset{S}}$.
 \end{proof}

### 2016-10-08 p2/works-inverse.tex
New symbol and definition for the w relation

@@
 \subsection{Conditional Operation and Inverse Sequences}
-
-\begin{mydef}[$\works{x}$]
-% Unsure if this relation should be in the algebra.
-For a set of $k$ sequences
-$\works{A_1,A_2,\ldots,A_k}$ means that 
-$A_1,A_2,\ldots,A_k$ work at the same time, that is,
-% intended interpretation:
-\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_k\FS\neq\fsbroken.\]
-As the sequences form a set, their order is irrelevant.
-% inference rules:
-We also know that $\works{A} \Leftrightarrow A\nequiv \cbrk$. 
-\end{mydef}
-
-\begin{mydef}[$\worksc{x}{y}$]
-For two sets of sequences, $\worksc{A_1,A_2,\ldots,A_k}{B_1,B_2,\ldots,B_l}$ means that 
-all of $A_1,\ldots,A_k$ work where all of $B_1,\ldots,B_l$ work,
-that is,
-% intended interpretation:
-\begin{align*}
-\forall \FS:{}& 
-B_1\FS\neq\fsbroken \wedge \cdots \wedge B_k\FS\neq\fsbroken\\
-&\Rightarrow\\
-&A_1\FS\neq\fsbroken \wedge \cdots \wedge A_l\FS\neq\fsbroken.
-\end{align*}
-As above, the order of the sequences in the sets is not relevant.
-\end{mydef}
 
@@
 
+\begin{mydef}[$\Dom{X}$ and $\Img{X}$]
+$\Dom{X}$ is the domain of $X$.
+For a sequence of commands $A$, $\Dom{A}$ is the set of filesystems $A$ does not break.
+For a set of sequences $\seqset{A}$, $\Dom{\seqset{A}}$ is the set of filesystems no $A\in\seqset{A}$ breaks.
+We write $\Img{X}$ to denote the image of the domain of the sequence $X$.
+\end{mydef}
+
+\begin{mydef}[$\worksmsign$, $\worksmeqsign$]
+For two sets of sequences $\sqs{A}$ and $\sqs{B}$
+we write $\worksm{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subseteq \Dom{\sqs{B}}$;
+that is, if all sequences in $\sqs{B}$ work (do not break the filesystem)
+on any filesystem all sequences in $\sqs{A}$ work on.
+We write $\worksmstr{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subset \Dom{\sqs{B}}$.
+
+As a special case, we write $\worksmnil{\sqs{A}}$ if we know that there is a filesystem
+all sequences in $\sqs{A}$ work on,
+and we apply these relations to sequences directly:
+$\worksm{A}{B}$ with the meaning $\worksm{\{A\}}{\{B\}}$.
+\end{mydef}
+
 It is easy to see that the following corollaries are true:
-
-% An inference rule in the algebra
-% $\worksc{X}{X}$ is always true for any set of sequences $X$,
-
-% \begin{mycor}
-% % An inference rule in the algebra
-% $B\eqext A \Rightarrow \worksc{A}{B}$.
-% \end{mycor}
 
@@
 % An inference rule in the algebra
-$\forall A,S: \worksc{A}{A\cc S}$, that is, if a sequence works, its initial segment also works.
+$\forall A,S: \worksm{A\cc S}{A}$, that is, if a sequence works, its initial segment also works.
 \end{mycor}
@@
 % An inference rule in the algebra
-$\workssign$ can be chained:
-if $\seqset{A'}\subset\seqset{A}$, then
-$ \worksc{\seqset{C}}{\seqset{A'}} \wedge \worksc{\seqset{A}}{\seqset{B}} \Rightarrow \worksc{\seqset{A}\cup\seqset{C}}{\seqset{B}}$.
+$\worksmeqsign$ can be chained:
+if $\seqset{B'}\subseteq\seqset{B}$, then
+$\worksm{\sqs{A}}{\sqs{B}} \wedge \worksm{\sqs{B'}}{\sqs{C}} \Rightarrow \worksm{\sqs{A}}{\sqs{B}\cup\sqs{C}}$.
 \end{mycor}
@@
 The combination of independent commands works wherever the original commands work:
-\[ \alpha\indep \beta \Rightarrow \worksc{\alpha\cc \beta}{\alpha, \beta}. \]
-% \begin{align*}
-% \forall\FS:{}&\cxynv\indep \czwmv \\
-% &\quad\wedge \cxynv\aFS\neq\fsbroken \\
-% &\quad\wedge \czwmv\aFS\neq\fsbroken \\
-% &\Rightarrow \cxynv\cc \czwmv\aFS\neq\fsbroken.
-% \end{align*}
+\[ \alpha\indep \beta \Rightarrow \worksm{\{\alpha, \beta\}}{\{\alpha\cc \beta\}}. \]
 \end{myax}
@@
 The combination of independent sequences works wherever the original sequences work:
-\[ S\indep T \Rightarrow \worksc{S\cc T}{S,T}. \]
+\[ S\indep T \Rightarrow \worksm{\{S,T\}}{\{S\cc T\}}. \]
 \end{mylem}
@@
 \begin{mylem}\label{worksinputmatch}
-If $A$ and $B$ are minimal sequences, $\works{A,B}$,
+If $A$ and $B$ are minimal sequences, $\worksmnil{\{A,B\}}$,
 and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$),
@@
 
+% TODO We introduced BREAK to deal with cases where commands
+% are in effect not defined. Now we need to undo this 
+% to see that repr commands are bijective.
+
 \begin{mydef}[Inverse commands and sequences]
@@
 \begin{mylem}\label{r_invmove}
-A common initial segment of a set of \emph{representative} sequences can be moved to the other side of $\workssign$ by inverting it:
+A common initial segment of a set of \emph{representative} sequences can be moved to the other side of $\worksmeqsign$ by inverting it:
 \begin{gather*}
-\worksc{B\cc \seqset{A}}{\seqset{C}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{C}} \\
-\worksc{B}{\seqset{C}} \wedge \worksc{\seqset{A}}{B^{-1}\cc \seqset{C}} \Rightarrow \worksc{B\cc \seqset{A}}{\seqset{C}}
+\worksm{\seqset{C}}{B\cc \seqset{A}}
+\ \Longleftrightarrow \ \worksm{B^{-1}\cc \seqset{C}}{\seqset{A}} 
+\ \wedge \  \worksm{\seqset{C}}{\{B\}}
 \end{gather*}
@@
 \begin{proof}
+% TODO Rewrite for equivalence, and swap A and C.
+% This result is quite expected as we're mapping a subset statement using a bijection,
+% but made more complicated a as B is not defined everywhere.
 
-The proof for both propositions is illustrated by \cref{fig_invmove}, where
-$\Dom{X}$, the domain of $X$, represents the set of filesystems
-the sequence $X$ does not break, or neither of the sequences in the set $X$ breaks.
-We write $\Img{X}$ to denote the image of the domain of the sequence $X$.
-We also note that in general $\worksc{\seqset{X}}{\seqset{Y}} \Leftrightarrow \Dom{\seqset{Y}} \subset \Dom{\seqset{X}}$.
+The proof for both propositions is illustrated by \cref{fig_invmove}.
 
@@
 As $\worksc{B\cc \seqset{A}}{\seqset{C}}$, 
-we know that $\Dom{\seqset{C}} \subset \Dom{B\cc\seqset{A}}$.
+we know that $\Dom{\seqset{C}} \subseteq \Dom{B\cc\seqset{A}}$.
 We now use $B$ to map both sides of this statement, which yields
-$\Dom{B^{-1}\cc \seqset{C}} \subset \Dom{B^{-1}\cc B\cc\seqset{A}}$,
-but the latter is a subset of $\Dom{\seqset{A}}$,
-and so $\Dom{B^{-1}\cc \seqset{C}} \subset \Dom{\seqset{A}}$,
+$\Dom{B^{-1}\cc \seqset{C}} \subseteq \Dom{B^{-1}\cc B\cc\seqset{A}}$,
+but the latter is a subseteq of $\Dom{\seqset{A}}$,
+and so $\Dom{B^{-1}\cc \seqset{C}} \subseteq \Dom{\seqset{A}}$,
 from which $\worksc{\seqset{A}}{B^{-1}\cc \seqset{C}}$.
@@
 For the second proposition, 
-from $\worksc{B}{\seqset{C}}$ we know $\Dom{\seqset{C}} \subset \Dom{B}$.
+from $\worksc{B}{\seqset{C}}$ we know $\Dom{\seqset{C}} \subseteq \Dom{B}$.
 Therefore we can project the whole of $\Dom{\seqset{C}}$ using the bijective representative sequence $B$
@@
 we know
-$\Dom{B^{-1}\cc\seqset{C}} \subset \Dom{\seqset{A}}$.
+$\Dom{B^{-1}\cc\seqset{C}} \subseteq \Dom{\seqset{A}}$.
 We use $B^{-1}$ to project both sides of this statement to get
-$\Dom{B\cc B^{-1}\cc\seqset{C}} \subset \Dom{B\cc\seqset{A}}$.
+$\Dom{B\cc B^{-1}\cc\seqset{C}} \subseteq \Dom{B\cc\seqset{A}}$.
 But we also know that $\Dom{B\cc B^{-1}\cc\seqset{C}} = \Dom{\seqset{C}}$
-as $\Dom{\seqset{C}} \subset \Dom{B}$,
-and so $\Dom{\seqset{C}} \subset \Dom{B\cc\seqset{A}}$
+as $\Dom{\seqset{C}} \subseteq \Dom{B}$,
+and so $\Dom{\seqset{C}} \subseteq \Dom{B\cc\seqset{A}}$
 from which $\worksc{B\cc \seqset{A}}{\seqset{C}}$.

### 2016-10-11 p2/def-commands.tex
Introduction of partial functions

@@
 
-\begin{mydef}[Regular commands]
-Therefore we have three pieces of information related to each command,
+\begin{mydef}[Filesystem commands]
+We model filesystem commands as partial endofunctions on filesystems,
+that is, functions that map filesystems to filesystems, but which
+are not defined everywhere.
+%% TODO Return \bottom where undefined.
+
+TODO. Therefore we have three pieces of information related to each command,
 and represent them using triples that contain

### 2016-10-12 p2/def-commands.tex
New definition of commands

--- 2016-10-08 p2/def-commands.tex
@@
 We start by summarizing our reasons for doing so.
+
+% What is encoded in a command?
 
@@
 
-\begin{mydef}[Regular commands]
-Therefore we have three pieces of information related to each command,
-and represent them using triples that contain
-their input type ($[v_{in}]$), output value ($v_{out}$),
-and the node to which they are applied ($n$):
-\[ \caaaa{v_{in}}{v_{out}}{n}. \]
+\bigskip
+
+% Break / empty command
+
+\noindent
+A command at times will return an error.
+This happens if the encoded type of the original filesystem value does not match
+what is actually in the filesystem, or if the modified filesystem no
+longer has the tree property.
+In these cases we say that the command {\em breaks} the filesystem,
+and the function we use to model the command will be undefined on the filesystem.
+
+So that we could reason about sequences of commands that break every filesystem, 
+we also introduce the command $\cbrk$ which is not defined anywhere,
+that is, which simply breaks every filesystem.
+
+% Definition
+
+\begin{mydef}[Filesystem commands]
+In other words, we model filesystem commands as partial endofunctions on filesystems,
+that is, functions that map filesystems to filesystems, but which
+are not defined everywhere:
+\[ \alpha: \setf \nrightarrow \setf \]
+A command $\alpha$ is not defined on filesystems that it would break.
+At times in these cases we write that the command returns the bottom element, $\fsbroken$.
+We write $\cbrk$ for the empty partial function which is not defined anywhere.
+
+We have three pieces of information defining a non-empty command,
+which we represent using a triple. These are its
+input type ($[v_\textrm{in}]$), output value ($v_\textrm{out}$),
+and the node to which it is applied ($n$):
+\[ \alpha = \caaaa{v_\textrm{in}}{v_\textrm{out}}{n}. \]
 \end{mydef}
@@
 
-\bigskip
-
-\noindent
-A command can only succeed if the original value at node $n$ has a type that matches
-the input type of the command. If this is not the case, or if the resulting
-filesystem no longer has the tree property, then we say that the command
-{\em breaks} the filesystem, and assigns $\fsbroken$ to it.
-Broken filesystems are considered equal, but not equal to any working filesystem.
-
-So that we could reason about sequences of commands that break every filesystem, 
-we introduce, in addition to the regular commands,
-the command $\cbrk$ that simply breaks every filesystem.
-
 We note that a command or a sequence of commands is applied to a filesystem
@@
 We use a replacement operator of the form
-$\FS_{[\valv/n]}$ to denote a filesystem derived from a non-broken $\FS$ 
+$\FS_{[\valv/n]}$ to denote a filesystem derived from $\FS$ 
 by replacing its value at $n$ with $\valv$:
@@
    \begin{cases}
-   \fsbroken &\mbox{if~} \FS=\fsbroken\\
+   % \fsbroken &\mbox{if~} \FS=\fsbroken\\
    \fsbroken &\mbox{if~} [\FS(n)]\neq[x]\\

### 2016-10-12 p2/def-filesystem.tex
New definition of commands

@@
 and a set of possible contents or values $\setv$ as its codomain.
-Alternatively, if the filesystem has encountered a problem and is no longer usable, 
-we assign it the special value $\fsbroken$:
-\begin{mydef}[Filesystem]
-\begin{gather*}
-\FS =
-\begin{cases}
-\setn \rightarrow \setv \\
-\fsbroken
-\end{cases}
-\end{gather*}
-\end{mydef}
+\begin{mydef}[Filesystems, $\setn$, $\setv$ and $\setf$]
+\[ \FS: \setn \rightarrow \setv \]
 In our model, $\setn$ 
@@
 where in our model $\FS$ has a special value, $\empt\in\setv$.
+We write $\setfs$ for the set of filesystems.
+\end{mydef}
 
@@
 \begin{mydef}[$\parent$]
-The function $\parent(n)$ returns the parent node of $n$, or
-returns $\topnode$ if $n$ is the root of a tree.
+The partial function $\parent:\setn\nrightarrow\setn$
+returns the parent node of $n$,
+and is undefined if $n$ is the root of a tree.
 \end{mydef}
@@
 are both directories, or are both $\empt$.
+% TODO needed? v
 In other words, if $\setf$ is the set of file values and $\setd$ is the set of directories, then
@@
 \begin{mydef}[Tree property]
-\begin{align*}
-\forall n\in\setn:{} &\FS(n) \neq \empt \\
-&\quad\wedge \parent(n) \neq \topnode \\
-&\Rightarrow \FS(\parent(n)) \in \setd. 
-\end{align*}
+\[ \forall n\in\setn: \FS(n) \neq \empt \Rightarrow \FS(\parent(n)) \in \setd \]
+where $\parent(n)$ is defined.
 \end{mydef}

### 2016-10-12 p2/axioms.tex
Starting with the definition of domains

@@
 $\emptyseq$ denotes its unit element, the empty sequence,
-which by definition leaves all filesystems unchanged.
+which is defined on all filesystems and by definition leaves all filesystems unchanged.
+\end{mydef}
+
+\begin{mydef}[$\Dom{S}$ and $\Img{S}$]
+For a sequence of commands $S$, $\Dom{S}$ is the domain of $S$, which is the set of filesystems $S$ is defined on,
+that is, which it does not break.
+
+We write $\Img{S}$ to denote the image of the domain of the sequence $X$.
 \end{mydef}
@@
 on any filesystem $A$ does not break:
-$\forall \FS: A\FS\neq\fsbroken\Rightarrow A\aFS=B\aFS$.
+$\forall \FS\in\Dom{A}: A\aFS=B\aFS$.
 % old inference rule: $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
-We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\eqext T$.
+We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\cc T$.
 % preorder: reflexive and transitive

### 2016-10-12 p2/works-inverse.tex
Introduction of partial functions
Starting with the definition of domains

@@
 to denote such sets for brevity.
-We will use $A\cc\seqset{B}$ to denote the set of sequences $\{A\cc B|B\in\seqset{B}\}$.
-\end{mydef}
-
-\begin{mydef}[$\Dom{X}$ and $\Img{X}$]
-$\Dom{X}$ is the domain of $X$.
-For a sequence of commands $A$, $\Dom{A}$ is the set of filesystems $A$ does not break.
-For a set of sequences $\seqset{A}$, $\Dom{\seqset{A}}$ is the set of filesystems no $A\in\seqset{A}$ breaks.
-We write $\Img{X}$ to denote the image of the domain of the sequence $X$.
+We will use $A\cc\seqset{B}$ to denote the set of sequences $\{A\cc B|B\in\seqset{B}\}$,
+and $\Dom{\sqs{A}}$ to denote $\bigcap_{A\in\sqs{A}} \Dom{A}$.
 \end{mydef}
@@
 
+% TODO Commands/sequences are in fact partial (one-to-one) functions, and/or partial bijections. See
+% https://en.wikipedia.org/wiki/Inverse_semigroup#Origins
+% https://en.wikipedia.org/wiki/Symmetric_inverse_semigroup
+% https://en.wikipedia.org/wiki/Partial_function
+
 \begin{mydef}[Inverse commands and sequences]

### 2016-10-15 p2/axioms.tex
Improved text

@@
 \begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
-We use ``$\cc$'' to concatenate commands to form a sequence, or concatenate sequences to form a longer sequence,
+We use ``$\cc$'' to combine commands to form a sequence, or combine sequences to form a longer sequence,
 with the meaning that the command on the left is applied first:
 \[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
-For example, we will write
-$S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
-% monoid, but not free monoid
-% monoid: semigroup with identity element
-% Sequences of commands form a free semigroup
+% For example, we will write
+% $S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
+%% monoid, but not free monoid
+%% monoid: semigroup with identity element
+%% Sequences of commands form a free semigroup
 Sequences of commands form a monoid, and, as usual,
@@
 \begin{mydef}[$\Dom{S}$ and $\Img{S}$]
-For a sequence of commands $S$, $\Dom{S}$ is the domain of $S$, which is the set of filesystems $S$ is defined on,
-that is, which it does not break.
+For a sequence of commands $S$, $\Dom{S}$ is the domain of $S$,
+which is the set of filesystems $S$
+(that is, the commands it contains in the given order)
+does not break.
 
@@
 (which echo the ones defined in \cite{NREC})
-allow us to investigate sequences independently of filesystems.
-In the definitions, $A,B,S,T$ stand for arbitrary sequences of commands.
+allow us to investigate sequences of commands independently of filesystems.
+In the definitions, $A,B,S,T$ stand for arbitrary sequences.
 
@@
 
-It is easy to see that equivalence holds on the level of filesystems:
+It is easy to see that this equivalence holds on the level of filesystems:
 
@@
 If $\forall \FS: A\aFS=B\aFS$ then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
-For the reverse statement we assume that $A\eqext B$ and $B\eqext A$.
+For the reverse statement we know $A\eqext B$ and $B\eqext A$.
 $B\eqext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
-Therefore, for every $\FS$ either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
+Therefore, for every filesystem $\FS$ either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
 in which case $B\aFS=\fsbroken$ must be true, and therefore $A\aFS=B\aFS$ still holds.
@@
 during synchronization, and what commands will never be compatible.
-Below we list a number of statements derived using this method.
+Below we list a number of statements derived using this method,
+which are in fact lemmas that can be derived from our definitions of filesystems and of commands.
 
@@
 A command is an assertion command if
-for every filesystem it either breaks it or leaves it in the same state.
+it leaves every filesystem in the same state
+where it is defined.
 In other words, assertion commands have the same input and output type,
@@
 Two different commands that are not assertion commands are independent iff the nodes they change are incomparable:
-\[ \cxynv\indep\czwmv \Leftrightarrow n\unrel m \]
+\[ \cxynv\indep\czwmv \Longleftrightarrow n\unrel m \]
 if $\cxynv\neq\czwmv$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
@@
 \begin{proof}
-This is easy to show based on the output of the software that investigates the behavior of command pairs.
+This is easy to show based on the output of the program that investigates the behavior of command pairs.
 However, this proposition can also be derived from the \namecrefs{ax_separate_commute} already listed
@@
 from \cref{ax_separate_commute,ax_separate_nobreaks} we know that
-if $n\unrel m$, then $\cxynv$ and $\czwmv$ must necessarily be independent, and therefore
-$ \cxynv\nindep\czwmv \wedge n\unrel m $ cannot be the case.
+if $n\unrel m$, then $\cxynv$ and $\czwmv$ must necessarily be independent.
 
-Next, we prove that
-\[ \cxynv\indep\czwmv \wedge n\nunrel m \] is also impossible as it would lead to contradiction.
+We prove the second step by contradiction.
+We assume that both $\cxynv\indep\czwmv$ and $n\nunrel m$,
+and show that it leads to contradiction.
 As $n\nunrel m$
@@
 and they could not be independent.
-The commands are not assertion commands, and so from \cref{ax_same_singlec}
+The commands are not assertion commands, so from \cref{ax_same_singlec}
 we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $y=w$.
-Therefore $[x]=[y]=[z]=[w]$ which is only possible if both commands are $\cff$ and have the same
-output value. This, however, contradicts our assumption that they are different.
+Therefore $[x]=[y]=[z]=[w]$ which with $y=w$ contradicts our assumption that the commands are different.
 

### 2016-10-15 p2/def-filesystem.tex
Starting with the definition of domains
Improved text

@@
 are both directories, or are both $\empt$.
-% TODO needed? v
-In other words, if $\setf$ is the set of file values and $\setd$ is the set of directories, then
-with $\{\empt\}$ they form a partition of $\setv$:
-\[ \setv/{\typeeq} = \{\setd,\setf,\{\empt\}\}. \]
+% In other words, if $\setf$ is the set of file values and $\setd$ is the set of directories, then
+% with $\{\empt\}$ they form a partition of $\setv$:
+% \[ \setv/{\typeeq} = \{\setd,\setf,\{\empt\}\}. \]
 \end{mydef}
 
-As usual, we write $[v]$ for the equivalence class of $v$, which is its type.
-We also regard all file contents including all metadata to be included in the values in $\setf$.
+As usual, we write $[v]$ for the equivalence class of $v$, which represents its type.
+We also consider metadata to be part of the values in $\setv$.
 
@@
 \begin{mydef}[Tree property]
-\[ \forall n\in\setn: \FS(n) \neq \empt \Rightarrow \FS(\parent(n)) \in \setd \]
-where $\parent(n)$ is defined.
+\[ \forall n\in\setn, \FS\in\setfs: \FS(n) \neq \empt \Longrightarrow \FS(\parent(n)) \in \setd \]
+where $\parent(n)$ is defined, and where $\setd\subset\setv$ is the set of directories.
 \end{mydef}
@@
 and $n$, $m$ and $o$ are nodes in $\setn$.
-We will write $\valf$ for an arbitrary element in $\setf$.
+We write $\valf$ for an arbitrary file value. % element in $\setf$.

### 2016-10-15 p2/rec-intro.tex
Improved text

@@
 So that we can formalize statements needed to prove this,
-let us introduce two relations that describe under what conditions
+let us introduce relations that describe under what conditions
 sequences of commands work, that is, do not break a filesystem.

### 2016-10-15 p2/works-inverse.tex
Improved text

@@
 As we will frequently refer to sets of fequences,
-we will use calligraphic letters (e.g. $\seqset{A, B, C}$ and $\seqset{S}$)
+we will use calligraphic letters (e.g. $\sqs{A}$, $\sqs{B}$, $\sqs{C}$ and $\seqset{S}$)
 to denote such sets for brevity.
@@
 As a special case, we write $\worksmnil{\sqs{A}}$ if we know that there is a filesystem
-all sequences in $\sqs{A}$ work on,
-and we apply these relations to sequences directly:
+all sequences in $\sqs{A}$ work on.
+We also apply these relations to sequences directly:
 $\worksm{A}{B}$ with the meaning $\worksm{\{A\}}{\{B\}}$.
@@
 Let $\alpha=\cxynv$ and $\beta=\czwmv$.
-%% TODO by contradiction
-We proceed in an indirect way and
+We prove the proposition by contradiction and
 assume that there is a filesystem $\FS$ for which
@@
 $\czwmv$ that breaks it.
-Applying a command can only result in a broken filesystem in three cases.
-First, if the filesystem was already broken, which cannot be the case here.
-Second, if the input type does not match the filesystem,
+Applying a command can only result in a broken filesystem in two cases.
+First, if the input type does not match the filesystem,
 but we know $[\FS(m)]=[w]$ and so
 $[(\cxynv\aFS)(m)]=[w]$ as based on \cref{incomparable_is_independent}, $n\neq m$.
-Third, if the new filesystem violates the tree property.
+Second, if the new filesystem violates the tree property.
 This again cannot be the case because we also know that $n\unrel m$
-and the tree property only depends on the types of the parent and children of $m$,
+and the tree property only depends on the types of values at the parent and children of $m$,
 which therefore cannot be changed by $\cxynv$.
@@
 
-From \cref{incomparable_is_independent,ax_separate_commute} we know that
+From \cref{def_indep} we know that
 the commands in $S$ and $T$ pairwise commute, and so any sequence
@@
 This result is similar to \cref{equiv_simple_same_commands} and
-%% TODO by contradiction
-is easily shown using an indirect proof: if $[x]\neq [z]$, then there is no filesystem that
+is easily shown using a proof by contradiction: if $[x]\neq [z]$, then there is no filesystem that
 either $\cxynv$ or $\czwnv$ would not break, 
@@
 \bigskip
-
-%% TODO https://en.wikipedia.org/wiki/Equivalence_class
 
@@
 
+% TODO repeated
 As whether a sequence of commands breaks a filesystem does not depend on the output values
@@
 
+% TODO partially bijective (?)
 \begin{mylem}\label{repr_comm_inject}

### 2016-10-15 p2/rec-intro.tex
Rewrote proof for new notation

@@
 So that we can formalize statements needed to prove this,
-let us introduce relations that describe under what conditions
+let us introduce partial orders that describe under what conditions
 sequences of commands work, that is, do not break a filesystem.

### 2016-10-15 p2/works-inverse.tex
Rewrote proof for new notation

@@
 As we will frequently refer to sets of fequences,
-we will use calligraphic letters (e.g. $\sqs{A}$, $\sqs{B}$, $\sqs{C}$ and $\seqset{S}$)
+we will use calligraphic letters (e.g. $\sqs{A}$, $\sqs{B}$, $\sqs{C}$ and $\sqs{S}$)
 to denote such sets for brevity.
-We will use $A\cc\seqset{B}$ to denote the set of sequences $\{A\cc B|B\in\seqset{B}\}$,
+We will use $A\cc\sqs{B}$ to denote the set of sequences $\{A\cc B|B\in\sqs{B}\}$,
 and $\Dom{\sqs{A}}$ to denote $\bigcap_{A\in\sqs{A}} \Dom{A}$.
 \end{mydef}
+
+% works operators
+% ---------------
 
@@
 
+In a sense, $A\worksmeqsign B$ is a weaker counterpart of $A\eqext B$, as the former
+only requires that $B$ works where $A$ works, where the latter also requires
+that their effect is the same.
 It is easy to see that the following corollaries are true:
@@
 $\worksmeqsign$ can be chained:
-if $\seqset{B'}\subseteq\seqset{B}$, then
+if $\sqs{B'}\subseteq\sqs{B}$, then
 $\worksm{\sqs{A}}{\sqs{B}} \wedge \worksm{\sqs{B'}}{\sqs{C}} \Rightarrow \worksm{\sqs{A}}{\sqs{B}\cup\sqs{C}}$.
@@
 
+% Type equivalence classes
+% ------------------------
+
 \noindent
-We know that whether commands break a filesystem depends solely on their input and output
-types and the node, but not their actual output value.
-To represent this, we introduce an equivalence relation between filesystems, commands
-and sequences of commands.
-%% TODO extending it!
-\begin{mydef}[Equivalence by type: $\typeeq$]
+For the proof of the correctness of the reconciliation algorithm,
+we will also need a way of moving parts of sequences between the two
+sides of the $\worksmeqsign$ relation.
+We can do this based on the observation that commands are bijections
+if we only distinguish between types in our objects.
+To formalise this, we extend type equality ($\typeeq$)
+to filesystems, commands and sequences of commands.
+\begin{mydef}[Equivalence by type, extended: $\typeeq$]
 $ $ % otherwise first list element starts on same line
 \begin{itemize}
-\item For two filesystems $\FS\typeeq\GS$ iff they are both broken, or they share the same nodes $\setn$,
+\item For two filesystems $\FS\typeeq\GS$ iff they share the same nodes $\setn$,
 and for all $n\in\setn$, $\FS(n) \typeeq \GS(n)$.
-\item For two commands $\cxynv\typeeq\czwnv$ iff 
-$x\typeeq z$ and $y\typeeq w$ and $n=m$.
+\item For two commands $\cxynv\typeeq\czwmv$ iff 
+$x\typeeq z$ and $y\typeeq w$
+(that is, $[x]=[z]$ and $[y]=[w]$)
+and $n=m$.
 \item For two sequences of commands $\emptyseq\typeeq\emptyseq$, and
@@
 \begin{mydef}[$\T$]
-We use $\T$ and write $X\T$ to denote the canonical mapping of 
+We use $\T$ and write $a\T$ to denote the canonical mapping of 
 values, filesystems, commands and sequences to the
@@
 \item For values, $\vald\T=\vald$, $\valf\T=\fil$ and $\empt\T=\empt$.
-\item For filesystems, $\fsbroken\T=\fsbroken$ and in other cases $\FS\T$ is defined by $\FS\T(n) = \FS(n)\T$.
+\item For filesystems, $\FS\T$ is defined by $\FS\T(n) = \FS(n)\T$.
 \item For commands, $\cbrk\T=\cbrk$ and $\cxynv\T = \cTxynv$.
 \item For sequences of commands, $\emptyseq\T=\emptyseq$, and if $S'=\alpha\cc S$, then $S'\T=\alpha\T\cc S\T$.
-\item Finally we extend $\T$ to sets of sequences: $\seqset{A}\T = \{S\T | S\in\seqset{A}\}$.
+\item Finally we extend $\T$ to sets of sequences: $\sqs{A}\T = \{S\T | S\in\sqs{A}\}$.
 \end{itemize}
@@
 
-It is easy to see that for all objects where it is defined, $X\T\typeeq X$.
+It is easy to see that for all objects where it is defined, $a\T\typeeq a$.
 % $|\setf|$ is also $1$.
@@
 
-% TODO repeated
-As whether a sequence of commands breaks a filesystem does not depend on the output values
-of the commands, only the input and output types, we know that
+As the types of values determine whether a command breaks a filesystem,
+we know $\Dom{A}=\Dom{A\T}$ and therefore $\Dom{\sqs{A}}=\Dom{\sqs{A}\T}$.
+From this it follows that
+
 \begin{mycor}\label{repr_works_is_same}
 \begin{gather*}
-\works{\seqset{A}} \Leftrightarrow \works{\seqset{A}\T} \\
-\worksc{\seqset{A}}{\seqset{B}} \Leftrightarrow \worksc{\seqset{A}\T}{\seqset{B}\T}.
+\worksmnil{\sqs{A}} \Longleftrightarrow \worksmnil{\sqs{A}\T} \\
+\worksm{\sqs{A}}{\sqs{B}} \Longleftrightarrow \worksm{\sqs{A}\T}{\sqs{B}\T}.
 \end{gather*}
@@
 
+% Inverse commands
+% ----------------
+
 We are now ready to define the inverse of representative commands $\alpha\T$
 which allows us to move parts of sequences between the
-condition and consequence parts of $\workssign$.
+two sides of $\worksmeqsign$.
 This is based on the following observation.
 
-% TODO partially bijective (?)
 \begin{mylem}\label{repr_comm_inject}
-Representative commands $\alpha\T$ are injections over representative filesystems ($\FS\T$)
-except for the cases where they break a filesystem, that is,
+Representative commands $\alpha\T$ are partial bijections over representative filesystems ($\FS\T$).
+Because partial functions are trivially surjective when restricted to their images, this is
+equivalent to saying that representative functions are injective except for cases
+where they break a filesystem (they are not defined):
 \[ \forall\FS,\GS,\alpha: \FS\T\neq\GS\T \wedge \alpha\T(\FS\T)\neq\fsbroken \Longrightarrow \alpha\T(\FS\T) \neq \alpha\T(\GS\T). \]
@@
 
-% TODO We introduced BREAK to deal with cases where commands
-% are in effect not defined. Now we need to undo this 
-% to see that repr commands are bijective.
-
-% TODO Commands/sequences are in fact partial (one-to-one) functions, and/or partial bijections. See
+% See
 % https://en.wikipedia.org/wiki/Inverse_semigroup#Origins
@@
 \begin{mydef}[Inverse commands and sequences]
-If based on \cref{repr_comm_inject}
-we regard the representative command $\alpha\T$ a bijective function whose
-domain is the subset of representative filesystems $\{\FS\T | \alpha\aFS\neq\fsbroken\}$,
-then we can define the inverse of $\alpha\T$
-for which we write $\alpha\T^{-1}$.
-For any $\GS\T$ outside the image of the domain of $\alpha\T$ we define $\alpha\T^{-1}(\GS\T)$ to be $\fsbroken$.
+We write $\alpha\T^{-1}$ for
+the inverse of the representative command (partial bijection) $\alpha\T$.
 
@@
 \end{mydef}
+Per definition, for any filesystem $\FS\T$ outside the image of $\alpha\T$, the inverse $\alpha\T^{-1}$ is undefined.
 
-%% TODO
-% Do we need <[x],[y],n>-1 = <[y],[x],n> ?
-% Do we need to prove if a filesystem is not in the image, then a-1 will break it?
 \begin{mylem}
@@
 \[ \cTxynv^{-1} = \cTyxnv. \]
+TODO needed? -maybe for \cref{negneg_is_typeeq}
 \end{mylem}
-TODO needed? -maybe for \cref{negneg_is_typeeq}
 
@@
 
-For brevity, in the following lemma we use $B$, $B'$, $\seqset{A}$ and $\seqset{C}$ to denote
+For brevity, in the following lemma we use $B$, $B'$, $\sqs{A}$ and $\sqs{C}$ to denote
 representative sequences and sets.
 
+\newcommand{\ia}{\sqs{A}}
+\newcommand{\ic}{\sqs{C}}
+\newcommand{\ibi}{B^{-1}}
+
 \begin{mylem}\label{r_invmove}
-A common initial segment of a set of \emph{representative} sequences can be moved to the other side of $\worksmeqsign$ by inverting it:
+A common initial segment of a set of \emph{representative} sequences can be moved 
+to the other side of $\worksmeqsign$ by inverting it:
 \begin{gather*}
-\worksm{\seqset{C}}{B\cc \seqset{A}}
-\ \Longleftrightarrow \ \worksm{B^{-1}\cc \seqset{C}}{\seqset{A}} 
-\ \wedge \  \worksm{\seqset{C}}{\{B\}}
+\worksm{\ia}{B\cc\ic}
+\ \Longleftrightarrow \ \worksm{\ibi\cc\ia}{\ic} 
+\ \wedge \  \worksm{\ia}{\{B\}}
 \end{gather*}
@@
 \begin{proof}
-% TODO Rewrite for equivalence, and swap A and C.
 % This result is quite expected as we're mapping a subset statement using a bijection,
@@
 
-The proof for both propositions is illustrated by \cref{fig_invmove}.
+The proof is illustrated by \cref{fig_invmove}.
 
@@
 
-Unless $\works{\seqset{C}}$, both propositions are trivially true. Otherwise,
-for the first proposition
-we know $\works{B\cc\seqset{A}}$, which implies that $\Dom{\seqset{A}}$ intersects with $\Img{B}$ 
-as otherwise $B\cc\seqset{A}$ would break all filesystems.
+Unless $\worksmnil{\ia}$, the propositions is trivially true. Otherwise,
+for the left-to-right part of the proposition,
+we know $\worksmnil{B\cc\ic}$, which implies that $\Dom{\ic}$ intersects with $\Img{B}$ 
+as otherwise $B\cc\ic$ would break all filesystems.
 As the (representative) $B$ is a bijection between its domain and image,
-we can use $B^{-1}$ to map this intersection back
-onto the domain of $B$ and get $\Dom{B\cc\seqset{A}}$.
-As $\worksc{B\cc \seqset{A}}{\seqset{C}}$, 
-we know that $\Dom{\seqset{C}} \subseteq \Dom{B\cc\seqset{A}}$.
+we can use $\ibi$ to map this intersection back
+onto the domain of $B$ and get $\Dom{B\cc\ic}$.
+As $\worksm{\ia}{B\cc\ic}$, 
+we also know that $\Dom{\ia} \subseteq \Dom{B\cc\ic}$.
 We now use $B$ to map both sides of this statement, which yields
-$\Dom{B^{-1}\cc \seqset{C}} \subseteq \Dom{B^{-1}\cc B\cc\seqset{A}}$,
-but the latter is a subseteq of $\Dom{\seqset{A}}$,
-and so $\Dom{B^{-1}\cc \seqset{C}} \subseteq \Dom{\seqset{A}}$,
-from which $\worksc{\seqset{A}}{B^{-1}\cc \seqset{C}}$.
+$\Dom{B^{-1}\cc\ia} \subseteq \Dom{\ibi\cc B\cc\ic}$,
+but the latter is a subset of $\Dom{\ic}$,
+and so $\Dom{\ibi\cc\ia} \subseteq \Dom{\ic}$,
+which is the same as $\worksm{\ibi\cc\ia}{\ic}$.
 
-For the second proposition, 
-from $\worksc{B}{\seqset{C}}$ we know $\Dom{\seqset{C}} \subseteq \Dom{B}$.
-Therefore we can project the whole of $\Dom{\seqset{C}}$ using the bijective representative sequence $B$
-to get $\Dom{B^{-1}\cc\seqset{C}}$, and as $\worksc{\seqset{A}}{B^{-1}\cc \seqset{C}}$
+For the right-to-left part,
+from $\worksm{\ia}{B}$ we know $\Dom{\ia} \subseteq \Dom{B}$.
+Therefore we can project the whole of $\Dom{\ia}$ using the bijective representative sequence $B$
+to get $\Dom{\ibi\cc\ia}$, and as $\worksm{\ibi\cc\ia}{\ic}$
 we know
-$\Dom{B^{-1}\cc\seqset{C}} \subseteq \Dom{\seqset{A}}$.
-We use $B^{-1}$ to project both sides of this statement to get
-$\Dom{B\cc B^{-1}\cc\seqset{C}} \subseteq \Dom{B\cc\seqset{A}}$.
-But we also know that $\Dom{B\cc B^{-1}\cc\seqset{C}} = \Dom{\seqset{C}}$
-as $\Dom{\seqset{C}} \subseteq \Dom{B}$,
-and so $\Dom{\seqset{C}} \subseteq \Dom{B\cc\seqset{A}}$
-from which $\worksc{B\cc \seqset{A}}{\seqset{C}}$.
+$\Dom{\ibi\cc\ia} \subseteq \Dom{\ic}$.
+We use $\ibi$ to project both sides of this statement to get
+$\Dom{B\cc\ibi\cc\ia} \subseteq \Dom{B\cc\ic}$.
+But we also know that $\Dom{B\cc\ibi\cc\ia} = \Dom{\ia}$
+as $\Dom{\ia} \subseteq \Dom{B}$,
+and so $\Dom{\ia} \subseteq \Dom{B\cc\ic}$ which is the same as
+$\worksm{\ia}{B\cc\ic}$.
 \end{proof}
@@
 continues to work under the same conditions:
-\[ \worksc{A\cc B}{\seqset{S}} \wedge \worksc{A\cc C}{\seqset{S}} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{\seqset{S}} \]
+\[ \worksc{A\cc B}{\sqs{S}} \wedge \worksc{A\cc C}{\sqs{S}} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{\sqs{S}} \]
 \end{mylem}
@@
 Based on \cref{repr_works_is_same} we have
-$\worksc{A\T\cc B\T}{\seqset{S\T}}$ and $\worksc{A\T\cc C\T}{\seqset{S\T}}$,
+$\worksc{A\T\cc B\T}{\sqs{S\T}}$ and $\worksc{A\T\cc C\T}{\sqs{S\T}}$,
 and from \cref{r_invmove} we know
-$\worksc{B\T}{{A\T}^{-1}\cc \seqset{S\T}}$ and $\worksc{C\T}{{A\T}^{-1}\cc \seqset{S\T}}$.
+$\worksc{B\T}{{A\T}^{-1}\cc \sqs{S\T}}$ and $\worksc{C\T}{{A\T}^{-1}\cc \sqs{S\T}}$.
 Using \cref{combine_independent_sequences} we get
@@
 we get
-$\worksc{B\T\cc C\T}{{A\T}^{-1}\cc \seqset{S\T}}$.
+$\worksc{B\T\cc C\T}{{A\T}^{-1}\cc \sqs{S\T}}$.
 
-From $\worksc{A\cc B}{\seqset{S}}$ we also know $\worksc{A}{\seqset{S}}$ and $\worksc{A\T}{\seqset{S\T}}$.
-We can combine this and $\worksc{B\T\cc C\T}{{A\T}^{-1}\cc \seqset{S\T}}$ using
+From $\worksc{A\cc B}{\sqs{S}}$ we also know $\worksc{A}{\sqs{S}}$ and $\worksc{A\T}{\sqs{S\T}}$.
+We can combine this and $\worksc{B\T\cc C\T}{{A\T}^{-1}\cc \sqs{S\T}}$ using
 the second proposition of \cref{r_invmove} to get
-$\worksc{A\T\cc B\T\cc C\T}{\seqset{S\T}}$, and from \cref{repr_works_is_same} we know
-$\worksc{A\cc B\cc C}{\seqset{S}}$.
+$\worksc{A\T\cc B\T\cc C\T}{\sqs{S\T}}$, and from \cref{repr_works_is_same} we know
+$\worksc{A\cc B\cc C}{\sqs{S}}$.
 \end{proof}

### 2016-10-15 p2/algebra.tex
Improved notation

@@
 one can also include symbols, inference rules and axioms for 
-$\works{\seqset{A}}$ and $\worksc{\seqset{A}}{\seqset{B}}$.
+$\worksmnil{\seqset{A}}$ and $\worksm{\seqset{A}}{\seqset{B}}$.
 We see proving the soundness and completeness of this extended algebra

### 2016-10-15 p2/axioms.tex
Rewrote proof for new notation
Improved notation

@@
 \section{Investigating Command Pairs}\label{section_axioms}
+
+% Sequences
+% ---------
 
@@
 %% Sequences of commands form a free semigroup
-Sequences of commands form a monoid, and, as usual,
+We write $\sets$ for the set of sequences of commands.
+They form a monoid, and, as usual,
 $\emptyseq$ denotes its unit element, the empty sequence,
@@
 % preorder: reflexive and transitive
+% patial order: reflexive, transitive and antisymmetric (aRb & bRa => a=b) TODO
 In other words, $\eqext$ is a preorder, and also a precongruence.
@@
 which are in fact lemmas that can be derived from our definitions of filesystems and of commands.
+
+% TODO Rewrite script for new notation
 
@@
 for all $\alpha$ in $A$ and all $\beta$ in $B$, $\alpha\indep\beta$.
+We also write $\alpha\indep B$ iff $\forall \beta\in B:\alpha\indep\beta$.
 \end{mydef}
@@
 we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $y=w$.
+% TODO Does this depend on |Vd|=1?
 Therefore $[x]=[y]=[z]=[w]$ which with $y=w$ contradicts our assumption that the commands are different.

### 2016-10-15 p2/conclusion.tex
Improved notation

@@
 the demonstrated properties of minimal sequences of commands
-and conditional operation of sequences ($\workssign$)
+and conditional operation of sequences ($\worksmsign$) % TODO
 may also contribute to future research into algebraic structures

### 2016-10-15 p2/rec-sound.tex
Minor updates
Improved notation

--- 2015-12-25 2015/rec-sound.tex
@@
 \begin{myth}
-If $A, B$ are simple, then $\worksc{B\cc \reca}{A,B}$,
+If $A, B$ are simple, then $\worksmbb{A,B}{B\cc \reca}$,
 where, to restate \cref{def:reconciliation},
-% { % scope
-% \renewcommand{\themydef}{\ref{def:reconciliation}}
-% \begin{mydef}
-\begin{align*}
-\reca = \{\alpha|{}& \\
-& \alpha\in A\setminus B \\
-& \wedge \\
-& \forall \beta\in B\setminus A: \alpha\indep\beta\\
-\}. &
-\end{align*}
-% \end{mydef}
-% } % scope
+\[ \reca = \{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp \}. \]
 \end{myth}
 
-This is trivial unless $\works{A,B}$, so we assume that it is true.
+This is trivial unless $\worksmnilb{A,B}$, so we assume that it is true.
 Let us first investigate the part of $A$ and $B$ that is excluded from
@@
 \begin{mylem}\label{can_move_intersection}
-Let $A$ and $B$ be two simple sequences so that $\works{A, B}$.
+Let $A$ and $B$ be two simple sequences so that $\worksmnilb{A, B}$.
 Then their intersection, in some suitable order, also works on any filesystem
 either of them works on:
-$\worksc{\acbnp}{A}$, and, by symmetry,
-$\worksc{\acbnp}{B}$.
+$\worksm{A}{\acbnp}$, and, by symmetry,
+$\worksm{B}{\acbnp}$.
 \end{mylem}
@@
 \end{gather*}
-As $A$ is simple and $\works{A}$, from 
+As $A$ is simple and $\worksmnilb{A}$, from 
 \cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
@@
 
-As $\works{A,B}$ and so $\works{A,B'}$, 
+As $\worksmnilb{A,B}$ and so $\worksmnilb{A,B'}$, 
 from \cref{worksinputmatch}
-we know that $Q=Z$.
+we know that $[q]=[z]$.
 
-Going back to the construction and destruction pairs we see that the output type of the first command
-is always the same, and it is either $\cchard$ or $\ccharb$ depending on the relationship between $n$ and $m$.
-Therefore $R=W$ and $\cqrmv=\czwmv$
-as $|\setd|=|\setb|=1$. 
+Going back to the construction and destruction pairs we see that the output value of the first command
+is either $\vald$ or $\empt$ and is determined by the relationship between $n$ and $m$.
+Therefore $r=w$ and $\cqrmv=\czwmv$.
 If $B$ originally had a command on $m$,
@@
 If $B$ had no command on $m$,
-this is a contradiction because the command on $m$ in $B'$ is an assertion command, so $Z=Q=R=W$, 
+this is a contradiction because the command on $m$ in $B'$ is an assertion command, so $[z]=[q]=[r]=[w]$, 
 but $A$ contained no assertion commands.
@@
 from \cref{worksextpostfix} we know that
-$\worksc{\acbnp}{A}$ and by symmetry $\worksc{\acbnp}{B}$.
+$\worksm{A}{\acbnp}$ and by symmetry $\worksm{B}{\acbnp}$.
 \end{proof}
@@
 \noindent
-We would like to prove that $\worksc{B\cc \reca}{A,B}$.
+We would like to prove that $\worksmbb{A,B}{B\cc \reca}$.
 From the above we know that we can move commands in $\acbnp$
 to the beginning of $B$ and so this is equivalent to
-\[ \worksc{\acb\cc \bma\cc \reca}{A,B}. \]
+\[ \worksmbb{A,B}{\acb\cc \bma\cc \reca}. \]
 As we already know that $\reca\indep\bma$
-and that $\worksc{\acb\cc \bma}{A,B}$
-(as $\worksc{B}{A,B}$),
+and that $\worksmbb{A,B}{\acb\cc \bma}$
+(as $\worksmbb{A,B}{B}$),
 we can prove our theorem based on \cref{indep_prefix_combine}
 if we can prove that
-\[ \worksc{\acb\cc \reca}{A,B}. \]
-Using \cref{r_invmove} we can rephrase this as
-\[ \worksc{\reca}{\acbi\cc A,\acbi\cc B}. \]
+\[ \worksmbb{A,B}{\acb\cc \reca}. \]
+Based on \cref{r_invmove} and \cref{repr_works_is_same}, and because
+we already know that $\worksmbb{A,B}{\acbnp}$,
+this is equivalent to
+\[ \worksmbb{\acbi\cc A\T,\acbi\cc B\T}{\reca\T}. \]
 
@@
 \item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
-\item $\worksc{\amb, \bma}{\acbi\cc A,\acbi\cc B}$ 
+\item $\worksmbb{\acbi\cc A,\acbi\cc B}{\amb, \bma}$ 
 because of \cref{r_invmove}
-as $\worksc{A,B}{A,B}$,
+as $\worksmbb{A,B}{A,B}$,
 and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
@@
    \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
-   \item[\condWork] $\worksc{S,T}{\seqset{C}}$ for some set of sequences $\seqset{C}$,
+   \item[\condWork] $\worksmxb{\sqs{C}}{S,T}$ for some set of sequences $\sqs{C}$,
    \end{itemize}
 then
-\[ \worksc{S^*}{\seqset{C}}. \]
+\[ \worksmxb{\sqs{C}}{S^*}. \]
 \end{mylem}
@@
 \begin{proof}
-This is trivial unless $\works{\seqset{C}}$, so we will assume that it is true
-and therefore $\works{S,T}$.
+This is trivial unless $\worksmnil{\sqs{C}}$, so we will assume that it is true
+and therefore $\worksmnilb{S,T}$.
 
@@
 If so, then 
-$\worksc{S^*}{\seqset{C}}$ 
+$\worksmxb{\sqs{C}}{S^*}$ 
 based on \cref{worksextpostfix}
-as $\worksc{S'}{\seqset{C}}$ and $S'=S^*\cc S_0$ 
+as $\worksmxb{\sqs{C}}{S'}$ and $S'=S^*\cc S_0$ 
 where $S_0$ contains the remaining (conflicting) commands.
@@
 and the preceding unmarked command be $\czwmv$.
-As $S$ is simple and $\works{S}$, from 
+As $S$ is simple and $\worksmnilb{S}$, from 
 \cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}

### 2016-10-15 p2/upd-def.tex
New notation for commands
Improved notation

--- 2016-01-04 ii/upd-def.tex
@@
 sufficient, as there are commands available for any input and output value. 
-Specifically, if at node $n$, $\FS(n)=\valvx$ and $\FS_A(n)=\valvy\neq \valvx$, then we add the command $\cxyaa{n}{\valvy}$ to $A$
-where $\valvx\in\setvx{X}$ and $\valvy\in\setvx{Y}$.
+Specifically, if at node $n$, $\FS(n)=x$ and $\FS_A(n)=y\neq x$, then we add the command $\cxyaa{n}$ to $A$.
 
@@
 
-\begin{mydef}[Minimal set or sequence]
+\begin{mydef}[Minimal sets or sequences, $\setsmin$]
 A sequence or set of commands is minimal if it contains at most one command on each node.
+We write $\setsmin$ for the set of minimal sequences.
 \end{mydef}
 
-\begin{mydef}[Simple set or sequence]
+\begin{mydef}[Simple sets or sequences, $\setssmp$]
 A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
+We write $\setssmp$ for the set of simple sequences.
 \end{mydef}

### 2016-10-15 p2/works-inverse.tex
Improved notation

@@
 to denote such sets for brevity.
-We will use $A\cc\sqs{B}$ to denote the set of sequences $\{A\cc B|B\in\sqs{B}\}$,
+We will use $A\cc\sqs{B}$ to denote the set of sequences $\{A\cc B\whr B\in\sqs{B}\}$,
 and $\Dom{\sqs{A}}$ to denote $\bigcap_{A\in\sqs{A}} \Dom{A}$.
@@
 if $\sqs{B'}\subseteq\sqs{B}$, then
-$\worksm{\sqs{A}}{\sqs{B}} \wedge \worksm{\sqs{B'}}{\sqs{C}} \Rightarrow \worksm{\sqs{A}}{\sqs{B}\cup\sqs{C}}$.
+$\worksm{\sqs{A}}{\sqs{B}} \wedge \worksm{\sqs{B'}}{\sqs{C}} \Rightarrow \worksm{\sqs{A}}{\sqs{C}}$.
 \end{mycor}
@@
 \item For sequences of commands, $\emptyseq\T=\emptyseq$, and if $S'=\alpha\cc S$, then $S'\T=\alpha\T\cc S\T$.
-\item Finally we extend $\T$ to sets of sequences: $\sqs{A}\T = \{S\T | S\in\sqs{A}\}$.
+\item Finally we extend $\T$ to sets of sequences: $\sqs{A}\T = \{S\T \whr S\in\sqs{A}\}$.
 \end{itemize}
@@
 
-From the definitions we can clearly see that
+From the definitions we can clearly see that - TODO not used
 \begin{mycor}\label{negneg_is_typeeq}
@@
 
+We use this result to prove the following:
+
 \begin{mylem}\label{indep_prefix_combine}
@@
 continues to work under the same conditions:
-\[ \worksc{A\cc B}{\sqs{S}} \wedge \worksc{A\cc C}{\sqs{S}} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{\sqs{S}} \]
+\begin{gather*}
+ \worksmxb{\sqs{S}}{A\cc B} \,\wedge\, \worksmxb{\sqs{S}}{A\cc C} \,\wedge\, B\indep C \\
+ \Longrightarrow \worksmxb{\sqs{S}}{A\cc B\cc C}
+\end{gather*}
 \end{mylem}
@@
 Based on \cref{repr_works_is_same} we have
-$\worksc{A\T\cc B\T}{\sqs{S\T}}$ and $\worksc{A\T\cc C\T}{\sqs{S\T}}$,
+$\worksmxb{\sqs{S}\T}{A\T\cc B\T}$ and $\worksmxb{\sqs{S}\T}{A\T\cc C\T}$,
 and from \cref{r_invmove} we know
-$\worksc{B\T}{{A\T}^{-1}\cc \sqs{S\T}}$ and $\worksc{C\T}{{A\T}^{-1}\cc \sqs{S\T}}$.
+$\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{B\T}$ 
+and $\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{C\T}$.
 Using \cref{combine_independent_sequences} we get
-$\worksc{B\T\cc C\T}{B\T,C\T}$,
-and combining these using \cref{workschained}
+$\worksmbb{B\T,C\T}{B\T\cc C\T}$,
+and chaining these using \cref{workschained}
 we get
-$\worksc{B\T\cc C\T}{{A\T}^{-1}\cc \sqs{S\T}}$.
+$\worksmxb{{A\T}^{-1}\cc \sqs{S}\T}{B\T\cc C\T}$.
 
-From $\worksc{A\cc B}{\sqs{S}}$ we also know $\worksc{A}{\sqs{S}}$ and $\worksc{A\T}{\sqs{S\T}}$.
-We can combine this and $\worksc{B\T\cc C\T}{{A\T}^{-1}\cc \sqs{S\T}}$ using
-the second proposition of \cref{r_invmove} to get
-$\worksc{A\T\cc B\T\cc C\T}{\sqs{S\T}}$, and from \cref{repr_works_is_same} we know
-$\worksc{A\cc B\cc C}{\sqs{S}}$.
+From $\worksmxb{\sqs{S}}{A\cc B}$ we also know $\worksmxb{\sqs{S}}{A}$ and $\worksmxb{\sqs{S}\T}{A\T}$.
+We can combine this and $\worksmxb{{A\T}^{-1}\cc \sqs{S}\T}{B\T\cc C\T}$ using
+\cref{r_invmove} to get
+$\worksmxb{\sqs{S}\T}{A\T\cc B\T\cc C\T}$, and from \cref{repr_works_is_same} we know
+$\worksmxb{\sqs{S}}{A\cc B\cc C}$.
 \end{proof}

### 2016-10-16 p2/def-commands.tex
Starting with the definition of domains
New ordering method; hyperlinks

@@
 it is not necessary to encode the actual input value.
-For example, the behavior of two commands that differ only in what the original file contains
-that they overwrite is never going to be different.
 
@@
 we also introduce the command $\cbrk$ which is not defined anywhere,
-that is, which simply breaks every filesystem.
+that is, which breaks every filesystem.
 
@@
 are not defined everywhere:
-\[ \alpha: \setf \nrightarrow \setf \]
+\[ \alpha: \setfs \nrightarrow \setfs \]
 A command $\alpha$ is not defined on filesystems that it would break.

### 2016-10-16 p2/def-filesystem.tex
Improved notation
New ordering method; hyperlinks

@@
 and a set of possible contents or values $\setv$ as its codomain.
-\begin{mydef}[Filesystems, $\setn$, $\setv$ and $\setf$]
+\begin{mydef}[Filesystems, $\setn$, $\setv$, $\setfs$ and $\empt$]
 \[ \FS: \setn \rightarrow \setv \]
@@
 
-\begin{mydef}[$n\descendant m$]
-On $\setn$ the \emph{ancestor / descendant} relation is the
+\begin{mydef}[$\descendant$, $\descendantEq$]
+On $\setn$ the \emph{ancestor / descendant} relation $\descendant$ is the
 strict partial ordering determined by the $\parent$ function.
@@
 \begin{mydef}[Equivalence by type: $\typeeq$]
-We write $v_1\typeeq v_2$ for $v_1,v_2\in\setv$ if $v_1$ and $v_2$ are both files,
+We write $v_1\typeeq v_2$ for $v_1,v_2\in\setv$ iff $v_1$ and $v_2$ are both files,
 are both directories, or are both $\empt$.

### 2016-10-16 p2/ordering.tex
Improved notation
New ordering method; hyperlinks

@@
 
-In this section we describe an algorithm with which all possible orderings of a
+In this section we describe a method with which all possible orderings of a
 simple set of commands can be generated, but before doing so, let us consider the following lemma.
@@
 from \cref{ax_distantrel_breaks} we get $A\equiv\cbrk$ which contradicts our assumptions.
-(Note that $A$ cannot contains assertion commands.)
+(Note that $A$ cannot contain assertion commands.)
 By repeating this step we can therefore convert $A$ into $A'$ where $\cxynv$ and $\czwnnv$ are neighboring commands.
@@
 \noindent
-We can now define our algorithm to generate orders of sets of commands.
+We can now define the method to generate possible orders of sets of commands.
+What we expect is that if the commands can be applied to a filesystem
+in some order without breaking it, then the method will yield all possible orders
+in which they can be applied.
 
 \begin{mydef}[$\ordersetsign$]
-We use $\orderset{U}$ to denote the set of sequences 
-generated by the algorithm / (all possible orderings)
-from the commands in the simple-? set or sequence $U$.
+For a simple set or sequence $U\nequiv\cbrk$,
+we use $\orderset{U}$ to denote the set of sequences
+that are all permutations of the commands in $U$
+for which the following holds:
+for any two commands $\cxynv$ and $\czwmv$ in a sequence in $\orderset{U}$
+where $\cxynv$ comes earlier in the sequence than $\czwmv$,
+\begin{itemize}
+\item if $n=\parent(m)$, then $y=\vald$
+\item if $\parent(n)=m$, then $y=\empt$.
+\end{itemize}
 \end{mydef}
 
-Let $U$ be a simple set of commands
-that we know can be applied to at least one filesystem in some order without breaking it.
-Then we can split $U$ into a maximum number of disjoint subsets
-(components) so that the nodes of two commands from two different subsets are incomparable.
-These will simply be the components of the subset of the node forest that contains 
-the nodes affected by $U$.
+The principal ideas behind this algorithm are 
+\cref{ax_separate_commute}, from which we know that commands on incomparable
+nodes can be applied in any order, so we only need to focus on the order of commands
+with comparable nodes;
+\cref{connected_changes}, from which we know that if $U$ contains commands on two comparable
+nodes, then it contains commands on all nodes in between, so it is enough to specify
+the order of commands on parent and child nodes;
+and finally, \cref{ax_directchild_breaks,ax_directparent_breaks}, from which we know
+that commands on parent--child pairs must be construction or destruction pairs.
+Investigating the pairs we see that they are identified by the output value of the first command ($y$),
+and that they determine whether the command on the parent or the child must precede the other.
 
-From \cref{ax_separate_commute} we know that commands from different 
-components can be applied in any order.
-Therefore once we have ordered the commands inside the components, we generate
-all permutations of the components themselves, including the ones
-in which commands from separate components mix and overlap
-(but where the possible orders determined for commands inside the components are respected).
-
-Next, consider the ordering inside a component.
-
-This is not a problem in the case of components containing a single command only.
-(Note that a file-to-file command ($\cff$) can only appear in a component of one.)
-
-In each component that is larger than one, 
-we know that all nodes are related, and from \cref{connected_changes}
-we also know that it must contain commands on nodes in between the related nodes.
-Therefore the nodes
-form a rooted ordered tree,
-and the pairs of commands connected by the edges in the tree 
-must be construction or destruction pairs.
-(Otherwise, there would be no ordering of the component that is not equivalent to $\cbrk$
-and via \cref{ax_separate_commute} there would be no ordering of the whole set, either.)
-
-To order the commands in the component,
-select the command with the topmost node, so that there is no command
-on its parent node (if there is one). 
-If the command removes content at this node (it is of the form $\caa{X}{\ccharb}$), 
-then it must follow all other commands in the component, and
-all parent--child pairs in the whole component must be destruction pairs.
-Otherwise, the command with the topmost node needs to precede the other commands,
-and the component must be made of construction pairs.
-These follow from the patterns of construction and destruction pairs, which
-at no point can mix without causing any ordering to break all filesystems.
-
-Then move the command with the topmost node to the beginning or the end of
-the sequence we are creating out of the component,
-and recursively start the whole algorithm again on the commands in the component that remain,
-potentially splitting them into sub-components.
-The result of this process is a set of possible orders for each component,
-which are then combined into a set of possible orders for the whole set of commands.
-
-\bigskip
-
-\noindent As a specific case, we can regard a simple sequence $S$
-as a set, and use the above algorithm to generate all possible orderings
-of the commands it contains.
-\Cref{simple_reorder_equiv} is
+In \cref{simple_reorder_equiv} we offer a formal proof that $\orderset{U}$ meets our expectations.
+It is
 an important property of simple sequences: namely, that
@@
 To prove this, first we prove the following:
+
+%% TODO Define set operations on sequences?
+% \noindent As a specific case, we can regard a simple sequence $S$
+% as a set, and use the above algorithm to generate all possible orderings
+% of the commands it contains.
 
@@
 For a simple sequence $S\nequiv\cbrk$,
-\[ \orderset{S} = [S]_\equiv, \]
-where $[S]_\equiv$ denotes the set of simple sequences equivalent to $S$.
+\[ \orderset{S} = [S]_\equiv \cap \setssmp, \]
+where $[S]_\equiv \cap \setssmp$ is the set of simple sequences equivalent to $S$.
 \end{mylem}
@@
 
+TODO:
 Second, based on the algorithm we also know that $\orderset{S}$ contains

### 2016-10-16 p2/works-inverse.tex
New ordering method; hyperlinks

@@
 only requires that $B$ works where $A$ works, where the latter also requires
-that their effect is the same.
-It is easy to see that the following corollaries are true:
+that where they work, their effect is the same.
+It is easy to see that the following corollary is true:
 
@@
 
-\begin{mycor}\label{workschained}
-% An inference rule in the algebra
-$\worksmeqsign$ can be chained:
-if $\sqs{B'}\subseteq\sqs{B}$, then
-$\worksm{\sqs{A}}{\sqs{B}} \wedge \worksm{\sqs{B'}}{\sqs{C}} \Rightarrow \worksm{\sqs{A}}{\sqs{C}}$.
-\end{mycor}
-
 We also prove the following lemmas.
@@
 \begin{myax}\label{combine_independent_commands}
-The combination of independent commands works wherever the original commands work:
+The combination of independent commands works wherever both of the commands work:
 \[ \alpha\indep \beta \Rightarrow \worksm{\{\alpha, \beta\}}{\{\alpha\cc \beta\}}. \]
@@
 \begin{mylem}\label{combine_independent_sequences}
-The combination of independent sequences works wherever the original sequences work:
+The combination of independent sequences works wherever both of the sequences work:
 \[ S\indep T \Rightarrow \worksm{\{S,T\}}{\{S\cc T\}}. \]
@@
 $\worksmbb{B\T,C\T}{B\T\cc C\T}$,
-and chaining these using \cref{workschained}
+and chaining these (as $\worksmeqsign$ is transitive)
 we get

### 2016-10-17 p2/axioms.tex
New ordering method; hyperlinks
Towards a new proof

@@
 
-We write $\Img{S}$ to denote the image of the domain of the sequence $X$.
+We write $\Img{S}$ to denote the image of the domain of the sequence $S$.
 \end{mydef}
@@
 \end{proof}
+
+% Rules
+% -----
 
@@
 and the pair is not a construction pair.
+
+We can derive this from our filesystem model in the following way:
+we know if $y\neq\vald$ then the commands will break every filesystem $\FS$
+as either before or after $\czwnv$, $\FS(n)$ is not empty, and therefore
+at its parent $\nn$ there must be a directory.
+We also know if $[z]\neq[\empt]$ then the commands will again break every filesystem
+as either before or after $\cxynnv$, $\FS(\nn)$ is not a directory.
 \end{myax}
@@
 and the pair is not a destruction pair.
+
+The derivation of this \namecref{ax_directparent_breaks} is similar to that of \cref{ax_directchild_breaks}.
+We know if $y\neq\empt$ then the commands will break every filesystem $\FS$
+as either before or after $\czwnnv$, $\FS(\nn)$ is not a directory, and therefore
+every child of $\nn$ must be empty.
+We also know if $[z]\neq[\vald]$ then the commands will again break every filesystem
+as either before or after $\cxynv$, $\FS(n)$ is not empty.
 \end{myax}
@@
 \bigskip
+
+% Independent commands
+% --------------------
 

### 2016-10-17 p2/ordering.tex
Towards a new proof

@@
 
-In this section we describe a method with which all possible orderings of a
-simple set of commands can be generated, but before doing so, let us consider the following lemma.
+Let us therefore define $\ordersetsign$ which gives us all
+possible orders in which a set of commands can be applied
+to filesystems without breaking it
+provided that the commands can be applied to a fileystem in some order.
+
+\begin{mydef}[$\ordersetsign$]\label{def_orderset}
+For a simple set or sequence $U$,
+we use $\orderset{U}$ to denote the set of sequences
+that are all permutations of the commands in $U$
+for which the following holds:
+for any two commands $\cxynv$ and $\czwmv$ in a sequence in $\orderset{U}$
+where $\cxynv$ comes earlier in the sequence than $\czwmv$,
+\begin{itemize}
+\item if $n=\parent(m)$, then $y=\vald$
+\item if $\parent(n)=m$, then $y=\empt$.
+\end{itemize}
+\end{mydef}
+
+The principal ideas behind this algorithm are 
+\cref{ax_separate_commute}, from which we know that commands on incomparable
+nodes can be applied in any order, so we only need to focus on the order of commands
+with comparable nodes;
+\cref{connected_changes}, from which we know that if $U$ contains commands on two comparable
+nodes, then it contains commands on all nodes in between, so it is enough to specify
+the order of commands on parent and child nodes;
+and finally, \cref{ax_directchild_breaks,ax_directparent_breaks}, from which we know
+that commands on parent--child pairs must be construction or destruction pairs.
+Investigating the pairs we see that they are identified by the output value of the first command ($y$),
+and that they determine whether the command on the parent or the child must precede the other.
+
+In \cref{simple_reorder_equiv} we offer a formal proof that $\orderset{U}$ meets our expectations.
+It is an important property of simple sequences: namely, that
+all of their valid reorderings are equivalent,
+and all equivalent sequences are mere reorderings.
+To prove this, we will need the following results:
+
+\begin{mylem}\label{order_is_only_possible}
+For any simple sequence $S$ and its permutation $T$, 
+\[ T\not\in\orderset{S} \Longrightarrow T\equiv\cbrk. \]
+\end{mylem}
+\begin{proof}
+$T$ can only be excluded from $\orderset{S}$ if it contains commands on a node and its parent
+which violate the conditions in \cref{def_orderset},
+which, as simple sequences do not contain assertion commands,
+entails that those commands placed next to each other in the same order
+would not form a construction or destruction pair.
+
+Informally speaking,
+our proposition for simple sequences $T\nequiv\cbrk$ is equivalent to the statement that
+two commands on a node and its parent must form
+a construction or destruction pair even if they are not next to each other.
+This is true because in simple sequences
+there cannot be another command between either of the nodes involved,
+so if the commands are incompatible, no command between them can change that.
+
+% BACK_TO_THE_FS TODO
+% TODO Review any proof depending on "nothing changes FS at n until...".
+To prove our proposition formally, we reach back to our filesystem model.
+Select two commands in $T$ that do not conform to \cref{def_orderset}, $\cxynv$ and $\czwmv$,
+and split $T$ around them into three parts:
+\[ T = T_0 \cc \cxynv \cc T_1 \cc \czwmv \cc T_2 \]
+As $T$ is simple, there cannot be any commands on $n$ or $m$ in $T_1$,
+and therefore $(T_0\cc\cxynv\cc T_1)\FS(n) = y$.
+If $n=\parent(m)$, then we know $y\neq\vald$, and
+(similarly to the reasoning in \cref{ax_directchild_breaks})
+as either before or after $\czwmv$ which is not an assertion command,
+$\FS(m)\neq\empt$, the latter command will break the filesystem.
+If $\parent(n)=m$, then we know $y\neq\empt$, and
+(similarly to the reasoning in \cref{ax_directparent_breaks})
+as wither before or after $\czwmv$, $\FS(m)\neq\vald$,
+the latter command will break the filesystem.
+\end{proof}
 
@@
 
-\bigskip
-
-\noindent
-We can now define the method to generate possible orders of sets of commands.
-What we expect is that if the commands can be applied to a filesystem
-in some order without breaking it, then the method will yield all possible orders
-in which they can be applied.
-
-\begin{mydef}[$\ordersetsign$]
-For a simple set or sequence $U\nequiv\cbrk$,
-we use $\orderset{U}$ to denote the set of sequences
-that are all permutations of the commands in $U$
-for which the following holds:
-for any two commands $\cxynv$ and $\czwmv$ in a sequence in $\orderset{U}$
-where $\cxynv$ comes earlier in the sequence than $\czwmv$,
-\begin{itemize}
-\item if $n=\parent(m)$, then $y=\vald$
-\item if $\parent(n)=m$, then $y=\empt$.
-\end{itemize}
-\end{mydef}
-
-The principal ideas behind this algorithm are 
-\cref{ax_separate_commute}, from which we know that commands on incomparable
-nodes can be applied in any order, so we only need to focus on the order of commands
-with comparable nodes;
-\cref{connected_changes}, from which we know that if $U$ contains commands on two comparable
-nodes, then it contains commands on all nodes in between, so it is enough to specify
-the order of commands on parent and child nodes;
-and finally, \cref{ax_directchild_breaks,ax_directparent_breaks}, from which we know
-that commands on parent--child pairs must be construction or destruction pairs.
-Investigating the pairs we see that they are identified by the output value of the first command ($y$),
-and that they determine whether the command on the parent or the child must precede the other.
-
-In \cref{simple_reorder_equiv} we offer a formal proof that $\orderset{U}$ meets our expectations.
-It is
-an important property of simple sequences: namely, that
-all of their valid reorderings are equivalent,
-and all equivalent sequences are mere reorderings.
-To prove this, first we prove the following:
-
-%% TODO Define set operations on sequences?
-% \noindent As a specific case, we can regard a simple sequence $S$
-% as a set, and use the above algorithm to generate all possible orderings
-% of the commands it contains.
-
 \begin{mylem}\label{equiv_simple_same_commands}
@@
 \begin{proof}
+% BACK_TO_THE_FS
 We use a proof by contradiction. Let $A$ and $B$ be simple sequences
@@
 \begin{proof}
+First, we prove, by contradiction, that if a simple sequence $T\equiv S$, then $T\in\orderset{S}$.
+We assume $T\equiv S$ and $T\not\in\orderset{S}$.
+Then, from \cref{order_is_only_possible} we know $T\equiv\cbrk$ which
+is a contradiction as $T\equiv S\nequiv\cbrk$.
+
+Next, we prove that if $T\in\orderset{S}$, then $T\equiv S$.
+We proceed by induction.
+Our base cases are $\emptyseq$, where $\orderset{\emptyseq}=\{\emptyseq\}$,
+and one-long sequences, where this is trivially true.
+In our induction step we assume that $T^*\in\orderset{S^*}\Rightarrow T^*\equiv S^*$ holds
+for all sequences of length $i\geq 1$ or less.
+
+Let us consider $T\in\orderset{S}$ where $T$ and $S$ are of length $i+1$.
+We note that for any subsequence of $S$, $S_0$, which contains
+only part of the commands in $S$ but in the same order as in $S$,
+and for the corresponding subsequence of $T$, $T_0$, which
+contains the same commands but in the order they are found in $T$,
+$T_0\in\orderset{S_0}$ must hold as
+if there were no command pairs in $T$ not conforming to \cref{def_orderset},
+then there cannot be any in $T_0$.
+
+We also know that due to \cref{ax_separate_commute,incomparable_is_independent}
+$T$ can be rearranged into $T'\equiv T$ where
+$T'=T_1\cc T_2\cc \cdots \cc T_k$ and the segments $T_j$ are pairwise independent,
+and where we have the maximum number of segments possible.
+$S$ can be converted similarly into $S'$, and
+as because of \cref{equiv_simple_same_commands} $S$ and $T$ contain the same commands,
+the segments of $S'$ will contain the same commands as those of $T$.
+Let us therefore rearrange the segments of $S'$ so that the first segment
+$S_1$ would correspond to (i.e. contain the same commands as) $T_1$, the second segment $S_2$ to $T_2$,
+and so on.
+
+The segments contain commands in the same order as the full sequences.
+Therefore, from the observation abvout subsequences
+we know for all $1\leq j\leq k$, $T_j\in\orderset{S_j}$,
+and if $T'$ has at least two segments and so 
+they are shorter than $i+1$,
+from the induction hypothesis
+we also know $T_j\equiv S_j$, from which we get $T\equiv S$.
+
+We can assume $T'$ has at least two commands,
+and in the remaining case, when $T'$ has only one segment,
+we know all nodes that the commands in $T'$ apply to
+are related via $\descendant$.
+$T'$ contains the same commands as $S$, and
+from \cref{connected_changes} we see that the nodes the commands apply to therefore form a tree in $\setn$.
+We can therefore select the command on the topmost node (let it be $\cxynv$),
+and we know $T'$ contains commands on some of its child nodes.
+Let one of these be $\czwmv$.
+Now mark the command $\czwmv$ and all commands in $T'$ that are applied to nodes that are descendants of $m$.
+From \cref{ax_separate_commute} we know that all remaining commands in $T'$ (except $\cxynv$)
+commute with the marked commands; therefore we can swap them to get $T''\equiv T'$
+where marked commands are next to $\cxynv$:
+\[ T'' = T_\mathrm{unmarked\ left} \cc T_\mathrm{marked\ left} \cc \cxynv \cc T_\mathrm{marked\ right} \cc T_\mathrm{unmarked\ right}. \]
+
+TODO
+
 First, as $S$ only has at most one command on each node,
@@
 or it leaves it in the same state as $S$.
+\end{proof}
+
+%% TODO Define set operations on sequences?
+% \noindent As a specific case, we can regard a simple sequence $S$
+% as a set, and use the above algorithm to generate all possible orderings
+% of the commands it contains.
 
 TODO:
-Second, based on the algorithm we also know that $\orderset{S}$ contains
-all possible orderings of $S$ as the only ordering between commands
-it prescribes are when the commands in the reverse order would break every filesystem.
-
-If, for example, in a component or sub-component
-made up of construction pairs,
-the command on the topmost node, $\cxynv$, was not before all other commands
-in the component as prescribed by the algorithm,
-then any resulting sequence would necessarily contain
-a $\czwmv$ where $n\descendant m$, potentially followed by commands
-on incomparable nodes, and then followed by $\cxynv$.
-From \cref{ax_separate_commute} we know we can convert this sequence
-to an equivalent sequence by swapping the commands on incomparable nodes with
-$\czwmv$, which sequence would therefore have the commands on
-$m$ and $n$ next to each other. Then from \cref{ax_distantrel_breaks,ax_directparent_breaks}
-we know the sequence would break all filesystems
-as a reversed construction pair is never a valid destruction pair.
-
-We can prove that an order not generated by the algorithm
-in the case of a component made of destruction pairs breaks all filesystems
-in a similar way.
-
-Also, from \cref{ax_separate_commute} we know
-that the order between any other command pairs is not fixed in the sense
-that if one order works, so will the other.
-
-From these we know that all sequences in $\orderset{S}$
-are equivalent, and that any sequence of the same commands outside it
-necessarily breaks all filesystems.
-We also know $S\in\orderset{S}$ as $S\nequiv\cbrk$
-and therefore $T\in\orderset{S} \Rightarrow T\equiv S$.
-
-From \cref{equiv_simple_same_commands} we know that 
-if $T\equiv S$, then $T$ contains the same commands as $S$,
-from which we see
-that $T\equiv S\Rightarrow T\in\orderset{S}$.
-\end{proof}
-
-%% TODO https://en.wikipedia.org/wiki/Equivalence_class
-
 It follows from the algorithm that:
@@
 
+TODO:
 It follows from this that given a simple set,

### 2016-10-18 p2/ordering.tex
Stronger lemma about distant pairs

@@
 and all equivalent sequences are mere reorderings.
-To prove this, we will need the following results:
+To prove this, we will need the following results.
+
+\begin{mylem}\label{simple_distant_pairs}
+For any simple sequence $S\nequiv\cbrk$
+if $\cxynv\cc\czwmv$ is a subsequence of $S$ and $n=\parent(m)$ or $\parent(n)=m$,
+then $\cxynv\cc\czwmv\nequiv\cbrk$.
+\end{mylem}
+\begin{proof}
+As usual, by subsequence we mean a subset of the commands in $S$ in the same order as they are found in $S$.
+
+Informally speaking, the proposition means that
+the two commands must form a construction or destruction pair even
+if they are not next to each other.
+This is true because in simple sequences
+there cannot be another command on $n$ or $m$,
+so if the commands are incompatible, no command between them can change that.
+In fact, this \namecref{simple_distant_pairs} is the general case
+of \cref{ax_directchild_breaks,ax_directparent_breaks}.
+
+% BACK_TO_THE_FS TODO
+% TODO Review any proof depending on "nothing changes FS at n until...".
+Formally, we prove our proposition by contradiction,
+and in this version of the proof we reach back to our filesystem model.
+We assume $S\nequiv\cbrk$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
+but it contains commands that do not form a construction or destruction pair.
+Select two such commands, $\cxynv$ and $\czwmv$,
+and split $S$ around them into three parts:
+\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2 \]
+As $S$ is simple, there cannot be any commands on $n$ or $m$ in $S_1$,
+and therefore $(S_0\cc\cxynv\cc S_1)\FS(n) = y$,
+and $[(S_0\cc\cxynv\cc S_1)\FS(m)] = [S_0\FS(m)]$.
+If $[z]\neq[S_0\FS(m)]$, then $S\aFS=\fsbroken$, which is a contradiction.
+
+If $n=\parent(m)$, then 
+we know $(S_0\cc\cxynv\cc S_1)\FS(n) = y$, and as $[z]\neq[w]$, either
+$[(S_0\cc\cxynv\cc S_1)\FS(m)]=[z]\neq[\empt]$,
+or $[(S_0\cc\cxynv\cc S_1\cc\czwmv)\FS(m)]=[w]\neq[\empt]$.
+Therefore $y$ must be $\vald$, as otherwise the tree property would be violated
+when applying $\czwmv$,
+and $[x]\neq[\vald]$ as $\cxynv$ is not an assertion command.
+As $[S_0\FS(n)]=[x]\neq[\vald]$, we know
+$S_0\FS(m)=\empt$ as otherwise the tree property would be violated.
+Therefore $[S_0\FS(m)]=[z]=[\empt]$, which, combined with $y=\vald$
+means that $\cxynv\cc\czwmv\nequiv\cbrk$ is a construction pair, which is a contradiction.
+
+If $\parent(n)=m$, then 
+as $(S_0\cc\cxynv\cc S_1)\FS(n) = y$, and either
+$[(S_0\cc\cxynv\cc S_1)\FS(m)]=[z]\neq[\vald]$
+or $[(S_0\cc\cxynv\cc S_1\cc\czwmv)\FS(m)]=[w]\neq[\vald]$,
+$y$ must be $\empt$, and $[x]\neq[\empt]$.
+As $[S_0\FS(n)]=[x]\neq[\empt]$, we know $S_0\FS(m)=\vald$.
+Therefore $[S_0\FS(m)]=[z]=[\vald]$, which, combined with $y=\empt$
+means that $\cxynv\cc\czwmv\nequiv\cbrk$ is a destruction pair, which is a contradiction.
+\end{proof}
 
@@
 \begin{proof}
-$T$ can only be excluded from $\orderset{S}$ if it contains commands on a node and its parent
-which violate the conditions in \cref{def_orderset},
-which, as simple sequences do not contain assertion commands,
-entails that those commands placed next to each other in the same order
-would not form a construction or destruction pair.
-
-Informally speaking,
-our proposition for simple sequences $T\nequiv\cbrk$ is equivalent to the statement that
-two commands on a node and its parent must form
-a construction or destruction pair even if they are not next to each other.
-This is true because in simple sequences
-there cannot be another command between either of the nodes involved,
-so if the commands are incompatible, no command between them can change that.
-
-% BACK_TO_THE_FS TODO
-% TODO Review any proof depending on "nothing changes FS at n until...".
-To prove our proposition formally, we reach back to our filesystem model.
-Select two commands in $T$ that do not conform to \cref{def_orderset}, $\cxynv$ and $\czwmv$,
-and split $T$ around them into three parts:
-\[ T = T_0 \cc \cxynv \cc T_1 \cc \czwmv \cc T_2 \]
-As $T$ is simple, there cannot be any commands on $n$ or $m$ in $T_1$,
-and therefore $(T_0\cc\cxynv\cc T_1)\FS(n) = y$.
-If $n=\parent(m)$, then we know $y\neq\vald$, and
-(similarly to the reasoning in \cref{ax_directchild_breaks})
-as either before or after $\czwmv$ which is not an assertion command,
-$\FS(m)\neq\empt$, the latter command will break the filesystem.
-If $\parent(n)=m$, then we know $y\neq\empt$, and
-(similarly to the reasoning in \cref{ax_directparent_breaks})
-as wither before or after $\czwmv$, $\FS(m)\neq\vald$,
-the latter command will break the filesystem.
+TODO corollary
 \end{proof}

### 2016-10-31 p2/ordering.tex
Continue with update detection

@@
 To prove this, we will need the following results.
+
+\begin{mycor}\label{subseq_in_orderset}
+For simple sequences $S$ and $T$,
+if $T\in\orderset{S}$, then for any subsequence of $S$, $S_0$, which contains
+only part of the commands in $S$ but in the same order as in $S$,
+and for the corresponding subsequence of $T$, $T_0$, which
+contains the same commands but in the order they are found in $T$,
+$T_0\in\orderset{S_0}$ must hold.
+\end{mycor}
+\begin{proof}
+This is because
+if there are no command pairs in $T$ not conforming to \cref{def_orderset},
+then there cannot be any in $T_0$.
+\end{proof}
 
@@
 
-\begin{mylem}\label{order_is_only_possible}
-For any simple sequence $S$ and its permutation $T$, 
-\[ T\not\in\orderset{S} \Longrightarrow T\equiv\cbrk. \]
-\end{mylem}
+\begin{mycor}\label{order_is_only_possible}
+For any simple sequence $S$ and its permutation $S'$, 
+\[ S'\not\in\orderset{S} \Longrightarrow S'\equiv\cbrk. \]
+\end{mycor}
 \begin{proof}
-TODO corollary
+This follows directly from \cref{simple_distant_pairs}.
+If $S'\not\in\orderset{S}$ then by \cref{def_orderset}
+it contains two commands on a node $n$ and its parent
+that placed next to each other do not form
+a construction or destruction pair.
+Let them be $\cxynv$ and $\czwmv$.
+By \cref{ax_directchild_breaks,ax_directparent_breaks}
+we know the subsequence of $S'$,
+$\cxynv\cc\czwmv\equiv\cbrk$ and therefore by \cref{simple_distant_pairs}
+$S'\equiv\cbrk$.
 \end{proof}
@@
 We assume $T\equiv S$ and $T\not\in\orderset{S}$.
-Then, from \cref{order_is_only_possible} we know $T\equiv\cbrk$ which
+Then, from \cref{equiv_simple_same_commands} we know $T$ is a permutation of $S$,
+and from \cref{order_is_only_possible} we know $T\equiv\cbrk$ which
 is a contradiction as $T\equiv S\nequiv\cbrk$.
@@
 Let us consider $T\in\orderset{S}$ where $T$ and $S$ are of length $i+1$.
-We note that for any subsequence of $S$, $S_0$, which contains
-only part of the commands in $S$ but in the same order as in $S$,
-and for the corresponding subsequence of $T$, $T_0$, which
-contains the same commands but in the order they are found in $T$,
-$T_0\in\orderset{S_0}$ must hold as
-if there were no command pairs in $T$ not conforming to \cref{def_orderset},
-then there cannot be any in $T_0$.
-
-We also know that due to \cref{ax_separate_commute,incomparable_is_independent}
+We know that due to \cref{ax_separate_commute,incomparable_is_independent}
 $T$ can be rearranged into $T'\equiv T$ where
@@
 The segments contain commands in the same order as the full sequences.
-Therefore, from the observation abvout subsequences
+Therefore, from \cref{subseq_in_orderset}
 we know for all $1\leq j\leq k$, $T_j\in\orderset{S_j}$,
@@
 from the induction hypothesis
-we also know $T_j\equiv S_j$, from which we get $T\equiv S$.
+we also know $T_j\equiv S_j$, from which we get $T'\equiv S'$ and $T\equiv S$.
 
-We can assume $T'$ has at least two commands,
-and in the remaining case, when $T'$ has only one segment,
-we know all nodes that the commands in $T'$ apply to
+The remaining case is when $T'$ has at least two commands,
+but only one segment, which means
+that all nodes that the commands in $T'$ apply to
 are related via $\descendant$.

### 2016-11-02 p2/ordering.tex
Continue with update detection (ordering)

@@
 
+% TODO delete unused results
+
 \begin{mylem}\label{simple_reorder_equiv}
@@
 Next, we prove that if $T\in\orderset{S}$, then $T\equiv S$.
-We proceed by induction.
+We proceed by induction on the length of $S$.
 Our base cases are $\emptyseq$, where $\orderset{\emptyseq}=\{\emptyseq\}$,
@@
 $S$ can be converted similarly into $S'$, and
-as because of \cref{equiv_simple_same_commands} $S$ and $T$ contain the same commands,
-the segments of $S'$ will contain the same commands as those of $T$.
+as $S$ and $T$ contain the same commands,
+the segments of $S'$ will contain the same commands as those of $T'$.
 Let us therefore rearrange the segments of $S'$ so that the first segment
@@
 but only one segment, which means
-that all nodes that the commands in $T'$ apply to
-are related via $\descendant$.
-$T'$ contains the same commands as $S$, and
-from \cref{connected_changes} we see that the nodes the commands apply to therefore form a tree in $\setn$.
+all nodes the commands in $T$ apply to are related via $\descendant$.
+$T$ contains the same commands as $S$, and
+from \cref{connected_changes} we see that the nodes the commands apply to form a tree in $\setn$.
 We can therefore select the command on the topmost node (let it be $\cxynv$),
-and we know $T'$ contains commands on some of its child nodes.
+and we know $T$ contains commands on some of its child nodes.
 Let one of these be $\czwmv$.
-Now mark the command $\czwmv$ and all commands in $T'$ that are applied to nodes that are descendants of $m$.
-From \cref{ax_separate_commute} we know that all remaining commands in $T'$ (except $\cxynv$)
-commute with the marked commands; therefore we can swap them to get $T''\equiv T'$
+Now mark the command $\czwmv$ and all commands in $T$ that are applied to nodes that are descendants of $m$.
+From \cref{ax_separate_commute} we know that all remaining commands in $T$ (except $\cxynv$)
+commute with the marked commands; therefore we can swap them to get $T''\equiv T$
 where marked commands are next to $\cxynv$:

### 2016-12-01 p2/ordering.tex
Next step

@@
 
-In \cref{simple_reorder_equiv} we offer a formal proof that $\orderset{U}$ meets our expectations.
+In \cref{simple_reorder_equiv} we offer a formal proof that 
+$\orderset{U}$ contains all possible permutations.
 It is an important property of simple sequences: namely, that
@@
 Let us consider $T\in\orderset{S}$ where $T$ and $S$ are of length $i+1$.
+Let the first command in $S$ be $\cxynv$, that is, $S=\cxynv\cc S_0$.
+We proceed by a nested induction on the number of commands before $\cxynv$ in $T$.
+Our base case is when it is the first command, which means $T=\cxynv\cc T_0$.
+Then from \cref{subseq_in_orderset} we know $T_1\in\orderset{S_0}$
+and from the induction hypothesis $T_0\equiv S_0$ from which we get $T\equiv S$.
+
+In our nested induction step we assume $T'\equiv S$ for all $T'\in\orderset{S}$
+where there are at most $j$ commands in $T'$ to the left of $\cxynv$.
+Let us then consider $T$ where there are $j+1$ such commands.
+We aim to transform $T$ into $T''\equiv T$ by swapping $\cxynv$ with the preceding
+command. Then from the induction hypothesis we will know $T\equiv T''\equiv S$,
+which proves our lemma.
+
+Let the command to the left of $\cxynv$ in $T$ be $\czwmv$.
+If $n\unrel m$, then from \cref{ax_separate_commute} we know we can swap the two commands
+and get an equivalent sequence.
+Otherwise we note that necessarily $\cxynv$ and $\czwmv$ occur in the reverse order in $S$.
+We know $n=\parent(m)$ or $m=\parent(n)$ cannot be the case,
+
+TODO against definition
+
+The only remaining case is when $n$ and $m$ are comparable but not in a parent--child relationship.
+
+....................................
+
 We know that due to \cref{ax_separate_commute,incomparable_is_independent}

### 2016-12-02 p2/ordering.tex
Improved text

@@
 for which the following holds:
-for any two commands $\cxynv$ and $\czwmv$ in a sequence in $\orderset{U}$
-where $\cxynv$ comes earlier in the sequence than $\czwmv$,
+for any two commands $\cxynv$ and $\czwmv$ in a permutation
+where $\cxynv$ comes earlier,
 \begin{itemize}
@@
 nodes, then it contains commands on all nodes in between, so it is enough to specify
-the order of commands on parent and child nodes;
+the order of commands on directly related nodes;
 and finally, \cref{ax_directchild_breaks,ax_directparent_breaks}, from which we know
 that commands on parent--child pairs must be construction or destruction pairs.
-Investigating the pairs we see that they are identified by the output value of the first command ($y$),
-and that they determine whether the command on the parent or the child must precede the other.
+Investigating these pairs we see that they are identified by the output value of the first command ($y$),
+which in turn determines whether the command on the parent or the child must precede the other.
 
@@
 We assume $S\nequiv\cbrk$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
-but it contains commands that do not form a construction or destruction pair.
+but it contains commands on a node and its parent that do not form a construction or destruction pair.
 Select two such commands, $\cxynv$ and $\czwmv$,
@@
 Our base case is when it is the first command, which means $T=\cxynv\cc T_0$.
-Then from \cref{subseq_in_orderset} we know $T_1\in\orderset{S_0}$
+Then from \cref{subseq_in_orderset} we know $T_0\in\orderset{S_0}$
 and from the induction hypothesis $T_0\equiv S_0$ from which we get $T\equiv S$.

### 2017-09-30 p2/axioms.tex
Stronger lemma about distant pairs
Improved text. Added definitions of construction/destruction commands.

--- 2016-10-15 p2/axioms.tex
@@
 
-So that we can describe the effects of commands in general,
+So that we can describe the effects of commands independently of filesystems,
 let us introduce some notation
@@
 and are applied to filesystems in time.
-Therefore we will investigate sequences of commands with a well-defined order.
+Therefore we investigate sequences of commands with a well-defined order.
 \begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
@@
 (that is, the commands it contains in the given order)
-does not break.
+is defined on, that is, it does not break.
 
-We write $\Img{S}$ to denote the image of the domain of the sequence $X$.
+We write $\Img{S}$ to denote the image of the domain of the sequence $S$.
 \end{mydef}
@@
 The following two relations 
-(which echo the ones defined in \cite{NREC})
-allow us to investigate sequences of commands independently of filesystems.
+echo the ones defined in \cite{NREC}.
 In the definitions, $A,B,S,T$ stand for arbitrary sequences.
@@
 % Relation in the algebra
-$A\eqext B$ means that $B$ \emph{extends} $A$,
+We write $A\eqext B$, or $B$ \emph{extends} $A$,
 % intended interpretation:
-that is, they behave in the same way
+to mean that they behave in the same way
 on any filesystem $A$ does not break:
@@
 \begin{proof}
-If $\forall \FS: A\aFS=B\aFS$ then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
+% TODO APPENDIX
+If $\forall \FS: A\aFS=B\aFS$, then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
 For the reverse statement we know $A\eqext B$ and $B\eqext A$.
 $B\eqext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
-Therefore, for every filesystem $\FS$ either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
-in which case $B\aFS=\fsbroken$ must be true, and therefore $A\aFS=B\aFS$ still holds.
+Therefore, for every filesystem $\FS$, either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
+in which case $B\aFS=\fsbroken$ must be true, and therefore $A\aFS=B\aFS$.
 \end{proof}
+
+% Rules
+% -----
 
@@
             \cbdaa{\nn}\cc  \cbdaa{n} \\
-            \cfdaa{\nn}\cc  \cbfaa{n} \\
+            \cfdaa{\nn}\cc  \caaa{\empt}{\valff}{n} \\
             \cfdaa{\nn}\cc  \cbdaa{n}
    \end{gather*}
+\end{mydef}
+
+\begin{mydef}[Construction command]
+A command $\cxynv$ is a construction command if it can appear in a construction pair,
+that is, if $[x]=[\empt]$ and $[y]=[\valf]$ or $[y]=[\vald]$,
+or if $[x]=[\valf]$ and $[y]=[\vald]$.
 \end{mydef}
@@
 and the pair is not a construction pair.
+As we shall see, this can be extended to \cref{simple_distant_pairs}.
+% TODO
 \end{myax}
@@
             \cfba{n}\cc  \cdba{\nn} \\
-            \cfba{n}\cc  \cdfaa{\nn} \\
+            \cfba{n}\cc  \caaa{\vald}{\valff}{\nn} \\
             \cdba{n}\cc  \cdba{\nn} \\
@@
    \end{gather*}
+\end{mydef}
+
+\begin{mydef}[Destruction command]
+A command $\cxynv$ is a destruction command if it can appear in a destruction pair,
+that is, 
+if $[x]=[\valf]$ and $[y]=[\empt]$,
+or if $[x]=[\vald]$ and $[y]=[\empt]$ or $[y]=[\valf]$.
+Note that a command cannot be both a construction and a destruction command.
 \end{mydef}
@@
 and the pair is not a destruction pair.
+This can also be extended to \cref{simple_distant_pairs}.
+% TODO
 \end{myax}
@@
 
+% Independent commands
+% --------------------
+
 \noindent
@@
 
-\begin{mydef}[$A\indep B$: Independent commands, sequences and sets]\label{def_indep}
+\begin{mydef}[$A\indep B$: Independent commands, sequences and sets of commands]\label{def_indep}
 Two commands $\cxynv$ and $\czwmv$ 
@@
 for all $\alpha$ in $A$ and all $\beta$ in $B$, $\alpha\indep\beta$.
-We also write $\alpha\indep B$ iff $\forall \beta\in B:\alpha\indep\beta$.
+We also write $\alpha\indep B$ iff $\{\alpha\}\indep B$.
 \end{mydef}
@@
 \begin{mylem}\label{incomparable_is_independent}
-Two different commands that are not assertion commands are independent iff the nodes they change are incomparable:
+Two different commands that are not assertion commands are independent iff the nodes they change are incomparable. In other words,
 \[ \cxynv\indep\czwmv \Longleftrightarrow n\unrel m \]
-if $\cxynv\neq\czwmv$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
+if $\cxy\neq\czw$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
 \end{mylem}

### 2017-09-30 p2/def-commands.tex
Improved text. Added definitions of construction/destruction commands.

@@
 more precisely.
-In other words, encoding the outputvalue in the commands is definitely useful.
+In other words, encoding the output value in the commands is definitely useful.
 As the success or failure of filesystem commands only depends on the types of values in the filesystem,
@@
 we propose a set of commands that encode
-the type of the original value $\FS(n)$ as well.
+the type of the input value $\FS(n)$ as well.
 (Some real-life filesystem commands like $rmdir$ do this already.)
@@
 
-\bigskip
-
+% Definition
 % Break / empty command
 
-\noindent
-A command at times will return an error.
-This happens if the encoded type of the original filesystem value does not match
-what is actually in the filesystem, or if the modified filesystem no
-longer has the tree property.
-In these cases we say that the command {\em breaks} the filesystem,
-and the function we use to model the command will be undefined on the filesystem.
-
-So that we could reason about sequences of commands that break every filesystem, 
-we also introduce the command $\cbrk$ which is not defined anywhere,
-that is, which breaks every filesystem.
-
-% Definition
-
-\begin{mydef}[Filesystem commands]
-In other words, we model filesystem commands as partial endofunctions on filesystems,
+\begin{mydef}[Filesystem commands, $\cbrk$]
+We model filesystem commands as partial endofunctions on filesystems,
 that is, functions that map filesystems to filesystems, but which
@@
 \[ \alpha: \setfs \nrightarrow \setfs \]
-A command $\alpha$ is not defined on filesystems that it would break.
-At times in these cases we write that the command returns the bottom element, $\fsbroken$.
+A command $\alpha$ is not defined on filesystems where it returns an error.
+This happens if the input type of the command does not match
+what is actually in the filesystem, or if the modified filesystem no
+longer has the tree property.
+At times in these cases we write that the command {\em breaks} the filesystem,
+or that it returns the bottom element, $\fsbroken$.
+
 We write $\cbrk$ for the empty partial function which is not defined anywhere.
@@
 
-For example, $\cbfaa{n}$ will represent $create(n,\valf)$,
-and $\cdba{n}$ will represent $rmdir(n)$.
+For example, $\cbfaa{n}$ represents $create(n,\valf)$,
+and $\cdba{n}$ represents $rmdir(n)$.
 When describing unknown commands, we substitute one or both
@@
 (its input and output types), and write
-$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$
-(or equivalently $x\typeeq z$ and $y\typeeq w$).
+$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$.
 

### 2017-09-30 p2/ordering.tex
Improved text. Added definitions of construction/destruction commands.

@@
 
-Let us therefore define $\ordersetsign$ which gives us all
-possible orders in which a set of commands can be applied
-to filesystems without breaking it
-provided that the commands can be applied to a fileystem in some order.
+Let us therefore define $\ordersetsign$ which gives all
+permutations of a set of commands that do not break all filesystems.
 
 \begin{mydef}[$\ordersetsign$]\label{def_orderset}
-For a simple set or sequence $U$,
+For a simple set or sequence of commands $U$,
 we use $\orderset{U}$ to denote the set of sequences
@@
 for which the following holds:
-for any two commands $\cxynv$ and $\czwmv$ in a permutation
-where $\cxynv$ comes earlier,
+for all subsequences $\cxynv\cc\czwmv$,
 \begin{itemize}
@@
 
-The principal ideas behind this algorithm are 
+As usual, by subsequence we mean a subset of the commands in $S$ in the same order as they are found in $S$.
+
+The principal ideas behind these conditions are 
 \cref{ax_separate_commute}, from which we know that commands on incomparable
@@
 \begin{proof}
-As usual, by subsequence we mean a subset of the commands in $S$ in the same order as they are found in $S$.
-
 Informally speaking, the proposition means that
@@
 % TODO Review any proof depending on "nothing changes FS at n until...".
+% TODO Move to rules
+% TODO APPENDIX
 Formally, we prove our proposition by contradiction,
@@
 We assume $S\nequiv\cbrk$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
-but it contains commands on a node and its parent that do not form a construction or destruction pair.
+but $S$ contains commands on a node and its parent that do not form a construction or destruction pair.
 Select two such commands, $\cxynv$ and $\czwmv$,
 and split $S$ around them into three parts:
-\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2 \]
+\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2. \]
 As $S$ is simple, there cannot be any commands on $n$ or $m$ in $S_1$,
@@
 By \cref{ax_directchild_breaks,ax_directparent_breaks}
-we know the subsequence of $S'$,
-$\cxynv\cc\czwmv\equiv\cbrk$ and therefore by \cref{simple_distant_pairs}
-$S'\equiv\cbrk$.
+we know
+$\cxynv\cc\czwmv\equiv\cbrk$, which is a subsequence of $S'$,
+and therefore by \cref{simple_distant_pairs} $S'\equiv\cbrk$.
 \end{proof}
@@
 then so must all sets because otherwise there would be no order in which the commands they contain could be
-applied to any filesystem.
+applied to a filesystem.
 
@@
 For a simple sequence $S\nequiv\cbrk$,
-\[ \orderset{S} = [S]_\equiv \cap \setssmp, \]
-where $[S]_\equiv \cap \setssmp$ is the set of simple sequences equivalent to $S$.
+$\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
+\[ \orderset{S} = [S]_\equiv \cap \setssmp. \]
 \end{mylem}

### 2017-09-30 p2/axioms.tex
Finally, the proof

@@
 
-\begin{mydef}[Construction command]
-A command $\cxynv$ is a construction command if it can appear in a construction pair,
-that is, if $[x]=[\empt]$ and $[y]=[\valf]$ or $[y]=[\vald]$,
-or if $[x]=[\valf]$ and $[y]=[\vald]$.
-\end{mydef}
-
 \begin{myax}\label{ax_directchild_breaks}
@@
    \end{gather*}
-\end{mydef}
-
-\begin{mydef}[Destruction command]
-A command $\cxynv$ is a destruction command if it can appear in a destruction pair,
-that is, 
-if $[x]=[\valf]$ and $[y]=[\empt]$,
-or if $[x]=[\vald]$ and $[y]=[\empt]$ or $[y]=[\valf]$.
-Note that a command cannot be both a construction and a destruction command.
 \end{mydef}

### 2017-09-30 p2/ordering.tex
Finally, the proof

@@
 \end{mylem}
+
+For the proof we define construction and descruction commands as follows:
+\begin{mydef}[Construction command]
+A command $\cxynv$ is a construction command if it can appear in a construction pair,
+that is, if $[x]=[\empt]$ and $[y]\neq[\empt]$,
+or if $[x]=[\valf]$ and $[y]=[\vald]$.
+\end{mydef}
+\begin{mydef}[Destruction command]
+A command $\cxynv$ is a destruction command if it can appear in a destruction pair,
+that is, 
+if $[x]=[\valf]$ and $[y]=[\empt]$,
+or if $[x]=[\vald]$ and $[y]\neq[\vald]$.
+Note that a command cannot be both a construction and a destruction command.
+\end{mydef}
+
+% TODO APPENDIX
 \begin{proof}
@@
 In our induction step we assume that $T^*\in\orderset{S^*}\Rightarrow T^*\equiv S^*$ holds
-for all sequences of length $i\geq 1$ or less.
+for all sequences of length $i$ or less, where $i\geq 1$.
 
@@
 Let the command to the left of $\cxynv$ in $T$ be $\czwmv$.
+As $S$ is simple, we know $n\neq m$.
 If $n\unrel m$, then from \cref{ax_separate_commute} we know we can swap the two commands
 and get an equivalent sequence.
-Otherwise we note that necessarily $\cxynv$ and $\czwmv$ occur in the reverse order in $S$.
-We know $n=\parent(m)$ or $m=\parent(n)$ cannot be the case,
 
-TODO against definition
+\newcommand{\indx}{\varphi}
+Otherwise, either $n\descendant m$, or $m\descendant n$, and so from
+\cref{connected_changes} we know that $S$ contains a command on all nodes
+between $n$ and $m$, and therefore so does $T$.
+Let these nodes be $n_0, n_1, \ldots, n_k$ where $n_0=n$ and $n_k=m$,
+and where 
+either $n_\indx=\parentf{n_{\indx+1}}$ for all $\indx$ between $1$ and $k-1$,
+or $n_{\indx+1}=\parentf{n_\indx}$ for all $\indx$.
+We assume that $n_\indx=\parentf{n_{\indx+1}}$ is true.
 
-The only remaining case is when $n$ and $m$ are comparable but not in a parent--child relationship.
+Also, let $I^S_\indx$ be the index of the command on $n_\indx$ in $S$.
+For all $\indx$, both the commands on $n_\indx$ and $n_{\indx+1}$ must be either
+construction commands, or destruction commands, depending on
+whether $I^S_\indx<I^S_{\indx+1}$ or $I^S_{\indx+1}<I^S_\indx$.
+This is because otherwise, \cref{simple_distant_pairs} would not hold for $S$.
 
-....................................
+As a command cannot be both a construction and a desrtruction command,
+this means that the indices $I^S$ are either monotone increasing, or monotone
+decreasing, but cannot change direction.
+And as $S$ begins with $\cxynv$ and so $I^S_0=1$, we know they are monotone increasing,
+and the commands on $n_\indx$ are construction commands.
+If we denote the command on $n_\indx$ with $\caaa{x_\indx}{y_\indx}{n_\indx}$,
+by definition this means that $[y_\indx]\neq[\empt]$ for all $\indx$.
 
-We know that due to \cref{ax_separate_commute,incomparable_is_independent}
-$T$ can be rearranged into $T'\equiv T$ where
-$T'=T_1\cc T_2\cc \cdots \cc T_k$ and the segments $T_j$ are pairwise independent,
-and where we have the maximum number of segments possible.
-$S$ can be converted similarly into $S'$, and
-as $S$ and $T$ contain the same commands,
-the segments of $S'$ will contain the same commands as those of $T'$.
-Let us therefore rearrange the segments of $S'$ so that the first segment
-$S_1$ would correspond to (i.e. contain the same commands as) $T_1$, the second segment $S_2$ to $T_2$,
-and so on.
+Let us turn to the location of these commands in $T$,
+and denote their indices in $T$ with $I^T_\indx$.
+We know $I^T_k=I^T_0-1$ as $\czwmv$ precedes $\cxynv$.
+This means there must exist a $\indx$ for which $I^T_{\indx+1}<I^T_\indx$.
+We therefore know that
+$\caaa{x_{\indx+1}}{y_{\indx+1}}{n_{\indx+1}} \cc \caaa{x_\indx}{y_\indx}{n_\indx}$
+is a subsequence of $T$, and by assumption $\parentf{n_{\indx+1}}=n_\indx$.
+By definition of $\ordersetsign$, therefore $y_{\indx+1}=\empt$ must be true,
+which is a constradiction.
 
-The segments contain commands in the same order as the full sequences.
-Therefore, from \cref{subseq_in_orderset}
-we know for all $1\leq j\leq k$, $T_j\in\orderset{S_j}$,
-and if $T'$ has at least two segments and so 
-they are shorter than $i+1$,
-from the induction hypothesis
-we also know $T_j\equiv S_j$, from which we get $T'\equiv S'$ and $T\equiv S$.
-
-The remaining case is when $T'$ has at least two commands,
-but only one segment, which means
-all nodes the commands in $T$ apply to are related via $\descendant$.
-$T$ contains the same commands as $S$, and
-from \cref{connected_changes} we see that the nodes the commands apply to form a tree in $\setn$.
-We can therefore select the command on the topmost node (let it be $\cxynv$),
-and we know $T$ contains commands on some of its child nodes.
-Let one of these be $\czwmv$.
-Now mark the command $\czwmv$ and all commands in $T$ that are applied to nodes that are descendants of $m$.
-From \cref{ax_separate_commute} we know that all remaining commands in $T$ (except $\cxynv$)
-commute with the marked commands; therefore we can swap them to get $T''\equiv T$
-where marked commands are next to $\cxynv$:
-\[ T'' = T_\mathrm{unmarked\ left} \cc T_\mathrm{marked\ left} \cc \cxynv \cc T_\mathrm{marked\ right} \cc T_\mathrm{unmarked\ right}. \]
-
-TODO
-
-First, as $S$ only has at most one command on each node,
-any sequence in $\orderset{S}$ either breaks a filesystem,
-or it leaves it in the same state as $S$.
+It can be shown in the same way
+that the case when the $n_\indx$ nodes ascend the tree,
+that is, $n_{\indx+1}=\parentf{n_\indx}$ is true, also leads to a contradiction,
+by using destruction commands instead of construction ones.
 \end{proof}

### 2017-09-30 p2/ordering.tex
Improved intro to ordering

@@
 
-Let us therefore define $\ordersetsign$ which gives all
-permutations of a set of commands that do not break all filesystems.
+We recognize that mulitple orders may be possible;
+let us therefore describe our ordering algorithm by
+defining a subset of the permutations, $\ordersetsign$.
+The simplicity of the definition means that enumerating
+all sequences in $\ordersetsign$ can be implemented by a straightforward
+algorithm.
+
+As we will see, $\ordersetsign$ generates all possible
+sequences of commands that do not break all filesystems.
+In \cref{simple_reorder_equiv}, we offer a formal proof of this.
+It is an important property of simple sequences: namely, that
+all of their valid reorderings are equivalent,
+and all equivalent sequences are mere reorderings.
 
 \begin{mydef}[$\ordersetsign$]\label{def_orderset}
-For a simple set or sequence of commands $U$,
-we use $\orderset{U}$ to denote the set of sequences
-that are all permutations of the commands in $U$
+For a simple set or sequence of commands $S$,
+we use $\orderset{S}$ to denote the set of sequences
+that are all permutations of the commands in $S$
 for which the following holds:
@@
 
-In \cref{simple_reorder_equiv} we offer a formal proof that 
-$\orderset{U}$ contains all possible permutations.
-It is an important property of simple sequences: namely, that
-all of their valid reorderings are equivalent,
-and all equivalent sequences are mere reorderings.
-To prove this, we will need the following results.
+To prove \cref{simple_reorder_equiv}, we need the following results.
 
@@
 
+% TODO APPENDIX
 For the proof we define construction and descruction commands as follows:

### 2017-09-30 p2/ordering.tex
Clarifications, todo flags

@@
 and get an equivalent sequence.
+We finish the proof by showing that $n\unrel m$ must hold, as
+all other cases lead to contradiction.
 
 \newcommand{\indx}{\varphi}
-Otherwise, either $n\descendant m$, or $m\descendant n$, and so from
+If $n\nunrel m$, then either $n\descendant m$, or $m\descendant n$, and so from
 \cref{connected_changes} we know that $S$ contains a command on all nodes
@@
 
-TODO:
-It follows from the algorithm that:
+TODO TODO TODO -- ONLY USED ONCE WHERE INTERNALS OF OLD PROOF ARE USED
 \begin{mycor}\label{lemma:neighbor}
-If $U$ contains commands on both $n$ and $\parent(n)$, then
-there is a simple $U'\equiv U$ in which they are next to each other.
+If a simple sequence $S$ contains commands on both $n$ and $\parent(n)$, then
+there is a simple $S'\equiv S$ in which they are next to each other.
 \end{mycor}
 
-TODO:
+TODO TODO TODO:
 It follows from this that given a simple set,

### 2017-09-30 p2/rec-sound.tex
Clarifications, todo flags

@@
 If $B$ has a command on $m$, then
+-- TODO TODO TODO --
 from \cref{lemma:neighbor}

### 2017-10-01 p2/works-inverse.tex
Towards a new proof
New script to enumerate references

@@
 
-\begin{mydef}[$\worksmsign$, $\worksmeqsign$]
+\begin{mydef}[$\worksmsign$, $\worksmeqsign$]\label{def_works}
 For two sets of sequences $\sqs{A}$ and $\sqs{B}$
@@
 
-\begin{mydef}[$\T$]
+\begin{mydef}[$\T$]\label{def_typemapping}
 We use $\T$ and write $a\T$ to denote the canonical mapping of 
@@
 
-\begin{mycor}
+\begin{mycor}\label{cor_typemap_transitive}
 For any filesystem $\FS$ and command $\alpha$, 
@@
 
+% TODO \alpha \neq \cbrk
 \begin{mylem}\label{repr_comm_inject}
@@
 \begin{proof}
-This is trivial if $\GS\T=\fsbroken$, so we assume it is not so.
 Let $\alpha\T = \cTxynv$.
@@
 \end{mydef}
-Per definition, for any filesystem $\FS\T$ outside the image of $\alpha\T$, the inverse $\alpha\T^{-1}$ is undefined.
+Per definition, for any filesystem $\FS\T$ outside the image of $\alpha\T$, the inverse $\alpha\T^{-1}$ is not defined.
 
-\begin{mylem}
-For representative commands
-\[ \cTxynv^{-1} = \cTyxnv. \]
-TODO needed? -maybe for \cref{negneg_is_typeeq}
-\end{mylem}
-
-From the definitions we can clearly see that - TODO not used
-\begin{mycor}\label{negneg_is_typeeq}
-$\forall S: ({S\T}^{-1})^{-1} = S\T$.
-\end{mycor}
+% Some further observations:
+% For representative commands \[ \cTxynv^{-1} = \cTyxnv. \]
+% $\forall S: ({S\T}^{-1})^{-1} = S\T$.
 

### 2017-10-01 p2/get_references.pl

@@ -1,0 +1,99 @@
+#!/usr/bin/perl
+
+# This script parses TeX files to enumerate references to results
+
+use strict;
+
+use Data::Dumper;
+
+sub readfile {
+  my $filename = shift;
+  local $/ = undef;
+  open my $f, $filename or die "Cannot open $filename: $1";
+  my $contents = <$f>;
+  close($f);
+  return $contents;
+}
+
+my %References; # 'From' => ['To', ... ]
+
+sub process_file {
+  my $filename = shift;
+  
+  print "Processing $filename\n";
+  
+  my $contents = readfile($filename);
+
+  my $LastLabel = "___";
+  my $NonCorLabel = "___";
+  my $process_block = sub {
+    my $type1 = shift;
+    my $contents = shift;
+    my $type2 = shift;
+    
+    my $contents2 = substr($contents, 0, 40); # excerpt for logging
+    $contents2 =~ s/\s+/ /g;
+    
+    die "type mismatch '$type1' '$type2' '$contents'" unless $type1 eq $type2;
+
+    my $label;
+    unless($type1 eq 'proof') {
+      if($contents =~ /\\label\{([^\}]+)\}/){ $label = $1; }
+    }
+    
+    print "Found '$type1' '$label' '$contents2'\n";
+    
+    die "without label" if $type1 =~ /^my(cor|lem|th|ax)$/ && ! $label;
+    
+    $LastLabel = $label if $label;
+    $NonCorLabel = $label if $label && $type1 ne 'mycor';
+    
+    if($label && $References{$LastLabel}){
+      die "duplicate label";
+    }
+    
+    $References{$LastLabel} //= [];
+    
+    $contents =~ s/\\cref\{([^\}]+)\}/do{
+      my $refs = $1;
+      my @refs = split(m!,!, $refs);
+      push @{$References{$LastLabel}}, @refs;
+    }/ge;
+    
+    # A corollary depends on the previous result
+    if($type1 eq 'mycor'){
+      die "corollary without previous result" unless $NonCorLabel;
+      push @{$References{$LastLabel}}, $NonCorLabel;
+    }
+    
+  };
+
+  $contents =~ s/\\begin\{(proof|my[a-z]+)\}(.*?)\\end\{(proof|my[a-z]+)\}/do{
+    $process_block->($1, $2, $3);
+    '';
+  }/ges; 
+}
+
+sub process_index {
+  my $filename = shift;
+  
[…]

### 2017-10-02 p2/axioms.tex
New script to enumerate references
Rename "works" to "defined"

@@
 %% Sequences of commands form a free semigroup
+Sequences are also partial endofunctions on filesystems, defined only if all commands succeed.
 We write $\sets$ for the set of sequences of commands.
@@
 
-\begin{mylem}
+\begin{mylem}\label{equiv_on_fs}
 $A\equiv B$

### 2017-10-02 p2/rec-complete.tex
Minor updates
New definitions based on equivalence classes
Rename "works" to "defined"

@@
 
+%% TODO general properties of commands ==> behavior on specific filesystems
+
 The reconciliation algorithm defined above is also maximal, that is,
 it is not possible to apply any further commands from $A\setminus B$ to $\FS_B$.
-To show this, we are going to prove the following \namecref{rec_is_complete}:
+To show this, we are going to prove the following theorem:
 
@@
 Let us therefore suppose $n\neq m$ and, to use an inverse proof,
-that the sequence works on $\FS$ where $A\aFS\neq\fsbroken$.
-If so, its initial segment, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also work.
+that the sequence is defined on $\FS$ where $A\aFS\neq\fsbroken$.
+If so, its initial segment, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also be defined.
 
 We know $\cxynv\nindep\czwmv$, and so from \cref{incomparable_is_independent}, $n\nunrel m$.
-As the sequence works, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
+As the sequence is defined, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
 As $\czwmv$ and $T_0$ originate from $\bmanp$ and $B$ is simple, we also know there are
@@
 
-On the one hand we therefore know that $\FS(m)$ must be of type $Z$,
+On the one hand we therefore know that $\FS(m)$ must be of type $[z]$,
 but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},
@@
 
-Clearly $Q=Z$ (from \cref{worksinputmatch}), and from the construction and destruction
-pairs we also see that $R=W$ must hold, where $W=\cchard$ or $W=\ccharb$.
+Clearly $[q]=[z]$ (from \cref{worksinputmatch}), and from the construction and destruction
+pairs we also see that $r=w$ must hold, where $w=\vald$ or $w=\empt$.
 As $|\setd|=1$ and $|\setb|=1$, this also means that $v_R=v_W$ and therefore
@@
 As $A$ and $B$ are simple, we therefore know that these are the first commands on $n$,
-and so (again from \cref{worksinputmatch}) $Z=X$.
-We also know $\valvw\neq\valvy$ as otherwise the two commands would be equal and
+and so (again from \cref{worksinputmatch}) $[z]=[x]$.
+We also know $w\neq y$ as otherwise the two commands would be equal and
 would be included in $\acbnp$,

### 2017-10-02 p2/rec-intro.tex
Improved notation
Rename "works" to "defined"

@@
 and so they are simple sequences.
+% TODO
 (Otherwise, they can be simplified to become simple sequences; see \cref{update_works}.)
-We also assume that $\FS_A$ and $\FS_B$ are not broken.
+We also assume that $\FS$, $\FS_A$ and $\FS_B$ are not broken.
 With these assumptions,
@@
 the updates applied to replicas $\FS_A$ and $\FS_B$:
-\begin{align*}
-\reca = \{\alpha|{}& \\
-& \alpha\in A\setminus B \\
-& \wedge \\
-& \forall \beta\in B\setminus A: \alpha\indep\beta\\
-\}. &
-\end{align*}
+\[ \reca = \{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp \}. \]
 \end{mydef}
@@
 we can order the commands using the algorithm described in
-\cref{ordering} as any subset of $A$ is also simple.
+\cref{ordering} as $\reca$, being a subset of $A$, is also simple.
 

### 2017-10-02 p2/rec-sound.tex
New script to enumerate references
Rename "works" to "defined"

@@
 based on $\FS_B=B\aFS$ and so we aim to prove that
-$B\cc\reca$ works wherever $A$ and $B$ work:
+$B\cc\reca$ is defined wherever $A$ and $B$ are defined:
 
-\begin{myth}
+\begin{myth}\label{reconciliation_correct}
 If $A, B$ are simple, then $\worksmbb{A,B}{B\cc \reca}$,
@@
 Let $A$ and $B$ be two simple sequences so that $\worksmnilb{A, B}$.
-Then their intersection, in some suitable order, also works on any filesystem
-either of them works on:
-$\worksm{A}{\acbnp}$, and, by symmetry,
-$\worksm{B}{\acbnp}$.
+Then their intersection, in some suitable order, is also defined on any filesystem
+either of them is defined on:
+$\worksm{A}{\orderset{\acbnp}}$, and, by symmetry,
+$\worksm{B}{\orderset{\acbnp}}$.
 \end{mylem}
@@
 and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
+-- TODO TODO TODO --
 When describing our ordering algorithm in \cref{ordering} we saw
@@
 
+% TODO Set or sequence? See also above
+
 \noindent
@@
 \newcommand{\condWork}{(c4)}
-\begin{mylem}
+\begin{mylem}\label{reconciliation_correct_part}
 If

### 2017-10-02 p2/works-inverse.tex
Rename "works" to "defined"

@@
 we write $\worksm{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subseteq \Dom{\sqs{B}}$;
-that is, if all sequences in $\sqs{B}$ work (do not break the filesystem)
-on any filesystem all sequences in $\sqs{A}$ work on.
+that is, iff all sequences in $\sqs{B}$ are defined on (that is, do not break)
+all filesystems sequences in $\sqs{A}$ are defined on.
 We write $\worksmstr{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subset \Dom{\sqs{B}}$.
 
-As a special case, we write $\worksmnil{\sqs{A}}$ if we know that there is a filesystem
-all sequences in $\sqs{A}$ work on.
-We also apply these relations to sequences directly:
+As a special case, we write $\worksmnil{\sqs{A}}$ if we know that there is at least one filesystem
+all sequences in $\sqs{A}$ are defined on.
+We also apply these relations to sequences directly;
+e.g. we write
 $\worksm{A}{B}$ with the meaning $\worksm{\{A\}}{\{B\}}$.
@@
 In a sense, $A\worksmeqsign B$ is a weaker counterpart of $A\eqext B$, as the former
-only requires that $B$ works where $A$ works, where the latter also requires
-that where they work, their effect is the same.
+only requires that $B$ is defined where $A$ is defined, where the latter also requires
+that where they are defined, their effect is the same.
 It is easy to see that the following corollary is true:
@@
 % An inference rule in the algebra
-$\forall A,S: \worksm{A\cc S}{A}$, that is, if a sequence works, its initial segment also works.
+$\forall A,S: \worksm{A\cc S}{A}$, that is, if a sequence is defined,
+its initial segment is also defined.
 \end{mycor}
@@
 \begin{myax}\label{combine_independent_commands}
-The combination of independent commands works wherever both of the commands work:
+The combination of independent commands is defined on all filesystems
+where both of the commands are defined:
 \[ \alpha\indep \beta \Rightarrow \worksm{\{\alpha, \beta\}}{\{\alpha\cc \beta\}}. \]
@@
 \begin{mylem}\label{combine_independent_sequences}
-The combination of independent sequences works wherever both of the sequences work:
+The combination of independent sequences is defined on all filesystems
+where both of the sequences are defined:
 \[ S\indep T \Rightarrow \worksm{\{S,T\}}{\{S\cc T\}}. \]
@@
 
-Let the command that breaks $\FS$ in $T$ when applying $S\cc T$ be $t$
+Let the command in $T$ that breaks $\FS$ when applying $S\cc T$ be $t$
 so that $T=T_0\cc t\cc T_1$.
@@
 
-It is easy to see that for all objects where it is defined, $a\T\typeeq a$.
+By definiton, for all objects where it is defined, $a\T\typeeq a$.
 % $|\setf|$ is also $1$.
@@
 \begin{proof}
-Let $\alpha\T = \cTxynv$.
+Choose values that satisfy the left side, and let $\alpha\T = \cTxynv$.
 If $\FS\T$ and $\GS\T$ have different values at any node apart from $n$, then this difference remains
-even after applying $\cTxynv$ to $\FS\T$. The only remaining case therefore is where they have the same values
-at all nodes except $n$.
+even after applying $\cTxynv$ to $\FS\T$. 
+The only remaining case therefore is where they have the same values
+at all nodes except at $n$.
 As $\cTxynv(\FS\T)\neq\fsbroken$, we know $[\FS\T(n)]=[x]$.
@@
 
-Unless $\worksmnil{\ia}$, the propositions is trivially true. Otherwise,
-for the left-to-right part of the proposition,
-we know $\worksmnil{B\cc\ic}$, which implies that $\Dom{\ic}$ intersects with $\Img{B}$ 
-as otherwise $B\cc\ic$ would break all filesystems.
+For the left-to-right part of the proposition,
+from $\worksm{\ia}{B\cc\ic}$ we know $\Dom{\ia} \subseteq \Dom{B\cc\ic}$.
 As the (representative) $B$ is a bijection between its domain and image,
-we can use $\ibi$ to map this intersection back
-onto the domain of $B$ and get $\Dom{B\cc\ic}$.
-As $\worksm{\ia}{B\cc\ic}$, 
-we also know that $\Dom{\ia} \subseteq \Dom{B\cc\ic}$.
-We now use $B$ to map both sides of this statement, which yields
+we can use $B$ to map both sides of this statement, which yields
 $\Dom{B^{-1}\cc\ia} \subseteq \Dom{\ibi\cc B\cc\ic}$,
@@
 and so $\Dom{\ibi\cc\ia} \subseteq \Dom{\ic}$,
-which is the same as $\worksm{\ibi\cc\ia}{\ic}$.
+which means that $\worksm{\ibi\cc\ia}{\ic}$.
+It is easy to see that $\worksm{\ia}{B\cc\ic} \Leftrightarrow \worksm{\ia}{\{B\}}$.
 
 For the right-to-left part,
-from $\worksm{\ia}{B}$ we know $\Dom{\ia} \subseteq \Dom{B}$.
+from $\worksm{\ia}{\{B\}}$ we know $\Dom{\ia} \subseteq \Dom{B}$.
 Therefore we can project the whole of $\Dom{\ia}$ using the bijective representative sequence $B$
@@
 as $\Dom{\ia} \subseteq \Dom{B}$,
-and so $\Dom{\ia} \subseteq \Dom{B\cc\ic}$ which is the same as
+and so $\Dom{\ia} \subseteq \Dom{B\cc\ic}$ which means
 $\worksm{\ia}{B\cc\ic}$.
@@
 \begin{mylem}\label{indep_prefix_combine}
-The combination of sequences with a common head and independent tails 
-continues to work under the same conditions:
+The combination of two sequences with a common head and independent tails 
+is defined wherever the two sequences are defined:
 \begin{gather*}

### 2017-10-02 p2/axioms.tex
New "works" symbol, fixes

@@
 %% Sequences of commands form a free semigroup
-Sequences are also partial endofunctions on filesystems, defined only if all commands succeed.
+Sequences are also partial endofunctions on filesystems, defined only if all commands it contains succeed in the given order.
 We write $\sets$ for the set of sequences of commands.
@@
 \begin{mydef}[$\Dom{S}$ and $\Img{S}$]
-For a sequence of commands $S$, $\Dom{S}$ is the domain of $S$,
-which is the set of filesystems $S$
-(that is, the commands it contains in the given order)
-is defined on, that is, it does not break.
-
+For a sequence of commands $S$, $\Dom{S}$ is the domain of $S$.
 We write $\Img{S}$ to denote the image of the domain of the sequence $S$.
@@
 
+\begin{mydef}[$\strext$]
+We write $A\strext B$ if $A\eqext B$ and $A\nequiv B$.
+In particular, we write $\wrks{A}$ if $A$ is defined on some filesystems.
+\end{mydef}
+
 % Rules
@@
 \begin{myax}\label{ax_separate_nobreaks}
-Commands on incomparable nodes do not break every filesystem:
-$\cxynv\cc\czwmv \nequiv \cbrk$ where $n\unrel m$.
+Commands on incomparable nodes do not break all filesystems:
+$\wrksx{\cxynv\cc\czwmv}$ where $n\unrel m$.
 \end{myax}
@@
 \end{myax}
+
+% TODO \nequiv\cbrk -> \wrks
 

### 2017-10-02 p2/works-inverse.tex
New "works" symbol, fixes

@@
 and $\Dom{\sqs{A}}$ to denote $\bigcap_{A\in\sqs{A}} \Dom{A}$.
+
+We also write $\wrks{\sqs{A}}$ if $\varnothing \subset \Dom{\sqs{A}}$, that is,
+if we know that there is at least one filesystem
+all sequences in $\sqs{A}$ are defined on.
 \end{mydef}
@@
 
-As a special case, we write $\worksmnil{\sqs{A}}$ if we know that there is at least one filesystem
-all sequences in $\sqs{A}$ are defined on.
 We also apply these relations to sequences directly;
 e.g. we write
-$\worksm{A}{B}$ with the meaning $\worksm{\{A\}}{\{B\}}$.
+$\worksm{A}{B}$ with the meaning $\Dom{A} \subseteq \Dom{B}$.
 \end{mydef}
@@
 In a sense, $A\worksmeqsign B$ is a weaker counterpart of $A\eqext B$, as the former
-only requires that $B$ is defined where $A$ is defined, where the latter also requires
+only requires that $B$ is defined where $A$ is defined, 
+while the latter also requires
 that where they are defined, their effect is the same.
@@
 By definiton, for all objects where it is defined, $a\T\typeeq a$.
-% $|\setf|$ is also $1$.
 As representatives of filesystems, commands, sequences, etc.
-are subsets of their non-representative counterparts, all
-propositions proven so far apply to them as well.
+are subsets of their non-representative counterparts, 
+all propositions proven so far apply to them as well.
 
@@
 equivalent to saying that representative functions are injective except for cases
-where they break a filesystem (they are not defined):
+where they are not defined:
 \[ \forall\FS,\GS,\alpha: \FS\T\neq\GS\T \wedge \alpha\T(\FS\T)\neq\fsbroken \Longrightarrow \alpha\T(\FS\T) \neq \alpha\T(\GS\T). \]
@@
 which means that $\worksm{\ibi\cc\ia}{\ic}$.
-It is easy to see that $\worksm{\ia}{B\cc\ic} \Leftrightarrow \worksm{\ia}{\{B\}}$.
+It is easy to see that $\worksm{\ia}{B\cc\ic} \Rightarrow \worksm{\ia}{\{B\}}$.
 

### 2017-10-03 p2/works-inverse.tex
Simpler theorem for common heads

@@
 \end{gather*}
+
+TODO WHY NOT: See \cref{combine_independent_sequences}
+\[ B\indep C \Rightarrow \worksmbb{A\cc B, A\cc C}{A\cc B\cc C} \]
+
 \end{mylem}
 \begin{proof}
+
+TODO NEW PROOF:
+
+TODO OLD PROOF:
+
 Based on \cref{repr_works_is_same} we have

### 2017-10-03 p2/get_references.pl

@@ -96,4 +96,8 @@ while(my($from, $tos) = each %References) {
   }
 }
 
-print Dumper(\%Backreferences);
+foreach my $to (sort keys %Backreferences){
+  my $from = $Backreferences{$to};
+  print "$to From:\n";
+  print join('', map { "  ".$_."\n" } @$from) . "\n";
+}

### 2017-10-05 p2/rec-sound.tex
Simpler lemma

@@
 \[ \worksmbb{A,B}{\acb\cc \bma\cc \reca}. \]
-As we already know that $\reca\indep\bma$
-and that $\worksmbb{A,B}{\acb\cc \bma}$
-(as $\worksmbb{A,B}{B}$),
-we can prove our theorem based on \cref{indep_prefix_combine}
-if we can prove that
+We can prove this if we can show that
 \[ \worksmbb{A,B}{\acb\cc \reca}. \]
-Based on \cref{r_invmove} and \cref{repr_works_is_same}, and because
-we already know that $\worksmbb{A,B}{\acbnp}$,
-this is equivalent to
-\[ \worksmbb{\acbi\cc A\T,\acbi\cc B\T}{\reca\T}. \]
+This is because we already know
+that $\worksmbb{A,B}{\acb\cc \bma}$ (as $\worksmbb{A,B}{B}$),
+which, combined with the above, yields
+\[ \worksmbb{A,B}{\acb\cc \reca, \acb\cc \bma}. \]
+Also, as $\reca\indep\bma$,
+from \cref{indep_prefix_combine}
+we know
+\[ \worksmbb{\acb\cc \reca, \acb\cc \bma}{\acb\cc \bma\cc \reca}. \]
+As $\worksmeqsign$ is transitive, combining the two results
+gives the statement we intended to prove.
 
@@
 \item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
+% TODO Inverse is used here - how/why?
 \item $\worksmbb{\acbi\cc A,\acbi\cc B}{\amb, \bma}$ 

### 2017-10-05 p2/works-inverse.tex
New section title
Simpler lemma

--- 2017-10-02 p2/works-inverse.tex
@@
 
-\subsection{Conditional Operation and Inverse Sequences}
+\subsection{Domains and Inverse Sequences}
 
@@
 From this it follows that
+% TODO what's the set of all filesystems?
 
@@
 is defined wherever the two sequences are defined:
-\begin{gather*}
- \worksmxb{\sqs{S}}{A\cc B} \,\wedge\, \worksmxb{\sqs{S}}{A\cc C} \,\wedge\, B\indep C \\
- \Longrightarrow \worksmxb{\sqs{S}}{A\cc B\cc C}
-\end{gather*}
+\[ B\indep C \Rightarrow \worksmbb{A\cc B, A\cc C}{A\cc B\cc C} \]
 \end{mylem}
 \begin{proof}
-Based on \cref{repr_works_is_same} we have
-$\worksmxb{\sqs{S}\T}{A\T\cc B\T}$ and $\worksmxb{\sqs{S}\T}{A\T\cc C\T}$,
-and from \cref{r_invmove} we know
-$\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{B\T}$ 
-and $\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{C\T}$.
-Using \cref{combine_independent_sequences} we get
-$\worksmbb{B\T,C\T}{B\T\cc C\T}$,
-and chaining these (as $\worksmeqsign$ is transitive)
+This is trivial unless $\worksmnil{A}$, so we assume that that is the case.
+From $B\indep C$ and \cref{combine_independent_sequences} we know
+$\worksmbb{B, C}{B\cc C}$.
+Based on \cref{repr_works_is_same} this is equivalent to
+$\worksmbb{B\T, C\T}{B\T\cc C\T}$.
+Since $A\T^{-1}\cc A\T \equiv \emptyseq$, this can also be written as
+\[\worksmxb{A\T^{-1}\cc\{A\T\cc B\T, A\T\cc C\T\}}{B\T\cc C\T}.\]
+From \cref{worksextpostfix} we also know that
+$\worksmbb{A\T\cc B\T, A\T\cc C\T}{A\T}$.
+Combining the last two statements using \cref{r_invmove}
 we get
-$\worksmxb{{A\T}^{-1}\cc \sqs{S}\T}{B\T\cc C\T}$.
-
-From $\worksmxb{\sqs{S}}{A\cc B}$ we also know $\worksmxb{\sqs{S}}{A}$ and $\worksmxb{\sqs{S}\T}{A\T}$.
-We can combine this and $\worksmxb{{A\T}^{-1}\cc \sqs{S}\T}{B\T\cc C\T}$ using
-\cref{r_invmove} to get
-$\worksmxb{\sqs{S}\T}{A\T\cc B\T\cc C\T}$, and from \cref{repr_works_is_same} we know
-$\worksmxb{\sqs{S}}{A\cc B\cc C}$.
+\[ \worksmbb{A\T\cc B\T, A\T\cc C\T}{A\T\cc B\T\cc C\T}, \]
+which with \cref{repr_works_is_same} proves the
+\namecref{indep_prefix_combine}.
 \end{proof}

### 2017-10-06 p2/conclusion.tex
Remove unused symbols; clarify text

--- 2016-01-07 p2/conclusion.tex
@@
 the demonstrated properties of minimal sequences of commands
-and conditional operation of sequences ($\workssign$)
+and conditional operation of sequences ($\worksmeqsign$) % TODO
 may also contribute to future research into algebraic structures

### 2017-10-06 p2/ordering.tex
New script to enumerate references
Remove unused symbols; clarify text

@@
 \begin{mylem}\label{simple_distant_pairs}
-For any simple sequence $S\nequiv\cbrk$
+For any simple sequence $\wrksx{S}$,
 if $\cxynv\cc\czwmv$ is a subsequence of $S$ and $n=\parent(m)$ or $\parent(n)=m$,
-then $\cxynv\cc\czwmv\nequiv\cbrk$.
+then $\wrks{\cxynv\cc\czwmv}$.
 \end{mylem}
@@
 and in this version of the proof we reach back to our filesystem model.
-We assume $S\nequiv\cbrk$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
+We assume $\wrks{S}$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
 but $S$ contains commands on a node and its parent that do not form a construction or destruction pair.
@@
 Therefore $[S_0\FS(m)]=[z]=[\empt]$, which, combined with $y=\vald$
-means that $\cxynv\cc\czwmv\nequiv\cbrk$ is a construction pair, which is a contradiction.
+means that $\wrksx{\cxynv\cc\czwmv}$ is a construction pair, which is a contradiction.
 
@@
 Therefore $[S_0\FS(m)]=[z]=[\vald]$, which, combined with $y=\empt$
-means that $\cxynv\cc\czwmv\nequiv\cbrk$ is a destruction pair, which is a contradiction.
+means that $\wrksx{\cxynv\cc\czwmv}$ is a destruction pair, which is a contradiction.
 \end{proof}
@@
 
+% TODO breaks --> not defined on
+
 \begin{mylem}\label{equiv_simple_same_commands}
 If two simple sequences $A$ and $B$ are equivalent
-and do not break all filesystems ($A\equiv B\nequiv\cbrk$),
+and do not break all filesystems ($A\equiv \wrksx{B}$),
 then they must contain the same commands.
@@
 % BACK_TO_THE_FS
+% TODO Rule?
 We use a proof by contradiction. Let $A$ and $B$ be simple sequences
-such that $A\equiv B\nequiv\cbrk$,
-and $\FS$ be a filesystem that they do not break.
+such that $A\equiv \wrksx{B}$,
+and $\FS$ be a filesystem that they are defined on.
 
@@
 \begin{mylem}\label{simple_reorder_equiv}
-For a simple sequence $S\nequiv\cbrk$,
+For a simple sequence $\wrksx{S}$,
 $\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
@@
 and from \cref{order_is_only_possible} we know $T\equiv\cbrk$ which
-is a contradiction as $T\equiv S\nequiv\cbrk$.
+is a contradiction as $T\equiv \wrksx{S}$.
 
@@
 By definition of $\ordersetsign$, therefore $y_{\indx+1}=\empt$ must be true,
-which is a constradiction.
+which is a contradiction.
 

### 2017-10-06 p2/works-inverse.tex
Remove unused symbols; clarify text

@@
 to denote such sets for brevity.
-We will use $A\cc\sqs{B}$ to denote the set of sequences $\{A\cc B\whr B\in\sqs{B}\}$,
-and $\Dom{\sqs{A}}$ to denote $\bigcap_{A\in\sqs{A}} \Dom{A}$.
+We will write $\Dom{\sqs{A}}$ for $\bigcap_{A\in\sqs{A}} \Dom{A}$,
+and $\sqs{A}\cc\sqs{B}$ for $\{A\cc B\whr A\in\sqs{A}, B\in\sqs{B}\}$.
+We will also use $A\cc\sqs{B}$ with the meaning $\{A\}\cc\sqs{B}$.
 
-We also write $\wrks{\sqs{A}}$ if $\varnothing \subset \Dom{\sqs{A}}$, that is,
+% This has only been defined for sequences, not sets.
+Moreover, we write $\wrks{\sqs{A}}$ if $\varnothing \subset \Dom{\sqs{A}}$, that is,
 if we know that there is at least one filesystem
@@
 
-\begin{mydef}[$\worksmsign$, $\worksmeqsign$]\label{def_works}
+\begin{mydef}[$\worksmeqsign$]\label{def_works}
 For two sets of sequences $\sqs{A}$ and $\sqs{B}$
 we write $\worksm{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subseteq \Dom{\sqs{B}}$;
-that is, iff all sequences in $\sqs{B}$ are defined on (that is, do not break)
-all filesystems sequences in $\sqs{A}$ are defined on.
-We write $\worksmstr{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subset \Dom{\sqs{B}}$.
+that is, iff all sequences in $\sqs{B}$ are defined on (do not break)
+all filesystems on which sequences in $\sqs{A}$ are defined.
 

### 2017-10-08 p2/axioms.tex
Remove unused symbols; clarify text
Improvements

@@
 
-% TODO \nequiv\cbrk -> \wrks
-
 \begin{mydef}[Destruction pair]
@@
 they commute and do not break all filesystems:
-\[ \cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk. \]
+\[ \cxynv\cc\czwmv \equiv \wrksx{\czwnv\cc\cxynv}. \]
 For two sequences or unordered sets of commands $A$ and $B$ we write $A\indep B$ if
@@
 
-We proceed in two steps. First, we note that
+For the right-to-left part, we note that
 from \cref{ax_separate_commute,ax_separate_nobreaks} we know that
@@
 
-We prove the second step by contradiction.
+We prove the left-to-right part by contradiction.
 We assume that both $\cxynv\indep\czwmv$ and $n\nunrel m$,

### 2017-10-08 p2/def-commands.tex
Improvements

@@
 For reasons also listed in \cite{NREC}, in this paper we will not consider
-a $move$ or $rename$ command. Regarding the theoretical reasoning we aim to follow,
-this turns out to be useful because this would be the only command that affects
+a $move$ or $rename$ command.
+This turns out to be useful because this would be the only command that affects
 filesystems at two nodes at once, therefore describing 

### 2017-10-08 p2/def-filesystem.tex
F depends on N
Improved text. Added definitions of construction/destruction commands.
Improvements

@@
 and a set of possible contents or values $\setv$ as its codomain.
+We consider metadata to be part of the values in $\setv$.
 \begin{mydef}[Filesystems, $\setn$, $\setv$, $\setfs$ and $\empt$]
@@
 where in our model $\FS$ has a special value, $\empt\in\setv$.
-We write $\setfs$ for the set of filesystems.
+We write $\setfs$ for the set of filesystems over $\setn$.
 \end{mydef}
@@
 As usual, we write $[v]$ for the equivalence class of $v$, which represents its type.
-We also consider metadata to be part of the values in $\setv$.
 
@@
 \begin{mydef}[Tree property]
-\[ \forall n\in\setn, \FS\in\setfs: \FS(n) \neq \empt \Longrightarrow \FS(\parent(n)) \in \setd \]
-where $\parent(n)$ is defined, and where $\setd\subset\setv$ is the set of directories.
+\[ \forall n\in\setn, \FS\in\setfs: \FS(n) \neq \empt \Longrightarrow \FS(\parent(n)) \typeeq \vald \]
+where $\parent(n)$ is defined, and where $\vald\in\setv$ is a directory value.
 \end{mydef}
@@
 
-% This means that as we move down from the root of a tree of nodes,
-% the types of values we encounter in the filesystem can only change according to the
-% transition diagram in \cref{fig_transition}, from directories ($\cchard$) to files ($\ccharf$)
-% to empty nodes ($\ccharb$).
-% 
-% \begin{figure}[htb]
-% \input{fig-type-transition}
-% \caption{Transitions between types of values from the root of a tree in a filesystem}\label{fig_transition}
-% \end{figure}
-
 In this paper, $\FS$ and $\GS$ denote filesystems,
 and $n$, $m$ and $o$ are nodes in $\setn$.
-We write $\valf$ for an arbitrary file value. % element in $\setf$.
+We write $\valf$ for a file value. % element in $\setf$.

### 2017-10-08 p2/ordering.tex
Improvements

@@
 For simple sequences $S$ and $T$,
-if $T\in\orderset{S}$, then for any subsequence of $S$, $S_0$, which contains
-only part of the commands in $S$ but in the same order as in $S$,
+if $T\in\orderset{S}$, then for any subsequence of $S$, $S_0$,
 and for the corresponding subsequence of $T$, $T_0$, which
@@
 if $\cxynv\cc\czwmv$ is a subsequence of $S$ and $n=\parent(m)$ or $\parent(n)=m$,
-then $\wrks{\cxynv\cc\czwmv}$.
+then $\wrksx{\cxynv\cc\czwmv}$.
 \end{mylem}
@@
 $\cxynv\cc\czwmv\equiv\cbrk$, which is a subsequence of $S'$,
-and therefore by \cref{simple_distant_pairs} $S'\equiv\cbrk$.
+and therefore by \cref{simple_distant_pairs}, $S'\equiv\cbrk$.
 \end{proof}
@@
 
+\begin{mydev}[$\orderd{S}$]
+It follows from \cref{simple_reorder_equiv} that given a simple set of commands $S$,
+which can be applied to a filesystem without breaking it,
+all sequences in $\orderset{S}$
+represent the same partial endofunction on filesystems.
+This allows us to treat such a set as a sequence for any purpose
+where the internal order of the commands is irrelevant.
+We write $\orderd{S}$ to represent this endofunction.
+\end{mydev}
+
 %% TODO Define set operations on sequences?

### 2017-10-08 p2/works-inverse.tex
Improvements

@@
 to denote such sets for brevity.
+
 We will write $\Dom{\sqs{A}}$ for $\bigcap_{A\in\sqs{A}} \Dom{A}$,
@@
 \begin{mylem}\label{worksinputmatch}
-If $A$ and $B$ are minimal sequences, $\worksmnil{\{A,B\}}$,
-and there are commands on node $n$ in both $A$ ($\cxynv\in A$) and $B$ ($\czwnv\in B$),
+If $S$ and $T$ are minimal sequences, $\worksmnil{\{A,B\}}$,
+and there are commands on node $n$ in both $S$ ($\cxynv\in A$) and $T$ ($\czwnv\in B$),
 then the input types of these commands must match ($[x]=[z]$).
@@
 either $\cxynv$ or $\czwnv$ would not break, 
-and consequently $A$ and $B$ cannot work on the same filesystem.
+and consequently $S$ and $T$ cannot work on the same filesystem.
 \end{proof}
@@
 
-By definiton, for all objects where it is defined, $a\T\typeeq a$.
+By definiton,
+for any filesystem $\FS$ and command $\alpha$, 
+$\alpha\T(\FS\T) = (\alpha\aFS)\T$.
+
+% TODO ???
+Also, for all objects where it is defined, $a\T\typeeq a$.
 As representatives of filesystems, commands, sequences, etc.
@@
 all propositions proven so far apply to them as well.
-
-\begin{mycor}\label{cor_typemap_transitive}
-For any filesystem $\FS$ and command $\alpha$, 
-$\alpha\T(\FS\T) = (\alpha\aFS)\T$.
-TODO needed?
-\end{mycor}
 
@@
 \begin{mylem}\label{repr_comm_inject}
-Representative commands $\alpha\T$ are partial bijections over representative filesystems ($\FS\T$).
+Representative commands $\alpha\T$ are partial bijections over representative filesystems
+($\FS\T$, $\GS\T$).
 Because partial functions are trivially surjective when restricted to their images, this is
@@
 Choose values that satisfy the left side, and let $\alpha\T = \cTxynv$.
-If $\FS\T$ and $\GS\T$ have different values at any node apart from $n$, then this difference remains
+If $\FS\T$ and $\GS\T$ have different values (types) at any node apart from $n$, then this difference remains
 even after applying $\cTxynv$ to $\FS\T$. 
@@
 at all nodes except at $n$.
-As $\cTxynv(\FS\T)\neq\fsbroken$, we know $[\FS\T(n)]=[x]$.
-We also know that $\GS\T(n)\neq\FS\T(n)$, and therefore, as there is a one-to-one correspondence between values and types,
-$[\GS\T(n)]\neq[x]$.
+As $\cTxynv(\FS\T)\neq\fsbroken$, we know $[\FS(n)]=[x]$.
+We also know that $\GS\T(n)\neq\FS\T(n)$, and therefore
+$[\GS(n)]\neq[x]$.
 This implies $\cTxynv(\GS\T)=\fsbroken$,
@@
 \end{mydef}
-Per definition, for any filesystem $\FS\T$ outside the image of $\alpha\T$, the inverse $\alpha\T^{-1}$ is not defined.
+By definition, for any representative filesystem $\FS\T$ outside the image of $\alpha\T$, the inverse $\alpha\T^{-1}$ is not defined.
 

### 2017-10-08 p2/ordering.tex
Symbol for sequences from sets; improvements

@@
 
-\begin{mydev}[$\orderd{S}$]
+\begin{mydef}[$\ordsign$]
 It follows from \cref{simple_reorder_equiv} that given a simple set of commands $S$,
-which can be applied to a filesystem without breaking it,
-all sequences in $\orderset{S}$
+which can be applied to a filesystem in some order without breaking it,
+this order will be in $\orderset{S}$,
+and all sequences in $\orderset{S}$
 represent the same partial endofunction on filesystems.
@@
 where the internal order of the commands is irrelevant.
-We write $\orderd{S}$ to represent this endofunction.
-\end{mydev}
+We write $\ordp{S}$ to represent this endofunction.
+Also, let $\ordp{S}=\cbrk$ if such an order does not exist.
+\end{mydef}
 

### 2017-10-08 p2/rec-intro.tex
Symbol for sequences from sets; improvements

@@
 As some commands may have been applied to both filesystems, our first approximation
-is $\reca = A\setminus B$ and $\recb = B\setminus A$
-(in some suitable order).
+is $\reca = \amb$ and $\recb = \bma$.
 This, however, will break both filesystems if there have been incompatible updates
@@
 and show that these are the longest sequences with this property, that is,
-adding any command left out from $\reca$ or $\recb$ will break the filesystems.
+adding any further command from $\reca$ or $\recb$ will break the filesystems.
 
@@
 the updates applied to replicas $\FS_A$ and $\FS_B$:
-\[ \reca = \{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp \}. \]
+\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
 \end{mydef}

### 2017-10-08 p2/rec-sound.tex
Symbol for sequences from sets; improvements

@@
 \begin{myth}\label{reconciliation_correct}
-If $A, B$ are simple, then $\worksmbb{A,B}{B\cc \reca}$,
+If $A$ and $B$ are simple, then $\worksmbb{A,B}{B\cc \reca}$,
 where, to restate \cref{def:reconciliation},
-\[ \reca = \{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp \}. \]
+\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
 \end{myth}
@@
 Let $A$ and $B$ be two simple sequences so that $\worksmnilb{A, B}$.
-Then their intersection, in some suitable order, is also defined on any filesystem
+Then their intersection is also defined on any filesystem
 either of them is defined on:
-$\worksm{A}{\orderset{\acbnp}}$, and, by symmetry,
-$\worksm{B}{\orderset{\acbnp}}$.
+$\worksm{A}{\ordp{\acbnp}}$, and, by symmetry,
+$\worksm{B}{\ordp{\acbnp}}$.
 \end{mylem}
@@
 \end{gather*}
-As $A$ is simple and $\worksmnilb{A}$, from 
+As $A$ is simple and $\wrks{A}$, from 
 \cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
@@
 from \cref{worksextpostfix} we know that
-$\worksm{A}{\acbnp}$ and by symmetry $\worksm{B}{\acbnp}$.
+$\worksm{A}{\acb}$ and by symmetry $\worksm{B}{\acb}$.
 \end{proof}
@@
 Our theorem is therefore proven if we prove the following lemma,
-in which we rename $\ambnp$ to $S$ and $\bmanp$ to $T$:
+in which we rename $\amb$ to $S$ and $\bma$ to $T$:
 \newcommand{\condSimple}{(c1)}

### 2017-10-08 p2/works-inverse.tex
Symbol for sequences from sets; improvements

@@
 where they are not defined:
-\[ \forall\FS,\GS,\alpha: \FS\T\neq\GS\T \wedge \alpha\T(\FS\T)\neq\fsbroken \Longrightarrow \alpha\T(\FS\T) \neq \alpha\T(\GS\T). \]
+\begin{align*}
+\forall\FS,\GS,\alpha:& \\
+& \FS\T\neq\GS\T \wedge \alpha\T(\FS\T)\neq\fsbroken \\
+& \Rightarrow \alpha\T(\FS\T) \neq \alpha\T(\GS\T).
+\end{align*}
 \end{mylem}
@@
 \begin{mylem}\label{r_invmove}
-A common initial segment of a set of \emph{representative} sequences can be moved 
+A common initial segment of a set of representative sequences can be moved 
 to the other side of $\worksmeqsign$ by inverting it:

### 2017-10-08 p2/rec-sound.tex
Many improvements; \T now has an argument

@@
 \begin{myth}\label{reconciliation_correct}
-If $A$ and $B$ are simple, then $\worksmbb{A,B}{B\cc \reca}$,
+If $A$ and $B$ are simple, then $\worksmbx{A,B}{B\cc \reca}$,
 where, to restate \cref{def:reconciliation},
@@
 either of them is defined on:
-$\worksm{A}{\ordp{\acbnp}}$, and, by symmetry,
-$\worksm{B}{\ordp{\acbnp}}$.
+$\worksm{A}{\acb}$, and, by symmetry,
+$\worksm{B}{\acb}$.
 \end{mylem}
@@
 \noindent
-We would like to prove that $\worksmbb{A,B}{B\cc \reca}$.
+We would like to prove that $\worksmbx{A,B}{B\cc \reca}$.
 From the above we know that we can move commands in $\acbnp$
 to the beginning of $B$ and so this is equivalent to
-\[ \worksmbb{A,B}{\acb\cc \bma\cc \reca}. \]
+\[ \worksmbx{A,B}{\acb\cc \bma\cc \reca}. \]
 We can prove this if we can show that
-\[ \worksmbb{A,B}{\acb\cc \reca}. \]
+\[ \worksmbx{A,B}{\acb\cc \reca}. \]
 This is because we already know
-that $\worksmbb{A,B}{\acb\cc \bma}$ (as $\worksmbb{A,B}{B}$),
+that $\worksmbx{A,B}{\acb\cc \bma}$ (as $\worksmbx{A,B}{B}$),
 which, combined with the above, yields
@@
 we know
-\[ \worksmbb{\acb\cc \reca, \acb\cc \bma}{\acb\cc \bma\cc \reca}. \]
+\[ \worksmbx{\acb\cc \reca, \acb\cc \bma}{\acb\cc \bma\cc \reca}. \]
 As $\worksmeqsign$ is transitive, combining the two results
@@
 then
-\[ \worksmxb{\sqs{C}}{S^*}. \]
+\[ \worksm{\sqs{C}}{S^*}. \]
 \end{mylem}
@@
 If so, then 
-$\worksmxb{\sqs{C}}{S^*}$ 
+$\worksm{\sqs{C}}{S^*}$ 
 based on \cref{worksextpostfix}
-as $\worksmxb{\sqs{C}}{S'}$ and $S'=S^*\cc S_0$ 
+as $\worksm{\sqs{C}}{S'}$ and $S'=S^*\cc S_0$ 
 where $S_0$ contains the remaining (conflicting) commands.
@@
 and the preceding unmarked command be $\czwmv$.
-As $S$ is simple and $\worksmnilb{S}$, from 
+As $S$ is simple and $\wrks{S}$, from 
 \cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}

### 2017-10-08 p2/works-inverse.tex
Many improvements; \T now has an argument

@@
 and $\sqs{A}\cc\sqs{B}$ for $\{A\cc B\whr A\in\sqs{A}, B\in\sqs{B}\}$.
-We will also use $A\cc\sqs{B}$ with the meaning $\{A\}\cc\sqs{B}$.
 
@@
 
-In a sense, $A\worksmeqsign B$ is a weaker counterpart of $A\eqext B$, as the former
+When $\sqs{A}$ or $\sqs{B}$ contains a single sequence,
+we leave out the curly brackets and write,
+e.g. $A\cc\sqs{B}$ to mean $\{A\}\cc\sqs{B}$,
+or $\worksm{A}{B}$ to mean $\worksmbb{A}{B}$.
+
+We can see that $A\eqext B$ implies $\worksm{A}{B}$, as the latter
 only requires that $B$ is defined where $A$ is defined, 
-while the latter also requires
+while the former also requires
 that where they are defined, their effect is the same.
-It is easy to see that the following corollary is true:
 
-\begin{mycor}\label{worksextpostfix}
+The following claim follows immediately from the definition:
+
+\begin{myclm}\label{worksextpostfix}
 % An inference rule in the algebra
 $\forall A,S: \worksm{A\cc S}{A}$, that is, if a sequence is defined,
-its initial segment is also defined.
-\end{mycor}
+its initial segments are also defined.
+\end{myclm}
 
@@
 where both of the commands are defined:
-\[ \alpha\indep \beta \Rightarrow \worksm{\{\alpha, \beta\}}{\{\alpha\cc \beta\}}. \]
+\[ \alpha\indep \beta \Rightarrow \worksmbx{\alpha, \beta}{\alpha\cc \beta}. \]
 \end{myax}
@@
 Let $\alpha=\cxynv$ and $\beta=\czwmv$.
-We prove the proposition by contradiction and
+The proof is by contradiction;
 assume that there is a filesystem $\FS$ for which
@@
 
-This result can be extended to sequences:
+\cref{combine_independent_commands} extends to sequences as well:
 
@@
 where both of the sequences are defined:
-\[ S\indep T \Rightarrow \worksm{\{S,T\}}{\{S\cc T\}}. \]
+\[ S\indep T \Rightarrow \worksmbx{S,T}{S\cc T}. \]
 \end{mylem}
@@
 \begin{mylem}\label{worksinputmatch}
-If $S$ and $T$ are minimal sequences, $\worksmnil{\{A,B\}}$,
+If $S$ and $T$ are minimal sequences, $\worksmnilb{S,T}$,
 and there are commands on node $n$ in both $S$ ($\cxynv\in A$) and $T$ ($\czwnv\in B$),
-then the input types of these commands must match ($[x]=[z]$).
+then the input types of these commands must match, i.e. $[x]=[z]$.
 \end{mylem}
@@
 \begin{itemize}
-\item For two filesystems $\FS\typeeq\GS$ iff they share the same nodes $\setn$,
-and for all $n\in\setn$, $\FS(n) \typeeq \GS(n)$.
+\item For two filesystems in $\setfs$, $\FS\typeeq\GS$ iff
+for all $n\in\setn$, $\FS(n) \typeeq \GS(n)$.
 \item For two commands $\cxynv\typeeq\czwmv$ iff 
@@
 and $n=m$.
-\item For two sequences of commands $\emptyseq\typeeq\emptyseq$, and
+\item To sequences of commands, the relation $\typeeq$ extends as usual: $\emptyseq\typeeq\emptyseq$, and
 if $A'=\alpha\cc A$ and $B'=\beta\cc B$, then $A'\typeeq B'$ iff $\alpha\typeeq\beta$ and $A\typeeq B$.
@@
 
-We select representatives of each $\typeeq$-equivalence class of values:
+We select representatives from each $\typeeq$-equivalence class of values:
 for $[\empt]$ and $[\vald]$ this must be $\empt$ and $\vald$; and
@@
 We then use these representative values to
-introduce the canonical mapping $\T$ that preserves the types of values,
+introduce the \emph{canonical mapping} $\T{}$ that preserves the types of values,
 but maps all objects into a subsystem where there is a one-to-one
@@
 
-\begin{mydef}[$\T$]\label{def_typemapping}
-We use $\T$ and write $a\T$ to denote the canonical mapping of 
+\begin{mydef}[canonical mapping, $\T{}$]\label{def_typemapping}
+We use $\T{}$ and write $\T{a}$ to denote the canonical mapping of 
 values, filesystems, commands and sequences to the
@@
 \begin{itemize}
-\item For values, $\vald\T=\vald$, $\valf\T=\fil$ and $\empt\T=\empt$.
-\item For filesystems, $\FS\T$ is defined by $\FS\T(n) = \FS(n)\T$.
-\item For commands, $\cbrk\T=\cbrk$ and $\cxynv\T = \cTxynv$.
-\item For sequences of commands, $\emptyseq\T=\emptyseq$, and if $S'=\alpha\cc S$, then $S'\T=\alpha\T\cc S\T$.
-\item Finally we extend $\T$ to sets of sequences: $\sqs{A}\T = \{S\T \whr S\in\sqs{A}\}$.
+\item For values, $\T{\vald}=\vald$, $\T{\valf}=\fil$ and $\T{\empt}=\empt$.
+\item For filesystems, $\T{\FS}$ is defined by $\T{\FS}(n) = \T{\FS(n)}$.
+\item For commands, $\T{\cbrk}=\cbrk$ and $\T{\cxynv} = \cTxynv$.
+\item To sequences of commands, the mapping extends as usual: $\T{\emptyseq}=\emptyseq$, and if $S'=\alpha\cc S$, then $\T{S'}=\T{\alpha}\cc \TS$.
+\item Finally we extend $\T{}$ to sets of sequences: $\T{\sqs{A}} = \{\TS \whr S\in\sqs{A}\}$.
 \end{itemize}
@@
 
+We refer to any object in the image of $\T{}$ as \emph{canonical}.
+
 By definiton,
 for any filesystem $\FS$ and command $\alpha$, 
-$\alpha\T(\FS\T) = (\alpha\aFS)\T$.
+$\T{\alpha}(\T{\FS}) = \T{(\alpha\aFS)}$.
 
 % TODO ???
-Also, for all objects where it is defined, $a\T\typeeq a$.
-As representatives of filesystems, commands, sequences, etc.
-are subsets of their non-representative counterparts, 
+Also, for all objects where it is defined, $\T{a}\typeeq a$.
+As canonical filesystems, commands, sequences, etc.
+are subsets of their non-canonical counterparts, 
 all propositions proven so far apply to them as well.
 
-% It is easy to see that 
-% $A\equiv B \Rightarrow A\T\equiv B\T$ 
-% and
-% $A\eqext B \Rightarrow A\T\eqext B\T$,
-% but the reverse is not true as 
-% $A\T$ and $B\T$ will have the same effect on all filesystems
-% if $A$ and $B$ differ only in some of the values in their commands,
-% whereas clearly $A\nequiv B$.
-
 As the types of values determine whether a command breaks a filesystem,
-we know $\Dom{A}=\Dom{A\T}$ and therefore $\Dom{\sqs{A}}=\Dom{\sqs{A}\T}$.
+we know $\Dom{A}=\Dom{\TA}$ and therefore $\Dom{\sqs{A}}=\Dom{\T{\sqs{A}}}$.
 From this it follows that
 % TODO what's the set of all filesystems?
-
+% TODO:
 \begin{mycor}\label{repr_works_is_same}
 \begin{gather*}
-\worksmnil{\sqs{A}} \Longleftrightarrow \worksmnil{\sqs{A}\T} \\
-\worksm{\sqs{A}}{\sqs{B}} \Longleftrightarrow \worksm{\sqs{A}\T}{\sqs{B}\T}.
+\worksmnil{\sqs{A}} \Longleftrightarrow \worksmnil{\T{\sqs{A}}} \\
+\worksm{\sqs{A}}{\sqs{B}} \Longleftrightarrow \worksm{\T{\sqs{A}}}{\T{\sqs{B}}}.
 \end{gather*}
@@
 
-We are now ready to define the inverse of representative commands $\alpha\T$
+We are now ready to define the inverse of canonical commands $\T{\alpha}$
 which allows us to move parts of sequences between the
@@
 \begin{mylem}\label{repr_comm_inject}
-Representative commands $\alpha\T$ are partial bijections over representative filesystems
-($\FS\T$, $\GS\T$).
+Canonical commands $\T{\alpha}$ are partial bijections over canonical filesystems
+($\T{\FS}$, $\T{\GS}$).
 Because partial functions are trivially surjective when restricted to their images, this is
-equivalent to saying that representative functions are injective except for cases
+equivalent to saying that canonical functions are injective except for cases
 where they are not defined:
@@
 \forall\FS,\GS,\alpha:& \\
-& \FS\T\neq\GS\T \wedge \alpha\T(\FS\T)\neq\fsbroken \\
-& \Rightarrow \alpha\T(\FS\T) \neq \alpha\T(\GS\T).
+& \T{\FS}\neq\T{\GS} \wedge \T{\alpha}(\T{\FS})\neq\fsbroken \\
+& \Rightarrow \T{\alpha}(\T{\FS}) \neq \T{\alpha}(\T{\GS}).
 \end{align*}
@@
 \begin{proof}
-Choose values that satisfy the left side, and let $\alpha\T = \cTxynv$.
-If $\FS\T$ and $\GS\T$ have different values (types) at any node apart from $n$, then this difference remains
-even after applying $\cTxynv$ to $\FS\T$. 
+Choose values that satisfy the left side, and let $\T{\alpha} = \cTxynv$.
+If $\T{\FS}$ and $\T{\GS}$ have different values (types) at any node apart from $n$, then this difference remains
+even after applying $\cTxynv$ to $\T{\FS}$. 
 The only remaining case therefore is where they have the same values
 at all nodes except at $n$.
-As $\cTxynv(\FS\T)\neq\fsbroken$, we know $[\FS(n)]=[x]$.
-We also know that $\GS\T(n)\neq\FS\T(n)$, and therefore
+As $\cTxynv(\T{\FS})\neq\fsbroken$, we know $[\FS(n)]=[x]$.
+We also know that $\T{\GS}(n)\neq\T{\FS}(n)$, and therefore
 $[\GS(n)]\neq[x]$.
-This implies $\cTxynv(\GS\T)=\fsbroken$,
-and again we have $\alpha\T(\FS\T) \neq \alpha\T(\GS\T)$.
+This implies $\cTxynv(\T{\GS})=\fsbroken$,
+and again we have $\T{\alpha}(\T{\FS}) \neq \T{\alpha}(\T{\GS})$.
 \end{proof}
@@
 \begin{mydef}[Inverse commands and sequences]
-We write $\alpha\T^{-1}$ for
-the inverse of the representative command (partial bijection) $\alpha\T$.
+We write $\T{\alpha}^{-1}$ for
+the inverse of the canonical command (partial bijection) $\T{\alpha}$,
+which is uniquely defined by \cref{repr_comm_inject}.
 
-We write ${S\T}^{-1}$ for the inverse of the sequence $S\T$, which consists of the inverses of the commands in $S\T$
-in reverse order.
+We write $\TS^{-1}$ for the inverse of the sequence $\TS$, which consists of the inverses of the commands in $\TS$ in reverse order.
 \end{mydef}
-By definition, for any representative filesystem $\FS\T$ outside the image of $\alpha\T$, the inverse $\alpha\T^{-1}$ is not defined.
+By definition, for any canonical filesystem $\T{\FS}$ outside the image of 
+$\T{\alpha}$, the inverse $\T{\alpha}^{-1}$ is not defined.
 
 % Some further observations:
-% For representative commands \[ \cTxynv^{-1} = \cTyxnv. \]
-% $\forall S: ({S\T}^{-1})^{-1} = S\T$.
+% For canonical commands \[ \cTxynv^{-1} = \cTyxnv. \]
+% $\forall S: ({\TS}^{-1})^{-1} = \TS$.
 
 For brevity, in the following lemma we use $B$, $B'$, $\sqs{A}$ and $\sqs{C}$ to denote
-representative sequences and sets.
+canonical sequences and sets.
 
@@
 \begin{mylem}\label{r_invmove}
-A common initial segment of a set of representative sequences can be moved 
+A common initial segment of a set of canonical sequences can be moved 
 to the other side of $\worksmeqsign$ by inverting it:
@@
 from $\worksm{\ia}{B\cc\ic}$ we know $\Dom{\ia} \subseteq \Dom{B\cc\ic}$.
-As the (representative) $B$ is a bijection between its domain and image,
+As the (canonical) $B$ is a bijection between its domain and image,
 we can use $B$ to map both sides of this statement, which yields
@@
 which means that $\worksm{\ibi\cc\ia}{\ic}$.
-It is easy to see that $\worksm{\ia}{B\cc\ic} \Rightarrow \worksm{\ia}{\{B\}}$.
+It is easy to see that $\worksm{\ia}{B\cc\ic} \Rightarrow \worksm{\ia}{B}$.
 
 For the right-to-left part,
-from $\worksm{\ia}{\{B\}}$ we know $\Dom{\ia} \subseteq \Dom{B}$.
-Therefore we can project the whole of $\Dom{\ia}$ using the bijective representative sequence $B$
+from $\worksm{\ia}{B}$ we know $\Dom{\ia} \subseteq \Dom{B}$.
+Therefore we can project the whole of $\Dom{\ia}$ using the bijective canonical sequence $B$
 to get $\Dom{\ibi\cc\ia}$, and as $\worksm{\ibi\cc\ia}{\ic}$
@@
 is defined wherever the two sequences are defined:
-\[ B\indep C \Rightarrow \worksmbb{A\cc B, A\cc C}{A\cc B\cc C} \]
+\[ B\indep C \Rightarrow \worksmbx{A\cc B, A\cc C}{A\cc B\cc C} \]
 \end{mylem}
@@
 From $B\indep C$ and \cref{combine_independent_sequences} we know
-$\worksmbb{B, C}{B\cc C}$.
+$\worksmbx{B, C}{B\cc C}$.
 Based on \cref{repr_works_is_same} this is equivalent to
-$\worksmbb{B\T, C\T}{B\T\cc C\T}$.
-Since $A\T^{-1}\cc A\T \equiv \emptyseq$, this can also be written as
-\[\worksmxb{A\T^{-1}\cc\{A\T\cc B\T, A\T\cc C\T\}}{B\T\cc C\T}.\]
+$\worksmbx{\TB, \TC}{\TB\cc \TC}$.
+Since $\TA^{-1}\cc \TA \equiv \emptyseq$, this can also be written as
+\[\worksm{\TA^{-1}\cc\{\TA\cc \TB, \TA\cc \TC\}}{\TB\cc \TC}.\]
 From \cref{worksextpostfix} we also know that
-$\worksmbb{A\T\cc B\T, A\T\cc C\T}{A\T}$.
+$\worksmbx{\TA\cc \TB, \TA\cc \TC}{\TA}$.
 Combining the last two statements using \cref{r_invmove}
 we get
-\[ \worksmbb{A\T\cc B\T, A\T\cc C\T}{A\T\cc B\T\cc C\T}, \]
+\[ \worksmbx{\TA\cc \TB, \TA\cc \TC}{\TA\cc \TB\cc \TC}, \]
 which with \cref{repr_works_is_same} proves the

### 2017-10-14 p2/ordering.tex
New proof for the correctness of reconciliation

@@
 
-\begin{mycor}\label{subseq_in_orderset}
+\begin{myclm}\label{subseq_in_orderset}
 For simple sequences $S$ and $T$,
@@
 $T_0\in\orderset{S_0}$ must hold.
-\end{mycor}
+\end{myclm}
 \begin{proof}
@@
 if $\cxynv\cc\czwmv$ is a subsequence of $S$ and $n=\parent(m)$ or $\parent(n)=m$,
-then $\wrksx{\cxynv\cc\czwmv}$.
+then $\cxynv\cc\czwmv$ is either a construction or a destruction pair.
 \end{mylem}
@@
 Therefore $[S_0\FS(m)]=[z]=[\empt]$, which, combined with $y=\vald$
-means that $\wrksx{\cxynv\cc\czwmv}$ is a construction pair, which is a contradiction.
+means that $\cxynv\cc\czwmv$ is a construction pair, which is a contradiction.
 
@@
 Therefore $[S_0\FS(m)]=[z]=[\vald]$, which, combined with $y=\empt$
-means that $\wrksx{\cxynv\cc\czwmv}$ is a destruction pair, which is a contradiction.
+means that $\cxynv\cc\czwmv$ is a destruction pair, which is a contradiction.
 \end{proof}
@@
 \end{mycor}
-
-TODO TODO TODO:
-It follows from this that given a simple set,
-we can simply assume that it has an order.
-Accordingly, we will at times treat not only sequences as sets,
-but simple sets as sequences.

### 2017-10-14 p2/rec-sound.tex
New proof for the correctness of reconciliation

@@
 that is, applying its result is not going to break the replicas.
-We reformulate the original proposition, $\reca\aFS_B\neq\fsbroken$,
-based on $\FS_B=B\aFS$ and so we aim to prove that
+We reformulate the original proposition ($\reca\aFS_B\neq\fsbroken$)
+based on $\FS_B=B\aFS$, and so we aim to prove that
 $B\cc\reca$ is defined wherever $A$ and $B$ are defined:
@@
 
-We show that $A$ can be transformed via equivalences into $A'$ for which it is true.
-Our proposition is that if the marked commands are not at the beginning, then
+We show that $A$ can be transformed via equivalences into $A'$ for which this is true.
+We know that if the marked commands are not at the beginning, then
 the sequence contains an unmarked command followed by a marked command.
 We show that these can be swapped resulting in an equivalent sequence.
-Then, by repeating this process similarly to bubble sorting, we can generate 
+Then, by repeating this process similarly to bubble sorting, we arrive at 
 a suitable $A'$.
@@
 As $A$ is simple and $\wrks{A}$, from 
-\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
+\cref{ax_distantrel_breaks,simple_distant_pairs}
 we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
@@
 
-In these cases, either $m=\parent(n)$ or $n=\parent(m)$.
-If $B$ has a command on $m$, then
--- TODO TODO TODO --
-from \cref{lemma:neighbor}
-we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxynv$ (also in $B$),
-and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
--- TODO TODO TODO --
-When describing our ordering algorithm in \cref{ordering} we saw
-that the command on the parent path determines whether a pair of commands
-is a construction or destruction pair,
-and that this, in turn, determines whether the command on the child path must
-precede or follow the other command as otherwise the sequence would break all filesystems.
-This argument holds for both $A$ and $B$, and so the command on $m$ must be on
-the same side of the command on $n$ in both sequences.
+In the cases then $\czmwv\cc\cxynv$ is either a construction or a destruction pair,
+and, depending on which is the case,
+$m=\parent(n)$ or $n=\parent(m)$, respectively.
+
+If $B$ has a command on $m$, let it be $\cqrmv$.
+As \cref{simple_distant_pairs} applies to $B$, we know that
+$\cxynv$ (which is in $B$), and $\cqrmv$ must also form a construction
+or destruction pair.
+As $\cxynv$ cannot be both a construction and a destruction command,
+this pair must be of the same type as $\czmwv\cc\cxynv$,
+and as the relationship between $n$ and $m$ is given,
+we know $\cqrmv$ must precede $\cxynv$ in $B$.
+
+Because the output value of the first command in construction
+and destruction pairs is determined by the type of the pair,
+$r=w$.
+Also, as $\worksmnilb{A,B}$, 
+from \cref{worksinputmatch}
+we know that $[q]=[z]$.
+Therefore $\cqrmv=\czwmv$,
+which is a contradiction as $\czwmv$ was not marked,
+but we see it must also be in $B$.
+
+The last remaining case is when there is no command on $m$ in $B$.
+TODO
+TODO
+
+OLD:
 
@@
 
-As $\worksmnilb{A,B}$ and so $\worksmnilb{A,B'}$, 
-from \cref{worksinputmatch}
-we know that $[q]=[z]$.
-
 Going back to the construction and destruction pairs we see that the output value of the first command
 is either $\vald$ or $\empt$ and is determined by the relationship between $n$ and $m$.
-Therefore $r=w$ and $\cqrmv=\czwmv$.
-If $B$ originally had a command on $m$,
-this is a contradiction as $\czwmv$ was not marked, but we see it must also be in $B'$ and therefore in $B$.
 If $B$ had no command on $m$,
@@
 from \cref{worksextpostfix} we know that
-$\worksm{A}{\acb}$ and by symmetry $\worksm{B}{\acb}$.
+$\worksm{A}{\acb}$ and, by symmetry, $\worksm{B}{\acb}$.
 \end{proof}

### 2017-10-15 p2/rec-sound.tex
Finished first part of proof

@@
 \begin{mylem}\label{can_move_intersection}
-Let $A$ and $B$ be two simple sequences so that $\worksmnilb{A, B}$.
-Then their intersection is also defined on any filesystem
-either of them is defined on:
-$\worksm{A}{\acb}$, and, by symmetry,
-$\worksm{B}{\acb}$.
+Let $A$ and $B$ be two simple sequences for which $\worksmnilb{A, B}$.
+Then $A$ can be separated into their intersection and the remaining commands:
+\[ \acb\cc\amb \in \orderset{A}. \]
 \end{mylem}
@@
 \begin{proof}
-The difficulty is that commands in $\acbnp$ can occur anywhere in $A$.
-Therefore, first we prove the following:
+We prove that
 if all commands are marked in $A$ that also appear in $B$,
@@
 
-We show that $A$ can be transformed via equivalences into $A'$ for which this is true.
+We show that $A$ can be transformed into $A'$ for which this is true.
 We know that if the marked commands are not at the beginning, then
@@
 Then, by repeating this process similarly to bubble sorting, we arrive at 
-a suitable $A'$.
+a suitable permutation of $A$, which is also equivalent to $A$, and therefore in $\orderset{A}$.
 
@@
 
-In the cases then $\czmwv\cc\cxynv$ is either a construction or a destruction pair,
+In the cases then $\czwmv\cc\cxynv$ is either a construction or a destruction pair,
 and, depending on which is the case,
@@
 As $\cxynv$ cannot be both a construction and a destruction command,
-this pair must be of the same type as $\czmwv\cc\cxynv$,
+this pair must be of the same type as $\czwmv\cc\cxynv$,
 and as the relationship between $n$ and $m$ is given,
@@
 The last remaining case is when there is no command on $m$ in $B$.
-TODO
-TODO
-
-OLD:
-
-If $B$ has no command on $m$, then let $B'$ be $B$, 
-but with an extra command added to it just before $\cxynv$
+Let $B'$ be $B$
+with an extra assertion command added just before $\cxynv$
 according to \cref{ax_child_assert,ax_parent_assert}, 
 from which we know that $B'\equiv B$.
-We also know that $B'$ is still minimal (but no longer simple).
-
-In either case, therefore,
-we have a minimal $B'$ which has a command on $m$ just before $\cxynv$ and $B'\equiv B$.
-Let this command on $m$ be $\cqrmv$.
-\begin{gather*}
-A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
-B' = \cdots\cc  \cqrmv\cc  \cxynv\cc  \cdots
-\end{gather*}
-
-Going back to the construction and destruction pairs we see that the output value of the first command
-is either $\vald$ or $\empt$ and is determined by the relationship between $n$ and $m$.
-If $B$ had no command on $m$,
-this is a contradiction because the command on $m$ in $B'$ is an assertion command, so $[z]=[q]=[r]=[w]$, 
-but $A$ contained no assertion commands.
-
-We now know that there is an $A'\equiv A$ in which commands in $\acbnp$
-are at the beginning, and therefore 
-from \cref{worksextpostfix} we know that
-$\worksm{A}{\acb}$ and, by symmetry, $\worksm{B}{\acb}$.
+Let the new command be $\cqrmv$.
+As $B'$ is still minimal (but no longer simple),
+the argument above applies, and we again know
+that $[q]=[z]$ and $r=w$.
+As $\cqrmv$ is an assertion command, $[q]=[r]$ also holds,
+from which $[z]=[w]$ (as $[z]=[q]=[r]=[w]$), which is a contradiction
+as $A$ contains no assertion commands.
 \end{proof}
@@
 
-% TODO Set or sequence? See also above
-
 \noindent
 We would like to prove that $\worksmbx{A,B}{B\cc \reca}$.
-From the above we know that we can move commands in $\acbnp$
+From \cref{can_move_intersection} above we know that we can move commands in $\acbnp$
 to the beginning of $B$ and so this is equivalent to
@@
 \[ \worksmbx{\acb\cc \reca, \acb\cc \bma}{\acb\cc \bma\cc \reca}. \]
-As $\worksmeqsign$ is transitive, combining the two results
-gives the statement we intended to prove.
+As $\worksmeqsign$ is transitive, combining the two statement above
+gives $\worksmbx{A,B}{B\cc \reca}$, which is what we intend to prove.
 
-To restate some results above, we therefore already know the following things:
+\bigskip
+
+\noindent
+To restate some results above, we therefore already know the following:
 \begin{itemize}
@@
 and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
+TODO HOW IS THIS USED?
 \end{itemize}
@@
 Our theorem is therefore proven if we prove the following lemma,
-in which we rename $\amb$ to $S$ and $\bma$ to $T$:
+in which we rename $\amb$ to $S$, $\reca$ to $S^*$, and $\bma$ to $T$:
 \newcommand{\condSimple}{(c1)}
@@
 We mark all commands in $S$ that are in its subset $S^*$, and
-we prove that $S$ can be transformed into $S'$ via equivalences
+we prove that $S$ can be transformed into $S'$
 so that all marked commands would be at its beginning.
@@
 As $S$ is simple and $\wrks{S}$, from 
-\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
+\cref{ax_distantrel_breaks,simple_distant_pairs}
 we know that these commands can only be on incomparable nodes or form a construction or destruction pair.

### 2017-10-15 p2/rec-sound.tex
Inverses are no longer needed

@@
 From \cref{can_move_intersection} above we know that we can move commands in $\acbnp$
-to the beginning of $B$ and so this is equivalent to
-\[ \worksmbx{A,B}{\acb\cc \bma\cc \reca}. \]
-We can prove this if we can show that
-\[ \worksmbx{A,B}{\acb\cc \reca}. \]
-This is because we already know
-that $\worksmbx{A,B}{\acb\cc \bma}$ (as $\worksmbx{A,B}{B}$),
-which, combined with the above, yields
-\[ \worksmbb{A,B}{\acb\cc \reca, \acb\cc \bma}. \]
-Also, as $\reca\indep\bma$,
-from \cref{indep_prefix_combine}
+to the beginning of $A$ and $B$, and so this is equivalent to
+\[ \worksmbx{\acb\cc\amb, \acb\cc\bma}{\acb\cc \bma\cc \reca}, \]
+which is equivalent to
+\[ \worksmbx{\amb, \bma}{\bma\cc \reca}. \]
+
+For ease of reading, let us rename
+$\amb$ to $S$,
+$\reca$ to $S^*$,
+and $\bma$ to $T$.
+In this notation, we intend to prove that
+\[ \worksmbx{S,T}{T\cc S^*}. \]
+We can do so if we can show that
+\[ \worksmbx{S,T}{S^*}. \]
+
+This is because 
+$\worksmbx{S,T}{T}$ is trivially true, and this, combined with the above,
+yields 
+$ \worksmbb{S,T}{S^*,T}. $
+As $\reca\indep\bma$, that is, $S^*\indep T$,
+from \cref{combine_independent_sequences}
 we know
-\[ \worksmbx{\acb\cc \reca, \acb\cc \bma}{\acb\cc \bma\cc \reca}. \]
-As $\worksmeqsign$ is transitive, combining the two statement above
-gives $\worksmbx{A,B}{B\cc \reca}$, which is what we intend to prove.
+$ \worksmbx{S^*,T}{T\cc S^*}, $
+and as $\worksmeqsign$ is transitive, combining the two statements above
+gives $\worksmbx{S,T}{T\cc S^*}$.
 
 \bigskip
+
+TODO TODO TODO TODO TODO
 

### 2017-10-15 p2/unused.tex
Inverses are no longer needed

--- 2017-10-08 p2/works-inverse.tex
@@
-% Works
-% -----
-
-\subsection{Domains and Inverse Sequences}
-
-\begin{mydef}[Sets of sequences]
-As we will frequently refer to sets of fequences,
-we will use calligraphic letters (e.g. $\sqs{A}$, $\sqs{B}$, $\sqs{C}$ and $\sqs{S}$)
-to denote such sets for brevity.
-
-We will write $\Dom{\sqs{A}}$ for $\bigcap_{A\in\sqs{A}} \Dom{A}$,
-and $\sqs{A}\cc\sqs{B}$ for $\{A\cc B\whr A\in\sqs{A}, B\in\sqs{B}\}$.
-
-% This has only been defined for sequences, not sets.
-Moreover, we write $\wrks{\sqs{A}}$ if $\varnothing \subset \Dom{\sqs{A}}$, that is,
-if we know that there is at least one filesystem
-all sequences in $\sqs{A}$ are defined on.
-\end{mydef}
-
-% works operators
-% ---------------
-
-\begin{mydef}[$\worksmeqsign$]\label{def_works}
-For two sets of sequences $\sqs{A}$ and $\sqs{B}$
-we write $\worksm{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subseteq \Dom{\sqs{B}}$;
-that is, iff all sequences in $\sqs{B}$ are defined on (do not break)
-all filesystems on which sequences in $\sqs{A}$ are defined.
-
-We also apply these relations to sequences directly;
-e.g. we write
-$\worksm{A}{B}$ with the meaning $\Dom{A} \subseteq \Dom{B}$.
-\end{mydef}
-
-When $\sqs{A}$ or $\sqs{B}$ contains a single sequence,
-we leave out the curly brackets and write,
-e.g. $A\cc\sqs{B}$ to mean $\{A\}\cc\sqs{B}$,
-or $\worksm{A}{B}$ to mean $\worksmbb{A}{B}$.
-
-We can see that $A\eqext B$ implies $\worksm{A}{B}$, as the latter
-only requires that $B$ is defined where $A$ is defined, 
-while the former also requires
-that where they are defined, their effect is the same.
-
-The following claim follows immediately from the definition:
-
-\begin{myclm}\label{worksextpostfix}
-% An inference rule in the algebra
-$\forall A,S: \worksm{A\cc S}{A}$, that is, if a sequence is defined,
-its initial segments are also defined.
-\end{myclm}
-
-We also prove the following lemmas.
-
-\begin{myax}\label{combine_independent_commands}
-The combination of independent commands is defined on all filesystems
-where both of the commands are defined:
-\[ \alpha\indep \beta \Rightarrow \worksmbx{\alpha, \beta}{\alpha\cc \beta}. \]
-\end{myax}
-\begin{proof}
-We name this proposition a \namecref{combine_independent_commands} 
-because to prove it, we must reach back to our filesystem model.
-Let $\alpha=\cxynv$ and $\beta=\czwmv$.
-The proof is by contradiction;
-assume that there is a filesystem $\FS$ for which
-$\cxynv\aFS\neq\fsbroken$ and $\czwmv\aFS\neq\fsbroken$, but
-$\cxynv\cc \czwmv\aFS=\fsbroken$.
-We know $\cxynv\aFS\neq\fsbroken$ so it must be applying 
-$\czwmv$ that breaks it.
-Applying a command can only result in a broken filesystem in two cases.
-First, if the input type does not match the filesystem,
-but we know $[\FS(m)]=[w]$ and so
-$[(\cxynv\aFS)(m)]=[w]$ as based on \cref{incomparable_is_independent}, $n\neq m$.
-Second, if the new filesystem violates the tree property.
-This again cannot be the case because we also know that $n\unrel m$
-and the tree property only depends on the types of values at the parent and children of $m$,
-which therefore cannot be changed by $\cxynv$.
-\end{proof}
-
-\cref{combine_independent_commands} extends to sequences as well:
-
-\begin{mylem}\label{combine_independent_sequences}
-The combination of independent sequences is defined on all filesystems
-where both of the sequences are defined:
-\[ S\indep T \Rightarrow \worksmbx{S,T}{S\cc T}. \]
-\end{mylem}
-\begin{proof}
-Assume that there is a filesystem $\FS$ so that
-$S\aFS\neq\fsbroken$ and $T\aFS\neq\fsbroken$, but
-$(S\cc T)\FS=\fsbroken$.
-
-From \cref{def_indep} we know that
-the commands in $S$ and $T$ pairwise commute, and so any sequence
-that contains the commands from $S$ and $T$ and preserve their original partial order
-is equivalent to $S\cc T$ on all filesystems.
-
-Let the command in $T$ that breaks $\FS$ when applying $S\cc T$ be $t$
-so that $T=T_0\cc t\cc T_1$.
-It is still true that $(T_0 \cc t)\FS\neq\fsbroken$,
-and by definition $(S\cc T_0)\FS\neq\fsbroken$,
-but $(S\cc T_0\cc t)\FS=\fsbroken$.
-Also, from above we know that $S\cc T_0\equiv T_0\cc S$
-and so $(T_0 \cc S)\FS\neq\fsbroken$.
-
-If we denote the first command in $S$ with $s_1$,
-this means that $(T_0 \cc s_1)\FS\neq\fsbroken$,
-which we can combine with $(T_0 \cc t)\FS\neq\fsbroken$, $t\indep s_1$ and
-\cref{combine_independent_commands}
-(using $T_0\FS$ as the reference filesystem)
-to arrive at $(T_0 \cc s_1\cc t)\FS\neq\fsbroken$.
-
-We can repeat this step for $s_2$, the next command in $S$,
-and from 
-$(T_0 \cc s_1\cc t)\FS\neq\fsbroken$
-and
-$(T_0 \cc s_1\cc s_2)\FS\neq\fsbroken$
-arrive at
-$(T_0 \cc s_1\cc s_2\cc t)\FS\neq\fsbroken$.
-This can be repeated until $S$ is exhausted and we get
-$(T_0 \cc S\cc t)\FS\neq\fsbroken$, which is a contradiction.
-\end{proof}
-
-We also prove the following:
-
-\begin{mylem}\label{worksinputmatch}
-If $S$ and $T$ are minimal sequences, $\worksmnilb{S,T}$,
-and there are commands on node $n$ in both $S$ ($\cxynv\in A$) and $T$ ($\czwnv\in B$),
-then the input types of these commands must match, i.e. $[x]=[z]$.
-\end{mylem}
-\begin{proof}
-This result is similar to \cref{equiv_simple_same_commands} and
-is easily shown using a proof by contradiction: if $[x]\neq [z]$, then there is no filesystem that
-either $\cxynv$ or $\czwnv$ would not break, 
-and consequently $S$ and $T$ cannot work on the same filesystem.
-\end{proof}
-
-\bigskip
+\section{UNUSED RESULTS}
 
@@
 
-% TODO \alpha \neq \cbrk
 \begin{mylem}\label{repr_comm_inject}
@@
 \ \Longleftrightarrow \ \worksm{\ibi\cc\ia}{\ic} 
-\ \wedge \  \worksm{\ia}{\{B\}}
+\ \wedge \  \worksm{\ia}{B}
 \end{gather*}
@@
 is defined wherever the two sequences are defined:
+% Use A\cc\{B,C\}
 \[ B\indep C \Rightarrow \worksmbx{A\cc B, A\cc C}{A\cc B\cc C} \]

### 2017-10-15 p2/works-inverse.tex
New proof for the correctness of reconciliation
Finished first part of proof
Inverses are no longer needed

@@
 
-\subsection{Domains and Inverse Sequences}
+\subsection{Domains of Sets of Sequences}
 
@@
 all filesystems on which sequences in $\sqs{A}$ are defined.
-
-We also apply these relations to sequences directly;
-e.g. we write
-$\worksm{A}{B}$ with the meaning $\Dom{A} \subseteq \Dom{B}$.
 \end{mydef}
@@
 \end{proof}
-
-\bigskip
-
-% Type equivalence classes
-% ------------------------
-
-\noindent
-For the proof of the correctness of the reconciliation algorithm,
-we will also need a way of moving parts of sequences between the two
-sides of the $\worksmeqsign$ relation.
-We can do this based on the observation that commands are bijections
-if we only distinguish between types in our objects.
-To formalise this, we extend type equality ($\typeeq$)
-to filesystems, commands and sequences of commands.
-\begin{mydef}[Equivalence by type, extended: $\typeeq$]
-$ $ % otherwise first list element starts on same line
-\begin{itemize}
-\item For two filesystems in $\setfs$, $\FS\typeeq\GS$ iff
-for all $n\in\setn$, $\FS(n) \typeeq \GS(n)$.
-\item For two commands $\cxynv\typeeq\czwmv$ iff 
-$x\typeeq z$ and $y\typeeq w$
-(that is, $[x]=[z]$ and $[y]=[w]$)
-and $n=m$.
-\item To sequences of commands, the relation $\typeeq$ extends as usual: $\emptyseq\typeeq\emptyseq$, and
-if $A'=\alpha\cc A$ and $B'=\beta\cc B$, then $A'\typeeq B'$ iff $\alpha\typeeq\beta$ and $A\typeeq B$.
-\end{itemize}
-\end{mydef}
-
-We select representatives from each $\typeeq$-equivalence class of values:
-for $[\empt]$ and $[\vald]$ this must be $\empt$ and $\vald$; and
-for $[\valf]$ we select an arbitrary file value $\fil\in[\valf]$.
-We then use these representative values to
-introduce the \emph{canonical mapping} $\T{}$ that preserves the types of values,
-but maps all objects into a subsystem where there is a one-to-one
-correspondence between types and values.
-
-\begin{mydef}[canonical mapping, $\T{}$]\label{def_typemapping}
-We use $\T{}$ and write $\T{a}$ to denote the canonical mapping of 
-values, filesystems, commands and sequences to the
-representatives of their $\typeeq$-equivalence class.
-\begin{itemize}
-\item For values, $\T{\vald}=\vald$, $\T{\valf}=\fil$ and $\T{\empt}=\empt$.
-\item For filesystems, $\T{\FS}$ is defined by $\T{\FS}(n) = \T{\FS(n)}$.
-\item For commands, $\T{\cbrk}=\cbrk$ and $\T{\cxynv} = \cTxynv$.
-\item To sequences of commands, the mapping extends as usual: $\T{\emptyseq}=\emptyseq$, and if $S'=\alpha\cc S$, then $\T{S'}=\T{\alpha}\cc \TS$.
-\item Finally we extend $\T{}$ to sets of sequences: $\T{\sqs{A}} = \{\TS \whr S\in\sqs{A}\}$.
-\end{itemize}
-\end{mydef}
-
-We refer to any object in the image of $\T{}$ as \emph{canonical}.
-
-By definiton,
-for any filesystem $\FS$ and command $\alpha$, 
-$\T{\alpha}(\T{\FS}) = \T{(\alpha\aFS)}$.
-
-% TODO ???
-Also, for all objects where it is defined, $\T{a}\typeeq a$.
-As canonical filesystems, commands, sequences, etc.
-are subsets of their non-canonical counterparts, 
-all propositions proven so far apply to them as well.
-
-As the types of values determine whether a command breaks a filesystem,
-we know $\Dom{A}=\Dom{\TA}$ and therefore $\Dom{\sqs{A}}=\Dom{\T{\sqs{A}}}$.
-From this it follows that
-% TODO what's the set of all filesystems?
-% TODO:
-\begin{mycor}\label{repr_works_is_same}
-\begin{gather*}
-\worksmnil{\sqs{A}} \Longleftrightarrow \worksmnil{\T{\sqs{A}}} \\
-\worksm{\sqs{A}}{\sqs{B}} \Longleftrightarrow \worksm{\T{\sqs{A}}}{\T{\sqs{B}}}.
-\end{gather*}
-\end{mycor}
-
-% Inverse commands
-% ----------------
-
-We are now ready to define the inverse of canonical commands $\T{\alpha}$
-which allows us to move parts of sequences between the
-two sides of $\worksmeqsign$.
-This is based on the following observation.
-
-% TODO \alpha \neq \cbrk
-\begin{mylem}\label{repr_comm_inject}
-Canonical commands $\T{\alpha}$ are partial bijections over canonical filesystems
-($\T{\FS}$, $\T{\GS}$).
-Because partial functions are trivially surjective when restricted to their images, this is
-equivalent to saying that canonical functions are injective except for cases
-where they are not defined:
-\begin{align*}
-\forall\FS,\GS,\alpha:& \\
-& \T{\FS}\neq\T{\GS} \wedge \T{\alpha}(\T{\FS})\neq\fsbroken \\
-& \Rightarrow \T{\alpha}(\T{\FS}) \neq \T{\alpha}(\T{\GS}).
-\end{align*}
-\end{mylem}
-\begin{proof}
-Choose values that satisfy the left side, and let $\T{\alpha} = \cTxynv$.
-If $\T{\FS}$ and $\T{\GS}$ have different values (types) at any node apart from $n$, then this difference remains
-even after applying $\cTxynv$ to $\T{\FS}$. 
-The only remaining case therefore is where they have the same values
-at all nodes except at $n$.
-As $\cTxynv(\T{\FS})\neq\fsbroken$, we know $[\FS(n)]=[x]$.
-We also know that $\T{\GS}(n)\neq\T{\FS}(n)$, and therefore
-$[\GS(n)]\neq[x]$.
-This implies $\cTxynv(\T{\GS})=\fsbroken$,
-and again we have $\T{\alpha}(\T{\FS}) \neq \T{\alpha}(\T{\GS})$.
-\end{proof}
-
-% See
-% https://en.wikipedia.org/wiki/Inverse_semigroup#Origins
-% https://en.wikipedia.org/wiki/Symmetric_inverse_semigroup
-% https://en.wikipedia.org/wiki/Partial_function
-
-\begin{mydef}[Inverse commands and sequences]
-We write $\T{\alpha}^{-1}$ for
-the inverse of the canonical command (partial bijection) $\T{\alpha}$,
-which is uniquely defined by \cref{repr_comm_inject}.
-
-We write $\TS^{-1}$ for the inverse of the sequence $\TS$, which consists of the inverses of the commands in $\TS$ in reverse order.
-\end{mydef}
-By definition, for any canonical filesystem $\T{\FS}$ outside the image of 
-$\T{\alpha}$, the inverse $\T{\alpha}^{-1}$ is not defined.
-
-% Some further observations:
-% For canonical commands \[ \cTxynv^{-1} = \cTyxnv. \]
-% $\forall S: ({\TS}^{-1})^{-1} = \TS$.
-
-For brevity, in the following lemma we use $B$, $B'$, $\sqs{A}$ and $\sqs{C}$ to denote
-canonical sequences and sets.
-
-\newcommand{\ia}{\sqs{A}}
-\newcommand{\ic}{\sqs{C}}
-\newcommand{\ibi}{B^{-1}}
-
-\begin{mylem}\label{r_invmove}
-A common initial segment of a set of canonical sequences can be moved 
-to the other side of $\worksmeqsign$ by inverting it:
-\begin{gather*}
-\worksm{\ia}{B\cc\ic}
-\ \Longleftrightarrow \ \worksm{\ibi\cc\ia}{\ic} 
-\ \wedge \  \worksm{\ia}{\{B\}}
-\end{gather*}
-\end{mylem}
-\begin{proof}
-% This result is quite expected as we're mapping a subset statement using a bijection,
-% but made more complicated a as B is not defined everywhere.
-
-The proof is illustrated by \cref{fig_invmove}.
-
-\begin{figure}[htb]
-\input{fig-inverse-works}
-\caption{Proof of \cref{r_invmove}}\label{fig_invmove}
-\end{figure}
-
-For the left-to-right part of the proposition,
-from $\worksm{\ia}{B\cc\ic}$ we know $\Dom{\ia} \subseteq \Dom{B\cc\ic}$.
-As the (canonical) $B$ is a bijection between its domain and image,
-we can use $B$ to map both sides of this statement, which yields
-$\Dom{B^{-1}\cc\ia} \subseteq \Dom{\ibi\cc B\cc\ic}$,
-but the latter is a subset of $\Dom{\ic}$,
-and so $\Dom{\ibi\cc\ia} \subseteq \Dom{\ic}$,
-which means that $\worksm{\ibi\cc\ia}{\ic}$.
-It is easy to see that $\worksm{\ia}{B\cc\ic} \Rightarrow \worksm{\ia}{B}$.
-
-For the right-to-left part,
-from $\worksm{\ia}{B}$ we know $\Dom{\ia} \subseteq \Dom{B}$.
-Therefore we can project the whole of $\Dom{\ia}$ using the bijective canonical sequence $B$
-to get $\Dom{\ibi\cc\ia}$, and as $\worksm{\ibi\cc\ia}{\ic}$
-we know
-$\Dom{\ibi\cc\ia} \subseteq \Dom{\ic}$.
-We use $\ibi$ to project both sides of this statement to get
-$\Dom{B\cc\ibi\cc\ia} \subseteq \Dom{B\cc\ic}$.
-But we also know that $\Dom{B\cc\ibi\cc\ia} = \Dom{\ia}$
-as $\Dom{\ia} \subseteq \Dom{B}$,
-and so $\Dom{\ia} \subseteq \Dom{B\cc\ic}$ which means
-$\worksm{\ia}{B\cc\ic}$.
-\end{proof}
-
-We use this result to prove the following:
-
-\begin{mylem}\label{indep_prefix_combine}
-The combination of two sequences with a common head and independent tails 
-is defined wherever the two sequences are defined:
-\[ B\indep C \Rightarrow \worksmbx{A\cc B, A\cc C}{A\cc B\cc C} \]
-\end{mylem}
-\begin{proof}
-This is trivial unless $\worksmnil{A}$, so we assume that that is the case.
-From $B\indep C$ and \cref{combine_independent_sequences} we know
-$\worksmbx{B, C}{B\cc C}$.
-Based on \cref{repr_works_is_same} this is equivalent to
-$\worksmbx{\TB, \TC}{\TB\cc \TC}$.
-Since $\TA^{-1}\cc \TA \equiv \emptyseq$, this can also be written as
-\[\worksm{\TA^{-1}\cc\{\TA\cc \TB, \TA\cc \TC\}}{\TB\cc \TC}.\]
-From \cref{worksextpostfix} we also know that
-$\worksmbx{\TA\cc \TB, \TA\cc \TC}{\TA}$.
-Combining the last two statements using \cref{r_invmove}
-we get
-\[ \worksmbx{\TA\cc \TB, \TA\cc \TC}{\TA\cc \TB\cc \TC}, \]
-which with \cref{repr_works_is_same} proves the
-\namecref{indep_prefix_combine}.
-\end{proof}

### 2017-10-15 p2/rec-sound.tex
Fixed the soundness proof. Inverses are needed after all.

@@
 to the beginning of $A$ and $B$, and so this is equivalent to
-\[ \worksmbx{\acb\cc\amb, \acb\cc\bma}{\acb\cc \bma\cc \reca}, \]
-which is equivalent to
-\[ \worksmbx{\amb, \bma}{\bma\cc \reca}. \]
+\[ \worksmbx{\acb\cc\amb, \acb\cc\bma}{\acb\cc \bma\cc \reca}. \]
 
 For ease of reading, let us rename
-$\amb$ to $S$,
-$\reca$ to $S^*$,
-and $\bma$ to $T$.
+\begin{itemize}
+\item $\amb$ to $S$
+\item $\reca$ to $S^*$
+\item $\bma$ to $T$
+\item and $\acb$ to $U$.
+\end{itemize}
 In this notation, we intend to prove that
-\[ \worksmbx{S,T}{T\cc S^*}. \]
+\[ \worksmbx{U\cc S,U\cc T}{U\cc T\cc S^*}. \]
 We can do so if we can show that
@@
 
-This is because 
-$\worksmbx{S,T}{T}$ is trivially true, and this, combined with the above,
-yields 
-$ \worksmbb{S,T}{S^*,T}. $
-As $\reca\indep\bma$, that is, $S^*\indep T$,
-from \cref{combine_independent_sequences}
-we know
-$ \worksmbx{S^*,T}{T\cc S^*}, $
-and as $\worksmeqsign$ is transitive, combining the two statements above
-gives $\worksmbx{S,T}{T\cc S^*}$.
+This is because from \cref{indep_prefix_combine} we know
+$\worksmbx{U\cc T, U\cc S^*}{U\cc T\cc S^*}$ as $S^* \indep T$.
+From $\worksmbx{S,T}{S^*}$ trivially
+$\worksmbb{S,T}{S^*, T}$,
+and from \cref{works_restricted} we know
+$\worksmbb{U\cc S, U\cc T}{U\cc S^*, U\cc T}$.
+Because $\worksmeqsign$ is transitive, combining these results
+we get $\worksmbx{U\cc S,U\cc T}{U\cc T\cc S^*}$.
 
 \bigskip
-
-TODO TODO TODO TODO TODO
 
@@
 \begin{itemize}
-\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
-\item $\amb \cap \bma = \emptyset$
-\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
-% TODO Inverse is used here - how/why?
-\item $\worksmbb{\acbi\cc A,\acbi\cc B}{\amb, \bma}$ 
-because of \cref{r_invmove}
-as $\worksmbb{A,B}{A,B}$,
-and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
-TODO HOW IS THIS USED?
+\item $S=\amb$ and $T=\bma$ are simple as $A$ and $B$ are simple
+\item $S\cap T = \amb \cap \bma = \emptyset$
+\item 
+$S^*$ is the largest subset of $S$ for which $S^*\indep T$, as
+$\reca$ is the largest subset of $\amb$ for which $\reca\indep\bma$
 \end{itemize}
 
-Our theorem is therefore proven if we prove the following lemma,
-in which we rename $\amb$ to $S$, $\reca$ to $S^*$, and $\bma$ to $T$:
+Our theorem is therefore proven if we prove the following lemma.
 \newcommand{\condSimple}{(c1)}
@@
 \newcommand{\condApr}{(c3)}
-\newcommand{\condWork}{(c4)}
 \begin{mylem}\label{reconciliation_correct_part}
 If
-   \begin{itemize}
-   \item[\condSimple] $S$ and $T$ are simple sequences,
-   \item[\condDisj] $S\cap T=\emptyset$,
-   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
-   \item[\condWork] $\worksmxb{\sqs{C}}{S,T}$ for some set of sequences $\sqs{C}$,
-   \end{itemize}
+{\condSimple} $S$ and $T$ are simple sequences,
+{\condDisj} $S\cap T=\emptyset$,
+and {\condApr} $S^*$ is the largest subset of $S$ where $S^*\indep T$,
 then
-\[ \worksm{\sqs{C}}{S^*}. \]
+$\worksmbx{S,T}{S^*}$.
 \end{mylem}
@@
 \begin{proof}
-This is trivial unless $\worksmnil{\sqs{C}}$, so we will assume that it is true
-and therefore $\worksmnilb{S,T}$.
+This is trivial unless $\worksmnilb{S,T}$, so we assume that it is the case.
 
@@
 we prove that $S$ can be transformed into $S'$
-so that all marked commands would be at its beginning.
+where all marked commands are at the beginning.
 If so, then 
-$\worksm{\sqs{C}}{S^*}$ 
-based on \cref{worksextpostfix}
-as $\worksm{\sqs{C}}{S'}$ and $S'=S^*\cc S_0$ 
-where $S_0$ contains the remaining (conflicting) commands.
+$\worksm{S}{S^*}$ based on \cref{worksextpostfix},
+from which trivially $\worksmbx{S,T}{S^*}$.
 
@@
 \end{gather*}
-We know none of these commands is an assertion command, and 
-from {\condDisj} that $\cqrov\neq\czwmv$.
-Therefore, based on \cref{incomparable_is_independent} we know this means that
+Based on \cref{incomparable_is_independent} we know this means that
 either $m\descendantEq o$ or $o\descendantEq m$.
@@
 $n\unrel o$.
+We also know none of these commands is an assertion command, and 
+from {\condDisj} that $\cqrov\neq\czwmv$.
 
@@
 \begin{itemize}
-\item $n=\parent(m) \wedge o\descendantEq m$.
-   This would mean that $o\descendantEq n$ or $n=\parent(o)$, which contradicts $n\unrel o$.
-\item $n=\parent(m) \wedge m\descendantEq o$.
+\item $n=\parent(m)$ and $o\descendantEq m$.
+   This would mean that $o\descendantEq n$ or $n=\parent(o)$ (if $o=m$), which contradicts $n\unrel o$.
+\item $n=\parent(m)$ and $m\descendantEq o$.
    This would mean that $n\descendant o$, which contradicts $n\unrel o$.
-\item $m=\parent(n) \wedge o\descendantEq m$.
+\item $m=\parent(n)$ and $o\descendantEq m$.
    This would mean that $o\descendant n$, which contradicts $n\unrel o$.
-\item $m=\parent(n) \wedge m\descendantEq o$.
+\item $m=\parent(n)$ and $m\descendantEq o$.
    Let us continue with this case.
@@
 
+As $m=\parent(n)$, we know $\czwmv\cc\cxynv$ must be a construction pair.
 We know that $T$ cannot have a command on $m$ as $m=\parent(n)$ and $\cxynv\indep T$,
@@
 $m$ into $T$ before $\cqrov$
-according to \cref{ax_parent_assert}.
-We now have $\cxynv\indep T\equiv T'$, which is a contradiction as
-$T'$ has a command on $m$ and $m=\parent(n)$.
+according to \cref{ax_parent_assert}, the input type of which is $[\vald]$.
+As $T'$ is still minimal, and $\worksmnilb{S,T}$,
+from \cref{worksinputmatch} we get $[z]=[\vald]$, which is a contradiction,
+as $\czwmv$ is the first command in a construction pair.
 \end{proof}

### 2017-10-15 p2/works-inverse.tex
Fixed the soundness proof. Inverses are needed after all.

--- 2017-10-08 p2/works-inverse.tex
@@
 
-\subsection{Domains and Inverse Sequences}
+\subsection{Domains of Sets and Inverses}
 
@@
 its initial segments are also defined.
+\end{myclm}
+
+\begin{myclm}\label{works_restricted}
+$\forall \sqs{A},\sqs{B},S: \worksm{\sqs{A}}{\sqs{B}} \Leftarrow \worksm{S\cc \sqs{A}}{S\cc \sqs{B}}$, that is,
+the relationship between the domains of the sets $\sqs{A}$ and $\sqs{B}$ continues to hold
+even if they are restricted to the image of $S$.
 \end{myclm}
@@
 % See
-% https://en.wikipedia.org/wiki/Inverse_semigroup#Origins
+% https://en.wikipedia.org/wiki/Inverse_semigroup#Origins TODO
 % https://en.wikipedia.org/wiki/Symmetric_inverse_semigroup

### 2017-10-16 p2/axioms.tex
New proof for the correctness of reconciliation
Removed unused results
Output labels for easier reviewing

@@
-\section{Investigating Command Pairs}\label{section_axioms}
+\section{Investigating Command Pairs}\mlabel{section_axioms}
 
@@
 \[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
-% For example, we will write
-% $S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
 %% monoid, but not free monoid
@@
 
-\begin{mylem}\label{equiv_on_fs}
+\begin{mylem}\mlabel{equiv_on_fs}
 $A\equiv B$
@@
 
-\begin{myax}\label{ax_separate_commute}
+\begin{myax}\mlabel{ax_separate_commute}
 Commands on incomparable nodes commute:
@@
 
-\begin{myax}\label{ax_separate_nobreaks}
+\begin{myax}\mlabel{ax_separate_nobreaks}
 Commands on incomparable nodes do not break all filesystems:
@@
 
-\begin{myax}\label{ax_same_breaks}
+\begin{myax}\mlabel{ax_same_breaks}
 Commands on the same node break every filesystem if their types are incompatible:
@@
 
-\begin{myax}\label{ax_same_emptyseq}
+\begin{myax}\mlabel{ax_same_emptyseq}
 Commands on the same node simplify:
@@
 
-\begin{myax}\label{ax_same_singlec}
+\begin{myax}\mlabel{ax_same_singlec}
 Commands on the same node simplify:
@@
 
-\begin{myax}\label{ax_distantrel_breaks}
+\begin{myax}\mlabel{ax_distantrel_breaks}
 Commands on distant relatives break all filesystems:
@@
 
-\begin{myax}\label{ax_directchild_breaks}
+\begin{myax}\mlabel{ax_directchild_breaks}
 All other commands on a child break every filesystem:
@@
 As we shall see, this can be extended to \cref{simple_distant_pairs}.
-% TODO
+% TODO Delete this rule
 \end{myax}
@@
 
-\begin{myax}\label{ax_directparent_breaks}
+\begin{myax}\mlabel{ax_directparent_breaks}
 All other commands on a parent break every filesystem:
@@
 This can also be extended to \cref{simple_distant_pairs}.
-% TODO
+% TODO Delete this rule
 \end{myax}
@@
 
-\begin{myax}\label{ax_child_assert}
+\begin{myax}\mlabel{ax_child_assert}
 An assertion command can be added on a descendant node:
@@
 
-\begin{myax}\label{ax_parent_assert}
+\begin{myax}\mlabel{ax_parent_assert}
 An assertion command can be added on an ancestor node:
@@
 
-\begin{myax}\label{ax_assert}
+\begin{myax}\mlabel{ax_assert}
 Assertion commands can be removed:
@@
 
-\begin{mydef}[$A\indep B$: Independent commands, sequences and sets of commands]\label{def_indep}
+\begin{mydef}[$A\indep B$: Independent commands, sequences and sets of commands]\mlabel{def_indep}
 Two commands $\cxynv$ and $\czwmv$ 
@@
 
-\begin{mylem}\label{incomparable_is_independent}
+\begin{mylem}\mlabel{incomparable_is_independent}
 Two different commands that are not assertion commands are independent iff the nodes they change are incomparable. In other words,

### 2017-10-16 p2/ordering.tex
Fixed the soundness proof. Inverses are needed after all.
Removed unused results
Output labels for easier reviewing

@@
-\subsection{Ordering commands}\label{ordering}
+% TODO Commuting commands important as we need to establish order
+
+\subsection{Ordering commands}\mlabel{ordering}
 
@@
 
-\begin{mydef}[$\ordersetsign$]\label{def_orderset}
+\begin{mydef}[$\ordersetsign$]\mlabel{def_orderset}
 For a simple set or sequence of commands $S$,
@@
 
-\begin{myclm}\label{subseq_in_orderset}
+\begin{myclm}\mlabel{subseq_in_orderset}
 For simple sequences $S$ and $T$,
@@
 
-\begin{mylem}\label{simple_distant_pairs}
+\begin{mylem}\mlabel{simple_distant_pairs}
 For any simple sequence $\wrksx{S}$,
@@
 
-\begin{mycor}\label{order_is_only_possible}
+\begin{mycor}\mlabel{order_is_only_possible}
 For any simple sequence $S$ and its permutation $S'$, 
@@
 
-\begin{mylem}\label{connected_changes}
+\begin{mylem}\mlabel{connected_changes}
 Given a set of commands that
@@
 
-\begin{mylem}\label{equiv_simple_same_commands}
+\begin{mylem}\mlabel{equiv_simple_same_commands}
 If two simple sequences $A$ and $B$ are equivalent
@@
 
-\begin{mylem}\label{simple_reorder_equiv}
+\begin{mylem}\mlabel{simple_reorder_equiv}
 For a simple sequence $\wrksx{S}$,
@@
 \end{mydef}
-
-%% TODO Define set operations on sequences?
-% \noindent As a specific case, we can regard a simple sequence $S$
-% as a set, and use the above algorithm to generate all possible orderings
-% of the commands it contains.
-
-TODO TODO TODO -- ONLY USED ONCE WHERE INTERNALS OF OLD PROOF ARE USED
-\begin{mycor}\label{lemma:neighbor}
-If a simple sequence $S$ contains commands on both $n$ and $\parent(n)$, then
-there is a simple $S'\equiv S$ in which they are next to each other.
-\end{mycor}

### 2017-10-16 p2/rec-complete.tex
New "works" symbol, fixes
Output labels for easier reviewing

@@
 
-\begin{myth}\label{rec_is_complete}
+\begin{myth}\mlabel{rec_is_complete}
 If $A$ and $B$ are simple sequences,
@@
 pairs we also see that $r=w$ must hold, where $w=\vald$ or $w=\empt$.
-As $|\setd|=1$ and $|\setb|=1$, this also means that $v_R=v_W$ and therefore
+As $|\setd|=1$ and $|\setb|=1$, this also means that $::v_R=v_W::$ and therefore
 $\cqrmv = \czwmv$.

### 2017-10-16 p2/rec-intro.tex
Output labels for easier reviewing

@@
 
-\begin{mydef}[Reconciliation]\label{def:reconciliation}
+\begin{mydef}[Reconciliation]\mlabel{def:reconciliation}
 We determine $\reca$---which we apply to $\FS_B$ 

### 2017-10-16 p2/rec-sound.tex
Output labels for easier reviewing

@@
 
-\begin{myth}\label{reconciliation_correct}
+\begin{myth}\mlabel{reconciliation_correct}
 If $A$ and $B$ are simple, then $\worksmbx{A,B}{B\cc \reca}$,
@@
 
-\begin{mylem}\label{can_move_intersection}
+\begin{mylem}\mlabel{can_move_intersection}
 Let $A$ and $B$ be two simple sequences for which $\worksmnilb{A, B}$.
@@
 \newcommand{\condApr}{(c3)}
-\begin{mylem}\label{reconciliation_correct_part}
+\begin{mylem}\mlabel{reconciliation_correct_part}
 If

### 2017-10-16 p2/upd-correct.tex
Output labels for easier reviewing

@@
 
-\begin{myth}\label{update_works}
+\begin{myth}\mlabel{update_works}
 A sequence of commands returned by the update detector

### 2017-10-16 p2/works-inverse.tex
Output labels for easier reviewing

@@
 
-\begin{mydef}[$\worksmeqsign$]\label{def_works}
+\begin{mydef}[$\worksmeqsign$]\mlabel{def_works}
 For two sets of sequences $\sqs{A}$ and $\sqs{B}$
@@
 
-\begin{myclm}\label{worksextpostfix}
+\begin{myclm}\mlabel{worksextpostfix}
 % An inference rule in the algebra
@@
 
-\begin{myclm}\label{works_restricted}
-$\forall \sqs{A},\sqs{B},S: \worksm{\sqs{A}}{\sqs{B}} \Leftarrow \worksm{S\cc \sqs{A}}{S\cc \sqs{B}}$, that is,
+\begin{myclm}\mlabel{works_restricted}
+$\forall \sqs{A},\sqs{B},S: \worksm{\sqs{A}}{\sqs{B}} \Rightarrow \worksm{S\cc \sqs{A}}{S\cc \sqs{B}}$, that is,
 the relationship between the domains of the sets $\sqs{A}$ and $\sqs{B}$ continues to hold
@@
 
-\begin{myax}\label{combine_independent_commands}
+\begin{myax}\mlabel{combine_independent_commands}
 The combination of independent commands is defined on all filesystems
@@
 
-\begin{mylem}\label{combine_independent_sequences}
+\begin{mylem}\mlabel{combine_independent_sequences}
 The combination of independent sequences is defined on all filesystems
@@
 
-\begin{mylem}\label{worksinputmatch}
+\begin{mylem}\mlabel{worksinputmatch}
 If $S$ and $T$ are minimal sequences, $\worksmnilb{S,T}$,
@@
 
-\begin{mydef}[canonical mapping, $\T{}$]\label{def_typemapping}
+\begin{mydef}[canonical mapping, $\T{}$]\mlabel{def_typemapping}
 We use $\T{}$ and write $\T{a}$ to denote the canonical mapping of 
@@
 % TODO:
-\begin{mycor}\label{repr_works_is_same}
+\begin{mycor}\mlabel{repr_works_is_same}
 \begin{gather*}
@@
 
-\begin{mylem}\label{repr_comm_inject}
+\begin{mylem}\mlabel{repr_comm_inject}
 Canonical commands $\T{\alpha}$ are partial bijections over canonical filesystems
@@
 
-\begin{mylem}\label{r_invmove}
+\begin{mylem}\mlabel{r_invmove}
 A common initial segment of a set of canonical sequences can be moved 
@@
 
-\begin{mylem}\label{indep_prefix_combine}
+\begin{mylem}\mlabel{indep_prefix_combine}
 The combination of two sequences with a common head and independent tails 

### 2017-10-16 p2/rec-complete.tex
Rephrasing

@@
 If $A$ and $B$ are simple sequences,
-and we select a sequence $S\subset \amb$ so that
-it contains a command $\cxynv$ for which $\cxynv\nindep\bma$,
-then $B\cc S$ either breaks all filesystems $A$ and $B$ do not break
+and we select a sequence $S$ from the commands in $\ambnp$ so that
+it contains a command $\cxynv$ for which $\cxynv\nindep\bmanp$,
+then $B\cc S$ either breaks all filesystems $A$ and $B$ are defined on
 (that is, $S$ breaks all possible $\FS_B$ replicas),
@@
 Such an override could occur if a given node was modified differently in
-$A$ and $B$ (to different values but the same type), which is clearly
-a conflict that should be marked for review
-by a human or a different system.
+$A$ and $B$ (to different values but the same type), which 
+our algorithm must treat as a conflict to be resolved by
+by the user or a different system.
 \begin{proof}

### 2017-10-18 p2/rec-complete.tex
Clarify the completeness theorem

--- 2017-10-16 p2/rec-complete.tex
@@
 The reconciliation algorithm defined above is also maximal, that is,
-it is not possible to apply any further commands from $A\setminus B$ to $\FS_B$.
-To show this, we are going to prove the following theorem:
+it is not possible to apply any further commands from $\ambnp$ to $\FS_B$.
+To show this, we are going to prove that any sequence $S$ formed from commands
+in $\ambnp$ that is not independent of $\bmanp$ necessarily breaks $B\aFS=\FS_B$
+or introduces a conflicting update.
 
@@
 If $A$ and $B$ are simple sequences,
-and we select a sequence $S\subset \amb$ so that
-it contains a command $\cxynv$ for which $\cxynv\nindep\bma$,
-then $B\cc S$ either breaks all filesystems $A$ and $B$ do not break
+$S'\in\orderset{\ambnp}$,
+and $S$ is a subsequence of $S'$ that
+contains a command $\cxynv$ for which $\cxynv\nindep\bmanp$,
+then $B\cc S$ either breaks all filesystems $A$ and $B$ are defined on
 (that is, $S$ breaks all possible $\FS_B$ replicas),
-or it changes a node that $B$ has already changed to a different value,
+or $S$ changes a node that $B$ has already changed to a different value,
 that is, it overrides a change in $\FS_B$.
@@
 Such an override could occur if a given node was modified differently in
-$A$ and $B$ (to different values but the same type), which is clearly
-a conflict that should be marked for review
-by a human or a different system.
+$A$ and $B$ (to different values but to values of the same type), which 
+our algorithm must treat as a conflict to be resolved by
+by the user or a different system.
 \begin{proof}
 The proof is similar to the ones we have seen above.
+Let $T$ be an arbitrary sequence in $\orderset{\bmanp}$.
 Without loss of generality, we assume that $\cxynv$ is the first command in $S$
-that is not independent of $\bmanp$.
-If so, we can split $S$ into $S_0\cc\cxynv\cc S_1$ where $S_0\indep\bma$.
-Let us also split $\bmanp$ into $T_0\cc\czwmv\cc T_1$ where $T_1\indep\cxynv$.
+that is not independent of $T$.
+If so, we can split $S$ into $S_0\cc\cxynv\cc S_1$ where $S_0\indep T$.
+
+Let $\czwmv$ be the last command in $T$ that is not independent of $\cxynv$,
+and split $T$ into $T_0\cc\czwmv\cc T_1$, where therefore $T_1\indep\cxynv$.
+
 From \cref{can_move_intersection} we know that
-$B\cc S \equiv \acb\cc\bma\cc S$.
-We also know that commands in $S_0$ and $\bmanp$ commute, and so this is equivalent to
-$\acb\cc S_0\cc\bma\cc\cxynv\cc S_1$.
-Expanding $\bmanp$ and swapping $T_1$ and $\cxynv$ we get
+$\acb\cc\bma \in \orderset{B}$, and so
+$B\cc S \equiv \acb\cc\bma\cc S \equiv \acb\cc T\cc S$.
+We also know that commands in $S_0$ and $T$ commute, and so this is equivalent to
+$\acb\cc S_0\cc T\cc\cxynv\cc S_1$.
+Expanding $T$ and swapping $T_1$ and $\cxynv$ we get
 \[ \acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv\cc T_1\cc S_1. \]
@@
 First, we prove that this sequence breaks all filesystems
-unless $n=m$.
+where $A$ and $B$ are defined unless $n=m$.
 Let us therefore suppose $n\neq m$ and, to use an inverse proof,
@@
 We know $\cxynv\nindep\czwmv$, and so from \cref{incomparable_is_independent}, $n\nunrel m$.
-As the sequence is defined, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
-As $\czwmv$ and $T_0$ originate from $\bmanp$ and $B$ is simple, we also know there are
-no commands on $m$ in $\acbnp$ or $T_0$,
-and that there are no commands on $m$ in $S_0$ as $S_0\indep\bma$.
+As the sequence is defined on $\FS$, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
+Also, because $B$ is simple and contains $\czwmv$,
+we know there are no commands on $m$ 
+in either $\acb$ or $T_0$, which are both formed from other commands in $B$.
+Moreover, we know there are no commands on $m$ in $S_0$ because $S_0\indep T$.
 
-On the one hand we therefore know that $\FS(m)$ must be of type $[z]$,
+TODO TODO TODO
+
+On the one hand, we therefore know that $\FS(m)$ must be of type $[z]$,
 but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},

### 2017-10-19 p2/def-commands.tex
Completed the completeness theorem

@@
 We use a replacement operator of the form
-$\FS_{[\valv/n]}$ to denote a filesystem derived from $\FS$ 
+$\fsreplacement{\FS}{n}{\valv}$ to denote a filesystem derived from $\FS$ 
 by replacing its value at $n$ with $\valv$:
-\[ \FS_{[\valv/n]}(m) =
+\[ \fsreplacement{\FS}{n}{\valv}(m) =
    \begin{cases}
@@
    \fsbroken &\mbox{if~} [\FS(n)]\neq[x]\\
-   \fsbroken &\mbox{if~} \FS_{[y/n]} \mbox{~violates the tree property}\\
-   \FS_{[y/n]} &\mbox{otherwise.}
+   \fsbroken &\mbox{if~} \fsreplacement{\FS}{n}{y} \mbox{~violates the tree property}\\
+   \fsreplacement{\FS}{n}{y} &\mbox{otherwise.}
    \end{cases}

### 2017-10-19 p2/rec-complete.tex
Completed the completeness theorem

@@
 Let us therefore suppose $n\neq m$ and, to use an inverse proof,
-that the sequence is defined on $\FS$ where $A\aFS\neq\fsbroken$.
-If so, its initial segment, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also be defined.
+that the sequence is defined on $\FS$ 
+where $A\aFS\neq\fsbroken$ and $B\aFS\neq\fsbroken$.
+If so, its initial segment,
+\[ \acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv, \]
+must also be defined on $\FS$.
 
 We know $\cxynv\nindep\czwmv$, and so from \cref{incomparable_is_independent}, $n\nunrel m$.
-As the sequence is defined on $\FS$, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
+As the sequence is defined on $\FS$,
+because of \cref{simple_distant_pairs}
+$\czwmv\cc\cxynv$ can only be a construction or destruction pair.
+
 Also, because $B$ is simple and contains $\czwmv$,
@@
 Moreover, we know there are no commands on $m$ in $S_0$ because $S_0\indep T$.
+We therefore know that $\FS(m)$ must be of type $[z]$.
 
-TODO TODO TODO
+If $m=\parentf{n}$ then $\czwmv\cc\cxynv$ is a construction pair, and we know
+$[\FS(m)]=[z]\neq[\vald]$ and $y\neq\empt$ as none of these commands is an assertion command.
+If so, $\fsreplacement{\FS}{n}{y}$ 
+(that is, applying $\cxynv$ to $\FS$ without modifying $\FS(m)$ first) would violate the tree property.
+The same is true when $\parentf{m}=n$, where we have a destruction pair,
+and $[z]\neq\empt$ and $[y]\neq[\vald]$.
 
-On the one hand, we therefore know that $\FS(m)$ must be of type $[z]$,
-but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},
-we also know that $\cxynv$ cannot be applied to $\FS$ without
-changing $\FS(m)$ first.
-As $A\aFS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
-Let this command be $\cqrmv$.
+Since $\cxynv\in S$ and therefore $\cxynv\in A$, and $A\aFS\neq\fsbroken$,
+the above means that $A$ must also contain a command on $m$ before $\cxynv$.
+From \cref{simple_distant_pairs} we then know that $\cqrmv\cc\cxynv$
+is also a construction or destruction pair, and it is the same type as
+$\czwmv\cc\cxynv$.
 
-Clearly $[q]=[z]$ (from \cref{worksinputmatch}), and from the construction and destruction
-pairs we also see that $r=w$ must hold, where $w=\vald$ or $w=\empt$.
-As $|\setd|=1$ and $|\setb|=1$, this also means that $::v_R=v_W::$ and therefore
-$\cqrmv = \czwmv$.
-This is a contradiction as $\cqrmv\in A$, but $\czwmv\in\bmanp$.
+Because the type of the pair determines the output type of the first command,
+this means that $[r]=[w]$, and they can either be $[\empt]$ or $[\vald]$.
+As we assumed that $|\setd|=1$, we therefore know that $r=w$.
+From \cref{worksinputmatch} we also know that $[q]=[z]$.
+
+Therefore $\cqrmv = \czwmv$, which is a contradiction
+because $\cqrmv$ was selected from $A$, and
+$\czwmv$ was selected from $T$, that is, from $\bmanp$.
 
 The only possibility is therefore $n=m$.
-As $A$ and $B$ are simple, we therefore know that these are the first commands on $n$,
+As $A$ and $B$ are simple, we then know that
+$\cxynv$ and $\czwmv$ are the first commands on $n$,
 and so (again from \cref{worksinputmatch}) $[z]=[x]$.
 We also know $w\neq y$ as otherwise the two commands would be equal and
-would be included in $\acbnp$,
-but this means that $\cxynv$, from $A$, overrides a change introduced 
-by $\czwnv$, from $B$, which should be treated as a conflict.
+would be in $\acbnp$.
+This, however, means that $\cxynv$, from $A$, overrides a change introduced 
+by $\czwnv$, from $B$, which must be treated as a conflict.
 \end{proof}

### 2017-10-19 p2/ordering.tex
Added TODO comments

@@
 the order of commands on directly related nodes;
-and finally, \cref{ax_directchild_breaks,ax_directparent_breaks}, from which we know
+and finally, \cref{simple_distant_pairs}, from which we know
 that commands on parent--child pairs must be construction or destruction pairs.
@@
 \end{mylem}
-\begin{proof}
+
 Informally speaking, the proposition means that
@@
 
+TODO MOVE TO AMONG THE AXIOMS TO AVOID DUPLICATION.
+BUT THIS NEEDS THE DEFINITION OF SIMPLE SEQUENCES.
+
+\begin{proof}
 % BACK_TO_THE_FS TODO
-% TODO Review any proof depending on "nothing changes FS at n until...".
-% TODO Move to rules
 % TODO APPENDIX

### 2017-10-19 p2/rec-intro.tex
Added TODO comments

--- 2017-10-08 p2/rec-intro.tex
@@
 where $A$ and $B$ are simple sequences representing
-the updates applied to replicas $\FS_A$ and $\FS_B$:
+the updates applied to $\FS$ to arrive at replicas $\FS_A$ and $\FS_B$:
 \[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]

### 2017-10-19 p2/axioms.tex
Completed the completeness theorem
Added TODO comments
Various improvements

@@
 %% Sequences of commands form a free semigroup
-Sequences are also partial endofunctions on filesystems, defined only if all commands it contains succeed in the given order.
+Sequences are also partial endofunctions on filesystems,
+defined only if all commands they contain succeed in the given order.
 We write $\sets$ for the set of sequences of commands.
@@
 As we shall see, this can be extended to \cref{simple_distant_pairs}.
-% TODO Delete this rule
+TODO TO BE DELETED -- WE ONLY WANT TO USE \cref{simple_distant_pairs}
 \end{myax}
@@
 This can also be extended to \cref{simple_distant_pairs}.
-% TODO Delete this rule
+TODO TO BE DELETED -- WE ONLY WANT TO USE \cref{simple_distant_pairs}
 \end{myax}
@@
 we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $y=w$.
-% TODO Does this depend on |Vd|=1?
+% TODO Does this depend on |[D]|=1?
 Therefore $[x]=[y]=[z]=[w]$ which with $y=w$ contradicts our assumption that the commands are different.

### 2017-10-19 p2/ordering.tex
Various improvements

@@
 \begin{itemize}
-\item if $n=\parent(m)$, then $y=\vald$
+\item if $n=\parent(m)$, then $[y]=[\vald]$
 \item if $\parent(n)=m$, then $y=\empt$.
@@
 with comparable nodes;
-\cref{connected_changes}, from which we know that if $U$ contains commands on two comparable
+\cref{connected_changes}, from which we know that if a simple sequence contains commands on two comparable
 nodes, then it contains commands on all nodes in between, so it is enough to specify
@@
 This follows directly from \cref{simple_distant_pairs}.
+We use an inverse proof and assume $\wrks{S'}$.
 If $S'\not\in\orderset{S}$ then by \cref{def_orderset}
 it contains two commands on a node $n$ and its parent
-that placed next to each other do not form
-a construction or destruction pair.
-Let them be $\cxynv$ and $\czwmv$.
-By \cref{ax_directchild_breaks,ax_directparent_breaks}
-we know
-$\cxynv\cc\czwmv\equiv\cbrk$, which is a subsequence of $S'$,
-and therefore by \cref{simple_distant_pairs}, $S'\equiv\cbrk$.
+that, as a subsequence,
+do not form a construction or destruction pair.
+However, this contradicts \cref{simple_distant_pairs}
+which means that no such subsequence exists.
 \end{proof}
@@
 $\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
-\[ \orderset{S} = [S]_\equiv \cap \setssmp. \]
+\[ \orderset{S} = [S]_\equiv \cap \setssmp, \]
+where $\setssmp$ is the set of all simple sequences.
 \end{mylem}
@@
 \begin{proof}
-First, we prove, by contradiction, that if a simple sequence $T\equiv S$, then $T\in\orderset{S}$.
-We assume $T\equiv S$ and $T\not\in\orderset{S}$.
+First, we prove, by contradiction, that if a simple sequence $T$, $T\equiv S$, then $T\in\orderset{S}$.
+We use an inverse proof and assume $T\equiv S$ and $T\not\in\orderset{S}$.
 Then, from \cref{equiv_simple_same_commands} we know $T$ is a permutation of $S$,
@@
 We aim to transform $T$ into $T''\equiv T$ by swapping $\cxynv$ with the preceding
-command. Then from the induction hypothesis we will know $T\equiv T''\equiv S$,
+command. Then from the induction hypothesis we know $T\equiv T''\equiv S$,
 which proves our lemma.
@@
 that the case when the $n_\indx$ nodes ascend the tree,
-that is, $n_{\indx+1}=\parentf{n_\indx}$ is true, also leads to a contradiction,
-by using destruction commands instead of construction ones.
+that is, $n_{\indx+1}=\parentf{n_\indx}$ is true, also leads to a contradiction.
+In this case we find that all commands are destruction commands,
+and so $[y_\indx]\neq[\vald]$, while in a subsequence of $T$ for a given $\indx$,
+$[y_\indx]=[\vald]$ must be true by the definition of $\ordersetsign$.
 \end{proof}
@@
 We write $\ordp{S}$ to represent this endofunction.
-Also, let $\ordp{S}=\cbrk$ if such an order does not exist.
+We leave $\ordp{S}$ undefined if such an order does not exist.
 \end{mydef}

### 2017-10-19 p2/upd-correct.tex
Various improvements

@@
 the update detector does function as intended as:
+
+% TODO
+TODO ENSURE UPDATE DETECTOR IS DEFINED.
 
@@
 \begin{proof}
-Let $\FS\neq\fsbroken$ be the original filesystem, and $\FS^*\neq\fsbroken$
+Let $\FS$ be the original filesystem, and $\FS^*$
 be the filesystem after the changes we intend to detect.
@@
 at node $\nn$ and $n$, then it had to change on the nodes in between.
+
+TODO TODO TODO
 

### 2017-10-19 p2/upd-def.tex
Rename "works" to "defined"
Various improvements

@@
 
-\begin{mydef}[Minimal sets or sequences, $\setsmin$]
+% TODO Define, spell out update decetion algorithm
+
+\begin{mydef}[Minimal sets or sequences]
 A sequence or set of commands is minimal if it contains at most one command on each node.
-We write $\setsmin$ for the set of minimal sequences.
 \end{mydef}
 
-\begin{mydef}[Simple sets or sequences, $\setssmp$]
+\begin{mydef}[Simple sets or sequences]
 A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
-We write $\setssmp$ for the set of simple sequences.
 \end{mydef}

### 2017-10-20 p2/upd-correct.tex
Full proof for the correctness of update detection

@@
 \begin{myth}\mlabel{update_works}
-A sequence of commands returned by the update detector
-when comparing the non-broken $\FS^*$ to the original $\FS$
-will not break $\FS$ if it is applied to it.
+For a sequence of commands $U$ returned by the update detector
+when comparing the non-broken $\FS^*$ to the original $\FS$,
+$U\aFS = \FS^*$.
 \end{myth}
@@
 to $\FS$ until it reached the state $\FS^*$.
-Our set if commands is sufficient to record any change, as
+Our set of commands is sufficient to record any change, as
 there are commands for every input and output type pair, therefore
@@
 
-Therefore, \cref{connected_changes} applies to $S$ and we know
-if it contains commands on $\nn$ and $n$ where $\nn\descendant n$,
-then it also contains commands on nodes in between;
-which is equivalent to saying that if $\FS$ changed
-at node $\nn$ and $n$, then it had to change on the nodes in between.
+\newcommand{\ucx}{\alpha}
+\newcommand{\ucy}{\beta}
+\newcommand{\ucz}{\gamma}
 
-TODO TODO TODO
+We aim to find a simple sequence that is equivalent to $S$.
+If $S$ is already simple, there is nothing to do.
+If it is not simple, let $\ucx$ be the first command
+on a node $n$ that is already present in $S$,
+and let $\ucy$ be the previous command on $n$.
+Splitting $S$ around these commands we get
+\[ S = S_0 \cc \ucy \cc S_1 \cc \ucx \cc S_2. \]
 
-If so, then, similarly to what happens in the ordering algorithm,
-we can separate $S$ into components of commands on related nodes,
-as commands from separate components freely commute yielding equivalent sequences.
-From the arguments above we also know that each component
-must be made up of only destruction or only construction pairs,
-but not a mixture of the two.
-This means that in each component, commands on parents 
-either strictly precede or succeed child nodes
-(as otherwise $S\equiv\cbrk$ would hold),
-from which it follows that once the components are separated
-in a new sequence $S'\equiv S$,
-commands on the same nodes are next to each other in $S'$.
+We now show that $S_1\indep\ucx$,
+which is equivalent to $S_1\indep\ucy$ as both commands are on $n$.
+We use an inverse proof and assume that there is a command on $m$ in $S_1$
+where $m\descendant n$ or $m\ancestor n$.
+We know both $\ucy\cc S_1$ and $S_1\cc\ucx$ are simple,
+and both are defined on a filesystem
+(on $S_0\aFS$ and $(S_0\cc\beta)\FS$, respectively).
+Therefore from \cref{connected_changes} we know that
+$S_1$ must also contain a command on $m'$ where
+$m'=\parentf{n}$ or $n=\parentf{m'}$.
+Let this command be $\ucz$.
 
-Applying \cref{ax_same_emptyseq,ax_same_singlec} we can
-convert $S'$ into
-an $S''\eqnrw S'$ in which multiple commands on the same nodes
-are simplified into a single command or an empty sequence,
-and therefore $S''$ is simple and $S\equiv S'\eqext S''$.
-It is easy to see that $S''$ must contain the same commands
-as the output of the update detector, $U$, as both are simple
-but reflect all changes between $\FS$ and $\FS^*$.
-If so, then $S''\in\orderset{U}$ and based on \cref{simple_reorder_equiv}
-we have
-$S\equiv S'\eqext S''\equiv U$, and as $S\aFS = \FS^* \neq \fsbroken$,
-therefore $U\aFS\neq\fsbroken$.
+If $n=\parentf{m'}$,
+from \cref{simple_distant_pairs} 
+and the relationship of nodes in construction and destruction pairs
+we know that the subsequence
+$\ucy\cc\ucz$ must be a construction pair,
+and both $\ucy$ and $\ucz$ must be construction commands.
+But we also know that $\ucz\cc\ucx$ must be a destruction pair,
+and both $\ucz$ and $\ucx$ must be destruction commands.
+This is a contradiction as a command cannot be both.
+We arrive at the same contradiction if $m'=\parentf{n}$.
+
+We therefore know that $S_1\indep\ucx$ and so
+from \cref{ax_separate_commute}
+\[ S \equiv S_0\cc\ucy\cc\ucx\cc S_1 \cc S_2. \]
+We can apply \cref{ax_same_emptyseq,ax_same_singlec} to
+$\ucy\cc\ucx$ and get a $S'\equiv S$ that contains one or two less commands on $n$.
+Repeating the swap and the simplification we
+can convert $S$ into an equivalent simple sequence.
+Let this sequence be $S^*$.
+
+As $S^*\equiv S$, we know $S^*\aFS=\FS^*$, and that
+$\FS^*$ and $\FS$ differ at exactly those nodes that $S^*$ has commands on.
+If $U$ is the simple sequence returned by the update detector
+when comparing $\FS^*$ to $\FS$, it must also contain commands on the same set of nodes,
+and it must contain the same commands,
+as for the command $\cxynv$, $[x]$ must be $[\FS(n)]$, and $y$ must be $\FS^*(n)$.
+From this we know that $U$ is a permutation of $S^*$ and so $\orderset{U}=\orderset{S^*}$.
+
+As the update detector uses $\ordersetsign$ to order the commands in $U$,
+trivially $U\in\orderset{U}$,
+and as $S^*$ is defined on $\FS$,
+from \cref{order_is_only_possible} we know $S^* \in \orderset{S^*}$.
+This means $U\in\orderset{S^*}$,
+and so from \cref{simple_reorder_equiv} we know that $U\equiv S^*$,
+from which $U\aFS=\FS^*$.
 \end{proof}

### 2017-10-20 p2/works-inverse.tex
Added TODO comments
Fixed "works" notation for sets

@@
 or $\worksm{A}{B}$ to mean $\worksmbb{A}{B}$.
+In particular, we write $\worksmnil{\sqs{A}}$ to mean that
+there are filesystems on which all sequences in $\sqs{A}$ are defined.
+If $\sqs{A}$ contains a single sequence only, $A$, this is equivalent to $\wrks{A}$.
 
@@
 
-% TODO ???
 Also, for all objects where it is defined, $\T{a}\typeeq a$.
@@
 all propositions proven so far apply to them as well.
+-- TODO NEEDED? % TODO
 
@@
 we know $\Dom{A}=\Dom{\TA}$ and therefore $\Dom{\sqs{A}}=\Dom{\T{\sqs{A}}}$.
+TODO FIND A BETTER WAY OF SAYING THIS -- $\Dom{}$ PRESUPPOSES A SET OF % TODO
+ALL FILESYSTEMS THAT IS DIFFERENT FOR CANONICAL OBJECTS.
 From this it follows that
-% TODO what's the set of all filesystems?
-% TODO:
 \begin{mycor}\mlabel{repr_works_is_same}
@@
 \begin{proof}
-This is trivial unless $\worksmnil{A}$, so we assume that that is the case.
+This is trivial unless $\wrks{A}$, so we assume that that is the case.
 From $B\indep C$ and \cref{combine_independent_sequences} we know

### 2017-10-20 p2/works-inverse.tex
Extending domains to canonical sequences

@@
 
-By definiton,
-for any filesystem $\FS$ and command $\alpha$, 
+By definiton, for any filesystem $\FS$ and command $\alpha$, 
 $\T{\alpha}(\T{\FS}) = \T{(\alpha\aFS)}$.
+This implies $\T{\FS}\in\Dom{\T{\alpha}} \Leftrightarrow \FS\in\Dom{\alpha}$,
+where we interpret $\Dom{\T{\alpha}}$ as the subset of canonical filesystems $\T{\alpha}$ is defined on.
+This can be extended to sequences and sets of sequences, that is,
+\[ \T{\FS}\in\Dom{\T{\sqs{A}}} \Longleftrightarrow \FS\in\Dom{\sqs{A}}. \]
 
-Also, for all objects where it is defined, $\T{a}\typeeq a$.
-As canonical filesystems, commands, sequences, etc.
-are subsets of their non-canonical counterparts, 
-all propositions proven so far apply to them as well.
--- TODO NEEDED? % TODO
+To illuminate this more, we observe
+that $\typeeq$-equivalence classes of filesystems are a \emph{partition} of $\setfs$,
+and as whether a command is defined on a filesystem is determined solely by its input type,
+domains of commands, sequences and sets are unions of these classes:
+they either contain a full equivalence class, or none of the filesystems in it.
+In other words, $\FS\in\Dom{\sqs{A}} \Leftrightarrow [\FS] \subset \Dom{\sqs{A}}$.
+A domain therefore can be fully desribed by the canonical filesystems it contains.
 
-As the types of values determine whether a command breaks a filesystem,
-we know $\Dom{A}=\Dom{\TA}$ and therefore $\Dom{\sqs{A}}=\Dom{\T{\sqs{A}}}$.
-TODO FIND A BETTER WAY OF SAYING THIS -- $\Dom{}$ PRESUPPOSES A SET OF % TODO
-ALL FILESYSTEMS THAT IS DIFFERENT FOR CANONICAL OBJECTS.
-From this it follows that
-\begin{mycor}\mlabel{repr_works_is_same}
+In particular, the above means:
+
+\begin{myclm}\mlabel{repr_works_is_same}
 \begin{gather*}
@@
 \end{gather*}
-\end{mycor}
+\end{myclm}
+
+Also, as canonical filesystems, commands, sequences, etc.
+are subsets of their non-canonical counterparts, 
+all propositions proven so far apply to them as well.
 
@@
 
-We are now ready to define the inverse of canonical commands $\T{\alpha}$
+\bigskip
+
+\noindent We are now ready to define the inverse of canonical commands $\T{\alpha}$
 which allows us to move parts of sequences between the

### 2017-10-25 p2/rec-sound.tex
Rephrasing
We don't need the canonical mapping

@@
 
-This is because from \cref{indep_prefix_combine} we know
-$\worksmbx{U\cc T, U\cc S^*}{U\cc T\cc S^*}$ as $S^* \indep T$.
-From $\worksmbx{S,T}{S^*}$ trivially
-$\worksmbb{S,T}{S^*, T}$,
-and from \cref{works_restricted} we know
-$\worksmbb{U\cc S, U\cc T}{U\cc S^*, U\cc T}$.
-Because $\worksmeqsign$ is transitive, combining these results
-we get $\worksmbx{U\cc S,U\cc T}{U\cc T\cc S^*}$.
+This is because from $\worksmbx{S,T}{S^*}$ trivially $\worksmbb{S,T}{S^*, T}$,
+and from $S^* \indep T$ and \cref{combine_independent_sequences} we know $\worksmbx{S^*,T}{T\cc S^*}$.
+Combining the two we get $\worksmbx{S,T}{T\cc S^*}$,
+which using \cref{works_restricted} yields
+$\worksm{U\cc\{S,T\}}{U\cc T\cc S^*}$, that is,
+$\worksmbx{U\cc S,U\cc T}{U\cc T\cc S^*}$.
 
@@
 $\worksm{S}{S^*}$ based on \cref{worksextpostfix},
-from which trivially $\worksmbx{S,T}{S^*}$.
+from which we get $\worksmbx{S,T}{S^*}$.
 

### 2017-10-25 p2/unused/inverse.tex
We don't need the canonical mapping

--- 2017-10-20 p2/works-inverse.tex
@@
-% Works
-% -----
-
-\subsection{Domains of Sets and Inverses}
-
-\begin{mydef}[Sets of sequences]
-As we will frequently refer to sets of fequences,
-we will use calligraphic letters (e.g. $\sqs{A}$, $\sqs{B}$, $\sqs{C}$ and $\sqs{S}$)
-to denote such sets for brevity.
-
-We will write $\Dom{\sqs{A}}$ for $\bigcap_{A\in\sqs{A}} \Dom{A}$,
-and $\sqs{A}\cc\sqs{B}$ for $\{A\cc B\whr A\in\sqs{A}, B\in\sqs{B}\}$.
-
-% This has only been defined for sequences, not sets.
-Moreover, we write $\wrks{\sqs{A}}$ if $\varnothing \subset \Dom{\sqs{A}}$, that is,
-if we know that there is at least one filesystem
-all sequences in $\sqs{A}$ are defined on.
-\end{mydef}
-
-% works operators
-% ---------------
-
-\begin{mydef}[$\worksmeqsign$]\mlabel{def_works}
-For two sets of sequences $\sqs{A}$ and $\sqs{B}$
-we write $\worksm{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subseteq \Dom{\sqs{B}}$;
-that is, iff all sequences in $\sqs{B}$ are defined on (do not break)
-all filesystems on which sequences in $\sqs{A}$ are defined.
-\end{mydef}
-
-When $\sqs{A}$ or $\sqs{B}$ contains a single sequence,
-we leave out the curly brackets and write,
-e.g. $A\cc\sqs{B}$ to mean $\{A\}\cc\sqs{B}$,
-or $\worksm{A}{B}$ to mean $\worksmbb{A}{B}$.
-In particular, we write $\worksmnil{\sqs{A}}$ to mean that
-there are filesystems on which all sequences in $\sqs{A}$ are defined.
-If $\sqs{A}$ contains a single sequence only, $A$, this is equivalent to $\wrks{A}$.
-
-We can see that $A\eqext B$ implies $\worksm{A}{B}$, as the latter
-only requires that $B$ is defined where $A$ is defined, 
-while the former also requires
-that where they are defined, their effect is the same.
-
-The following claim follows immediately from the definition:
-
-\begin{myclm}\mlabel{worksextpostfix}
-% An inference rule in the algebra
-$\forall A,S: \worksm{A\cc S}{A}$, that is, if a sequence is defined,
-its initial segments are also defined.
-\end{myclm}
-
-\begin{myclm}\mlabel{works_restricted}
-$\forall \sqs{A},\sqs{B},S: \worksm{\sqs{A}}{\sqs{B}} \Rightarrow \worksm{S\cc \sqs{A}}{S\cc \sqs{B}}$, that is,
-the relationship between the domains of the sets $\sqs{A}$ and $\sqs{B}$ continues to hold
-even if they are restricted to the image of $S$.
-\end{myclm}
-
-We also prove the following lemmas.
-
-\begin{myax}\mlabel{combine_independent_commands}
-The combination of independent commands is defined on all filesystems
-where both of the commands are defined:
-\[ \alpha\indep \beta \Rightarrow \worksmbx{\alpha, \beta}{\alpha\cc \beta}. \]
-\end{myax}
-\begin{proof}
-We name this proposition a \namecref{combine_independent_commands} 
-because to prove it, we must reach back to our filesystem model.
-Let $\alpha=\cxynv$ and $\beta=\czwmv$.
-The proof is by contradiction;
-assume that there is a filesystem $\FS$ for which
-$\cxynv\aFS\neq\fsbroken$ and $\czwmv\aFS\neq\fsbroken$, but
-$\cxynv\cc \czwmv\aFS=\fsbroken$.
-We know $\cxynv\aFS\neq\fsbroken$ so it must be applying 
-$\czwmv$ that breaks it.
-Applying a command can only result in a broken filesystem in two cases.
-First, if the input type does not match the filesystem,
-but we know $[\FS(m)]=[w]$ and so
-$[(\cxynv\aFS)(m)]=[w]$ as based on \cref{incomparable_is_independent}, $n\neq m$.
-Second, if the new filesystem violates the tree property.
-This again cannot be the case because we also know that $n\unrel m$
-and the tree property only depends on the types of values at the parent and children of $m$,
-which therefore cannot be changed by $\cxynv$.
-\end{proof}
-
-\cref{combine_independent_commands} extends to sequences as well:
-
-\begin{mylem}\mlabel{combine_independent_sequences}
-The combination of independent sequences is defined on all filesystems
-where both of the sequences are defined:
-\[ S\indep T \Rightarrow \worksmbx{S,T}{S\cc T}. \]
-\end{mylem}
-\begin{proof}
-Assume that there is a filesystem $\FS$ so that
-$S\aFS\neq\fsbroken$ and $T\aFS\neq\fsbroken$, but
-$(S\cc T)\FS=\fsbroken$.
-
-From \cref{def_indep} we know that
-the commands in $S$ and $T$ pairwise commute, and so any sequence
-that contains the commands from $S$ and $T$ and preserve their original partial order
-is equivalent to $S\cc T$ on all filesystems.
-
-Let the command in $T$ that breaks $\FS$ when applying $S\cc T$ be $t$
-so that $T=T_0\cc t\cc T_1$.
-It is still true that $(T_0 \cc t)\FS\neq\fsbroken$,
-and by definition $(S\cc T_0)\FS\neq\fsbroken$,
-but $(S\cc T_0\cc t)\FS=\fsbroken$.
-Also, from above we know that $S\cc T_0\equiv T_0\cc S$
-and so $(T_0 \cc S)\FS\neq\fsbroken$.
-
-If we denote the first command in $S$ with $s_1$,
-this means that $(T_0 \cc s_1)\FS\neq\fsbroken$,
-which we can combine with $(T_0 \cc t)\FS\neq\fsbroken$, $t\indep s_1$ and
-\cref{combine_independent_commands}
-(using $T_0\FS$ as the reference filesystem)
-to arrive at $(T_0 \cc s_1\cc t)\FS\neq\fsbroken$.
-
-We can repeat this step for $s_2$, the next command in $S$,
-and from 
-$(T_0 \cc s_1\cc t)\FS\neq\fsbroken$
-and
-$(T_0 \cc s_1\cc s_2)\FS\neq\fsbroken$
-arrive at
-$(T_0 \cc s_1\cc s_2\cc t)\FS\neq\fsbroken$.
-This can be repeated until $S$ is exhausted and we get
-$(T_0 \cc S\cc t)\FS\neq\fsbroken$, which is a contradiction.
-\end{proof}
-
-We also prove the following:
-
-\begin{mylem}\mlabel{worksinputmatch}
-If $S$ and $T$ are minimal sequences, $\worksmnilb{S,T}$,
-and there are commands on node $n$ in both $S$ ($\cxynv\in A$) and $T$ ($\czwnv\in B$),
-then the input types of these commands must match, i.e. $[x]=[z]$.
-\end{mylem}
-\begin{proof}
-This result is similar to \cref{equiv_simple_same_commands} and
-is easily shown using a proof by contradiction: if $[x]\neq [z]$, then there is no filesystem that
-either $\cxynv$ or $\czwnv$ would not break, 
-and consequently $S$ and $T$ cannot work on the same filesystem.
-\end{proof}
-
 \bigskip
@@
 \begin{proof}
+TODO Trivial from \cref{combine_independent_sequences} and \cref{works_restricted}.
+
 This is trivial unless $\wrks{A}$, so we assume that that is the case.

### 2017-10-25 p2/works-inverse.tex
We don't need the canonical mapping

--- 2017-10-20 p2/works-inverse.tex
@@
 \begin{myclm}\mlabel{works_restricted}
-$\forall \sqs{A},\sqs{B},S: \worksm{\sqs{A}}{\sqs{B}} \Rightarrow \worksm{S\cc \sqs{A}}{S\cc \sqs{B}}$, that is,
-the relationship between the domains of the sets $\sqs{A}$ and $\sqs{B}$ continues to hold
-even if they are restricted to the image of $S$.
+$\forall \sqs{A},\sqs{B},S: \worksm{\sqs{A}}{\sqs{B}} \Rightarrow \worksm{S\cc \sqs{A}}{S\cc \sqs{B}}$,
+that is,
+the relationship between the domains of the sets $\sqs{A}$ and $\sqs{B}$ 
+does not change if both are prefixed by a sequence $S$.
 \end{myclm}
+\begin{proof}
+This is because the function $S$ is a binary relation between filesystems,
+and we can treat its inverse relation as a one-to-many mapping between filesystems
+that maps $\Dom{\sqs{A}}$ to $\Dom{S\cc\sqs{A}}$ and $\Dom{\sqs{B}}$ to $\Dom{S\cc\sqs{B}}$.
+As such a one-to-many mapping maps a subset of a set to a subset of the image of the set,
+if $\Dom{\sqs{A}}\subseteq\Dom{\sqs{B}}$, then $\Dom{S\cc\sqs{A}}\subseteq\Dom{S\cc\sqs{B}}$.
+\end{proof}
 
@@
 \end{proof}
-
-\bigskip
-
-% Type equivalence classes
-% ------------------------
-
-\noindent
-For the proof of the correctness of the reconciliation algorithm,
-we will also need a way of moving parts of sequences between the two
-sides of the $\worksmeqsign$ relation.
-We can do this based on the observation that commands are bijections
-if we only distinguish between types in our objects.
-To formalise this, we extend type equality ($\typeeq$)
-to filesystems, commands and sequences of commands.
-\begin{mydef}[Equivalence by type, extended: $\typeeq$]
-$ $ % otherwise first list element starts on same line
-\begin{itemize}
-\item For two filesystems in $\setfs$, $\FS\typeeq\GS$ iff
-for all $n\in\setn$, $\FS(n) \typeeq \GS(n)$.
-\item For two commands $\cxynv\typeeq\czwmv$ iff 
-$x\typeeq z$ and $y\typeeq w$
-(that is, $[x]=[z]$ and $[y]=[w]$)
-and $n=m$.
-\item To sequences of commands, the relation $\typeeq$ extends as usual: $\emptyseq\typeeq\emptyseq$, and
-if $A'=\alpha\cc A$ and $B'=\beta\cc B$, then $A'\typeeq B'$ iff $\alpha\typeeq\beta$ and $A\typeeq B$.
-\end{itemize}
-\end{mydef}
-
-We select representatives from each $\typeeq$-equivalence class of values:
-for $[\empt]$ and $[\vald]$ this must be $\empt$ and $\vald$; and
-for $[\valf]$ we select an arbitrary file value $\fil\in[\valf]$.
-We then use these representative values to
-introduce the \emph{canonical mapping} $\T{}$ that preserves the types of values,
-but maps all objects into a subsystem where there is a one-to-one
-correspondence between types and values.
-
-\begin{mydef}[canonical mapping, $\T{}$]\mlabel{def_typemapping}
-We use $\T{}$ and write $\T{a}$ to denote the canonical mapping of 
-values, filesystems, commands and sequences to the
-representatives of their $\typeeq$-equivalence class.
-\begin{itemize}
-\item For values, $\T{\vald}=\vald$, $\T{\valf}=\fil$ and $\T{\empt}=\empt$.
-\item For filesystems, $\T{\FS}$ is defined by $\T{\FS}(n) = \T{\FS(n)}$.
-\item For commands, $\T{\cbrk}=\cbrk$ and $\T{\cxynv} = \cTxynv$.
-\item To sequences of commands, the mapping extends as usual: $\T{\emptyseq}=\emptyseq$, and if $S'=\alpha\cc S$, then $\T{S'}=\T{\alpha}\cc \TS$.
-\item Finally we extend $\T{}$ to sets of sequences: $\T{\sqs{A}} = \{\TS \whr S\in\sqs{A}\}$.
-\end{itemize}
-\end{mydef}
-
-We refer to any object in the image of $\T{}$ as \emph{canonical}.
-
-By definiton,
-for any filesystem $\FS$ and command $\alpha$, 
-$\T{\alpha}(\T{\FS}) = \T{(\alpha\aFS)}$.
-
-Also, for all objects where it is defined, $\T{a}\typeeq a$.
-As canonical filesystems, commands, sequences, etc.
-are subsets of their non-canonical counterparts, 
-all propositions proven so far apply to them as well.
--- TODO NEEDED? % TODO
-
-As the types of values determine whether a command breaks a filesystem,
-we know $\Dom{A}=\Dom{\TA}$ and therefore $\Dom{\sqs{A}}=\Dom{\T{\sqs{A}}}$.
-TODO FIND A BETTER WAY OF SAYING THIS -- $\Dom{}$ PRESUPPOSES A SET OF % TODO
-ALL FILESYSTEMS THAT IS DIFFERENT FOR CANONICAL OBJECTS.
-From this it follows that
-\begin{mycor}\mlabel{repr_works_is_same}
-\begin{gather*}
-\worksmnil{\sqs{A}} \Longleftrightarrow \worksmnil{\T{\sqs{A}}} \\
-\worksm{\sqs{A}}{\sqs{B}} \Longleftrightarrow \worksm{\T{\sqs{A}}}{\T{\sqs{B}}}.
-\end{gather*}
-\end{mycor}
-
-% Inverse commands
-% ----------------
-
-We are now ready to define the inverse of canonical commands $\T{\alpha}$
-which allows us to move parts of sequences between the
-two sides of $\worksmeqsign$.
-This is based on the following observation.
-
-\begin{mylem}\mlabel{repr_comm_inject}
-Canonical commands $\T{\alpha}$ are partial bijections over canonical filesystems
-($\T{\FS}$, $\T{\GS}$).
-Because partial functions are trivially surjective when restricted to their images, this is
-equivalent to saying that canonical functions are injective except for cases
-where they are not defined:
-\begin{align*}
-\forall\FS,\GS,\alpha:& \\
-& \T{\FS}\neq\T{\GS} \wedge \T{\alpha}(\T{\FS})\neq\fsbroken \\
-& \Rightarrow \T{\alpha}(\T{\FS}) \neq \T{\alpha}(\T{\GS}).
-\end{align*}
-\end{mylem}
-\begin{proof}
-Choose values that satisfy the left side, and let $\T{\alpha} = \cTxynv$.
-If $\T{\FS}$ and $\T{\GS}$ have different values (types) at any node apart from $n$, then this difference remains
-even after applying $\cTxynv$ to $\T{\FS}$. 
-The only remaining case therefore is where they have the same values
-at all nodes except at $n$.
-As $\cTxynv(\T{\FS})\neq\fsbroken$, we know $[\FS(n)]=[x]$.
-We also know that $\T{\GS}(n)\neq\T{\FS}(n)$, and therefore
-$[\GS(n)]\neq[x]$.
-This implies $\cTxynv(\T{\GS})=\fsbroken$,
-and again we have $\T{\alpha}(\T{\FS}) \neq \T{\alpha}(\T{\GS})$.
-\end{proof}
-
-% See
-% https://en.wikipedia.org/wiki/Inverse_semigroup#Origins TODO
-% https://en.wikipedia.org/wiki/Symmetric_inverse_semigroup
-% https://en.wikipedia.org/wiki/Partial_function
-
-\begin{mydef}[Inverse commands and sequences]
-We write $\T{\alpha}^{-1}$ for
-the inverse of the canonical command (partial bijection) $\T{\alpha}$,
-which is uniquely defined by \cref{repr_comm_inject}.
-
-We write $\TS^{-1}$ for the inverse of the sequence $\TS$, which consists of the inverses of the commands in $\TS$ in reverse order.
-\end{mydef}
-By definition, for any canonical filesystem $\T{\FS}$ outside the image of 
-$\T{\alpha}$, the inverse $\T{\alpha}^{-1}$ is not defined.
-
-% Some further observations:
-% For canonical commands \[ \cTxynv^{-1} = \cTyxnv. \]
-% $\forall S: ({\TS}^{-1})^{-1} = \TS$.
-
-For brevity, in the following lemma we use $B$, $B'$, $\sqs{A}$ and $\sqs{C}$ to denote
-canonical sequences and sets.
-
-\newcommand{\ia}{\sqs{A}}
-\newcommand{\ic}{\sqs{C}}
-\newcommand{\ibi}{B^{-1}}
-
-\begin{mylem}\mlabel{r_invmove}
-A common initial segment of a set of canonical sequences can be moved 
-to the other side of $\worksmeqsign$ by inverting it:
-\begin{gather*}
-\worksm{\ia}{B\cc\ic}
-\ \Longleftrightarrow \ \worksm{\ibi\cc\ia}{\ic} 
-\ \wedge \  \worksm{\ia}{B}
-\end{gather*}
-\end{mylem}
-\begin{proof}
-% This result is quite expected as we're mapping a subset statement using a bijection,
-% but made more complicated a as B is not defined everywhere.
-
-The proof is illustrated by \cref{fig_invmove}.
-
-\begin{figure}[htb]
-\input{fig-inverse-works}
-\caption{Proof of \cref{r_invmove}}\label{fig_invmove}
-\end{figure}
-
-For the left-to-right part of the proposition,
-from $\worksm{\ia}{B\cc\ic}$ we know $\Dom{\ia} \subseteq \Dom{B\cc\ic}$.
-As the (canonical) $B$ is a bijection between its domain and image,
-we can use $B$ to map both sides of this statement, which yields
-$\Dom{B^{-1}\cc\ia} \subseteq \Dom{\ibi\cc B\cc\ic}$,
-but the latter is a subset of $\Dom{\ic}$,
-and so $\Dom{\ibi\cc\ia} \subseteq \Dom{\ic}$,
-which means that $\worksm{\ibi\cc\ia}{\ic}$.
-It is easy to see that $\worksm{\ia}{B\cc\ic} \Rightarrow \worksm{\ia}{B}$.
-
-For the right-to-left part,
-from $\worksm{\ia}{B}$ we know $\Dom{\ia} \subseteq \Dom{B}$.
-Therefore we can project the whole of $\Dom{\ia}$ using the bijective canonical sequence $B$
-to get $\Dom{\ibi\cc\ia}$, and as $\worksm{\ibi\cc\ia}{\ic}$
-we know
-$\Dom{\ibi\cc\ia} \subseteq \Dom{\ic}$.
-We use $\ibi$ to project both sides of this statement to get
-$\Dom{B\cc\ibi\cc\ia} \subseteq \Dom{B\cc\ic}$.
-But we also know that $\Dom{B\cc\ibi\cc\ia} = \Dom{\ia}$
-as $\Dom{\ia} \subseteq \Dom{B}$,
-and so $\Dom{\ia} \subseteq \Dom{B\cc\ic}$ which means
-$\worksm{\ia}{B\cc\ic}$.
-\end{proof}
-
-We use this result to prove the following:
-
-\begin{mylem}\mlabel{indep_prefix_combine}
-The combination of two sequences with a common head and independent tails 
-is defined wherever the two sequences are defined:
-% Use A\cc\{B,C\}
-\[ B\indep C \Rightarrow \worksmbx{A\cc B, A\cc C}{A\cc B\cc C} \]
-\end{mylem}
-\begin{proof}
-This is trivial unless $\wrks{A}$, so we assume that that is the case.
-From $B\indep C$ and \cref{combine_independent_sequences} we know
-$\worksmbx{B, C}{B\cc C}$.
-Based on \cref{repr_works_is_same} this is equivalent to
-$\worksmbx{\TB, \TC}{\TB\cc \TC}$.
-Since $\TA^{-1}\cc \TA \equiv \emptyseq$, this can also be written as
-\[\worksm{\TA^{-1}\cc\{\TA\cc \TB, \TA\cc \TC\}}{\TB\cc \TC}.\]
-From \cref{worksextpostfix} we also know that
-$\worksmbx{\TA\cc \TB, \TA\cc \TC}{\TA}$.
-Combining the last two statements using \cref{r_invmove}
-we get
-\[ \worksmbx{\TA\cc \TB, \TA\cc \TC}{\TA\cc \TB\cc \TC}, \]
-which with \cref{repr_works_is_same} proves the
-\namecref{indep_prefix_combine}.
-\end{proof}

### 2017-10-25 p2/ordering.tex
Full proof for the correctness of update detection
New parent function symbol
Various improvements

@@
 \begin{itemize}
-\item if $n=\parent(m)$, then $[y]=[\vald]$
-\item if $\parent(n)=m$, then $y=\empt$.
+\item if $n=\parentf{m}$, then $[y]=[\vald]$
+\item if $\parentf{n}=m$, then $y=\empt$.
 \end{itemize}
@@
 
-% TODO breaks --> not defined on
-
 \begin{mylem}\mlabel{equiv_simple_same_commands}
@@
 % TODO Rule?
-We use a proof by contradiction. Let $A$ and $B$ be simple sequences
+Let $A$ and $B$ be simple sequences
 such that $A\equiv \wrksx{B}$,
@@
 
-We also assume that they do not contain the same commands.
+We use a proof by contradiction, and assume that they do not contain the same commands.
 Without loss of generality, we can assume
@@
 
-As a command cannot be both a construction and a desrtruction command,
+As a command cannot be both a construction and a destruction command,
 this means that the indices $I^S$ are either monotone increasing, or monotone

### 2017-10-25 p2/works-inverse.tex
Various improvements

@@
 
-\subsection{Domains of Sets and Inverses}
+\subsection{Domains of Sets}
 
@@
 and $\sqs{A}\cc\sqs{B}$ for $\{A\cc B\whr A\in\sqs{A}, B\in\sqs{B}\}$.
-
-% This has only been defined for sequences, not sets.
-Moreover, we write $\wrks{\sqs{A}}$ if $\varnothing \subset \Dom{\sqs{A}}$, that is,
-if we know that there is at least one filesystem
-all sequences in $\sqs{A}$ are defined on.
 \end{mydef}
@@
 or $\worksm{A}{B}$ to mean $\worksmbb{A}{B}$.
-In particular, we write $\worksmnil{\sqs{A}}$ to mean that
+
+Also, we write $\worksmnil{\sqs{A}}$ to mean that
 there are filesystems on which all sequences in $\sqs{A}$ are defined.
@@
 
-The following claim follows immediately from the definition:
+The following claims follow from the definition:
 

### 2017-10-28 p2/axioms.tex
Various fixes; fixed the "set works" notation.

@@
 defined only if all commands they contain succeed in the given order.
-We write $\sets$ for the set of sequences of commands.
-They form a monoid, and, as usual,
-$\emptyseq$ denotes its unit element, the empty sequence,
+The sequences of commands form a monoid, and, as usual,
+we write $\emptyseq$ for the unit element, the empty sequence,
 which is defined on all filesystems and by definition leaves all filesystems unchanged.

### 2017-10-28 p2/upd-correct.tex
We don't need the canonical mapping
Fix: simplifying the sequence may increase the domain

@@
 TODO ENSURE UPDATE DETECTOR IS DEFINED.
+
+TODO What is not trivial here is that $U$ works at all.
 
@@
 We can apply \cref{ax_same_emptyseq,ax_same_singlec} to
-$\ucy\cc\ucx$ and get a $S'\equiv S$ that contains one or two less commands on $n$.
+$\ucy\cc\ucx$ and get a $S'\eqext S$ that contains one or two less commands on $n$.
 Repeating the swap and the simplification we

### 2017-10-31 p2/ordering.tex
Todo flags

@@
 \begin{proof}
+TODO: If something changes, everything changes up to the leaves.
+
 Without loss of generality, we can assume that $\nn\neq\parent(n)$.
@@
 $\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
-\[ \orderset{S} = [S]_\equiv \cap \setssmp, \]
-where $\setssmp$ is the set of all simple sequences.
+\[ \orderset{S} = \{T \whr T\equiv S \wedge T \mbox{~is simple} \}. \]
 \end{mylem}

### 2017-10-31 p2/paper.tex
Updated URL, improved documentation
Inverses are no longer needed
Fixed the soundness proof. Inverses are needed after all.
Output labels for easier reviewing
New parent function symbol
Todo flags

--- 2016-01-03 2015/paper.tex
@@
 \usepackage{amsthm}
+\usepackage{stmaryrd}
 \usepackage{centernot}
 \usepackage{tikz}
-\usepackage[capitalise]{cleveref}
+\usepackage{hyperref}
+\usepackage[capitalise,poorman,nameinlink]{cleveref}
 
@@
 \texttt{\rot{\rot{maz.}{csir}{ep}com}{@}{elod}}}
+\date{}
 
@@
 \begin{abstract}
+
+TODO: $n'$ should always be parent(n).
+
+TODO: Theorem 1, S' extends S. ... All S is extended by simple sequence, and generate with inference rules.
+
+TODO: Explain what happens to FF commands.
 
@@
 % conflict detection,
-% operation-based 
 % conflict resolution
@@
 
-\section{Definitions}\label{sec_def}
+\section{Definitions}\mlabel{sec_def}
 
@@
 
-\section{Update Detection}\label{sec_update}
+\section{Update Detection}\mlabel{sec_update}
 
@@
 
-\section{Reconciliation}\label{sec_rec}
+\section{Reconciliation}\mlabel{sec_rec}
 
@@
 
-I thank Laszlo Csirmaz for his invaluable input on this paper,
+% TODO Add reviewer
+% TODO Consider below
+I thank L. Csirmaz for his invaluable input on this paper,
 and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.

### 2017-11-05 p2/paper.tex
More TODO

@@
 TODO: Explain what happens to FF commands.
+
+TODO: $|[D]|=1$ - where used? Can we move $A \cap B$ to the beginning?
+
+% A: <D1,D2,n'>
+% B: <D1,D3,n'> <empt,F,n>
+% Reconciliation does not create file, but we can create it -> reconciliation maximal not true.
+
+TODO: After reconciliation, subsequence order works.
 
@@
 
-% TODO Add reviewer
-% TODO Consider below
-I thank L. Csirmaz for his invaluable input on this paper,
+I thank Laszlo Csirmaz for his invaluable input on this paper,
 and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.

### 2017-11-05 p2/works-inverse.tex

@@
 \begin{proof}
+TODO: they are the same? FF?
+
 We name this proposition a \namecref{combine_independent_commands} 

### 2017-11-07 p2/def-commands.tex
TeX improvements

@@
 \begin{itemize}
-\item $create(n,\valv)$, which creates a file or directory ($\valv$) at $n$
+\item \textit{create}$(n,\valv$), which creates a file or directory ($\valv$) at $n$
 where the file system contains no file or directory ($\empt$);
-\item $edit(n,\valv)$, which replaces the earlier file or directory at $n$ with $\valv$;
-\item $remove(n)$, which removes the file or directory at $n$, and replaces it with $\empt$.
+\item \textit{edit}$(n,\valv)$, which replaces the earlier file or directory at $n$ with $\valv$;
+\item \textit{remove}$(n)$, which removes the file or directory at $n$, and replaces it with $\empt$.
 \end{itemize}
@@
 after applying the command,
-we know that after $create$ or $edit$, $\FS(n)\neq\empt$, whereas after $remove$,
+we know that after \textit{create} or \textit{edit,} $\FS(n)\neq\empt$, whereas after \textit{remove,}
 $\FS(n)$ will be $\empt$. 
@@
 will in some cases need to distinguish between, for example,
-$edit$s that result in directories ($edit(n,\vald)$) and
-ones that result in files ($edit(n,\valf)$), and treat them as separate commands,
+\textit{edit}s that result in directories (\textit{edit}$(n,\vald)$) and
+ones that result in files (\textit{edit}$(n,\valf)$), and treat them as separate commands,
 as their behaviors are quite different when combined with other commands.
@@
 their input, the state of the filesystem
-before the command is applied. In particular, $create(n,\valv)$ requires that there are no files
-or directories at $n$, while $edit(n,\valv)$ and $remove(n)$ require the opposite.
+before the command is applied. In particular, \textit{create}$(n,\valv)$ requires that there are no files
+or directories at $n$, while \textit{edit}$(n,\valv)$ and \textit{remove}$(n)$ require the opposite.
 This creates an arbitrary asymmetry where
@@
 the type of the input value $\FS(n)$ as well.
-(Some real-life filesystem commands like $rmdir$ do this already.)
+(Some real-life filesystem commands like \textit{rmdir} do this already.)
 Again, as the success of failure of commands depends on types of values,

### 2017-11-09 p2/def-filesystem.tex
New proof for the correctness of reconciliation
Various improvements
Merged definitions

@@
 
-We model a working filesystem
-using a function $\FS$ with a set of nodes (filesystem paths) $\setn$ as its domain,
-and a set of possible contents or values $\setv$ as its codomain.
+\begin{mydef}[Filesystems]
+We model a filesystem
+using a function $\FS$ with a set of nodes (potential filesystem paths) $\setn$ as its domain,
+and a set of possible contents or values $\setv$ as its codomain:
+\[ \FS: \setn \rightarrow \setv. \]
 We consider metadata to be part of the values in $\setv$.
-\begin{mydef}[Filesystems, $\setn$, $\setv$, $\setfs$ and $\empt$]
-\[ \FS: \setn \rightarrow \setv \]
-In our model, $\setn$ 
-serves as a namespace or ``skeleton'' for the filesystem.
-It contains all possible nodes, including the ones 
-where the file system contains no file or directory,
-where in our model $\FS$ has a special value, $\empt\in\setv$.
-We write $\setfs$ for the set of filesystems over $\setn$.
+In this model, $\setn$ 
+serves as a namespace for the filesystem:
+it contains all possible nodes, including the ones 
+where the file system contains no file or directory.
 \end{mydef}
 
-There is an ancestor / descendant relation defined over the nodes,
-which arranges them in a (disjoint) union of rooted directed trees,
-and which can be derived from the following $\parent$ function.
+There is an ancestor / descendant relation defined over the nodes in $\setn$
+which arranges them in a disjoint union of rooted directed trees,
+and which can be derived from the partial function $\parent$ yielding
+the parent of a node in $\setn$ provided it exists.
+
 Tao et al. \cite{TSR} describe a similar filesystem model, although
 they also model inodes and restrict the filesystem to just a single tree.
-\begin{mydef}[$\parent$]
+
+\begin{mydef}[Ordering on $\setn$: $\parent$, $\descendant$, $\descendantEq$, $\unrel$]
 The partial function $\parent:\setn\nrightarrow\setn$
@@
 and is undefined if $n$ is the root of a tree.
-\end{mydef}
 
-\begin{mydef}[$\descendant$, $\descendantEq$]
-On $\setn$ the \emph{ancestor / descendant} relation $\descendant$ is the
+The \emph{ancestor} / \emph{descendant} relation $\descendant$ is the
 strict partial ordering determined by the $\parent$ function.
@@
 We write $n\descendantEq m$ if $n\descendant m$ or $n=m$.
-\end{mydef}
 
-\begin{mydef}[$n\unrel m$]
-We write $n\unrel m$, or $n$ and $m$ are \emph{incomparable}
+We write $n\unrel m$, or $n$ and $m$ are \emph{incomparable},
 iff $n\not\descendantEq m$ and $n\not\ancestorEq m$;
@@
 
-Every working filesystem has a so-called \emph{tree property}, which means that
+We assume that the $\parent$ function does not induce loops, and so
+$\descendant$ is indeed a strict partial ordering.
+
+The set of nodes $\setn$, combined with $\parent$ form a \emph{skeleton}
+which the filesytems populates with values from $\setv$.
+As we require the filesystem functions to be total,
+we use a special value, $\empt\in\setv$, to indicates that the filesystem
+has no file or directory at a particular node.
+
+\begin{mydef}[Filesystem values: $\vald$, $\valf$, $\empt$, $\typeeq$, $[v]$]
+The set of values $\setv$ is partitioned into files, directories, and the empty value $\empt$.
+For $v_1,v_2\in\FV$ we write $v_1\typeeq v_2$ iff
+$v_1$ and $v_2$ are both files, are both directories, or are both $\empt$.
+As usual, we write $[v]$ for the the equivalence class of $v\in\FV$ which represents its type.
+Files and directories are also denoted by $\valf$ and $\vald$, respectively,
+with or without indices.
+\end{mydef}
+
+Every filesystem has a so-called \emph{tree property}, which means that
 if the filesystem is not empty at a node, and the node has a parent,
@@
 
-\begin{mydef}[Equivalence by type: $\typeeq$]
-We write $v_1\typeeq v_2$ for $v_1,v_2\in\setv$ iff $v_1$ and $v_2$ are both files,
-are both directories, or are both $\empt$.
-% In other words, if $\setf$ is the set of file values and $\setd$ is the set of directories, then
-% with $\{\empt\}$ they form a partition of $\setv$:
-% \[ \setv/{\typeeq} = \{\setd,\setf,\{\empt\}\}. \]
-\end{mydef}
-
 As usual, we write $[v]$ for the equivalence class of $v$, which represents its type.
-
 The formal definition of the tree property is therefore
 \begin{mydef}[Tree property]
-\[ \forall n\in\setn, \FS\in\setfs: \FS(n) \neq \empt \Longrightarrow \FS(\parent(n)) \typeeq \vald \]
+% TODO \setf no longer defined
+\begin{align*}
+\forall n\in\setn, \FS\in\setfs:& \\
+& \FS(n) \neq \empt \Rightarrow \FS(\parent(n)) \typeeq \vald,
+\end{align*}
 where $\parent(n)$ is defined, and where $\vald\in\setv$ is a directory value.

### 2017-11-12 p2/def-filesystem.tex
New filesystem definitions

@@
-\subsection{The Filesystem}
+\subsection{Filesystems}
 
-\begin{mydef}[Filesystems]
+\begin{mydef}[Filesystems, $\FS$]
 We model a filesystem
@@
 
+% Ordering nodes
+
 There is an ancestor / descendant relation defined over the nodes in $\setn$
@@
 the parent of a node in $\setn$ provided it exists.
-
 Tao et al. \cite{TSR} describe a similar filesystem model, although
@@
 strict partial ordering determined by the $\parent$ function.
-We write $n\descendant m$ if $n$ is the ancestor of $m$,
-that is, $n=\parent^i(m)$ for some integer $i\ge 1$.
+We write $n\descendant m$, or $n$ is the ancestor of $m$,
+iff $n=\parent^i(m)$ for some integer $i\ge 1$.
 % or the path name of $n$ is an initial segment of that of $m$. 
-We write $n\descendantEq m$ if $n\descendant m$ or $n=m$.
+We write $n\descendantEq m$ iff $n\descendant m$ or $n=m$.
 
@@
 
-The set of nodes $\setn$, combined with $\parent$ form a \emph{skeleton}
-which the filesytems populates with values from $\setv$.
+% Values
+
+The combination of the set of nodes and the parent function,
+$\langle \setn, \parent \rangle$, forms a \emph{skeleton}
+which the filesytems populate with values from $\setv$.
 As we require the filesystem functions to be total,
-we use a special value, $\empt\in\setv$, to indicates that the filesystem
-has no file or directory at a particular node.
+we use a special value, $\empt\in\setv$, to indicate that the filesystem
+is empty at a particular node, that is, there are no files or directories there.
+We also assume that a filesystem has finitely many non-empty nodes.
 
-\begin{mydef}[Filesystem values: $\vald$, $\valf$, $\empt$, $\typeeq$, $[v]$]
+\begin{mydef}[Filesystem values: $\vald$, $\valfx$, $\empt$, $\typeeq$, $\eqclass{v}$]
 The set of values $\setv$ is partitioned into files, directories, and the empty value $\empt$.
-For $v_1,v_2\in\FV$ we write $v_1\typeeq v_2$ iff
+% TODO May be able to delete \typeeq
+For $v_1,v_2\in\setv$ we write $v_1\typeeq v_2$ iff
 $v_1$ and $v_2$ are both files, are both directories, or are both $\empt$.
-As usual, we write $[v]$ for the the equivalence class of $v\in\FV$ which represents its type.
-Files and directories are also denoted by $\valf$ and $\vald$, respectively,
+As usual, we write $[v]$ for the the equivalence class of $v\in\setv$, which represents its type.
+File and directory values are also denoted by $\valfx$ and $\vald$, respectively,
 with or without indices.
 \end{mydef}
+
+% Tree property
 
@@
 then there must be a directory at the parent node.
-To model this, we differentiate between files, directories, and the
-empty value in $\setv$, and introduce the equivalence relation
-$\typeeq$.
-
-As usual, we write $[v]$ for the equivalence class of $v$, which represents its type.
-The formal definition of the tree property is therefore
+Using the notation introduced above, we can formally express this as follows.
 \begin{mydef}[Tree property]
-% TODO \setf no longer defined
-\begin{align*}
-\forall n\in\setn, \FS\in\setfs:& \\
-& \FS(n) \neq \empt \Rightarrow \FS(\parent(n)) \typeeq \vald,
-\end{align*}
-where $\parent(n)$ is defined, and where $\vald\in\setv$ is a directory value.
+A filesystem $\FS:\setn \rightarrow \setv$ has the tree property iff
+\[ \forall n\in\setn
+\FS(n) \neq \empt \Rightarrow \FS(\parent(n)) \typeeq \vald \]
+wherever $\parent(n)$ is defined, that is, $n$ has a parent.
 \end{mydef}
 
+% SINGLEDIR
+
 To avoid the proliferation of edge cases, we will furthermore suppose that
-$|\setd|=1$, that is, apart from their location, all directories are equal;
-and use $\vald$ to denote the single value of the directory type.
+$|\setd|=1$, that is, there is only one directory value $\vald\in\setv$, and so
+apart from their location, all directories are equal.
 In appendix TODO we describe why it can be a sensible choice
@@
 
-%% TODO
-% % To model this, in $\setv$ we select another special value
-% % to represent directories, as we assume that apart from their location
-% % in the filesystem, all directories are equal.
 % % We do this because, as Bill Zissimopoulos pointed 
@@
 
-In this paper, $\FS$ and $\GS$ denote filesystems,
-and $n$, $m$ and $o$ are nodes in $\setn$.
-We write $\valf$ for a file value. % element in $\setf$.
+% Notation
+
+\smallskip
+In the rest of this paper,
+we fix the skeleton $\langle\setn,\parent\rangle$,
+and the set of values $\setv$.
+$\FS$ (with or without indices) denotes a filesystem,
+and $n$, $m$ and $o$ are nodes in $\setn$,
+and we write $\nn$ for the parent of $n$, assuming it exists.

### 2017-11-12 p2/def-filesystem.tex
Symbol for end of definition

@@
 which the filesytems populate with values from $\setv$.
-As we require the filesystem functions to be total,
+As we require filesystem functions to be total,
 we use a special value, $\empt\in\setv$, to indicate that the filesystem

### 2017-11-14 p2/def-commands.tex
Improved definitions

@@
 
-% TODO identity command instead of the empty sequence?
-
-Next we define commands on filesystems.
+Next, we define commands on filesystems.
 As described above, we aim to select a set of commands
@@
 more precisely.
-In other words, encoding the output value in the commands is definitely useful.
-As the success or failure of filesystem commands only depends on the types of values in the filesystem,
-we expect to use the type of their output when modelling their behavior.
 
@@
 (Some real-life filesystem commands like \textit{rmdir} do this already.)
-Again, as the success of failure of commands depends on types of values,
+Because the success of failure of commands depends on types of values,
 it is not necessary to encode the actual input value.
@@
 
-\begin{mydef}[Filesystem commands, $\cbrk$]
 We model filesystem commands as partial endofunctions on filesystems,
 that is, functions that map filesystems to filesystems, but which
-are not defined everywhere:
+are only defined
+
+\begin{mydef}[Filesystem commands, $\cbrk$]
 \[ \alpha: \setfs \nrightarrow \setfs \]
@@
 (its input and output types), and write
-$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$.
+$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$. % TODO delete
 

### 2017-11-15 p2/def-commands.tex
Improved definition of commands

@@
 
-We model filesystem commands as partial endofunctions on filesystems,
-that is, functions that map filesystems to filesystems, but which
-are only defined
+We model filesystem commands as partial functions 
+that map filesystems to filesystems, but which
+are only defined where the commands succeed.
+As usual, if the function is not defined, we say that that it returns the bottom element, $\fsbroken$,
+or that it \emph{breaks} the filesystem.
+We describe a filesystem commands using its input, output, and
+the node it is applied to.
 
-\begin{mydef}[Filesystem commands, $\cbrk$]
+\begin{mydef}[Filesystem commands]
+Filesystem commands are partial endofunctions on filesystems:
 \[ \alpha: \setfs \nrightarrow \setfs \]
 A command $\alpha$ is not defined on filesystems where it returns an error.
-This happens if the input type of the command does not match
-what is actually in the filesystem, or if the modified filesystem no
-longer has the tree property.
-At times in these cases we write that the command {\em breaks} the filesystem,
-or that it returns the bottom element, $\fsbroken$.
+The commands are represented using triplets of the form
+\[ \alpha = \caaaa{x}{y}{n}, \]
+where $x,y\in\setv$ and $n\in\setn$.
+The equivalence class $[x]$ is the \emph{input type} of the function;
+$y$ is its \emph{output value} implicitly specifying the \emph{output type} $[y]$,
+and $n$ is the node the command is applied to.
+\end{mydef}
+For example, $\cbfaa{n}$ represents \texit{create}$(n,\valf)$,
+and $\cdba{n}$ represents \textit{rmdir}$(n)$.
 
 We write $\cbrk$ for the empty partial function which is not defined anywhere.
+This does not naturally occur in sequences of commands we will investigate,
+but is useful when reasoning about the combined effects of commands.
 
-We have three pieces of information defining a non-empty command,
-which we represent using a triple. These are its
-input type ($[v_\textrm{in}]$), output value ($v_\textrm{out}$),
-and the node to which it is applied ($n$):
-\[ \alpha = \caaaa{v_\textrm{in}}{v_\textrm{out}}{n}. \]
-\end{mydef}
-
-For example, $\cbfaa{n}$ represents $create(n,\valf)$,
-and $\cdba{n}$ represents $rmdir(n)$.
-When describing unknown commands, we substitute one or both
-of their values with variables, and write e.g. $\cxynv$.
-By $\cxynv=\czwmv$ we mean that the commands are identical
-($[x]=[z]$ and $y=z$ and $n=m$).
+TODO DELETE:
 As suggested above, we will frequently only investigate
@@
 (its input and output types), and write
-$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$. % TODO delete
+$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$.
 
@@
 
-\begin{mydef}[Effect of commands]
-We use a replacement operator of the form
+To define the effect of a command on a filesystem, we use
+the replacement operator of the form
 $\fsreplacement{\FS}{n}{\valv}$ to denote a filesystem derived from $\FS$ 
@@
    \begin{cases}
-   \valv &\mbox{if~} m=n\\
-   \FS(m) &\mbox{otherwise.}
+   \valv &\textrm{if~} m=n\\
+   \FS(m) &\textrm{otherwise.}
    \end{cases}
 \]
-The effect of the commands is then as follows:
-\begin{align*}
-&\cbrk\aFS = \fsbroken \\
-&\cxynv\aFS = 
+
+\begin{mydef}[Effect of commands]
+The effect of the command $\cxynv$ is defined as follows:
+\cxynv\aFS = 
    \begin{cases}
-   % \fsbroken &\mbox{if~} \FS=\fsbroken\\
-   \fsbroken &\mbox{if~} [\FS(n)]\neq[x]\\
-   \fsbroken &\mbox{if~} \fsreplacement{\FS}{n}{y} \mbox{~violates the tree property}\\
-   \fsreplacement{\FS}{n}{y} &\mbox{otherwise.}
+   \fsbroken &\textrm{if $\FS(n)]\neq[x]$,}\\
+   \fsbroken &\textrm{if $\fsreplacement{\FS}{n}{y}$ violates the tree property,}\\
+   \fsreplacement{\FS}{n}{y} &\textrm{otherwise.}
    \end{cases}
-\end{align*}
 \end{mydef}
+In other words, the command $\cxynv$ breaks a filesystem if the input type $[x]$
+does not match the type of the value in the filesystem at $n$, or if after replacing
+the value at $n$ with $y$, the resulting filesystem ceases to satisfy the tree property.
 
@@
 For reasons also listed in \cite{NREC}, in this paper we will not consider
-a $move$ or $rename$ command.
+a \textit{move} or \textit{rename} command.
 This turns out to be useful because this would be the only command that affects
 filesystems at two nodes at once, therefore describing 
-the dependencies for $move$ would call for a more complicated model.
+the dependencies for \textit{move} would call for a more complicated model.
 From a pragmatic perspective, this restriction does not mean that in an application

### 2017-11-16 p2/axioms.tex
Minor improvements
TeX improvements
Command categories

@@
-\section{Investigating Command Pairs}\mlabel{section_axioms}
+\section{Command Pairs and Sequences}\mlabel{section_axioms}
 
@@
 of the following:
-   \begin{gather*}
-            \cbdaa{\nn}\cc  \cbfaa{n} \\
-            \cbdaa{\nn}\cc  \cbdaa{n} \\
-            \cfdaa{\nn}\cc  \caaa{\empt}{\valff}{n} \\
-            \cfdaa{\nn}\cc  \cbdaa{n}
-   \end{gather*}
+   \begin{align*}
+            \cbda{\nn}&\cc  \cbfa{n} \\
+            \cbda{\nn}&\cc  \cbda{n} \\
+            \cfda{\nn}&\cc  \caaa{\empt}{\valff}{n} \\
+            \cfda{\nn}&\cc  \cbda{n}
+   \end{align*}
 \end{mydef}
@@
 of the following:
-   \begin{gather*}
-            \cfba{n}\cc  \cdba{\nn} \\
-            \cfba{n}\cc  \caaa{\vald}{\valff}{\nn} \\
-            \cdba{n}\cc  \cdba{\nn} \\
-            \cdba{n}\cc  \cdfaa{\nn}
-   \end{gather*}
+   \begin{align*}
+            \cfba{n}&\cc  \cdba{\nn} \\
+            \cfba{n}&\cc  \caaa{\vald}{\valff}{\nn} \\
+            \cdba{n}&\cc  \cdba{\nn} \\
+            \cdba{n}&\cc  \cdfa{\nn}
+   \end{align*}
 \end{mydef}
@@
 \[ \cxynv\indep\czwmv \Longleftrightarrow n\unrel m \]
-if $\cxy\neq\czw$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
+if $\cxynv\neq\czwmv$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
 \end{mylem}

### 2017-11-16 p2/comparisons.tex
Command categories

@@
 \begin{align*}
-A&=\cbdaa{\nn}{\valdi}\cc\cbfaa{n}{\valf} \\
-B&=\cbdaa{\nn}{\valdii}
+A&=\caaa{\empt}{\valdi}{\nn}\cc\caaa{\empt}{\valf}{n} \\
+B&=\caaa{\empt}{\valdii}{\nn}
 \end{align*}
 where $\parent(n)=\nn$ (\cite{NREC} did not require all directories to have the same value).
-Clearly $\cbfaa{n}{\valf}$ could be applied to $\FS_B$, but it is not as
+Clearly $\caaa{\empt}{\valf}{n}$ could be applied to $\FS_B$, but it is not as
 it must be preceded by creating the directory, which conflicts with the same command in $B$

### 2017-11-16 p2/def-commands.tex
Command categories

@@
 \end{mydef}
-For example, $\cbfaa{n}$ represents \texit{create}$(n,\valf)$,
+For example, $\cbfa{n}$ represents \textit{create}$(n,\valf)$,
 and $\cdba{n}$ represents \textit{rmdir}$(n)$.
@@
 We note that a command or a sequence of commands is applied to a filesystem
-by prefixing the command or sequence to it, for example: $\cbrk\aFS$, $\cbdaa{n}\aFS$, 
+by prefixing the command or sequence to it, for example: $\cbrk\aFS$, $\cbda{n}\aFS$, 
 or $S\aFS$ if $S$ is a sequence of commands.
@@
 The effect of the command $\cxynv$ is defined as follows:
+\[
 \cxynv\aFS = 
    \begin{cases}
-   \fsbroken &\textrm{if $\FS(n)]\neq[x]$,}\\
+   \fsbroken &\textrm{if $[\FS(n)]\neq[x]$,}\\
    \fsbroken &\textrm{if $\fsreplacement{\FS}{n}{y}$ violates the tree property,}\\
@@
    \end{cases}
+\]
 \end{mydef}
@@
 the value at $n$ with $y$, the resulting filesystem ceases to satisfy the tree property.
+
+\bigskip
+\noindent
+Depending on their input and output types, there are nine types of commands,
+which we separate into four categories depending on the overall effect of the command.
+Constructions commands extend the filesystem,
+while destruction commands shrink it;
+the replacement command replaces a file value with a (presumably different) file value,
+and assertion commands either break the filesystem, or assert the type of the value at a node.
+\begin{mydef}[Command categories]
+Depending on their input and output types, filesystem commands
+belong to exactly one of the following four categories:
+\begin{itemize}
+\item[]\emph{Construction commands:}
+    $\cbfa{n}$, $\cbda{n}$ and $\cfda{n}$;
+\item[]\emph{Destruction commands:}
+    $\cdfa{n}$, $\cdba{n}$ and $\cfba{n}$;
+\item[]\emph{Assertion commands:}
+    $\cbba{n}$ and $\cdda{n}$;
+\item[]\emph{Replacement command:}
+    $\caaa{\valfx}{\valff}{n}$.
+\qedhere
+\end{itemize}
+\end{mydef}
 

### 2017-11-16 p2/ordering.tex
Command categories

@@
 % TODO APPENDIX
-For the proof we define construction and descruction commands as follows:
-\begin{mydef}[Construction command]
-A command $\cxynv$ is a construction command if it can appear in a construction pair,
-that is, if $[x]=[\empt]$ and $[y]\neq[\empt]$,
-or if $[x]=[\valf]$ and $[y]=[\vald]$.
-\end{mydef}
-\begin{mydef}[Destruction command]
-A command $\cxynv$ is a destruction command if it can appear in a destruction pair,
-that is, 
-if $[x]=[\valf]$ and $[y]=[\empt]$,
-or if $[x]=[\vald]$ and $[y]\neq[\vald]$.
-Note that a command cannot be both a construction and a destruction command.
-\end{mydef}
-
-% TODO APPENDIX
 \begin{proof}

### 2017-11-23 p2/axioms.tex
Merged definitions

@@
 We use ``$\cc$'' to combine commands to form a sequence, or combine sequences to form a longer sequence,
-with the meaning that the command on the left is applied first:
+with the meaning that the sequence is executed from left to right:
 \[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
@@
 defined only if all commands they contain succeed in the given order.
-The sequences of commands form a monoid, and, as usual,
-we write $\emptyseq$ for the unit element, the empty sequence,
-which is defined on all filesystems and by definition leaves all filesystems unchanged.
+Sequences form a monoid, and, as usual,
+we write $\emptyseq$ to denote the unit element, the empty sequence,
+which is defined on all filesystems and, by definition, leaves all filesystems unchanged.
 \end{mydef}
 
-\begin{mydef}[$\Dom{S}$ and $\Img{S}$]
-For a sequence of commands $S$, $\Dom{S}$ is the domain of $S$.
-We write $\Img{S}$ to denote the image of the domain of the sequence $S$.
+\begin{mydef}[$\Dom{S}$]
+For a sequence of commands $S$, $\Dom{S}$ is the domain of $S$, that is,
+the set of filesystems $S$ does not break.
 \end{mydef}
@@
 echo the ones defined in \cite{NREC}.
-In the definitions, $A,B,S,T$ stand for arbitrary sequences.
+In the definitions, $A,B,S$ and $T$ stand for arbitrary sequences.
 
-\begin{mydef}[$\eqext$]
+\begin{mydef}[$\eqext$, $\strext$ and $\equiv$]
 % Relation in the algebra
-We write $A\eqext B$, or $B$ \emph{extends} $A$,
+We write $A\eqext B$, or say that $B$ \emph{extends} $A$,
 % intended interpretation:
@@
 on any filesystem $A$ does not break:
-$\forall \FS\in\Dom{A}: A\aFS=B\aFS$.
+$\forall \FS\in\Dom{A}:\,A\aFS=B\aFS$.
 % old inference rule: $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
 We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\cc T$.
-% preorder: reflexive and transitive
-% patial order: reflexive, transitive and antisymmetric (aRb & bRa => a=b) TODO
-In other words, $\eqext$ is a preorder, and also a precongruence.
-\end{mydef}
+% symmetric:     aRb <=> bRa
+% antisymmetric: aRb & bRa => a=b
+% reflexive:     aRa
+% transitive:    aRb & bRC => aRc
+% preorder:      reflexive, transitive
+% partial order: reflexive, transitive, antisymmetric
+% equivalence:   reflexive, transitive, symmetric
+% congruence:    https://en.wikipedia.org/wiki/Congruence_relation
+% precongruence: congruence of a preorder
+In other words, $\eqext$ is a preorder, and also a precongruence. % TODO
 
-\begin{mydef}[$\equiv$]
 % Relation in the algebra
-$A\equiv B$,
-or $A$ and $B$ are \emph{equivalent,}
+We write $A\equiv B$,
+or say that $A$ and $B$ are \emph{equivalent,}
 iff $A\eqext B$ and $B\eqext A$;
 that is, $\equiv$ is the intersection of the preorder $\eqext$ with its inverse,
-and so it is a congruence.
-% symmetric: aRb <=> bRa
-% reflexive: aRa
-% transitive: aRb & bRC => aRc
+and so it is a congruence. % TODO
 % old inference rule: $ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.
+
+Finally, we write $A\strext B$ to mean $A\eqext B$ and $A\nequiv B$.
+In particular, we write $\wrks{A}$
+to mean that $\Dom{A}$ is not empty, that is, if $A$ is defined on some filesystems.
 \end{mydef}
@@
 \end{proof}
-
-\begin{mydef}[$\strext$]
-We write $A\strext B$ if $A\eqext B$ and $A\nequiv B$.
-In particular, we write $\wrks{A}$ if $A$ is defined on some filesystems.
-\end{mydef}
 

### 2017-11-23 p2/axioms.tex
Updated script

@@
 
-It is easy to see that this equivalence holds on the level of filesystems:
-
+It is easy to see that the equivalence $\equiv$ holds on the level of filesystems:
 \begin{mylem}\mlabel{equiv_on_fs}
@@
 \begin{proof}
-% TODO APPENDIX
-If $\forall \FS: A\aFS=B\aFS$, then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
-For the reverse statement we know $A\eqext B$ and $B\eqext A$.
-$B\eqext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
-Therefore, for every filesystem $\FS$, either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
-in which case $B\aFS=\fsbroken$ must be true, and therefore $A\aFS=B\aFS$.
+As $A\equiv B$ means that both $A$ extends $B$ and $B$ extends $A$, it necessarily
+follows that $A$ and $B$, as partial functions, are identical.
 \end{proof}
@@
 
+\myskip
 Our aim is to derive information about the effects of sequences
@@
 to a finite number of cases.
-
-We methodically investigate all possibilities using a computer 
-program\footnote{The program is accessible on-line at \\
-https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/p2/prove.py.}
-to determine
-which pairs of commands cause errors all the time,
-which can be simplified to one command or $\emptyseq$,
-and which commute and can be reversed without any change in their overall effect.
-Our basis for this investigation was the model of filesystems introduced in this paper.
 These properties of command pairs are crucial as they determine
 how a set of commands can be re-ordered to be applied to a filesystem
-during synchronization, and what commands will never be compatible.
-Below we list a number of statements derived using this method,
-which are in fact lemmas that can be derived from our definitions of filesystems and of commands.
+during synchronization, and what command pairs will never be compatible.
+
+% TODO \footnote{The program is accessible on-line at \\
+% https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/p2/prove.py.}
 
@@
 
-\bigskip
-
-\noindent
-Pairs of commands in general have the form
+\myskip
+Command pairs in genral have the form
 \[ \cxynv\cc  \czwmv \]
@@
 
-\bigskip
-
 % Independent commands
@@
 
-\noindent
+\myskip
 We also define the concept of two commands being independent:

### 2017-11-23 p2/def-commands.tex
Updated script

@@
 
-\bigskip
-\noindent
+\myskip
 Depending on their input and output types, there are nine types of commands,
@@
 
-\bigskip
-
-\noindent
+\myskip
 For reasons also listed in \cite{NREC}, in this paper we will not consider

### 2017-11-23 p2/paper.tex
Updated script

--- 2017-10-31 p2/paper.tex
@@
 
+TODO: $|[D]|=1$ - where used? Can we move $A \cap B$ to the beginning?
+
+% A: <D1,D2,n'>
+% B: <D1,D3,n'> <empt,F,n>
+% Reconciliation does not create file, but we can create it -> reconciliation maximal not true.
+
+TODO: After reconciliation, subsequence order works.
+
 \input{abstract}
 
-\bigskip\noindent
+\myskip
 {\bf Keywords:} % (4-6)
@@
 
-\bigskip\noindent
+\myskip
 {\bf MSC classes:} % http://www.ams.org/mathscinet/msc/msc2010.html
@@
 
-\bigskip\noindent
+\myskip
 {\bf ACM classes:} % http://www.acm.org/about/class/ccs98-html

### 2017-11-23 p2/prove.py

@@ -7,7 +7,7 @@ https://github.com/csirmaz/AlgebraicSyncPaper/tree/master/p2
 
 It is used to test pairs of commands on filesystems and determine
 (1) if they break all filesystems, 
-(2) or they are equivalent to (or extended by) an empty sequence of commands
+(2) or they are equivalent to (or extended by) the empty function
 (3) or they are equivalent to (or extended by) a single command
 (4) or they are equivalent to (or extended by) the same commands applied in reverse order.
 
@@ -15,6 +15,28 @@ The commands are tested on a minimal model of a filesystem that includes informa
 about two nodes, their immediate surroundings that determine the tree-property
 the filesystem needs to satisfy, and the relationship between the nodes.
 
+Copyright (c) 2017 Elod Pal Csirmaz
+
+Permission is hereby granted, free of charge, to any person obtaining a copy
+of this software and associated documentation files (the "Software"), to deal
+in the Software without restriction, including without limitation the rights
+to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
+copies of the Software, and to permit persons to whom the Software is
+furnished to do so, subject to the following conditions:
+
+The above copyright notice and this permission notice shall be included in
+all copies or substantial portions of the Software.
+
+THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.  IN NO EVENT SHALL THE
+AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
+LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
+OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
+THE SOFTWARE.
+"""
+
+"""
 The script considers the following possible relationships between the nodes (paths)
 to which the commands are applied:
 """
@@ -45,29 +67,7 @@ BR - the command pair breaks all filesystems (for (1) and (3))
 [[ - the pair is extended by the empty sequence, single command or reversed pair
 .. - none of the above is true    
 
[…]

### 2018-01-29 p2/axioms.tex
Revisions

@@
 
-% TODO Rewrite script for new notation
-
 \myskip
@@
 where $x,y,z,w\in\setv$ and $n,m\in\setn$. 
+Extending \cref{def:command_categories}, we call certain pairs
+\emph{construction} or \emph{destruction pairs}.
+
+\begin{mydef}[Construction and destruction pairs]
+A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parentf{n}$ 
+and the commands are one
+of the following:
+   \begin{align*}
+            \cbda{\nn}&\cc  \cbfa{n} \\
+            \cbda{\nn}&\cc  \cbda{n} \\
+            \cfda{\nn}&\cc  \caaa{\empt}{\valff}{n} \\
+            \cfda{\nn}&\cc  \cbda{n}
+   \end{align*}
+\end{mydef}
+
+\begin{mydef}[Destruction pair]
+A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parentf{n}=\nn$ and the commands are one
+of the following:
+   \begin{align*}
+            \cfba{n}&\cc  \cdba{\nn} \\
+            \cfba{n}&\cc  \caaa{\vald}{\valff}{\nn} \\
+            \cdba{n}&\cc  \cdba{\nn} \\
+            \cdba{n}&\cc  \cdfa{\nn}
+   \end{align*}
+\end{mydef}
 
@@
 
-\begin{mydef}[Construction pair]
-A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parent(n)$ 
-and the commands are one
-of the following:
-   \begin{align*}
-            \cbda{\nn}&\cc  \cbfa{n} \\
-            \cbda{\nn}&\cc  \cbda{n} \\
-            \cfda{\nn}&\cc  \caaa{\empt}{\valff}{n} \\
-            \cfda{\nn}&\cc  \cbda{n}
-   \end{align*}
-\end{mydef}
-
 \begin{myax}\mlabel{ax_directchild_breaks}
@@
 \end{myax}
-
-\begin{mydef}[Destruction pair]
-A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parent(n)=\nn$ and the commands are one
-of the following:
-   \begin{align*}
-            \cfba{n}&\cc  \cdba{\nn} \\
-            \cfba{n}&\cc  \caaa{\vald}{\valff}{\nn} \\
-            \cdba{n}&\cc  \cdba{\nn} \\
-            \cdba{n}&\cc  \cdfa{\nn}
-   \end{align*}
-\end{mydef}
 

### 2018-01-29 p2/def-commands.tex
Revisions

@@
 and assertion commands either break the filesystem, or assert the type of the value at a node.
-\begin{mydef}[Command categories]
+\begin{mydef}[Command categories]\mlabel{def:command_categories}
 Depending on their input and output types, filesystem commands

### 2018-02-05 p2/axioms.tex
Converted axioms

@@
 
-% TODO \footnote{The program is accessible on-line at \\
-% https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/p2/prove.py.}
-
 \myskip
@@
 \begin{mydef}[Construction and destruction pairs]
-A pair of commands on nodes $\nn$ and $n$ is a construction pair if $\nn=\parentf{n}$ 
-and the commands are one
-of the following:
+A pair of commands on nodes $\nn$ and $n$ where $\nn=\parentf{n}$
+is a \emph{construction pair} if the input and output types match
+one of the following patterns:
    \begin{align*}
@@
    \end{align*}
-\end{mydef}
-
-\begin{mydef}[Destruction pair]
-A pair of commands on nodes $n$ and $\nn$ is a destruction pair if $\parentf{n}=\nn$ and the commands are one
-of the following:
+The pair is a \emph{destruction pair} if the types match one of the following:
    \begin{align*}
@@
 
-\begin{myax}\mlabel{ax_separate_commute}
+We can see that construction pairs consist of construction comands,
+while destruction pairs consist of destruction commands.
+
+\Cref{rules_lemma} summarizes the basic properties of command pairs.
+The claims listed are named \emph{\namecref{ax_separate_commute}}
+as they can also be interpreted as inference rules in a pure
+algebraic treatment of filesystem synchronization.
+TODO elaborates this approach.
+
+\begin{mylem}\mlabel{rules_lemma}
+\newcounter{rulecounter}
+\begin{list}{\bf Rule~\arabic{rulecounter}.}{\usecounter{rulecounter}}
+
+\item[] % line break after the lemma label
+
+\item\mlabel{ax_separate_commute}
 Commands on incomparable nodes commute:
 $\cxynv\cc\czwmv \equiv \czwmv\cc\cxynv$ where $n\unrel m$.
-\end{myax}
 
-\begin{myax}\mlabel{ax_separate_nobreaks}
-Commands on incomparable nodes do not break all filesystems:
+\item\mlabel{ax_separate_nobreaks}
+Commands on incomparable nodes also do not break all filesystems:
 $\wrksx{\cxynv\cc\czwmv}$ where $n\unrel m$.
-\end{myax}
 
-\begin{myax}\mlabel{ax_same_breaks}
+\item\mlabel{ax_same_breaks}
 Commands on the same node break every filesystem if their types are incompatible:
 $\cxynv\cc\czwnv \equiv \cbrk$ where $[y]\ne [z]$.
-\end{myax}
 
-\begin{myax}\mlabel{ax_same_emptyseq}
-Commands on the same node simplify:
+\item\mlabel{ax_same_emptyseq}
+Otherwise commands on the same node are extended by an empty sequence if their outer types represent
+an assertion command:
 $\cxynv\cc\czwnv \eqext \emptyseq$ where $[y]=[z]$, and $\cxw=\cbb$ 
 or $\cxw=\cdd$.
-\end{myax}
 
-\begin{myax}\mlabel{ax_same_singlec}
-Commands on the same node simplify:
+\item\mlabel{ax_same_singlec}
+All other command pairs on the same node are equivalent to a single command:
 $\cxynv\cc \czwnv \equiv \cxwnv$ where $[y]=[z]$ and $\cxw\neq\cbb$ and $\cxw\neq\cdd$.
-\end{myax}
 
-\begin{myax}\mlabel{ax_distantrel_breaks}
-Commands on distant relatives break all filesystems:
+% TODO Renumber rules in script
+
+\item\mlabel{ax_directchild_breaks}
+Commands on a parent and a child node break every filesystem
+if the pair is not a construction pair
+and the commands do not simply assert a directory at the parent
+or an empty node at the child:
+$\cxynnv\cc\czwnv \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
+
+\item\mlabel{ax_directparent_breaks}
+Commands on a child and parent node break every filesystem
+if the pair is not a destruction pair
+and the commands do not simply assert an empty node at the child
+or a directory at the parent:
+$\cxynv\cc\czwnnv \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$.
+
+\item\mlabel{ax_distantrel_breaks}
+Commands on distant relatives break all filesystems
+if the commands do not simply assert a directory at the ancestor
+or an empty node at the descendant:
 $\cxynnv\cc\czwnv \equiv \cbrk$
@@
 where $\nn\descendant n$ and $\nn\neq\parent(n)$, and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
-(More intuitively, if $\czw\neq\cbb$ then either before or after $\czwnv$, the filesystem at
-$n$ is not empty, and therefore there must be a directory at all ancestors of $n$, including at a child of $\nn$.
-Consequently $\cxynnv$ will break the filesystem as either before or after it the filesystem at $\nn$
-does not have a directory.)
-\end{myax}
 
-\begin{myax}\mlabel{ax_directchild_breaks}
-All other commands on a child break every filesystem:
-$\cxynnv\cc\czwnv \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
-and the pair is not a construction pair.
-As we shall see, this can be extended to \cref{simple_distant_pairs}.
-TODO TO BE DELETED -- WE ONLY WANT TO USE \cref{simple_distant_pairs}
-\end{myax}
-
-\begin{myax}\mlabel{ax_directparent_breaks}
-All other commands on a parent break every filesystem:
-$\cxynv\cc\czwnnv \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
-and the pair is not a destruction pair.
-This can also be extended to \cref{simple_distant_pairs}.
-TODO TO BE DELETED -- WE ONLY WANT TO USE \cref{simple_distant_pairs}
-\end{myax}
-
-\begin{mydef}[Assertion command]
-A command is an assertion command if
-it leaves every filesystem in the same state
-where it is defined.
-In other words, assertion commands have the same input and output type,
-and there must also be only one possible value for their output.
-Accordingly, $\cbba{n}$ and $\cdda{n}$ are the only two types of assertion commands.
-\end{mydef}
-
-\begin{myax}\mlabel{ax_child_assert}
-An assertion command can be added on a descendant node:
+\item\mlabel{ax_child_assert}
+An assertion command can be freely added on a descendant node
+next to a command that does not simply assert a directory:
 \[ \cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n} \] 
 where $\nn\descendant n$ and $\cxy\neq\cdd$.
-(Note that this and next rule is true because the assertion command is
-adjacent to the original command.)
-\end{myax}
 
-\begin{myax}\mlabel{ax_parent_assert}
-An assertion command can be added on an ancestor node:
+\item\mlabel{ax_parent_assert}
+An assertion command can be freely added on an ancestor node
+next to a command that does not simply assert an empty node:
 \[ \cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn} \]
 where $\nn\descendant n$ and $\cxy\neq\cbb$.
-\end{myax}
 
-\begin{myax}\mlabel{ax_assert}
-Assertion commands can be removed:
+\item\mlabel{ax_assert}
+All assertion commands can be removed as the empty sequence extends them:
 $\cdda{n}\eqext\emptyseq$ and $\cbba{n}\eqext\emptyseq$.
-% $\cxynv \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
-\end{myax}
+
+\end{list}
+\end{mylem}
+
+These claims are easy but tedious to check.
+To ensure that all cases were considered when verifying these claims,
+a computer program was prepared that models the relevant parts of
+a filesystem and checks the results of applying all different command pairs
+against the above claims.\footnote{The program is accessible at \\ 
+https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/p2/prove.py.}
+
+For \cref{ax_distantrel_breaks}, we also provide a simple proof.
+Suppose $\cxynnv$ and $\czwnv$ satisfy the conditions in the \namecref{ax_distantrel_breaks},
+and there if an $\FS$ for which $(\cxynnv\cc\czwnv)\aFS\neq\fsbroken$.
+If $\czw\neq\cbb$, then either $\FS(n)\neq\empty$ or $\czwnv\aFS(n)\neq\empty$,
+and therefore $\FS(\parentf{n})$ must be a directory for the filesystem to satisfy
+the tree property at all times.
+However, from $\cxy\neq\cdd$ we also know that either $\FS(\nn)$ 
+(before applying $\cxynv$) or $\cxynv\aFS(\nn)$ (after applying $\cxynv$)
+is not a directory. Depending on which is true, we have a point in the sequence
+of applying the commands where the filesystem cannot satify the tree property
+and therefore becomes broken as $\parentf{n}$, a descendant of $\nn$, contains
+a directory and so must all its ancestors.
+
+For \cref{ax_child_assert,ax_parent_assert}, we note that these claims
+easily follow from the fact that the commands are adjacent to each other.
+
+Finally, we have included \cref{ax_directchild_breaks,ax_directparent_breaks}
+for completeness, but we will use the more generic \cref{simple_distant_pairs},
+which extends these rules to non-adjacent commands, although only in the case
+of command sequences without any assertion commands.
 

### 2018-02-05 p2/def-filesystem.tex
Command categories
Updated script
Converted axioms

@@
 \[ \forall n\in\setn
-\FS(n) \neq \empt \Rightarrow \FS(\parent(n)) \typeeq \vald \]
+\FS(n) \neq \empt \Rightarrow \FS(\parentf{n}) \typeeq \vald \]
 wherever $\parent(n)$ is defined, that is, $n$ has a parent.
@@
 
-\smallskip
+\myskip
 In the rest of this paper,

### 2018-02-05 p2/axioms.tex
Review

@@
 \myskip
-We also define the concept of two commands being independent:
+We also define the concept of two commands being independent.
 
 \begin{mydef}[$A\indep B$: Independent commands, sequences and sets of commands]\mlabel{def_indep}
-Two commands $\cxynv$ and $\czwmv$ 
-are independent, and we write $\cxynv\indep\czwmv$ if 
+Two commands $\alpha$ and $\beta$ 
+are independent, and we write $\alpha\indep\beta$ if 
 they commute and do not break all filesystems:
-\[ \cxynv\cc\czwmv \equiv \wrksx{\czwnv\cc\cxynv}. \]
+\[ \alpha\cc\beta \equiv \wrksx{\beta\cc\alpha}. \]
 For two sequences or unordered sets of commands $A$ and $B$ we write $A\indep B$ if
 for all $\alpha$ in $A$ and all $\beta$ in $B$, $\alpha\indep\beta$.
-We also write $\alpha\indep B$ iff $\{\alpha\}\indep B$.
+We also write $\alpha\indep B$ for $\{\alpha\}\indep B$.
 \end{mydef}
@@
 It is intentional that we use the same symbol for independent commands
-and sequences as for incomparable nodes. As we will see in the next
+and sequences as for incomparable nodes. As the next
 \namecref{incomparable_is_independent},
-these two concepts are closely related.
+shows, these concepts are closely related.
 
 \begin{mylem}\mlabel{incomparable_is_independent}
-Two different commands that are not assertion commands are independent iff the nodes they change are incomparable. In other words,
+Two different commands that are not assertion commands are independent 
+iff the nodes they change are incomparable. In other words,
 \[ \cxynv\indep\czwmv \Longleftrightarrow n\unrel m \]
@@
 \begin{proof}
-This is easy to show based on the output of the program that investigates the behavior of command pairs.
-However, this proposition can also be derived from the \namecrefs{ax_separate_commute} already listed
-in the following way.
-
-For the right-to-left part, we note that
-from \cref{ax_separate_commute,ax_separate_nobreaks} we know that
-if $n\unrel m$, then $\cxynv$ and $\czwmv$ must necessarily be independent.
+The right-to-left part is a restatement of
+\cref{ax_separate_commute,ax_separate_nobreaks}.
 

### 2018-02-06 p2/axioms.tex
Review

@@
 
-We prove the left-to-right part by contradiction.
-We assume that both $\cxynv\indep\czwmv$ and $n\nunrel m$,
-and show that it leads to contradiction.
-As $n\nunrel m$
+We prove the left-to-right part by contradiction,
+assuming that both $\cxynv\indep\czwmv$ and $n\nunrel m$.
+From $n\nunrel m$
 we know that $n=m$, $n\descendant m$ or $m\descendant n$.
 
-If $n=m$, then from \cref{ax_same_breaks} we know $[y]=[z]$ and $[w]=[x]$
-as otherwise the commands, in one order or the other, would break all filesystems
-and they could not be independent.
+If $n=m$, then from \cref{ax_same_breaks} we must have $[y]=[z]$ and $[w]=[x]$
+as otherwise the commands, in one order or the other, would break all filesystems.
 The commands are not assertion commands, so from \cref{ax_same_singlec}
@@
 
-If $n\descendant m$ or $m\descendant n$, then
-from \cref{ax_distantrel_breaks} we know that if they are not directly related,
-then $\cxynv\cc\czwmv$ breaks all filesystems, and they cannot be independent.
+The remaining case is that $n\descendant m$ or $m\descendant n$.
+If they are not directly related,
+then from \cref{ax_distantrel_breaks} we know that
+$\cxynv\cc\czwmv$ breaks all filesystems,
+which contradicts the assumption that the commands are independent.
 From the construction and destruction pairs and 
 \cref{ax_directchild_breaks,ax_directparent_breaks} we also see that
-even if they are directly related, either
+even if the nodes are directly related, either
 $\cxynv\cc\czwmv$ or $\czwmv\cc\cxynv$ 

### 2018-02-06 p2/upd-def.tex
Review

@@
 In a command-based reconciliation solution we assume that we have two sequences of commands
-$A$ and $B$ that have modified a single filesystem $\FS$ yielding two different replicas $\FS_A$ and $\FS_B$ that we
-need to reconcile. While it is conceivable that the sequences would be based on a record of
+$A$ and $B$ that have modified a single filesystem $\FS$ yielding two different replicas $\FS_1$ and $\FS_2$ that we
+need to reconcile. While it is conceivable that the sequences are based on a record of
 all operations that modified the two filesystems, in most filesystem implementations
 such records are not implemented, and therefore we must construct suitable sequences
-by comparing $\FS_A$ and $\FS_B$ to their common ancestor, $\FS$. This is called update detection.
+by comparing $\FS_1$ (and $\FS_2$) to their common ancestor, $\FS$. 
+This is called \emph{update detection.}
 
-A sequence that transforms $\FS$ into $\FS_A$ must contain at least one command on each node
-that changes between the two states of the filesystem. Also, it is easy to see that this is also
-sufficient, as there are commands available for any input and output value. 
-Specifically, if at node $n$, $\FS(n)=x$ and $\FS_A(n)=y\neq x$, then we add the command $\cxyaa{n}$ to $A$.
+The set of commands $U$ necessary to transform $\FS$ into $\FS_1$ can be collected
+by inspecting the union of non-empty nodes in the two filesystems.
+If at node $n$, $\FS(n)=x$ and $\FS_1(n)=y\neq x$, then we add the command $\cxyaa{n}$ to $U$.
+We can always do so as there is a command available for all combinations of input and output types and values.
+We see that any suitable $U$ necessarily contains commands on all nodes that have changed.
 
-To be able to describe such sequences better, let us introduce the following properties:
+To be able to reason about sets and sequences of commands, let us introduce the following properties:
 

### 2018-02-27 p2/ordering.tex
Review
Merged definitions

@@
 
-We recognize that mulitple orders may be possible;
-let us therefore describe our ordering algorithm by
+As we recognize that mulitple orders may be possible,
+let us describe our ordering algorithm by
 defining a subset of the permutations, $\ordersetsign$.
@@
 
-As we will see, $\ordersetsign$ generates all possible
+As we will see, $\ordersetsign$ contains all possible
 sequences of commands that do not break all filesystems.
 In \cref{simple_reorder_equiv}, we offer a formal proof of this.
-It is an important property of simple sequences: namely, that
-all of their valid reorderings are equivalent,
-and all equivalent sequences are mere reorderings.
+The facts that all valid reorderings of simple sequences are equivalent,
+and all equivalent sequences are reorderings are important 
+properties of simple sequences.
 
@@
 For a simple set or sequence of commands $S$,
-we use $\orderset{S}$ to denote the set of sequences
-that are all permutations of the commands in $S$
+we use $\orderset{S}$ to denote the set of 
+permutations of the commands in $S$
 for which the following holds:
-for all subsequences $\cxynv\cc\czwmv$,
+for any subsequence $\cxynv\cc\czwmv$,
 \begin{itemize}
@@
 
-To prove \cref{simple_reorder_equiv}, we need the following results.
+To prove \cref{simple_reorder_equiv}, we need the following simple results.
 
@@
 
-TODO MOVE TO AMONG THE AXIOMS TO AVOID DUPLICATION.
-BUT THIS NEEDS THE DEFINITION OF SIMPLE SEQUENCES.
-
 \begin{proof}
 % BACK_TO_THE_FS TODO
-% TODO APPENDIX
 Formally, we prove our proposition by contradiction,

### 2018-02-27 p2/upd-def.tex
Merged definitions

@@
 In a command-based reconciliation solution we assume that we have two sequences of commands
-$A$ and $B$ that have modified a single filesystem $\FS$ yielding two different replicas $\FS_1$ and $\FS_2$ that we
+$A$ and $B$ that have modified a single filesystem $\FS$ 
+yielding two different replicas $\FS_1$ and $\FS_2$ that we
 need to reconcile. While it is conceivable that the sequences are based on a record of
@@
 We can always do so as there is a command available for all combinations of input and output types and values.
-We see that any suitable $U$ necessarily contains commands on all nodes that have changed.
+We see that any suitable $U$ necessarily contains commands on all nodes at which the values have changed.
 
@@
 
-\begin{mydef}[Minimal sets or sequences]
-A sequence or set of commands is minimal if it contains at most one command on each node.
-\end{mydef}
-
-\begin{mydef}[Simple sets or sequences]
-A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
+\begin{mydef}[Minimal and simple command sets and command sequences]
+A sequence or set of commands is \emph{minimal} if it contains at most one command on each node.
+It is \emph{simple} if it is minimal and it does not contain assertion commands.
 \end{mydef}

### 2018-07-02 p2/axiom-proof.tex
Proofs for the rules

In this section we offer proofs for the \namecrefs{ax_separate_commute} listed in
\cref{rules_lemma}.
For the purposes of the proofs we extend the notion of filesystems 
to the full set of functions mapping $\setn$ to $\setv$, even if they
do not have the tree property.
In this case we continue to say that the filsystem is broken,
but we also describe the filesystem values at certain nodes.
Also, in order to pinpoint the region that violates the tree property,
we say that the filesystem is \emph{broken at $n$} if 
$n$ is not a dictionary, but has at least one non-empty child.

Accordingly, we also extend filsystem commands from partial to full functions,
and assume that they return a filesystem we can describe in all cases.
We note that once a filesystem is broken, it stays broken, even if
after a subsequent command it no longer violates the tree property.

It follows from the definition of the tree property that
whether a filesystem is \emph{broken at a node $n$} is determined only
by the values at $n$, $\parentf{n}$, and the children of $n$.
In other words,

\begin{myclm}[Locality of tree property violations]\mlabel{broken_local}
If two filesystems over $\setn$ have the same values at a node $n$,
$\parentf{n}$ (if exists), and at all children of $n$ (if they exist),
then either both filesystems are broken at $n$, or none of them are.
\end{myclm}

\cref{ax_separate_commute}

We use an inverse proof and assume $\cxynv\cc\czwmv \nequiv \czwmv\cc\cxynv$.
Since the values in the resulting filesystems are the same,
this is only possible if, for an initial non-broken filesystem $\FS$,
one side results in a broken filesystem, and the other side does not.
Without loss of generality, we can assume
$(\cxynv\cc\czwmv)\aFS$ is not broken, but $(\czwmv\cc\cxynv)\aFS$ is.
This means that either $\czwmv\aFS$ is already broken, or it is not, and applying $\cxynv$
breaks the filesystem.

In the former case, the filesystem must be broken at $m$ or $\parentf{m}$.
Since the set of $n$ with its granparent, parent and children; and $m$ with its grandparent, parent and children
are disjunct, we know $\cxynv\aFS$ contains the same values around $m$ as $\aFS$.
This leads to contradiction as from \cref{broken_local} we know
that being broken at $m$ or $\parentf{m}$
... WHAT ABOUT SIBLINGS? ...
while applying $\czwmv$ to $\cxynv\aFS$ on the left-hand side resulted in a working filesystem,
it resulted in a broken filesystem when applied to $\FS$ on the right-hand side.
The proof is similar in the case when applying $\cxynv$ breaks the filesystem on the right-hand side.

### 2018-07-02 p2/axioms.tex
Proofs for the rules

@@
 \begin{mydef}[Construction and destruction pairs]
-A pair of commands on nodes $\nn$ and $n$ where $\nn=\parentf{n}$
+A pair of commands on nodes $\pn$ and $n$
 is a \emph{construction pair} if the input and output types match
@@
    \begin{align*}
-            \cbda{\nn}&\cc  \cbfa{n} \\
-            \cbda{\nn}&\cc  \cbda{n} \\
-            \cfda{\nn}&\cc  \caaa{\empt}{\valff}{n} \\
-            \cfda{\nn}&\cc  \cbda{n}
+            \cbda{\pn}&\cc  \cbfa{n} \\
+            \cbda{\pn}&\cc  \cbda{n} \\
+            \cfda{\pn}&\cc  \caaa{\empt}{\valff}{n} \\
+            \cfda{\pn}&\cc  \cbda{n}
    \end{align*}
@@
    \begin{align*}
-            \cfba{n}&\cc  \cdba{\nn} \\
-            \cfba{n}&\cc  \caaa{\vald}{\valff}{\nn} \\
-            \cdba{n}&\cc  \cdba{\nn} \\
-            \cdba{n}&\cc  \cdfa{\nn}
+            \cfba{n}&\cc  \cdba{\pn} \\
+            \cfba{n}&\cc  \caaa{\vald}{\valff}{\pn} \\
+            \cdba{n}&\cc  \cdba{\pn} \\
+            \cdba{n}&\cc  \cdfa{\pn}
    \end{align*}
@@
 \Cref{rules_lemma} summarizes the basic properties of command pairs.
-The claims listed are named \emph{\namecref{ax_separate_commute}}
+The claims listed are named \emph{\namecrefs{ax_separate_commute}}
 as they can also be interpreted as inference rules in a pure
@@
 \item\mlabel{ax_same_emptyseq}
-Otherwise commands on the same node are extended by an empty sequence if their outer types represent
-an assertion command:
-$\cxynv\cc\czwnv \eqext \emptyseq$ where $[y]=[z]$, and $\cxw=\cbb$ 
-or $\cxw=\cdd$.
+Commands on the same node are extended by an empty sequence if their types are compatible,
+and their outer types represent an assertion command:
+$\cxynv\cc\czwnv \eqext \emptyseq$ where $[y]=[z]$; and 
+$[x]=[\empt]$ and $[w]=[\empt]$,
+or $[x]=[\vald]$ and $[w]=[\vald]$.
 
 \item\mlabel{ax_same_singlec}
-All other command pairs on the same node are equivalent to a single command:
-$\cxynv\cc \czwnv \equiv \cxwnv$ where $[y]=[z]$ and $\cxw\neq\cbb$ and $\cxw\neq\cdd$.
-
-% TODO Renumber rules in script
+Command pairs on the same node are equivalent to a single command if their types are compatible,
+and their outer types do not represent an assertion command:
+$\cxynv\cc \czwnv \equiv \cxwnv$ where $[y]=[z]$; and
+neither $[x]=[\empt]$ and $[w]=[\empt]$,
+nor $[x]=[\vald]$ and $[w]=[\vald]$.
 
@@
 or an empty node at the child:
-$\cxynnv\cc\czwnv \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
+$\cxynnv\cc\czwnv \equiv \cbrk$ where $\cxy\neq\cdd$ and $\czw\neq\cbb$.
 
@@
 or a directory at the parent:
-$\cxynv\cc\czwnnv \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$.
+$\cxynv\cc\czwnnv \equiv \cbrk$ where $\cxy\neq\cbb$ and $\czw\neq\cdd$.
 
@@
 Suppose $\cxynnv$ and $\czwnv$ satisfy the conditions in the \namecref{ax_distantrel_breaks},
-and there if an $\FS$ for which $(\cxynnv\cc\czwnv)\aFS\neq\fsbroken$.
+and there is an $\FS$ for which $(\cxynnv\cc\czwnv)\aFS\neq\fsbroken$.
 If $\czw\neq\cbb$, then either $\FS(n)\neq\empty$ or $\czwnv\aFS(n)\neq\empty$,

### 2018-07-02 p2/axiom-proof.tex
Final proof

@@
 If two filesystems over $\setn$ have the same values at a node $n$,
-$\parentf{n}$ (if exists), and at all children of $n$ (if they exist),
+and at all children of $n$ (if they exist),
 then either both filesystems are broken at $n$, or none of them are.
@@
 
+\begin{proof}
 We use an inverse proof and assume $\cxynv\cc\czwmv \nequiv \czwmv\cc\cxynv$.
@@
 
-In the former case, the filesystem must be broken at $m$ or $\parentf{m}$.
-Since the set of $n$ with its granparent, parent and children; and $m$ with its grandparent, parent and children
-are disjunct, we know $\cxynv\aFS$ contains the same values around $m$ as $\aFS$.
-This leads to contradiction as from \cref{broken_local} we know
-that being broken at $m$ or $\parentf{m}$
-... WHAT ABOUT SIBLINGS? ...
-while applying $\czwmv$ to $\cxynv\aFS$ on the left-hand side resulted in a working filesystem,
-it resulted in a broken filesystem when applied to $\FS$ on the right-hand side.
-The proof is similar in the case when applying $\cxynv$ breaks the filesystem on the right-hand side.
+In the former case, based on \cref{broken_local}, 
+$\czwmv\aFS$ must be broken at $m$ or $\parentf{m}$, since it only changed at $m$.
+Let us look at the first case.
+Since $n\indep m$, we know that the parent and children of $m$ have the same value
+in $\FS$ as they do in $\cxynv\aFS$. However, this is a contradiction,
+as applying $\czwmv$ to $\FS$ leads to a broken filesystem,
+but applying it to $\cxynv\aFS$ (from the left side) does not.
+
+Therefore $\czwmv\aFS$ must be broken at $\parentf{m}$.
+By definition this means that its value at $\parentf{m}$ cannot be a directory.
+Also, reasoning similar to the above shows that it is only possible if $\cxynv$ changes
+the environment of $\parentf{m}$, which, since $n\indep m$, is only possible
+if $n$ and $m$ are siblings.
+
+Since then the value at $\parentf{n}=\parentf{m}$ is not changed by either command,
+we know it cannot be a directory in $\FS$, either, and that therefore
+$\FS$ is empty at all children of the parent node.
+Since by assumption $\czwmv\aFS$ is broken, $[w]\neq[\empt]$ must hold.
+However, this is a contradiction, as this would necessarily mean that
+the left side, $\czwmv(\cxynv\aFS)$ must also be broken.
+
+We can proceed in the same fashion if $\czwmv\aFS$ is not broken, but
+$(\czwmv\cc\cxynv)\aFS$ is.
+\end{proof}
+
+\cref{ax_separate_nobreaks}
+
+\begin{proof}
+\end{proof}

### 2018-07-02 p2/axiom-proof.tex
More proofs

@@
+TODO From filesystem definition
+
 In this section we offer proofs for the \namecrefs{ax_separate_commute} listed in
@@
 do not have the tree property.
-In this case we continue to say that the filsystem is broken,
-but we also describe the filesystem values at certain nodes.
+In such cases we continue to say that the filsystem is broken,
+but we also continue to describe the filesystem values at nodes in $\setn$.
 Also, in order to pinpoint the region that violates the tree property,
@@
 
-Accordingly, we also extend filsystem commands from partial to full functions,
-and assume that they return a filesystem we can describe in all cases.
+Accordingly, where needed, we also implicitly extend filesystem commands
+so that they would return a filesystem even if it violates the tree property.
+They continue to be undefined in cases where their input types are incompatible
+with the input filesystem.
 We note that once a filesystem is broken, it stays broken, even if
-after a subsequent command it no longer violates the tree property.
+after a subsequent command it would no longer violate the tree property.
 
@@
 whether a filesystem is \emph{broken at a node $n$} is determined only
-by the values at $n$, $\parentf{n}$, and the children of $n$.
+by the values at $n$ and the children of $n$.
 In other words,
@@
 By definition this means that its value at $\parentf{m}$ cannot be a directory.
-Also, reasoning similar to the above shows that it is only possible if $\cxynv$ changes
+Also, reasoning similar to the above shows that this is only possible if $\cxynv$ changes
 the environment of $\parentf{m}$, which, since $n\indep m$, is only possible
@@
 \begin{proof}
+It is easy to see that over any $\setn$ one can construct a filesystem that neither command breaks.
+Since $n\indep m$, it is always possible to set all descendants of both $n$ and $m$ empty,
+and have a directory at all ancestors of both $n$ and $m$. In such positions any values are permissible,
+so neither command will break the filesystem.
 \end{proof}
+
+\cref{ax_same_breaks}
+
+\begin{proof}
+This is trivial, as either $\cxynv$ breaks the filesystem, or, if it does not, then
+we know $[\cxynv\aFS(n)]=[y]\neq [z]$, and therefore $\czwnv$ will break the filesystem.
+\end{proof}
+
+\cref{ax_same_emptyseq}
+
+\begin{proof}
+From the conditions we see that for every $\FS$,
+$\FS$ and $(\cxynv\cc\czwnv)\aFS$ have the same values at every node,
+while the latter can still be broken if $\cxynv\aFS$ is broken.
+This is equivalent to saying that where the $\cxynv\cc\czwnv$ function is defined,
+it is the identity function, that is, it is extended by $\emptyseq$.
+\end{proof}
+
+\cref{ax_same_singlec}
+
+\begin{proof}
+It is easy to see that where both $\cxynv\cc \czwnv$ and $\cxwnv$ are defined
+(they do not break the filesystem), they are equivalent.
+What remains to show is that they break the same set of filesystems.
+If $(\cxynv\cc \czwnv)\aFS$ is not broken, then we know that neither of
+$\FS$, $\fsreplacement{\FS}{n}{y}$ or $\fsreplacement{\FS}{n}{w}$ is broken,
+and therefore $\cxwnv$ does not break $\FS$.
+Conversely, if $\cxwnv$ does not break $\FS$, then 
+we know that $\FS$ and $\fsreplacement{\FS}{n}{w}$ are not broken.
+Also, as
+either $[x]\neq[\empt]$ or $[w]\neq[\empt]$,
+there must be a directory at $\FS(\parentf{n})$,
+and so $\fsreplacement{\FS}{n}{y}$ cannot be broken, either,
+as any value is permissible at $n$.
+This is equivalent to saying that $\cxynv\cc \czwnv$ does not break the filesystem.
+\end{proof}
+
+\cref{ax_directchild_breaks}
+
+\begin{proof}
+\end{proof}

### 2018-07-02 p2/axioms.tex
More proofs

@@
 or an empty node at the child:
-$\cxynnv\cc\czwnv \equiv \cbrk$ where $\cxy\neq\cdd$ and $\czw\neq\cbb$.
+$\cxypnv\cc\czwnv \equiv \cbrk$ where $\cxypnv\cc\czwnv$ is not a construction pair, 
+$\cxypnv\neq\caaaa{x}{y}{\pn}$ and $\czwnv\neq\cbba{n}$.
 

### 2018-07-03 p2/axiom-proof.tex
All proofs for the rules

@@
 \begin{proof}
+If neither of the commands is an assertion command, then the claim follows from
+\cref{simple_distant_pairs} in the following way.
+We use an inverse proof and assume that $\cxypnv\cc\czwnv$ is not a construction pair,
+none of the commands is an assertion command, and $\wrksx{\cxypnv\cc\czwnv}$.
+Therefore \cref{simple_distant_pairs} applies to this sequence, and the two commands
+must form a construction or destruction pair. This is a contradiction as due to
+the relationship between the nodes, they cannot form a destruction pair, and
+they do not form a construction pair by assumption.
+
+Otherwise, let $\FS_1$ be $\cxypnv\aFS$, and $\FS_2$ be $(\cxypnv\cc\czwnv)\aFS$.
+If $\cxypnv=\cbba{\pn}$ (the only assertion command it can be given the conditions),
+then either $\FS_1$ is broken, or
+$\FS(\pn)=\FS_1(\pn)=\FS_2(\pn)=\empt$.
+Since $\czwnv\neq\cbba{n}$, we know that either $\czwnv$ breaks $\FS_1$,
+or, depending on $z$ and $w$, either $\FS_1(n)\neq\empt$ or $\FS_2(n)\neq\empt$.
+In any case $\FS_2$ will be broken at $\pn$ which is empty but at one point has a non-empty child.
+
+Finally, if $\czwnv=\cdda{n}$, we can proceed in a similar way,
+as since $\cxypnv\neq\cdda{n}$, we know at one point the value at $\pn$ is not a directory.
 \end{proof}
+
+\cref{ax_directparent_breaks}
+
+\begin{proof}
+This proof follows the same logic as that of \cref{ax_directchild_breaks},
+using destruction pairs instead of construction pairs.
+\end{proof}
+
+\cref{ax_distantrel_breaks}
+
+\begin{proof}
+Suppose $\cxynnv$ and $\czwnv$ satisfy the conditions,
+and there is an $\FS$ for which $(\cxynnv\cc\czwnv)\aFS\neq\fsbroken$.
+If $\czwnv\neq\cbba{n}$, then either $\FS(n)\neq\empty$ or $\czwnv\aFS(n)\neq\empty$,
+and therefore $\FS(\parentf{n})$ must be a directory for the filesystem to satisfy
+the tree property at all times.
+However, from $\cxynnv\neq\cdda{\nn}$ we also know that either $\FS(\nn)$ 
+(before applying $\cxynv$) or $\cxynv\aFS(\nn)$ (after applying $\cxynv$)
+is not a directory. Depending on which is true, we have a point in the sequence
+of applying the commands where the filesystem cannot satify the tree property
+and therefore becomes broken as $\parentf{n}$, a descendant of $\nn$, contains
+a directory and so must all its ancestors.
+\end{proof}
+
+\cref{ax_child_assert}
+
+\begin{proof}
+Since $\cxynnv\neq\cdda{\nn}$, we know that
+either $\cxynnv\aFS$ is broken, or, depending on $x$ and $y$,
+either $\FS(\nn)\neq\vald$, or $\cxynnv\aFS(\nn)\neq\vald$.
+In the latter two cases $\FS$ must be empty at all descendants of $\nn$
+for it to satisfy the tree property.
+The assertion command $\cbba{n}$ will therefore not break $\FS$.
+\end{proof}
+
+\cref{ax_parent_assert}
+
+\begin{proof}
+This proof follows the same logic as that of \cref{ax_child_assert}.
+\end{proof}
+
+\cref{ax_assert}
+
+\begin{proof}
+As for an assertion command $\cxynv$, $x=y$, we see that it either
+breaks a filesystem, or leaves it in the same state.
+\end{proof}

### 2018-07-03 p2/axioms.tex
All proofs for the rules

--- 2018-07-02 p2/axioms.tex
@@
 or an empty node at the child:
-$\cxynnv\cc\czwnv \equiv \cbrk$ where $\cxy\neq\cdd$ and $\czw\neq\cbb$.
+$\cxypnv\cc\czwnv \equiv \cbrk$ where $\cxypnv\cc\czwnv$ is not a construction pair, 
+$\cxypnv\neq\cdda{\pn}$ and $\czwnv\neq\cbba{n}$.
 
@@
 or a directory at the parent:
-$\cxynv\cc\czwnnv \equiv \cbrk$ where $\cxy\neq\cbb$ and $\czw\neq\cdd$.
+$\cxynv\cc\czwpnv \equiv \cbrk$ where $\cxynv\cc\czwpnv$ is not a destruction pair,
+$\cxynv\neq\cbba{n}$ and $\czwpnv\neq\cdda{\pn}$.
 
@@
 \[ \cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n} \] 
-where $\nn\descendant n$ and $\cxy\neq\cdd$.
+where $\nn\descendant n$ and $\cxynnv\neq\cdda{\nn}$.
 
@@
 \[ \cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn} \]
-where $\nn\descendant n$ and $\cxy\neq\cbb$.
+where $\nn\descendant n$ and $\cxynv\neq\cbba{n}$.
 
@@
 
-These claims are easy but tedious to check.
-To ensure that all cases were considered when verifying these claims,
-a computer program was prepared that models the relevant parts of
-a filesystem and checks the results of applying all different command pairs
-against the above claims.\footnote{The program is accessible at \\ 
-https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/p2/prove.py.}
-
-For \cref{ax_distantrel_breaks}, we also provide a simple proof.
-Suppose $\cxynnv$ and $\czwnv$ satisfy the conditions in the \namecref{ax_distantrel_breaks},
-and there is an $\FS$ for which $(\cxynnv\cc\czwnv)\aFS\neq\fsbroken$.
-If $\czw\neq\cbb$, then either $\FS(n)\neq\empty$ or $\czwnv\aFS(n)\neq\empty$,
-and therefore $\FS(\parentf{n})$ must be a directory for the filesystem to satisfy
-the tree property at all times.
-However, from $\cxy\neq\cdd$ we also know that either $\FS(\nn)$ 
-(before applying $\cxynv$) or $\cxynv\aFS(\nn)$ (after applying $\cxynv$)
-is not a directory. Depending on which is true, we have a point in the sequence
-of applying the commands where the filesystem cannot satify the tree property
-and therefore becomes broken as $\parentf{n}$, a descendant of $\nn$, contains
-a directory and so must all its ancestors.
-
-For \cref{ax_child_assert,ax_parent_assert}, we note that these claims
-easily follow from the fact that the commands are adjacent to each other.
-
-Finally, we have included \cref{ax_directchild_breaks,ax_directparent_breaks}
+We have included \cref{ax_directchild_breaks,ax_directparent_breaks}
 for completeness, but we will use the more generic \cref{simple_distant_pairs},

### 2018-07-03 p2/axiom-def.tex
Restating rules for proofs

% ax_separate_commute
\newcommand{\axaxseparatecommute}{
Commands on incomparable nodes commute: $\cxynv\cc\czwmv \equiv \czwmv\cc\cxynv$ where $n\unrel m$.
}

% ax_separate_nobreaks
\newcommand{\axaxseparatenobreaks}{
Commands on incomparable nodes also do not break all filesystems:
$\wrksx{\cxynv\cc\czwmv}$ where $n\unrel m$.
}

% ax_same_breaks
\newcommand{\axaxsamebreaks}{
Commands on the same node break every filesystem if their types are incompatible:
$\cxynv\cc\czwnv \equiv \cbrk$ where $[y]\ne [z]$.
}

% ax_same_emptyseq
\newcommand{\axaxsameemptyseq}{
Commands on the same node are extended by an empty sequence if their types are compatible,
and their outer types represent an assertion command:
$\cxynv\cc\czwnv \eqext \emptyseq$ where $[y]=[z]$; and 
$[x]=[\empt]$ and $[w]=[\empt]$,
or $[x]=[\vald]$ and $[w]=[\vald]$.
}

% ax_same_singlec
\newcommand{\axaxsamesinglec}{
Command pairs on the same node are equivalent to a single command if their types are compatible,
and their outer types do not represent an assertion command:
$\cxynv\cc \czwnv \equiv \cxwnv$ where $[y]=[z]$; and
neither $[x]=[\empt]$ and $[w]=[\empt]$,
nor $[x]=[\vald]$ and $[w]=[\vald]$.
}

% ax_directchild_breaks
\newcommand{\axaxdirectchildbreaks}{
Commands on a parent and a child node break every filesystem
if the pair is not a construction pair
and the commands do not simply assert a directory at the parent
or an empty node at the child:
$\cxypnv\cc\czwnv \equiv \cbrk$ where $\cxypnv\cc\czwnv$ is not a construction pair, 
$\cxypnv\neq\cdda{\pn}$ and $\czwnv\neq\cbba{n}$.
}

% ax_directparent_breaks
\newcommand{\axaxdirectparentbreaks}{
Commands on a child and parent node break every filesystem
if the pair is not a destruction pair
and the commands do not simply assert an empty node at the child
or a directory at the parent:
$\cxynv\cc\czwpnv \equiv \cbrk$ where $\cxynv\cc\czwpnv$ is not a destruction pair,
$\cxynv\neq\cbba{n}$ and $\czwpnv\neq\cdda{\pn}$.
}

% ax_distantrel_breaks
\newcommand{\axaxdistantrelbreaks}{
Commands on distant relatives break all filesystems
if the commands do not simply assert a directory at the ancestor
or an empty node at the descendant:
$\cxynnv\cc\czwnv \equiv \cbrk$
and $\czwnv\cc\cxynnv \equiv\cbrk$
where $\nn\descendant n$ and $\nn\neq\parent(n)$, and $\cxynnv\neq\cdda{\nn}$ and $\czwnv\neq\cbba{n}$.
}

% ax_child_assert
\newcommand{\axaxchildassert}{
An assertion command can be freely added on a descendant node
next to a command that does not simply assert a directory:
\[ \cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n} \] 
where $\nn\descendant n$ and $\cxynnv\neq\cdda{\nn}$.
}

% ax_parent_assert
\newcommand{\axaxparentassert}{
An assertion command can be freely added on an ancestor node
next to a command that does not simply assert an empty node:
\[ \cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn} \]
where $\nn\descendant n$ and $\cxynv\neq\cbba{n}$.
}

% ax_assert
\newcommand{\axaxassert}{
All assertion commands can be removed as the empty sequence extends them:
$\cdda{n}\eqext\emptyseq$ and $\cbba{n}\eqext\emptyseq$.
}

### 2018-07-03 p2/axioms.tex
Restating rules for proofs

@@
 TODO elaborates this approach.
+In \cref{axiom_proof} we offer proofs of each of the
+\emph{\namecrefs{ax_separate_commute}} based on our model of filesystems.
 
@@
 \item\mlabel{ax_separate_commute}
-Commands on incomparable nodes commute:
-$\cxynv\cc\czwmv \equiv \czwmv\cc\cxynv$ where $n\unrel m$.
+\axaxseparatecommute
 
 \item\mlabel{ax_separate_nobreaks}
-Commands on incomparable nodes also do not break all filesystems:
-$\wrksx{\cxynv\cc\czwmv}$ where $n\unrel m$.
+\axaxseparatenobreaks
 
 \item\mlabel{ax_same_breaks}
-Commands on the same node break every filesystem if their types are incompatible:
-$\cxynv\cc\czwnv \equiv \cbrk$ where $[y]\ne [z]$.
+\axaxsamebreaks
 
 \item\mlabel{ax_same_emptyseq}
-Commands on the same node are extended by an empty sequence if their types are compatible,
-and their outer types represent an assertion command:
-$\cxynv\cc\czwnv \eqext \emptyseq$ where $[y]=[z]$; and 
-$[x]=[\empt]$ and $[w]=[\empt]$,
-or $[x]=[\vald]$ and $[w]=[\vald]$.
+\axaxsameemptyseq
 
 \item\mlabel{ax_same_singlec}
-Command pairs on the same node are equivalent to a single command if their types are compatible,
-and their outer types do not represent an assertion command:
-$\cxynv\cc \czwnv \equiv \cxwnv$ where $[y]=[z]$; and
-neither $[x]=[\empt]$ and $[w]=[\empt]$,
-nor $[x]=[\vald]$ and $[w]=[\vald]$.
+\axaxsamesinglec
 
 \item\mlabel{ax_directchild_breaks}
-Commands on a parent and a child node break every filesystem
-if the pair is not a construction pair
-and the commands do not simply assert a directory at the parent
-or an empty node at the child:
-$\cxypnv\cc\czwnv \equiv \cbrk$ where $\cxypnv\cc\czwnv$ is not a construction pair, 
-$\cxypnv\neq\cdda{\pn}$ and $\czwnv\neq\cbba{n}$.
+\axaxdirectchildbreaks
 
 \item\mlabel{ax_directparent_breaks}
-Commands on a child and parent node break every filesystem
-if the pair is not a destruction pair
-and the commands do not simply assert an empty node at the child
-or a directory at the parent:
-$\cxynv\cc\czwpnv \equiv \cbrk$ where $\cxynv\cc\czwpnv$ is not a destruction pair,
-$\cxynv\neq\cbba{n}$ and $\czwpnv\neq\cdda{\pn}$.
+\axaxdirectparentbreaks
 
 \item\mlabel{ax_distantrel_breaks}
-Commands on distant relatives break all filesystems
-if the commands do not simply assert a directory at the ancestor
-or an empty node at the descendant:
-$\cxynnv\cc\czwnv \equiv \cbrk$
-and $\czwnv\cc\cxynnv \equiv\cbrk$
-where $\nn\descendant n$ and $\nn\neq\parent(n)$, and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
+\axaxdistantrelbreaks
 
 \item\mlabel{ax_child_assert}
-An assertion command can be freely added on a descendant node
-next to a command that does not simply assert a directory:
-\[ \cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n} \] 
-where $\nn\descendant n$ and $\cxynnv\neq\cdda{\nn}$.
+\axaxchildassert
 
 \item\mlabel{ax_parent_assert}
-An assertion command can be freely added on an ancestor node
-next to a command that does not simply assert an empty node:
-\[ \cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn} \]
-where $\nn\descendant n$ and $\cxynv\neq\cbba{n}$.
+\axaxparentassert
 
 \item\mlabel{ax_assert}
-All assertion commands can be removed as the empty sequence extends them:
-$\cdda{n}\eqext\emptyseq$ and $\cbba{n}\eqext\emptyseq$.
+\axaxassert
 

### 2018-07-03 p2/ordering.tex
Minor fixes

@@
 In fact, this \namecref{simple_distant_pairs} is the general case
-of \cref{ax_directchild_breaks,ax_directparent_breaks}.
+of \cref{ax_directchild_breaks,ax_directparent_breaks} when there are no assertion commands.
 
@@
 This follows directly from \cref{simple_distant_pairs}.
-We use an inverse proof and assume $\wrks{S'}$.
+We use an inverse proof and assume $\wrksx{S'}$.
 If $S'\not\in\orderset{S}$ then by \cref{def_orderset}
@@
 $\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
-\[ \orderset{S} = \{T \whr T\equiv S \wedge T \mbox{~is simple} \}. \]
+\[ \orderset{S} = \{T \whr T\equiv S \:\wedge\: T \mbox{~is simple} \}. \]
 \end{mylem}
 
-% TODO APPENDIX
 \begin{proof}
@@
 and so $[y_\indx]\neq[\vald]$, while in a subsequence of $T$ for a given $\indx$,
-$[y_\indx]=[\vald]$ must be true by the definition of $\ordersetsign$.
+$[y_\indx]=[\vald]$ must be true by definition of $\ordersetsign$.
 \end{proof}

### 2018-07-03 p2/rec-intro.tex
Updated script
Revisions

@@
 and show that these are the longest sequences with this property, that is,
-adding any further command from $\reca$ or $\recb$ will break the filesystems.
+adding any further command to $\reca$ or $\recb$ will break the filesystems.
 
@@
 the updates applied to $\FS$ to arrive at replicas $\FS_A$ and $\FS_B$:
-\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
+\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \mbox{~and~}  \alpha\indep \bmanp }. \]
+$\recb$ can be obtained in a similar way by reversing $A$ and $B$
+in the definition.
 \end{mydef}
@@
 
-$\recb$ can be obtained in a similar way by reversing $A$ and $B$
-in the definition.
-
-\bigskip
-
-\noindent
+\myskip
 Next, we would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,

### 2018-07-03 p2/works-inverse.tex
Revisions

@@
 
-\subsection{Domains of Sets}
+\subsection{Domains of Sets of Command Sequences}
 
-\begin{mydef}[Sets of sequences]
+\begin{mydef}[Sets of sequences, their domains]
 As we will frequently refer to sets of fequences,
@@
 to denote such sets for brevity.
-
 We will write $\Dom{\sqs{A}}$ for $\bigcap_{A\in\sqs{A}} \Dom{A}$,
@@
 or $\worksm{A}{B}$ to mean $\worksmbb{A}{B}$.
-
 Also, we write $\worksmnil{\sqs{A}}$ to mean that
@@
 If $S$ and $T$ are minimal sequences, $\worksmnilb{S,T}$,
-and there are commands on node $n$ in both $S$ ($\cxynv\in A$) and $T$ ($\czwnv\in B$),
+and there are commands $\cxynv\in S$ and $\czwnv\in T$ on the same node $n$,
 then the input types of these commands must match, i.e. $[x]=[z]$.

### 2018-07-03 p2/ordering.tex
Clarifications

@@
 and $\FS$ be a filesystem that they are defined on.
-
 We use a proof by contradiction, and assume that they do not contain the same commands.
@@
 As $A$ is simple, we know that $\cxynv$ is not an assertion command,
-and therefore $[x]\neq [y]$ and $\FS(n)\neq y$ as $[\FS(n)]=[x]$.
-If so, then if $B$ has no command on $n$, then $B\aFS(n)=\FS(n)$ and
+and therefore either $[x]\neq [y]$, or it is a replacement command.
+
+If $[x]\neq [y]$, then $\FS(n)\neq y$ as $[\FS(n)]=[x]$.
+Therefore, if $B$ has no command on $n$, then $B\aFS(n)=\FS(n)\neq y=A\aFS(n)$ and
 $A$ and $B$ cannot be equivalent.
-Otherwise we know that $[z]=[x]$ as $B$ does not break $\FS$ either,
+If $B$ includes $\czwnv$, then we know that $[z]=[x]$ as $B$ does not break $\FS$ either,
 and that $w=y$ as $B\aFS(n)$ must
 be $y$ and $B$ only has one command on $n$.
-However, then $\czwnv=\cxynv$, which is a contradiction.
+This means that $\czwnv=\cxynv$, which is a contradiction.
+
+If $\cxynv$ is a replacement command, then we know $[x]=[y]=[\valfx]$, and
+$[\FS(n)]=[\valfx]$. If $\FS(n)=y$, then instead of this filesystem,
+consider $\fsreplacement{\FS}{n}{\valf}$ where $\valf$ is any file value
+other than $y$.
+(We assume that there are more than one file values; if this is not so,
+$\cffa{n}$ becomes an assertion command.)
+From here the proof concludes in the same way as above.
 \end{proof}
@@
 For a simple sequence $\wrksx{S}$,
-$\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
-\[ \orderset{S} = \{T \whr T\equiv S \:\wedge\: T \mbox{~is simple} \}. \]
+$\orderset{S}$ is the set of all simple sequences equivalent to $S$.
+% that is, \[ \orderset{S} = \{T \whr T\equiv S \:\wedge\: T \mbox{~is simple} \}. \]
 \end{mylem}
@@
 \begin{proof}
-First, we prove, by contradiction, that if a simple sequence $T$, $T\equiv S$, then $T\in\orderset{S}$.
+First, we prove, by contradiction, that if $T$ is a simple sequence and $T\equiv S$, then $T\in\orderset{S}$.
 We use an inverse proof and assume $T\equiv S$ and $T\not\in\orderset{S}$.
@@
 
-\begin{mydef}[$\ordsign$]
 It follows from \cref{simple_reorder_equiv} that given a simple set of commands $S$,
@@
 where the internal order of the commands is irrelevant.
-We write $\ordp{S}$ to represent this endofunction.
+\begin{mydef}[$\ordp{S}$]
+For a simple set or sequence of commands $S$,
+$\ordp{S}$ is the unique partial endofunction on filesystems
+defined by any order in $\orderset{S}$.
 We leave $\ordp{S}$ undefined if such an order does not exist.

### 2018-07-03 p2/def-commands.tex
Proofs for the rules

@@
 
-TODO DELETE:
-As suggested above, we will frequently only investigate
-the types of the input and output values of a command
-(its input and output types), and write
-$\cxy=\czw$, by which we mean $[x]=[z]$ and $[y]=[w]$.
-
 We note that a command or a sequence of commands is applied to a filesystem
@@
 while destruction commands shrink it;
-the replacement command replaces a file value with a (presumably different) file value,
+the replacement command replaces a file value with a file value
+(which may or may not be different from the original value),
 and assertion commands either break the filesystem, or assert the type of the value at a node.

### 2018-07-03 p2/rec-sound.tex
Various improvements
Updated script
Minor improvements

@@
 where, to restate \cref{def:reconciliation},
-\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
+\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \mbox{~and~}  \alpha\indep \bmanp }. \]
 \end{myth}
@@
 \begin{proof}
-We prove that
-if all commands are marked in $A$ that also appear in $B$,
-then there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.
+Mark those commands in $A$ that are also in $B$.
+We show that
+there is an $A'$ in $\orderset{A}$ in which all marked commands are at the beginning.
 
@@
 In the first case, swapping the commands results in a sequence equivalent to $A$,
-and we show that the last two cases are impossible as they would lead to contradiction.
+and we show that the last two cases are impossible.
 
@@
 
-\bigskip
-
-\noindent
 We would like to prove that $\worksmbx{A,B}{B\cc \reca}$.
@@
 to the beginning of $A$ and $B$, and so this is equivalent to
-\[ \worksmbx{\acb\cc\amb, \acb\cc\bma}{\acb\cc \bma\cc \reca}. \]
+\[ \worksm{\big\{\acb\cc\amb,~ \acb\cc\bma\big\}}{\acb\cc \bma\cc \reca}. \]
 
@@
 \begin{itemize}
-\item $\amb$ to $S$
-\item $\reca$ to $S^*$
-\item $\bma$ to $T$
+\item $\amb$ to $S$,
+\item $\reca$ to $S^*$,
+\item $\bma$ to $T$,
 \item and $\acb$ to $U$.
@@
 This is because from $\worksmbx{S,T}{S^*}$ trivially $\worksmbb{S,T}{S^*, T}$,
-and from $S^* \indep T$ and \cref{combine_independent_sequences} we know $\worksmbx{S^*,T}{T\cc S^*}$.
+and from $S^* \indep T$ and \cref{combine_independent_sequences} we know 
+$\worksmbx{S^*,T}{T\cc S^*}$.
 Combining the two we get $\worksmbx{S,T}{T\cc S^*}$,
@@
 
-\bigskip
-
-\noindent
 To restate some results above, we therefore already know the following:
@@
 \item $S\cap T = \amb \cap \bma = \emptyset$
-\item 
-$S^*$ is the largest subset of $S$ for which $S^*\indep T$, as
-$\reca$ is the largest subset of $\amb$ for which $\reca\indep\bma$
+\item $S^*$ is the largest subset of $S$ for which $S^*\indep T$, as
+$\reca$ is the largest subset of $\amb$ for which $\reca\indep\bma$.
 \end{itemize}
-
 Our theorem is therefore proven if we prove the following lemma.

### 2018-07-04 p2/axioms.tex
Unified syntax

@@
 \begin{mylem}\mlabel{incomparable_is_independent}
-Two different commands that are not assertion commands are independent 
-iff the nodes they change are incomparable. In other words,
-\[ \cxynv\indep\czwmv \Longleftrightarrow n\unrel m \]
-if $\cxynv\neq\czwmv$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
+Two $\cxynv$ and $\czwmv$ are different commands,
+and none of them is an assertion command, then
+$\cxynv\indep\czwmv$ if and only if $n\unrel m$.
 \end{mylem}

### 2018-07-04 p2/def-commands.tex
Unified syntax

@@
 \begin{mydef}[Filesystem commands]
-Filesystem commands are partial endofunctions on filesystems:
-\[ \alpha: \setfs \nrightarrow \setfs \]
-A command $\alpha$ is not defined on filesystems where it returns an error.
+Filesystem commands are partial endofunctions on filesystems,
+which are not defined on filesystems where they return an error.
 The commands are represented using triplets of the form

### 2018-07-04 p2/rec-complete.tex
More TODO
Unified syntax

@@
 % -------------------------
-% This is where we're using |D|=1
 
@@
 If $A$ and $B$ are simple sequences,
-$S'\in\orderset{\ambnp}$,
-and $S$ is a subsequence of $S'$ that
+and $S$ is a subsequence of $S'\in\orderset{\ambnp}$ that
 contains a command $\cxynv$ for which $\cxynv\nindep\bmanp$,
@@
 The proof is similar to the ones we have seen above.
-Let $T$ be an arbitrary sequence in $\orderset{\bmanp}$.
+Let $T$ be an arbitrary sequence from $\orderset{\bmanp}$.
 Without loss of generality, we assume that $\cxynv$ is the first command in $S$
@@
 
+% TODO Used elsewhere too!
 From the proof it is apparent that this result depends on $|\setd|=1$.

### 2018-07-04 p2/rec-sound.tex
Unified syntax

@@
 If
-{\condSimple} $S$ and $T$ are simple sequences,
-{\condDisj} $S\cap T=\emptyset$,
-and {\condApr} $S^*$ is the largest subset of $S$ where $S^*\indep T$,
+{\rm\condSimple} $S$ and $T$ are simple sequences,
+{\rm\condDisj} $S\cap T=\emptyset$,
+and {\rm\condApr} $S^*$ is the largest subset of $S$ where $S^*\indep T$,
 then
@@
 \end{mylem}
-
 \begin{proof}
 This is trivial unless $\worksmnilb{S,T}$, so we assume that it is the case.
-
 The proof is similar to that of \cref{can_move_intersection}.
@@
 In the first case, swapping the commands results in a sequence equivalent to $S$,
-and we show that the other two cases are not possible as they would lead to a contradiction.
+and we show that the other two cases are not possible as they would lead to contradiction.
 
@@
 as $\czwmv$ is not part of $S^*$.
-\begin{gather*}
-S = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
-T = \cdots\cc  \cqrov\cc \cdots
-\end{gather*}
+% \begin{gather*}
+% S = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots \\
+% T = \cdots\cc  \cqrov\cc \cdots
+% \end{gather*}
 Based on \cref{incomparable_is_independent} we know this means that

### 2018-07-04 p2/intro.tex
Improved introduction

@@
 
-In this paper we build on our previous work done 
+We extend significantly the results of the previous work done
 with Prof. Norman Ramsey
@@
 then under certain circumstances they are not compatible and will give rise to conflicts.
-Accordingly, in this paper the commutativity of command pairs and their other properties
+Accordingly, in this paper command pairs, their commutativity and other properties
 play a special role.
@@
 
-We start by defining a model of filesystems and a set of commands
-that we will use to describe updates and modifications in \cref{sec_def}.
-This is followed by investigating the properties and behaviors
-of command pairs in \cref{section_axioms}.
-\Cref{sec_update} describes update detection, and it is
-in \cref{ordering} that we describe how commands can be ordered
-and prove that under some simple conditions all valid orders
-have the same effect.
-
-\Cref{sec_rec} defines our reconciliation 
-and conflict detection algorithms.
-We then proceed to prove that the output of reconciliation
-is correct in the sense that 
-it can be applied to the replicas without causing an error,
-and it is maximal
-inasmuch as no further updates can be applied under any circumstances.
-In order to be able to do this, we introduce
-the concept of \emph{conditional operation} of sequences of commands,
-and show that it has a number of highly convenient properties.
-We finish by comparing our results to other research
-and outlining directions for further work
-on the introduced algebraic system.
-
-The approach in the present paper offers an improvement
-over results presented in \cite{NREC} in multiple ways.
+The approach presented in this paper offers an improvement
+over results desribed in \cite{NREC} in multiple ways.
 We introduce a new set of commands that is symmetric and
@@
 our reconciliation algorithm, but also makes it maximal.
-
-The previous work also lacked proofs that the update detection
+\cite{NREC} also lacked proofs that the update detection
 and reconciliation algorithms it presented work as intended,
@@
 that is worthy of interest and of further research on its own.
+
+The paper is organised as follows.
+We start by defining a model of filesystems and a set of commands
+that we will use to describe updates and modifications in \cref{sec_def}.
+This is followed by investigating the properties and behaviors
+of command pairs in \cref{section_axioms}.
+\Cref{sec_update} describes update detection and ordering filesystem commands.
+The main result of this section if that under some simple conditions,
+a set of filesystem commands executed in any feasible order leads
+to the same changes in the filesystem.
+The reconciliation and conflict detection algorithm is defined in
+\cref{sec_rec}, which merges two sets of commands.
+We then proceed to prove that the output of reconciliation
+is correct in the sense that 
+it can be applied to the replicas without causing an error,
+and it is maximal
+inasmuch as no further updates can be applied under any circumstances.
+In order to be able to do this, we introduce
+domains of sets of command sequences,
+and show that it has a number of highly convenient properties.
+\Cref{sec_relatedwork,sec_algebra,sec_conclusion}
+discuss related work, comparing our results to other research,
+outlining directions for further work
+on the introduced algebraic system, and provide the conclusion.
+\Cref{axiom_proof} contains technical proofs for propositions on the behavior of command pairs.

### 2018-07-04 p2/comparisons.tex
Improved introduction
Updated notation

@@
-\section{Related Work}
+\section{Related Work}\mlabel{sec_relatedwork}
 
@@
 \begin{align*}
-A&=\caaa{\empt}{\valdi}{\nn}\cc\caaa{\empt}{\valf}{n} \\
-B&=\caaa{\empt}{\valdii}{\nn}
+A&=\caaa{\empt}{\valdi}{\pn}\cc\caaa{\empt}{\valf}{n} \\
+B&=\caaa{\empt}{\valdii}{\pn}
 \end{align*}
-where $\parent(n)=\nn$ (\cite{NREC} did not require all directories to have the same value).
+(\cite{NREC} did not require all directories to have the same value).
 Clearly $\caaa{\empt}{\valf}{n}$ could be applied to $\FS_B$, but it is not as
@@
 (In other words, 
-$\FS_A(n)\not\in\setd \vee \FS_B(n)\not\in\setd$; see section 4.1 in \cite{BP}.
+$[\FS_A(n)]\neq[\vald]$ or $[\FS_B(n)]\neq[\vald]$; see section 4.1 in \cite{BP}.
 Let us note that there is an alternative approach to defining an algorithm for
@@
 We use the example we described in \cite{NREC},
-where $\nn=\parent(n)$ and $\FS(\nn)$ is a directory and $\FS(n)$ is a file, and
+where $\FS(\pn)$ is a directory and $\FS(n)$ is a file, and
 the two replicas are derived in the following way:
 \begin{gather*}
-\FS_A = \cfba{n} \cc \cdba{\nn} \aFS \\
+\FS_A = (\cfba{n} \cc \cdba{\pn}) \aFS \\
 \FS_B = \cfba{n} \aFS.
 \end{gather*}
-Then, $\nn$ is dirty in both replicas:
+Then, $\pn$ is dirty in both replicas:
 in $\FS_A$ it was modified, and in $\FS_B$ one of its descendants was modified.
-Moreover, $\FS_A(\nn)\neq\FS_B(\nn)$ and $\FS_A(\nn)=\empt\not\in\setd$,
-and therefore a conflict is detected at $\nn$.
+Moreover, $\FS_A(\pn)\neq\FS_B(\pn)$ and $[\FS_A(\pn)]\neq[\vald]$ as it is empty.
+Therefore, a conflict is detected at $\pn$.
 (This behaviour is preserved in the more recent Harmony synchronizer.
@@
 Our reconciliation algorithm detects no conflicts;
-instead, it propagates $\cdba{\nn}$ to $\FS_B$, which we think is as expected
+instead, it propagates $\cdba{\pn}$ to $\FS_B$, which we think is as expected
 and desired.
@@
 and therefore there is a conflict at $n$ in the state-based reconciler.
+
 If $n=m$, this follows from the fact that $\cxynv\neq\czwmv$ 
 (because they are not in $A\cap B$),
-as from \cref{worksinputmatch} we have $X=Z$,
-and therefore the above can only be true
-if $\FS_A(n)=\valvy\neq\valvw=\FS_B(n)$.
-If $n\descendant m$ and there is no command on $n$ in $B$, then it is also
-true as $\cxynv$ is not an assertion command, and therefore 
+as from \cref{worksinputmatch} we have $[x]=[z]$,
+and therefore necessarily $y\neq w$,
+that is, $\FS_A(n)=y\neq w=\FS_B(n)$.
+
+If $n\descendant m$ and there is no command on $n$ in $B$, then 
+because $\cxynv$ is not an assertion command, we again have
 $\FS_A(n)\neq\FS(n)=\FS_B(n)$, where $\FS$ is the common ancestor of the replicas.

### 2018-07-04 p2/axioms.tex
Removed cc symbol

@@
 Therefore we investigate sequences of commands with a well-defined order.
-\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
-We use ``$\cc$'' to combine commands to form a sequence, or combine sequences to form a longer sequence,
-with the meaning that the sequence is executed from left to right:
-\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
+\begin{mydef}[Sequences of commands and $\emptyseq$]
+We concatenate commands in writing to note that they form a sequence,
+and concatenate sequences of commands to form a longer sequence,
+with the meaning that the resulting sequence is executed from left to right:
+\[ (\alpha\cc\beta)\aFS = \beta(\alpha\aFS). \]
 %% monoid, but not free monoid

### 2018-07-04 p2/works-inverse.tex
Minor improvements
Removed cc symbol

@@
 
-We also prove the following lemmas.
+We proceed by proving the following lemmas.
 
@@
 $\cxynv\aFS\neq\fsbroken$ and $\czwmv\aFS\neq\fsbroken$, but
-$\cxynv\cc \czwmv\aFS=\fsbroken$.
+$(\cxynv\cc \czwmv)\aFS=\fsbroken$.
 We know $\cxynv\aFS\neq\fsbroken$ so it must be applying 
@@
 but we know $[\FS(m)]=[w]$ and so
-$[(\cxynv\aFS)(m)]=[w]$ as based on \cref{incomparable_is_independent}, $n\neq m$.
+$[\cxynv\aFS(m)]=[w]$ as based on \cref{incomparable_is_independent}, $n\neq m$.
 Second, if the new filesystem violates the tree property.
@@
 where both of the sequences are defined:
-\[ S\indep T \Rightarrow \worksmbx{S,T}{S\cc T}. \]
+\[ S\indep T \Longrightarrow \worksmbx{S,T}{S\cc T}. \]
 \end{mylem}

### 2018-07-05 p2/algebra.tex
Towards a new proof
Output labels for easier reviewing
Process todos

--- 2016-01-07 p2/algebra.tex
@@
-\section{Towards a Formal Algebra}\label{sec_algebra}
+\section{Towards a Filesystem-Free Algebra}\mlabel{sec_algebra}
 
 Similarly to \cite{NREC} we can consider creating an algebra over command sequences
-which will enable us to draw conclusions about the behaviors of the sequences
-independently of filesystems.
-This would provide a secondary model of (filesystem) commands above the model a filesystems
+which would enable us to draw conclusions about the behaviors of the sequences
+without considering the underlying filesystems.
+This would provide a secondary model of (filesystem) commands above (and indepentent of) the model of filesystems
 defined in this paper. The new model would no longer describe filesystems as such,
-but use known relationships between sequences of commands as its starting point.
+but would use known relationships between sequences of commands as its starting point.
 
@@
 using the inference rules.
-Such a system can allow us to deduce, for example, whether two sequences are equivalent
-or one extends the other
-without reference to filesystems.
+Such a system would allow us to deduce, for example, whether two sequences are equivalent
+or one extends the other without reference to filesystems.
 
@@
 the commands act on, which would require a more complicated set of symbols to represent
-in the algebra.
+in the new algebra.
 To avoid this, we think it will be more fruitful to regard commands (and sequences)
@@
 in the algebra as there are nodes in the namespace of the filesystems.
-This allows us to reduce the number of types of symbols in our algebra, and regard
+This will allow us to reduce the number of types of symbols in our algebra, and regard
 the \namecrefs{ax_separate_commute} not as axioms, but as templates for axioms
@@
 Indeed, results in the current paper can serve as building blocks of such a proof:
-the computer program used to check the \namecrefs{ax_separate_commute}
+derivations in \cref{axiom_proof} for the \namecrefs{ax_separate_commute}
 in effect proves the soundness of all axioms,
@@
 do not actually refer to specific filesystems or the definition of commands,
-but draw on known relationships and the
-\namecrefs{ax_separate_commute} in \cref{section_axioms}.
+but draw on known relationships between the commands themselves.
 In other words, many proofs are transferable to the algebra that we describe here.
@@
 of reconciliation could also be derived,
-one can also include symbols, inference rules and axioms for 
-$\works{\seqset{A}}$ and $\worksc{\seqset{A}}{\seqset{B}}$.
+one would also include symbols, inference rules and axioms for 
+$\worksmnil{\seqset{A}}$ and $\worksm{\seqset{A}}{\seqset{B}}$.
 We see proving the soundness and completeness of this extended algebra

### 2018-07-05 p2/axiom-proof.tex
Restating rules for proofs
Process todos

@@
-TODO From filesystem definition
-
-In this section we offer proofs for the \namecrefs{ax_separate_commute} listed in
-\cref{rules_lemma}.
+In this section we derive the \namecrefs{ax_separate_commute} listed in
+\cref{rules_lemma} from our filesystem model.
 For the purposes of the proofs we extend the notion of filesystems 
@@
 do not have the tree property.
-In such cases we continue to say that the filsystem is broken,
-but we also continue to describe the filesystem values at nodes in $\setn$.
-Also, in order to pinpoint the region that violates the tree property,
-we say that the filesystem is \emph{broken at $n$} if 
+This is so that we can describe the values they would acquire under certain nodes,
+and pinpoint where they may be violating the tree property.
+If they do, we continue to say that the filesystem is broken,
+and say that the filesystem is \emph{broken at $n$} if 
 $n$ is not a dictionary, but has at least one non-empty child.
+We continue to require that filesystems are not empty at finitely many nodes.
 
@@
 so that they would return a filesystem even if it violates the tree property.
-They continue to be undefined in cases where their input types are incompatible
+We continue to say that they break the filesystem in these cases,
+and commands continue to be undefined where their input types are incompatible
 with the input filesystem.
@@
 
-\cref{ax_separate_commute}
+Below we restate the \namecrefs{ax_separate_commute} defined in
+\cref{rules_lemma}.
+
+\begin{myaxproof}
+% ax_separate_commute
+\axaxseparatecommute
+\end{myaxproof}
 
@@
 
-\cref{ax_separate_nobreaks}
+\begin{myaxproof}
+% \cref{ax_separate_nobreaks}
+\axaxseparatenobreaks
+\end{myaxproof}
 
@@
 
-\cref{ax_same_breaks}
+\begin{myaxproof}
+% \cref{ax_same_breaks}
+\axaxsamebreaks
+\end{myaxproof}
 
@@
 
-\cref{ax_same_emptyseq}
+\begin{myaxproof}
+% \cref{ax_same_emptyseq}
+\axaxsameemptyseq
+\end{myaxproof}
 
@@
 
-\cref{ax_same_singlec}
+\begin{myaxproof}
+% \cref{ax_same_singlec}
+\axaxsamesinglec
+\end{myaxproof}
 
@@
 
-\cref{ax_directchild_breaks}
+\begin{myaxproof}
+% \cref{ax_directchild_breaks}
+\axaxdirectchildbreaks
+\end{myaxproof}
 
@@
 
-\cref{ax_directparent_breaks}
+\begin{myaxproof}
+% \cref{ax_directparent_breaks}
+\axaxdirectparentbreaks
+\end{myaxproof}
 
@@
 
-\cref{ax_distantrel_breaks}
+\begin{myaxproof}
+% \cref{ax_distantrel_breaks}
+\axaxdistantrelbreaks
+\end{myaxproof}
 
@@
 
-\cref{ax_child_assert}
+\begin{myaxproof}
+% \cref{ax_child_assert}
+\axaxchildassert
+\end{myaxproof}
 
@@
 
-\cref{ax_parent_assert}
+\begin{myaxproof}
+% \cref{ax_parent_assert}
+\axaxparentassert
+\end{myaxproof}
 
@@
 
-\cref{ax_assert}
+\begin{myaxproof}
+% \cref{ax_assert}
+\axaxassert
+\end{myaxproof}
 

### 2018-07-05 p2/conclusion.tex
Improved introduction
Process todos

--- 2016-01-07 p2/conclusion.tex
@@
-\section{Conclusions and Further Research}
+\section{Conclusions and Further Research}\mlabel{sec_conclusion}
 
-Apart from constructing an algebra,
+Apart from constructing a filesystem-free algebra,
 there are many other ways in which further work can extend the current results.
@@
 the updates specific to the replicas start from different points
-in the update history of the filesystem.
+in the update history of the filesystems.
 Existing research can offer pointers as to how such cases can be modelled
@@
 the simplifying assumptions we used.
+% TODO TODO TODO
 Identifying which results depend on the assumption that $|\setd|=1$
@@
 to identify and resolve a wider range of conflicts.
+
 Similarly, designing pre- and post-processors that
@@
 the demonstrated properties of minimal sequences of commands
-and conditional operation of sequences ($\workssign$)
+and domains of sets of sequences ($\worksmeqsign$)
 may also contribute to future research into algebraic structures

### 2018-07-05 p2/def-filesystem.tex
Proofs for the rules
Process todos

@@
 
-\begin{mydef}[Filesystem values: $\vald$, $\valfx$, $\empt$, $\typeeq$, $\eqclass{v}$]
+\begin{mydef}[Filesystem values: $\vald$, $\valfx$, $\empt$, $\eqclass{v}$]
 The set of values $\setv$ is partitioned into files, directories, and the empty value $\empt$.
-% TODO May be able to delete \typeeq
-For $v_1,v_2\in\setv$ we write $v_1\typeeq v_2$ iff
-$v_1$ and $v_2$ are both files, are both directories, or are both $\empt$.
-As usual, we write $[v]$ for the the equivalence class of $v\in\setv$, which represents its type.
+As usual, we write $[v]$ for the the equivalence class of $v\in\setv$ according to this partition,
+which represents its type.
 File and directory values are also denoted by $\valfx$ and $\vald$, respectively,
@@
 \[ \forall n\in\setn
-\FS(n) \neq \empt \Rightarrow \FS(\parentf{n}) \typeeq \vald \]
+\FS(n) \neq \empt \; \Longrightarrow \; [\FS(\parentf{n})] = [\vald] \]
 wherever $\parent(n)$ is defined, that is, $n$ has a parent.
@@
 $\FS$ (with or without indices) denotes a filesystem,
-and $n$, $m$ and $o$ are nodes in $\setn$,
-and we write $\nn$ for the parent of $n$, assuming it exists.
+and $n$, $m$ and $o$ are nodes in $\setn$.

### 2018-07-05 p2/works-inverse.tex
Process todos

@@
 
-\begin{myax}\mlabel{combine_independent_commands}
+\begin{mylem}\mlabel{combine_independent_commands}
 The combination of independent commands is defined on all filesystems
@@
 \[ \alpha\indep \beta \Rightarrow \worksmbx{\alpha, \beta}{\alpha\cc \beta}. \]
-\end{myax}
+\end{mylem}
 \begin{proof}
@@
 
-We name this proposition a \namecref{combine_independent_commands} 
-because to prove it, we must reach back to our filesystem model.
+In the following proof we reach back to our filesystem model.
 Let $\alpha=\cxynv$ and $\beta=\czwmv$.

### 2018-07-05 p2/axioms.tex
Process todos
Clarifying inpedendence

@@
 % precongruence: congruence of a preorder
-In other words, $\eqext$ is a preorder, and also a precongruence. % TODO
+In other words, $\eqext$ is a preorder, and also a precongruence.
 
@@
 that is, $\equiv$ is the intersection of the preorder $\eqext$ with its inverse,
-and so it is a congruence. % TODO
+and so it is a congruence.
 % old inference rule: $ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.
@@
 algebraic treatment of filesystem synchronization.
-TODO elaborates this approach.
+\Cref{sec_algebra} elaborates this approach.
 In \cref{axiom_proof} we offer proofs of each of the
@@
 as otherwise the commands, in one order or the other, would break all filesystems.
-The commands are not assertion commands, so from \cref{ax_same_singlec}
-we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $y=w$.
-% TODO Does this depend on |[D]|=1?
-Therefore $[x]=[y]=[z]=[w]$ which with $y=w$ contradicts our assumption that the commands are different.
+We also see that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $w=y$.
+Therefore $n=m$, $[x]=[y]=[z]=[w]$ and $w=y$, which contradicts our assumption that the commands are different.
 
@@
 then from \cref{ax_distantrel_breaks} we know that
-$\cxynv\cc\czwmv$ breaks all filesystems,
+$\cxynv\cc\czwmv$ breaks all filesystems as they are not assertion commands,
 which contradicts the assumption that the commands are independent.

### 2018-07-05 p2/works-inverse.tex
Clarifying inpedendence

@@
 \begin{proof}
-TODO: they are the same? FF?
+TODO: they are the same? FF? assertion commands?
 
@@
 $\czwmv$ that breaks it.
+
+We note that as the two commands are independent, they commute, and so
+the proposition is symmetric.
+Therefore, if either of the commands is an assertion command,
+without loss of generality we can assume $\cxynv$ is an assertion command.
+If so, 
+$[\cxynv\aFS(m)]=[\FS(m)]$ even if $n=m$.
+This means $\czwmv$ cannot break $\cxynv\aFS(m)$, which is a contradiction.
+
+In the remaining cases neither command is an assertion command.
+
+TODO continue here. Require not replacement?
+
 Applying a command can only result in a broken filesystem in two cases.

### 2018-07-06 p2/axioms.tex
Added todo
Description of independent commands

@@
 It is intentional that we use the same symbol for independent commands
-and sequences as for incomparable nodes. As the next
+and sequences as for incomparable nodes. As
 \namecref{incomparable_is_independent},
@@
 
-\begin{mylem}\mlabel{incomparable_is_independent}
-Two $\cxynv$ and $\czwmv$ are different commands,
+\begin{mycor}\mlabel{incomparable_is_independent}
+If $\cxynv$ and $\czwmv$ are different commands,
 and none of them is an assertion command, then
 $\cxynv\indep\czwmv$ if and only if $n\unrel m$.
+\end{mycor}
+
+To prove this, we are going to prove the following lemma,
+which characterizes independent commands in a more detailed way.
+
+\begin{mylem}\mlabel{independent_details}
+For two commands $\cxynv\indep\czwmv$ if and only if
+one of the following holds:
+\begin{itemize}
+\item $n\unrel m$;
+\item or $n=m$ and the commands are equivalent assertion or replacement commands;
+\item or $n\descendant m$ or $m\descendant n$,
+and either the command on the ancestor asserts a directory,
+or the command on the descendant asserts an empty node (or both).
+\end{itemize}
 \end{mylem}
+
 \begin{proof}
-The right-to-left part is a restatement of
+By definition we know that $\cxynv\cc\czwmv\equiv\wrksx{\czwmv\cc\cxynv}$.
+The first case is a restatement of
 \cref{ax_separate_commute,ax_separate_nobreaks}.
-
-We prove the left-to-right part by contradiction,
-assuming that both $\cxynv\indep\czwmv$ and $n\nunrel m$.
-From $n\nunrel m$
-we know that $n=m$, $n\descendant m$ or $m\descendant n$.
+Otherwise $n\nunrel m$, in which case either $n=m$, or, without loss of generality, $n\descendant m$.
 
@@
 as otherwise the commands, in one order or the other, would break all filesystems.
-We also see that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $w=y$.
-Therefore $n=m$, $[x]=[y]=[z]=[w]$ and $w=y$, which contradicts our assumption that the commands are different.
+The equivalence also implies $[x]=[z]$ as otherwise the two sides would not be defined on the same filesystem,
+as well as $y=w$ as their effects is the same.
+The two commands are therefore the same, and they are either assertion or replacement commands.
 
-The remaining case is that $n\descendant m$ or $m\descendant n$.
-If they are not directly related,
-then from \cref{ax_distantrel_breaks} we know that
-$\cxynv\cc\czwmv$ breaks all filesystems as they are not assertion commands,
-which contradicts the assumption that the commands are independent.
-From the construction and destruction pairs and 
-\cref{ax_directchild_breaks,ax_directparent_breaks} we also see that
-even if the nodes are directly related, either
-$\cxynv\cc\czwmv$ or $\czwmv\cc\cxynv$ 
-breaks all filesystems, so they again cannot be independent.
+The remaining case is that $n\descendant m$.
+If the nodes are not directly related, then \cref{ax_distantrel_breaks} gives
+the conditions in the third case in the lemma.
+If they are directly related, 
+\cref{ax_directchild_breaks,ax_directparent_breaks}
+gives the same conditions, while they also allow the commands being
+a construction or destruction pair.
+However, the reversals of construction and destruction pairs break all filesystems.
 \end{proof}
+
+\Cref{incomparable_is_independent} follows directly from \cref{independent_details}.
+While equivalent commands can hardly be thought of as independent,
+we retain this name for this relation as in most
+cases we use it on pairs of different commands that are also not assertion commands.

### 2018-07-06 p2/rec-intro.tex
Description of independent commands

@@
 
-Whether two commands are independent is easy to determine programmatically
-either based on \cref{def_indep} and the rules listed in \cref{section_axioms},
-or based on \cref{incomparable_is_independent} 
-in at most $O(x^2)$ time, where $x$ is the number of commands.
+Note that $\alpha$ is not an assertion command, and $\bmanp$ contains no assertion commands;
+also, $\alpha\not\in\bmanp$, so independence in this case is equivalent to
+the node $\alpha$ affects being incomparable to the nodes commands in $\bmanp$ affect.
+Therefore whether two commands are independent is easy to determine programmatically
+in at most $O(x^2)$ time, where $x$ is the number of commands. % TODO
 Then, to generate the sequence $\reca$ from the resulting set, 

### 2018-07-06 p2/rec-sound.tex
Description of independent commands

@@
 either $m\descendantEq o$ or $o\descendantEq m$.
-From {\condApr} we also know that $\cxynv\indep \cqrov$,
+We know none of these commands is an assertion command, and 
+from {\condDisj} that $\cqrov\neq\czwmv$.
+Also, from {\condApr} we know that $\cxynv\indep \cqrov$,
 and so because of \cref{incomparable_is_independent},
 $n\unrel o$.
-We also know none of these commands is an assertion command, and 
-from {\condDisj} that $\cqrov\neq\czwmv$.
 

### 2018-07-06 p2/works-inverse.tex
Description of independent commands

@@
 \begin{proof}
-TODO: they are the same? FF? assertion commands?
+% In the following proof we reach back to our filesystem model.
+The proposition follows from \cref{independent_details},
+and we follow the three cases listed there.
 
-In the following proof we reach back to our filesystem model.
+The first case is that $n\unrel m$ where $\alpha=\cxynv$, $\beta=\czwmv$.
+
+TODO CONTINUE
+
+Using an inverse proof we assume that for a filesystem $\FS$
+both $\cxynv\aFS$ and $\czwmv\aFS$ are defined, but $(\cxynv\cc\czwmv)\FS$ is broken.
+We know a command breaks a filesystem either if
+its input type is not compatible with the filesystem,
+or if the filesystem ceases to have the tree property.
+
+We also know that whether a filesystem has the tree property
+depends
+
+The second case is that the two commands are the same and are assertion or replacement
+commands, when the proposition is trivially true.
+Finally, the third case is that the two commands are on comparable nodes and one of them
+is an assertion command, when the proposition is again trivially true.
+
+TODO END
+
 Let $\alpha=\cxynv$ and $\beta=\czwmv$.
@@
 In the remaining cases neither command is an assertion command.
-
-TODO continue here. Require not replacement?
 

### 2018-07-06 p2/axiom-proof.tex
Clarifying inpedendence
Proof for combining independent commands

@@
 \begin{proof}
+This proof is similar to the first case in the proof of \cref{combine_independent_commands}.
+However, this result is needed for \cref{independent_details} on which that proof rests.
+
 We use an inverse proof and assume $\cxynv\cc\czwmv \nequiv \czwmv\cc\cxynv$.
@@
 This is equivalent to saying that $\cxynv\cc \czwnv$ does not break the filesystem.
+
+We note that if $\cxwnv$ is an assertion command, then it extends $\cxynv\cc\czwnv$
+instead of being equivalent to it.
 \end{proof}

### 2018-07-06 p2/works-inverse.tex
Proof for combining independent commands

@@
 The first case is that $n\unrel m$ where $\alpha=\cxynv$, $\beta=\czwmv$.
-
-TODO CONTINUE
-
 Using an inverse proof we assume that for a filesystem $\FS$
 both $\cxynv\aFS$ and $\czwmv\aFS$ are defined, but $(\cxynv\cc\czwmv)\FS$ is broken.
-We know a command breaks a filesystem either if
-its input type is not compatible with the filesystem,
-or if the filesystem ceases to have the tree property.
+Since $n\neq m$, we know the input types of the command are compatible with $\FS$,
+so $\FS$ must be broken because it violates the tree property.
 
-We also know that whether a filesystem has the tree property
-depends
+We know that applying $\czwmv$ breaks $\cxynv\aFS$. As it changes the filesystem
+at $m$, this can be because either $m$ would no longer be a directory but has non-empty children,
+or $\parentf{m}$ is not a directory but acquired non-empty children.
+Let us look at the first case.
+Since $n\indep m$, we know the parent and children of $m$ have the same value
+in $\FS$ as in $\cxynv\aFS$. However, this leads to contradiction
+as applying $\czwmv$ to $\cxynv\aFS$ leads to a broken filesystem, but
+applying it to $\FS$ does not.
+
+Therefore $\parentf{m}$ must not be a directory in $\FS$ but acquire non-empty children.
+Since $\czwmv\aFS$ is defined, it must be $\cxynv$ that changes the children of
+$\parentf{m}$ in this way, which means that $n$ and $m$ must be siblings.
+As then the value at $\parentf{n}=\parentf{m}$ is not changed by either command,
+we know it cannot be a directory in $\FS$, either, and that therefore
+$\FS$ is empty at all children of the parent node.
+This means that $[x]=[z]=[\empt]$, and
+since both $\cxynv\aFS$ and $\czwmv\aFS$ are defined, $y=w=\empt$ must also hold.
+However, this contradicts our assumption that $(\cxynv\cc\czwmv)\FS$ is broken.
 
@@
 is an assertion command, when the proposition is again trivially true.
-
-TODO END
-
-Let $\alpha=\cxynv$ and $\beta=\czwmv$.
-The proof is by contradiction;
-assume that there is a filesystem $\FS$ for which
-$\cxynv\aFS\neq\fsbroken$ and $\czwmv\aFS\neq\fsbroken$, but
-$(\cxynv\cc \czwmv)\aFS=\fsbroken$.
-We know $\cxynv\aFS\neq\fsbroken$ so it must be applying 
-$\czwmv$ that breaks it.
-
-We note that as the two commands are independent, they commute, and so
-the proposition is symmetric.
-Therefore, if either of the commands is an assertion command,
-without loss of generality we can assume $\cxynv$ is an assertion command.
-If so, 
-$[\cxynv\aFS(m)]=[\FS(m)]$ even if $n=m$.
-This means $\czwmv$ cannot break $\cxynv\aFS(m)$, which is a contradiction.
-
-In the remaining cases neither command is an assertion command.
-
-Applying a command can only result in a broken filesystem in two cases.
-First, if the input type does not match the filesystem,
-but we know $[\FS(m)]=[w]$ and so
-$[\cxynv\aFS(m)]=[w]$ as based on \cref{incomparable_is_independent}, $n\neq m$.
-Second, if the new filesystem violates the tree property.
-This again cannot be the case because we also know that $n\unrel m$
-and the tree property only depends on the types of values at the parent and children of $m$,
-which therefore cannot be changed by $\cxynv$.
 \end{proof}

### 2018-07-07 p2/def-filesystem.tex
Single directory value assumption

@@
 
-To avoid the proliferation of edge cases, we will furthermore suppose that
-$|\setd|=1$, that is, there is only one directory value $\vald\in\setv$, and so
-apart from their location, all directories are equal.
-In appendix TODO we describe why it can be a sensible choice
-for actual synchronizers, and we also present an encoding that makes it possible
-to extend our results to the $|\setd|>1$ case.
+An essential assumption in our model is that there is only
+a \emph{single directory value} ($|\setd|=1$).
+The realisation that
+this creates a symmetry between directories and empty nodes
+that allows formulating a correct and complete reconciliation algorithm
+is one of the main contributions of this paper.
+This assumption does not hinder the applicability of our results
+(in fact, many real-life synchronizers make the same assumption),
+but makes it possible to exploit a hidden symmetry in filesystem commands.
+
+% TODO To avoid the proliferation of edge cases
+% TODO In appendix TODO we describe why it can be a sensible choice
+% TODO for actual synchronizers, and we also present an encoding that makes it possible
+% TODO to extend our results to the $|\setd|>1$ case.
 
@@
 \myskip
-In the rest of this paper,
+In this paper
 we fix the skeleton $\langle\setn,\parent\rangle$,

### 2018-07-07 p2/intro.tex
Single directory value assumption

@@
 We introduce a new set of commands that is symmetric and
-captures more information about the updates.
-This has the effect that reasoning about commands
+captures more information about the updates,
+and we restrict information content in directories
+to exploit a further hidden symmetry in the command set.
+These have the effect that reasoning about commands
 becomes simpler as there are fewer edge cases,

### 2018-07-07 p2/get_references.pl
Resolve TODOs

@@ -15,7 +15,8 @@ sub readfile {
   return $contents;
 }
 
-my %References; # 'From' => ['To', ... ]
+my %Types; # 'Label' => 'Type'
+my %References; # 'From' => [['To', ConnectionType], ... ]
 
 sub process_file {
   my $filename = shift;
@@ -38,12 +39,13 @@ sub process_file {
 
     my $label;
     unless($type1 eq 'proof') {
-      if($contents =~ /\\label\{([^\}]+)\}/){ $label = $1; }
+      if($contents =~ /\\mlabel\{([^\}]+)\}/){ $label = $1; }
     }
     
     print "Found '$type1' '$label' '$contents2'\n";
+    $Types{$label} = $type1 if $label;
     
-    die "without label" if $type1 =~ /^my(cor|lem|th|ax)$/ && ! $label;
+    die "without label" if $type1 =~ /^my(cor|lem|th)$/ && ! $label;
     
     $LastLabel = $label if $label;
     $NonCorLabel = $label if $label && $type1 ne 'mycor';
@@ -57,13 +59,13 @@ sub process_file {
     $contents =~ s/\\cref\{([^\}]+)\}/do{
       my $refs = $1;
       my @refs = split(m!,!, $refs);
-      push @{$References{$LastLabel}}, @refs;
+      push @{$References{$LastLabel}}, map{[$_, 'normal']} @refs;
     }/ge;
     
     # A corollary depends on the previous result
     if($type1 eq 'mycor'){
       die "corollary without previous result" unless $NonCorLabel;
-      push @{$References{$LastLabel}}, $NonCorLabel;
+      push @{$References{$LastLabel}}, [$NonCorLabel, 'corollary'];
     }
     
   };
@@ -89,15 +91,15 @@ process_index('paper.tex');
 
 my %Backreferences; # To => From
 keys %References;
-while(my($from, $tos) = each %References) {
+while(my($from, $todata) = each %References) {
   $Backreferences{$from} //= [];
-  foreach my $to (@$tos) {
-    push @{$Backreferences{$to} //= []}, $from;
+  foreach my $td (@$todata) {
+    push @{$Backreferences{$td->[0]} //= []}, [$from, $td->[1]];
   }
 }
 
 foreach my $to (sort keys %Backreferences){
-  my $from = $Backreferences{$to};
-  print "$to From:\n";
[…]

### 2018-07-08 p2/conclusion.tex
New section on multiple directory values; reorganizing section

@@
 the simplifying assumptions we used.
-% TODO TODO TODO
-Identifying which results depend on the assumption that $|\setd|=1$
-and devising updated proofs and algorithms for when $|\setd|>1$,
-or specifying a pre-processing step that reconciles meta-information in directories
-can enable the synchronizer
+The model and algorithms could be extended to the $|\setd|>1$ case, % TODO write this
+to enable the synchronizer
 to identify and resolve a wider range of conflicts.
-
-Similarly, designing pre- and post-processors that
-present removing and creating a node
-not as separate updates but as a single rename (move),
-could contribute to the user-friendliness of the reconciler
+Also, pre- and post-processors could be designed that
+reconcile meta-information in directories or encode them as files, % TODO write this
+or present removing and creating the same content at a different node
+not as separate updates but as a single rename (move).
+These could contribute to the user-friendliness of the reconciler
 and help avoid human error.

### 2018-07-08 p2/def-filesystem.tex
New section on multiple directory values; reorganizing section

@@
 this creates a symmetry between directories and empty nodes
+and makes it possible to exploit a hidden symmetry in filesystem commands
 that allows formulating a correct and complete reconciliation algorithm
 is one of the main contributions of this paper.
-This assumption does not hinder the applicability of our results
-(in fact, many real-life synchronizers make the same assumption),
-but makes it possible to exploit a hidden symmetry in filesystem commands.
 
-% TODO To avoid the proliferation of edge cases
-% TODO In appendix TODO we describe why it can be a sensible choice
-% TODO for actual synchronizers, and we also present an encoding that makes it possible
-% TODO to extend our results to the $|\setd|>1$ case.
-
-% % We do this because, as Bill Zissimopoulos pointed 
-% % out \cite{BZ},
-% % we often do not want to consider metadata stored in
-% % directories (e.g. permission settings) during synchronization,
-% % as these are not generally understood well by users,
-% % and, if needed, conflict resolution on these settings can be easily automated.
-% % We will also see that this assumption makes it possible
-% % to define a maximal reconciliation algorithm.
+This assumption does not hinder the applicability of our results.
+In fact, commercial designs for synchronizers 
+often avoid considering metadata in directories as % TODO expand
+as these are generally not understood well by users,
+and, if needed, conflict resolution on these settings can be easily automated
+\cite{BZ}.
 

### 2018-07-08 p2/intro.tex
New section on multiple directory values; reorganizing section

@@
 The paper is organised as follows.
+%
 We start by defining a model of filesystems and a set of commands
 that we will use to describe updates and modifications in \cref{sec_def}.
+%
 This is followed by investigating the properties and behaviors
 of command pairs in \cref{section_axioms}.
+%
 \Cref{sec_update} describes update detection and ordering filesystem commands.
@@
 to the same changes in the filesystem.
+%
 The reconciliation and conflict detection algorithm is defined in
@@
 and show that it has a number of highly convenient properties.
-\Cref{sec_relatedwork,sec_algebra,sec_conclusion}
-discuss related work, comparing our results to other research,
-outlining directions for further work
-on the introduced algebraic system, and provide the conclusion.
-\Cref{axiom_proof} contains technical proofs for propositions on the behavior of command pairs.
+%
+\Cref{sec_multidir,sec_algebra,sec_conclusion}
+describe extending our model to widen its applicability;
+outline directions for further work on the introduced algebraic system,\
+and provide the conclusion.
+%
+We discuss related work, comparing our results to other research in \cref{sec_relatedwork},
+while
+\cref{axiom_proof} contains technical proofs for propositions on the behavior of command pairs.

### 2018-07-08 p2/multidir.tex
New section on multiple directory values; reorganizing section

\section{Extending the Synchronizer for Directory Metadata}\mlabel{sec_multidir}

As suggested above, one of the central assumptions of our model is that
there is only one directory value, that is, directories are not differentiated
by the meta-information they contain.
In this section we describe reasons why this may not limit the applicability
of even the current model, and we describe pre- and post-processing steps
to overcome this limitation.

% TODO

### 2018-07-08 p2/paper.tex
Proofs for the rules
Restating rules for proofs
Improved introduction
Updated notation
Process todos
Resolve TODOs
New section on multiple directory values; reorganizing section

@@
 \input{macros}
+\input{axiom-def}
 
@@
 \begin{abstract}
-
-TODO: $n'$ should always be parent(n).
-
-TODO: Theorem 1, S' extends S. ... All S is extended by simple sequence, and generate with inference rules.
-
-TODO: Explain what happens to FF commands.
-
-TODO: $|[D]|=1$ - where used? Can we move $A \cap B$ to the beginning?
-
-% A: <D1,D2,n'>
-% B: <D1,D3,n'> <empt,F,n>
-% Reconciliation does not create file, but we can create it -> reconciliation maximal not true.
-
-TODO: After reconciliation, subsequence order works.
 
@@
 
-% section
-\input{comparisons}
+%section
+\input{multidir}
 
@@
 
-% TODO Add reviewer
-% TODO Consider below
-I thank L. Csirmaz for his invaluable input on this paper,
+I thank L.~Csirmaz for his invaluable input on this paper,
 and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.
+I am indebted to the anonymous reviewers of the previous version of this paper
+for their helpful and detailed remarks
+that helped improve the presentation of the paper
+and make it accessible for a wider audience.
 
@@
 
+\appendix
+
+% section
+\input{comparisons}
+
+\section{Proofs for Rules}\mlabel{axiom_proof}
+\input{axiom-proof}
+
 \end{document}

### 2018-07-08 p2/def-filesystem.tex
Workaround to |D|=1

@@
 is one of the main contributions of this paper.
-
-This assumption does not hinder the applicability of our results.
-In fact, commercial designs for synchronizers 
-often avoid considering metadata in directories as % TODO expand
-as these are generally not understood well by users,
-and, if needed, conflict resolution on these settings can be easily automated
-\cite{BZ}.
+In \cref{sec_multidir} we explore the applicability of our model given this assumption:
+why applicability may not be affected and ways to relax this restriction.
 

### 2018-07-08 p2/multidir.tex
Workaround to |D|=1

@@
 
-% TODO
+We note that commercial designs for synchronizers 
+often avoid considering metadata in directories as
+as these are generally not understood well by users,
+and, if needed, conflict resolution on these settings can be easily automated.
+See, for example, the seminal work of Balasubramaniam and Pierce and the Unison synchronizer \cite{BP} or \cite{BZ}.
+
+Despite the above, there can be applications where directory metadata
+is considered important.
+Synchronizers based on our model can be readily extended to handle them
+by duplicating $\setn$. 
+Given the input filesystems, we add a special node as an extra child under each original node,
+and we encode directory metadata in a file under each directory.
+It is easy to see that update detection and conflict resolution can continue as expected,
+with the only exception of a potential conflict detected on one of these special nodes.
+In these cases the synchronizer may prescribe creating a directory without creating
+the special metadata file, which is clearly not possible to do on the target filesystem,
+as creating a directory entails specifying its metadata as well.
+In these cases, the synchronizer can either fall back to default values and flag the issue
+for review later, or if, as suggested above, conflicts on the metadata (e.g. readable, writeable and executable flags)
+can be easily automated, then it could form part of the implementation.

### 2018-07-08 p2/multidir.tex
Added strategy to reintroduce move

@@
-\section{Extending the Synchronizer for Directory Metadata}\mlabel{sec_multidir}
+\section{Extending the Synchronizer}\mlabel{sec_multidir}
 
-As suggested above, one of the central assumptions of our model is that
+The two assumptions we used to increase the symmetry of our model were
+that there is no move command,
+and that
 there is only one directory value, that is, directories are not differentiated
 by the meta-information they contain.
-In this section we describe reasons why this may not limit the applicability
-of even the current model, and we describe pre- and post-processing steps
-to overcome this limitation.
+In this section we describe reasons why the latter assumption may not limit the applicability
+of even the current model, and we also describe pre- and post-processing steps
+to overcome the two restrictions.
 
@@
 and, if needed, conflict resolution on these settings can be easily automated.
-See, for example, the seminal work of Balasubramaniam and Pierce and the Unison synchronizer \cite{BP} or \cite{BZ}.
+See, for example, the seminal work of Balasubramaniam and Pierce and the Unison synchronizer \cite{BP} and \cite{BZ}.
 
@@
 by duplicating $\setn$. 
-Given the input filesystems, we add a special node as an extra child under each original node,
+Given the input filesystems over $\setn$, we add a special node as an extra child under each original node,
 and we encode directory metadata in a file under each directory.
@@
 can be easily automated, then it could form part of the implementation.
+
+Reintroducing the \emph{move} command can happen in a similar fashion.
+Its main advantages include that 
+\emph{move} commands are easier to review,
+and if the synchronizer sugegsts or performs a move instead
+of deleting a file and recreating it somewhere else, the user
+can be assured that no information is lost.
+During pre-processing, if an update detector is used,
+\emph{move} commands still do not need to be part of the command sequences
+the synchronizer operates on.
+If the command sequences are derived from filesystem journals, they
+can be broken into two updates to allow the existing reconciliation
+algorithm to operate.
+
+In a post-processing stage, deleted or overwritten file contents
+can be paired up with created ones to reintroduce \emph{move}
+commands in the output sequences and take advantage of their benefits.
+The renaming of whole filesystem subtrees can also be detected
+to further aid the user.

### 2018-07-08 p2/axiom-proof.tex
Spellcheck

@@
 is not a directory. Depending on which is true, we have a point in the sequence
-of applying the commands where the filesystem cannot satify the tree property
+of applying the commands where the filesystem cannot satisfy the tree property
 and therefore becomes broken as $\parentf{n}$, a descendant of $\nn$, contains

### 2018-07-08 p2/axioms.tex
Spellcheck

@@
 We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\cc T$.
-% symmetric:     aRb <=> bRa
-% antisymmetric: aRb & bRa => a=b
-% reflexive:     aRa
-% transitive:    aRb & bRC => aRc
+% symmetric:     a R b <=> b R a
+% antisymmetric: a R b & b R a => a = b
+% reflexive:     a R a
+% transitive:    a R b & b R C => a R c
 % preorder:      reflexive, transitive
@@
 \myskip
-Command pairs in genral have the form
+Command pairs in general have the form
 \[ \cxynv\cc  \czwmv \]
@@
 
-We can see that construction pairs consist of construction comands,
+We can see that construction pairs consist of construction commands,
 while destruction pairs consist of destruction commands.

### 2018-07-08 p2/def-filesystem.tex
Spellcheck

@@
 $\langle \setn, \parent \rangle$, forms a \emph{skeleton}
-which the filesytems populate with values from $\setv$.
+which the filesystems populate with values from $\setv$.
 As we require filesystem functions to be total,
@@
 a \emph{single directory value} ($|\setd|=1$).
-The realisation that
+The realization that
 this creates a symmetry between directories and empty nodes

### 2018-07-08 p2/multidir.tex
Spellcheck

@@
 In these cases, the synchronizer can either fall back to default values and flag the issue
-for review later, or if, as suggested above, conflicts on the metadata (e.g. readable, writeable and executable flags)
+for review later, or if, as suggested above, conflicts on the metadata (e.g. readable, writable and executable flags)
 can be easily automated, then it could form part of the implementation.
@@
 \emph{move} commands are easier to review,
-and if the synchronizer sugegsts or performs a move instead
+and if the synchronizer suggests or performs a move instead
 of deleting a file and recreating it somewhere else, the user

### 2018-07-08 p2/ordering.tex
Resolve TODOs
Spellcheck

@@
-% TODO Commuting commands important as we need to establish order
-
 \subsection{Ordering commands}\mlabel{ordering}
@@
 
-As we recognize that mulitple orders may be possible,
+As we recognize that multiple orders may be possible,
 let us describe our ordering algorithm by
@@
 \begin{proof}
-% BACK_TO_THE_FS TODO
+% BACK_TO_FS
 Formally, we prove our proposition by contradiction,
@@
 \begin{proof}
-% BACK_TO_THE_FS
-% TODO Rule?
+% BACK_TO_FS
 Let $A$ and $B$ be simple sequences
@@
 \end{proof}
-
-% TODO delete unused results
 

### 2018-07-08 p2/get_references.pl

@@ -1,105 +1,0 @@
-#!/usr/bin/perl
-
-# This script parses TeX files to enumerate references to results
-
-use strict;
-
-use Data::Dumper;
-
-sub readfile {
-  my $filename = shift;
-  local $/ = undef;
-  open my $f, $filename or die "Cannot open $filename: $1";
-  my $contents = <$f>;
-  close($f);
-  return $contents;
-}
-
-my %Types; # 'Label' => 'Type'
-my %References; # 'From' => [['To', ConnectionType], ... ]
-
-sub process_file {
-  my $filename = shift;
-  
-  print "Processing $filename\n";
-  
-  my $contents = readfile($filename);
-
-  my $LastLabel = "___";
-  my $NonCorLabel = "___";
-  my $process_block = sub {
-    my $type1 = shift;
-    my $contents = shift;
-    my $type2 = shift;
-    
-    my $contents2 = substr($contents, 0, 40); # excerpt for logging
-    $contents2 =~ s/\s+/ /g;
-    
-    die "type mismatch '$type1' '$type2' '$contents'" unless $type1 eq $type2;
-
-    my $label;
-    unless($type1 eq 'proof') {
-      if($contents =~ /\\mlabel\{([^\}]+)\}/){ $label = $1; }
-    }
-    
-    print "Found '$type1' '$label' '$contents2'\n";
-    $Types{$label} = $type1 if $label;
-    
-    die "without label" if $type1 =~ /^my(cor|lem|th)$/ && ! $label;
-    
-    $LastLabel = $label if $label;
-    $NonCorLabel = $label if $label && $type1 ne 'mycor';
-    
-    if($label && $References{$LastLabel}){
-      die "duplicate label";
-    }
-    
-    $References{$LastLabel} //= [];
-    
-    $contents =~ s/\\cref\{([^\}]+)\}/do{
-      my $refs = $1;
-      my @refs = split(m!,!, $refs);
-      push @{$References{$LastLabel}}, map{[$_, 'normal']} @refs;
-    }/ge;
-    
-    # A corollary depends on the previous result
-    if($type1 eq 'mycor'){
-      die "corollary without previous result" unless $NonCorLabel;
-      push @{$References{$LastLabel}}, [$NonCorLabel, 'corollary'];
-    }
-    
-  };
-
[…]

### 2018-07-09 p2/axiom-proof.tex
Added TODO

@@
 \cref{rules_lemma} from our filesystem model.
-For the purposes of the proofs we extend the notion of filesystems 
+For the purposes of the proofs we extend the notion of filesystems % TODO review if needed
 to the full set of functions mapping $\setn$ to $\setv$, even if they

### 2018-07-09 p2/conclusion.tex
Spellcheck
Clarify update detector

@@
 in the update history of the filesystems.
-Existing research can offer pointers as to how such cases can be modelled
+Existing research can offer pointers as to how such cases can be modeled
 in our algebraic system.
@@
 
-An extension of our results could also entail relaxing
-the simplifying assumptions we used.
-The model and algorithms could be extended to the $|\setd|>1$ case, % TODO write this
-to enable the synchronizer
-to identify and resolve a wider range of conflicts.
-Also, pre- and post-processors could be designed that
-reconcile meta-information in directories or encode them as files, % TODO write this
-or present removing and creating the same content at a different node
-not as separate updates but as a single rename (move).
-These could contribute to the user-friendliness of the reconciler
-and help avoid human error.
+Future work could also investigate extending the 
+model and algorithms to the $|\setd|>1$ case
+so that directory metadata could be represented directly
+as opposed to through pre- and post-processing as described
+in \cref{sec_multidir}.
 
@@
 (e.g. XML trees, mailbox folders, generic relational databases, etc.),
-and of demonstrating the adequacy and completeness of update and conflict detection and reconciliation
+and of demonstrating the adequacy and completeness of the update and conflict detection and reconciliation
 algorithms defined over it.

### 2018-07-09 p2/ordering.tex
Clarify update detector

@@
 defining a subset of the permutations, $\ordersetsign$.
-The simplicity of the definition means that enumerating
-all sequences in $\ordersetsign$ can be implemented by a straightforward
-algorithm.
-
 As we will see, $\ordersetsign$ contains all possible
@@
 The facts that all valid reorderings of simple sequences are equivalent,
-and all equivalent sequences are reorderings are important 
+and all equivalent sequences are reorderings, are important 
 properties of simple sequences.
+
+% Define this with the help or a relation / partial order? But then all sequences
+% could be ordered while this definition rules out illegal ones.
 
@@
 \begin{itemize}
-\item if $n=\parentf{m}$, then $[y]=[\vald]$
+\item if $n=\parentf{m}$, then $y=\vald$,
 \item if $\parentf{n}=m$, then $y=\empt$.
@@
 As usual, by subsequence we mean a subset of the commands in $S$ in the same order as they are found in $S$.
+The simplicity of the definition means that sorting the commands
+and enumerating
+all sequences in $\ordersetsign$ can be implemented by a straightforward
+algorithm.
 
@@
 \begin{proof}
-TODO: If something changes, everything changes up to the leaves.
-
+% If something changes, everything changes up to the leaves.
 Without loss of generality, we can assume that $\nn\neq\parent(n)$.
@@
 \end{mydef}
+
+Building on the results above, we finish by proving an important result,
+namely, that command sequences can be made simple using syntactical operations.
+
+\begin{mylem}\mlabel{can_simplify}
+Each sequence of commands $\wkrsx{S}$
+can be transformed into a simple sequence
+$T\equiv S$ by applying repeatedly the following transformations:
+{\rm(i)} swap neighboring commands on incomparable nodes;
+{\rm(ii)} simplify neighboring commands on the same node;
+{\rm(iii)} delete assertion commands.
+\end{mylem}
+\begin{proof}
+We can remove all assertion commands, as based on
+\cref{ax_assert} the resulting sequence extends the original one.
+We therefore assume that $S$ contains no assertion commands.
+
+\newcommand{\ucx}{\alpha}
+\newcommand{\ucy}{\beta}
+\newcommand{\ucz}{\gamma}
+
+We aim to find a simple sequence that is equivalent to $S$.
+If $S$ is already simple, there is nothing to do.
+If it is not simple, let $\ucx$ be the first command
+on a node $n$ that is already present in $S$,
+and let $\ucy$ be the previous command on $n$.
+Splitting $S$ around these commands we get
+\[ S = S_0 \cc \ucy \cc S_1 \cc \ucx \cc S_2. \]
+
+We now show that $S_1\indep\ucx$,
+which is equivalent to $S_1\indep\ucy$ as both commands are on $n$.
+We use an inverse proof and assume that there is a command on $m$ in $S_1$
+where $m\descendant n$ or $m\ancestor n$.
+We know both $\ucy\cc S_1$ and $S_1\cc\ucx$ are simple,
+and both are defined on a filesystem
+(on $S_0\aFS$ and $(S_0\cc\beta)\FS$, respectively).
+Therefore from \cref{connected_changes} we know that
+$S_1$ must also contain a command on $m'$ where
+$m'=\parentf{n}$ or $n=\parentf{m'}$.
+Let this command be $\ucz$.
+
+If $n=\parentf{m'}$,
+from \cref{simple_distant_pairs} 
+and the relationship of nodes in construction and destruction pairs
+we know that the subsequence
+$\ucy\cc\ucz$ must be a construction pair,
+and both $\ucy$ and $\ucz$ must be construction commands.
+But we also know that $\ucz\cc\ucx$ must be a destruction pair,
+and both $\ucz$ and $\ucx$ must be destruction commands.
+This is a contradiction as a command cannot be both.
+We arrive at the same contradiction if $m'=\parentf{n}$.
+
+We therefore know that $S_1\indep\ucx$ and so
+from \cref{ax_separate_commute}
+\[ S \equiv S_0\cc\ucy\cc\ucx\cc S_1 \cc S_2. \]
+We can apply \cref{ax_same_emptyseq,ax_same_singlec} to
+$\ucy\cc\ucx$ and get a $S'\eqext S$ that contains one or two less commands on $n$.
+Repeating the swap and the simplification we
+can convert $S$ into an equivalent simple sequence $S^*$.
+\end{proof}

### 2018-07-09 p2/upd-correct.tex
Minor improvements
Clarify update detector

@@
 
-Based on \cref{connected_changes} we can also show that
-the update detector does function as intended as:
+With $\ordersetsign$ we can now define our update detection algorithm.
+Its inputs are the original filesystem $\FS$ which has been modified to yield $\FS_1$.
+\begin{mydef}[Update detection]\mlabel{def_upddetect}
+\begin{enumerate}
+    \item For each node $n$ where the value in $\FS$ and $\FS_1$ differ, add the command $\cxynv$ to
+        a set of commands $U$.
+    \item % TODO
+\end{enumerate}
+\end{mydef}
+% TODO from journal? Simplify sequence?
 
-% TODO
 TODO ENSURE UPDATE DETECTOR IS DEFINED.
 
-TODO What is not trivial here is that $U$ works at all.
+% There is a sequence between any two states: destroy one completely and construct the other one. (finite FS)
 
@@
 \end{myth}
+
+TODO What is not trivial here is that $U$ works at all.
+
+TODO And that it can be ordered?
+
 \begin{proof}
@@
 where $S\aFS=\FS^*$.
-Note that $S$ will not contain assertion commands, as they do not
-represent an actual change in the filesystem.
+($S$ will not contain assertion commands, as they do not
+represent an actual change in the filesystem.)
+Based on \cref{can_simplify}, there is a simple sequence $S^*$
+that is equivalent to $S$.
 
-\newcommand{\ucx}{\alpha}
-\newcommand{\ucy}{\beta}
-\newcommand{\ucz}{\gamma}
-
-We aim to find a simple sequence that is equivalent to $S$.
-If $S$ is already simple, there is nothing to do.
-If it is not simple, let $\ucx$ be the first command
-on a node $n$ that is already present in $S$,
-and let $\ucy$ be the previous command on $n$.
-Splitting $S$ around these commands we get
-\[ S = S_0 \cc \ucy \cc S_1 \cc \ucx \cc S_2. \]
-
-We now show that $S_1\indep\ucx$,
-which is equivalent to $S_1\indep\ucy$ as both commands are on $n$.
-We use an inverse proof and assume that there is a command on $m$ in $S_1$
-where $m\descendant n$ or $m\ancestor n$.
-We know both $\ucy\cc S_1$ and $S_1\cc\ucx$ are simple,
-and both are defined on a filesystem
-(on $S_0\aFS$ and $(S_0\cc\beta)\FS$, respectively).
-Therefore from \cref{connected_changes} we know that
-$S_1$ must also contain a command on $m'$ where
-$m'=\parentf{n}$ or $n=\parentf{m'}$.
-Let this command be $\ucz$.
-
-If $n=\parentf{m'}$,
-from \cref{simple_distant_pairs} 
-and the relationship of nodes in construction and destruction pairs
-we know that the subsequence
-$\ucy\cc\ucz$ must be a construction pair,
-and both $\ucy$ and $\ucz$ must be construction commands.
-But we also know that $\ucz\cc\ucx$ must be a destruction pair,
-and both $\ucz$ and $\ucx$ must be destruction commands.
-This is a contradiction as a command cannot be both.
-We arrive at the same contradiction if $m'=\parentf{n}$.
-
-We therefore know that $S_1\indep\ucx$ and so
-from \cref{ax_separate_commute}
-\[ S \equiv S_0\cc\ucy\cc\ucx\cc S_1 \cc S_2. \]
-We can apply \cref{ax_same_emptyseq,ax_same_singlec} to
-$\ucy\cc\ucx$ and get a $S'\eqext S$ that contains one or two less commands on $n$.
-Repeating the swap and the simplification we
-can convert $S$ into an equivalent simple sequence.
-Let this sequence be $S^*$.
-
-As $S^*\equiv S$, we know $S^*\aFS=\FS^*$, and that
+Therefore we know $S^*\aFS=\FS^*$, and that
 $\FS^*$ and $\FS$ differ at exactly those nodes that $S^*$ has commands on.
@@
 
-As the update detector uses $\ordersetsign$ to order the commands in $U$,
-trivially $U\in\orderset{U}$,
+As the update detector uses $\ordersetsign$ to order the commands in $U$, trivially $U\in\orderset{U}$, % TODO
 and as $S^*$ is defined on $\FS$,

### 2018-07-09 p2/upd-def.tex
Clarify update detector

@@
 $A$ and $B$ that have modified a single filesystem $\FS$ 
-yielding two different replicas $\FS_1$ and $\FS_2$ that we
+yielding two different replicas $\FS_1$ and $\FS_2$ which we
 need to reconcile. While it is conceivable that the sequences are based on a record of
@@
 The set of commands $U$ necessary to transform $\FS$ into $\FS_1$ can be collected
-by inspecting the union of non-empty nodes in the two filesystems.
+by inspecting the (necessarily finite) union of non-empty nodes in the two filesystems.
 If at node $n$, $\FS(n)=x$ and $\FS_1(n)=y\neq x$, then we add the command $\cxyaa{n}$ to $U$.
@@
 To be able to reason about sets and sequences of commands, let us introduce the following properties:
-
-% TODO Define, spell out update decetion algorithm
 

### 2018-07-09 p2/ordering.tex
New partial order that defines ordering

@@
 
-% Define this with the help or a relation / partial order? But then all sequences
-% could be ordered while this definition rules out illegal ones.
+We define $\ordersetsign$ with the help of a partial order.
+\begin{mydef}[$\orderrel$]\mlabel{def_orderrel}
+The binary relation $\orderrel$ holds for some command pairs
+on directly related nodes if they are
+of the following form:
+\begin{itemize}
+\item $\caaa{x}{\vald}{\parentf{n}}\orderrel\caaa{z}{w}{n}$, and
+\item $\caaa{x}{\empt}{n}\orderrel\caaa{z}{w}{\parentf{n}}$.
+\end{itemize}
+\end{mydef}
+This relation is clearly irreflexive and asymmetric,
+and thus defines a partial order.
 
 \begin{mydef}[$\ordersetsign$]\mlabel{def_orderset}
-For a simple set or sequence of commands $S$,
-we use $\orderset{S}$ to denote the set of 
-permutations of the commands in $S$
-for which the following holds:
-for any subsequence $\cxynv\cc\czwmv$,
-\begin{itemize}
-\item if $n=\parentf{m}$, then $y=\vald$,
-\item if $\parentf{n}=m$, then $y=\empt$.
-\end{itemize}
+For a simple sequence of commands $\wrksx{S}$,
+$\orderset{S}$ is the set of permutations satisfying the partial order defined by $\orderrel$.
+% For a simple set or sequence of commands $S$,
+% we use $\orderset{S}$ to denote the set of 
+% permutations of the commands in $S$
+% for which the following holds:
+% for any subsequence $\cxynv\cc\czwmv$,
+% \begin{itemize}
+% \item if $n=\parentf{m}$, then $y=\vald$,
+% \item if $\parentf{n}=m$, then $y=\empt$.
+% \end{itemize}
 \end{mydef}
 
-As usual, by subsequence we mean a subset of the commands in $S$ in the same order as they are found in $S$.
-The simplicity of the definition means that sorting the commands
+% As usual, by subsequence we mean a subset of the commands in $S$ in the same order as they are found in $S$.
+The simplicity of the definitions mean that sorting the commands
 and enumerating
@@
 
-The principal ideas behind these conditions are 
+The principal ideas behind the ordering are 
 \cref{ax_separate_commute}, from which we know that commands on incomparable
@@
 
-\begin{myclm}\mlabel{subseq_in_orderset}
+\begin{mycor}\mlabel{subseq_in_orderset}
 For simple sequences $S$ and $T$,
@@
 $T_0\in\orderset{S_0}$ must hold.
-\end{myclm}
-\begin{proof}
-This is because
-if there are no command pairs in $T$ not conforming to \cref{def_orderset},
-then there cannot be any in $T_0$.
-\end{proof}
+\end{mycor}
 
@@
 \begin{mycor}\mlabel{order_is_only_possible}
-For any simple sequence $S$ and its permutation $S'$, 
+For any simple sequence $\wrksx{S}$ and its permutation $S'$, 
 \[ S'\not\in\orderset{S} \Longrightarrow S'\equiv\cbrk. \]
@@
 We use an inverse proof and assume $\wrksx{S'}$.
-If $S'\not\in\orderset{S}$ then by \cref{def_orderset}
+If $S'\not\in\orderset{S}$ then by \cref{def_orderrel,def_orderset}
 it contains two commands on a node $n$ and its parent
@@
 If we denote the command on $n_\indx$ with $\caaa{x_\indx}{y_\indx}{n_\indx}$,
-by definition this means that $[y_\indx]\neq[\empt]$ for all $\indx$.
+by definition this means that
+% $[y_\indx]\neq[\empt]$ for all $\indx$.
+$y_\indx=\vald$ for all $\indx<k$.
 
@@
 We know $I^T_k=I^T_0-1$ as $\czwmv$ precedes $\cxynv$.
-This means there must exist a $\indx$ for which $I^T_{\indx+1}<I^T_\indx$.
+This means there must exist a $1\leq \indx<k$ for which $I^T_{\indx+1}<I^T_\indx$.
 We therefore know that
 $\caaa{x_{\indx+1}}{y_{\indx+1}}{n_{\indx+1}} \cc \caaa{x_\indx}{y_\indx}{n_\indx}$
-is a subsequence of $T$, and by assumption $\parentf{n_{\indx+1}}=n_\indx$.
-By definition of $\ordersetsign$, therefore $y_{\indx+1}=\empt$ must be true,
-which is a contradiction.
+is a subsequence of $T$.
+Because we know $y_\indx=\vald$ and by assumption $\parentf{n_{\indx+1}}=n_\indx$,
+this has the form
+$\caaa{x_{\indx+1}}{y_{\indx+1}}{n_{\indx+1}} \cc \caaa{x_\indx}{\vald}{\parentf{n_{\indx+1}}}$.
+If so, the inverse of $\orderrel$ holds for this subsequence, which is a contradiction.
+% By definition of $\ordersetsign$, therefore $y_{\indx+1}=\empt$ must be true,
+% which is a contradiction.
 
@@
 In this case we find that all commands are destruction commands,
-and so $[y_\indx]\neq[\vald]$, while in a subsequence of $T$ for a given $\indx$,
-$[y_\indx]=[\vald]$ must be true by definition of $\ordersetsign$.
+and so 
+% $[y_\indx]\neq[\vald]$, 
+$y_\indx=\empt$ for all $1<\indx\leq k$,
+which again leads to a subsequence in $T$ violating $\orderrel$.
+% while in a subsequence of $T$ for a given $\indx$,
+% $[y_\indx]=[\vald]$ must be true by definition of $\ordersetsign$.
 \end{proof}
@@
 \begin{mydef}[$\ordp{S}$]
-For a simple set or sequence of commands $S$,
+For a simple set or sequence of commands $\wrksx{S}$,
 $\ordp{S}$ is the unique partial endofunction on filesystems
 defined by any order in $\orderset{S}$.
-We leave $\ordp{S}$ undefined if such an order does not exist.
+% We leave $\ordp{S}$ undefined if such an order does not exist.
 \end{mydef}
@@
 \begin{mylem}\mlabel{can_simplify}
-Each sequence of commands $\wkrsx{S}$
+Each sequence of commands $\wrksx{S}$
 can be transformed into a simple sequence
@@
 Repeating the swap and the simplification we
-can convert $S$ into an equivalent simple sequence $S^*$.
+can convert $S$ into an equivalent simple sequence.
 \end{proof}

### 2018-07-09 p2/rec-intro.tex
New partial order that defines ordering

@@
 and so they are simple sequences.
-% TODO
-(Otherwise, they can be simplified to become simple sequences; see \cref{update_works}.)
+(Otherwise, they can be simplified to become simple sequences; see \cref{can_simplify}.)
 We also assume that $\FS$, $\FS_A$ and $\FS_B$ are not broken.

### 2018-07-09 p2/upd-correct.tex
New partial order that defines ordering

@@
 With $\ordersetsign$ we can now define our update detection algorithm.
-Its inputs are the original filesystem $\FS$ which has been modified to yield $\FS_1$.
-\begin{mydef}[Update detection]\mlabel{def_upddetect}
+Its inputs are the original filesystem $\FS$ which has been modified to yield $\FS^*$.
+\begin{mydef}[Update detection]\mlabel{def_upddetect}~
 \begin{enumerate}
-    \item For each node $n$ where the value in $\FS$ and $\FS_1$ differ, add the command $\cxynv$ to
-        a set of commands $U$.
-    \item % TODO
+    \item For each node $n$ where the value in $\FS$ and $\FS^*$ differ, add the command $\caaa{\FS(n)}{\FS^*(n)}{n}$ to
+        a set of commands $U_S$. The result is a simple set of commands.
+    \item Order the commands according to $\orderrel$, that is, 
+        return any sequence $U$ from $\orderset{U_S}$.
 \end{enumerate}
 \end{mydef}
-% TODO from journal? Simplify sequence?
 
-TODO ENSURE UPDATE DETECTOR IS DEFINED.
+\Cref{update_works} proves that $U$ functions as expected, that is, $U\aFS=\FS^*$.
+While this is trivial if we know that $U$ does not break $\FS$, we
+still need to show that it is defined.
+
+On systems where filesystem updates a recorded,
+an alternative update detection algorithm is to
+omit step 1, and use \cref{can_simplify} to simplify the series of recorded updates into a simple sequence containing the necessary
+updates.
+In fact, we use such a hypothetical record in the proof \cref{update_works}.
 
@@
 \begin{myth}\mlabel{update_works}
-For a sequence of commands $U$ returned by the update detector
+For a simple sequence of commands $U$ returned by the update detector
 when comparing the non-broken $\FS^*$ to the original $\FS$,
@@
 
-TODO What is not trivial here is that $U$ works at all.
-
-TODO And that it can be ordered?
-
 \begin{proof}
-Let $\FS$ be the original filesystem, and $\FS^*$
-be the filesystem after the changes we intend to detect.
 Let us assume that some mechanism recorded all changes that occurred
@@
 $\FS^*$ and $\FS$ differ at exactly those nodes that $S^*$ has commands on.
-If $U$ is the simple sequence returned by the update detector
-when comparing $\FS^*$ to $\FS$, it must also contain commands on the same set of nodes,
+$U$ must also contain commands on the same set of nodes,
 and it must contain the same commands,
@@
 
-As the update detector uses $\ordersetsign$ to order the commands in $U$, trivially $U\in\orderset{U}$, % TODO
-and as $S^*$ is defined on $\FS$,
-from \cref{order_is_only_possible} we know $S^* \in \orderset{S^*}$.
-This means $U\in\orderset{S^*}$,
+As the update detector uses $\orderrel$ to order the commands in $U$, trivially $U\in\orderset{U}$,
+which means $U\in\orderset{S^*}$,
 and so from \cref{simple_reorder_equiv} we know that $U\equiv S^*$,

### 2018-07-09 p2/axiom-proof.tex
Simplified the proofs of rules

--- 2018-07-08 p2/axiom-proof.tex
@@
 \cref{rules_lemma} from our filesystem model.
-For the purposes of the proofs we extend the notion of filesystems 
-to the full set of functions mapping $\setn$ to $\setv$, even if they
-do not have the tree property.
-This is so that we can describe the values they would acquire under certain nodes,
-and pinpoint where they may be violating the tree property.
-If they do, we continue to say that the filesystem is broken,
-and say that the filesystem is \emph{broken at $n$} if 
+In the proofs, we may say that a filesystem
+is \emph{broken at $n$}
+if after applying a command, it violates the tree property
+because
 $n$ is not a dictionary, but has at least one non-empty child.
-We continue to require that filesystems are not empty at finitely many nodes.
 
-Accordingly, where needed, we also implicitly extend filesystem commands
-so that they would return a filesystem even if it violates the tree property.
-We continue to say that they break the filesystem in these cases,
-and commands continue to be undefined where their input types are incompatible
-with the input filesystem.
-We note that once a filesystem is broken, it stays broken, even if
-after a subsequent command it would no longer violate the tree property.
+% For the purposes of the proofs we extend the notion of filesystems
+% to the full set of functions mapping $\setn$ to $\setv$, even if they
+% do not have the tree property.
+% This is so that we can describe the values they would acquire under certain nodes,
+% and pinpoint where they may be violating the tree property.
+% If they do, we continue to say that the filesystem is broken,
+% and say that the filesystem  if 
+% We continue to require that filesystems are not empty at finitely many nodes.
+% 
+% Accordingly, where needed, we also implicitly extend filesystem commands
+% so that they would return a filesystem even if it violates the tree property.
+% We continue to say that they break the filesystem in these cases,
+% and commands continue to be undefined where their input types are incompatible
+% with the input filesystem.
+% We note that once a filesystem is broken, it stays broken, even if
+% after a subsequent command it would no longer violate the tree property.
 
@@
 by the values at $n$ and the children of $n$.
-In other words,
-
-\begin{myclm}[Locality of tree property violations]\mlabel{broken_local}
-If two filesystems over $\setn$ have the same values at a node $n$,
-and at all children of $n$ (if they exist),
-then either both filesystems are broken at $n$, or none of them are.
-\end{myclm}
+% In other words,
+% 
+% \begin{myclm}[Locality of tree property violations]\mlabel{broken_local}
+% If two filesystems over $\setn$ have the same values at a node $n$,
+% and at all children of $n$ (if they exist),
+% then either both filesystems are broken at $n$, or none of them are.
+% \end{myclm}
 
@@
 
-In the former case, based on \cref{broken_local}, 
+In the former case 
 $\czwmv\aFS$ must be broken at $m$ or $\parentf{m}$, since it only changed at $m$.
@@
 \begin{proof}
-Suppose $\cxynnv$ and $\czwnv$ satisfy the conditions,
+We use an inverse proof and
+suppose $\cxynnv$ and $\czwnv$ satisfy the conditions,
 and there is an $\FS$ for which $(\cxynnv\cc\czwnv)\aFS\neq\fsbroken$.
-If $\czwnv\neq\cbba{n}$, then either $\FS(n)\neq\empty$ or $\czwnv\aFS(n)\neq\empty$,
+If $\czwnv\neq\cbba{n}$, then either $\FS(n)\neq\empt$ or $\czwnv\aFS(n)\neq\empt$,
 and therefore $\FS(\parentf{n})$ must be a directory for the filesystem to satisfy
@@
 \begin{proof}
-As for an assertion command $\cxynv$, $x=y$, we see that it either
+The two assertion commands $\cdda{n}$ and $\cbba{n}$ either
 breaks a filesystem, or leaves it in the same state.

### 2018-07-09 p2/ordering.tex
New acyclic ordering relation

@@
 The binary relation $\orderrel$ holds for some command pairs
-on directly related nodes if they are
-of the following form:
+on directly related nodes in the following cases:
 \begin{itemize}
-\item $\caaa{x}{\vald}{\parentf{n}}\orderrel\caaa{z}{w}{n}$, and
-\item $\caaa{x}{\empt}{n}\orderrel\caaa{z}{w}{\parentf{n}}$.
+\item $\caaa{x}{y}{\parentf{n}} \orderrel \caaa{z}{w}{n}$ if both commands are construction commands, and
+\item $\caaa{x}{y}{n} \orderrel \caaa{z}{w}{\parentf{n}}$ if both commands are destruction commands.
 \end{itemize}
 \end{mydef}
-This relation is clearly irreflexive and asymmetric,
+This relation is clearly irreflexive and anti-symmetric,
+and as a command cannot be both a construction and a destruction command and
+the relation follows the tree of nodes, it is acyclic,
 and thus defines a partial order.
@@
 that commands on parent--child pairs must be construction or destruction pairs.
-Investigating these pairs we see that they are identified by the output value of the first command ($y$),
-which in turn determines whether the command on the parent or the child must precede the other.
+% Investigating these pairs we see that they are identified by the output value of the first command ($y$),
+% which in turn determines whether the command on the parent or the child must precede the other.
 
@@
 that, as a subsequence,
-do not form a construction or destruction pair.
+cannot form a construction or destruction pair.
 However, this contradicts \cref{simple_distant_pairs}
@@
 and the commands on $n_\indx$ are construction commands.
-If we denote the command on $n_\indx$ with $\caaa{x_\indx}{y_\indx}{n_\indx}$,
-by definition this means that
+% If we denote the command on $n_\indx$ with $\caaa{x_\indx}{y_\indx}{n_\indx}$,
+% by definition this means that
 % $[y_\indx]\neq[\empt]$ for all $\indx$.
-$y_\indx=\vald$ for all $\indx<k$.
+% -----
+% $y_\indx=\vald$ for all $\indx<k$.
 
@@
 is a subsequence of $T$.
-Because we know $y_\indx=\vald$ and by assumption $\parentf{n_{\indx+1}}=n_\indx$,
-this has the form
-$\caaa{x_{\indx+1}}{y_{\indx+1}}{n_{\indx+1}} \cc \caaa{x_\indx}{\vald}{\parentf{n_{\indx+1}}}$.
-If so, the inverse of $\orderrel$ holds for this subsequence, which is a contradiction.
+However, because we know these are construction commands, and by assumption $\parentf{n_{\indx+1}}=n_\indx$,
+the inverse of $\orderrel$ holds for this subsequence, which is a contradiction.
+% Because we know $y_\indx=\vald$ and by assumption $\parentf{n_{\indx+1}}=n_\indx$,
+% this has the form
+% $\caaa{x_{\indx+1}}{y_{\indx+1}}{n_{\indx+1}} \cc \caaa{x_\indx}{\vald}{\parentf{n_{\indx+1}}}$.
+% If so, the inverse of $\orderrel$ holds for this subsequence, which is a contradiction.
+% -----
 % By definition of $\ordersetsign$, therefore $y_{\indx+1}=\empt$ must be true,
@@
 In this case we find that all commands are destruction commands,
-and so 
+% and so 
 % $[y_\indx]\neq[\vald]$, 
-$y_\indx=\empt$ for all $1<\indx\leq k$,
-which again leads to a subsequence in $T$ violating $\orderrel$.
+% $y_\indx=\empt$ for all $1<\indx\leq k$,
+and a subsequence in $T$ again violates $\orderrel$.
+% which again leads to a subsequence in $T$ violating $\orderrel$.
 % while in a subsequence of $T$ for a given $\indx$,

### 2018-07-09 p2/upd-correct.tex
New acyclic ordering relation

@@
 While this is trivial if we know that $U$ does not break $\FS$, we
-still need to show that it is defined.
+still need to show that it is defined on $\FS$.
 
-On systems where filesystem updates a recorded,
+On systems where filesystem updates are recorded,
 an alternative update detection algorithm is to
-omit step 1, and use \cref{can_simplify} to simplify the series of recorded updates into a simple sequence containing the necessary
-updates.
-In fact, we use such a hypothetical record in the proof \cref{update_works}.
+omit step 1, and use \cref{can_simplify} to simplify the series of recorded updates
+into a simple sequence containing the necessary updates.
+In fact, we use such a hypothetical record in the proof of \cref{update_works}.
 
@@
 \end{proof}
-
-An important consequence of this proof is that any sequence
-of recorded updates that were applied to a filesystem can be
-converted to a simple sequence using the rules listed in
-\cref{section_axioms} alone.

### 2018-07-09 p2/axioms.tex
Minor improvements

@@
 \myskip
-Our aim is to derive information about the effects of sequences
-of commands independently of the actual filesystems.
+One aim of our algebraic model is to
+derive as much information about the effects of sequences
+of commands independently of the actual filesystems as possible.
 In order to make this possible, we investigate the smallest building
@@
 
-\myskip
 Command pairs in general have the form

### 2018-07-09 p2/def-commands.tex
Minor improvements

@@
 \myskip
-For reasons also listed in \cite{NREC}, in this paper we will not consider
+For reasons also listed in \cite{NREC}, in this model we will not consider
 a \textit{move} or \textit{rename} command.
@@
 the dependencies for \textit{move} would call for a more complicated model.
-From a pragmatic perspective, this restriction does not mean that in an application
+As \cref{sec_multidir} details, this restriction does not mean that in an application
 implementing conflict resolution using the algorithm described here would not be
 able to handle renames by pre- and post-processing changes in the filesystem to
-discover them, which can enhance usability, but which
-(especially when a rename is combined with changes to the content)
-is a non-trivial problem in itself.
+discover them, which can enhance usability.

### 2018-07-10 p2/def-filesystem.tex
Minor improvements
Style tweaks

@@
 \end{mydef}
-
 We assume that the $\parent$ function does not induce loops, and so
@@
 
-\myskip
 In this paper

### 2018-07-10 p2/conclusion.tex
Minor improvements
Added conclusion

@@
 
+In this paper we presented an algebraic model to file synchronization,
+and defined an update detector and a reconciliation algorithm.
+With its extended command set the model was carefully designed to take
+advantage of an inherent symmetry of filesystem commands,
+which was enhanced by removing meta-information from directories
+as well as the \emph{move} command.
+These assumptions enabled us to prove that
+the update detector algorithm is correct (\cref{update_works}),
+and that reconciliation is not only correct (\cref{reconciliation_correct})
+but also yields maximal results (\cref{rec_is_complete}).
+
+We introduced relations and concepts that have proven particularly
+useful, including 
+independent commands, % (\cref{def_indep}), 
+simple sequences, % (\cref{def_min_simp}),
+and relationships between domains of sets of command sequences ($\worksmeqsign$)
+that allowed us to formalize the correctness of reconciliation.
+Among our partial results were interesting properties of these concepts,
+for example,
+that all legal permutations of simple sequences are equivalent (\cref{simple_reorder_equiv}),
+that command sequences can be transformed into simple sequences using syntactical rules (\cref{can_simplify}),
+or that the combination of independent sequences is defined wherever the components are defined (\cref{combine_independent_sequences}).
+We believe these results will prove useful outside their current usage as well.
+
+Our results can be immediately applied to practical filesystem synchronizers,
+which could benefit from e.g. recording changes using the extended command set,
+and from the theoretical background that guarantees their correct operation.
+Furthermore, with the encoding and decoding steps described in \cref{sec_multidir},
+the reconciliation algorithm can be extended to handle directory meta-information
+and the \emph{move} command,
+which makes our model applicable to more use cases and filesystems.
+
+\myskip
 Apart from constructing a filesystem-free algebra,
@@
 so that directory metadata could be represented directly
-as opposed to through pre- and post-processing as described
-in \cref{sec_multidir}.
+as opposed to through encoding and decoding steps.
 

### 2018-07-10 p2/def-commands.tex
Added conclusion

@@
 implementing conflict resolution using the algorithm described here would not be
-able to handle renames by pre- and post-processing changes in the filesystem to
+able to handle renames by post-processing changes in the filesystem to
 discover them, which can enhance usability.

### 2018-07-10 p2/intro.tex
Spellcheck
Added conclusion

@@
 The approach presented in this paper offers an improvement
-over results desribed in \cite{NREC} in multiple ways.
+over results described in \cite{NREC} in multiple ways.
 We introduce a new set of commands that is symmetric and
@@
 
-The paper is organised as follows.
+The paper is organized as follows.
 %
@@
 describe extending our model to widen its applicability;
-outline directions for further work on the introduced algebraic system,\
+outline directions for further work on the introduced algebraic system,
 and provide the conclusion.

### 2018-07-10 p2/multidir.tex
Minor improvements
Added conclusion

@@
 In this section we describe reasons why the latter assumption may not limit the applicability
-of even the current model, and we also describe pre- and post-processing steps
+of even the current model, and we also describe encoding and decoding steps
 to overcome the two restrictions.
@@
 and, if needed, conflict resolution on these settings can be easily automated.
-See, for example, the seminal work of Balasubramaniam and Pierce and the Unison synchronizer \cite{BP} and \cite{BZ}.
+See, for example, \cite{BZ} and the seminal work of Balasubramaniam and Pierce and the Unison synchronizer \cite{BP}.
 

### 2018-07-10 p2/upd-def.tex
Added conclusion

@@
 
-\begin{mydef}[Minimal and simple command sets and command sequences]
+\begin{mydef}[Minimal and simple command sets and command sequences]\mlabel{def_min_simp}
 A sequence or set of commands is \emph{minimal} if it contains at most one command on each node.

### 2018-07-12 p2/def-filesystem.tex
Style improvements

--- 2018-07-08 p2/def-filesystem.tex
@@
 
+We model filesystems using functions with a set of potential filesystem paths or \emph{nodes} ($\setn$) as their domain,
+and a set of possible contents or values ($\setv$) as their codomain.
+$\setn$  serves as a namespace for the filesystem:
+it contains all possible nodes, including the ones 
+where the file system contains no file or directory,
+and so for most filesystems it is infinite.
+Nodes in $\setn$ are also arranged in trees by a parent function ($\parent$) as described in \cref{def_noderel}.
+
 \begin{mydef}[Filesystems, $\FS$]
-We model a filesystem
-using a function $\FS$ with a set of nodes (potential filesystem paths) $\setn$ as its domain,
-and a set of possible contents or values $\setv$ as its codomain:
+A filesystem $\FS$ is a function
+mapping the set of nodes $\setn$ to values in $\setv$:
 \[ \FS: \setn \rightarrow \setv. \]
-We consider metadata to be part of the values in $\setv$.
-In this model, $\setn$ 
-serves as a namespace for the filesystem:
-it contains all possible nodes, including the ones 
-where the file system contains no file or directory.
 \end{mydef}
@@
 
-There is an ancestor / descendant relation defined over the nodes in $\setn$
+The tree-like structure of $\setn$ is determined by
+an ancestor / descendant relation defined over the nodes
 which arranges them in a disjoint union of rooted directed trees,
@@
 
-\begin{mydef}[Ordering on $\setn$: $\parent$, $\descendant$, $\descendantEq$, $\unrel$]
+\begin{mydef}[Ordering on $\setn$: $\parent$, $\descendant$, $\descendantEq$, $\unrel$]\mlabel{def_noderel}
 The partial function $\parent:\setn\nrightarrow\setn$
@@
 \end{mydef}
-
-We assume that the $\parent$ function does not induce loops, and so
+By assumption that the $\parent$ function does not induce loops, and so
 $\descendant$ is indeed a strict partial ordering.
@@
 is empty at a particular node, that is, there are no files or directories there.
-We also assume that a filesystem has finitely many non-empty nodes.
+We also assume that a filesystem has finitely many non-empty nodes,
+and we consider any kind of metadata to be part of the values in $\setv$.
 
 \begin{mydef}[Filesystem values: $\vald$, $\valfx$, $\empt$, $\eqclass{v}$]
-The set of values $\setv$ is partitioned into files, directories, and the empty value $\empt$.
+The set of values $\setv$ is partitioned into directories, files, and the empty value $\empt$.
 As usual, we write $[v]$ for the the equivalence class of $v\in\setv$ according to this partition,
-which represents its type.
-File and directory values are also denoted by $\valfx$ and $\vald$, respectively,
-with or without indices.
+which represents the type of the value.
+File and directory values are denoted by $\valfx$ and $\vald$, respectively,
+with or without indices, and so the partitioning is in fact $[\vald], [\valfx], [\empt]$.
 \end{mydef}
@@
 
-Every filesystem has a so-called \emph{tree property}, which means that
+Every filesystem must have a so-called \emph{tree property}, which means that
 if the filesystem is not empty at a node, and the node has a parent,
@@
 \begin{mydef}[Tree property]
-A filesystem $\FS:\setn \rightarrow \setv$ has the tree property iff
-\[ \forall n\in\setn
-\FS(n) \neq \empt \; \Longrightarrow \; [\FS(\parentf{n})] = [\vald] \]
+A filesystem $\FS$ has the tree property iff
+\[ \forall n\in\setn:
+\FS(n) \neq \empt \: \Longrightarrow \: \Big[\FS\big(\parentf{n}\big)\Big] = [\vald] \]
 wherever $\parent(n)$ is defined, that is, $n$ has a parent.
@@
 
-An essential assumption in our model is that there is only
+An essential additional assumption in our model is that there is only
 a \emph{single directory value} ($|\setd|=1$).
@@
 
-\myskip
-In this paper
+In the rest of paper
 we fix the skeleton $\langle\setn,\parent\rangle$,

### 2018-07-12 p2/intro.tex
Style improvements

@@
 Accordingly, in this paper command pairs, their commutativity and other properties
-play a special role.
+play a significant role.
 
@@
 is far from trivial.
-During the process, we define a number of useful concepts
+During the process, we define a number of auxiliary concepts
 and show their relationships and the properties they possess.
@@
 \Cref{sec_update} describes update detection and ordering filesystem commands.
-The main result of this section if that under some simple conditions,
+The main result of this section is that under some simple conditions,
 a set of filesystem commands executed in any feasible order leads

### 2018-07-16 p2/def-commands.tex
Improvements

@@
 (Some real-life filesystem commands like \textit{rmdir} do this already.)
-Because the success of failure of commands depends on types of values,
+Because the success or failure of commands depends on types of values,
 it is not necessary to encode the actual input value.
@@
 
-We model filesystem commands as partial functions 
+According to the above,
+we model filesystem commands with partial functions 
 that map filesystems to filesystems, but which
@@
 \end{mydef}
-For example, $\cbfa{n}$ represents \textit{create}$(n,\valf)$,
+For example, $\cbfa{n}$ represents \textit{create}$(n,\valfx)$,
 and $\cdba{n}$ represents \textit{rmdir}$(n)$.
@@
 does not match the type of the value in the filesystem at $n$, or if after replacing
-the value at $n$ with $y$, the resulting filesystem ceases to satisfy the tree property.
+the value at $n$ with $y$, the resulting filesystem ceases to satisfy the tree property
+in \cref{def_treeprop}.
 
 \myskip
-Depending on their input and output types, there are nine types of commands,
-which we separate into four categories depending on the overall effect of the command.
+There are nine groups of commands considering their input and output types.
+Based on these groups we separate commands into four categories 
+that reflect their overall effect.
 Constructions commands extend the filesystem,
@@
 For reasons also listed in \cite{NREC}, in this model we will not consider
-a \textit{move} or \textit{rename} command.
+a \textit{move (rename)} command.
 This turns out to be useful because this would be the only command that affects
@@
 the dependencies for \textit{move} would call for a more complicated model.
-As \cref{sec_multidir} details, this restriction does not mean that in an application
-implementing conflict resolution using the algorithm described here would not be
-able to handle renames by post-processing changes in the filesystem to
-discover them, which can enhance usability.
+As \cref{sec_multidir} details, even with this restriction,
+an implementation of the reconciliation algorithm presented here
+can still handle \emph{move} commands in its input and output
+by splitting them into \emph{delete} and \emph{create} commands,
+and merging them later.

### 2018-07-16 p2/def-filesystem.tex
Improvements

@@
 which represents the type of the value.
-File and directory values are denoted by $\valfx$ and $\vald$, respectively,
-with or without indices, and so the partitioning is in fact $[\vald], [\valfx], [\empt]$.
+Specific directory and file values are denoted by $\vald$ and $\valfx$, respectively,
+and so the partitioning is in fact $[\vald], [\valfx], [\empt]$.
 \end{mydef}
@@
 Using the notation introduced above, we can formally express this as follows.
-\begin{mydef}[Tree property]
+\begin{mydef}[Tree property]\mlabel{def_treeprop}
 A filesystem $\FS$ has the tree property iff
@@
 is one of the main contributions of this paper.
-In \cref{sec_multidir} we explore the applicability of our model given this assumption:
+In \cref{sec_multidir} we explore the applicability of our model given this assumption;
+specifically,
 why applicability may not be affected and ways to relax this restriction.
+
+We also assume that there are multiple different file contents, that is, $|[\valfx]|>1$.
 

### 2018-07-17 p2/axioms.tex
Style tweaks
Minor improvements

@@
 In particular, we write $\wrks{A}$
-to mean that $\Dom{A}$ is not empty, that is, if $A$ is defined on some filesystems.
+to mean that $\Dom{A}$ is not empty, that is, $A$ is defined on some filesystems.
 \end{mydef}
@@
             \cbda{\pn}&\cc  \cbda{n} \\
-            \cfda{\pn}&\cc  \caaa{\empt}{\valff}{n} \\
+            \cfda{\pn}&\cc  \caaa{\empt}{\valf}{n} \\
             \cfda{\pn}&\cc  \cbda{n}
@@
             \cfba{n}&\cc  \cdba{\pn} \\
-            \cfba{n}&\cc  \caaa{\vald}{\valff}{\pn} \\
+            \cfba{n}&\cc  \caaa{\vald}{\valf}{\pn} \\
             \cdba{n}&\cc  \cdba{\pn} \\
-            \cdba{n}&\cc  \cdfa{\pn}
+            \cdba{n}&\cc  \cdfa{\pn} \qedhere
    \end{align*}
 \end{mydef}
-
 We can see that construction pairs consist of construction commands,
@@
 \Cref{sec_algebra} elaborates this approach.
-In \cref{axiom_proof} we offer proofs of each of the
-\emph{\namecrefs{ax_separate_commute}} based on our model of filesystems.
 

### 2018-07-17 p2/def-commands.tex
Minor improvements

@@
 the value at $n$ with $y$, the resulting filesystem ceases to satisfy the tree property
-in \cref{def_treeprop}.
+as described in \cref{def_treeprop}.
 
@@
 Based on these groups we separate commands into four categories 
-that reflect their overall effect.
-Constructions commands extend the filesystem,
+that reflect their overall effect:
+construction commands extend the filesystem,
 while destruction commands shrink it;
@@
 (which may or may not be different from the original value),
-and assertion commands either break the filesystem, or assert the type of the value at a node.
+and assertion commands simply assert the type of the value at a node.
 \begin{mydef}[Command categories]\mlabel{def:command_categories}
@@
 \item[]\emph{Replacement command:}
-    $\caaa{\valfx}{\valff}{n}$.
+    $\caaa{\valfx}{\valf}{n}$.
 \qedhere
@@
 the dependencies for \textit{move} would call for a more complicated model.
-As \cref{sec_multidir} details, even with this restriction,
+As detailed in \cref{sec_multidir}, even with this restriction,
 an implementation of the reconciliation algorithm presented here

### 2018-07-17 p2/axiom-def.tex
Improvements

@@
 \newcommand{\axaxseparatecommute}{
-Commands on incomparable nodes commute: $\cxynv\cc\czwmv \equiv \czwmv\cc\cxynv$ where $n\unrel m$.
+Commands on incomparable nodes commute:
+$\cxynv\cc\czwmv \equiv \czwmv\cc\cxynv$
+when $n\unrel m$.
 }
@@
 Commands on incomparable nodes also do not break all filesystems:
-$\wrksx{\cxynv\cc\czwmv}$ where $n\unrel m$.
+$\wrksx{\cxynv\cc\czwmv}$
+when $n\unrel m$.
 }
@@
 Commands on the same node break every filesystem if their types are incompatible:
-$\cxynv\cc\czwnv \equiv \cbrk$ where $[y]\ne [z]$.
+$\cxynv\cc\czwnv \equiv \cbrk$
+when $[y]\ne [z]$.
 }
@@
 and their outer types represent an assertion command:
-$\cxynv\cc\czwnv \eqext \emptyseq$ where $[y]=[z]$; and 
-$[x]=[\empt]$ and $[w]=[\empt]$,
-or $[x]=[\vald]$ and $[w]=[\vald]$.
+$\cxynv\cc\czwnv \eqext \emptyseq$ 
+when $[y]=[z]$, and
+$[x]$ and $[w]$ are either both $[\empt]$ or both $[\vald]$.
 }
@@
 and their outer types do not represent an assertion command:
-$\cxynv\cc \czwnv \equiv \cxwnv$ where $[y]=[z]$; and
-neither $[x]=[\empt]$ and $[w]=[\empt]$,
-nor $[x]=[\vald]$ and $[w]=[\vald]$.
+$\cxynv\cc \czwnv \equiv \cxwnv$
+when $[y]=[z]$, and
+$[x]$ and $[w]$ are neither both $[\empt]$ nor both $[\vald]$.
 }
@@
 or an empty node at the child:
-$\cxypnv\cc\czwnv \equiv \cbrk$ where $\cxypnv\cc\czwnv$ is not a construction pair, 
+$\cxypnv\cc\czwnv \equiv \cbrk$ when $\cxypnv\cc\czwnv$ is not a construction pair, 
 $\cxypnv\neq\cdda{\pn}$ and $\czwnv\neq\cbba{n}$.
@@
 or a directory at the parent:
-$\cxynv\cc\czwpnv \equiv \cbrk$ where $\cxynv\cc\czwpnv$ is not a destruction pair,
+$\cxynv\cc\czwpnv \equiv \cbrk$ when $\cxynv\cc\czwpnv$ is not a destruction pair,
 $\cxynv\neq\cbba{n}$ and $\czwpnv\neq\cdda{\pn}$.
@@
 and $\czwnv\cc\cxynnv \equiv\cbrk$
-where $\nn\descendant n$ and $\nn\neq\parent(n)$, and $\cxynnv\neq\cdda{\nn}$ and $\czwnv\neq\cbba{n}$.
+when $\nn\descendant n$ and $\nn\neq\parent(n)$, and $\cxynnv\neq\cdda{\nn}$ and $\czwnv\neq\cbba{n}$.
 }
@@
 \[ \cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n} \] 
-where $\nn\descendant n$ and $\cxynnv\neq\cdda{\nn}$.
+when $\nn\descendant n$ and $\cxynnv\neq\cdda{\nn}$.
 }
@@
 \[ \cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn} \]
-where $\nn\descendant n$ and $\cxynv\neq\cbba{n}$.
+when $\nn\descendant n$ and $\cxynv\neq\cbba{n}$.
 }

### 2018-07-17 p2/axioms.tex
Improvements

@@
 of command sequences without any assertion commands.
+The \namecrefs{ax_separate_commute} can be derived from the filesystem model
+relatively easily. Proofs are included in \cref{axiom_proof}.
 
@@
 Two commands $\alpha$ and $\beta$ 
-are independent, and we write $\alpha\indep\beta$ if 
+are independent, written as $\alpha\indep\beta$, if 
 they commute and do not break all filesystems:
@@
 It is intentional that we use the same symbol for independent commands
-and sequences as for incomparable nodes. As
-\namecref{incomparable_is_independent},
+as for incomparable nodes. As the
+\namecref{incomparable_is_independent} below
 shows, these concepts are closely related.
@@
 
-To prove this, we are going to prove the following lemma,
+\Cref{incomparable_is_independent} follows independently from
+the following lemma,
 which characterizes independent commands in a more detailed way.
@@
 \begin{itemize}
-\item $n\unrel m$;
-\item or $n=m$ and the commands are equivalent assertion or replacement commands;
-\item or $n\descendant m$ or $m\descendant n$,
-and either the command on the ancestor asserts a directory,
+\item $n\unrel m$,
+\item $n=m$ and the commands are equivalent assertion or replacement commands,
+\item either $n\descendant m$ or $m\descendant n$,
+\emph{and} either the command on the ancestor asserts a directory,
 or the command on the descendant asserts an empty node (or both).
@@
 
-\Cref{incomparable_is_independent} follows directly from \cref{independent_details}.
-While equivalent commands can hardly be thought of as independent,
+While equivalent commands can hardly be considered independent,
 we retain this name for this relation as in most

### 2018-07-18 p2/ordering.tex
Style tweaks
Improvements
Further minor improvements

@@
 
-As we recognize that multiple orders may be possible,
-let us describe our ordering algorithm by
-defining a subset of the permutations, $\ordersetsign$.
-As we will see, $\ordersetsign$ contains all possible
+As multiple orders may be possible,
+we describe our ordering algorithm by
+defining a subset of the permutations of the commands, $\ordersetsign$.
+\Cref{simple_reorder_equiv} proves that $\ordersetsign$ indeed contains all possible
 sequences of commands that do not break all filesystems.
-In \cref{simple_reorder_equiv}, we offer a formal proof of this.
 The facts that all valid reorderings of simple sequences are equivalent,
-and all equivalent sequences are reorderings, are important 
+and all equivalent sequences are reorderings follow from this \namecref{simple_reorder_equiv}, and are important 
 properties of simple sequences.
@@
 \item $\caaa{x}{y}{\parentf{n}} \orderrel \caaa{z}{w}{n}$ if both commands are construction commands, and
-\item $\caaa{x}{y}{n} \orderrel \caaa{z}{w}{\parentf{n}}$ if both commands are destruction commands.
+\item $\caaa{x}{y}{n} \orderrel \caaa{z}{w}{\parentf{n}}$ if both commands are destruction commands. \qedhere
 \end{itemize}
@@
 and as a command cannot be both a construction and a destruction command and
-the relation follows the tree of nodes, it is acyclic,
-and thus defines a partial order.
+the relation follows the tree of nodes, it is acyclic.
+Therefore its transitive closure, also denoted by $\orderrel$, is a partial order.
 
@@
 For a simple sequence of commands $\wrksx{S}$,
-$\orderset{S}$ is the set of permutations satisfying the partial order defined by $\orderrel$.
+$\orderset{S}$ is the set of permutations of the commands in $S$ respecting the partial order defined by $\orderrel$,
+that is,
+for any $T\in\orderset{S}$ and any $\alpha,\beta\in T$, if $\alpha\orderrel\beta$ then $\alpha$
+precedes $\beta$ in $T$.
 % For a simple set or sequence of commands $S$,
@@
 % As usual, by subsequence we mean a subset of the commands in $S$ in the same order as they are found in $S$.
-The simplicity of the definitions mean that sorting the commands
-and enumerating
-all sequences in $\ordersetsign$ can be implemented by a straightforward
-algorithm.
+Returning a valid $T\in\orderset{S}$ order for a set of commands $S$
+can be implemented using any well-known algorithm for topological sorting,
+where the directed acyclic graph that is the input of the algorithm is defined by $\orderrel$.
 
-The principal ideas behind the ordering are 
+The principal ideas behind the definition of $\orderrel$ are 
 \cref{ax_separate_commute}, from which we know that commands on incomparable
@@
 \end{mycor}
+
+This follows directly from \cref{def_orderset}.
 
@@
 other than $y$.
-(We assume that there are more than one file values; if this is not so,
-$\cffa{n}$ becomes an assertion command.)
 From here the proof concludes in the same way as above.

### 2018-07-18 p2/upd-def.tex
Further minor improvements

--- 2018-07-09 p2/upd-def.tex
@@
 all operations that modified the two filesystems, in most filesystem implementations
-such records are not implemented, and therefore we must construct suitable sequences
+such records do not exist, and therefore we must construct suitable sequences
 by comparing $\FS_1$ (and $\FS_2$) to their common ancestor, $\FS$. 
@@
 The set of commands $U$ necessary to transform $\FS$ into $\FS_1$ can be collected
-by inspecting the (necessarily finite) union of non-empty nodes in the two filesystems.
+by inspecting the (finite) union of non-empty nodes in the two filesystems.
 If at node $n$, $\FS(n)=x$ and $\FS_1(n)=y\neq x$, then we add the command $\cxyaa{n}$ to $U$.
@@
 
-To be able to reason about sets and sequences of commands, let us introduce the following properties:
+% To be able to reason about sets and sequences of commands, let us introduce the following properties:
 
-\begin{mydef}[Minimal and simple command sets and command sequences]
+\begin{mydef}[Minimal and simple command sets and sequences]\mlabel{def_min_simp}
 A sequence or set of commands is \emph{minimal} if it contains at most one command on each node.

### 2018-07-18 p2/ordering.tex
Text review

@@
 \begin{mylem}\mlabel{simple_distant_pairs}
-For any simple sequence $\wrksx{S}$,
-if $\cxynv\cc\czwmv$ is a subsequence of $S$ and $n=\parent(m)$ or $\parent(n)=m$,
-then $\cxynv\cc\czwmv$ is either a construction or a destruction pair.
+For any simple sequence $\wrksx{S}$ and its subsequence $\cxynv\cc\allowbreak\czwmv$,
+if $n=\parent(m)$, then the subsequence is a construction pair;
+and if $\parent(n)=m$, then the subsequence is a destruction pair.
 \end{mylem}
@@
 and in this version of the proof we reach back to our filesystem model.
-We assume $\wrks{S}$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
-but $S$ contains commands on a node and its parent that do not form a construction or destruction pair.
-Select two such commands, $\cxynv$ and $\czwmv$,
+By assumption $\wrks{S}$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$.
+Select two commands on a node and its parent, $\cxynv$ and $\czwmv$,
 and split $S$ around them into three parts:
-\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2. \]
-As $S$ is simple, there cannot be any commands on $n$ or $m$ in $S_1$,
-and therefore $(S_0\cc\cxynv\cc S_1)\FS(n) = y$,
-and $[(S_0\cc\cxynv\cc S_1)\FS(m)] = [S_0\FS(m)]$.
-If $[z]\neq[S_0\FS(m)]$, then $S\aFS=\fsbroken$, which is a contradiction.
+\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2, \]
+where any of the three parts can be empty.
+As $S$ is simple, there are no commands on $n$ or $m$ in $S_0$, $S_1$, or $S_2$,
+and therefore $(S_0\cc\cxynv\cc S_1)\aFS(n) = y$,
+and $[(S_0\cc\cxynv\cc S_1)\aFS(m)] = [S_0\aFS(m)]$,
+and so $[z]$ must be $[S_0\aFS(m)]$.
 
 If $n=\parent(m)$, then 
-we know $(S_0\cc\cxynv\cc S_1)\FS(n) = y$, and as $[z]\neq[w]$, either
-$[(S_0\cc\cxynv\cc S_1)\FS(m)]=[z]\neq[\empt]$,
-or $[(S_0\cc\cxynv\cc S_1\cc\czwmv)\FS(m)]=[w]\neq[\empt]$.
+we know $(S_0\cc\cxynv\cc S_1)\aFS(n) = y$, and as $[z]\neq[w]$, either
+$[(S_0\cc\cxynv\cc S_1)\allowbreak\aFS(m)]=[z]\neq[\empt]$,
+or $[(S_0\cc\cxynv\cc S_1\cc\czwmv)\allowbreak\aFS(m)]=[w]\neq[\empt]$.
 Therefore $y$ must be $\vald$, as otherwise the tree property would be violated
@@
 and $[x]\neq[\vald]$ as $\cxynv$ is not an assertion command.
-As $[S_0\FS(n)]=[x]\neq[\vald]$, we know
-$S_0\FS(m)=\empt$ as otherwise the tree property would be violated.
-Therefore $[S_0\FS(m)]=[z]=[\empt]$, which, combined with $y=\vald$
-means that $\cxynv\cc\czwmv$ is a construction pair, which is a contradiction.
+As $[S_0\aFS(n)]=[x]\neq[\vald]$, we know
+$S_0\aFS(m)=\empt$ as otherwise the tree property would be violated.
+Therefore $[S_0\aFS(m)]=[z]=[\empt]$, which, combined with $y=\vald$
+means that $\cxynv\cc\czwmv$ is a construction pair.
 
 If $\parent(n)=m$, then 
-as $(S_0\cc\cxynv\cc S_1)\FS(n) = y$, and either
-$[(S_0\cc\cxynv\cc S_1)\FS(m)]=[z]\neq[\vald]$
-or $[(S_0\cc\cxynv\cc S_1\cc\czwmv)\FS(m)]=[w]\neq[\vald]$,
+as $(S_0\cc\cxynv\cc S_1)\aFS(n) = y$, and either
+$[(S_0\cc\cxynv\cc S_1)\allowbreak\aFS(m)]=[z]\neq[\vald]$
+or $[(S_0\cc\cxynv\cc S_1\cc\czwmv)\allowbreak\aFS(m)]=[w]\neq[\vald]$,
 $y$ must be $\empt$, and $[x]\neq[\empt]$.
-As $[S_0\FS(n)]=[x]\neq[\empt]$, we know $S_0\FS(m)=\vald$.
-Therefore $[S_0\FS(m)]=[z]=[\vald]$, which, combined with $y=\empt$
-means that $\cxynv\cc\czwmv$ is a destruction pair, which is a contradiction.
+As $[S_0\aFS(n)]=[x]\neq[\empt]$, we know $S_0\aFS(m)=\vald$.
+Therefore $[S_0\aFS(m)]=[z]=[\vald]$, which, combined with $y=\empt$
+means that $\cxynv\cc\czwmv$ is a destruction pair.
 \end{proof}
@@
 This follows directly from \cref{simple_distant_pairs}.
-We use an inverse proof and assume $\wrksx{S'}$.
 If $S'\not\in\orderset{S}$ then by \cref{def_orderrel,def_orderset}
-it contains two commands on a node $n$ and its parent
+$S'$ contains two commands on a node $n$ and its parent
 that, as a subsequence,
-cannot form a construction or destruction pair.
-However, this contradicts \cref{simple_distant_pairs}
-which means that no such subsequence exists.
+form a construction or destruction pair in the wrong order.
+\Cref{simple_distant_pairs} implies that no such subsequence exists
+if $\wrksx{S'}$, and therefore $S'\equiv\cbrk$.
 \end{proof}
@@
 and which can be applied to a filesystem in some order without breaking it,
-and which contains commands on $n$ and $\nn$ where $\nn\descendant n$,
+and which contains commands on $\nn$ and $n$ where $\nn\descendant n$,
 then the set must also contain a command
-on each node between $n$ and $\nn$.
+on each node between $\nn$ and $n$.
 \end{mylem}

### 2018-07-18 p2/multidir.tex
Text review

@@
 The two assumptions we used to increase the symmetry of our model were
-that there is no move command,
+that there is no \emph{move} command,
 and that
@@
 In these cases, the synchronizer can either fall back to default values and flag the issue
-for review later, or if, as suggested above, conflicts on the metadata (e.g. readable, writable and executable flags)
+for review later, or if, as suggested above, resolution of conflicts on the metadata (e.g. readable, writable and executable flags)
 can be easily automated, then it could form part of the implementation.
@@
 If the command sequences are derived from filesystem journals, they
-can be broken into two updates to allow the existing reconciliation
+can be encoded as separate delete and create operations to allow the existing reconciliation
 algorithm to operate.

### 2018-07-18 p2/ordering.tex
Text review

@@
 and another command $\czwnnv$ on $\nn$.
-We use a proof by contradiction and assume that there are no commands on $\parent(n)$ in $A$.
+By contradiction assume that there are no commands on $\parent(n)$ in $A$.
 Next, we create a new sequence $A'\equiv A$ in which $\cxynv$ and $\czwnnv$ are next to each other.
@@
 from \cref{ax_distantrel_breaks} we get $A\equiv\cbrk$ which contradicts our assumptions.
-(Note that $A$ cannot contain assertion commands.)
+(Note that $A$ does not contain assertion commands.)
 By repeating this step we can therefore convert $A$ into $A'$ where $\cxynv$ and $\czwnnv$ are neighboring commands.
@@
 First, we prove, by contradiction, that if $T$ is a simple sequence and $T\equiv S$, then $T\in\orderset{S}$.
-We use an inverse proof and assume $T\equiv S$ and $T\not\in\orderset{S}$.
+Assume $T\equiv S$ but $T\not\in\orderset{S}$.
 Then, from \cref{equiv_simple_same_commands} we know $T$ is a permutation of $S$,
@@
 We proceed by induction on the length of $S$.
-Our base cases are $\emptyseq$, where $\orderset{\emptyseq}=\{\emptyseq\}$,
-and one-long sequences, where this is trivially true.
+Our base cases are $\emptyseq$, when $\orderset{\emptyseq}=\{\emptyseq\}$,
+and one-long sequences, when this is trivially true.
 In our induction step we assume that $T^*\in\orderset{S^*}\Rightarrow T^*\equiv S^*$ holds
@@
 Let the first command in $S$ be $\cxynv$, that is, $S=\cxynv\cc S_0$.
-We proceed by a nested induction on the number of commands before $\cxynv$ in $T$.
-Our base case is when it is the first command, which means $T=\cxynv\cc T_0$.
+We proceed by a nested induction on $j$, the number of commands before $\cxynv$ in $T$.
+Our base case is $j=0$, when it is the first command, which means $T=\cxynv\cc T_0$.
 Then from \cref{subseq_in_orderset} we know $T_0\in\orderset{S_0}$
@@
 Also, let $I^S_\indx$ be the index of the command on $n_\indx$ in $S$.
-For all $\indx$, both the commands on $n_\indx$ and $n_{\indx+1}$ must be either
+By \cref{simple_distant_pairs}, for all $\indx$, both the commands on $n_\indx$ and on $n_{\indx+1}$ must be either
 construction commands, or destruction commands, depending on
 whether $I^S_\indx<I^S_{\indx+1}$ or $I^S_{\indx+1}<I^S_\indx$.
-This is because otherwise, \cref{simple_distant_pairs} would not hold for $S$.
 
@@
 $\ordp{S}$ is the unique partial endofunction on filesystems
-defined by any order in $\orderset{S}$.
+defined by any sequence in $\orderset{S}$.
 % We leave $\ordp{S}$ undefined if such an order does not exist.
@@
 Building on the results above, we finish by proving an important result,
-namely, that command sequences can be made simple using syntactical operations.
+which states that command sequences can be made simple using syntactical operations only.
 
-\begin{mylem}\mlabel{can_simplify}
+\begin{myth}\mlabel{can_simplify}
 Each sequence of commands $\wrksx{S}$
 can be transformed into a simple sequence
-$T\equiv S$ by applying repeatedly the following transformations:
+$S^*\eqnrv S$ by applying repeatedly the following transformations:
 {\rm(i)} swap neighboring commands on incomparable nodes;
@@
 {\rm(iii)} delete assertion commands.
-\end{mylem}
+\end{myth}
 \begin{proof}
@@
 
-We aim to find a simple sequence that is equivalent to $S$.
+We aim to find a simple sequence that extends $S$.
 If $S$ is already simple, there is nothing to do.
@@
 This is a contradiction as a command cannot be both.
-We arrive at the same contradiction if $m'=\parentf{n}$.
+We arrive at the same contradiction when $m'=\parentf{n}$.
 
@@
 We can apply \cref{ax_same_emptyseq,ax_same_singlec} to
-$\ucy\cc\ucx$ and get a $S'\eqext S$ that contains one or two less commands on $n$.
+$\ucy\cc\ucx$ and get a $S^*\eqext S$ that contains one or two less commands on $n$.
 Repeating the swap and the simplification we
-can convert $S$ into an equivalent simple sequence.
+can convert $S$ into a simple sequence.
 \end{proof}

### 2018-07-18 p2/upd-correct.tex
Minor improvements
Style tweaks
Text review

@@
 
-With $\ordersetsign$ we can now define our update detection algorithm.
+With the relation $\orderrel$ we can now define our update detection algorithm.
 Its inputs are the original filesystem $\FS$ which has been modified to yield $\FS^*$.
@@
     \item For each node $n$ where the value in $\FS$ and $\FS^*$ differ, add the command $\caaa{\FS(n)}{\FS^*(n)}{n}$ to
-        a set of commands $U_S$. The result is a simple set of commands.
+        a set of commands $U^*$. The result is a simple set of commands.
     \item Order the commands according to $\orderrel$, that is, 
-        return any sequence $U$ from $\orderset{U_S}$.
+        return any sequence $U$ from $\orderset{U^*}$. \qedhere
 \end{enumerate}
@@
 
-\Cref{update_works} proves that $U$ functions as expected, that is, $U\aFS=\FS^*$.
+\Cref{update_works} below proves that $U$ functions as expected, that is, $U\aFS=\FS^*$.
 While this is trivial if we know that $U$ does not break $\FS$, we
@@
 Based on \cref{can_simplify}, there is a simple sequence $S^*$
-that is equivalent to $S$.
+that extends $S$.
 

### 2018-07-19 p2/ordering.tex
Review

@@
 can be transformed into a simple sequence
-$S^*\eqnrv S$ by applying repeatedly the following transformations:
+$S^*\eqnrw S$ by applying repeatedly the following transformations:
 {\rm(i)} swap neighboring commands on incomparable nodes;

### 2018-07-19 p2/rec-intro.tex
Added conclusion
Review

@@
-If we start with two copies of the filesystem $\FS$,
+If we start with two copies of a filesystem $\FS$,
 and two different sequences are applied to the copies to yield $\FS_A=A\aFS$
@@
 \begin{mydef}[Reconciliation]\mlabel{def:reconciliation}
-We determine $\reca$---which we apply to $\FS_B$ 
-to reconcile it with $\FS_A$---to be
+For two simple sequences $A$ and $B$,
+$\reca$ is a valid ordering of
 the largest subset of $A\setminus B$
-that is independent of $B\setminus A$,
-where $A$ and $B$ are simple sequences representing
-the updates applied to $\FS$ to arrive at replicas $\FS_A$ and $\FS_B$:
+that is independent of $B\setminus A$:
 \[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \mbox{~and~}  \alpha\indep \bmanp }. \]
@@
 
-Note that $\alpha$ is not an assertion command, and $\bmanp$ contains no assertion commands;
-also, $\alpha\not\in\bmanp$, so independence in this case is equivalent to
+Note that $\alpha\in\reca$ is not an assertion command, and $\bmanp$ contains no assertion commands,
+and $\alpha\not\in\bmanp$, therefore $\alpha\indep\bmanp$ is equivalent to
 the node $\alpha$ affects being incomparable to the nodes commands in $\bmanp$ affect.
@@
 Then, to generate the sequence $\reca$ from the resulting set, 
-we can order the commands using the algorithm described in
-\cref{ordering} as $\reca$, being a subset of $A$, is also simple.
+apply topological sorting according to $\orderrel$ as defined in \cref{ordering}.
 

### 2018-07-19 p2/upd-correct.tex
Review

@@
 \begin{proof}
-Let us assume that some mechanism recorded all changes that occurred
-to $\FS$ until it reached the state $\FS^*$.
-Our set of commands is sufficient to record any change, as
-there are commands for every input and output type pair, therefore
-we know that the changes can be recorded as a sequence of commands $S$
-where $S\aFS=\FS^*$.
-($S$ will not contain assertion commands, as they do not
-represent an actual change in the filesystem.)
-Based on \cref{can_simplify}, there is a simple sequence $S^*$
-that extends $S$.
+First, we create a sequence of commands $S$ for which $S\aFS=\FS^*$.
+First, create a topological sort of all nodes in $\setn$ that are
+not empty in $\FS$ so that children come first,
+that is, if $n'\descendant n$, then $n$ precedes $n'$.
+For each node in the given order, add a destruction command to a sequence $S_0$
+that deletes the value at $n$.
+We know that the commands will never break the filesystem, as the types of nodes
+with empty children can be freely changed, and that $S_0\aFS$ is empty at all nodes.
+Next, order nodes in $\setn$ that re not empty in $\FS^*$ in the reverse order,
+that is, if $n'\descendant n$, then $n'$ precedes $n$.
+Add a construction command to a sequence $S_1$ for each node that changes an empty value
+to $\FS^*(n)$.
+We know that $S_1$ is defined on an empty filesystem for the same reason,
+and clearly $(S_0\cc S_1)\aFS=\FS^*$.
+By \cref{can_simplify} there exists a simple $S$ for which $S\eqnrw (S_0\cc S_1)$.
 
-Therefore we know $S^*\aFS=\FS^*$, and that
-$\FS^*$ and $\FS$ differ at exactly those nodes that $S^*$ has commands on.
+Therefore we know $S\aFS=\FS^*$, and that
+$\FS^*$ and $\FS$ differ at exactly those nodes that $S$ has commands on.
 $U$ must also contain commands on the same set of nodes,
@@
 as for the command $\cxynv$, $[x]$ must be $[\FS(n)]$, and $y$ must be $\FS^*(n)$.
-From this we know that $U$ is a permutation of $S^*$ and so $\orderset{U}=\orderset{S^*}$.
+From this we know that $U$ is a permutation of $S$ and so $\orderset{U}=\orderset{S}$.
 
-As the update detector uses $\orderrel$ to order the commands in $U$, trivially $U\in\orderset{U}$,
-which means $U\in\orderset{S^*}$,
-and so from \cref{simple_reorder_equiv} we know that $U\equiv S^*$,
+As the update detector uses the $\orderrel$ relation to order the commands in $U$, trivially $U\in\orderset{U}$,
+which means $U\in\orderset{S}$,
+and so from \cref{simple_reorder_equiv} we know that $U\equiv S$,
 from which $U\aFS=\FS^*$.

### 2018-07-20 p2/conclusion.tex
Text review

@@
 for example,
-that all legal permutations of simple sequences are equivalent (\cref{simple_reorder_equiv}),
+that all permutations of simple sequences satisfying a partial order are equivalent (\cref{simple_reorder_equiv}),
 that command sequences can be transformed into simple sequences using syntactical rules (\cref{can_simplify}),

### 2018-07-20 p2/rec-intro.tex
Text review

@@
 As some commands may have been applied to both filesystems, our first approximation
-is $\reca = \amb$ and $\recb = \bma$.
+is to apply the commands in $\bmanp$ to $\FS_A$ and those in $\ambnp$ to $\FS_B$.
 This, however, will break both filesystems if there have been incompatible updates
@@
 so that $\reca\aFS_B\neq\fsbroken$ and $\recb\aFS_A\neq\fsbroken$,
-and show that these are the longest sequences with this property, that is,
+and show that these are maximal in the sense that
 adding any further command to $\reca$ or $\recb$ will break the filesystems.
 
-We assume that $A$ and $B$ are returned by an update detector,
-and so they are simple sequences.
-(Otherwise, they can be simplified to become simple sequences; see \cref{can_simplify}.)
-We also assume that $\FS$, $\FS_A$ and $\FS_B$ are not broken.
-With these assumptions,
-we can now define our reconciliation algorithm.
+We will work based on update sequences $A$ and $B$ that are simple.
+If the reconciliation algorithm is to work on arbitrary sequences,
+\cref{can_simplify} can be used to convert those sequences to simple ones.
 
@@
 and $\alpha\not\in\bmanp$, therefore $\alpha\indep\bmanp$ is equivalent to
-the node $\alpha$ affects being incomparable to the nodes commands in $\bmanp$ affect.
-Therefore whether two commands are independent is easy to determine programmatically
-in at most $O(x^2)$ time, where $x$ is the number of commands. % TODO
+the node of $\alpha$ being incomparable to the nodes of the commands in $\bmanp$.
+Therefore whether two commands are independent 
+for the purposes of reconciliation
+is easy to determine programmatically.
 Then, to generate the sequence $\reca$ from the resulting set, 
@@
 \myskip
-Next, we would now like to prove that $\reca$ and $\recb$ can be applied to the replicas,
+We aim prove that $\reca$ and $\recb$ can be applied to the replicas,
 that is, without loss of generality,
@@
 So that we can formalize statements needed to prove this,
-let us introduce partial orders that describe under what conditions
+we introduce the partial order $\worksmeqsign$ that describes under what conditions
 sequences of commands work, that is, do not break a filesystem.

### 2018-07-20 p2/rec-sound.tex
Added conclusion
Text review

@@
 
-We show that $A$ can be transformed into $A'$ for which this is true.
 We know that if the marked commands are not at the beginning, then
@@
 Then, by repeating this process similarly to bubble sorting, we arrive at 
-a suitable permutation of $A$, which is also equivalent to $A$, and therefore in $\orderset{A}$.
+a suitable permutation of $A$, which is also equivalent to $A$, and therefore is in $\orderset{A}$.
 
@@
 
-We would like to prove that $\worksmbx{A,B}{B\cc \reca}$.
+We aim to prove that $\worksmbx{A,B}{B\cc \reca}$.
 From \cref{can_move_intersection} above we know that we can move commands in $\acbnp$
-to the beginning of $A$ and $B$, and so this is equivalent to
+to the beginning of $A$ and $B$, and so this claim is equivalent to
 \[ \worksm{\big\{\acb\cc\amb,~ \acb\cc\bma\big\}}{\acb\cc \bma\cc \reca}. \]
@@
 For ease of reading, let us rename
-\begin{itemize}
-\item $\amb$ to $S$,
-\item $\reca$ to $S^*$,
-\item $\bma$ to $T$,
-\item and $\acb$ to $U$.
-\end{itemize}
+ $\amb$ to $S$,
+ $\reca$ to $S^*$,
+ $\bma$ to $T$,
+ and $\acb$ to $U$.
 In this notation, we intend to prove that
@@
 \begin{itemize}
-\item $S=\amb$ and $T=\bma$ are simple as $A$ and $B$ are simple
-\item $S\cap T = \amb \cap \bma = \emptyset$
+\item $S=\amb$ and $T=\bma$ are simple as $A$ and $B$ are simple;
+\item $S\cap T = \amb \cap \bma = \emptyset$;
 \item $S^*$ is the largest subset of $S$ for which $S^*\indep T$, as
@@
 \end{itemize}
-Our theorem is therefore proven if we prove the following lemma.
+Our theorem is therefore proven if we prove that these imply the proposition above:
 \newcommand{\condSimple}{(c1)}

### 2018-07-20 p2/works-inverse.tex
Resolve TODOs
Spellcheck
Text review

@@
 \begin{mydef}[Sets of sequences, their domains]
-As we will frequently refer to sets of fequences,
+As we will frequently refer to sets of sequences,
 we will use calligraphic letters (e.g. $\sqs{A}$, $\sqs{B}$, $\sqs{C}$ and $\sqs{S}$)
@@
 all filesystems on which sequences in $\sqs{A}$ are defined.
+We write $\sqs{A}\worksmsign\sqs{B}$ iff $\Dom{\sqs{A}} \subset \Dom{\sqs{B}}$.
 \end{mydef}
@@
 Also, we write $\worksmnil{\sqs{A}}$ to mean that
-there are filesystems on which all sequences in $\sqs{A}$ are defined.
+there is at least one filesystem on which all sequences in $\sqs{A}$ are defined.
 If $\sqs{A}$ contains a single sequence only, $A$, this is equivalent to $\wrks{A}$.
@@
 \begin{proof}
-This is because the function $S$ is a binary relation between filesystems,
+This is because the sequence $S$, as an endofunction on filesystems, is a binary relation,
 and we can treat its inverse relation as a one-to-many mapping between filesystems
@@
 \begin{proof}
+% BACK_TO_FS
 % In the following proof we reach back to our filesystem model.
-The proposition follows from \cref{independent_details},
+The proposition uses \cref{independent_details},
 and we follow the three cases listed there.
+Let $\alpha=\cxynv$ and $\beta=\czwmv$.
 
 The first case is that $n\unrel m$ where $\alpha=\cxynv$, $\beta=\czwmv$.
-Using an inverse proof we assume that for a filesystem $\FS$
-both $\cxynv\aFS$ and $\czwmv\aFS$ are defined, but $(\cxynv\cc\czwmv)\FS$ is broken.
+Assume, by contradiction, that for a filesystem $\FS$
+both $\cxynv\aFS$ and $\czwmv\aFS$ are defined, but $(\cxynv\cc\czwmv)\aFS$ is broken.
 Since $n\neq m$, we know the input types of the command are compatible with $\FS$,
-so $\FS$ must be broken because it violates the tree property.
+so $(\cxynv\cc\czwmv)\aFS$ must be broken because it violates the tree property.
 
@@
 \begin{proof}
-Assume that there is a filesystem $\FS$ so that
+Assume, by contradiction, that there is a filesystem $\FS$ so that
 $S\aFS\neq\fsbroken$ and $T\aFS\neq\fsbroken$, but
@@
 
-From \cref{def_indep} we know that
+From \cref{def_indep}
 the commands in $S$ and $T$ pairwise commute, and so any sequence
@@
 \begin{proof}
-This result is similar to \cref{equiv_simple_same_commands} and
-is easily shown using a proof by contradiction: if $[x]\neq [z]$, then there is no filesystem that
+This result is similar to \cref{equiv_simple_same_commands}.
+If, by contradiction, $[x]\neq [z]$, then there would be no filesystem that
 either $\cxynv$ or $\czwnv$ would not break, 
-and consequently $S$ and $T$ cannot work on the same filesystem.
+and consequently $S$ and $T$ could not work on the same filesystem.
 \end{proof}

### 2018-07-20 p2/axiom-proof.tex
Review
Formatting

@@
 
+\begin{sloppypar}
 We can proceed in the same fashion if $\czwmv\aFS$ is not broken, but
 $(\czwmv\cc\cxynv)\aFS$ is.
+\end{sloppypar}
 \end{proof}
@@
 This is equivalent to saying that $\cxynv\cc \czwnv$ does not break the filesystem.
-
 We note that if $\cxwnv$ is an assertion command, then it extends $\cxynv\cc\czwnv$
@@
 The two assertion commands $\cdda{n}$ and $\cbba{n}$ either
-breaks a filesystem, or leaves it in the same state.
+break a filesystem, or leave it in the same state.
 \end{proof}

### 2018-07-20 p2/axiom-def.tex
Final changes

@@
 \newcommand{\axaxdirectchildbreaks}{
+\begin{sloppypar}
 Commands on a parent and a child node break every filesystem
@@
 $\cxypnv\neq\cdda{\pn}$ and $\czwnv\neq\cbba{n}$.
+\end{sloppypar}
 }
@@
 \newcommand{\axaxdirectparentbreaks}{
+\begin{sloppypar}
 Commands on a child and parent node break every filesystem
@@
 $\cxynv\neq\cbba{n}$ and $\czwpnv\neq\cdda{\pn}$.
+\end{sloppypar}
 }

### 2018-07-20 p2/axioms.tex
Final changes

@@
 
-\Cref{incomparable_is_independent} follows independently from
-the following lemma,
+\Cref{incomparable_is_independent} follows from
+the next \namecref{independent_details},
 which characterizes independent commands in a more detailed way.

### 2018-07-20 p2/rec-intro.tex
Final changes

@@
 so that $\reca\aFS_B\neq\fsbroken$ and $\recb\aFS_A\neq\fsbroken$,
-and show that these are maximal in the sense that
-adding any further command to $\reca$ or $\recb$ will break the filesystems.
+and show that these are the longest sequences with this property.
 
@@
 If the reconciliation algorithm is to work on arbitrary sequences,
-\cref{can_simplify} can be used to convert those sequences to simple ones.
+\cref{can_simplify} can be used to convert these sequences to simple ones.
 
@@
 So that we can formalize statements needed to prove this,
-we introduce the partial order $\worksmeqsign$ that describes under what conditions
+we introduce the partial order $\worksmeqsign$ that describes conditions under which
 sequences of commands work, that is, do not break a filesystem.

### 2018-07-20 p2/upd-correct.tex
Final changes

@@
 into a simple sequence containing the necessary updates.
-In fact, we use such a hypothetical record in the proof of \cref{update_works}.
-
-% There is a sequence between any two states: destroy one completely and construct the other one. (finite FS)
 
@@
 First, we create a sequence of commands $S$ for which $S\aFS=\FS^*$.
-First, create a topological sort of all nodes in $\setn$ that are
+We create a topological sort of all nodes in $\setn$ that are
 not empty in $\FS$ so that children come first,
 that is, if $n'\descendant n$, then $n$ precedes $n'$.
-For each node in the given order, add a destruction command to a sequence $S_0$
+For each node in the given order, we add a destruction command to a sequence $S_0$
 that deletes the value at $n$.
@@
 with empty children can be freely changed, and that $S_0\aFS$ is empty at all nodes.
-Next, order nodes in $\setn$ that re not empty in $\FS^*$ in the reverse order,
+Next, we order nodes in $\setn$ that are not empty in $\FS^*$ in the reverse order,
 that is, if $n'\descendant n$, then $n'$ precedes $n$.
-Add a construction command to a sequence $S_1$ for each node that changes an empty value
+We add a construction command to a sequence $S_1$ for each node that changes an empty value
 to $\FS^*(n)$.
